### 2025-03-07 edipack2.tex
first commit

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
%% 5p,twocolumn, preprint, review
\documentclass[final,3p,10pt]{elsarticle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{makecell}

\usepackage{xcolor}

%% natbib.sty is loaded by default. natbib options with \biboptions{...}
\biboptions{sort&compress,super}

% Hypelinks in the document; settings
\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
% \usepackage[normalem]{ulem}

\usepackage{listings}
\lstset{
  frame=lines,
  language=fortran,
  basicstyle=\footnotesize,
  stringstyle=\ttfamily,
  commentstyle=\itshape,
  fontadjust=true,
  keywordstyle=\color{magenta},
  mathescape,
  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt}

\usepackage{array}
\usepackage{tabularx}
\usepackage{ltablex}

\renewcommand{\arraystretch}{1.4}
% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}

\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}

\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}

\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
\newcommand {\new}[1]{{\color{blue}\it #1}}
%\newcommand {\new}[1]{{#1}}
% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}

%Reference to a given labelled equation
%and definition of a bib. element.
%-------------------------------------------
\newcommand{\equ}[1]
{Eq.~(\ref{#1})}

\newcommand{\figu}[1]
{Fig.~\ref{#1}}

\newcommand{\secu}[1]
{Sec.~\ref{#1}}

\newcommand{\ket}[1]
{|#1\rangle}

\newcommand{\bra}[1]
{\langle #1|}

\newcommand{\sgn}
{\mathop{\mathrm{sgn}}}

%SIMBOLI VARI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\bcen{\begin{center}}
\def\ecen{\end{center}}

\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}

\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
\def\DD{{\cal D}}
\def\AA{{\cal A}}
\def\GG{{\cal G}} \def\SS{{\cal S}}
\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
\def\SB{{\cal S}{\cal B}}
\def\aa{{\V \a}}
\def\hh{{\V h}}\def\HHH{{\V H}}
%\def\AA{{\V A}}
%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
\def\ZZZ{\mathbb{Z}}
%\def\TTT{\hbox{\msytw T}}

\def\ul{\underline}
\def\=={\equiv}
\def\defi{{\buildrel def \over =}}
\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
\def\us{\underline \s} \def\ue{{\underline \e}}
\def\la{\left\langle}
\def\ra{\right\rangle}
\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
\def\iomn{i\omega_n}
\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
\def\cG0{{\cal G}_0}
\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}

\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
% \def\Im{\mbox{Im}}
\def\=={\equiv}
\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
\def\det{{\rm det}\,}

\def\ibra{\langle}
\def\iket{\rangle}

\def\ka{{\bf k}}
\def\vk{{\bf k}}
\def\qa{{\bf q}}
\def\vQ{{\bf Q}}
\def\vr{{\bf r}}
\def\q{{\bf q}}
\def\R{{\bf R}}
\def\vR{{\bf R}}
\def\kx{{ k_x}}
\def\ia{{\bf i}}
\def\ja{{\bf j}}

\usepackage{bbold}
\def\11{\mathbb{1}}
\def\00{\mathbf{0}}
\def\NAME{{\rm EDIpack2.0}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\journal{Computer Physics Communications}

\begin{document}

\begin{frontmatter}

\title{\NAME plus Triqs interface}
\author[]{L.~Crippa}
\author[]{I.~Krivenko}
\author[]{S.~Giuli}
\author[]{G.~Bellomia}
\author[]{....}
% \author[]{A.~Scazzola}
% \author[]{F.~Petocchi}
% \author[]{G.~Mazza}
% \author[]{L.~de Medici}
% \author[]{M.~Capone}
\author[a]{A.~Amaricci\corref{author}}

\cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}

\address[a]{CNR-IOM, Istituto Officina dei Materiali,
    Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136 Trieste, Italy}
\begin{abstract}

\end{abstract}

\begin{keyword}
  %% keywords here, in the form: keyword \sep keyword
  Exact diagonalization \sep
  Quantum Impurity models\sep  
  Strongly correlated electrons \sep  
  Dynamical Mean-Field Theory
\end{keyword}

\end{frontmatter}

% Computer program descriptions should contain the following
% PROGRAM SUMMARY.
\noindent
{\bf PROGRAM SUMMARY}
\begin{small}
  \noindent
  \\
  {\em Program Title:}  \NAME                                        \\
{\em Licensing provisions:} GPLv3\\
{\em Programming language:}  Fortran, Python \\
{\em Classification:} 6.5, 7.4, 20 \\
{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
{\em Nature of problem:}. \\
{\em Solution method:} .\\
\end{small}

\section{Introduction}\label{SecIntro}

\section{Library Structure}\label{SecStruct}
\subsection{Dependencies}
\subsection{EDIpack2}
\subsection{EDIpy}
\subsection{EDIpack2Triqs}

\section{Installation}\label{SecInstall}
\subsection{Building}
\subsection{Install}
\subsection{Python API and TRIQS interface}
\subsection{Conda Packaging}

\section{Usage}\label{SecUsage}
\subsection{Basic Fortran: Bethe lattice DMFT}
\subsection{Python code: Attractive Hubbard model}
\subsection{TRIQS interface: Multi-orbital Hubbard}
\subsection{Advance: Non-SU2}

\section{EDIpack2 Implementation}\label{SecEDIpack}

\subsection{The quantum impurity problem}\label{sSecQIM}
We consider a system of $N_s$ electronic levels.  A portion $N_\alpha$  of them,
i.e. the impurity levels, interact via a local repulsion, while the
remaining $N_s-N_\alpha$, i.e. the  \textit{bath} levels, are  non-interacting.
In a typical setup the impurity levels are independently coupled to a
set of $N_b$ electronic levels, so that the total number is $N_{s}=N_\alpha 
(N_{b}+1)$. Other choices for the bath topology are possible, which entail a different counting of the total levels.
The Hamiltonian of the electronic system we consider has the form:
\begin{equation}\label{Ham1}
  \begin{split}
    \hat{H}^{e}=&\hat{H}^0+\hat{H}^{int} \\
    \hat{H}^0 = &
    \sum_{\a\b\sigma}
    H^{loc}_{\a\b\sigma}d^{+}_{\a\sigma}d_{\b\sigma}  + \cr
    &\sum_{\nu\a\b\sigma}h^\nu_{\a\b\sigma}a^{+}_{\nu\a\sigma}a_{\nu\b\sigma}+ 
  % 
    \sum_{\nu\a\sigma}V^\nu_{\a\sigma}d^{+}_{\a\sigma}a_{\nu\a\sigma}+
    H.c. \\
    \hat{H}^{int}=& U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}-\\
    &J_X\sum_{\a\neq \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a \neq \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}
\end{split}
\end{equation}
where $a_{\alpha\sigma}$, $d_{\a\sigma}$ ($a^+_{\alpha\sigma}$,
$d^+_{\a\sigma}$) are, respectively, the destruction (creation) operators for
the bath and impurity electrons with
orbital $\alpha$ and spin $\sigma$,
$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
The term $H_{\a\b\s}^{loc}$ is the non-interacting part of
the impurity Hamiltonian, 
$h_{\a\b\s}^\nu$ and $V_{\a\s}^\nu$ are, respectively, the local Hamiltonian
and the impurity hybridization of the $\nu-$th bath level. 
  Finally, $\hat{H}^{int}$ is the local
  multi-orbital interaction~\cite{Georges2013ACMP}.
  The first three terms represent the density-density part of the
  interaction, while the remaining two are,
  respectively, the spin-exchange and pair-hopping terms. 
  $U$ is the local Coulomb interaction strength, $J$ is the Hund's
  coupling~\cite{Georges2013ACMP}. We introduced
  independent coupling controlling the spin-exchange and pair-hopping terms,
  respectively $J_X$ and $J_P$. The fully symmetric Kanamori
  interaction is obtained setting $U'=U-2J$ and
  $J_X=J_P=J$~\cite{Georges2013ACMP}.

\subsection{The  basis states}\label{sSecBasis}
A natural representation of the basis states for the Fock space $\FF_e$
is obtained in the occupation number formalism of second quantization.
The \textit{Fock basis} for a finite system of $N_s$ electrons is
composed of states of the form
$\ket{\vec{n}}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}$, 
where each element $n_{a\sigma}=0,1$ describes the absence or the
presence of an electron with spin $\sigma$ at the level $a$. In
conjunction with the basis states, we introduce the non-Hermitian, anti-commuting, annihilation and
creation operators $c_{a\sigma}$ and
$c^{+}_{a\sigma}$, respectively. These operators act on the states
$\ket{\vec{n}}$ as:  
\begin{equation}
  \begin{aligned}
    % 1.
    c_{a\sigma}\ket{\vec{n}}=
    \begin{cases}
      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
      &\text{if $n_{a\sigma}\!=\! 1$}\\
      0 &\text{otherwise}
    \end{cases};
  \end{aligned}
\end{equation}
    \begin{equation}
  \begin{aligned}
    c^{+}_{a\sigma}\ket{\vec{n}}=
     \begin{cases}
      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
      & \text{if $n_{a\sigma}\!=\! 0$}\\
      0 & \text{otherwise}
    \end{cases}    
  \end{aligned}
\end{equation}
with $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$. 
Thus, each state is represented as a string of zeros and
ones, i.e. the binary decomposition of a given integer number $I$. Using
the identification $\ket{\vec{n}}=\ket{I}$, with
$I=0,\dots,2^{2N_s}-1$, each state in the Fock space can be encoded in a computer using
a sequence of $2N_s$ bits or, equivalently, an integer number in a
fixed representation.
The exponentially growing size of the Fock space will
eventually make such representation unpractical.
A solution is obtained by decomposing each state according to the
existing QNs. For a given set $[\vec{N}_\up,\vec{N}_\dw]$ of QNs we
then have: 
\begin{equation}
  \begin{split}
  \ket{\vec{n}} &=
  \prod_{\a=1}^{N_{ud}}\prod_{\sigma=\up\dw}\ket{n_1\dots
    n_{N_{bit}}}_{\a\sigma}\cr
  &=
  \begin{cases}
    \ket{\vec{n}_\up}\ket{\vec{n}_\dw},\
    \text{if}\ N_{ud}=1\\
    %
      \ket{\vec{n}_{1\up}}\cdots\ket{\vec{n}_{N_{ud}\up}}
      \ket{\vec{n}_{1\dw}}\cdots\ket{\vec{n}_{N_{ud}\dw}},\
      \text{if}\ N_{ud}=N_\alpha
    \end{cases}
    \end{split}
\end{equation}
so that, if the total number of electrons with spin $\up$ and $\dw$ is 
conserved, any state is identified by two binary sequences of
$N_{bit}=N_s$ bits, one per spin orientation.
Alternatively, if the number of electrons with spin $\up$ and $\dw$ per orbital is conserved, the
states are decomposed into two sets of
binary sequences (one set per spin orientation), each sequence
being made of  $N_{bit}=N_s/N_\alpha$ bits.
Each binary sequence is associated to a suitable tuple
of integer numbers,  univocally identifying the Fock state:
$I \rightarrow [\vec{I}_\up,\vec{I}_\dw]$, 
where $I=0,\dots,2^{2N_s}-1$ and
$\vec{I}_\sigma=[I_{1\sigma},\dots,I_{N_{ud}\sigma}]$ with
$I_{\a\sigma}=0,\dots,2^{N_{bit}}-1$. 
Through such decomposition, each state can be described by the
smallest bit set compatible with the conserved QNs.
This setup generalizes the method introduced by Lin and Gubernatis in
Ref.\onlinecite{Lin1993CIP}. 
The relation
between the Fock state index $I$ and its tuple decomposition can be
easily inverted:
\begin{equation}\label{Irelation}
I = I_1 + \sum_{i=2}^{2N_{ud}}I_i 2^{N_{bit}(i-1)}\,,
\end{equation}
where we rearranged the tuple as $[\vec{I}_\up,\vec{I}_\dw]=[I_1,\dots,I_{2N_{ud}}]$.

Such organization of the Fock states is used to construct
a suitable basis for the sectors $\SS[\vec{N}_\up,\vec{N}_\dw]$.
To any given Fock state $\ket{\vec{n}}$ and its
integer representation $I$, containing the correct bit decomposition
dictated by the QNs, it is associated a state $\ket{i}$ and an integer
$i=1,\dots,D_\SS$ through a suitable \textit{map} $\vec{\MM}_\SS$.
In particular,
each tuple of integers identifying a Fock state belonging to $\SS$ is associated to a new
tuple specific for each sector state:
$I\in\SS=[\vec{I}_\up,\vec{I}_\dw]\in\SS \xrightarrow{\vec{\MM}_\SS}
[\vec{i}_\up,\vec{i}_\dw]=i$, 
where $\vec{i}_\sigma=[i_{1\sigma},\dots,i_{N_{ud}\sigma}]$ and
$i_{\a\sigma}=1,\dots,D_{\a\sigma}$.
The tuple $[\vec{i}_\up,\vec{i}_\dw]$ univocally identifies a basis state
$\ket{i}=\ket{\vec{i}_\up,\vec{i}_\dw}$ of the sector $\SS$, through a
relation similar to \eqref{Irelation}:
\begin{equation}
i = i_{1\up} +
\sum_\sigma\sum_{l=2}^{N_{ud}}(i_{l\sigma}-1)\prod_{\a=1}^{l-1}D_{\a\sigma}
\label{SectorIndxDecomp}
\end{equation}

\subsection{Conserved quantum numbers}\label{sSecQNs}
A system of $N_s$ electrons is associated to
a Fock space of the form $\FF_e=\bigoplus_{n=0}^{N_s}
S_-\HH_e^{\otimes n}$,  where $\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$ is the local
Hilbert space of the electrons on a single level,
$S_-$ is the anti-symmetrization operator, $\bigoplus$ is the direct sum and
$\bigotimes$ the tensor product.
The total dimension of the Fock space $\FF_e$ is
$\text{dim}(\HH_e)^{N_s}=4^{N_s}= 2^{2N_s}$.

The solution of the eigenvalue problem for $H_e$ is simplified by taking
into account the existence of conserved quantities.
The Hamiltonian \eqref{Ham1} conserves the total charge
$\hat{N}$ and the spin component $\hat{S}_z$, as long as we assume
that no terms  breaking the particle number or spin conservation are present,
e.g. local spin-orbital coupling, in-plane magnetic field,
superconducting order, etc.
The conservation of  $\hat{N}$ and $\hat{S}_z$ can be conveniently
re-expressed in terms of conserved number of electrons with spin $\up$ and $\dw$, i.e. $\hat{N}_\up$,
$\hat{N}_\dw$.
Moreover,  if the terms $H^{loc}$ and $h$ are
diagonal and we consider only the density-density part of the
interaction, i.e. $J_X=J_P=0$, the number of electrons with spin $\up$ and $\dw$ is conserved \textit{per
  orbital}, i.e. $\hat{N}^m_\up$, $\hat{N}^m_\dw$, where
$m=1,\dots,N_\alpha$.

%
% 
In order to formally unify the treatment of these two cases we introduce some convenient
parameters,
  namely  $N_{ud}=1$ $(N_\alpha)$ and
$N_{bit}=N_s$ $(N_s/N_\alpha)$ for conserved total (orbital resolved) number of
electrons with spin $\up$ and $\dw$.
The first corresponds to the number of conserved operators per
spin, the latter indicates the number of electronic levels per spin
(spin and orbital). In the following section we will give a more precise meaning to
$N_{bit}$.

In the rest of this work we will indicate the set of conserved quantum
numbers (QN)s with the tuple $[\vec{N}_\up,\vec{N}_\dw]$, where ($\sigma=\up,\dw$):
\begin{equation}
  \vec{N}_\sigma=
  \begin{cases}
    N_{1\sigma}\==N_\sigma, & \text{if}\ N_{ud}=1 \\
    [N_{1\sigma},\dots,N_{N_\alpha\sigma} ], & \text{if}\ N_{ud}=N_\alpha    
  \end{cases}
\end{equation}
  Note that for $N_{ud}=1$ we identified the single
  component $N_{1\sigma}$ of the vector $\vec{N}_\sigma$ with the
  total number of electrons with spin $\sigma$, i.e. $N_{\sigma}$.

In presence of a set of conserved QNs,  the Fock space decomposes into
a number of sub-spaces of reduced dimension, each
corresponding to a given value of the QNs tuple. We indicate
each sub-space with the term \textit{sector} and the symbol
$\SS[\vec{N}_\up,\vec{N}_\dw]$, or just $\SS$ where no confusion
arises.
The dimension of each sector is given by the number of ways we can
arrange $N_{\a\sigma}$ elements into $N_{bit}$ positions, i.e.:
\begin{equation}
  \begin{split}
  \text{dim}\left(\SS[\vec{N}_\up,\vec{N}_\dw]\right)  & =  \prod_{\a=1}^{N_{ud}}
  \binom{N_{bit}}{N_{\a\up}}
  \prod_{\a=1}^{N_{ud}}
  \binom{N_{bit}}{N_{\a\dw}}\cr
  &\==
  \prod_{\a=1}^{N_{ud}}D_{\a\up}
  \prod_{\a=1}^{N_{ud}}D_{\a\dw}
  \stackrel{\text{def}}{=}D_{\up}D_{\dw} \== D_\SS
  \end{split}
 \label{nud_dimension}
\end{equation}
where we introduced the symbols $D_\sigma$ and $D_{\a\sigma}$  to
indicate, respectively, the dimension of total and orbital spin-subspace 
associated to the given set of QNs. Note that $D_\sigma\==D_{1,\sigma}$ for
$N_{ud}=1$.

\subsection{Krylov based Diagonalization}\label{sSecHam}
The matrix representing the system Hamiltonian in the Fock space has a
block-diagonal structure in presence of a given set of conserved QNs.
Each block corresponds to the Hamiltonian of a sector
$\SS[\vec{N}_\up,\vec{N}_\dw]$. The analysis of the spectrum, thus,
reduces to the recursive analysis of the sector Hamiltonians. 
In each sector, the Hamiltonian of the system has the following general form: 
\begin{equation}
H^e_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
H_\dw + H_{nd}\,.
\label{Hdecomp}
\end{equation}
$H_d$ is a diagonal term containing the local part of the Hamiltonian,
including the density-density terms of the interaction.
The $H_\sigma$ components describe all the hopping processes of the
electrons with spin $\sigma=\up,\dw$.
Finally the term $H_{nd}$ contains all the remaining non-diagonal
elements which do not fit in the previous two components,
e.g. the spin-exchange and pair-hopping interaction terms.
If the QNs are conserved per orbital, i.e. if $H_{nd}\==0$ and no
inter-orbital local hopping terms are present,  each $H_\sigma$
further splits into a sum of smaller terms:
$$
H_\sigma = \sum_{\a=1}^{N_\alpha}\mathbb{I}_{1\sigma}\otimes\cdots\otimes
H_{\a\sigma}\otimes\cdots\otimes \mathbb{I}_{N_\alpha\sigma}
$$

Each term of the  Hamiltonian matrix is constructed  independently 
iterating over one or more  components of the sector basis states.
For example, the construction of the matrices $H_{\a\sigma}$ only involve iterations over the components
$\ket{i_{\a\sigma}}$ of the sector basis. In general we have:
\begin{equation}
\begin{split}
  \bra{\vec{i}_\up\vec{i}_\dw}H^e_\SS\ket{\vec{j}_\up\vec{j}_\dw}
  =&
  \bra{\vec{i}_\up\vec{i}_\dw}
  H_d + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes H_\dw + H_{nd}
  \ket{\vec{j}_\up\vec{j}_\dw}\cr
  =&
  \bra{\vec{i}_\up\vec{i}_\dw}H_d\ket{\vec{i}_\up\vec{i}_\dw} +\cr
  &\bra{\vec{i}_\up}H_\up\ket{\vec{j}_\up}\delta_{\vec{i}_\dw\vec{j}_\dw}
  +
  \bra{\vec{i}_\dw}H_\dw\ket{\vec{j}_\dw}\delta_{\vec{i}_\up\vec{j}_\up} + \cr
  &\bra{\vec{i}_\up\vec{i}_\dw}H_{nd}\ket{\vec{j}_\up\vec{j}_\dw} 
\end{split}
\label{Hbuild}
\end{equation}

For very large systems, storing the Hamiltonian matrix in the memory
can be highly inefficient.
In such cases, Krylov or Lanczos
methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
be implemented using a storage-free algorithm, performing the
necessary linear operations on-the-fly.
This solution has generally a negative impact on the execution
time, however this can be well compensated by scaling in a massively
parallel framework.

\subsection{Dynamical correlation functions, observables and reduced
  impurity density matrix}

\subsection{Bath parametrization}

\subsection{Bath $\chi^2$ fit}

\subsection{Input/Output}

\section{EDIpy: Python API}\label{SecEDIpy}

\section{edipack2triqs: a thin interface to TRIQS}\label{Secedi2triqs}

\section{Conclusions}

\section*{Acknowledgements}

% \section*{Appendix A: Input Variables}\label{AppendixA}
% Here is reported a list of the global input variables of the
% library. The input parameters are arranged into the following table,
% as discussed in \secu{SecWorkflow}.
% Note that only a subset of the input parameters are transparent to the
% user, i.e. can be directly accessed from the calling program.
% These variables  are indicated with a symbol in the first column of
% the table.  In the columns from $2^{\rm nd}$ to $4^{\rm th}$ we indicate,
% respectively, the variable name, the type and the default value.
% Finally, In the last column we provide a short
% description of the variable purpose.

% % \begin{longtable}{ M{0.01pt} T{0.19\textwidth}  T{0.04\textwidth}
%     %     D{0.11\textwidth} M{0.52\textwidth}  }

% \begin{tabularx}{\linewidth}{ M{0.01\textwidth} T{0.19\textwidth}
%     T{0.04\textwidth} D{0.11\textwidth} M{0.52\textwidth} }
%   \caption{List of the \NAME\ input variables.}\\
%   \hline 
%   \hline
%   {\it \footnotesize \phantom{T}} & {\it Variable} & {\it Type} & {\it Default} & {\it
%                                                          \footnotesize
%                                                          Description} \\
%   \hline
%   \hline
%   \endhead
%   \hline
%   \multicolumn{5}{c}{\bf Most relevant control variables}\\
%   \hline
%   $\circ$ & Norb & Int & 1 & Number of impurity orbitals.\\
%   \hline
%   $\circ$ & Nspin& Int & 1 & Number of spin channels treated
%                              independently. \texttt{Nspin}=1 enforces
%                              non-magnetic solution.\\
%   \hline
%    & Nbath& Int & 6  & Number of bath sites. See \texttt{bath\_type}
%                        for information about resulting total number of
%                        electronic levels $N_s$.\\
%   \hline
%   $\circ$ & bath\_type& Char & ``normal''    & Set the bath type:
%                                      \texttt{normal}:
%                                      $N_s=\mathtt{Norb}(1+\mathtt{Nbath})$,
%                                      \texttt{hybrid}:
%                                      $N_s=\mathtt{Norb}+\mathtt{Nbath}$,
%                                      and \texttt{replica}:
%                                      $N_s=\mathtt{Norb}(1+\mathtt{Nbath})$,
%                                      See \secu{SecBath}.\\
%   \hline
% %--------
%   $\circ$ & Uloc& Dble & 2.0   & Local intra-orbital interactions $U$,
%                                      different values per orbitals can
%                                      be defined.\\
%   \hline
%   $\circ$ & Ust& Dble & 0.0   & Local inter-orbital interaction $U'$,
%                                 with opposite spin orientations.
%                                 For the Kanamori interaction this 
%                                 must be set to
%                                 $\mathtt{Uloc}-2\mathtt{Jh}$, with \texttt{Jh}
%                                 the Hund's coupling. 
%                                 The value $U''$ for equal spin orientation
%                                 is automatically set by the difference 
%                                 $\mathtt{Ust}-\mathtt{Jh}$. \\
%   \hline
%   $\circ$ & Jh   & Dble & 0.0 &  Hund's coupling.\\
%   \hline
%   $\circ$ & Jx   & Dble & 0.0 & Spin-Exchange coupling constant.\\
%   \hline
%   $\circ$ & Jp   & Dble & 0.0 & Pair-Hopping coupling constant.\\
%   \hline
%     $\circ$ & beta   & Dble & 1000 & Inverse temperature. For $T=0$
%                                    calculations this value sets a 
%                                    discretization of the Matsubara
%                                    frequencies.\\
%   \hline
%   $\circ$ & xmu   & Dble & 0.0 & Chemical potential. This parameter
%                                  sets the average occupations of the
%                                  impurity. 
%                                  If \texttt{HFMODE=True} this value
%                                  contains the Hartree shift, i.e. $\mathtt{xmu}=0.0$ sets the half-filling for a particle-hole
%                                  symmetric case.\\
%   \hline
%      & HFmode  & Bool & .true. & If True the Hartree shift is included in the
%                 interaction, e.g. $U(n_\up-1/2)(n_\dw-1/2)$. In this
%                        case zero chemical potential corresponds to
%                        half-filling for a particle-hole symmetric system.\\  
%   \hline
%   $\circ$ & Lmats & Int & 4096 & Number of Matsubara frequencies.\\
%   \hline
%   $\circ$ & Lreal  & Int & 5000 & Number of real-axis frequencies\\
%   \hline
%     $\circ$ & eps   & Dble & 0.01 & Real-axis broadening.\\
%   \hline
%   $\circ$ & wini, wfin & Dble & -5, 5 & Real-axis frequency range.\\
%   \hline
%   $\circ$ & Nloop    & Int & 100 & Maximum number of allowed iterations in the DMFT solution.\\
%   \hline
%   $\circ$ & dmft\_error & Dble & 1e-5 & Convergence threshold for the
%                                         DMFT iterative cycle.\\
%   \hline
%   %--------
%   $\circ$ & Nph    & Int & 0 & Maximum number of phonons.\\
%   \hline
%   $\circ$ & g\_ph   & Dble & 0.0& Electron-Phonon coupling.\\
%   \hline
%   $\circ$ & w0\_ph  & Dble & 0.0& Holstein phonon frequency.\\
%   \hline
%   $\circ$ & xmin, xmax & Dble & -3, 3& Phonon probability distribution spatial range.\\
%   \hline
% %--------
%    & chispin\_flag & Bool & .false. & Flag to include the evaluation of Spin-Spin susceptibilities.\\
%   \hline
%    &  chidens\_flag &Bool & .false. & Flag to include the evaluation of Density-Density susceptibilities.\\
%   \hline
%    & chipair\_flag & Bool & .false. &  Flag to include the evaluation
%                                       of $s$-wave Pair susceptibilities.\\
%   \hline
%    & chiexct\_flag & Bool & .false. & Flag to include the evaluation of Excitonic susceptibilities.\\
%   \hline
%   %-------
%    & ed\_sparse\_H    & Bool & .true. &  Flag to select storage type of the sparse
%                          Hamiltonian. True: sparse matrix object,
%                          False:on-the-fly matrix-vector product.\\
%   \hline
%    & ed\_total\_ud     & Bool & .true. & Flag to select quantum numbers type.
%                                  True: conserved total electron occupation per
%                                  spin. 
%                                  False: conserved electrons
%                                  occupations per orbital and spin.\\
%   \hline 
%    & ed\_print\_Sigma & Bool & .true. & Flag to print out the impurity Self-energies.\\
%   \hline
%    & ed\_print\_G        & Bool & .true. & Flag to print out the interacting impurity Green's functions.\\
%   \hline
%    & ed\_print\_G0      & Bool & .true. & Flag to print out the non-interacting
%                               impurity Green's functions.\\
%   \hline
%    & ed\_twin             & Bool & .false. & Flag to reduce the number of visited
%                                        sector using  sectors symmetry:
%                                        $[\vec{N}_\up,\vec{N}_\dw]\leftrightarrow[\vec{N}_\dw,\vec{N}_\up]$.
%                                        A warning is raised if
%                                        \texttt{ed\_twin=.true.} and
%                                        \texttt{Nspin=2} as this
%                                        symmetry 
%                                        conflicts with possible long-range
%                                        magnetic order.\\ 
%   \hline
%    & ed\_verbose       & Int & 3 & Verbosity level [0-5]. \\
%   \hline
%   % ----------
%    & lanc\_method     & Char & ``arpack'' & String to select Lanczos
%                                    method. \texttt{ARPACK}: uses
%                                    P-Arpack, \texttt{LANCZOS}: uses
%                                    single vector Lanczos method
%                                    with no re-orthogonalization \\
%   \hline
%    & lanc\_tolerance  & Dble & 1e-18 & Tolerance for the Lanczos algorithm. \\
%   \hline
%    & lanc\_niter         & Int & 512 & Largest number of Lanczos
%                                        iterations used in the
%                                        Diagonalization of each sector Hamiltonian.\\
%   \hline
%    & lanc\_ngfiter      & Int & 200 & Largest dimension of the Krylov basis in
%                               the evaluation of the Green's function.\\
%   \hline
%   & lanc\_nstates\_sector  & Int & 2 & Maximum number of eigenvalues per sector
%                                         required to P-Arpack. For $T>0$ this number
%                                         indicates an initial guess and
%                                        is adjusted during the
%                                        annealing.  \\
%   \hline
%    & lanc\_nstates\_total    & Int & 1 & Maximum number of states in
%                                          the spectrum. 
%                                          $\mathtt{lanc\_nstates\_total}=1$
%                                          indicates that only the
%                                          groundstate should be
%                                          evaluated, resulting in zero
%                                          temperature calculation.
%                                          For $T>0$ calculations a value 
%                                          $\mathtt{lanc\_nstates\_total}>1$
%                                          is required. This value is
%                                          used as an initial guess and adjusted
%                                          during finite temperature
%                                          annealing. See
%                                          \texttt{cutoff} and
%                                          Sec.~\ref{CodeEigenspace}. \\
%   \hline
%      & ed\_finite\_temp & Bool & .false. &  Flag to select finite temperature
%                                          method. If True 
%                                          $\mathtt{lanc\_nstates\_total} > 1$ is required.\\  
%   \hline

%    & lanc\_ncv\_factor & Int & 10 & Factor to determine block size
%                                     \texttt{Ncv} used in P-Arpack 
%                                     using the expression:
%                                           $\mathtt{Ncv}=\mathtt{lanc\_ncv\_factor}*\mathtt{Neigen}+\mathtt{lanc\_ncv\_add}$.
%                                           P-Arpack requires \texttt{Ncv}
%                                           to be at least twice of the
%                                           required Eigensolutions \texttt{Neigen}.
%                                           At zero temperature
%                                           \texttt{Neigen}=\texttt{lanc\_nstates\_sector}. 
%                                           At finite temperature
%                                           \texttt{Neigen} is
%                                           automatically adjusted from
%                                           initial value, possibly leading to
%                                           a block size \texttt{Ncv}
%                                           too large.
%                                           Reducing the value of
%                                           \texttt{lanc\_ncv\_factor}
%                                           down to its minimum value 2
%                                           can be required to perform P-Arpack calculations.\\
%   \hline
%    & lanc\_ncv\_add       & Int & 0 & Factor to determine block size
%                                       \texttt{Ncv} used in P-Arpack 
%                                       using  the expression:
%                                       $\mathtt{Ncv}=\mathtt{lanc\_ncv\_factor}*\mathtt{Neigen}+\mathtt{lanc\_ncv\_add}$.
%                                       P-Arpack requires \texttt{Ncv}
%                                       to be at least twice of the
%                                       required Eigensolutions
%                                       \texttt{Neigen}. \\
%   \hline   
%   % ----------  
%   $\circ$ & cg\_Scheme           & Char & ``Weiss'' & Conjugate Gradient fit scheme.
%                                                       \texttt{Delta}: fit $\Delta(i\omega_n)$, \texttt{Weiss}: fit $\GG_0(i\omega_n)$.\\
%   \hline
%    & cg\_method           & Int & 0 & Conjugate Gradient minimization method.
%                                       $\mathtt{cg\_method}=0$: Fletcher-Reeves-Polak-Ribiere
%                                       minimisation algorithm. 
%                                       $\mathtt{cg\_method}=1$: use the f77 \texttt{minimize} procedure published in
%                                       Ref.\onlinecite{Georges1996RMP}
%                                       and largely used in the DMFT community.\\
%   \hline
%    & cg\_Lfit   & Int & 1000 & Number of Matsubara frequencies used in
%                                the calculation of the cost function
%                                $\chi$ with the Conjugate
%                                Gradient minimization. $\mathtt{Lfit}\leq\mathtt{Lmats}$.  \\
%   \hline
%    & cg\_grad             & Int & 0 & Type of gradient evaluation. $\mathtt{cg\_grad}=0$: Analytic,
%                                       $\mathtt{cg\_grad}=1$:
%                                       Numeric. If
%                                       $\mathtt{cg\_method}=1$ then use
%                                       of 
%                                       $\mathtt{cg\_grad}=1$ is
%                                       enforced as this method does not
%                                       support analytic gradient calculation.\\
%   \hline
%   \hline
%   \multicolumn{5}{c}{\bf More specific control variables, less
%   frequently changed}\\
%   \hline
%   \hline  
%   $\circ$ & sb\_field & Dble & 0.0& Small symmetry-breaking field.\\
%   \hline  
%   $\circ$ & Nsuccess  & Int & 1 & Minimum number of repeated iterations below
%                                   threshold required to reach convergence.  \\
%   \hline
%    & cutoff  & Dble & 1e-9 & Cutoff for the Boltzmann factor in the
%                              spectral summation, i.e.
%                              $e^{-\beta(E-E_0)}<\mathtt{cutoff}$. See Sec.~\ref{CodeEigenspace}.\\
%   \hline  
%    & gs\_threshold & Dble & 1e-9 & Energy threshold for the groundstate
%                       degeneracy. Eigenstates of energy $E$ within
%                                    $|E-E_0|<\mathtt{gs\_threshold}$
%                                    are considered as degenerate groundstates.\\
%   \hline
%    &ed\_sectors & Bool & .false. & This flag is used to reduce
%                                          the number of sectors
%                                     investigated during the
%                                     construction of the spectrum. Only
%                                     the sectors with QNs listed in the file
%                                     \texttt{SectorFile} and those with
%                                     plus and minus
%                                     \texttt{ed\_sectors\_shift} are considered.\\
%   \hline
%     & ed\_sectors\_shift & Int & 1 & A shift of the QNs for the list
%                                      of sectors read from
%                                      \texttt{SectorFile} is
%                                      \texttt{ed\_sectors=.true.}.
%                                      The list is enlarged
%                                      including the QNs obtained
%                                      by applying a shift
%                                      $\pm
%                                      1,\ldots,\pm\mathtt{ed\_sectors\_shift}$
%                                      to each element of the list.\\
%   \hline
%    & ed\_hw\_bath & Dble & 2.0 & The half-bandwidth for the bath
%                               initialization using discretized flat density of
%                               states.\\
%   \hline  
%    & ed\_offset\_bath & Dble & 0.1 & Energy offset for the
%                                    initialization of the diagonal
%                                    terms in replica bath. A small
%                                    value randomly chosen in the
%                                    interval
%                                    $\epsilon\in [-\mathtt{ed\_offset\_bath}:\mathtt{ed\_offset\_bath}]$
%                                    is added to the diagonal terms of
%                                    the bath to avoid possible spectral
%                                      degeneracies.\\
%   \hline
%   $\circ$ & Lpos & Int & 100 & Number of points used to obtain the phonon probability
%                      distribution function.\\ 
%   \hline
%   $\circ$ & nread & Dble & 0.0 & Target density for fixed density
%                        calculations. Use the procedure
%                        \texttt{ed\_search\_variable}   to adjust
%                        chemical potential \texttt{xmu} so that local
%                        occupation is
%                        $|n-\mathtt{nread}|<\mathtt{nerr}$. \\
%   \hline
%    & nerr & Dble & 1e-4 & Error threshold for fixed-density
%                        calculations.\\
%   \hline 
%    & ndelta& Dble & 0.1 & Initial step for the variation of the chemical
%                        potential in fixed-density calculations.\\
%   \hline  
%    & ncoeff & Dble & 1d0 & A multiplier for the initial ndelta as read
%                            from a file: $\mathtt{ndelta}\rightarrow\mathtt{ndelta}*\mathtt{ncoeff}$.\\
%   \hline  
%    & ed\_solve\_offdiag\_gf & Bool & .false. & Force the calculation of
%                                          the off-diagonal Green's
%                                          functions.
%                                          True if \texttt{bath\_type}$\neq$\texttt{normal} \\ 
%   \hline
%    & ed\_all\_G           & Bool & .false. & Flag to evaluate all components of the
%                                              impurity Green's functions,
%                                              irrespective of the symmetries of the
%                                              problem when using
%                                              \texttt{bath\_type}=\texttt{replica}.
%                                              If False only the Green's
%                                              functions corresponding
%                                              to non-vanishing
%                                              components of the bath
%                                              Hamiltonian
%                                              $h^\nu_{\a\b\sigma}$ are
%                                              evaluated.  \\
%   \hline
%    & lanc\_nstates\_step    & Int & 2 & Number of states to be added
%                                         to
%                                         \texttt{lanc\_nstates\_sector}
%                                         for each sector during finite
%                                         temperature annealing of the
%                                         state list. See
%                                         Sec.~\secu{CodeEigenspace}. \\  
%   \hline
%    & lanc\_dim\_threshold   & Int & 1024 & Dimension threshold below
%                                            which Lapack diagonalization method is
%                                            used to determine
%                                            eigensolutions. \\
%   \hline
%    & cg\_Niter             & Int & 500 & Maximum number of iteration
%                                          for the Conjugate Gradient minimization.\\
%   \hline
%    & cg\_Ftol             & Dble & 1e-6 & Tolerance for the Conjugate Gradient minimization.\\
%   \hline
%    & cg\_stop             & Int & 0 & Stop condition for the Conjugate Gradient
%                                       minimization of the cost function $\chi(x)$.
%                                       0: $C_1+C_2$, 1: $C_1$, 2: $C_2$ with
%                                       conditions 
%                                       $C_1=|\chi^{n-1} - \chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$,
%                                       $C_2=||x^{n-1}
%                                       -x^n||<\mathtt{cg\_Ftol}(1+||x^n||)$. See
%                                       Sec.~\secu{SecBathFit}.\\
%   \hline
%    & cg\_Weight         & Int & 1 & A weight factor used in the cost
%                                     function $\chi$ of the Conjugate
%                                     Gradient minimization. Increasing this
%                                     parameter favors the fit of the low
%                                     frequency part of $\chi$.
%                                     1: $\mathtt{cg\_weight}=1$,
%                                     2: $\mathtt{cg\_weight}=1/\mathtt{Lfit}$,
%                                     3:
%                                     $\mathtt{cg\_weight}=1/\omega_n$. See
%                                     Sec.~\secu{SecBathFit}.\\
%   \hline
%    & cg\_pow             & Int & 2 & The exponent of the cost function
%                                      $\chi$ as 
%                                      $|X -
%                                      X^{And}|^{\mathtt{cg\_pow}}$ used
%                                      in Conjugate Gradient
%                                      minimization. See Sec.~\ref{SecBathFit}.\\
%   \hline
%   % ----------
%   $\circ$ & Hfile & Char & ``hamiltonian'' & File name to read/write bath parameters\\
%   \hline
%   & SectorFile & Char & ``sectors'' & File name to read/write
%                                              sectors contributing to
%                                              the state list. On output
%                                              it contains the QNs of
%                                              the list of sectors
%                                              contributing to the
%                                              evaluated spectrum. On
%                                              input such list is used
%                                              to reduce the sectors
%                                              analysis. See
%                                       \texttt{ed\_sectors} and \texttt{ed\_sectors\_shift}. \\
%   \hline
%   $\circ$ & LOGfile  & Int & 6 & Fortran unit for the log
%                                  output. Value must be in  the range
%                                  $[6:999]$. 6 is the standard output. \\
%   \hline
%   \label{TableParameters}
% \end{tabularx}

% \section*{Appendix B: Main procedures}\label{AppendixB}
% In this appendix we report a list of all the procedures made
% accessible by either Fortan or Python API of the \NAME\ library. As
% discussed in Sec.~\ref{SecUsage} all such procedures feature implicit
% MPI support, i.e. they are executed in parallel if the MPI framework
% has been initialized in the calling program.

% In the first column we report the procedure names and the possible
% input arguments. In order to unify the naming conventions of the
% interfaces we use the prefix \texttt{?=ed\_,  edipack.} to indicate,
% respectively, the Fortran and Python procedures.
% In the second column we briefly describe the purpose of
% the procedure and the nature of the arguments.
% The inputs in square brackets are optional.

% The procedures are grouped with respect to the library module
% containing them, indicated in a single column at the beginning of each
% group.

% \begin{tabularx}{\linewidth}{ T{0.46\textwidth}  M{0.49\textwidth} }
%   \caption{List of the \NAME\ procedures.}\\
%   \hline
%   \hline
%   {\it PROCEDURE} {(\texttt{?=ed\_, edipack.})} & {\it \footnotesize INFO} \\
%   \hline
%   \hline
%   \endhead
%   \hline
%   \hline
%   \multicolumn{2}{c}{\bf INPUT\_VARS}\\
%   \hline
%   \hline
%   ?read\_input(File) &
%                        Reads global input variables from the user
%                        indicated file \texttt{File}.
%                        Argument: \texttt{File} is a character string of arbitrary length.
%                        If the file does not exist in the calling directory
%                        a default one with prefix 
%                        ``\texttt{used.}'' is produced using default
%                        values.
%                        The value of
%                        each variable can be updated also from command line
%                        using the syntax \texttt{Variable=}$Value$.\\
%   \hline
%   \hline
%   \multicolumn{2}{c}{\bf  MAIN}\\
%   \hline
%   \hline
%   ?init\_solver(Bath) & Initializes the whole ED calculation, allocate global static 
%                         memory, perform compatibility checks and setup global
%                         variables.
%                         Argument: \texttt{Bath}  is a rank-1 dble array 
%                         of dimension \texttt{Nb=?get\_bath\_dimension}.
%                         For problems with \texttt{Nsites} inequivalent atoms
%                         \texttt{Bath} is a rank-2 dble array of 
%                         dimensions [\texttt{Nsites},\texttt{Nb}].
%                         On \texttt{Bath} contains the bath parameters, either guessed from
%                         flat density of states  or read from the
%                         file \texttt{Hfile.restart}. \\
%   \hline
%   ?solve(Bath,Hloc)  &   Solve the quantum impurity problem using ED
%                        method.
%                        Arguments: \texttt{Bath} is a rank-1 dble array
%                         of dimension
%                        \texttt{Nb=?get\_bath\_dimension}.
%                        For problems with \texttt{Nsites} inequivalent atoms
%                        \texttt{Bath} is a rank-2 dble array of 
%                        dimensions [\texttt{Nsites},\texttt{Nb}].
%                        \texttt{Hloc} is a rank-4 dble array of
%                        dimensions [\texttt{Nspin,Nspin,Norb,Norb}] or
%                        a rank-5 of dimensions
%                        [\texttt{Nsites,Nspin,Nspin,Norb,Norb}]. Arguments
%                        are not changed on output.\\

%   \hline
%   \hline
%   \multicolumn{2}{c}{\bf  IO}\\
%   \hline
%   \hline
%   ?get\_sigma\_matsubara(Func,[Nsites])  & Returns the Matsubara
%                                               self-energy function in \texttt{Func}.
%                                               Argument: \texttt{Func}
%                                               is a rank-5 cmplx array
%                                               of dimensions
%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lmats}].
%                                               If \texttt{Nsites} is
%                                               present \texttt{Func}
%                                               is a rank-6 cmplx array
%                                               of dimensions
%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lmats}]
%                                               and the procedure returns
%                                               the function for each
%                                               inequivalent atom.\\
%   \hline
%   ?get\_sigma\_realaxis(Func,[Nsites])  &  Returns the real-axis
%                                               self-energy function in \texttt{Func}.
%                                               Argument: \texttt{Func}
%                                               is a rank-5 cmplx array
%                                               of dimensions
%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lreal}].
%                                               If \texttt{Nsites} is
%                                               present \texttt{Func}
%                                               is a rank-6 cmplx array
%                                               of dimensions
%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lreal}]
%                                               and the procedure returns
%                                               the function for each
%                                               inequivalent atom.\\
%   \hline
%   ?get\_gimp\_matsubara(Func,[Nsites])  & Returns the Matsubara
%                                              impurity Green's function in \texttt{Func}.
%                                               Argument: \texttt{Func}
%                                               is a rank-5 cmplx array
%                                               of dimensions
%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lmats}].
%                                               If \texttt{Nsites} is
%                                               present \texttt{Func}
%                                               is a rank-6 cmplx array
%                                               of dimensions
%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lmats}]
%                                               and the procedure returns
%                                               the function for each
%                                               inequivalent atom.\\
%   \hline
%   ?get\_gimp\_realaxis(Func,[Nsites])  & Returns the real-axis
%                                              impurity Green's function in \texttt{Func}.
%                                               Argument: \texttt{Func}
%                                               is a rank-5 cmplx array
%                                               of dimensions
%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lreal}].
%                                               If \texttt{Nsites} is
%                                               present \texttt{Func}
%                                               is a rank-6 cmplx array
%                                               of dimensions
%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lreal}]
%                                               and the procedure returns
%                                               the function for each
%                                               inequivalent atom.\\
%   \hline

%   ?get\_dens(Var,[Nsites])  & Returns the impurity occupations in
%                                  \texttt{Var}.
%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
%                                  dimensions [\texttt{Nsites,Norb}] and the procedure returns
%                                  the value for each inequivalent atom.\\
%   \hline
%   ?get\_mag(Var,[Nsites])  &  Returns the impurity magnetization in
%                                 \texttt{Var}.
%                                 Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
%                                 If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
%                                 dimensions [\texttt{Nsites,Norb}] and the procedure returns
%                                 the value for each inequivalent atom.\\
%   \hline
%   ?get\_docc(Var,[Nsites])  & Returns the impurity double occupancy
%                                  in \texttt{Var}.
%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
%                                  dimensions [\texttt{Nsites,Norb}] and the procedure returns
%                                  the value for each inequivalent atom.\\
%   \hline
%   ?get\_eimp(Var,[Nsites])  & Returns the impurity local energies components
%                                  in \texttt{Var}.
%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [4].
%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
%                                  dimensions [\texttt{Nsites,4}] and the procedure returns
%                                  the value for each inequivalent atom.\\
%   \hline
%   ?get\_doubles(Var,[Nsites])  & Returns additional impurity double
%                                  occupancies from multi-orbital
%                                  terms in \texttt{Var}.
%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [4].
%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
%                                  dimensions [\texttt{Nsites,4}] and the procedure returns
%                                  the value for each inequivalent atom.\\

%   \hline
%   \hline
%   \multicolumn{2}{c}{\bf  BATH}\\
%   \hline
%   \hline
%   ?get\_bath\_dimension() & Returns the number \texttt{Nb} of bath parameters
%                                required to describe the quantum
%                                impurity problem, based on the value of
%                                different input variables,
%                                e.g. \texttt{Norb, Nbath, bath\_type}.
%                                Output: \texttt{Nb} integer constant. \\
%   \hline
%   \makecell[l]{
%   ?set\_Hreplica(Hloc) \\
%   ?set\_Hreplica(Hvec,LambdaVec)} & Sets up the matrix basis and the
%                                     initial guess for the variational
%                                     bath parameters which determined
%                                     the shape of the  bath for \texttt{bath\_type=replica}.
%                                     The procedure
%                                     accepts either the local
%                                     non-interacting Hamiltonian
%                                     \texttt{Hloc} or  the \texttt{Nsym}
%                                     matrix basis components
%                                     \texttt{Hvec} and the
%                                     corresponding variational
%                                     parameters \texttt{Lambdavec}. See
%                                     Sec.~\ref{SecBath}.  
%                                     Arguments: \texttt{Hloc} is a
%                                     rank-4 dble array of dimensions
%                                     [\texttt{Nspin,Nspin,Norb,Norb}]
%                                     or a rank-2 dble array of dimensions
%                                     [\texttt{Nspin*Norb,Nspin*Norb}].
%                                     \texttt{Hvec} is a rank-5 dble
%                                     array of dimensions
%                                     [\texttt{Nspin,Nspin,Norb,Norb,Nsym}].
%                                     \texttt{LambdaVec} is a rank-1
%                                     dble array of dimensions
%                                     \texttt{Nsym} or a rank-2 dble
%                                     array of dimensions
%                                     [\texttt{Nsites,Nsym}], for
%                                     \texttt{Nsites} inequivalent
%                                     atoms. \\
%   \hline

%   ?get\_bath\_component\_dimension(Type) & Returns the dimensions a 
%                                            rank-3 dble array should
%                                            have to store a specific
%                                            component of the bath. 
%                                            The output is a rank-1 int
%                                            array \texttt{Ndim(1:3)} of dimension 3. 
%                                            Argument: \texttt{Type} is
%                                            a single
%                                            character. Possible values
%                                            are \texttt{Type=e, v, l},
%                                            corresponding to energy,
%                                            hybridization or lambda
%                                            components. \\
%   \hline
%   ?get\_bath\_component(Array,Bath,Type) & Returns in
%                                                 \texttt{Array} the
%                                                 specified components
%                                                 \texttt{Type} of the
%                                                 bath \texttt{Bath}.
%                                                 Arguments:
%                                                 \texttt{Array} a
%                                                 rank-3 dble array of
%                                                 dimensions
%                                                 [\texttt{Ndim(1),Ndim(2),Ndim(3)}]
%                                                 as returned by a call
%                                                 to
%                                                 \texttt{?get\_bath\_component\_dimension(Type)}.
%                                                 \texttt{Bath} is a
%                                                 rank-1 dble array of dimension
%                                                 \texttt{Nb=?get\_bath\_dimension}.
%                                                 \texttt{Type=e, v, l}
%                                                 is  a single character.\\
%   \hline
%   ?set\_bath\_component(Array,Bath,Type) &
%                                                Sets the specified component
%                                                \texttt{Type} in the
%                                                bath \texttt{Bath}
%                                                to \texttt{Array}.
%                                                Arguments:
%                                                \texttt{Array} a
%                                                rank-3 dble array of
%                                                dimensions
%                                                [\texttt{Ndim(1),Ndim(2),Ndim(3)}]
%                                                as returned by a call
%                                                to
%                                                \texttt{?get\_bath\_component\_dimension(Type)}.
%                                                \texttt{Bath} is a
%                                                 rank-1 dble array of dimension
%                                                \texttt{Nb=?get\_bath\_dimension}.
%                                                \texttt{Type=e, v, l}
%                                                is  a single character.\\
%   \hline
%   ?copy\_bath\_component(BathIN,BathOUT,Type) & Copies the specified component
%                                                \texttt{Type} from the
%                                                    input bath
%                                                    \texttt{BathIn} to
%                                                    the output bath \texttt{BathOut}. 
%                                                    Arguments:
%                                                    \texttt{BathIn} and
%                                                    \texttt{BathOut}
%                                                    are rank-1 dble array of dimension
%                                                    \texttt{Nb=?get\_bath\_dimension}.
%                                                    \texttt{Type=e, v, l}
%                                                    is  a single
%                                                    character.\\

%   \hline
%   ?spin\_symmetrize\_bath(Bath[,save])& Enforces spin symmetry in the bath
%                                         \texttt{Bath}.
%                                         Arguments: \texttt{Bath} is a rank-1 dble array
%                                         of dimension
%                                         \texttt{Nb=?get\_bath\_dimension}.
%                                         For problems with \texttt{Nsites} inequivalent atoms
%                                         \texttt{Bath} is a rank-2 dble array of 
%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
%                                         \texttt{save} is a logical
%                                         value used to optionally write
%                                         out the output bath.\\
%   \hline
%   ?orb\_symmetrize\_bath(Bath[,save])& Enforces symmetry among orbitals in the bath
%                                    \texttt{Bath}.
%                                    Arguments: \texttt{Bath} is a rank-1 dble array
%                                         of dimension
%                                         \texttt{Nb=?get\_bath\_dimension}.
%                                         For problems with \texttt{Nsites} inequivalent atoms
%                                         \texttt{Bath} is a rank-2 dble array of 
%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
%                                         \texttt{save} is a logical
%                                         value used to optionally write
%                                         out the output bath.\\
%   \hline
%   ?orb\_equality\_bath(Bath,Indx[,save])&
%                                              Equals each orbital 
%                                              components in the bath
%                                              \texttt{Bath} to be
%                                              identical to those of the
%                                              orbital \texttt{Indx}.
%                                               Arguments: \texttt{Bath} is a rank-1 dble array
%                                              of dimension
%                                              \texttt{Nb=?get\_bath\_dimension}.
%                                              For problems with \texttt{Nsites} inequivalent atoms
%                                              \texttt{Bath} is a rank-2 dble array of 
%                                              dimensions
%                                              [\texttt{Nsites},\texttt{Nb}].
%                                              \texttt{Indx} is a
%                                              integer constant. 
%                                              \texttt{save} is a logical
%                                              value used to optionally write
%                                              out the output bath.\\
%   \hline
%   ?ph\_symmetrize\_bath(Bath[,save])& Enforces particle-hole symmetry
%                                       in the bath \texttt{Bath}.
%                                        Arguments: \texttt{Bath} is a rank-1 dble array
%                                         of dimension
%                                         \texttt{Nb=?get\_bath\_dimension}.
%                                         For problems with \texttt{Nsites} inequivalent atoms
%                                         \texttt{Bath} is a rank-2 dble array of 
%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
%                                         \texttt{save} is a logical
%                                         value used to optionally write
%                                         out the output bath.\\
%   \hline
%   ?ph\_trans\_bath(Bath[,save])& Perform a particle-hole transformation onto the
%                           bath \texttt{Bath}.
%                            Arguments: \texttt{Bath} is a rank-1 dble array
%                                         of dimension
%                                         \texttt{Nb=?get\_bath\_dimension}.
%                                         For problems with \texttt{Nsites} inequivalent atoms
%                                         \texttt{Bath} is a rank-2 dble array of 
%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
%                                         \texttt{save} is a logical
%                                         value used to optionally write
%                                         out the output bath.\\
%   \hline
%   ?break\_symmetry\_bath(Bath,Field,Sign[,save]) &
%                                                     Breaks spin
%                                                     symmetry in the bath \texttt{Bath}
%                                                    using a small field of
%                                                    amplitude 
%                                                    \texttt{Field} with sign
%                                                    \texttt{Sign}. The
%                                                    quantity
%                                                    \texttt{Field*Sign}
%                                                    is added or
%                                                    subtracted,
%                                                    respectively for spin
%                                                    up and down, to the
%                                                    local energies of each bath level.  
%                                                    Arguments: \texttt{Bath} is a rank-1 dble array
%                                                    of dimension
%                                                    \texttt{Nb=?get\_bath\_dimension}.
%                                                    For problems with \texttt{Nsites} inequivalent atoms
%                                                    \texttt{Bath} is a rank-2 dble array of 
%                                                    dimensions
%                                                    [\texttt{Nsites},\texttt{Nb}].
%                                                    \texttt{Field,
%                                                    Sign} are dble
%                                                    constant.                                                     
%                                                    \texttt{save} is a logical
%                                                    value used to optionally write
%                                                    out the output bath.\\
%   \hline

%   \hline
%   \hline
%   \multicolumn{2}{c}{\bf  BATH\_FIT}\\
%   \hline
%   \hline
%   ?chi2\_fitgf(Func,Bath,Hloc,ispin[,iorb])   &  Optimizes the bath
%                                                 \texttt{Bath}
%                                                 according to the user-provided function
%                                                 \texttt{Func}, using a  Conjugate
%                                                 Gradient minimization
%                                                 of the cost function
%                                                 $\chi$, see
%                                                 Sec.~\ref{SecBathFit}.
%                                                 Argument: \texttt{Func}
%                                                 is a rank-5 cmplx array
%                                                 of dimensions 
%                                                 [\texttt{Nspin,Nspin,Norb,Norb,:}].
%                                                 For problems with
%                                                 \texttt{Nsites}
%                                                 inequivalent atoms
%                                                 \texttt{Func} is a rank-6 cmplx array
%                                                 of dimensions
%                                                 [\texttt{Nsites,Nspin,Nspin,Norb,Norb,:}]. 
%                                                 \texttt{Bath} is a rank-1 dble array
%                                                 of dimension
%                                                 \texttt{Nb=?get\_bath\_dimension}.
%                                                 or  a rank-2 dble array of 
%                                                 dimensions
%                                                 [\texttt{Nsites},\texttt{Nb}].
%                                                 \texttt{Hloc} is a rank-4 dble array of
%                                                 dimensions [\texttt{Nspin,Nspin,Norb,Norb}] or
%                                                 a rank-5 of dimensions
%                                                 [\texttt{Nsites,Nspin,Nspin,Norb,Norb}].
%                                                 \texttt{ispin} is an
%                                                 int constant
%                                                 indicating the spin
%                                                 components to fit.
%                                                 The optional argument
%                                                 \texttt{iorb} indicate
%                                                 the orbital components
%                                                 to fit. If not passed
%                                                 all orbitals are
%                                                 fitted.  \\   
%   \hline

%    \hline
%   \hline
%   \multicolumn{2}{c}{\bf  AUX\_FUNX}\\
%   \hline
%   \hline
%   ?set\_suffix(ilat,pads)   &  Sets an additional suffix for the
%                               output files of the \NAME\ library.
%                               Arguments: \texttt{ilat} is an integer
%                               constant. \texttt{pads} is an integer
%                               constant indicating the number of zero
%                               padding of the integer \texttt{ilat} in
%                               the suffix.\\
%   \hline
%   ?reset\_suffix()   &  Resets the suffix for the output
%                                    files of \NAME\ to the default value \\
%   \hline
%   ?search\_variable(var,ntmp,bool)   &  Varies the variable
%                                          \texttt{var} so that the
%                                        conjugated variable
%                                        \texttt{ntmp} is equal to the
%                                        input value \texttt{nread} up
%                                        to an error \texttt{nerr}.
%                                        Arguments: \texttt{var, ntmp}
%                                        are dble
%                                        constants. \texttt{bool} is a
%                                        logical constant indicating the success of the variation.\\
%   \hline
%   \label{TableProcedures}
% \end{tabularx}

%% References with bibTeX database:
% \section*{References}
\bibliographystyle{elsarticle-num}
\bibliography{references}

\end{document}

### 2025-03-20 edipack2.tex
Updated draft. Sketched Section 3: Installation

@@
 \usepackage{listings}
-\lstset{
+\lstdefinestyle{fstyle}{
   frame=lines,
@@
   mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt}
+  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
+}
 
@@
 \def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2.0}}
+\def\NAME{{\rm EDIpack2 }}
 
@@
 
-\title{\NAME plus Triqs interface}
-\author[]{L.~Crippa}
-\author[]{I.~Krivenko}
-\author[]{S.~Giuli}
-\author[]{G.~Bellomia}
-\author[]{....}
-% \author[]{A.~Scazzola}
-% \author[]{F.~Petocchi}
-% \author[]{G.~Mazza}
-% \author[]{L.~de Medici}
-% \author[]{M.~Capone}
-\author[a]{A.~Amaricci\corref{author}}
+\title{EDIpack2: interoperable Lanczos-based exact diagonalization solver for
+  generic quantum impurity problems.}
+% \author[]{L.~Crippa}
+% \author[]{I.~Krivenko}
+% \author[]{S.~Giuli}
+% \author[]{G.~Bellomia}
+% \author[]{....}
+% % \author[]{A.~Scazzola}
+% % \author[]{F.~Petocchi}
+% % \author[]{G.~Mazza}
+% % \author[]{L.~de Medici}
+% % \author[]{M.~Capone}
+% \author[a]{A.~Amaricci\corref{author}}
 
-\cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
+% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
 
-\address[a]{CNR-IOM, Istituto Officina dei Materiali,
-    Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136 Trieste, Italy}
+% \address[a]{CNR-IOM, Istituto Officina dei Materiali,
+%     Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136 Trieste, Italy}
 \begin{abstract}
@@
   \\
-  {\em Program Title:}  \NAME                                        \\
+  {\em Program Title:}  EDIpack2                                        \\
 {\em Licensing provisions:} GPLv3\\
@@
 
-\section{Introduction}\label{SecIntro}
+\section{Introduction and Motivation}\label{SecIntro}
 
-\section{Library Structure}\label{SecStruct}
-\subsection{Dependencies}
+A few words about the motivations who led us to develop this
+software, possible applications and advantages:
+
+* flexibility: can address generic cases including multi-orbital,
+superconducting or spin-non-conserving regimes
+
+* zero and low finite temperatures
+
+* direct access to (well approximated) analytic dynamical functions
+
+* direct access to impurity Fock space quantities
+
+bla bla bla
+
+\section{Structure}\label{SecStruct}
 \subsection{EDIpack2}
-\subsection{EDIpy}
+\subsection{EDIpack2ineq}
+\subsection{EDIpack2 C-bindings}
 \subsection{EDIpack2Triqs}
@@
 \section{Installation}\label{SecInstall}
-\subsection{Building}
-\subsection{Install}
-\subsection{Python API and TRIQS interface}
-\subsection{Conda Packaging}
+The installation of \NAME is available through CMake which ensures
+multi-platforms compabitility and dependencies resolution.  
+The software builds into two distinct libraries: {\tt
+  libedipack.a} and {\tt libedipack\_cbinding.so}.
+The former, alongside the generated Fortan modules files,
+wraps the \NAME software. The latter enables interoperability through
+bindings to the C language.
+
+\subsection{Dependencies}
+Although \NAME is as much self-contained as possible its development
+hinges on two external libraries.
+\begin{itemize}
+\item {\bf SciFortran}: an open-source Fortran library to support
+  mathematical and scientific software development. 
+\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
+\end{itemize}
+
+SciFortran provides a solid development platform enabling access to
+many algorithms and functions, including standard linear algebra
+operations and high-performance Lanczos based algorithms. This
+greatly reduces code clutter and development time.
+The use of distributed memory parallel environment, although optional,
+is required to access scalable parallel diagonalization algorithms
+which speed up calculations for large dimensional systems.
+
+\subsection{Build and Install}
+\subsubsection{Source}
+The software can be installed from source as follows. The source can
+be retrieved directly from its GitHub repository, for instance using:
+\begin{lstlisting}[language=Bash]
+git clone https://github.com/edipack/EDIpack2.0 EDIpack2
+\end{lstlisting}
+Then, assuming to be in the software directoru, a conventional
+out-of-source building is performed using two different compilations
+backends.
+
+\begin{itemize}
+  \item {\bf GNU Make}\\
+This is the default CMake workflow:
+\begin{lstlisting}[language=Bash]
+mkdir build
+cd build
+cmake ..
+make -j
+make install
+\end{lstlisting}
+
+\item{\bf Ninja}
+
+An alternative workflow employs the Ninja building backend with
+Fortran support. Ninja is generally faster and automatically supports
+multi-threaded building:
+\begin{lstlisting}[language=Bash]
+mkdir build
+cd build
+cmake -GNinja ..
+ninja
+ninja install
+\end{lstlisting}
+\end{itemize}
+
+\noindent
+The CMake configurations can be further tuned using the following variables:
+\begin{center}
+\begin{tabular}{ l|l|l } 
+ \hline
+  {\bf Option}               & {\bf Scope} & {\bf Value} \\
+  \hline
+  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
+  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
+  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
+  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
+  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
+ \hline
+\end{tabular}
+\end{center}
+
+The default target builds and install either the main library and the C-binding.
+However, a specific building for each library is available specifying
+the required target. A recap message is printed at the end of the
+CMake configuration step.
+
+\subsubsection{Anaconda}
+As an alternative we provide for both Linux and OSx systems
+installation through Anaconda packages into a virtual
+environment containing Python ($>3.10$).
+
+The Conda package installation procedure reads:
+\begin{lstlisting}[language=Bash]
+conda create -n edipack
+conda activate edipack
+conda install -c conda-forge -c edipack edipack2
+\end{lstlisting}
+\noindent
+which installs a bundle of Scifor and \NAME libraries together with
+specific {\tt pkg-config} configurations files which can be used to
+retrieve compilation and linking flags.
+
+\subsection{OS Loading}
+In oder to avoid possible conflicts or require administrative
+privileges, the building step results get installed by default in a user home
+directory, specified by the CMake variable {\tt PREFIX}.
+In doing so, however, one misses the chance of automatic loading into
+the operative system.
+
+We offer different strategies to perform this action:
+\begin{enumerate}
+\item  A CMake generated configuration file for environment module
+  which allows to load and unload the library at any time. This is
+  preferred solution for HPC systems. 
+\item A CMake generated bash script to be sourced (once or
+  permanently) in any shell session to add \NAME library to the
+  default environment.
+\item A CMake generated pkg-config configuration file to be added in
+  the pkg-config path itself.  
+\end{enumerate}
+An automatically generated recap message with all instructions is
+generated at the end of the installation procedure.
+
+\subsection{Python API}
+\subsubsection{Build from source}
+EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
+module which depends on both \NAME and SciFortran. The package can be
+obtained from the repository
+\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
+
+\begin{lstlisting}[language=Bash]
+git clone https://github.com/edipack/EDIpy2 EDIpy2
+cd EDIpy2
+pip install . 
+\end{lstlisting}
+In some more recent Python distribution the flag {\tt
+  --break-system-packages} might be required to complete
+installation or a virtual environment should be used instead.
+
+\subsubsection{Anaconda}
+As for EDIpack2, also the Python API in EDIpy2 are available through
+Anaconda packaging. In this case the resolution of the dependencies is
+taken care from Conda itself:
+
+\begin{lstlisting}[language=Bash]
+conda create -n edipack
+conda activate edipack
+conda install -c conda-forge -c edipack edipack2
+\end{lstlisting}
+
+\subsection{TRIQS interface}
+A purely Python \NAME to Triqs interface is available, leveraging on
+the C-bindings and Python API. The corresponding module depends on
+\NAME (which ultimately depends on SciFortran) and Triqs.
+Assuming the two software are correctly installed in the OS, the
+EDIpack2Triqs interface is installed as follows:
+
+\begin{lstlisting}[language=Bash]
+git clone https://github.com/krivenko/edipack2triqs
+cd edipack2triqs
+pip install .
+\end{lstlisting}
 
 \section{Usage}\label{SecUsage}
-\subsection{Basic Fortran: Bethe lattice DMFT}
-\subsection{Python code: Attractive Hubbard model}
-\subsection{TRIQS interface: Multi-orbital Hubbard}
-\subsection{Advance: Non-SU2}
+\subsection{Bethe lattice DMFT (Fortran API)}
+\subsection{Attractive Hubbard model (Python API)}
+\subsection{Multi-orbital Hubbard (Triqs)}
 
-\section{EDIpack2 Implementation}\label{SecEDIpack}
+\section{Implementation}\label{SecEDIpack}
 
 \subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a system of $N_s$ electronic levels.  A portion $N_\alpha$  of them,
-i.e. the impurity levels, interact via a local repulsion, while the
-remaining $N_s-N_\alpha$, i.e. the  \textit{bath} levels, are  non-interacting.
-In a typical setup the impurity levels are independently coupled to a
-set of $N_b$ electronic levels, so that the total number is $N_{s}=N_\alpha 
-(N_{b}+1)$. Other choices for the bath topology are possible, which entail a different counting of the total levels.
-The Hamiltonian of the electronic system we consider has the form:
-\begin{equation}\label{Ham1}
-  \begin{split}
-    \hat{H}^{e}=&\hat{H}^0+\hat{H}^{int} \\
-    \hat{H}^0 = &
-    \sum_{\a\b\sigma}
-    H^{loc}_{\a\b\sigma}d^{+}_{\a\sigma}d_{\b\sigma}  + \cr
-    &\sum_{\nu\a\b\sigma}h^\nu_{\a\b\sigma}a^{+}_{\nu\a\sigma}a_{\nu\b\sigma}+ 
-  % 
-    \sum_{\nu\a\sigma}V^\nu_{\a\sigma}d^{+}_{\a\sigma}a_{\nu\a\sigma}+
-    H.c. \\
-    \hat{H}^{int}=& U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}-\\
-    &J_X\sum_{\a\neq \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a \neq \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}
-\end{split}
-\end{equation}
-where $a_{\alpha\sigma}$, $d_{\a\sigma}$ ($a^+_{\alpha\sigma}$,
-$d^+_{\a\sigma}$) are, respectively, the destruction (creation) operators for
-the bath and impurity electrons with
-orbital $\alpha$ and spin $\sigma$,
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The term $H_{\a\b\s}^{loc}$ is the non-interacting part of
-the impurity Hamiltonian, 
-$h_{\a\b\s}^\nu$ and $V_{\a\s}^\nu$ are, respectively, the local Hamiltonian
-and the impurity hybridization of the $\nu-$th bath level. 
-  Finally, $\hat{H}^{int}$ is the local
-  multi-orbital interaction~\cite{Georges2013ACMP}.
-  The first three terms represent the density-density part of the
-  interaction, while the remaining two are,
-  respectively, the spin-exchange and pair-hopping terms. 
-  $U$ is the local Coulomb interaction strength, $J$ is the Hund's
-  coupling~\cite{Georges2013ACMP}. We introduced
-  independent coupling controlling the spin-exchange and pair-hopping terms,
-  respectively $J_X$ and $J_P$. The fully symmetric Kanamori
-  interaction is obtained setting $U'=U-2J$ and
-  $J_X=J_P=J$~\cite{Georges2013ACMP}.
 
 \subsection{The  basis states}\label{sSecBasis}
-A natural representation of the basis states for the Fock space $\FF_e$
-is obtained in the occupation number formalism of second quantization.
-The \textit{Fock basis} for a finite system of $N_s$ electrons is
-composed of states of the form
-$\ket{\vec{n}}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}$, 
-where each element $n_{a\sigma}=0,1$ describes the absence or the
-presence of an electron with spin $\sigma$ at the level $a$. In
-conjunction with the basis states, we introduce the non-Hermitian, anti-commuting, annihilation and
-creation operators $c_{a\sigma}$ and
-$c^{+}_{a\sigma}$, respectively. These operators act on the states
-$\ket{\vec{n}}$ as:  
-\begin{equation}
-  \begin{aligned}
-    % 1.
-    c_{a\sigma}\ket{\vec{n}}=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};
-  \end{aligned}
-\end{equation}
-    \begin{equation}
-  \begin{aligned}
-    c^{+}_{a\sigma}\ket{\vec{n}}=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-  \end{aligned}
-\end{equation}
-with $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$. 
-Thus, each state is represented as a string of zeros and
-ones, i.e. the binary decomposition of a given integer number $I$. Using
-the identification $\ket{\vec{n}}=\ket{I}$, with
-$I=0,\dots,2^{2N_s}-1$, each state in the Fock space can be encoded in a computer using
-a sequence of $2N_s$ bits or, equivalently, an integer number in a
-fixed representation.
-The exponentially growing size of the Fock space will
-eventually make such representation unpractical.
-A solution is obtained by decomposing each state according to the
-existing QNs. For a given set $[\vec{N}_\up,\vec{N}_\dw]$ of QNs we
-then have: 
-\begin{equation}
-  \begin{split}
-  \ket{\vec{n}} &=
-  \prod_{\a=1}^{N_{ud}}\prod_{\sigma=\up\dw}\ket{n_1\dots
-    n_{N_{bit}}}_{\a\sigma}\cr
-  &=
-  \begin{cases}
-    \ket{\vec{n}_\up}\ket{\vec{n}_\dw},\
-    \text{if}\ N_{ud}=1\\
-    %
-      \ket{\vec{n}_{1\up}}\cdots\ket{\vec{n}_{N_{ud}\up}}
-      \ket{\vec{n}_{1\dw}}\cdots\ket{\vec{n}_{N_{ud}\dw}},\
-      \text{if}\ N_{ud}=N_\alpha
-    \end{cases}
-    \end{split}
-\end{equation}
-so that, if the total number of electrons with spin $\up$ and $\dw$ is 
-conserved, any state is identified by two binary sequences of
-$N_{bit}=N_s$ bits, one per spin orientation.
-Alternatively, if the number of electrons with spin $\up$ and $\dw$ per orbital is conserved, the
-states are decomposed into two sets of
-binary sequences (one set per spin orientation), each sequence
-being made of  $N_{bit}=N_s/N_\alpha$ bits.
-Each binary sequence is associated to a suitable tuple
-of integer numbers,  univocally identifying the Fock state:
-$I \rightarrow [\vec{I}_\up,\vec{I}_\dw]$, 
-where $I=0,\dots,2^{2N_s}-1$ and
-$\vec{I}_\sigma=[I_{1\sigma},\dots,I_{N_{ud}\sigma}]$ with
-$I_{\a\sigma}=0,\dots,2^{N_{bit}}-1$. 
-Through such decomposition, each state can be described by the
-smallest bit set compatible with the conserved QNs.
-This setup generalizes the method introduced by Lin and Gubernatis in
-Ref.\onlinecite{Lin1993CIP}. 
-The relation
-between the Fock state index $I$ and its tuple decomposition can be
-easily inverted:
-\begin{equation}\label{Irelation}
-I = I_1 + \sum_{i=2}^{2N_{ud}}I_i 2^{N_{bit}(i-1)}\,,
-\end{equation}
-where we rearranged the tuple as $[\vec{I}_\up,\vec{I}_\dw]=[I_1,\dots,I_{2N_{ud}}]$.
-
-Such organization of the Fock states is used to construct
-a suitable basis for the sectors $\SS[\vec{N}_\up,\vec{N}_\dw]$.
-To any given Fock state $\ket{\vec{n}}$ and its
-integer representation $I$, containing the correct bit decomposition
-dictated by the QNs, it is associated a state $\ket{i}$ and an integer
-$i=1,\dots,D_\SS$ through a suitable \textit{map} $\vec{\MM}_\SS$.
-In particular,
-each tuple of integers identifying a Fock state belonging to $\SS$ is associated to a new
-tuple specific for each sector state:
-$I\in\SS=[\vec{I}_\up,\vec{I}_\dw]\in\SS \xrightarrow{\vec{\MM}_\SS}
-[\vec{i}_\up,\vec{i}_\dw]=i$, 
-where $\vec{i}_\sigma=[i_{1\sigma},\dots,i_{N_{ud}\sigma}]$ and
-$i_{\a\sigma}=1,\dots,D_{\a\sigma}$.
-The tuple $[\vec{i}_\up,\vec{i}_\dw]$ univocally identifies a basis state
-$\ket{i}=\ket{\vec{i}_\up,\vec{i}_\dw}$ of the sector $\SS$, through a
-relation similar to \eqref{Irelation}:
-\begin{equation}
-i = i_{1\up} +
-\sum_\sigma\sum_{l=2}^{N_{ud}}(i_{l\sigma}-1)\prod_{\a=1}^{l-1}D_{\a\sigma}
-\label{SectorIndxDecomp}
-\end{equation}
 
 \subsection{Conserved quantum numbers}\label{sSecQNs}
-A system of $N_s$ electrons is associated to
-a Fock space of the form $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$,  where $\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$ is the local
-Hilbert space of the electrons on a single level,
-$S_-$ is the anti-symmetrization operator, $\bigoplus$ is the direct sum and
-$\bigotimes$ the tensor product.
-The total dimension of the Fock space $\FF_e$ is
-$\text{dim}(\HH_e)^{N_s}=4^{N_s}= 2^{2N_s}$.
-
-The solution of the eigenvalue problem for $H_e$ is simplified by taking
-into account the existence of conserved quantities.
-The Hamiltonian \eqref{Ham1} conserves the total charge
-$\hat{N}$ and the spin component $\hat{S}_z$, as long as we assume
-that no terms  breaking the particle number or spin conservation are present,
-e.g. local spin-orbital coupling, in-plane magnetic field,
-superconducting order, etc.
-The conservation of  $\hat{N}$ and $\hat{S}_z$ can be conveniently
-re-expressed in terms of conserved number of electrons with spin $\up$ and $\dw$, i.e. $\hat{N}_\up$,
-$\hat{N}_\dw$.
-Moreover,  if the terms $H^{loc}$ and $h$ are
-diagonal and we consider only the density-density part of the
-interaction, i.e. $J_X=J_P=0$, the number of electrons with spin $\up$ and $\dw$ is conserved \textit{per
-  orbital}, i.e. $\hat{N}^m_\up$, $\hat{N}^m_\dw$, where
-$m=1,\dots,N_\alpha$.
-
-%
-% 
-In order to formally unify the treatment of these two cases we introduce some convenient
-parameters,
-  namely  $N_{ud}=1$ $(N_\alpha)$ and
-$N_{bit}=N_s$ $(N_s/N_\alpha)$ for conserved total (orbital resolved) number of
-electrons with spin $\up$ and $\dw$.
-The first corresponds to the number of conserved operators per
-spin, the latter indicates the number of electronic levels per spin
-(spin and orbital). In the following section we will give a more precise meaning to
-$N_{bit}$.
-
-In the rest of this work we will indicate the set of conserved quantum
-numbers (QN)s with the tuple $[\vec{N}_\up,\vec{N}_\dw]$, where ($\sigma=\up,\dw$):
-\begin{equation}
-  \vec{N}_\sigma=
-  \begin{cases}
-    N_{1\sigma}\==N_\sigma, & \text{if}\ N_{ud}=1 \\
-    [N_{1\sigma},\dots,N_{N_\alpha\sigma} ], & \text{if}\ N_{ud}=N_\alpha    
-  \end{cases}
-\end{equation}
-  Note that for $N_{ud}=1$ we identified the single
-  component $N_{1\sigma}$ of the vector $\vec{N}_\sigma$ with the
-  total number of electrons with spin $\sigma$, i.e. $N_{\sigma}$.
-
-In presence of a set of conserved QNs,  the Fock space decomposes into
-a number of sub-spaces of reduced dimension, each
-corresponding to a given value of the QNs tuple. We indicate
-each sub-space with the term \textit{sector} and the symbol
-$\SS[\vec{N}_\up,\vec{N}_\dw]$, or just $\SS$ where no confusion
-arises.
-The dimension of each sector is given by the number of ways we can
-arrange $N_{\a\sigma}$ elements into $N_{bit}$ positions, i.e.:
-\begin{equation}
-  \begin{split}
-  \text{dim}\left(\SS[\vec{N}_\up,\vec{N}_\dw]\right)  & =  \prod_{\a=1}^{N_{ud}}
-  \binom{N_{bit}}{N_{\a\up}}
-  \prod_{\a=1}^{N_{ud}}
-  \binom{N_{bit}}{N_{\a\dw}}\cr
-  &\==
-  \prod_{\a=1}^{N_{ud}}D_{\a\up}
-  \prod_{\a=1}^{N_{ud}}D_{\a\dw}
-  \stackrel{\text{def}}{=}D_{\up}D_{\dw} \== D_\SS
-  \end{split}
- \label{nud_dimension}
-\end{equation}
-where we introduced the symbols $D_\sigma$ and $D_{\a\sigma}$  to
-indicate, respectively, the dimension of total and orbital spin-subspace 
-associated to the given set of QNs. Note that $D_\sigma\==D_{1,\sigma}$ for
-$N_{ud}=1$.
 
 \subsection{Krylov based Diagonalization}\label{sSecHam}
-The matrix representing the system Hamiltonian in the Fock space has a
-block-diagonal structure in presence of a given set of conserved QNs.
-Each block corresponds to the Hamiltonian of a sector
-$\SS[\vec{N}_\up,\vec{N}_\dw]$. The analysis of the spectrum, thus,
-reduces to the recursive analysis of the sector Hamiltonians. 
-In each sector, the Hamiltonian of the system has the following general form: 
-\begin{equation}
-H^e_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{Hdecomp}
-\end{equation}
-$H_d$ is a diagonal term containing the local part of the Hamiltonian,
-including the density-density terms of the interaction.
-The $H_\sigma$ components describe all the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-Finally the term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-If the QNs are conserved per orbital, i.e. if $H_{nd}\==0$ and no
-inter-orbital local hopping terms are present,  each $H_\sigma$
-further splits into a sum of smaller terms:
-$$
-H_\sigma = \sum_{\a=1}^{N_\alpha}\mathbb{I}_{1\sigma}\otimes\cdots\otimes
-H_{\a\sigma}\otimes\cdots\otimes \mathbb{I}_{N_\alpha\sigma}
-$$
 
-Each term of the  Hamiltonian matrix is constructed  independently 
-iterating over one or more  components of the sector basis states.
-For example, the construction of the matrices $H_{\a\sigma}$ only involve iterations over the components
-$\ket{i_{\a\sigma}}$ of the sector basis. In general we have:
-\begin{equation}
-\begin{split}
-  \bra{\vec{i}_\up\vec{i}_\dw}H^e_\SS\ket{\vec{j}_\up\vec{j}_\dw}
-  =&
-  \bra{\vec{i}_\up\vec{i}_\dw}
-  H_d + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes H_\dw + H_{nd}
-  \ket{\vec{j}_\up\vec{j}_\dw}\cr
-  =&
-  \bra{\vec{i}_\up\vec{i}_\dw}H_d\ket{\vec{i}_\up\vec{i}_\dw} +\cr
-  &\bra{\vec{i}_\up}H_\up\ket{\vec{j}_\up}\delta_{\vec{i}_\dw\vec{j}_\dw}
-  +
-  \bra{\vec{i}_\dw}H_\dw\ket{\vec{j}_\dw}\delta_{\vec{i}_\up\vec{j}_\up} + \cr
-  &\bra{\vec{i}_\up\vec{i}_\dw}H_{nd}\ket{\vec{j}_\up\vec{j}_\dw} 
-\end{split}
-\label{Hbuild}
-\end{equation}
+\subsection{Dynamical correlation functions}
 
-For very large systems, storing the Hamiltonian matrix in the memory
-can be highly inefficient.
-In such cases, Krylov or Lanczos
-methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a massively
-parallel framework.
+\subsection{Observables}
 
-\subsection{Dynamical correlation functions, observables and reduced
-  impurity density matrix}
+\subsection{Reduced impurity density matrix}
 
@@
 
-\subsection{Bath $\chi^2$ fit}
+\subsection{Bath Optimization}
 
@@
 
-\section{EDIpy: Python API}\label{SecEDIpy}
+\section{Inequivalent impurities}
 
-\section{edipack2triqs: a thin interface to TRIQS}\label{Secedi2triqs}
+\section{C-bindings}\label{SecCbind}
+
+\section{Python API}
+
+\section{Triqs interface}\label{SecEDI2Triqs}
 
@@
 \section*{Acknowledgements}
-
-% \section*{Appendix A: Input Variables}\label{AppendixA}
-% Here is reported a list of the global input variables of the
-% library. The input parameters are arranged into the following table,
-% as discussed in \secu{SecWorkflow}.
-% Note that only a subset of the input parameters are transparent to the
-% user, i.e. can be directly accessed from the calling program.
-% These variables  are indicated with a symbol in the first column of
-% the table.  In the columns from $2^{\rm nd}$ to $4^{\rm th}$ we indicate,
-% respectively, the variable name, the type and the default value.
-% Finally, In the last column we provide a short
-% description of the variable purpose.
-
-% % \begin{longtable}{ M{0.01pt} T{0.19\textwidth}  T{0.04\textwidth}
-%     %     D{0.11\textwidth} M{0.52\textwidth}  }
-
-% \begin{tabularx}{\linewidth}{ M{0.01\textwidth} T{0.19\textwidth}
-%     T{0.04\textwidth} D{0.11\textwidth} M{0.52\textwidth} }
-%   \caption{List of the \NAME\ input variables.}\\
-%   \hline 
-%   \hline
-%   {\it \footnotesize \phantom{T}} & {\it Variable} & {\it Type} & {\it Default} & {\it
-%                                                          \footnotesize
-%                                                          Description} \\
-%   \hline
-%   \hline
-%   \endhead
-%   \hline
-%   \multicolumn{5}{c}{\bf Most relevant control variables}\\
-%   \hline
-%   $\circ$ & Norb & Int & 1 & Number of impurity orbitals.\\
-%   \hline
-%   $\circ$ & Nspin& Int & 1 & Number of spin channels treated
-%                              independently. \texttt{Nspin}=1 enforces
-%                              non-magnetic solution.\\
-%   \hline
-%    & Nbath& Int & 6  & Number of bath sites. See \texttt{bath\_type}
-%                        for information about resulting total number of
-%                        electronic levels $N_s$.\\
-%   \hline
-%   $\circ$ & bath\_type& Char & ``normal''    & Set the bath type:
-%                                      \texttt{normal}:
-%                                      $N_s=\mathtt{Norb}(1+\mathtt{Nbath})$,
-%                                      \texttt{hybrid}:
-%                                      $N_s=\mathtt{Norb}+\mathtt{Nbath}$,
-%                                      and \texttt{replica}:
-%                                      $N_s=\mathtt{Norb}(1+\mathtt{Nbath})$,
-%                                      See \secu{SecBath}.\\
-%   \hline
-% %--------
-%   $\circ$ & Uloc& Dble & 2.0   & Local intra-orbital interactions $U$,
-%                                      different values per orbitals can
-%                                      be defined.\\
-%   \hline
-%   $\circ$ & Ust& Dble & 0.0   & Local inter-orbital interaction $U'$,
-%                                 with opposite spin orientations.
-%                                 For the Kanamori interaction this 
-%                                 must be set to
-%                                 $\mathtt{Uloc}-2\mathtt{Jh}$, with \texttt{Jh}
-%                                 the Hund's coupling. 
-%                                 The value $U''$ for equal spin orientation
-%                                 is automatically set by the difference 
-%                                 $\mathtt{Ust}-\mathtt{Jh}$. \\
-%   \hline
-%   $\circ$ & Jh   & Dble & 0.0 &  Hund's coupling.\\
-%   \hline
-%   $\circ$ & Jx   & Dble & 0.0 & Spin-Exchange coupling constant.\\
-%   \hline
-%   $\circ$ & Jp   & Dble & 0.0 & Pair-Hopping coupling constant.\\
-%   \hline
-%     $\circ$ & beta   & Dble & 1000 & Inverse temperature. For $T=0$
-%                                    calculations this value sets a 
-%                                    discretization of the Matsubara
-%                                    frequencies.\\
-%   \hline
-%   $\circ$ & xmu   & Dble & 0.0 & Chemical potential. This parameter
-%                                  sets the average occupations of the
-%                                  impurity. 
-%                                  If \texttt{HFMODE=True} this value
-%                                  contains the Hartree shift, i.e. $\mathtt{xmu}=0.0$ sets the half-filling for a particle-hole
-%                                  symmetric case.\\
-%   \hline
-%      & HFmode  & Bool & .true. & If True the Hartree shift is included in the
-%                 interaction, e.g. $U(n_\up-1/2)(n_\dw-1/2)$. In this
-%                        case zero chemical potential corresponds to
-%                        half-filling for a particle-hole symmetric system.\\  
-%   \hline
-%   $\circ$ & Lmats & Int & 4096 & Number of Matsubara frequencies.\\
-%   \hline
-%   $\circ$ & Lreal  & Int & 5000 & Number of real-axis frequencies\\
-%   \hline
-%     $\circ$ & eps   & Dble & 0.01 & Real-axis broadening.\\
-%   \hline
-%   $\circ$ & wini, wfin & Dble & -5, 5 & Real-axis frequency range.\\
-%   \hline
-%   $\circ$ & Nloop    & Int & 100 & Maximum number of allowed iterations in the DMFT solution.\\
-%   \hline
-%   $\circ$ & dmft\_error & Dble & 1e-5 & Convergence threshold for the
-%                                         DMFT iterative cycle.\\
-%   \hline
-%   %--------
-%   $\circ$ & Nph    & Int & 0 & Maximum number of phonons.\\
-%   \hline
-%   $\circ$ & g\_ph   & Dble & 0.0& Electron-Phonon coupling.\\
-%   \hline
-%   $\circ$ & w0\_ph  & Dble & 0.0& Holstein phonon frequency.\\
-%   \hline
-%   $\circ$ & xmin, xmax & Dble & -3, 3& Phonon probability distribution spatial range.\\
-%   \hline
-% %--------
-%    & chispin\_flag & Bool & .false. & Flag to include the evaluation of Spin-Spin susceptibilities.\\
-%   \hline
-%    &  chidens\_flag &Bool & .false. & Flag to include the evaluation of Density-Density susceptibilities.\\
-%   \hline
-%    & chipair\_flag & Bool & .false. &  Flag to include the evaluation
-%                                       of $s$-wave Pair susceptibilities.\\
-%   \hline
-%    & chiexct\_flag & Bool & .false. & Flag to include the evaluation of Excitonic susceptibilities.\\
-%   \hline
-%   %-------
-%    & ed\_sparse\_H    & Bool & .true. &  Flag to select storage type of the sparse
-%                          Hamiltonian. True: sparse matrix object,
-%                          False:on-the-fly matrix-vector product.\\
-%   \hline
-%    & ed\_total\_ud     & Bool & .true. & Flag to select quantum numbers type.
-%                                  True: conserved total electron occupation per
-%                                  spin. 
-%                                  False: conserved electrons
-%                                  occupations per orbital and spin.\\
-%   \hline 
-%    & ed\_print\_Sigma & Bool & .true. & Flag to print out the impurity Self-energies.\\
-%   \hline
-%    & ed\_print\_G        & Bool & .true. & Flag to print out the interacting impurity Green's functions.\\
-%   \hline
-%    & ed\_print\_G0      & Bool & .true. & Flag to print out the non-interacting
-%                               impurity Green's functions.\\
-%   \hline
-%    & ed\_twin             & Bool & .false. & Flag to reduce the number of visited
-%                                        sector using  sectors symmetry:
-%                                        $[\vec{N}_\up,\vec{N}_\dw]\leftrightarrow[\vec{N}_\dw,\vec{N}_\up]$.
-%                                        A warning is raised if
-%                                        \texttt{ed\_twin=.true.} and
-%                                        \texttt{Nspin=2} as this
-%                                        symmetry 
-%                                        conflicts with possible long-range
-%                                        magnetic order.\\ 
-%   \hline
-%    & ed\_verbose       & Int & 3 & Verbosity level [0-5]. \\
-%   \hline
-%   % ----------
-%    & lanc\_method     & Char & ``arpack'' & String to select Lanczos
-%                                    method. \texttt{ARPACK}: uses
-%                                    P-Arpack, \texttt{LANCZOS}: uses
-%                                    single vector Lanczos method
-%                                    with no re-orthogonalization \\
-%   \hline
-%    & lanc\_tolerance  & Dble & 1e-18 & Tolerance for the Lanczos algorithm. \\
-%   \hline
-%    & lanc\_niter         & Int & 512 & Largest number of Lanczos
-%                                        iterations used in the
-%                                        Diagonalization of each sector Hamiltonian.\\
-%   \hline
-%    & lanc\_ngfiter      & Int & 200 & Largest dimension of the Krylov basis in
-%                               the evaluation of the Green's function.\\
-%   \hline
-%   & lanc\_nstates\_sector  & Int & 2 & Maximum number of eigenvalues per sector
-%                                         required to P-Arpack. For $T>0$ this number
-%                                         indicates an initial guess and
-%                                        is adjusted during the
-%                                        annealing.  \\
-%   \hline
-%    & lanc\_nstates\_total    & Int & 1 & Maximum number of states in
-%                                          the spectrum. 
-%                                          $\mathtt{lanc\_nstates\_total}=1$
-%                                          indicates that only the
-%                                          groundstate should be
-%                                          evaluated, resulting in zero
-%                                          temperature calculation.
-%                                          For $T>0$ calculations a value 
-%                                          $\mathtt{lanc\_nstates\_total}>1$
-%                                          is required. This value is
-%                                          used as an initial guess and adjusted
-%                                          during finite temperature
-%                                          annealing. See
-%                                          \texttt{cutoff} and
-%                                          Sec.~\ref{CodeEigenspace}. \\
-%   \hline
-%      & ed\_finite\_temp & Bool & .false. &  Flag to select finite temperature
-%                                          method. If True 
-%                                          $\mathtt{lanc\_nstates\_total} > 1$ is required.\\  
-%   \hline
-
-%    & lanc\_ncv\_factor & Int & 10 & Factor to determine block size
-%                                     \texttt{Ncv} used in P-Arpack 
-%                                     using the expression:
-%                                           $\mathtt{Ncv}=\mathtt{lanc\_ncv\_factor}*\mathtt{Neigen}+\mathtt{lanc\_ncv\_add}$.
-%                                           P-Arpack requires \texttt{Ncv}
-%                                           to be at least twice of the
-%                                           required Eigensolutions \texttt{Neigen}.
-%                                           At zero temperature
-%                                           \texttt{Neigen}=\texttt{lanc\_nstates\_sector}. 
-%                                           At finite temperature
-%                                           \texttt{Neigen} is
-%                                           automatically adjusted from
-%                                           initial value, possibly leading to
-%                                           a block size \texttt{Ncv}
-%                                           too large.
-%                                           Reducing the value of
-%                                           \texttt{lanc\_ncv\_factor}
-%                                           down to its minimum value 2
-%                                           can be required to perform P-Arpack calculations.\\
-%   \hline
-%    & lanc\_ncv\_add       & Int & 0 & Factor to determine block size
-%                                       \texttt{Ncv} used in P-Arpack 
-%                                       using  the expression:
-%                                       $\mathtt{Ncv}=\mathtt{lanc\_ncv\_factor}*\mathtt{Neigen}+\mathtt{lanc\_ncv\_add}$.
-%                                       P-Arpack requires \texttt{Ncv}
-%                                       to be at least twice of the
-%                                       required Eigensolutions
-%                                       \texttt{Neigen}. \\
-%   \hline   
-%   % ----------  
-%   $\circ$ & cg\_Scheme           & Char & ``Weiss'' & Conjugate Gradient fit scheme.
-%                                                       \texttt{Delta}: fit $\Delta(i\omega_n)$, \texttt{Weiss}: fit $\GG_0(i\omega_n)$.\\
-%   \hline
-%    & cg\_method           & Int & 0 & Conjugate Gradient minimization method.
-%                                       $\mathtt{cg\_method}=0$: Fletcher-Reeves-Polak-Ribiere
-%                                       minimisation algorithm. 
-%                                       $\mathtt{cg\_method}=1$: use the f77 \texttt{minimize} procedure published in
-%                                       Ref.\onlinecite{Georges1996RMP}
-%                                       and largely used in the DMFT community.\\
-%   \hline
-%    & cg\_Lfit   & Int & 1000 & Number of Matsubara frequencies used in
-%                                the calculation of the cost function
-%                                $\chi$ with the Conjugate
-%                                Gradient minimization. $\mathtt{Lfit}\leq\mathtt{Lmats}$.  \\
-%   \hline
-%    & cg\_grad             & Int & 0 & Type of gradient evaluation. $\mathtt{cg\_grad}=0$: Analytic,
-%                                       $\mathtt{cg\_grad}=1$:
-%                                       Numeric. If
-%                                       $\mathtt{cg\_method}=1$ then use
-%                                       of 
-%                                       $\mathtt{cg\_grad}=1$ is
-%                                       enforced as this method does not
-%                                       support analytic gradient calculation.\\
-%   \hline
-%   \hline
-%   \multicolumn{5}{c}{\bf More specific control variables, less
-%   frequently changed}\\
-%   \hline
-%   \hline  
-%   $\circ$ & sb\_field & Dble & 0.0& Small symmetry-breaking field.\\
-%   \hline  
-%   $\circ$ & Nsuccess  & Int & 1 & Minimum number of repeated iterations below
-%                                   threshold required to reach convergence.  \\
-%   \hline
-%    & cutoff  & Dble & 1e-9 & Cutoff for the Boltzmann factor in the
-%                              spectral summation, i.e.
-%                              $e^{-\beta(E-E_0)}<\mathtt{cutoff}$. See Sec.~\ref{CodeEigenspace}.\\
-%   \hline  
-%    & gs\_threshold & Dble & 1e-9 & Energy threshold for the groundstate
-%                       degeneracy. Eigenstates of energy $E$ within
-%                                    $|E-E_0|<\mathtt{gs\_threshold}$
-%                                    are considered as degenerate groundstates.\\
-%   \hline
-%    &ed\_sectors & Bool & .false. & This flag is used to reduce
-%                                          the number of sectors
-%                                     investigated during the
-%                                     construction of the spectrum. Only
-%                                     the sectors with QNs listed in the file
-%                                     \texttt{SectorFile} and those with
-%                                     plus and minus
-%                                     \texttt{ed\_sectors\_shift} are considered.\\
-%   \hline
-%     & ed\_sectors\_shift & Int & 1 & A shift of the QNs for the list
-%                                      of sectors read from
-%                                      \texttt{SectorFile} is
-%                                      \texttt{ed\_sectors=.true.}.
-%                                      The list is enlarged
-%                                      including the QNs obtained
-%                                      by applying a shift
-%                                      $\pm
-%                                      1,\ldots,\pm\mathtt{ed\_sectors\_shift}$
-%                                      to each element of the list.\\
-%   \hline
-%    & ed\_hw\_bath & Dble & 2.0 & The half-bandwidth for the bath
-%                               initialization using discretized flat density of
-%                               states.\\
-%   \hline  
-%    & ed\_offset\_bath & Dble & 0.1 & Energy offset for the
-%                                    initialization of the diagonal
-%                                    terms in replica bath. A small
-%                                    value randomly chosen in the
-%                                    interval
-%                                    $\epsilon\in [-\mathtt{ed\_offset\_bath}:\mathtt{ed\_offset\_bath}]$
-%                                    is added to the diagonal terms of
-%                                    the bath to avoid possible spectral
-%                                      degeneracies.\\
-%   \hline
-%   $\circ$ & Lpos & Int & 100 & Number of points used to obtain the phonon probability
-%                      distribution function.\\ 
-%   \hline
-%   $\circ$ & nread & Dble & 0.0 & Target density for fixed density
-%                        calculations. Use the procedure
-%                        \texttt{ed\_search\_variable}   to adjust
-%                        chemical potential \texttt{xmu} so that local
-%                        occupation is
-%                        $|n-\mathtt{nread}|<\mathtt{nerr}$. \\
-%   \hline
-%    & nerr & Dble & 1e-4 & Error threshold for fixed-density
-%                        calculations.\\
-%   \hline 
-%    & ndelta& Dble & 0.1 & Initial step for the variation of the chemical
-%                        potential in fixed-density calculations.\\
-%   \hline  
-%    & ncoeff & Dble & 1d0 & A multiplier for the initial ndelta as read
-%                            from a file: $\mathtt{ndelta}\rightarrow\mathtt{ndelta}*\mathtt{ncoeff}$.\\
-%   \hline  
-%    & ed\_solve\_offdiag\_gf & Bool & .false. & Force the calculation of
-%                                          the off-diagonal Green's
-%                                          functions.
-%                                          True if \texttt{bath\_type}$\neq$\texttt{normal} \\ 
-%   \hline
-%    & ed\_all\_G           & Bool & .false. & Flag to evaluate all components of the
-%                                              impurity Green's functions,
-%                                              irrespective of the symmetries of the
-%                                              problem when using
-%                                              \texttt{bath\_type}=\texttt{replica}.
-%                                              If False only the Green's
-%                                              functions corresponding
-%                                              to non-vanishing
-%                                              components of the bath
-%                                              Hamiltonian
-%                                              $h^\nu_{\a\b\sigma}$ are
-%                                              evaluated.  \\
-%   \hline
-%    & lanc\_nstates\_step    & Int & 2 & Number of states to be added
-%                                         to
-%                                         \texttt{lanc\_nstates\_sector}
-%                                         for each sector during finite
-%                                         temperature annealing of the
-%                                         state list. See
-%                                         Sec.~\secu{CodeEigenspace}. \\  
-%   \hline
-%    & lanc\_dim\_threshold   & Int & 1024 & Dimension threshold below
-%                                            which Lapack diagonalization method is
-%                                            used to determine
-%                                            eigensolutions. \\
-%   \hline
-%    & cg\_Niter             & Int & 500 & Maximum number of iteration
-%                                          for the Conjugate Gradient minimization.\\
-%   \hline
-%    & cg\_Ftol             & Dble & 1e-6 & Tolerance for the Conjugate Gradient minimization.\\
-%   \hline
-%    & cg\_stop             & Int & 0 & Stop condition for the Conjugate Gradient
-%                                       minimization of the cost function $\chi(x)$.
-%                                       0: $C_1+C_2$, 1: $C_1$, 2: $C_2$ with
-%                                       conditions 
-%                                       $C_1=|\chi^{n-1} - \chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$,
-%                                       $C_2=||x^{n-1}
-%                                       -x^n||<\mathtt{cg\_Ftol}(1+||x^n||)$. See
-%                                       Sec.~\secu{SecBathFit}.\\
-%   \hline
-%    & cg\_Weight         & Int & 1 & A weight factor used in the cost
-%                                     function $\chi$ of the Conjugate
-%                                     Gradient minimization. Increasing this
-%                                     parameter favors the fit of the low
-%                                     frequency part of $\chi$.
-%                                     1: $\mathtt{cg\_weight}=1$,
-%                                     2: $\mathtt{cg\_weight}=1/\mathtt{Lfit}$,
-%                                     3:
-%                                     $\mathtt{cg\_weight}=1/\omega_n$. See
-%                                     Sec.~\secu{SecBathFit}.\\
-%   \hline
-%    & cg\_pow             & Int & 2 & The exponent of the cost function
-%                                      $\chi$ as 
-%                                      $|X -
-%                                      X^{And}|^{\mathtt{cg\_pow}}$ used
-%                                      in Conjugate Gradient
-%                                      minimization. See Sec.~\ref{SecBathFit}.\\
-%   \hline
-%   % ----------
-%   $\circ$ & Hfile & Char & ``hamiltonian'' & File name to read/write bath parameters\\
-%   \hline
-%   & SectorFile & Char & ``sectors'' & File name to read/write
-%                                              sectors contributing to
-%                                              the state list. On output
-%                                              it contains the QNs of
-%                                              the list of sectors
-%                                              contributing to the
-%                                              evaluated spectrum. On
-%                                              input such list is used
-%                                              to reduce the sectors
-%                                              analysis. See
-%                                       \texttt{ed\_sectors} and \texttt{ed\_sectors\_shift}. \\
-%   \hline
-%   $\circ$ & LOGfile  & Int & 6 & Fortran unit for the log
-%                                  output. Value must be in  the range
-%                                  $[6:999]$. 6 is the standard output. \\
-%   \hline
-%   \label{TableParameters}
-% \end{tabularx}
-
-% \section*{Appendix B: Main procedures}\label{AppendixB}
-% In this appendix we report a list of all the procedures made
-% accessible by either Fortan or Python API of the \NAME\ library. As
-% discussed in Sec.~\ref{SecUsage} all such procedures feature implicit
-% MPI support, i.e. they are executed in parallel if the MPI framework
-% has been initialized in the calling program.
-
-% In the first column we report the procedure names and the possible
-% input arguments. In order to unify the naming conventions of the
-% interfaces we use the prefix \texttt{?=ed\_,  edipack.} to indicate,
-% respectively, the Fortran and Python procedures.
-% In the second column we briefly describe the purpose of
-% the procedure and the nature of the arguments.
-% The inputs in square brackets are optional.
-
-% The procedures are grouped with respect to the library module
-% containing them, indicated in a single column at the beginning of each
-% group.
-
-% \begin{tabularx}{\linewidth}{ T{0.46\textwidth}  M{0.49\textwidth} }
-%   \caption{List of the \NAME\ procedures.}\\
-%   \hline
-%   \hline
-%   {\it PROCEDURE} {(\texttt{?=ed\_, edipack.})} & {\it \footnotesize INFO} \\
-%   \hline
-%   \hline
-%   \endhead
-%   \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf INPUT\_VARS}\\
-%   \hline
-%   \hline
-%   ?read\_input(File) &
-%                        Reads global input variables from the user
-%                        indicated file \texttt{File}.
-%                        Argument: \texttt{File} is a character string of arbitrary length.
-%                        If the file does not exist in the calling directory
-%                        a default one with prefix 
-%                        ``\texttt{used.}'' is produced using default
-%                        values.
-%                        The value of
-%                        each variable can be updated also from command line
-%                        using the syntax \texttt{Variable=}$Value$.\\
-%   \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf  MAIN}\\
-%   \hline
-%   \hline
-%   ?init\_solver(Bath) & Initializes the whole ED calculation, allocate global static 
-%                         memory, perform compatibility checks and setup global
-%                         variables.
-%                         Argument: \texttt{Bath}  is a rank-1 dble array 
-%                         of dimension \texttt{Nb=?get\_bath\_dimension}.
-%                         For problems with \texttt{Nsites} inequivalent atoms
-%                         \texttt{Bath} is a rank-2 dble array of 
-%                         dimensions [\texttt{Nsites},\texttt{Nb}].
-%                         On \texttt{Bath} contains the bath parameters, either guessed from
-%                         flat density of states  or read from the
-%                         file \texttt{Hfile.restart}. \\
-%   \hline
-%   ?solve(Bath,Hloc)  &   Solve the quantum impurity problem using ED
-%                        method.
-%                        Arguments: \texttt{Bath} is a rank-1 dble array
-%                         of dimension
-%                        \texttt{Nb=?get\_bath\_dimension}.
-%                        For problems with \texttt{Nsites} inequivalent atoms
-%                        \texttt{Bath} is a rank-2 dble array of 
-%                        dimensions [\texttt{Nsites},\texttt{Nb}].
-%                        \texttt{Hloc} is a rank-4 dble array of
-%                        dimensions [\texttt{Nspin,Nspin,Norb,Norb}] or
-%                        a rank-5 of dimensions
-%                        [\texttt{Nsites,Nspin,Nspin,Norb,Norb}]. Arguments
-%                        are not changed on output.\\
-
-%   \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf  IO}\\
-%   \hline
-%   \hline
-%   ?get\_sigma\_matsubara(Func,[Nsites])  & Returns the Matsubara
-%                                               self-energy function in \texttt{Func}.
-%                                               Argument: \texttt{Func}
-%                                               is a rank-5 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lmats}].
-%                                               If \texttt{Nsites} is
-%                                               present \texttt{Func}
-%                                               is a rank-6 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lmats}]
-%                                               and the procedure returns
-%                                               the function for each
-%                                               inequivalent atom.\\
-%   \hline
-%   ?get\_sigma\_realaxis(Func,[Nsites])  &  Returns the real-axis
-%                                               self-energy function in \texttt{Func}.
-%                                               Argument: \texttt{Func}
-%                                               is a rank-5 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lreal}].
-%                                               If \texttt{Nsites} is
-%                                               present \texttt{Func}
-%                                               is a rank-6 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lreal}]
-%                                               and the procedure returns
-%                                               the function for each
-%                                               inequivalent atom.\\
-%   \hline
-%   ?get\_gimp\_matsubara(Func,[Nsites])  & Returns the Matsubara
-%                                              impurity Green's function in \texttt{Func}.
-%                                               Argument: \texttt{Func}
-%                                               is a rank-5 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lmats}].
-%                                               If \texttt{Nsites} is
-%                                               present \texttt{Func}
-%                                               is a rank-6 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lmats}]
-%                                               and the procedure returns
-%                                               the function for each
-%                                               inequivalent atom.\\
-%   \hline
-%   ?get\_gimp\_realaxis(Func,[Nsites])  & Returns the real-axis
-%                                              impurity Green's function in \texttt{Func}.
-%                                               Argument: \texttt{Func}
-%                                               is a rank-5 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nspin,Nspin,Norb,Norb,Lreal}].
-%                                               If \texttt{Nsites} is
-%                                               present \texttt{Func}
-%                                               is a rank-6 cmplx array
-%                                               of dimensions
-%                                               [\texttt{Nsites,Nspin,Nspin,Norb,Norb,Lreal}]
-%                                               and the procedure returns
-%                                               the function for each
-%                                               inequivalent atom.\\
-%   \hline
-
-%   ?get\_dens(Var,[Nsites])  & Returns the impurity occupations in
-%                                  \texttt{Var}.
-%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
-%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
-%                                  dimensions [\texttt{Nsites,Norb}] and the procedure returns
-%                                  the value for each inequivalent atom.\\
-%   \hline
-%   ?get\_mag(Var,[Nsites])  &  Returns the impurity magnetization in
-%                                 \texttt{Var}.
-%                                 Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
-%                                 If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
-%                                 dimensions [\texttt{Nsites,Norb}] and the procedure returns
-%                                 the value for each inequivalent atom.\\
-%   \hline
-%   ?get\_docc(Var,[Nsites])  & Returns the impurity double occupancy
-%                                  in \texttt{Var}.
-%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [\texttt{Norb}].
-%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
-%                                  dimensions [\texttt{Nsites,Norb}] and the procedure returns
-%                                  the value for each inequivalent atom.\\
-%   \hline
-%   ?get\_eimp(Var,[Nsites])  & Returns the impurity local energies components
-%                                  in \texttt{Var}.
-%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [4].
-%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
-%                                  dimensions [\texttt{Nsites,4}] and the procedure returns
-%                                  the value for each inequivalent atom.\\
-%   \hline
-%   ?get\_doubles(Var,[Nsites])  & Returns additional impurity double
-%                                  occupancies from multi-orbital
-%                                  terms in \texttt{Var}.
-%                                  Argument: \texttt{Var} is a rank-1 dble array of dimensions [4].
-%                                  If \texttt{Nsites} is present \texttt{var} is a rank-2 dble array of
-%                                  dimensions [\texttt{Nsites,4}] and the procedure returns
-%                                  the value for each inequivalent atom.\\
-
-%   \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf  BATH}\\
-%   \hline
-%   \hline
-%   ?get\_bath\_dimension() & Returns the number \texttt{Nb} of bath parameters
-%                                required to describe the quantum
-%                                impurity problem, based on the value of
-%                                different input variables,
-%                                e.g. \texttt{Norb, Nbath, bath\_type}.
-%                                Output: \texttt{Nb} integer constant. \\
-%   \hline
-%   \makecell[l]{
-%   ?set\_Hreplica(Hloc) \\
-%   ?set\_Hreplica(Hvec,LambdaVec)} & Sets up the matrix basis and the
-%                                     initial guess for the variational
-%                                     bath parameters which determined
-%                                     the shape of the  bath for \texttt{bath\_type=replica}.
-%                                     The procedure
-%                                     accepts either the local
-%                                     non-interacting Hamiltonian
-%                                     \texttt{Hloc} or  the \texttt{Nsym}
-%                                     matrix basis components
-%                                     \texttt{Hvec} and the
-%                                     corresponding variational
-%                                     parameters \texttt{Lambdavec}. See
-%                                     Sec.~\ref{SecBath}.  
-%                                     Arguments: \texttt{Hloc} is a
-%                                     rank-4 dble array of dimensions
-%                                     [\texttt{Nspin,Nspin,Norb,Norb}]
-%                                     or a rank-2 dble array of dimensions
-%                                     [\texttt{Nspin*Norb,Nspin*Norb}].
-%                                     \texttt{Hvec} is a rank-5 dble
-%                                     array of dimensions
-%                                     [\texttt{Nspin,Nspin,Norb,Norb,Nsym}].
-%                                     \texttt{LambdaVec} is a rank-1
-%                                     dble array of dimensions
-%                                     \texttt{Nsym} or a rank-2 dble
-%                                     array of dimensions
-%                                     [\texttt{Nsites,Nsym}], for
-%                                     \texttt{Nsites} inequivalent
-%                                     atoms. \\
-%   \hline
-
-%   ?get\_bath\_component\_dimension(Type) & Returns the dimensions a 
-%                                            rank-3 dble array should
-%                                            have to store a specific
-%                                            component of the bath. 
-%                                            The output is a rank-1 int
-%                                            array \texttt{Ndim(1:3)} of dimension 3. 
-%                                            Argument: \texttt{Type} is
-%                                            a single
-%                                            character. Possible values
-%                                            are \texttt{Type=e, v, l},
-%                                            corresponding to energy,
-%                                            hybridization or lambda
-%                                            components. \\
-%   \hline
-%   ?get\_bath\_component(Array,Bath,Type) & Returns in
-%                                                 \texttt{Array} the
-%                                                 specified components
-%                                                 \texttt{Type} of the
-%                                                 bath \texttt{Bath}.
-%                                                 Arguments:
-%                                                 \texttt{Array} a
-%                                                 rank-3 dble array of
-%                                                 dimensions
-%                                                 [\texttt{Ndim(1),Ndim(2),Ndim(3)}]
-%                                                 as returned by a call
-%                                                 to
-%                                                 \texttt{?get\_bath\_component\_dimension(Type)}.
-%                                                 \texttt{Bath} is a
-%                                                 rank-1 dble array of dimension
-%                                                 \texttt{Nb=?get\_bath\_dimension}.
-%                                                 \texttt{Type=e, v, l}
-%                                                 is  a single character.\\
-%   \hline
-%   ?set\_bath\_component(Array,Bath,Type) &
-%                                                Sets the specified component
-%                                                \texttt{Type} in the
-%                                                bath \texttt{Bath}
-%                                                to \texttt{Array}.
-%                                                Arguments:
-%                                                \texttt{Array} a
-%                                                rank-3 dble array of
-%                                                dimensions
-%                                                [\texttt{Ndim(1),Ndim(2),Ndim(3)}]
-%                                                as returned by a call
-%                                                to
-%                                                \texttt{?get\_bath\_component\_dimension(Type)}.
-%                                                \texttt{Bath} is a
-%                                                 rank-1 dble array of dimension
-%                                                \texttt{Nb=?get\_bath\_dimension}.
-%                                                \texttt{Type=e, v, l}
-%                                                is  a single character.\\
-%   \hline
-%   ?copy\_bath\_component(BathIN,BathOUT,Type) & Copies the specified component
-%                                                \texttt{Type} from the
-%                                                    input bath
-%                                                    \texttt{BathIn} to
-%                                                    the output bath \texttt{BathOut}. 
-%                                                    Arguments:
-%                                                    \texttt{BathIn} and
-%                                                    \texttt{BathOut}
-%                                                    are rank-1 dble array of dimension
-%                                                    \texttt{Nb=?get\_bath\_dimension}.
-%                                                    \texttt{Type=e, v, l}
-%                                                    is  a single
-%                                                    character.\\
-
-%   \hline
-%   ?spin\_symmetrize\_bath(Bath[,save])& Enforces spin symmetry in the bath
-%                                         \texttt{Bath}.
-%                                         Arguments: \texttt{Bath} is a rank-1 dble array
-%                                         of dimension
-%                                         \texttt{Nb=?get\_bath\_dimension}.
-%                                         For problems with \texttt{Nsites} inequivalent atoms
-%                                         \texttt{Bath} is a rank-2 dble array of 
-%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
-%                                         \texttt{save} is a logical
-%                                         value used to optionally write
-%                                         out the output bath.\\
-%   \hline
-%   ?orb\_symmetrize\_bath(Bath[,save])& Enforces symmetry among orbitals in the bath
-%                                    \texttt{Bath}.
-%                                    Arguments: \texttt{Bath} is a rank-1 dble array
-%                                         of dimension
-%                                         \texttt{Nb=?get\_bath\_dimension}.
-%                                         For problems with \texttt{Nsites} inequivalent atoms
-%                                         \texttt{Bath} is a rank-2 dble array of 
-%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
-%                                         \texttt{save} is a logical
-%                                         value used to optionally write
-%                                         out the output bath.\\
-%   \hline
-%   ?orb\_equality\_bath(Bath,Indx[,save])&
-%                                              Equals each orbital 
-%                                              components in the bath
-%                                              \texttt{Bath} to be
-%                                              identical to those of the
-%                                              orbital \texttt{Indx}.
-%                                               Arguments: \texttt{Bath} is a rank-1 dble array
-%                                              of dimension
-%                                              \texttt{Nb=?get\_bath\_dimension}.
-%                                              For problems with \texttt{Nsites} inequivalent atoms
-%                                              \texttt{Bath} is a rank-2 dble array of 
-%                                              dimensions
-%                                              [\texttt{Nsites},\texttt{Nb}].
-%                                              \texttt{Indx} is a
-%                                              integer constant. 
-%                                              \texttt{save} is a logical
-%                                              value used to optionally write
-%                                              out the output bath.\\
-%   \hline
-%   ?ph\_symmetrize\_bath(Bath[,save])& Enforces particle-hole symmetry
-%                                       in the bath \texttt{Bath}.
-%                                        Arguments: \texttt{Bath} is a rank-1 dble array
-%                                         of dimension
-%                                         \texttt{Nb=?get\_bath\_dimension}.
-%                                         For problems with \texttt{Nsites} inequivalent atoms
-%                                         \texttt{Bath} is a rank-2 dble array of 
-%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
-%                                         \texttt{save} is a logical
-%                                         value used to optionally write
-%                                         out the output bath.\\
-%   \hline
-%   ?ph\_trans\_bath(Bath[,save])& Perform a particle-hole transformation onto the
-%                           bath \texttt{Bath}.
-%                            Arguments: \texttt{Bath} is a rank-1 dble array
-%                                         of dimension
-%                                         \texttt{Nb=?get\_bath\_dimension}.
-%                                         For problems with \texttt{Nsites} inequivalent atoms
-%                                         \texttt{Bath} is a rank-2 dble array of 
-%                                         dimensions [\texttt{Nsites},\texttt{Nb}].
-%                                         \texttt{save} is a logical
-%                                         value used to optionally write
-%                                         out the output bath.\\
-%   \hline
-%   ?break\_symmetry\_bath(Bath,Field,Sign[,save]) &
-%                                                     Breaks spin
-%                                                     symmetry in the bath \texttt{Bath}
-%                                                    using a small field of
-%                                                    amplitude 
-%                                                    \texttt{Field} with sign
-%                                                    \texttt{Sign}. The
-%                                                    quantity
-%                                                    \texttt{Field*Sign}
-%                                                    is added or
-%                                                    subtracted,
-%                                                    respectively for spin
-%                                                    up and down, to the
-%                                                    local energies of each bath level.  
-%                                                    Arguments: \texttt{Bath} is a rank-1 dble array
-%                                                    of dimension
-%                                                    \texttt{Nb=?get\_bath\_dimension}.
-%                                                    For problems with \texttt{Nsites} inequivalent atoms
-%                                                    \texttt{Bath} is a rank-2 dble array of 
-%                                                    dimensions
-%                                                    [\texttt{Nsites},\texttt{Nb}].
-%                                                    \texttt{Field,
-%                                                    Sign} are dble
-%                                                    constant.                                                     
-%                                                    \texttt{save} is a logical
-%                                                    value used to optionally write
-%                                                    out the output bath.\\
-%   \hline
-
-%   \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf  BATH\_FIT}\\
-%   \hline
-%   \hline
-%   ?chi2\_fitgf(Func,Bath,Hloc,ispin[,iorb])   &  Optimizes the bath
-%                                                 \texttt{Bath}
-%                                                 according to the user-provided function
-%                                                 \texttt{Func}, using a  Conjugate
-%                                                 Gradient minimization
-%                                                 of the cost function
-%                                                 $\chi$, see
-%                                                 Sec.~\ref{SecBathFit}.
-%                                                 Argument: \texttt{Func}
-%                                                 is a rank-5 cmplx array
-%                                                 of dimensions 
-%                                                 [\texttt{Nspin,Nspin,Norb,Norb,:}].
-%                                                 For problems with
-%                                                 \texttt{Nsites}
-%                                                 inequivalent atoms
-%                                                 \texttt{Func} is a rank-6 cmplx array
-%                                                 of dimensions
-%                                                 [\texttt{Nsites,Nspin,Nspin,Norb,Norb,:}]. 
-%                                                 \texttt{Bath} is a rank-1 dble array
-%                                                 of dimension
-%                                                 \texttt{Nb=?get\_bath\_dimension}.
-%                                                 or  a rank-2 dble array of 
-%                                                 dimensions
-%                                                 [\texttt{Nsites},\texttt{Nb}].
-%                                                 \texttt{Hloc} is a rank-4 dble array of
-%                                                 dimensions [\texttt{Nspin,Nspin,Norb,Norb}] or
-%                                                 a rank-5 of dimensions
-%                                                 [\texttt{Nsites,Nspin,Nspin,Norb,Norb}].
-%                                                 \texttt{ispin} is an
-%                                                 int constant
-%                                                 indicating the spin
-%                                                 components to fit.
-%                                                 The optional argument
-%                                                 \texttt{iorb} indicate
-%                                                 the orbital components
-%                                                 to fit. If not passed
-%                                                 all orbitals are
-%                                                 fitted.  \\   
-%   \hline
-
-%    \hline
-%   \hline
-%   \multicolumn{2}{c}{\bf  AUX\_FUNX}\\
-%   \hline
-%   \hline
-%   ?set\_suffix(ilat,pads)   &  Sets an additional suffix for the
-%                               output files of the \NAME\ library.
-%                               Arguments: \texttt{ilat} is an integer
-%                               constant. \texttt{pads} is an integer
-%                               constant indicating the number of zero
-%                               padding of the integer \texttt{ilat} in
-%                               the suffix.\\
-%   \hline
-%   ?reset\_suffix()   &  Resets the suffix for the output
-%                                    files of \NAME\ to the default value \\
-%   \hline
-%   ?search\_variable(var,ntmp,bool)   &  Varies the variable
-%                                          \texttt{var} so that the
-%                                        conjugated variable
-%                                        \texttt{ntmp} is equal to the
-%                                        input value \texttt{nread} up
-%                                        to an error \texttt{nerr}.
-%                                        Arguments: \texttt{var, ntmp}
-%                                        are dble
-%                                        constants. \texttt{bool} is a
-%                                        logical constant indicating the success of the variation.\\
-%   \hline
-%   \label{TableProcedures}
-% \end{tabularx}
 

### 2025-03-21 edipack2.tex
Updated draft. Structure sketched

@@
 
-\section{Structure}\label{SecStruct}
-\subsection{EDIpack2}
-\subsection{EDIpack2ineq}
-\subsection{EDIpack2 C-bindings}
-\subsection{EDIpack2Triqs}
+% ##################################################################
+% ##################################################################
+% ##################################################################
+
+\section{Structure and derived software}\label{SecStruct}
+\NAME is a modular library which contains three principal structures.
+At the core is the exact diagonalization solver: \NAME.
+Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
+inequivalent impurity problems. Finally, there we provide a Fortran-C
+interface, which enables development of additional API or
+inter-operability with external libraries.
+
+\begin{itemize}
+\item{\bf EDIpack2.}
+This constitutes the  building block of the whole software. This part
+implement the  with the Lanczos-based solver for generic quantum
+impurity systems encoding different symmetries, i.e. quantum number
+conservations and apt to solve multi-orbital problems, also in
+presence of coupling to local phonons.  
+The \NAME solver has a hierarchical and modular structure: different
+sections of the library communicate through a shared memory layer. The
+top module of the library is {\tt EDIPACK2} which, once loaded,
+enables access to the Fortran API in terms of suitable procedures to
+initialize, execute and finalize the solver or to retrieve internal
+quantities while making opaque to the user the internal structure of
+the library. 
+A detailed presentation of the library can be found in
+Sec.\ref{SecEDIpack}.
+
+\item{\bf EDIpack2ineq.}
+This part of the software, leveraging on the object oriented concepts
+available in modern Fortran, aims to extend the \NAME library to the
+case of multiple inequivalent and independent impurity problems. This
+is particularly useful while using \NAME as a solver for DMFT in
+presence of unit cells with inequivalent atoms, for systems with
+somehow broken translational symmetry (e.g. heterostructures, large
+supercells, etc.).
+
+\item{\bf EDIpack2 C-bindings.}
+\NAME includes a single module implementing a Fortran-C interface of the main
+library procedures. The module is developed around the implicit {\tt
+  ISO\_C\_BINDING} capabilities of the most recent Fortran
+distributions, which enable to translate Fortran procedures directly
+to C. In order to overcome all the difficulties related to the internal
+structure of the library,  we interfaced all and just the
+procedures and the variables exposed to the user. 
+This module aims to foster interoperability of \NAME  with different
+third party softwares as well as to support development of additional
+API.
+
+% \subsection{Dependent software}
+% As a concrete example illustrating the interoperability of the
+% software we here illustrate the case of EDIpy2, i.e. the Python API for
+% \NAME and present an interface layer to Triqs (Toolbox
+% for Reasearch In Quantum Systems).
+
+\item{\bf EDIpy2.}
+This is a simple Python module which provides Python API to the
+\NAME Fortran library. This interface is built around the Python
+support to C-types, which allows to import the dynamic C-binding
+library generated upon building \NAME. The module contains a specific
+class, whose methods mirrors through  duck-typing all the available
+procedures of \NAME as well as it gives access to relevant shared
+control variables.
+
+\item{\bf EDIpack2Triqs.}
+This is a thin interface layer from \NAME to Triqs,
+built around the Python API of the \NAME library. The exact
+diagonalization solver is encapsulated in a dedicated class,
+containing the necessary methods to initialize and run a single
+instance of the solver. The interface also includes a specific class
+encompassing the effective discretized bath structure as well as their 
+optimization methods.
+
+\end{itemize}
+
+% ##################################################################
+% ##################################################################
+% ##################################################################
 
@@
 
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
+% ##################################################################
+% ##################################################################
+% ##################################################################
 
 \section{Implementation}\label{SecEDIpack}
+Here we present an overview of the implementation of the
+different parts of the \NAME library.
 
@@
 
-\subsection{Dynamical correlation functions}
+\subsection{Dynamical correlation functions}\label{sSecGF}
 
-\subsection{Observables}
+\subsection{Observables}\label{sSecObc}
 
-\subsection{Reduced impurity density matrix}
+\subsection{Reduced impurity density matrix}\label{sSecRDM}
 
-\subsection{Bath parametrization}
+\subsection{Bath parametrization}\label{sSecBath}
 
-\subsection{Bath Optimization}
+\subsection{Bath Optimization}\label{sSecFit}
 
-\subsection{Input/Output}
+\subsection{Input/Output}\label{sSecIO}
 
@@
 
+% ##################################################################
+% ##################################################################
+% ##################################################################
+
+\section{Usage}\label{SecUsage}
+\subsection{Bethe lattice DMFT (Fortran API)}
+\subsection{Attractive Hubbard model (Python API)}
+\subsection{Multi-orbital Hubbard (Triqs)}
+
+% ##################################################################
+% ##################################################################
+% ##################################################################
+
 \section{Conclusions}
+
+% ##################################################################
+% ##################################################################
+% ##################################################################
 

### 2025-03-27 edipack2.tex
Updated draft, up to Lanczos diagonalizaion. Let's speed up the writing huh...

@@
   fontadjust=true,
-  keywordstyle=\color{magenta},
+  keywordstyle=\color{red},
+  % morekeywords={*,...},
   mathescape,
@@
 }
+
+\lstdefinestyle{mybash}{
+  frame=lines,
+  language=bash,
+  basicstyle=\footnotesize,
+  captionpos=b,
+  stringstyle=\color{mymauve},%\ttfamily,
+  commentstyle=\itshape,
+  fontadjust=true,
+  keywordstyle=\bfseries,
+  morekeywords={*,git,mkdir,cmake,make},
+  mathescape,
+  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
+}
+
+% % MINTED:
+% % \usepackage[cache=true,cachedir=minted-cache]{minted}
+% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
+% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
+% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
+%   baselinestretch=1,fontsize=\footnotesize}
 
@@
 
-\title{EDIpack2: interoperable Lanczos-based exact diagonalization solver for
-  generic quantum impurity problems.}
-% \author[]{L.~Crippa}
-% \author[]{I.~Krivenko}
-% \author[]{S.~Giuli}
-% \author[]{G.~Bellomia}
-% \author[]{....}
-% % \author[]{A.~Scazzola}
-% % \author[]{F.~Petocchi}
-% % \author[]{G.~Mazza}
-% % \author[]{L.~de Medici}
-% % \author[]{M.~Capone}
-% \author[a]{A.~Amaricci\corref{author}}
+\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
+\author[a,b,c]{L.~Crippa\corref{AA}}
+\author[a]{I.~Krivenko}
+\author[d]{S.~Giuli\corref{BB}}
+\author[d]{G.~Bellomia\corref{CC}}
+\author[e]{A.~Scazzola}
+\author[f]{F.~Petocchi}
+\author[g]{G.~Mazza}
+\author[h]{L.~de Medici}
+\author[d]{M.~Capone}
+\author[i]{A.~Amaricci}
 
 % \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
+\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
+  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
+  Trieste, Italy}
+\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
+  Via Bonomea 265, 34136 Trieste, Italy}
+\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
+  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
+\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
+  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
+\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
+\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
+  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
+\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
+  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
+\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
 
-% \address[a]{CNR-IOM, Istituto Officina dei Materiali,
-%     Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136 Trieste, Italy}
+\address[a]{\ITPHamburg}
+\address[b]{\CTQMAT}
+\address[c]{\WZBURG}
+\address[d]{\SISSA}
+\address[e]{Torino}
+\address[f]{\Geneve}
+\address[g]{\UPISA}
+\address[h]{\ESPCI}
+\address[i]{\CNRIOM}
+\cortext[AA] {Corresponding author \textit{E-mail address:}
+  lorenzo.crippa@uni-hamburg.de}
+\cortext[BB] {Corresponding author \textit{E-mail address:}
+  giuli@sissa.it}
+\cortext[CC] {Corresponding author \textit{E-mail address:}
+  bellomia@sissa.it}
+
 \begin{abstract}
@@
 multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries: {\tt
-  libedipack.a} and {\tt libedipack\_cbinding.so}.
-The former, alongside the generated Fortan modules files,
-wraps the \NAME software. The latter enables interoperability through
-bindings to the C language.
+The software builds into two distinct libraries.
+The main one is {\tt  libedipack.a} which, alongside the generated Fortan
+modules, wraps the \NAME software possibly including support for  
+inequivalent impurities.
+A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
+specific bindings to the C programming language.
 
 \subsection{Dependencies}
-Although \NAME is as much self-contained as possible its development
-hinges on two external libraries.
+\NAME essentially depends on two external libraries.
 \begin{itemize}
@@
 be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 git clone https://github.com/edipack/EDIpack2.0 EDIpack2
@@
 This is the default CMake workflow:
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 mkdir build
@@
 multi-threaded building:
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 mkdir build
@@
 The Conda package installation procedure reads:
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 conda create -n edipack
@@
 
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 git clone https://github.com/edipack/EDIpy2 EDIpy2
@@
 
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 conda create -n edipack
@@
 
-\begin{lstlisting}[language=Bash]
+\begin{lstlisting}[style=mybash]
 git clone https://github.com/krivenko/edipack2triqs
@@
 
+% $H_{e-ph}= \sum_{\a\sigma} g_\a
+% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
+
 \section{Implementation}\label{SecEDIpack}
@@
 \subsection{The quantum impurity problem}\label{sSecQIM}
+We consider a general quantum impurity problem defined by the
+following Hamiltonian:
+$$
+\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
+$$
+which describes a  multi-orbital interacting quantum
+impurity coupled to an electronic bath and to local, i.e. Holstein,
+phonons. We assuming for the moment that no particular symmetry
+holds. The impurity part of the Hamiltonian reads: 
+\begin{equation}\label{Himp}
+  \begin{split}
+    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
+    \hat{H}^0_{imp} & =
+    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
+    %
+    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
+    &{\phantom =}- J_X\sum_{\a\neq
+      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
+      \neq
+      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
+    % 
+\end{split}
+\end{equation}
 
-\subsection{The  basis states}\label{sSecBasis}
+where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
+second-quantization operators for impurity electrons in the
+orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
+with spin $\sigma=\up,\dw$ and whose occupation is described
+by the  operator  
+$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
+The non-interacting internal structure of the impurity is described by
+the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
+$\hat{H}^{int}$ describes the  local multi-orbital
+interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
+generalized Hubbard-Kanamori form.  
+The first three terms represent the density-density part of the
+interaction, where $U$ is the local intra-orbital Coulomb repulsion,
+$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
+The  remaining two terms are, respectively, the spin-exchange and
+pair-hopping which we considered with their respective independent
+couplings $J_X$ and $J_P$.
+In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
+U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
+$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
+of the combined symmetry group, can be made for other values of
+$N_\a$~\cite{Georges2013ACMP}.
+
+The bath part and its coupling to the impurity has the form: 
+\begin{equation}\label{Hbath}
+  \begin{split}
+    \hat{H}_{bath} &=
+    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
+    %
+    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
+\end{split}
+\end{equation}
+where $p=1,\dots,N_{bath}$ is an index running over a finite number of
+bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
+the bath electrons with index $p$, with orbital $\alpha$ and
+spin $\sigma$.
+The  properties of each bath level are described by the
+matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
+composed of several electronic levels according the bath topology,
+which will be discussed further in the following.
+Each bath level couples to the impurity with an amplitude
+$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
+opposite spins.
+
+Finally, the electron-phonon part of the quantum impurity problems is
+described by the Hamiltonian terms: 
+\begin{equation}\label{Hph}
+  \begin{split}
+    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
+    % 
+    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
+\end{split}
+\end{equation}
+where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
+($b_q^+$) are the destruction (creation) operators for the phonon $q$
+with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
+Although feasible, dealing with more than one phonon mode becomes
+quickly computationally very demanding, thus in the rest of the this
+work we shall consider $N_q=1$.
+
+In the following we consider a bath discretized into a  number
+of bath degrees of freedom and a finite number of available phonons,
+to cut-off the unbounded dimensions of the local phonons Hilbert space.
+
+More specifically, we consider a system composed of $N_{imp}=1$
+impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
+and $N_{ph}$ phonons. The size of the system is determined by
+the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
+electronic Hilbert space
+$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
+Due to is internal structure, the single impurity contains
+$N_i= N_\a$ electronic levels.
+The total number of levels is then determined by
+the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
+i.e. the number of bath elements. In the simplest case each bath
+element corresponds to an independent electronic levels coupled to the
+impurity, thus $N_b\equiv N_{bath}$. 
+We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
+
+\subsection{The Fock basis states}\label{sSecBasis}
+The Fock space of the quantum impurity problems is defined as
+$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
+S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
+phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
+and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
+The total dimension of the Fock space is
+$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
+growth with the number of electron levels transparent. 
+The quantum states in the space $\FF$ are naturally represented in
+terms of occupation number formalism of the second quantization,
+i.e. the Fock basis. For a system of $N_s$ electrons each Fock state
+reads $\ket{p}\ket{\vec{n}}$ with $\ket{\vec{n}}=\ket{\vec{n}_\up}\ket{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}$, 
+where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
+presence of an electron with spin $\sigma$ at the level $a$.
+Remarkably, the electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
+zeros and ones of length $2N_s$. Thus, any such state can  be encoded
+in a computer using a sequence of $2N_s$ bits or, analogously, as a
+given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
+Together with the basis states one defines  destruction and creation 
+operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
+Fock space as: 
+$\ket{\vec{n}}$ as:  
+\begin{align*}
+  c_{a\sigma}\ket{\vec{n}} &=
+    \begin{cases}
+      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
+      &\text{if $n_{a\sigma}\!=\! 1$}\\
+      0 &\text{otherwise}
+    \end{cases};\qquad
+    c^{+}_{a\sigma}\ket{\vec{n}} &=
+     \begin{cases}
+      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
+      & \text{if $n_{a\sigma}\!=\! 0$}\\
+      0 & \text{otherwise}
+    \end{cases}    
+\end{align*}
+where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
+of the fermionic sign imposed by Pauli principle.
 
 \subsection{Conserved quantum numbers}\label{sSecQNs}
+In order to circumvent the exponential scaling of the dimensions of
+the problem scales it is necessary to take into account suitable symmetries.
+Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
+reduces of the Fock space into several symmetry sectors
+labelled by given quantum numbers $\vec{Q}$. 
+In the context of quantum impurity problems two symmetries are often considered: i)
+conservation of the total occupation $N$ and ii) the
+conservation of the total magnetization $S_z$. Although the total spin
+operator $S^2$ can also be conserved, the difficult  implementation
+and the marginal gain makes it often non convenient to include this symmetry.
+
+In \NAME we consider three different cases:
+\begin{itemize}
+\item{\bf normal:}  $\vec{Q}=[N,S_z]\equiv[N_\up,N_\dw]$
+\item{\bf superc:}  $\vec{Q}=S_z$
+\item{\bf nonsu2:} $\vec{Q}=N$
+\end{itemize}
+
+The {\bf normal} case consider independent conservation of the total occupation $N$
+and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
+$N_\dw$. Optionally, we consider the case in which the symmetry
+applies separately for each orbital and spin,
+i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
+extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
+this work.
+
+The {\bf superc} case deals with the conservation of the total
+magnetization only, so that total charge may not be conserved. This
+case includes a description of $s$-wave superconductivity, featuring
+intra- and inter-orbital components.
+
+Finally, the {\bf nonsu2} case consider the conservation of the total
+charge, whereas the spin symmetry group is not fully
+conserved. Although there many possible realization of this scenario,
+this particularly applies to the presence of local spin-orbit coupling
+$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
+in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.
+
+From a computational point of view the construction of a symmetry
+sector corresponds to the determination of a injective map
+$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
+belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
+Fock space. Operatively, the map corresponds to an integer rank-1
+array of dimension $D_\SS$ which is the {\it dimension} of the
+sector. According to the previously introduced symmetries we
+have:
+\begin{itemize}
+\item{\bf normal:}  $D_\SS = \binom{N_s}{N_\up}\binom{N_s}{N_\dw}$ 
+\item{\bf superc:}  $D_\SS = \sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
+\item{\bf nonsu2:} $D_\SS=\binom{2N_s}{N}$
+\end{itemize}
+
+The {\bf normal} case requires a brief remark. Because of the
+independent conservation of $N_\up$ and $N_\dw$, the sector can be further factorized into $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
+\SS_{N_\dw}$ and, correspondingly, the sector map reads $\MM = \MM_\up
+\otimes \MM_\dw$.
+As such, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
+sector is labelled by two integers $[i_\up,i_\dw]$, 
+$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
+D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
+$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
+$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
+discussion about Fock basis organization in this case see
+\onlinecite{amaricci2022}.
+
+The symmetry sector reduction of the Fock space induces a block
+digonal form to the Hamiltonian matrix. Each block, labelled by a
+value of the quantum numbers $\vec{Q}$ has dimension
+$D_{\SS(\vec{Q}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
+  normal} case $H_\SS$ takes a particularly symmetric form thanks to
+the product structure of the sector and its map~\cite{amaricci2022}.
+The analysis of the spectrum is then reconducted to the inspection of
+the Hamiltonian in each symmetry sector. Should particular constraint
+holds the search can be limited to only particular sector, further
+reducing the computational cost.
+
+Although the sectors have dimensions much smaller than the full Fock
+space, for large systems storing the Hamiltonian matrix in the memory
+can still be highly inefficient.
+In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
+be implemented using a storage-free algorithm, performing the
+necessary linear operations on-the-fly.
+This solution has generally a negative impact on the execution
+time, however this can be well compensated by scaling in a distributed 
+parallel framework.
 

### 2025-03-28 edipack2.tex
updated draft

@@
 
+\usepackage{stackengine}
+\newlength\llength
+\llength=1.38ex\relax
 \usepackage{xcolor}
@@
 \title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a,b,c]{L.~Crippa\corref{AA}}
+\author[a,b,c]{L.~Crippa}
 \author[a]{I.~Krivenko}
-\author[d]{S.~Giuli\corref{BB}}
-\author[d]{G.~Bellomia\corref{CC}}
+\author[d]{S.~Giuli}
+\author[d]{G.~Bellomia}
 \author[e]{A.~Scazzola}
@@
 \address[d]{\SISSA}
-\address[e]{Torino}
+\address[e]{Politecnico di Torino, Turin, Italy}
 \address[f]{\Geneve}
@@
 \address[i]{\CNRIOM}
-\cortext[AA] {Corresponding author \textit{E-mail address:}
-  lorenzo.crippa@uni-hamburg.de}
-\cortext[BB] {Corresponding author \textit{E-mail address:}
-  giuli@sissa.it}
-\cortext[CC] {Corresponding author \textit{E-mail address:}
-  bellomia@sissa.it}
+% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
+\cortext[BB] {Corresponding author:giuli@sissa.it}
+\cortext[CC]{Corresponding author:bellomia@sissa.it}
 
@@
 \end{small}
+
+\tableofcontents
 
@@
 
+The setup of the general quantum impurity problem is implemented in
+different parts of the \NAME software. The dimensions of the system
+are controlled by input variables {\tt Nspin}$=N_\sigma$,
+{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
+  ED\_INPUT\_VARS}. These are used to
+determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
+memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
+in {\tt ED\_SETUP}. 
+The user can define the local non-interacting Hamiltonian
+$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
+The matrix is then stored in the internal memory and shared throughout the
+code.
+On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
+requires a more involved procedure which will be illustrated in
+\secu{sSecBath}.
+
 \subsection{The Fock basis states}\label{sSecBasis}
@@
 terms of occupation number formalism of the second quantization,
-i.e. the Fock basis. For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with $\ket{\vec{n}}=\ket{\vec{n}_\up}\ket{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}$, 
+i.e. the Fock basis.
+For a system of $N_s$ electrons each Fock state
+reads $\ket{p}\ket{\vec{n}}$ with
+$$
+\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
+$$ 
 where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
 presence of an electron with spin $\sigma$ at the level $a$.
-Remarkably, the electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
+The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
 zeros and ones of length $2N_s$. Thus, any such state can  be encoded
@@
 of the fermionic sign imposed by Pauli principle.
+
+The Fock states and operators implementation can be found in {\tt
+  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
+and annihilation operators {\tt CDG} and {\tt C}, the binary
+decomposition {\tt bdecomp} required to reconstruct the Fock state as
+bits sequence and other accessory functions.
 
@@
 The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the sector can be further factorized into $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map reads $\MM = \MM_\up
+independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
+space and the electronic Fock can be factorizes as, respectively,
+$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
+Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
+\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
+mutually exclusive ones $\MM = \MM_\up
 \otimes \MM_\dw$.
-As such, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
+Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
 sector is labelled by two integers $[i_\up,i_\dw]$, 
@@
 
-\subsection{Krylov based Diagonalization}\label{sSecHam}
+The object {\tt sector}, defined globally in {\tt
+  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
+symmetry sector, its dimensions, its quantum numbers and an
+implementation of the map $\MM$. The constructor/destructor are defined {\tt
+  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
+  delete\_sector} using different algorithms according to the nature
+of the quantum numbers $\vec{Q}$ as reported in the following code
+snippet.
+\setbox0=\hbox{%
+  \begin{minipage}{0.3\linewidth}
+    \center{\bf normal}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+i=0
+do Iup=0,2**Nbit-1     
+  nup_ = popcnt(Iup) 
+  if(nup_ /= Nups(1))cycle
+  i = i+1
+  H(iud)%map(i) = lup
+enddo
+i=0
+do Idw=0,2**Nbit-1
+  ndw_= popcnt(Idw)
+  if(ndw_ /= Ndws(1))cycle
+  i = i+1
+  H(iud+Ns)%map(i) = Idw
+enddo
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingA}{\box0}
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.3\linewidth}
+    \center{\bf superc}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+i=0
+do Idw=0,2**Ns-1
+  ndw_= popcnt(idw)
+  do Iup=0,2**Ns-1
+    nup_ = popcnt(iup)
+    sz_  = nup_ - ndw_
+    if(sz_ /= self%Sz)cycle
+    i=i+1
+    self%H(1)%map(i) = &
+        Iup+Idw*2**N
+  enddo
+enddo
+
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingB}{\box0}
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.3\linewidth}
+    \center{\bf nonsu2}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+i=0
+do Idw=0,2**Ns-1
+  ndw_= popcnt(Idw)
+  do Iup=0,2**Ns-1
+    nup_ = popcnt(Iup)
+    nt_  = nup_ + ndw_
+    if(nt_ /= self%Ntot)cycle
+    i=i+1
+    self%H(1)%map(i) = &
+        Iup+Idw*2**Ns
+  enddo
+enddo
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingC}{\box0}
+
+\begin{tabular}{c|c|c}\label{list1}
+  \stackinset{l}{}{t}{}{}{\listingA} &
+\stackinset{l}{}{t}{}{}{\listingB} &
+\stackinset{l}{}{t}{}{}{\listingC} \\
+\end{tabular}
+%
+Alongside these definitions, this module additional functions to
+retrieve sector index or quantum number informations. Another set of
+key functions concern the application of arbitrary linear combinations
+of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
+$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
+$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
+the sector informations are implemented
+in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
+apply\_Cops} functions within {\tt ED\_SECTORS}.
+
+\subsection{Classes}
+The use of suitable objects enormously simplifies the  implementation
+of crucial mathematical concepts aking to the diagonalization of the
+quantum impurity problems. Here we discuss three main classes which
+are used in the code.    
+{\color{red} Text to be revised}
+
+\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
+A sparse matrix storage is performed using a
+dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
+The class defines a \texttt{sparse\_matrix\_csr} object as a 
+simplified hash-table. The keys corresponds to the rows of the matrix
+while the value is associated to a pair dynamical arrays, containing values and
+columns location of the non-zero elements of the sparse matrix.
+The \texttt{sparse\_matrix\_csr} object can be stored either serially,
+i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
+process.
+The elements are progressively stored in the dynamic arrays using
+\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
+\texttt{move\_alloc}.
+This ensures a faster execution compared to implicit  
+reallocation, i.e. \texttt{vec=[vec,new\_element]}.
+This solution enables to deal with the a priori unknown number of
+non-zero elements on each row, to optimize the memory footprint and
+to guarantee $O(1)$ access  to any element of the matrix, which are
+crucial aspect to speed-up the execution of the MVP.
+
+\subsubsection{Eigenspace}\label{CodeEigenspace}
+This class, contained in \texttt{ED\_EIGENSPACE} implements a
+dedicated storage for the eigenvalues and eigenvectors of the quantum impurity Hamiltonian
+The class defines the object \texttt{sparse\_espace}, an  
+ordered linked list storing the eigenvalue (the sorting key), the
+eigenvector and the corresponding QNs. To save memory the eigenvectors
+are automatically distributed to all processors in shares of the right
+size according to the nature of the quantum numbers $\vec{Q}$.
+
+For zero temperature calculations only the groundstates (with degeneracies) are stored
+in the list.
+For a finite temperature the excited states need to be stored too.
+In order to avoid unbounded growth of the list we adopt an 
+truncation mechanism. In the first call we collect a number 
+\texttt{lanc\_nstates\_sector} of states from each sector, up to a
+given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
+The list is truncated by keeping the states which
+fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
+$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
+groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
+is an input parameter fixing an a priori energy threshold.
+%  
+Annealing is achieved by successive diagonalization of the problem.
+The numbers of states required to any sector $\SS$ contributing to the list is increased by
+\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
+(of the order of ten) the distribution among the sectors of the
+numbers of states reaches a steady state.
+The corresponding annealed list contains all and just the states
+contributing to the spectrum up to the required energy threshold.
+A histogram of the number of states for each sector is produced after
+each diagonalization to check the evolution of their distribution.
+
+\subsubsection{GFmatrix}
+One of the main goal of the code is to evaluate dynamical correlations
+functions $\ibra \TT_\pm[ A(t)
+A^+ ]\iket$. As we shall see in the following, using Krylov method it is
+possible to express the dynamical correlations in terms of a suitably
+truncated Kallen-Lehmann spectral sum of the form
+$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
+  - dE_{mn}}\equiv $ where $w_{mn}$ is a weight set by the 
+projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
+component of the Krylov basis (which reduce the sector Hamiltonian
+into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
+The {\tt ED\_GFMATRIX} module contains a class efficiently storing all
+the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
+a specific dynamical correlation functions. Specifically, the {\tt
+  gfmatrix} object implements a dynamical multi-layer data structure
+gatering weights and poles from any initial state and for any
+combination of operators contributing to the dynamical correlation
+function.
+
+The use of this class enables the istantan
+
+  \subsection{Lanczos based Diagonalization}\label{sSecHam}
 

### 2025-03-29 edipack2.tex
Updated draft. Up to Bath parametrization. Still a lot to write ....

@@
 and the marginal gain makes it often non convenient to include this symmetry.
-
-In \NAME we consider three different cases:
-\begin{itemize}
-\item{\bf normal:}  $\vec{Q}=[N,S_z]\equiv[N_\up,N_\dw]$
-\item{\bf superc:}  $\vec{Q}=S_z$
-\item{\bf nonsu2:} $\vec{Q}=N$
-\end{itemize}
-
-The {\bf normal} case consider independent conservation of the total occupation $N$
+In \NAME we consider three different cases which are controlled by the
+input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
+  nonsu2}.
+
+The {\bf normal} case deals with independent conservation of the total occupation $N$
 and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
@@
 this work.
-
+%
 The {\bf superc} case deals with the conservation of the total
@@
 intra- and inter-orbital components.
-
+%
 Finally, the {\bf nonsu2} case consider the conservation of the total
@@
 in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-
+%
 From a computational point of view the construction of a symmetry
@@
 array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. According to the previously introduced symmetries we
-have:
-\begin{itemize}
-\item{\bf normal:}  $D_\SS = \binom{N_s}{N_\up}\binom{N_s}{N_\dw}$ 
-\item{\bf superc:}  $D_\SS = \sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-\item{\bf nonsu2:} $D_\SS=\binom{2N_s}{N}$
-\end{itemize}
+sector. 
+The table~\ref{TabSector} summarizes the properties of the symmetry
+sectors.
+
+\begin{table}%[ht]
+  \label{TabSector}
+\begin{center}
+\begin{tabularx}{\linewidth}{ |X|X|X| } 
+ \hline
+  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
+  \hline
+  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
+                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
+  \\
+  \hline
+  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
+  \\
+  \hline
+  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
+ \hline
+\end{tabularx}
+\end{center}
+\caption{Ciao}
+\end{table}
 
@@
 
-The symmetry sector reduction of the Fock space induces a block
-digonal form to the Hamiltonian matrix. Each block, labelled by a
-value of the quantum numbers $\vec{Q}$ has dimension
-$D_{\SS(\vec{Q}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+The presence of a symmetry induces a factorization of the Fock space,
+in turn inducing a block diagonal form to the Hamiltonian matrix.
+Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
+$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
 basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
@@
 One of the main goal of the code is to evaluate dynamical correlations
-functions $\ibra \TT_\pm[ A(t)
-A^+ ]\iket$. As we shall see in the following, using Krylov method it is
+functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
 possible to express the dynamical correlations in terms of a suitably
@@
 $\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}\equiv $ where $w_{mn}$ is a weight set by the 
+  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
 projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
@@
 into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class efficiently storing all
+The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
 the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific dynamical correlation functions. Specifically, the {\tt
+a specific correlation function. Specifically, the {\tt
   gfmatrix} object implements a dynamical multi-layer data structure
-gatering weights and poles from any initial state and for any
-combination of operators contributing to the dynamical correlation
-function.
-
-The use of this class enables the istantan
+storing any DCF as the set of all the weights and poles,
+from any contributing eigenstate  and for any
+combination of operators appearing in its definition.
+The use of this class enables the istantantaneous evaluation of a
+given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
+using a suitable compressed form.
+
+\subsection{Bath parametrization}\label{sSecBath}
+The bath parametrization is a key feature in determining the properties
+of the quantum impurity problem.
+Following the structure of Eq.~\ref{Hbath} the bath can be
+parametrized by two terms: the Hamiltonian matrices $h^p$ and the
+amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
+Internally, the bath is represented by a dedicated object {\tt
+  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
+On the
+user side all parameters are packed into a rank-1 array of
+doubles handled using reverse communication strategy.
+This ensures that a local array is always conserved by the user, while
+it prevents direct access to the internal copy.
+
+The bath topology, i.e. the links between the $N_b$ electronic levels
+assigned to the bath, is determined by the input variable {\tt
+  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
+{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
+%
+\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
+electronic levels coupled to each of the impurity orbital. The total
+count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
+matrices include a parametrization diagonal in the orbital and spin space: 
+$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
+If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
+amplitudes connecting bath levels with opposite spins. So we consider
+an additional set of parameters, diagonal in orbital space but
+off-diagonal in the spins:
+$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
+This choice corresponds to consider, for every orbital component,
+bath matrices with the following structure in the Nambu space:
+$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
+\Delta_{\a}\delta_{\a\b}\tau_x$. 
+The hybridization amplitudes between the impurity and the bath levels
+include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
+spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
+If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
+describing spin-flip processes (as total magnetization is not
+conserved) should be included $V^p_{\a\b\s\s'} =
+W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
+
+\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
+$N_{bath}$ coupled to all the impurity levels, correspondingly
+$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
+The main parametrization of the bath Hamiltonian matrices is still
+diagonal in both orbital and spin space, i.e.
+$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
+As for the previous case, the {\bf superc} mode requires the inclusion
+of a further set of parameters taking care of the anomalous components:
+$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
+  \overline{\s}}$.
+The key difference with respect to the {\bf normal} case lies in the
+off-diagonal nature of the hybridization amplitudes:
+$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
+is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
+set of parameters should be included to describe spin-flip processes:
+$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
+These sets of hybridization parameters allow to capture the effects of locally
+hybridized impurity orbitals. This comes at the cost of a
+slightly harder optimization process (see \secu{sSecFit}) specially
+for systems with reduced number of available bath levels with respect
+to the impurity.
+
+\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
+parametrization of the bath is represented by this topology. The
+original idea of this approach is to give to each bath element a structure which {\it replicates}
+that of the impurity while keeping a diagonal coupling between bath
+elements and impurity. This offloads the difficulties related to the
+representation and optimization of strucured quantum impurities to the
+bath Hamiltonan rather than the hybridizations.
+Taking a sligthly more general point of view we consider a user
+defined matrix basis $\{ \Gamma^\nu \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
+space and parametrize any bath Hamiltonian as:
+$$
+h^p_{\a\b\s\s'} = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu \Gamma^\nu_{\a\b\s\s'}
+$$
+where $\lambda^p_\nu\in\RRR$ are suitable variational parameters. 
+The choice of the matrix basis can be inspired either by the internal structure
+of the quantum impurity, i.e. $\hat{h}^0$, or be determined
+case-by-case by the properties of the problem.
+The total number of electronic levels used to describe the bath is in
+this case: $N_b = N_{sym} N_{bath}$. 
+For the {\bf replica}  topology the coupling between the impurity and
+each bath elements is diagonal in the spin, orbital and internal bath
+structure: $V^p_{\a\b\s\s'} = V^p$. The
+{\bf general} setup introduces a generalization introducing a
+dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
+= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
+
+All the procedures concerning the bath are grouped into a set of
+modules wrapped by {\tt ED\_BATH}.
+
+* get dimension
+
+* replica/general bath setup
 
@@
 
-\subsection{Bath parametrization}\label{sSecBath}
+\subsection{Bath Functions}\label{sSecFunc}
 

### 2025-04-02 edipack2.tex
Updated draft.

@@
 \usepackage{xcolor}
+\usepackage{makecell}
 
@@
 \title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a,b,c]{L.~Crippa}
+\author[a]{L.~Crippa}
 \author[a]{I.~Krivenko}
-\author[d]{S.~Giuli}
-\author[d]{G.~Bellomia}
-\author[e]{A.~Scazzola}
-\author[f]{F.~Petocchi}
-\author[g]{G.~Mazza}
-\author[h]{L.~de Medici}
-\author[d]{M.~Capone}
-\author[i]{A.~Amaricci}
+\author[b]{S.~Giuli}
+\author[b]{G.~Bellomia}
+% \author[c]{A.~Scazzola}
+\author[d]{F.~Petocchi}
+\author[e]{G.~Mazza}
+% \author[f]{L.~de Medici}
+\author[b]{M.~Capone}
+\author[g]{A.~Amaricci}
 
@@
 \address[a]{\ITPHamburg}
-\address[b]{\CTQMAT}
-\address[c]{\WZBURG}
-\address[d]{\SISSA}
-\address[e]{Politecnico di Torino, Turin, Italy}
-\address[f]{\Geneve}
-\address[g]{\UPISA}
-\address[h]{\ESPCI}
-\address[i]{\CNRIOM}
+% \address[b]{\CTQMAT}
+% \address[c]{\WZBURG}
+\address[b]{\SISSA}
+\address[c]{Politecnico di Torino, Turin, Italy}
+\address[d]{\Geneve}
+\address[e]{\UPISA}
+\address[f]{\ESPCI}
+\address[g]{\CNRIOM}
 % \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-\cortext[BB] {Corresponding author:giuli@sissa.it}
-\cortext[CC]{Corresponding author:bellomia@sissa.it}
+% \cortext[BB] {Corresponding author:giuli@sissa.it}
+% \cortext[CC]{Corresponding author:bellomia@sissa.it}
 
@@
 work we shall consider $N_q=1$. 
-
 In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons,
+of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
 to cut-off the unbounded dimensions of the local phonons Hilbert space.
+
+\paragraph{{\bf Remark}} As extensively discussed in
+\onlinecite{amaricci2022}, the inclusion of local phonons with
+truncated dimensions ultimately amounts to a sequential application of
+the procedures defined for the electronic part, i.e. one per phonon
+mode. This includes a linear scaling of the dimensions with $N_{ph}$
+and of course largely limit the available degrees of freedom to
+describe electronic states. In the rest of the paper we focus
+specifically on the electronic part of the quantum impurity problem,
+referring to the phonons in specific sections when their presence
+introduces non-trivial modifications.
 
@@
 are used in the code.
-{\color{red} Text to be revised}
 
@@
 
+\subsubsection{Sparse map}\label{CodeSparseMap}
+As it will be evident in the following \secu{sSecRDM}, there are cases in
+which the sector construction requires to store, for any sector state,
+disjoint information about the corresponding Fock state.
+Let's consider a Fock state $\ket{I}$. Its bit decomposition
+$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
+for instance to impurity and bath degrees of freedom as 
+$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
+The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
+  sparse\_map}, which is included as an element in the {\tt sector} object and  
+which stores  for every impurity configurations $\vec{i}_\s$ (key) the
+bath states $\vec{b}_\s$ (values) corresponding to it.
+The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
+  build\_sector} for any value of {\tt ed\_mode} using different
+algorithms.
+In the {\bf normal} case, the sector object contains two {\tt
+  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
+spin dependent factorization of the Fock and sector states: 
+$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
+\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
+The sparse maps are build as follows. 
+For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
+the key is determined by the integer $I_\s$ corresponding to the
+impurity bit set $\vec{i}_\s$. The values are given by any 
+integer $B_\s$ corresponding to any bath bit set
+$\vec{b_\s}$ associated with $\vec{i}_\s$.
+Thus, any given combination of key-value
+reconstructs an integer $J_\s$ representing the Fock states in the
+given spin sector according to the rule $J_s = I_\s +
+2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
+
+In the {\bf superc/nonsu2} case the construction of the unique sparse
+map is similar. For any Fock state $\ket{J}$ corresponding to sector
+state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
+B_\dw$ corresponding, respectively, to the bit sets
+$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
+state. These integers fulfill the relation
+$
+J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
+$
+To obtain a contiguous memory pattern we define as a key of the sparse
+map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
+  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
+  bit sets and Fock state can be reconstructed with simple algebra at
+  no additional cost.
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.5\linewidth}
+    \center{\bf normal}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+i=0
+do Iup=0,2**Nbit-1     
+  nup_ = popcnt(Iup) 
+  if(nup_ /= Nups(1))cycle
+  i=i+1 
+  !...
+  iImp  = ibits(iup,0,Norb)
+  iBath = ibits(iup,Norb,Norb*Nbath)
+  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
+enddo
+i=0
+do Idw=0,2**Nbit-1
+  ndw_= popcnt(Idw)
+  if(ndw_ /= Ndws(1))cycle
+  i=i+1 
+  !...
+  iIMP  = ibits(idw,0,Norb)
+  iBATH = ibits(idw,Norb,Norb*Nbath)
+  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
+enddo
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingA}{\box0}
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.5\linewidth}
+    \center{\bf superc/nonsu2}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+i=0
+do Idw=0,2**Ns-1
+  ndw_= popcnt(idw)
+  do Iup=0,2**Ns-1
+    nup_ = popcnt(iup)
+    !superc 
+    sz_  = nup_ - ndw_
+    if(sz_ /= self%Sz)cycle
+    !nonsu2 
+    !nt_  = nup_ + ndw_
+    !if(nt_ /= self%Ntot)cycle 
+    i=i+1 
+    !...
+    iImpUp  = ibits(iup,0,Norb)
+    iImpDw  = ibits(idw,0,Norb)
+    iBathUp = ibits(iup,Norb,Norb*Nbath)
+    iBathDw = ibits(idw,Norb,Norb*Nbath)
+    iImp    = iImpUp  + iImpDw*(2**Norb)
+    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
+    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
+  enddo
+enddo
+
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingB}{\box0}
+
+\begin{tabular}{c|c}\label{list2}
+  \stackinset{l}{}{t}{}{}{\listingA} &
+\stackinset{l}{}{t}{}{}{\listingB} 
+\end{tabular}
+%
+
 \subsubsection{Eigenspace}\label{CodeEigenspace}
-This class, contained in \texttt{ED\_EIGENSPACE} implements a
-dedicated storage for the eigenvalues and eigenvectors of the quantum impurity Hamiltonian
-The class defines the object \texttt{sparse\_espace}, an  
+The module \texttt{ED\_EIGENSPACE} implements a list
+storing for the eigenvalues and eigenvectors of the quantum impurity
+Hamiltonian. 
+This class defines the object \texttt{sparse\_espace}, an  
 ordered linked list storing the eigenvalue (the sorting key), the
@@
 Taking a sligthly more general point of view we consider a user
-defined matrix basis $\{ \Gamma^\nu \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
+defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
 space and parametrize any bath Hamiltonian as:
 $$
-h^p_{\a\b\s\s'} = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu \Gamma^\nu_{\a\b\s\s'}
-$$
-where $\lambda^p_\nu\in\RRR$ are suitable variational parameters. 
+h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
+\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
+$$
+where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
 The choice of the matrix basis can be inspired either by the internal structure
@@
 
-All the procedures concerning the bath are grouped into a set of
-modules wrapped by {\tt ED\_BATH}.
-
-* get dimension
-
-* replica/general bath setup
+All the procedures concerning the bath, either on the user side or the
+internal {\tt effective\_bath}, are grouped into a set of modules
+wrapped by {\tt ED\_BATH}.
+We divided the set of modules in three categories, according to their
+scope.
+\paragraph{Bath Auxiliary Tools}
+This part contains some functions directed to the user as, for
+istance, the implementation of suitable conventional symmetry
+operations acting on the user bath array like, e.g., orbital symmetry,
+particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
+However, the key functions of this group concerns the determination
+of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
+Starting from the values
+of some input variables the function {\tt ed\_get\_bath\_dimension}
+returns the dimension $B$ to which the  user should allocate the bath
+array to contains all and just the bath parameters. Any following call
+to functions hosting the bath as an input will check that the user supplied
+bath array has the correct dimensions compared to the value of $B$
+using {\tt check\_bath\_dimension}.
+
+\paragraph{Bath Replica (General)}
+The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
+for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
+conventional operations of object construction, destructin, reading
+and saving the module includes the matrix basis $\{ \Gamma^\nu
+\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
+$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
+  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
+\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
+  build\_Hgeneral}).
+
+\paragraph{Effective Bath}
+The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
+  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
+data structure contains and handles all the actual parameters of the
+bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
+referencing the class {\tt Hreplica} only for the {\bf
+  replica/general} bath topology.
+A global instance of the class {\tt dmft\_bath}  containing the
+current bath parameters is shared throughout the code.   
+The class constructor is supplemented with a specific procedure initializing
+the effective bath {\tt init\_dmft\_bath} which guess the bath
+parameters or read them from a file specified by the input variable {\tt
+  Hfile}.
+The class also contains procedures to transform the instance
+{\tt dmft\_bath} to/from the user bath array: {\tt
+  get/set\_dmft\_bath}.
+
+% \begin{table}%[ht]
+%   \label{TabBath}
+% \begin{center}
+% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
+%   \hline
+%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
+%   \hline
+%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
+%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
+%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
+%   \hline
+%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
+%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
+%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
+%   \hline
+%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
+%   \hline
+%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
+%   \hline
+% \end{tabularx}
+% \end{center}
+% \caption{Ciao}
+% \end{table}
 
 \subsection{Lanczos based Diagonalization}\label{sSecHam}
+In presence of symmetries (see \secu{sSecQNs}) the matrix representing
+the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
+contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
+given symmetry sector with quantum number $\vec{Q}$.
+The analysis of the energy spectrum of the quantum impurity problems
+thus reduces to the sequential solution of the sector secular problem
+$$
+H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
+$$
+
+Although the dimension of any such sector $\SS$ are much smaller than the
+total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
+the related eigenvalue problem represents an unsurmountable problem
+already with $N_s\simeq 8$. 
+In order to outwit this issue a number of
+algorithms have been developed leveraging on the sparse nature of
+$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
+In \NAME the alghoritm of choice is P-ARPACK, which represents the
+state-of-the-art Lanczos-based eigensolver with distributed memory
+support~\cite{P-Arpack}. This method includes re-orthogonalization
+within a block Lanczos algorithm which ensures convergence of the
+requred eigenpairs. Using the input variable {\tt lanc\_method} it is
+however possible to select a simple, but not as efficient, parallel
+Lanczos algorithm.
+The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
+(MVP), i.e. the application of the Hamiltonian to a given input
+vector:
+$$
+H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
+$$
+
+This operations easily takes over more than 80\% of the computation
+time, so its optimization is a crucial aspect in any diagonalization
+algorithms. In \onlinecite{amaricci2022} we covered in full details
+some distrubuted memory massively parallel algorithms to address this
+specific issue.
+Here, using the same naming convention introduced in \cite{amaricci}, 
+we briefly outline the main strategy for the implementation of the MVP
+according to the value of {\tt ed\_mode}.
+
+\paragraph{{\bf normal}}
+This case relies on the tensor structure of the Fock space and the
+symmetry sectors. In any given sector the electronic part of the
+Hamiltonian matrix reads:
+\begin{equation}
+H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
+H_\dw + H_{nd}\,.
+\label{HssNormal}
+\end{equation}
+where $H_d$ is a diagonal term containing the local part of the
+Hamiltonian, there including the density-density terms of the
+interaction,  $H_\sigma$ describes the hopping processes of the
+electrons with spin $\sigma=\up,\dw$.
+The term $H_{nd}$ contains all the remaining non-diagonal
+elements which do not fit in the previous two components,
+e.g. the spin-exchange and pair-hopping interaction terms.
+Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
+basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
+configurations. Leveraging on this setup it is possible the MVP using the 
+{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
+locality. Additional terms contained in $H_{nd}$ are treated using the
+{\tt MPI\_AllGatherV} algorithm which includes a slight communication
+overload ultimately reducing the parallel efficiency.
+
+\paragraph{{\bf superc/nonsu2}}
+In this two cases the symmetry enforce a specific relation between $\up$ and
+$\dw$ configurations ultimately suppressing the benefits arising from
+Fock space factorization.
+The electronic part of the Hamiltonian matrix is usually organized in this structure:
+$$
+H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
+$$
+where, with almost obvious meaning of the labels, $H_{imp}$ encodes
+the non-interacting part of the impurity Hamiltonian determined by
+$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
+effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
+$H_{imp-bath}$ describes the coupling between impurity and bath
+proportional to $V^p_{\a\b\s\s'}$. 
+In an MPI setup the first three terms contains elements local in the
+memory of each node. These are stored separately from the non-local
+ones in any {\tt sparse\_matrix} representing $H_\SS$. 
+The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
+which, as discussed in \onlinecite{amaricci2022}, requires the
+reconstruction of the distributed input array any node producing a
+overflow in the MPI communication.
+
+The diagonalization procedure is divided in two main steps: a global
+setup and the actual diagonalization.
+%
+The setup step takes care of allocating the required memory,
+setup the MPI environment and allocate the correct 
+Matrix-Vector Product (MVP) procedure according to the symmetries of
+the problem. 
+This part is implemented in a set of independent modules  {\tt
+  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
+Specifically, any such module includes two functions.
+The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
+allocate the MVP function, i.e. point the abstract function {\tt
+  sphtimesv\_p} to the correct procedure determined by the value of
+{\tt ed\_sparse\_H=True/False}.
+If {\tt True} the Hamiltonian terms in $H_\SS$
+get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
+using automatic parallel storage, and then used to perform
+the MVP. This part is implemented in the modules {\tt
+  ED\_HAMILTONIAN\_?\_STORED\_HxV}
+If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
+i.e. each element of $H_\SS$ is direcrtly applied to the given input
+vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
+either in serial or parallel mode as implemented in {\tt
+  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
+
+The function {\tt vecDim\_Hv\_sector\_?} returns the 
+dimension of the vector to be used in the
+MVP. In serial execution this number is just $D_\SS$ the dimension of
+the sector, whereas in a parallel mode the returned value is the
+dimension $d_i$ of the vector chunk per each node such that
+$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
+depends on the MPI algorithm used for the MVP function, which in turn
+is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
+
+The sector-by-sector diagonalization for each
+value of {\tt ed\_mode} is implemented in the modules {\tt
+  ED\_DIAG\_?} through the main functions {\tt
+  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
+steps: i) setup the diagonalization by selecting all or a sub-set of the
+sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
+sectors; iii) analysis of the resulting {\tt state\_list} containins
+all the eigensolutions to be conserved.
 
 \subsection{Dynamical correlation functions}\label{sSecGF}
+The determination of the low energy part of the Hamiltonian spectrum
+enables the evaluation of dynamical correlation functions using Krylov
+sub-space algorithm.
+This is a key part of the library when using \NAME as an impurity
+solver within DMFT framework.
+
+Before entering into the implementation details we briefly outline the
+generic algorithm. Let us consider the dynamical correlation function:
+\begin{equation}
+  \label{eqGaa}
+  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
+  \end{equation}
+where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
+bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
+      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
+average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
+\begin{equation}\label{KLgf}
+  \begin{split}
+    C_\AA(z) 
+    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
+    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
+    %
+    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
+  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
+  \mp
+  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
+\end{split}
+\end{equation}
+where $z\in\CCC$, 
+$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
+Hamiltonian $H$ and $E_0$ is the groundstate energy.
+While appealing, the previous expression requires the knowledge of the
+entire Hamiltonian spectrum. A key simplification is obtained looking
+at the first line in \equ{KLgf},
+showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
+resolvant. The Krylov sub-space method provides a controlled
+approximation for this element, leveraging over the
+reduction of the (sector) Hamiltonian to a partial tri-diagonal
+form and returning an arbitrary number of amplitudes to (unknown)
+excited states. To illustrate the algorithm let's consider the normalized initial state: 
+$$
+\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
+$$
+where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
+  \AA^+\ket{\psi_n}}$.
+We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
+H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
+\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
+Hamiltonian through MVP functions. 
+Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
+\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
+\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
+$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
+\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
+obtain the following approximation to $C_\AA$:
+\begin{equation}
+  \label{eqGKrylov}
+  \begin{split}
+    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
+    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
+      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
+      |a^n_m|^2}{ z + (E_m-E_n)}\cr
+    %
+    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
+    = \frac{1}{Z}\sum_n
+    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
+  \end{split}
+\end{equation}
+where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
+for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
+poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
+contributing to the low energy spectrum, for every order $m$ of the
+Krylov sub-space algorithm and for channel $\nu$.
+
+A stringent limitation of this procedure is to get applied to diagonal
+dynamical correlation functions of the form \equ{eqGaa}. However, as
+we will show in the following, many practical application requires to
+evaluate off-diagonal functions of the form:
+$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
+A direct extensin of the method is obtained considering suitable
+auxiliary operators prepared with independent linear combination of
+$\AA$ and $\BB$.
+A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
+$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
+obtain the desired function $C_{\AA \BB}$ from the evaluation of
+$C_\OO$ and $C_\PP$:
+$$
+C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
+$$
+
+In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
+c_{\b\s'}^+ ]\iket$,
+is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
+specific methods according to the symmetry of the problem expressed by
+{\tt ed\_mode}. In the {\bf normal} mode also spin,
+charge, pair and excitonic susceptibilities functions. 
+Computationally, the construction of the Krylov basis
+$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
+spectrum is the most time consuming step. As for the diagonalization
+part, here a crucial speed-up is obtained by the parallel execution of
+the MVP lying at the earth of the Hamiltonian tri-diaagonalization
+process. The input variable {\tt lanc\_gfniter} controls the largest order of
+the Krylov basis, i.e. the maximum number of excitations in
+\equ{eqGKrylov}.  
+Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
+the Green's functions implemented in {\tt ED\_GF\_?}
+
+\paragraph{{\bf normal}}
+In this case the all the orbital dependent and spin-diagonal Green's
+functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
+$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
+step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
+  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
+  state\_list}, i.e. a global instance of {\tt sparse\_espace}
+containing the low energy spectrum of the problem.
+The sector Hamiltonian matrix in this mode is assumed to be real
+symmetric. This brings a simplification in the evaluation of the
+off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
+These components are thus evaluated considering the auxiliary operator
+$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
+$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
+
+The diagonal spin, charge and pair susceptibility terms
+$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
+evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
+S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
+N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
+\Delta_\a$, where
+$\tau^{a=0,x,y,z}$ are the Pauli matrices.
+Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
++ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
+The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
+to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
+c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
+($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
+
+\paragraph{{\bf superc}}
+In the supercondutive case the Nambu orbital
+dependent $s$-wave Green's function reads:
+\begin{equation}
+  \label{GFnambu}
+  \hat{G}_{\a\b} =
+  \begin{bmatrix}
+    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
+    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
+  \end{bmatrix}  
+\end{equation}
+However, leveraging on the symmetries holding between the different
+components we can reduce to evaluate only the top row components plus
+auxiliary functions.
+The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
+very same scheme of the {\bf normal} case. For the off-diagonal terms
+however we do not rely on any symmetry relation but we consider 
+two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
+c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
+$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
+(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
+The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
+be evaluated using different combinations of creation/destruction
+operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
+an auxiliary term considering $\AA=c^+_{\a\dw}$. 
+Next, we consider the two linear combinations:
+$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
+contributing, respectively, to the auxiliary functions $C_\TT$,
+$C_\RR$. The searched anomalous functions reads:
+$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
+\bar{G}_{\b\b\dw\dw})]$.
+
+\paragraph{{\bf nonsu2}}
+In this case all the Green's functions components need
+to be evaluated. For the orbital and spin diagonal terms
+$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
+The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
+evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
+$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
+$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
+(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
 
 \subsection{Observables}\label{sSecObc}
+A number of predefined impurity observable or local static
+correlations, e.g. occupation, total energy, pair amplitude, excitonic
+order parameter ,etc.   are calculated in the module
+\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
+different implementations and quantities to evaluate from the
+operational modes {\tt ed\_mode=?} implemented in {\tt
+  ED\_OBSERVABLES\_?}. 
+Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
+\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
+low temperature using the stored low energy part of the spectrum
+leveraging on the exponential cutoff from the Boltzmann factor:
+$$
+\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
+  E_n}\bra{\psi_n}\OO\ket{\psi_n}
+$$
+where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
+system stored in the {\tt state\_list}.
 
 \subsection{Reduced impurity density matrix}\label{sSecRDM}
+This version of the \NAME library features the calculation of the
+impurity Reduced Density Matrix (iRDM), enabling the analysis of
+entanglement properties of the quantum impurity for any value of {\tt
+  ed\_mode}.
+To simplify the discussion in this section we take the zero
+temperature limit and consider the presence of a non-degenerate
+groundstate $\ket{\psi}$ populating the {\tt state\_list}.
+The generalization to the presence of degenerate states or the finite
+temperature regime are straightforward.
+The groundstate belongs to a given symmetry sector $\SS$ and it
+represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
+The density matrix $\rho$ is defined as:
+$$
+\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
+$$
+The iRDM is obtained from this by tracing out the bath degrees of
+freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
+previous expressions becomes quickly unmaneagable with the system
+size. To overcome this issue we proceed in three steps. 
+We use quantum numbers conservation which
+reduces extrema of the summation to the size $D_S$ of the sector $S$
+to which the groundstate belongs;
+Next we split the bits representation of any state $\ket{n}$ into
+their spin-dependent impurity and bath parts as $\ket{n} = \ket{
+  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
+set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
+Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
+$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
+(values) which contribute to that key, as detailed in
+\secu{CodeSparseMap}.
+We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
+The fast algorithm for the evaluation of the iRDM are outlined below
+for the two cases {\bf normal} and {\bf superc/nonsu2}.
+
+\paragraph{{\bf normal}}
+
+\paragraph{{\bf superc/nonsu2}}
 
@@
 \subsection{Bath Optimization}\label{sSecFit}
+In the DMFT context the bath is updated using a suitable 
+optimization of the bath parameters against a given realization of the Weiss field
+${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
+$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
+{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
+This step corresponds to a projection of the Weiss
+field (or the Delta function) onto the space of the Anderson quantum
+impurity model functions
+$\GG^{And}_0(z) =
+[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
+\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
+{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
+variational paramaters $\{V,h\}$.
+
+This  optimization can be performed using different
+  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
+  In \NAME\ we offer to perform this task using a  
+conjugate gradient (CG) minimization of the cost function:
+$$
+\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
+$$
+where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
+supplied local functions  and
+$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
+Anderson impurity model function, defined above.
+The fit procedures are contains in the module \texttt{BATH\_FIT}.  
+In order to exploit regularity of the functions the fit is 
+performed using imaginary Matsubara frequency. 
+The actual form of $X_{\a\b}$ is controlled by the input parameter
+\texttt{cg\_Scheme=Weiss,Delta}.
+
+Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
+introduced different specific control parameters. This aims to give
+the user the possibility of fine tuning the fit and adapt its behavior to
+specific situations.
+Two distinct CG algorithms can be used in the library, as controlled by the input variable
+\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
+Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
+Numerical Recipes~\cite{NumRec77}. In order to guarantee
+back-compatibility with respect to the literature, we also provide the
+possibility of using the minimization procedure published in
+Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
+community.
+
+The gradient $\nabla\chi$ required by the CG algorithm can be
+evaluated either analytically or numerically as
+controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
+\texttt{cg\_method=1} only numerical gradient can be used.
+The number of Matsubara frequency $L_{fit}$ used in the fit procedure
+is controlled  by the input parameter \texttt{cg\_Lfit}.
+This parameter can be used to restrict the fit to the low frequency
+part as the large frequency tails of the local Matsubara functions
+have universal behavior.
+Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
+enhance the weight of low energy part with respect to the
+intermediate-to-large energy one in the cost function.
+This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
+Another  factor contributing to determine the behavior
+of the fit is the power $q$ of the cost function $\chi$. By tuning
+this parameter, controlled by input variable \texttt{cg\_pow}, it is
+possible to enhance or suppress the differences in the $\chi$ in order
+to improve (or simplify) the optimization procedure.
+
+Finally, we introduced few additional parameters which aim to
+control the quality of the fit. The first is the fit tolerance,
+controlled by the input parameter \texttt{cg\_Ftol}, which
+determines the convergence threshold of the minimization procedure.
+The second is the maximum number of iterations \texttt{cg\_Niter}
+allowed for the CG algorithm to determine the minimum.
+The last parameter \texttt{cg\_stop=0,1,2} selects the exit
+condition of the minimization procedure. We envisaged  three
+possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
+$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
+$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
+is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
+the corresponding argument. Increasing the value of the stop
+parameter generally loosens up the exit conditions of the minimization.
 
@@
 \section{Triqs interface}\label{SecEDI2Triqs}
+
+\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
 

### 2025-04-03 edipack2.tex
Update draft. Completed sec.2, the main part

@@
 %% 5p,twocolumn, preprint, review
-\documentclass[final,3p,10pt]{elsarticle}
+\documentclass[preprint,3p,10pt]{elsarticle}
 
@@
 % \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
+
+\usepackage[inline]{showlabels}
 
@@
 The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
+freedom: $\rho^{i}=Tr_{b}\rho$. The summation appearing in the
 previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
+size. To overcome this issue we implemented a fast algorithm
+leveraging on symmetry sector and map sparsity.
+Using quantum number conservation the summation extrema get reducedto
+the size $D_S$ of the sector $S$ to which the groundstate (or in
+general any eigenstate) belongs. 
+Next we analyze the groundstate expansion on the Fock states, splitting the bit representation of any state $\ket{I}$ into
+their spin-dependent impurity and bath parts as $\ket{I} = \ket{
   i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
@@
 We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
+The fast summation algorithm for the evaluation of the iRDM takes on a
+different form for the two cases {\bf normal} and {\bf superc/nonsu2},
+as outlined below.
 
 \paragraph{{\bf normal}}
+In this case we take advantage of the Fock and sector spin resolved
+factorization discussed in \secu{sSecQNs}. As such we can also split
+impurity and bath bits independently for each spin configuration:
+$$
+\ket{\vec{n}} =
+\ket{\vec{n}_\up}\otimes \ket{\vec{n}_\dw} =
+\ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}
+$$
+In addition it should be noted that creation (destruction) operators at
+position $p$ for spin $\sigma$  $c^+_{p\sigma}$ ($c^+_{p\sigma}$) do
+not operate on the opposite spin so that they pass through without
+taking any fermionic sign. Finally, we observe that local iRDM admits
+only diagonal terms in the {\bf normal} case. Thus we obtain for the iRDM:
+\begin{equation}
+  \label{iRDMnormal}
+  \begin{aligned}
+  \rho^i &=
+  \sum_{\sigma=\up\dw}\sum_{b_\sigma=1}^{D_{b_\sigma}}
+  \bra{b_\up}\otimes\bra{b_\dw}
+    \rho
+    \ket{b_\dw}\otimes\ket{b_\up}    \cr
+    %
+    &=\sum_{\sigma=\up\dw}
+    \sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \sum_{i_\sigma=1}^{D_{i_\sigma}}
+    \sum_{p_\sigma=1}^{D_{p_\sigma}}
+    \sum_{j_\sigma=1}^{D_{j_\sigma}} 
+    \sum_{q_\sigma=1}^{D_{q_\sigma}}
+    C_{i,p}\,C_{j,q}\,a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw}
+    \langle b_\up| p_\up\rangle| i_\up\rangle\langle j_\up |\langle q_\up| b_\up\rangle   \otimes \langle b_\dw| p_\dw \rangle|i_\dw\rangle \langle j_\dw  |\langle q_\dw| b_\dw\rangle
+    \cr
+&=
+    \sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \sum_{i_\sigma=1}^{D_{i_\sigma}}
+    a_{i_\up b_\up i_\dw b_\dw} a^*_{i_\up b_\up i_\dw b_\dw}
+    \ket{i_\up}\bra{i_\up}\otimes \ket{i_\dw}\bra{i_\dw}
+  \end{aligned}
+\end{equation}
+where the constant $C_{i,b}$ take care of the sign change due to
+exchanging bath and impurity bit sets. As effect of the Kronecker
+delta symbols for bath and impurity these constants are identically 1.  
+The numerical implementation relies on the use of the {\tt
+  sparse\_map} ($\%sp$) for the groundstate sector as reported in the
+listing below:  
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+do IimpUp=0,2**Norb-1
+  do JimpUp=0,2**Norb-1
+    !Finding the unique bath states connecting IimpUp and JimpUp
+    call sp_return_intersection(sectorI%H(1)%sp,IimpUp,JimpUp,BATHup,lenBATHup)
+    if(lenBATHup==0)cycle
+    do IimpDw=0,2**Norb-1
+      do JimpDw=0,2**Norb-1
+        !Finding the unique bath states connecting IimpDw and JimpDw -> BATHdw(:)
+        call sp_return_intersection(sectorI%H(2)%sp,IimpDw,JimpDw,BATHdw,lenBATHdw)
+        if(lenBATHdw==0)cycle
+        do ibUP=1,lenBATHup
+          IbathUp = BATHup(ibUP)
+          do ibDW=1,lenBATHdw
+            IbathDw = BATHdw(ibDW)
+            !Allowed spin Fock space Istates:
+            !Iup = IimpUp +  2^Norb * IbathUp
+            !Idw = IimpDw +  2^Norb * IbathDw
+            iUP= binary_search(sectorI%H(1)%map,IimpUp + 2**Norb*IbathUp)
+            iDW= binary_search(sectorI%H(2)%map,IimpDw + 2**Norb*IbathDw)
+            i  = iUP + (iDW-1)*sectorI%DimUp
+            !Allowed spin Fock space Jstates:
+            !Jup = JimpUp +  2^Norb * IbathUp
+            !Jdw = JimpDw +  2^Norb * IbathDw
+            jUP= binary_search(sectorI%H(1)%map,JimpUp + 2**Norb*IbathUp)
+            jDW= binary_search(sectorI%H(2)%map,JimpDw + 2**Norb*IbathDw)
+            j  = jUP + (jDW-1)*sectorI%DimUp
+            ! 
+            io = (IimpUp + 2**Norb*IimpDw) + 1
+            jo = (JimpUp + 2**Norb*JimpDw) + 1
+            irdm(io,jo) = irdm (io,jo) + psi(i)*psi(j)*weight
+          enddo
+        enddo
+      enddo
+    enddo
+  enddo
+enddo
+\end{lstlisting}
 
 \paragraph{{\bf superc/nonsu2}}
+In presence of these symmetries suitable modifications related to the
+absence of Fock space factorization have to be taken into account. To
+start with a generic Fock state appearing in the groundstate
+decomposition has the form:
+$$
+\ket{\vec{n}} =\ket{\vec{i}_\up\vec{b}_\up\vec{i}_\dw\vec{b}_\dw}
+%
+$$
+% where the second is just a formal identity.  
+Inserting this latter in the definition of iRDM we obtain:
+\begin{equation}
+  \begin{aligned}
+    \Tr_{b_\up, b_\dw}{\rho} &=
+    \sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \bra{b_\up\, b_\dw}
+    \rho
+    \ket{b_\dw\, b_\up}    \cr
+    &=
+    \sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \sum_{i_\sigma=1}^{D_{i_\sigma}}
+    \sum_{p_\sigma=1}^{D_{p_\sigma}}
+    \sum_{j_\sigma=1}^{D_{j_\sigma}} 
+    \sum_{q_\sigma=1}^{D_{q_\sigma}}
+    a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw}% \cr
+    % &{\phantom =}
+    \langle{b_\up\, b_\dw}|{i_\up\, p_\up\, i_\dw\, p_\dw}\rangle
+    \langle{q_\dw \,  j_\dw \, q_\up\, j_\up }|{b_\dw\, b_\up}\rangle\, .
+  \end{aligned}
+\end{equation}
+In order to simplify this expression we should get rid of the sum with
+respect to the bath indices $p_\sigma$ and $q_\sigma$, ideally
+contracting them with the outer indices $b_\sigma$.
+However, this requires to bring all the bath bits so to preced the
+impurity ones:
+$$
+\ket{i_\up\, p_\up\, i_\dw\, p_\dw} \rightarrow C_{p_\up,i_\dw} \ket{i_\up\, i_\dw \,p_\up\,p_\dw}
+$$
+where $C_{p_\up,i_\dw}  = (-1)^{\#\vec{n}_{p\up} \cdot
+  \#\vec{n}_{i\dw}}$ with   $\#\vec{n}=\sum_i n_i$ is an overall
+fermionic sign which depends on the occupation of the $p_\up$ and the
+$i_\dw$ bit configurations. Inserting this relation in the equation
+for the iRDM we obtain:
+\begin{equation}
+  \begin{aligned}
+    \Tr_{b_\up, b_\dw}{\rho} &=
+    \sum_{i_\sigma=1}^{D_{i_\sigma}}
+    \sum_{j_\sigma=1}^{D_{j_\sigma}}
+    \left[\sum_{b_\sigma=1}^{D_{b_\sigma}}
+    a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
+    C_{b_\up,i_\dw}C_{b_\up,j_\dw}\right]
+    \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up}\cr
+&=
+    \sum_{i_\sigma=1}^{D_{i_\sigma}}
+    \sum_{j_\sigma=1}^{D_{j_\sigma}}
+    \rho^{i}_{i_\up i_\dw j_\dw j_\up}
+    \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up} 
+  \end{aligned}
+\end{equation}
+The numerical implementation requires few modifications with respect
+to the previous case. In particular it is important to recall that the
+ordering of the key-value pairs in the {\tt sparse\_map} in this case
+follow a contiguous ordering and that their decomposition is necessary
+to reconstruct the correct Fock state index, see the following
+listing:
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+do IimpUp=0,2**Norb-1
+  do IimpDw=0,2**Norb-1
+    do JimpUp=0,2**Norb-1
+      do JimpDw=0,2**Norb-1
+        !Build indices of the RDM in 1:4**Norb
+        iImp = iImpUp + iImpDw*2**Norb
+        jImp = jImpUp + jImpDw*2**Norb
+        call sp_return_intersection(sectorI%H(1)%sp,iImp,jImp,Bath,lenBath)
+        if(lenBATH==0)cycle
+        do ib=1,lenBath
+          iBath = Bath(ib)
+          !Decompose iBath into B_Up, B_dw to reconstruct B bit set. 
+          !B --> {B_up,B_dw}
+          iBathUp = mod(iBath,2**Nbath)
+          iBathDw = (iBath)/2**Nbath
+          !Reconstruct the Fock state Ii map back to sector state i
+          ii= iImpUp + iImpDw*2**Ns + 2**Norb*(IBathUp + IBathDw*2**Ns)
+          i = binary_search(sectorI%H(1)%map,ii)
+          !Reconstruct the Fock state Jj map back to sector state j
+          jj= jImpUp + jImpDw*2**Ns + 2**Norb*(IBathUp + IBathDw*2**Ns)
+          j = binary_search(sectorI%H(1)%map,jj)
+          !Build the signs of each components of RDM(io,jo)
+          nBup  = popcnt(Ibits(ii,Norb,Norb*Nbath))
+          nIdw  = popcnt(Ibits(ii,Ns,Norb))
+          nJdw  = popcnt(Ibits(jj,Ns,Norb))
+          signI = (-1)**(nIdw*nBup)
+          signJ = (-1)**(nJdw*nBup)
+          sgn   = signI*signJ
+          !  
+          io = (iImpUp+1) + 2**Norb*iImpDw
+          jo = (jImpUp+1) + 2**Norb*jImpDw
+          rdm(io,jo) = rdm(io,jo) + psi(i)*conjg(psi(j))*weight*sgn
+        enddo
+      enddo
+    enddo
+  enddo
+enddo
+\end{lstlisting}
 
 \subsection{Bath Functions}\label{sSecFunc}
+The module {\tt ED\_BATH\_FUNCTIONS} implements on-the-fly
+calculations of the hybridization function $\Delta_{\a\b\s\s'}(z)=\sum_\nu
+{V^\nu_{\a\s}}(z\11-h^\nu_{\a\b\s\s'})^{-1}V^\nu_{\b\s'}$ and the
+non-interacting Green's functions $G^0_{\a\b\s\s'}(z) =
+[(z + \mu)\delta_{\a\b\s\s'} - h^0_{\a\b\s\s'} -
+\Delta_{\a\b\s\s'}(z)]^{-1}$ for any frequency $z\in\CCC$. 
+The module contains implementations for any case according to the
+values of {\tt ed\_mode} and {\tt bath\_type}, either with supplied
+user bath (a rank-1 array of doubles) or using the allocated {\tt
+  effective\_bath} instance {\tt dmft\_bath}. 
+We provide different functions to get either $\Delta$, $G^0$ and its
+directly its inverse $[G^0]^{-1}$, which are used to evaluate the
+self-energy functions upon request, see \secu{sSecIO}.
+In the superconductive case {\tt ed\_mode}={\bf superc} different
+procedures can be used to retrieve the anomalous components of any
+function defined above in the Nambu basis.
 
 \subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
+{\color{red} to be revised, copy\&paste from edipack paper: well it is
+  essentiall the same shit} 
+In the DMFT context the bath needs to be optimized
+against a given realization of the Weiss field
+${\GG^{-1}_{0}}_{\a\b\s\s'}(z)$, or the corresponding {\it hybridization} function
+$\Theta = (z + \mu)\11 - H^{loc} -\GG_0^{-1}](z)$. While the Weiss
+field is obtained from the DMFT self-consistency
+equation~\cite{Georges1996RMP}, bath discretization impose to  find an optimal
+description of the continuous Weiss field in terms of the finite
+number of parameters of the bath (see \secu{sSecBath}.
+Although different algorithms can be envisaged to perform this
+step~\cite{Garcia2004PRL,Taranto2012PRB} which are perfectly valid in
+some physical contexts.
+In order to enable the users to use their preferred 
+method in \NAME we keep the optimization implementation independent
+from the rest of the code. Yet, we offer a fully fledged optimization
+strategy based on the  conjugate gradient (CG) minimization of the cost function:
+$$
+\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}||X(i\omega_n) - X^{QIM}(i\omega_n;\{V,h\})||_q
+$$
+where the symbol $|| \cdot ||_q$ is a suitably defined $q$-norm in the
+matrix function space, $X_{\a\b}={\GG_{0}}_{\a\b\s\s'},\,\Theta_{\a\b\s\s'}$ are the user
 supplied local functions and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
+$X_{\a\b}^{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
+quantum impurity model functions, defined above.
+Notably, more sophisticated optimization algorithms have been
+recently implemented to better undertake the minimization of similar
+cost functions. However, these developments are designed to work with truncated
+algorithms, e.g. sCI or DMRG, describing systems with a larger number of
+bath levels.   
+In the ED context however, where the efficient and wise selection of
+the relatively few bath levels becomes crucial, the CG minimization of
+the local functions proved to be the most efficient and
+flexible optimization scheme so far.
+
+The fit procedure is entirely wrapped by the single function {\tt
+  ed\_chi2\_fitgf} contained in the module \texttt{ED\_BATH\_FIT}.   
 In order to exploit regularity of the functions the fit is 
 performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
+The actual form of $X_{\a\b\s\s'}$ is controlled by the input parameter
 \texttt{cg\_Scheme=Weiss,Delta}.
 
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
+In order to fine tune the optimization step in \NAME\ we
+introduced a number of control parameters. To start with, we include
+two distinct CG algorithms in the library, controlled by the input variable
 \texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
 Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
+Numerical Recipes~\cite{NumRec77}. Yet, in order to guarantee
+back-compatibility with respect to the past literature, we also provide the
 possibility of using the minimization procedure published in
@@
 
+{\bf REMARK TODO}
+Notes on the norm function: a) the definition for conventional
+matrices, ;b) the definition for the replica/general case where you
+can choose between different norm defition.
+
 \subsection{Input/Output}\label{sSecIO}
+The module {\tt ED\_IO} provides access to the results of the Lanczos
+diagonalization of the quantum impurity problem.
+As any single instance of the code is preserved in the memory until a
+new call is made, access to the memory pool is only possible through
+specific functions implemented in {\tt ED\_IO}. For instance, dynamical response functions, self-energy components or impurity
+observables can all be retrieved using dedicated functionalities.
+Additionally we provide procedures to perform on-the-fly
+re-calculation of the impurity Green's functions and self-energy on a
+given arbitrary set of points in the complex frequency domain
+exploiting their storage in terms of {\tt gfmatrix} objects.
+A long list of available functions is contained in the on-line
+documentation (see
+\href{https://edipack.github.io/EDIpack2.0/edipack2/13_io.html#ed-io}{https://edipack.github.io/EDIpack2.0/edipack2/13\_io.html\#ed$-$io})
+Here we limit the discussion to two paradigmatic examples.
+The first is the function {\tt ed\_get\_dens} which write on the
+provided input array the value of the orbital impurity occupations
+$\langle n_{\a\s}\rangle$. Analogously {\tt ed\_get\_sigma} is used to
+retrieve the normal or anomaous components of the Matsubara or
+Real-axis self-energy function $\Sigma(z)$. This latter represents the
+key output of the calculation in 
+any DMFT application.
 

### 2025-04-04 edipack2.tex
Updated draft up to EDIpack2ineq Going to results, skip other sections

@@
 
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Inequivalent impurities: EDIpack2Ineq}\label{SecIneq}
+It is often necessary to solve systems with several, independent,
+quantum impurities. Paradigmatic examples arise in the DMFT
+framework when dealing with the effective description of lattices
+built out of unit cells hosting multiple inequivalent atoms or large
+super-cell systems with possibly broken translational symmetries,
+e.g. heterostructures of correlated materials, disordered systems,
+etc.
+As the structure of \NAME allows the presence of a single instance of
+the solver at any time, we implemented a suitable extension to deal
+with multiple impurities. Specifically {\tt EDIpack2Ineq} is a
+sub-library which complements \NAME, wrapping memory and procedures in
+order to enable simultaneous treatment of  inequivalent impurities. 
+Using standard Fortran interfaces it is possible to group all the
+\NAME and {\tt EDIpack2ineq} functions under the same name without
+compromising the software functionalities.  
+Here below we briefly discuss the main additions introduced by {\tt
+  EDIpack2ineq}.
+
+\subsection{Structure}\label{sSecIneqStructure}
+The sub-library is composed of a number of Fortran modules which are
+wrapped by {\tt EDIPACK2INEQ}. This latter represents the main user
+interface and gives access to all the available procedures and
+variables as needed to solve quantum impurity problems.
+The user needs to invoke use of this module alongside the \NAME one:
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+program test
+  !Load EDIpack2 library 
+  USE EDIPACK2 
+  !Load the Inequivalent impurities extension
+  USE EDIPACK2INEQ
+  ...
+\end{lstlisting}
+
+A major part of the {\tt EDIpack2ineq} library is to define global
+variables which wrap and conserve the memory pool of \NAME.
+For instance we implement a number of
+globally shared arrays with an increased rank to store the
+variables in any memory instance of \NAME and accessible through
+the input/output procedures (see \secu{sSecIO}).
+Specific objects, e.g. {\tt effective\_bath} or {\tt gfmatrix}, in
+principle require dedicated MPI
+communication when parallel execution of the solver among independent
+impurities. However, we opt for the much simpler and economic solution
+of reading these objects from the file in which they get saved
+anyway.
+
+\subsection{Core routines}\label{sSecIneqGlobal}
+The module {\tt E2I\_MAIN} wraps the extensions to the main algorithms
+of \NAME, namely: initialization, diagonalization and finalization,
+preserving the original naming convention.  
+The initialization process is handled by {\tt ed\_init} which is
+extended to accepts a bath array or rank-2 (as opposed to rank-1 array
+in the \NAME implementation). The leading dimension now determines the
+number of inequivalent impurity problems to be solved. This procedure
+initialize all the {\tt EDIpack2ineq} variables and prepare each bath
+for the diagonalization step. 
+In {\tt ed\_solve}, which accepts the same rank-2 bath array, performs the
+diagonalization of each quantum impurity problem in either serial of
+parallel mode. The parallel mode is further controlled by the input
+function {\tt mpi\_lanc=T/F}. If true Lanczos diagonalization is
+performed in parallel and inequivalent sites are treated
+sequentially. The inverse if false.   
+The finalization procedure with full memory release is performed in
+{\tt ed\_finalize}.
+
+\subsection{Inequivalent Baths}\label{sSecIneqBath}
+The inequivalent impurities extension is encoded in {\tt E2I\_BATH}
+which contains procedures to control the baths setup on the user side
+and the  implementation of conventional symmetry operations.
+In the {\tt E2I\_BATH\_REPLICA} module we extend all the functions
+which set the replica/general bath matrix basis 
+$\vec{\Gamma}$ and the corresponding initial variational parameters
+$\vec{\lambda}$. Although the variational parameters are generally
+different from site to site, in the current implementation the matrix
+basis is independent from the impurities number. This will possibly be
+relaxed in a future release. 
+Analogously, in the module {\tt E2I\_BATH\_FIT} we implement an extension of the generic
+function {\tt ed\_chi2\_fitgf} to perform multiple independent
+bath optimization for all inequivalent impurities in terms of an MPI iterative cycle.
+
+\subsection{Input/Output}\label{sSecIneqIO}
+A key part of the {\tt EDIpack2ineq} library is the extension for the
+input/output procedures to return observables or dynamical functions per inequivalent impurity.
+The module {\tt E2I\_IO} implements numerous functions which retrieve
+or evaluate on-the-fly any quantity accessible in \NAME for any given
+impurity (or all of them) using the same naming original convention
+defined in \NAME.
+
+\section{C-bindings: EDIpack2C}\label{SecCbind}
+
+\section{Python API: EDIpy2}\label{SecPyAPI}
+
+\section{Triqs interface: EDIpack2Triqs}\label{SecEDI2Triqs}
+
+\section{W2Dynamics interface: EDIpack2w2dyn}\label{SecEDI2W2Dyn}
 
@@
 
-\section{Conclusions}
+\section{Conclusions and perspectives}
+\subsection{Conclusions}
+
+\subsection{Perspectives}
 

### 2025-04-09 01_intro.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-02 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[final,3p,10pt]{elsarticle}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
-
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage{xcolor}
-\usepackage{makecell}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.~\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.~\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-
-\address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack2                                        \\
-{\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
-{\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
-{\em Nature of problem:}. \\
-{\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
 \section{Introduction and Motivation}\label{SecIntro}
@@
 bla bla bla
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Structure and derived software}\label{SecStruct}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
-interface, which enables development of additional API or
-inter-operability with external libraries.
-
-\begin{itemize}
-\item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
-
-\item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
-
-\item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
-
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
-
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
-
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
-
-\end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
-
-\subsection{Dependencies}
-\NAME essentially depends on two external libraries.
-\begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
-\end{itemize}
-
-SciFortran provides a solid development platform enabling access to
-many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
-greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
-
-\subsection{Build and Install}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
-be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
-\end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
-
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake ..
-make -j
-make install
-\end{lstlisting}
-
-\item{\bf Ninja}
-
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
-
-\noindent
-The CMake configurations can be further tuned using the following variables:
-\begin{center}
-\begin{tabular}{ l|l|l } 
- \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
-  \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
- \hline
-\end{tabular}
-\end{center}
-
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
-CMake configuration step.
-
-\subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
-installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
-
-The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-\noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
-
-\subsection{OS Loading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
-directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
-
-We offer different strategies to perform this action:
-\begin{enumerate}
-\item  A CMake generated configuration file for environment module
-  which allows to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
-  permanently) in any shell session to add \NAME library to the
-  default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
-\end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
-
-\subsection{Python API}
-\subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
-pip install . 
-\end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
-
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
-
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-
-\subsection{TRIQS interface}
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/krivenko/edipack2triqs
-cd edipack2triqs
-pip install .
-\end{lstlisting}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
-\section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
-
-\subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
-$$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
-$$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
-\begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
-    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
-    &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
-      \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
-\end{split}
-\end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
-The first three terms represent the density-density part of the
-interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The  remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
-\begin{equation}\label{Hbath}
-  \begin{split}
-    \hat{H}_{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
-    %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
-\end{split}
-\end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
-
-Finally, the electron-phonon part of the quantum impurity problems is
-described by the Hamiltonian terms: 
-\begin{equation}\label{Hph}
-  \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
-    % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
-\end{split}
-\end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$. 
-In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
-
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
-The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
-\subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
-The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
-The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
-\begin{align*}
-  c_{a\sigma}\ket{\vec{n}} &=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};\qquad
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-\end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
-
-\subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
-%
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
-\begin{table}%[ht]
-  \label{TabSector}
-\begin{center}
-\begin{tabularx}{\linewidth}{ |X|X|X| } 
- \hline
-  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
-  \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
-  \\
-  \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-  \\
-  \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
- \hline
-\end{tabularx}
-\end{center}
-\caption{Ciao}
-\end{table}
-
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i = i+1
-  H(iud)%map(i) = lup
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i = i+1
-  H(iud+Ns)%map(i) = Idw
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**N
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(Idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(Iup)
-    nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**Ns
-  enddo
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\begin{tabular}{c|c|c}\label{list1}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
-
-\subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
-
-\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-\subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
-\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
-given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
-
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
-$
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i=i+1 
-  !...
-  iImp  = ibits(iup,0,Norb)
-  iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i=i+1 
-  !...
-  iIMP  = ibits(idw,0,Norb)
-  iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf superc/nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    !superc 
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
-    i=i+1 
-    !...
-    iImpUp  = ibits(iup,0,Norb)
-    iImpDw  = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
-    iImp    = iImpUp  + iImpDw*(2**Norb)
-    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-%
-
-\subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
-$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
-
-\subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
-
-\subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_b$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
-The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
-spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
-$$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
-$$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
-dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
-= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
-\paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
-
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
-
-\paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
-
-\subsection{Lanczos based Diagonalization}\label{sSecHam}
-In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
-$$
-H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
-$$
-
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{HssNormal}
-\end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
-dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
-
-\subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
-sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
-\begin{equation}
-  \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
-  \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
-\begin{equation}\label{KLgf}
-  \begin{split}
-    C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
-    %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
-  \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
-\end{split}
-\end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
-$$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
-H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
-\begin{equation}
-  \label{eqGKrylov}
-  \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
-      |a^n_m|^2}{ z + (E_m-E_n)}\cr
-    %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
-  \end{split}
-\end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
-$$
-C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
-$$
-
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
-\equ{eqGKrylov}.  
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
-
-\paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
-
-The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
-
-\paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
-\begin{equation}
-  \label{GFnambu}
-  \hat{G}_{\a\b} =
-  \begin{bmatrix}
-    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
-  \end{bmatrix}  
-\end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
-$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
-
-\paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
-
-\subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-$$
-\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
-
-\paragraph{{\bf normal}}
-
-\paragraph{{\bf superc/nonsu2}}
-
-\subsection{Bath Functions}\label{sSecFunc}
-
-\subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
-supplied local functions  and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
-
-\subsection{Input/Output}\label{sSecIO}
-
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Conclusions}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section*{Acknowledgements}
-
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
-\end{document}

### 2025-04-09 02_install.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-02 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[final,3p,10pt]{elsarticle}
+\section{Installation}\label{SecInstall}
+The installation of \NAME is available through CMake which ensures
+multi-platforms compabitility and dependencies resolution.  
+The software builds into two distinct libraries.
+The main one is {\tt  libedipack.a} which, alongside the generated Fortan
+modules, wraps the \NAME software possibly including support for  
+inequivalent impurities.
+A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
+specific bindings to the C programming language.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
-
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage{xcolor}
-\usepackage{makecell}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.~\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.~\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-
-\address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack2                                        \\
-{\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
-{\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
-{\em Nature of problem:}. \\
-{\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
-\section{Introduction and Motivation}\label{SecIntro}
-
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
-
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
-
-* zero and low finite temperatures
-
-* direct access to (well approximated) analytic dynamical functions
-
-* direct access to impurity Fock space quantities
-
-bla bla bla
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Structure and derived software}\label{SecStruct}
+\subsection{Structure}\label{SSecStruct}
 \NAME is a modular library which contains three principal structures.
@@
 Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
+inequivalent impurity problems. Finally, there we provide a Fortran-C/C++
 interface, which enables development of additional API or
-inter-operability with external libraries.
+interoperability with other, external, software.
 
@@
 \item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
+\NAME includes a single module implementing a Fortran-C/C++ interface of the main
 library procedures. The module is developed around the implicit {\tt
@@
 
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
+% \item{\bf EDIpy2.}
+% This is a simple Python module which provides Python API to the
+% \NAME Fortran library. This interface is built around the Python
+% support to C-types, which allows to import the dynamic C-binding
+% library generated upon building \NAME. The module contains a specific
+% class, whose methods mirrors through  duck-typing all the available
+% procedures of \NAME as well as it gives access to relevant shared
+% control variables.
 
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
+% \item{\bf EDIpack2Triqs.}
+% This is a thin interface layer from \NAME to Triqs,
+% built around the Python API of the \NAME library. The exact
+% diagonalization solver is encapsulated in a dedicated class,
+% containing the necessary methods to initialize and run a single
+% instance of the solver. The interface also includes a specific class
+% encompassing the effective discretized bath structure as well as their 
+% optimization methods.
 
 \end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
 
@@
 generated at the end of the installation procedure.
-
-\subsection{Python API}
-\subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
-pip install . 
-\end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
-
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
-
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-
-\subsection{TRIQS interface}
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/krivenko/edipack2triqs
-cd edipack2triqs
-pip install .
-\end{lstlisting}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
-\section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
-
-\subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
-$$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
-$$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
-\begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
-    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
-    &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
-      \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
-\end{split}
-\end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
-The first three terms represent the density-density part of the
-interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The  remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
-\begin{equation}\label{Hbath}
-  \begin{split}
-    \hat{H}_{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
-    %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
-\end{split}
-\end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
-
-Finally, the electron-phonon part of the quantum impurity problems is
-described by the Hamiltonian terms: 
-\begin{equation}\label{Hph}
-  \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
-    % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
-\end{split}
-\end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$. 
-In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
-
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
-The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
-\subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
-The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
-The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
-\begin{align*}
-  c_{a\sigma}\ket{\vec{n}} &=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};\qquad
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-\end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
-
-\subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
-%
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
-\begin{table}%[ht]
-  \label{TabSector}
-\begin{center}
-\begin{tabularx}{\linewidth}{ |X|X|X| } 
- \hline
-  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
-  \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
-  \\
-  \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-  \\
-  \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
- \hline
-\end{tabularx}
-\end{center}
-\caption{Ciao}
-\end{table}
-
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i = i+1
-  H(iud)%map(i) = lup
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i = i+1
-  H(iud+Ns)%map(i) = Idw
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**N
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(Idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(Iup)
-    nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**Ns
-  enddo
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\begin{tabular}{c|c|c}\label{list1}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
-
-\subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
-
-\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-\subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
-\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
-given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
-
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
-$
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i=i+1 
-  !...
-  iImp  = ibits(iup,0,Norb)
-  iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i=i+1 
-  !...
-  iIMP  = ibits(idw,0,Norb)
-  iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf superc/nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    !superc 
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
-    i=i+1 
-    !...
-    iImpUp  = ibits(iup,0,Norb)
-    iImpDw  = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
-    iImp    = iImpUp  + iImpDw*(2**Norb)
-    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-%
-
-\subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
-$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
-
-\subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
-
-\subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_b$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
-The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
-spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
-$$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
-$$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
-dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
-= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
-\paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
-
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
-
-\paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
-
-\subsection{Lanczos based Diagonalization}\label{sSecHam}
-In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
-$$
-H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
-$$
-
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{HssNormal}
-\end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
-dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
-
-\subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
-sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
-\begin{equation}
-  \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
-  \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
-\begin{equation}\label{KLgf}
-  \begin{split}
-    C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
-    %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
-  \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
-\end{split}
-\end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
-$$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
-H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
-\begin{equation}
-  \label{eqGKrylov}
-  \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
-      |a^n_m|^2}{ z + (E_m-E_n)}\cr
-    %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
-  \end{split}
-\end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
-$$
-C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
-$$
-
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
-\equ{eqGKrylov}.  
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
-
-\paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
-
-The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
-
-\paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
-\begin{equation}
-  \label{GFnambu}
-  \hat{G}_{\a\b} =
-  \begin{bmatrix}
-    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
-  \end{bmatrix}  
-\end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
-$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
-
-\paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
-
-\subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-$$
-\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
-
-\paragraph{{\bf normal}}
-
-\paragraph{{\bf superc/nonsu2}}
-
-\subsection{Bath Functions}\label{sSecFunc}
-
-\subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
-supplied local functions  and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
-
-\subsection{Input/Output}\label{sSecIO}
-
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Conclusions}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section*{Acknowledgements}
-
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
-\end{document}

### 2025-04-09 03_edipack2.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-04 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[preprint,3p,10pt]{elsarticle}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
-
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage{xcolor}
-\usepackage{makecell}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-\usepackage[inline]{showlabels}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.~\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.~\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-
-\address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack2                                        \\
-{\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
-{\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
-{\em Nature of problem:}. \\
-{\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
-\section{Introduction and Motivation}\label{SecIntro}
-
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
-
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
-
-* zero and low finite temperatures
-
-* direct access to (well approximated) analytic dynamical functions
-
-* direct access to impurity Fock space quantities
-
-bla bla bla
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Structure and derived software}\label{SecStruct}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
-interface, which enables development of additional API or
-inter-operability with external libraries.
-
-\begin{itemize}
-\item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
-
-\item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
-
-\item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
-
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
-
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
-
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
-
-\end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
-
-\subsection{Dependencies}
-\NAME essentially depends on two external libraries.
-\begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
-\end{itemize}
-
-SciFortran provides a solid development platform enabling access to
-many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
-greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
-
-\subsection{Build and Install}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
-be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
-\end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
-
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake ..
-make -j
-make install
-\end{lstlisting}
-
-\item{\bf Ninja}
-
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
-
-\noindent
-The CMake configurations can be further tuned using the following variables:
-\begin{center}
-\begin{tabular}{ l|l|l } 
- \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
-  \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
- \hline
-\end{tabular}
-\end{center}
-
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
-CMake configuration step.
-
-\subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
-installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
-
-The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-\noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
-
-\subsection{OS Loading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
-directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
-
-We offer different strategies to perform this action:
-\begin{enumerate}
-\item  A CMake generated configuration file for environment module
-  which allows to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
-  permanently) in any shell session to add \NAME library to the
-  default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
-\end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
-
-\subsection{Python API}
-\subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
-pip install . 
-\end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
-
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
-
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-
-\subsection{TRIQS interface}
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/krivenko/edipack2triqs
-cd edipack2triqs
-pip install .
-\end{lstlisting}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
 \section{Implementation}\label{SecEDIpack}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Inequivalent impurities: EDIpack2Ineq}\label{SecIneq}
+\subsection{EDIpack2ineq: inequivalent impurities}\label{sSecIneq}
 It is often necessary to solve systems with several, independent,
@@
 
-\subsection{Structure}\label{sSecIneqStructure}
+\subsubsection{Structure}\label{ssSecIneqStructure}
 The sub-library is composed of a number of Fortran modules which are
@@
 
-\subsection{Core routines}\label{sSecIneqGlobal}
+\subsubsection{Core routines}\label{ssSecIneqGlobal}
 The module {\tt E2I\_MAIN} wraps the extensions to the main algorithms
@@
 
-\subsection{Inequivalent Baths}\label{sSecIneqBath}
+\subsubsection{Inequivalent Baths}\label{ssSecIneqBath}
 The inequivalent impurities extension is encoded in {\tt E2I\_BATH}
@@
 
-\subsection{Input/Output}\label{sSecIneqIO}
+\subsubsection{Input/Output}\label{ssSecIneqIO}
 A key part of the {\tt EDIpack2ineq} library is the extension for the
@@
 defined in \NAME.
-
-\section{C-bindings: EDIpack2C}\label{SecCbind}
-
-\section{Python API: EDIpy2}\label{SecPyAPI}
-
-\section{Triqs interface: EDIpack2Triqs}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface: EDIpack2w2dyn}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Conclusions and perspectives}
-\subsection{Conclusions}
-
-\subsection{Perspectives}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section*{Acknowledgements}
-
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
-\end{document}

### 2025-04-09 04_cbinding.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-02 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[final,3p,10pt]{elsarticle}
+\section{Interoperability}
+The recent growing availability of state-of-the-art software dedicated
+to the solution of quantum impurity problems using different methods
+poses a serious challenge to test accuracy and realiability of the
+results.
+As such, complex softwares are requested to develop a higher level of
+interoperability, i.e. the possibility to operate with other software
+possibly using different programming language.
+Modern Fortran, which is the language of choice for \NAME, since many
+years supports the standardized generation of procedures and
+variables that are interoperable with C.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{C-bindings}\label{sSecCbind}
+The interoperability with C language is encoded in the
+{\tt ISO\_C\_BINDING} module part of Fortran
+standard since 2003. The module contains definitions of named
+constants, types and procedures for C interoperability.
+Alongside, the second key feature essential to expose to C any Fortran
+entity is the {\tt BIND(C)} intrinsic function.
 
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
+\subsection{EDIpy, the Python API}\label{SecPyAPI}
 
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage{xcolor}
-\usepackage{makecell}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.~\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.~\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-
-\address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack2                                        \\
-{\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
-{\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
-{\em Nature of problem:}. \\
-{\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
-\section{Introduction and Motivation}\label{SecIntro}
-
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
-
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
-
-* zero and low finite temperatures
-
-* direct access to (well approximated) analytic dynamical functions
-
-* direct access to impurity Fock space quantities
-
-bla bla bla
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Structure and derived software}\label{SecStruct}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
-interface, which enables development of additional API or
-inter-operability with external libraries.
-
-\begin{itemize}
-\item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
-
-\item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
-
-\item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
-
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
-
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
-
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
-
-\end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
-
-\subsection{Dependencies}
-\NAME essentially depends on two external libraries.
-\begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
-\end{itemize}
-
-SciFortran provides a solid development platform enabling access to
-many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
-greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
-
-\subsection{Build and Install}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
-be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
-\end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
-
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake ..
-make -j
-make install
-\end{lstlisting}
-
-\item{\bf Ninja}
-
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
-
-\noindent
-The CMake configurations can be further tuned using the following variables:
-\begin{center}
-\begin{tabular}{ l|l|l } 
- \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
-  \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
- \hline
-\end{tabular}
-\end{center}
-
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
-CMake configuration step.
-
-\subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
-installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
-
-The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-\noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
-
-\subsection{OS Loading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
-directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
-
-We offer different strategies to perform this action:
-\begin{enumerate}
-\item  A CMake generated configuration file for environment module
-  which allows to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
-  permanently) in any shell session to add \NAME library to the
-  default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
-\end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
-
-\subsection{Python API}
 \subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
+EDIpy2 is available as a stand-alone
 module which depends on both \NAME and SciFortran. The package can be
@@
 
-\subsection{TRIQS interface}
+\subsection{TRIQS interface}\label{SecEDI2Triqs}
 A purely Python \NAME to Triqs interface is available, leveraging on
@@
 
-% ##################################################################
-% ##################################################################
-% ##################################################################
+\subsection{W2Dynamics interface}\label{SecEDI2W2Dyn}
 
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
-\section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
-
-\subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
-$$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
-$$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
-\begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
-    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
-    &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
-      \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
-\end{split}
-\end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
-The first three terms represent the density-density part of the
-interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The  remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
-\begin{equation}\label{Hbath}
-  \begin{split}
-    \hat{H}_{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
-    %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
-\end{split}
-\end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
-
-Finally, the electron-phonon part of the quantum impurity problems is
-described by the Hamiltonian terms: 
-\begin{equation}\label{Hph}
-  \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
-    % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
-\end{split}
-\end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$. 
-In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
-
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
-The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
-\subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
-The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
-The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
-\begin{align*}
-  c_{a\sigma}\ket{\vec{n}} &=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};\qquad
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-\end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
-
-\subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
-%
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
-\begin{table}%[ht]
-  \label{TabSector}
-\begin{center}
-\begin{tabularx}{\linewidth}{ |X|X|X| } 
- \hline
-  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
-  \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
-  \\
-  \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-  \\
-  \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
- \hline
-\end{tabularx}
-\end{center}
-\caption{Ciao}
-\end{table}
-
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i = i+1
-  H(iud)%map(i) = lup
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i = i+1
-  H(iud+Ns)%map(i) = Idw
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**N
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(Idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(Iup)
-    nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**Ns
-  enddo
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\begin{tabular}{c|c|c}\label{list1}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
-
-\subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
-
-\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-\subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
-\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
-given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
-
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
-$
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i=i+1 
-  !...
-  iImp  = ibits(iup,0,Norb)
-  iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i=i+1 
-  !...
-  iIMP  = ibits(idw,0,Norb)
-  iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf superc/nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    !superc 
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
-    i=i+1 
-    !...
-    iImpUp  = ibits(iup,0,Norb)
-    iImpDw  = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
-    iImp    = iImpUp  + iImpDw*(2**Norb)
-    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-%
-
-\subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
-$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
-
-\subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
-
-\subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_b$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
-The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
-spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
-$$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
-$$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
-dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
-= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
-\paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
-
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
-
-\paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
-
-\subsection{Lanczos based Diagonalization}\label{sSecHam}
-In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
-$$
-H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
-$$
-
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{HssNormal}
-\end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
-dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
-
-\subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
-sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
-\begin{equation}
-  \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
-  \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
-\begin{equation}\label{KLgf}
-  \begin{split}
-    C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
-    %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
-  \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
-\end{split}
-\end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
-$$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
-H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
-\begin{equation}
-  \label{eqGKrylov}
-  \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
-      |a^n_m|^2}{ z + (E_m-E_n)}\cr
-    %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
-  \end{split}
-\end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
-$$
-C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
-$$
-
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
-\equ{eqGKrylov}.  
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
-
-\paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
-
-The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
-
-\paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
-\begin{equation}
-  \label{GFnambu}
-  \hat{G}_{\a\b} =
-  \begin{bmatrix}
-    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
-  \end{bmatrix}  
-\end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
-$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
-
-\paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
-
-\subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-$$
-\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
-
-\paragraph{{\bf normal}}
-
-\paragraph{{\bf superc/nonsu2}}
-
-\subsection{Bath Functions}\label{sSecFunc}
-
-\subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
-supplied local functions  and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
-
-\subsection{Input/Output}\label{sSecIO}
-
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Conclusions}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section*{Acknowledgements}
-
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
-\end{document}
+\subsection{EDIjl, the Julia API}\label{SecJlAPI}

### 2025-04-09 05_examples.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-02 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[final,3p,10pt]{elsarticle}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
-
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage{xcolor}
-\usepackage{makecell}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.~\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.~\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
-\begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-
-\address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack2                                        \\
-{\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
-{\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
-{\em Nature of problem:}. \\
-{\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
-\section{Introduction and Motivation}\label{SecIntro}
-
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
-
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
-
-* zero and low finite temperatures
-
-* direct access to (well approximated) analytic dynamical functions
-
-* direct access to impurity Fock space quantities
-
-bla bla bla
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Structure and derived software}\label{SecStruct}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
-interface, which enables development of additional API or
-inter-operability with external libraries.
-
-\begin{itemize}
-\item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
-
-\item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
-
-\item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
-
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
-
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
-
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
-
-\end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
-
-\subsection{Dependencies}
-\NAME essentially depends on two external libraries.
-\begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
-\end{itemize}
-
-SciFortran provides a solid development platform enabling access to
-many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
-greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
-
-\subsection{Build and Install}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
-be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
-\end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
-
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake ..
-make -j
-make install
-\end{lstlisting}
-
-\item{\bf Ninja}
-
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
-
-\noindent
-The CMake configurations can be further tuned using the following variables:
-\begin{center}
-\begin{tabular}{ l|l|l } 
- \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
-  \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
- \hline
-\end{tabular}
-\end{center}
-
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
-CMake configuration step.
-
-\subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
-installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
-
-The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-\noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
-
-\subsection{OS Loading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
-directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
-
-We offer different strategies to perform this action:
-\begin{enumerate}
-\item  A CMake generated configuration file for environment module
-  which allows to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
-  permanently) in any shell session to add \NAME library to the
-  default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
-\end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
-
-\subsection{Python API}
-\subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
-pip install . 
-\end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
-
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
-
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-
-\subsection{TRIQS interface}
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/krivenko/edipack2triqs
-cd edipack2triqs
-pip install .
-\end{lstlisting}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
-\section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
-
-\subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
-$$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
-$$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
-\begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
-    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
-    &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
-      \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
-\end{split}
-\end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
-The first three terms represent the density-density part of the
-interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The  remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
-\begin{equation}\label{Hbath}
-  \begin{split}
-    \hat{H}_{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
-    %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
-\end{split}
-\end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
-
-Finally, the electron-phonon part of the quantum impurity problems is
-described by the Hamiltonian terms: 
-\begin{equation}\label{Hph}
-  \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
-    % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
-\end{split}
-\end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$. 
-In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
-
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
-The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
-\subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
-The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
-The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
-\begin{align*}
-  c_{a\sigma}\ket{\vec{n}} &=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};\qquad
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-\end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
-
-\subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
-%
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
-\begin{table}%[ht]
-  \label{TabSector}
-\begin{center}
-\begin{tabularx}{\linewidth}{ |X|X|X| } 
- \hline
-  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
-  \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
-  \\
-  \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-  \\
-  \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
- \hline
-\end{tabularx}
-\end{center}
-\caption{Ciao}
-\end{table}
-
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i = i+1
-  H(iud)%map(i) = lup
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i = i+1
-  H(iud+Ns)%map(i) = Idw
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**N
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(Idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(Iup)
-    nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**Ns
-  enddo
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\begin{tabular}{c|c|c}\label{list1}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
-
-\subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
-
-\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-\subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
-\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
-given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
-
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
-$
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i=i+1 
-  !...
-  iImp  = ibits(iup,0,Norb)
-  iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i=i+1 
-  !...
-  iIMP  = ibits(idw,0,Norb)
-  iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf superc/nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    !superc 
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
-    i=i+1 
-    !...
-    iImpUp  = ibits(iup,0,Norb)
-    iImpDw  = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
-    iImp    = iImpUp  + iImpDw*(2**Norb)
-    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-%
-
-\subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
-$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
-
-\subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
-
-\subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_b$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
-The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
-spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
-$$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
-$$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
-dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
-= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
-\paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
-
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
-
-\paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
-
-\subsection{Lanczos based Diagonalization}\label{sSecHam}
-In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
-$$
-H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
-$$
-
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{HssNormal}
-\end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
-dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
-
-\subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
-sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
-\begin{equation}
-  \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
-  \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
-\begin{equation}\label{KLgf}
-  \begin{split}
-    C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
-    %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
-  \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
-\end{split}
-\end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
-$$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
-H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
-\begin{equation}
-  \label{eqGKrylov}
-  \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
-      |a^n_m|^2}{ z + (E_m-E_n)}\cr
-    %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
-  \end{split}
-\end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
-$$
-C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
-$$
-
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
-\equ{eqGKrylov}.  
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
-
-\paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
-
-The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
-
-\paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
-\begin{equation}
-  \label{GFnambu}
-  \hat{G}_{\a\b} =
-  \begin{bmatrix}
-    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
-  \end{bmatrix}  
-\end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
-$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
-
-\paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
-
-\subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-$$
-\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
-
-\paragraph{{\bf normal}}
-
-\paragraph{{\bf superc/nonsu2}}
-
-\subsection{Bath Functions}\label{sSecFunc}
-
-\subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
-supplied local functions  and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
-
-\subsection{Input/Output}\label{sSecIO}
-
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
+\section{Examples}\label{SecExamples}
 \subsection{Bethe lattice DMFT (Fortran API)}
@@
 \subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Conclusions}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section*{Acknowledgements}
-
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
-\end{document}

### 2025-04-09 edipack2.tex
Updated structure of the .tex file. Start writing some 04_cbinding. WOrking on the 05_examples. Included now: C-binding Python API TRIQS W2Dyn Julia bonus: Monicelli... oh yeah

--- 2025-04-02 edipack2.tex
@@
 \title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a]{L.~Crippa}
+\author[a,b,c]{L.~Crippa}
 \author[a]{I.~Krivenko}
-\author[b]{S.~Giuli}
-\author[b]{G.~Bellomia}
-% \author[c]{A.~Scazzola}
-\author[d]{F.~Petocchi}
-\author[e]{G.~Mazza}
-% \author[f]{L.~de Medici}
-\author[b]{M.~Capone}
-\author[g]{A.~Amaricci}
+\author[d]{S.~Giuli}
+\author[d]{G.~Bellomia}
+\author[a,d,c,d,e,f,g,h,i]{...}
+% \author[]{A.~Scazzola}
+% \author[]{F.~Petocchi}
+% \author[]{A.~Kowalski}
+% \author[]{M.~Wallerberger}
+% \author[]{G.~Mazza}
+% \author[]{L.~de Medici}
+% \author[]{G.~Sangiovanni}
+% \author[]{M.~Capone}
+\author[i]{A.~Amaricci}
 
@@
 \address[a]{\ITPHamburg}
-% \address[b]{\CTQMAT}
-% \address[c]{\WZBURG}
-\address[b]{\SISSA}
-\address[c]{Politecnico di Torino, Turin, Italy}
-\address[d]{\Geneve}
-\address[e]{\UPISA}
-\address[f]{\ESPCI}
-\address[g]{\CNRIOM}
+\address[b]{\CTQMAT}
+\address[c]{\WZBURG}
+\address[d]{\SISSA}
+\address[e]{Politecnico di Torino, Turin, Italy}
+\address[f]{\Geneve}
+\address[g]{\UPISA}
+\address[h]{\ESPCI}
+\address[i]{\CNRIOM}
 % \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
@@
 
-\section{Introduction and Motivation}\label{SecIntro}
+\input{01_intro.tex}
+% ##################################################################
+% ##################################################################
+% ##################################################################
 
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
-
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
-
-* zero and low finite temperatures
-
-* direct access to (well approximated) analytic dynamical functions
-
-* direct access to impurity Fock space quantities
-
-bla bla bla
+\input{02_install.tex}
 
@@
 
-\section{Structure and derived software}\label{SecStruct}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C
-interface, which enables development of additional API or
-inter-operability with external libraries.
+\input{03_edipack2.tex}
 
-\begin{itemize}
-\item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
+\input{04_cbinding.tex}
 
-\item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
+\input{05_examples.tex}
 
-\item{\bf EDIpy2.}
-This is a simple Python module which provides Python API to the
-\NAME Fortran library. This interface is built around the Python
-support to C-types, which allows to import the dynamic C-binding
-library generated upon building \NAME. The module contains a specific
-class, whose methods mirrors through  duck-typing all the available
-procedures of \NAME as well as it gives access to relevant shared
-control variables.
-
-\item{\bf EDIpack2Triqs.}
-This is a thin interface layer from \NAME to Triqs,
-built around the Python API of the \NAME library. The exact
-diagonalization solver is encapsulated in a dedicated class,
-containing the necessary methods to initialize and run a single
-instance of the solver. The interface also includes a specific class
-encompassing the effective discretized bath structure as well as their 
-optimization methods.
-
-\end{itemize}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
-multi-platforms compabitility and dependencies resolution.  
-The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
-
-\subsection{Dependencies}
-\NAME essentially depends on two external libraries.
-\begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
-\end{itemize}
-
-SciFortran provides a solid development platform enabling access to
-many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
-greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
-
-\subsection{Build and Install}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
-be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
-\end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
-
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake ..
-make -j
-make install
-\end{lstlisting}
-
-\item{\bf Ninja}
-
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
-\begin{lstlisting}[style=mybash]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
-
-\noindent
-The CMake configurations can be further tuned using the following variables:
-\begin{center}
-\begin{tabular}{ l|l|l } 
- \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
-  \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
- \hline
-\end{tabular}
-\end{center}
-
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
-CMake configuration step.
-
-\subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
-installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
-
-The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-\noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
-
-\subsection{OS Loading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
-directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
-
-We offer different strategies to perform this action:
-\begin{enumerate}
-\item  A CMake generated configuration file for environment module
-  which allows to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
-  permanently) in any shell session to add \NAME library to the
-  default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
-\end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
-
-\subsection{Python API}
-\subsubsection{Build from source}
-EDIpy2, i.e. the Python API of EDIpack2, is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
-pip install . 
-\end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
-
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
-
-\begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack2
-\end{lstlisting}
-
-\subsection{TRIQS interface}
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
-
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/krivenko/edipack2triqs
-cd edipack2triqs
-pip install .
-\end{lstlisting}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-% $H_{e-ph}= \sum_{\a\sigma} g_\a
-% d^+_{\a\sigma}d_{\a\sigma}(b+b^+)$.
-
-\section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
-
-\subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
-$$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
-$$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
-\begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
-    \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
-    &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
-      \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
-\end{split}
-\end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
-The first three terms represent the density-density part of the
-interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The  remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
-\begin{equation}\label{Hbath}
-  \begin{split}
-    \hat{H}_{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
-    %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
-\end{split}
-\end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
-
-Finally, the electron-phonon part of the quantum impurity problems is
-described by the Hamiltonian terms: 
-\begin{equation}\label{Hph}
-  \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
-    % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
-\end{split}
-\end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$. 
-In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
-
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
-The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
-\subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
-The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
-The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
-\begin{align*}
-  c_{a\sigma}\ket{\vec{n}} &=
-    \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!-\!1,\dots}
-      &\text{if $n_{a\sigma}\!=\! 1$}\\
-      0 &\text{otherwise}
-    \end{cases};\qquad
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
-     \begin{cases}
-      (-1)^{\#_{a\sigma}}\ket{\dots,n_{a\sigma}\!+\!1,\dots}
-      & \text{if $n_{a\sigma}\!=\! 0$}\\
-      0 & \text{otherwise}
-    \end{cases}    
-\end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
-
-\subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
-%
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
-\begin{table}%[ht]
-  \label{TabSector}
-\begin{center}
-\begin{tabularx}{\linewidth}{ |X|X|X| } 
- \hline
-  {\tt ed\_mode} & {\it Quantum Numbers} & {\it Sector Dimension} \\
-  \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
-  \\
-  \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
-  \\
-  \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
- \hline
-\end{tabularx}
-\end{center}
-\caption{Ciao}
-\end{table}
-
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i = i+1
-  H(iud)%map(i) = lup
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i = i+1
-  H(iud+Ns)%map(i) = Idw
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**N
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(Idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(Iup)
-    nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
-    i=i+1
-    self%H(1)%map(i) = &
-        Iup+Idw*2**Ns
-  enddo
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\begin{tabular}{c|c|c}\label{list1}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
-
-\subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
-
-\subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-\subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
-\ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
-given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
-
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
-$
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf normal}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Iup=0,2**Nbit-1     
-  nup_ = popcnt(Iup) 
-  if(nup_ /= Nups(1))cycle
-  i=i+1 
-  !...
-  iImp  = ibits(iup,0,Norb)
-  iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
-enddo
-i=0
-do Idw=0,2**Nbit-1
-  ndw_= popcnt(Idw)
-  if(ndw_ /= Ndws(1))cycle
-  i=i+1 
-  !...
-  iIMP  = ibits(idw,0,Norb)
-  iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
-enddo
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
-    \center{\bf superc/nonsu2}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-i=0
-do Idw=0,2**Ns-1
-  ndw_= popcnt(idw)
-  do Iup=0,2**Ns-1
-    nup_ = popcnt(iup)
-    !superc 
-    sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
-    i=i+1 
-    !...
-    iImpUp  = ibits(iup,0,Norb)
-    iImpDw  = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
-    iImp    = iImpUp  + iImpDw*(2**Norb)
-    iBath   = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
-  enddo
-enddo
-
-\end{lstlisting}
-\end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-%
-
-\subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
-$E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
-
-\subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
-
-\subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_b$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
-The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
-spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
-$$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
-$$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
-dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
-= V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
-\paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
-
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
-
-\paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
-%   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
-
-\subsection{Lanczos based Diagonalization}\label{sSecHam}
-In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
-$$
-H_{\SS_{\vec{Q}}}\ket{v}=E_{\SS_{\vec{Q}}}\ket{v}.
-$$
-
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
-\label{HssNormal}
-\end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
-dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
-
-\subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
-sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
-\begin{equation}
-  \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
-  \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
-\begin{equation}\label{KLgf}
-  \begin{split}
-    C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
-    %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
-  \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
-\end{split}
-\end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
-$$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
-H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
-\begin{equation}
-  \label{eqGKrylov}
-  \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
-      |a^n_m|^2}{ z + (E_m-E_n)}\cr
-    %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
-  \end{split}
-\end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
-$$
-C_{\AA\BB} = \frac{1}{2}\left[C_\OO + C_\PP - (1-i)C_\AA -(1-i)C_\BB\right]
-$$
-
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
-\equ{eqGKrylov}.  
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
-
-\paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
-
-The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
-
-\paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
-\begin{equation}
-  \label{GFnambu}
-  \hat{G}_{\a\b} =
-  \begin{bmatrix}
-    G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
-  \end{bmatrix}  
-\end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
-$G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
-
-\paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
-
-\subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-$$
-\ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho_{imp}=Tr_{bath}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we proceed in three steps. 
-We use quantum numbers conservation which
-reduces extrema of the summation to the size $D_S$ of the sector $S$
-to which the groundstate belongs;
-Next we split the bits representation of any state $\ket{n}$ into
-their spin-dependent impurity and bath parts as $\ket{n} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
-The fast algorithm for the evaluation of the iRDM are outlined below
-for the two cases {\bf normal} and {\bf superc/nonsu2}.
-
-\paragraph{{\bf normal}}
-
-\paragraph{{\bf superc/nonsu2}}
-
-\subsection{Bath Functions}\label{sSecFunc}
-
-\subsection{Bath Optimization}\label{sSecFit}
-In the DMFT context the bath is updated using a suitable 
-optimization of the bath parameters against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b}(z)$, or the corresponding Delta function
-$\Delta_{\a\b}(z)= (z + \mu)\delta_{\a\b} - H^{loc}_{\a\b}-
-{\GG^{-1}_0}_{\a\b}(z)$, $z\in\CCC$, determined by the self-consistency procedure~\cite{Georges1996RMP}.
-This step corresponds to a projection of the Weiss
-field (or the Delta function) onto the space of the Anderson quantum
-impurity model functions
-$\GG^{And}_0(z) =
-[(z + \mu)\delta_{\a\b} - H^{loc}_{\a\b} -
-\Delta_{\a\b}(z)]^{-1}$, with $\Delta^{And}_{\a\b}(z)=\sum_\nu
-{V^\nu_{\a}}(z-h^\nu_{\a\b})^{-1}V^\nu_{\b}$, spanned by the
-variational paramaters $\{V,h\}$.
-
-This  optimization can be performed using different
-  algorithms~\cite{Garcia2004PRL,Taranto2012PRB}. 
-  In \NAME\ we offer to perform this task using a  
-conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}\sum_{\a\b}|X_{\a\b}(i\omega_n) - X_{\a\b}^{And}(i\omega_n;\{V,h\})|^q
-$$
-where $X_{\a\b}={\GG_{0}}_{\a\b},\,\Delta_{\a\b}$ are the user
-supplied local functions  and
-$X_{\a\b}^{And}={\GG_0}^{And}_{\a\b},\,\Delta^{And}_{\a\b}$ the
-Anderson impurity model function, defined above.
-The fit procedures are contains in the module \texttt{BATH\_FIT}.  
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-Given the importance of the fit for the convergence of DMFT calculations, in \NAME\ we
-introduced different specific control parameters. This aims to give
-the user the possibility of fine tuning the fit and adapt its behavior to
-specific situations.
-Two distinct CG algorithms can be used in the library, as controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. In order to guarantee
-back-compatibility with respect to the literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
-
-\subsection{Input/Output}\label{sSecIO}
-
-\section{Inequivalent impurities}
-
-\section{C-bindings}\label{SecCbind}
-
-\section{Python API}
-
-\section{Triqs interface}\label{SecEDI2Triqs}
-
-\section{W2Dynamics interface}\label{SecEDI2W2Dyn}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\section{Usage}\label{SecUsage}
-\subsection{Bethe lattice DMFT (Fortran API)}
-\subsection{Attractive Hubbard model (Python API)}
-\subsection{Multi-orbital Hubbard (Triqs)}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-% ##################################################################
-% ##################################################################
-% ##################################################################
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \section*{Acknowledgements}
+
+\section{Appendix A: Monicelli interface}
 

### 2025-04-10 02_install.tex
Updated draft. EDIpy2 to be completed. Next skip to examples.

@@
 
-\subsection{Structure}\label{SSecStruct}
+\subsection{Structure}\label{sSecInstallStructure}
 \NAME is a modular library which contains three principal structures.
@@
 
-\subsection{Dependencies}
+\subsection{Dependencies}\label{sSecInstallDependencies}
 \NAME essentially depends on two external libraries.
@@
 
-\subsection{Build and Install}
+\subsection{Build and Install}\label{sSecInstallBuildInstall}
 \subsubsection{Source}
@@
 
-\subsection{OS Loading}
+\subsection{OS Loading}\label{sSecInstallOSloading}
 In oder to avoid possible conflicts or require administrative

### 2025-04-10 04_cbinding.tex
Updated draft. EDIpy2 to be completed. Next skip to examples.

@@
-\section{Interoperability}
+\section{Interoperability}\label{SecInterop}
 The recent growing availability of state-of-the-art software dedicated
@@
 
-\subsection{C-bindings}\label{sSecCbind}
-The interoperability with C language is encoded in the
-{\tt ISO\_C\_BINDING} module part of Fortran
+\subsection{C-bindings}\label{sSecInteropCbindings}
+The interoperability with C language is provided by the
+{\tt ISO\_C\_BINDING} module, which is part of the Fortran
 standard since 2003. The module contains definitions of named
 constants, types and procedures for C interoperability.
-Alongside, the second key feature essential to expose to C any Fortran
+Alongside, a second key feature essential to expose to C any Fortran
 entity is the {\tt BIND(C)} intrinsic function.
+In \NAME we exploit these features of the language to provide a
+complete interface from the Fortran code to C/C++, i.e. {\tt
+  EDIpack2C}.
 
-\subsection{EDIpy, the Python API}\label{SecPyAPI}
+\subsubsection{Installation}\label{sSecInteropCbindingsInstallation}
+The C-binding module in included in the build process of \NAME and
+compiled into a dynamical library {\tt
+  libedipack2\_cbinding.so/.dylib}. As dicussed in the
+\secu{sSecInstallBuildInstall}, the support for inequivalent
+impurities is configured at the build level and propagates to the
+C-bindings library as well. An exported variable {\tt has\_ineq} is
+defined and export to C/C++ as a way to query the presence of
+inequivalent impurities support. 
+The generated library and header files get installed in the include
+directory at the prefix location, specified during configuration
+step. The corresponding path is added to the environment variable {\tt
+  LD\_LIBRARY\_PATH}, valid of any Unix/Linux system, via any of the
+loading methods outlines in \secu{sSecInstallOSloading}.
 
-\subsubsection{Build from source}
+\subsubsection{Implementation}\label{sSecInteropCbindingsImplementation}
+The interface layer is contained in the Fortran module {\tt
+  EDIpack2\_C}. This contains a common part and two set of functions,
+one to interface the procedures from \NAME and a second
+one to extend the interface to the inequivalent impurities case.
+Specifically, the implemented interface functions expose to C through
+{\tt bind(C)} statement a number of
+procedures composing the Fortran API of \NAME, i.e. contained in {\tt
+  ED\_MAIN}. The procedures and shared variables can be divided in four main groups:
+
+\paragraph{{\bf Variables}}
+A number of relevant input and shared variables which are normally
+required to setup or to control the calculation are interfaced to C
+directly in the \NAME modules {\tt ED\_INPUT\_VARIABLES} using {\tt
+  bind(C)} constructs. These are implicitly loaded into the C-binding module {\tt
+  EDIpack2\_C} through the Fortran {\tt USE EDIPACK2} statement and
+then further interfaced in the C++ header file.
+
+\paragraph{{\bf Main}} This group contains interface to the exact
+digonalization solver, interfacing the solver itself {\tt
+  solve\_site/ineq} as well as its initialization
+{\tt init\_solver\_site/ineq} and finalization {\tt
+  finalize\_solver} procedures. It also includes the functions used to
+set the non-interacting part of the impurity Hamiltonian
+$h^0_{\a\b\s\s'}$ through the functions {\tt set\_Hloc}.
+
+\paragraph{{\bf Bath}} In this group we implement a number of
+procedures dealing with bath initialization, symmetry operations and
+optimization. In particular it contains the function returning the
+dimension of the bath array on the user side {\tt
+  get\_bath\_dimension} as well as the setup of the matrix basis
+$\vec{\Gamma}$ for the replica/general bath via different instances of
+{\tt set\_Hreplica/general\_{site,lattice}\_d{3,5}}. 
+The crucial part in a DMFT framework is the optimization of the bath
+through conjugate-gradient algorithm. To this end we interfaced a
+number of functions {\tt
+  chi2\_fitgf\_{single,lattice}\_{normal,superc}\_n{3,4,5,6}} which
+cover all the cases supported in \NAME. Note that, because the actual
+optimization is still performed through the Fortran code, no changes
+apply to the outcome of this step.
+
+\paragraph{{\bf Input/Output}}
+The input and output part of the software is interfaced in this group
+of functions. In particular, {\tt read\_input} expose to C the input
+reading procedure of \NAME which set essentially set all the internal
+variables of \NAME.
+Next, in {\tt edipack{2ineq}\_c\_binding\_io} we interface all the
+functions implementing the communication from the \NAME instance to
+the user, namely those to retrieve static observables (e.g. {\tt
+  get\_dens}), the impurity Green's functions and self-energies
+(e.g. {\tt get\_Sigma\_{site,lattice}\_n{3,5}}), the
+impurity susceptibilities (e.g. {\tt get\_spinChi}), the impurity reduced density matrix as well
+as the non-interacting Green's and hybridization functions starting from the
+user bath array.
+
+Finally, in order to ensure compatibility to C and C++ language the
+entire set of C-binding functions and variables is enclosed into a
+header file {\tt edipack2\_cbinding.h}.
+
+% ##################################################################
+% ##################################################################
+
+\subsection{EDIpy2, the Python API}\label{sSecInteropEDIpy}
+As a first application of the \NAME C-bindings we implemented a
+complete Python interface, i.e. EDIpy2. This is a Python module which
+enables access to all the library features and unlock implementation of
+further interfaces of \NAME as a plug-in solver for external Python
+based software.
+
+\subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
 EDIpy2 is available as a stand-alone
-module which depends on both \NAME and SciFortran. The package can be
-obtained from the repository
+module which only depends on \NAME and SciFortran.
+The Python package can be obtained from the repository
 \href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
@@
 
-\subsubsection{Anaconda}
-As for EDIpack2, also the Python API in EDIpy2 are available through
-Anaconda packaging. In this case the resolution of the dependencies is
-taken care from Conda itself:
+\paragraph{PyPi}
+The EDIpy2 package is also available in PyPi at
+\href{https://pypi.org/project/edipy2/}{pypi.org/edipy2}. As such
+EDIpy2 can be conveniently installed in any system supporting {\tt pip} as:
 
+\begin{lstlisting}[style=mybash]
+pip install edipy2
+\end{lstlisting}
+
+\paragraph{Anaconda}
+As for \NAME, the Python API in EDIpy2 is available through
+Anaconda packaging for Unix/Linux systems. Packages are available for
+Python version $>3.10$. The EDIpack2.0 package contains the {\tt
+  edipy2} Python module as well as the EDIpack2.0 and SciFortran
+libraries. In this case the resolution of the dependencies is
+taken care from Conda itself. 
+Using conda the installation reads:
 \begin{lstlisting}[style=mybash]
@@
 
-\subsection{TRIQS interface}\label{SecEDI2Triqs}
+Once installed, any loading of the {\tt edipy2} module resolves in the
+attempt to load the dynamic library {\tt
+  libedipack2\_cbinding.so/.dylib} containing the Fortran-C bindings
+for \NAME. By default the library is searched proceeds as follow: 
+\begin{enumerate}
+\item First the user can override the location of the library
+  (determined during \NAME build configuration) by exporting an
+  environment variable called {\tt EDIPACK\_PATH} .
+\item By default, the Python module detects the position of the
+  Fortran libraries via {\tt pkg-config}. Any of the OS loading method
+  outlined in \secu{sSecInstallOSloading} automatically push the
+  correct configuration to the {\tt PKG\_CONFIG\_PATH}. 
+\item As a last resort the environment variables {\tt
+    LD\_LIBRARY\_PATH} and {\tt DYLD\_LIBRARY\_PATH} are analyzed to
+  retrieve the correct position. 
+\end{enumerate}
+If none of the previous attempts succeeds, the module will not not load correctly and an error message will be printed.
+
+\subsubsection{Implementation}\label{sSecInteropEDIpyImplementation}
+The Python API provided in the edipy2 module consists essentially of a
+suitable class called for convenience {\tt global\_env}.
+The class incorporates all the global variables inherited from \NAME
+C-bindings library and implements a number of interface functions
+leveraging the Python duck typing to \NAME.  
+The variables and the functions of \NAME are exposed to the user and
+are accessed as properties and
+methods of the {\tt global\_env} claass, which needs to be imported at the beginning
+of the python script, along with other useful modules. For instance Numpy is
+necessary, while mpi4py is strongly recommended.
+
+\begin{lstlisting}[language=python,  frame=lines]
+import numpy as np
+import mpi4py
+from mpi4py import MPI
+from edipy2 import global_env as ed
+import os,sys
+\end{lstlisting}
+
+The EDIpy2 supports the solution of problems with independent
+impurities, interfacing with the the EDIpack2ineq extension of the
+library, if present. Should the inequivalent impurities package not be
+built, the Python module silently disable the support to it, so that
+invoking any related procedure  will result in a {\tt RuntimeError}.
+The user can check the availability of the inequivalent impurities
+interface by querying the value of  {\tt edipy2.global\_env.has\_ineq}.
+
+The implementation of the Python API includes two main parts, namely
+the global variables and a number of functions.
+
+\paragraph{{\bf Global variables}}
+
+\paragraph{{\bf Functions}}
+
+% ##################################################################
+% ##################################################################
+
+\subsection{TRIQS interface}\label{sSecInteropTRIQS}
+{\color{red} Igor }
 A purely Python \NAME to Triqs interface is available, leveraging on
@@
 
-\subsection{W2Dynamics interface}\label{SecEDI2W2Dyn}
+\subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
+{\color{red} Giorgio, Alexander,?}
 
-\subsection{EDIjl, the Julia API}\label{SecJlAPI}
+\subsection{EDIjl, the Julia API}\label{sSecInteropEDIjl}
+{\color{red} Lorenzo?}

### 2025-04-12 04_cbinding.tex
Draft update. Completed EDIpy2. Moving to Examples, leaving behind other interfaces.

@@
 
-The implementation of the Python API includes two main parts, namely
-the global variables and a number of functions.
+The implementation of the Python API is divided in two main parts. The
+first is a set of global variables, the second includes 4 groups of
+functions: solver, bath, input/output, auxiliary.
 
 \paragraph{{\bf Global variables}}
+This includes a subset of the input variables available in \NAME which
+are used to control the calculation.
+The variables are loaded globally in {\tt EDIpy2} and can be accessed
+or set locally as properties of the class {\tt
+  global\_env}. Differently these are initialized, alongside the remaining
+default input variables, through a call to procedure {\tt
+  edipy2.global\_env.read\_input} which interface the {\tt
+  ed\_read\_input} function in \NAME. 
+A given example is reported in the following code extract:
 
-\paragraph{{\bf Functions}}
+\begin{lstlisting}[language=python,  frame=lines]
+import numpy as np
+from edipy2 import global_env as ed
+ed.Nspin = 1            # set a global variable
+mylocalvar = ed.Nspin   # assign to a local variable
+print(ed.Nspin)         # all functions can have global variables as arguments
+np.arange(ed.Nspin)
+\end{lstlisting}
+
+\paragraph{{\bf Solver functions}}
+This group includes a number of functions enabling initialization,
+execution and finalization  functionalities for the diagonalization
+solver.
+\begin{itemize}
+  \item {\tt init\_solver} and {\tt set\_Hloc}. The first 
+    initializes the \NAME environment for the quantum impurity problem
+    solution, sets the effective bath either reading it from a file or
+    initializing it from flat band model. Once this function is
+    called, it is not possible to allocate a second instance of the solver.
+    {\tt set\_Hloc} sets the
+    non-interacting part of the impurity Hamiltonian $\h^0_{\a\b\s\s'}$. 
+    Either function take different argument combinations there
+    including support for inequivalent impurities.
+
+  \item {\tt solve} This function solves the quantum impurity problem,
+    calculates the observables and any dynamical correlation
+    function. All results remain stored in the memory and get accessed
+    through input/output functions.
+
+  \item {\tt finalize\_solver} This function cleans up the \NAME
+    environment, free the memory deallocating all relevant arrays or
+    data structure. A call to this functions enables a new
+    initialization of the solver, i.e. a new call to {\tt
+      init\_solver}.  
+  \end{itemize}
+
+\paragraph{{\bf Bath functions}}
+This set covers the implementation of utility functions handling the
+effective bath on the user side as well as interfaces to specific
+\NAME procedures, either setting bath properties or applying
+conventional symmetry transformation. Here we discuss 
+a pair of crucial functions in this group.
+\begin{itemize}
+\item {\tt bath\_inspect}This function translates between the
+  user-accessible continuous bath array and the bath components
+  (energy level, hybridization and so on). It functions in both ways,
+  given the array returns the components and vice-versa. It
+  autonomously determines the type of bath and ED mode.
+
+\item {\tt chi2\_fitgf}
+  This function fits the Weiss field or Hybridization function (delta)
+  with a discrete set of level. The fit parameters are the bath
+  parameters contained in the user-accessible array. Depending on the
+  type of system we are considering (normal, superconductive,
+  non-SU(2)) a different set of inputs has to be passed. The specifics
+  of the numerical fitting routines are controlled in the input file.
+  \end{itemize}
+
+Additionally, the group includes the function {\tt
+  get\_bath\_dimension}, returning the correct
+dimension for the user bath array to be allocated and {\tt
+  set\_H{replica/general}} which set the matrix basis
+$\vec{\Gamma}$ and init the bath variational parameters
+$\vec{\lambda}$ for {\tt bath\_type=replica,general}.
+
+\paragraph{{\bf Input/Output functions}}
+This group includes functions which return to the userspace
+observables or dynamical correlation functions evaluated in \NAME and
+conserved in the corresponding memory instance. Each function
+provides a general interface which encompass all dimension of the
+input array there including inequivalent impurities support.
+For instance, the function {\tt get\_sigma} returns the self-energy
+function array (evaluated on-the-fly) for a specified supported shape,
+normal or anomlous type and on a specific axis or frequency domain.
+
+\paragraph{{\bf Auxiliary functions}}
+This group include some auxiliary functions, either interfacing \NAME
+procedures or defined locally in Python to provide specific new
+functionalities. Among the latter we include {\tt get\_ed\_mode} which
+return the value of the variable {\tt ed\_mode=normal,superc,nosu2}
+and {\tt get\_bath\_type} which similarly returns the value of {\tt bath\_type}.
 

### 2025-04-13 05_examples.tex
Updated draft. Start Examples. Bethe first.

@@
 \section{Examples}\label{SecExamples}
+In this section we illustrate the functioning of the \NAME
+library and their interfaces through specific examples, including
+discussion of relevant code snippets.
+Specifically, we show how the quantum impurity solver in \NAME can be used
+to address problems of different nature within the framework of DMFT.
+
 \subsection{Bethe lattice DMFT (Fortran API)}
+The description of the Mott or metal to insulator transition (MIT)
+within the Bethe lattice, i.e. Cayley tree with connection
+$z\to\infty$ is conventionally considered the test bed of any DMFT
+application. Here  we discuss a guided implementation based on the
+Fortran API of \NAME of the DMFT solution of the Bethe lattice at
+$T=0$.
+
+We consider a Fermi-Hubbard model:
+$$
+H = -t \sum_{\langle ij\rangle\s}c^+_{i\s}c_{j\s} + U \sum_i n_{i\up}n_{i\dw}
+$$
+defined on a Bethe lattice with density of states
+$\rho(x)=\frac{1}{2D}\sqrt{D^2-x^2}$, where $D=2t$ is the
+half-bandwidth.
+
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{figures/figBethe.pdf}
+    \caption{\label{fig1}%
+        \textbf{The Mott transition.}
+        }
+\end{figure}
+
 \subsection{Attractive Hubbard model (Python API)}

### 2025-04-13 edipack2_examples/Bethe_EDIpack/data/script_figBethe.py

@@ -1,0 +1,206 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+    
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 24})
+plt.rcParams['figure.figsize'] = [21, 10]
+
+
+fig = plt.figure()
+
+
+
+##################################################################
+ax  = plt.gca()
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U1.00/Gloc_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U2.00/Gloc_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U2.50/Gloc_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
+rho4 = np.genfromtxt('U2.75/Gloc_realw.dat',skip_header=0);x4=rho4[:,0];y4=-rho4[:,1]/np.pi
+rho5 = np.genfromtxt('U3.00/Gloc_realw.dat',skip_header=0);x5=rho5[:,0];y5=-rho5[:,1]/np.pi
+
+dos=dens_bethe(x1,1.0)
+
+ax.set_xlim([-3, 3])
+ax.set_ylim([0.00, 4.25])
+ax.set_xlabel(r'$\omega$')
+ax.set_ylabel(r'$-{\rm Im}G(\omega)/\pi$')
+ax.yaxis.set_tick_params(labelleft=False)
+ax.set_yticks([])
+
+ax.tick_params(length=6, width=2,direction='out')
[…]

### 2025-04-13 edipack2_examples/Bethe_EDIpack/data/script_figBethe_2.py

@@ -1,0 +1,197 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+
+def zimS(x,z):
+  y = (1.0-1.0/z)*x#-1/z*x
+  return y
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 24})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    """
+)
+
+
+axs["A"].text(0.94, 0.04, r"(a)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.94, 0.04, r"(b)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.94, 0.04, r"(c)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U1.00/Gloc_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U2.00/Gloc_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U2.50/Gloc_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
[…]

### 2025-04-14 05_examples.tex
Update. Start drafting Examples:AHM, getting data Fortan and Python (thanks Lorenzo Crippa)
co-authored-by: Lorenzo Crippa <lcrippa@gmail.com>

@@
 $T=0$. 
-
 We consider a Fermi-Hubbard model:
@@
 $\rho(x)=\frac{1}{2D}\sqrt{D^2-x^2}$, where $D=2t$ is the
-half-bandwidth.
+half-bandwidth~\cite{Georges1996}.
+In DMFT this model is mapped
+onto a quantum impurity problem with an effective electronic bath
+which needs to be determined self-consistently.
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+program ed_hm_bethe
+   USE EDIPACK2
+   USE SCIFOR
+   implicit none
+   !> Number of discretization points for the Bethe DOS
+   integer,parameter                           :: Le=5000
+   !> Bethe half-bandwidth = energy unit
+   real(8),parameter                           :: D=1d0
+   !>Bath:
+   real(8),allocatable                         :: Bath(:)
+   !> local dynamical functions, rank-5 [Nspin,Nspin,Norb,Norb,L]
+   complex(8),allocatable,dimension(:,:,:,:,:) :: Weiss,Smats,Sreal,Gmats,Greal,Weiss_
+   ... (omissis)
+   !> READ THE input using EDIpack procedure:
+   call ed_read_input(trim(finput))
+   !
+   !> Setup the Bethe DOS $\rho$ (linear dispersion)
+   Ene = linspace(-D,D,Le,mesh=de)
+   DOS = dens_bethe(Ene,D)
+\end{lstlisting}
+
+The bath is described
+by the (unknown) function $\GG^{-1}_0$, i.e. the Weiss field. Within \NAME
+exact diagonalization approach, where the bath is approximated with a
+finite number of levels, the function $\GG^{-1}_0$ is used to
+determine bath parameters $\vec{x}=\{V,h\}$ using the optimization method discussed in
+\secu{sSecFit}.
+The starting point of any calculation is determined by a suitable
+guess of the Weiss field, or equivalently of the bath parameters.
+In \NAME this operations is accomplished by the function {\tt
+  ed\_init\_solver}.
+
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+Nb=ed_get_bath_dimension()
+allocate(bath(Nb))
+call ed_init_solver(bath)
+\end{lstlisting}
+
+The iterative algorithm proceeds as follows:
+\begin{enumerate}
+\item Call the exact diagonalization {\bf impurity solver} {\tt
+    ed\_solve} whose only input is the set of parameters $\vec{x}$. All other
+  options are controlled by input file specifications ({\tt
+    ed\_read\_input}).
+\item Retrieve at least the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
+  Matsubara axis using {\tt ed\_get\_sigma}.
+\item Evaluate the local interacting Green's function
+  $G_{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
+  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
+  \item Update the Weiss field through the {\bf self-consistency}
+    relation: $\GG^{-1}_0(i\omega) = G_{loc}(i\omega) + \Sigma(i\omega)$. 
+  \item Optimize the bath parameters $\vec{x}$ against the updated
+    Weiss field using, for instance, {\tt ed\_chi2\_fitgf}. Restart at 1.
+\end{enumerate}
+In agreement with Reverse Communication Strategy setup, the step 3-4
+are left to the user. In addition step 5 is kept separated to
+guarantee enough freedom in the bath optimization, though we remark
+this is a crucial step which can potentially compromise the whole
+calculation.
+An example of implementation is given in the following listings.
+
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+iloop=0;converged=.false.
+   do while(.not.converged.AND.iloop<nloop)
+     iloop=iloop+1     
+     !> Solve the effective impurity problem
+     call ed_solve(bath)     
+     !> Retrieve impurity Self-energy on Matsubara axis
+     call ed_get_sigma(Smats,'m')
+     !
+     !> Build a local Green's function:
+     wfreq = pi/beta*(2*arange(1,Lmats)-1)   !automatic Fortran allocation
+     do i=1,Lmats ! One can do better than this of course 
+        zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
+        Gmats(1,1,1,1,i) = sum(DOS(:)/( zeta-Ene(:) ))*de  
+     enddo
+     !> Update Weiss field: Self-consistency
+     Weiss(1,1,1,1,:) = one/(one/Gmats(1,1,1,1,:) + Smats(1,1,1,1,:))
+     !> Close the self-consistency fitting the new bath:
+     call ed_chi2_fitgf(Weiss,bath,ispin=1)     
+     !>Check convergence
+     converged =( sum(abs(Weiss(1,1,1,1,:)-Weiss_(1,1,1,1,:)))/sum(abs(Weiss(1,1,1,1,:))) )<dmft_error
+     Weiss_=Weiss     
+   enddo
+\end{lstlisting}
+
+\subsubsection{Results}
+In the following we present some results obtained by executing this
+simple program varying the interaction strenght :f:var:`uloc`.
+Differently from the previous case of a quantum impurity embedded in a
+given bath describing the progressive formation of a
+strongly renormalized Fermi liquid state, here the DMFT
+self-consistency allows to describe the transition from a correlated
+metal to a Mott insulating state.
+
+To illustrate this point, in panel **A** we report the evolution of
+the spectral function $-{\rm Im}G(\omega)/\pi$ as a function of
+$U$. Despite the *spiky* nature of the spectrum, due to the
+finite size (i.e. number of poles) of the discretized effective bath,
+one can clearly distinguish the renormalization of the central
+quasi-particle peak at low-energy and the concomitant formation of
+rather incoherent  high-energy features which will develop into
+Hubbard bands for $U>U_c$, with $U_c\simeq 2.8D$.
 
@@
 
+In the panels (B) and (C) we further discuss the metal-insulator
+transition by showing the evolution of the self-energy functions.
+In panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
+on the Matsubara axis in the low energy regime. Increasing $U$
+we observe the progressive growth of this function until it takes a
+diverging behavior crossing the critical interaction strenght. We
+recall that this behavior can be observed on the Matsubara axis
+because of the particle-hole symmetry of the problem.
+
+Using the relation:
+
+$$
+   \frac{\Im\Sigma(i\omega_n)}{\omega_n}_{|_{\omega_n\rightarrow 0}}=
+   \frac{1}{\pi}\int_{\mathbb R}d\epsilon \frac{\Re\Sigma(\epsilon)}{\epsilon^2}=
+   \frac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow 0}}.
+$$
+we can extract the quasi-particle renormalization constant :math:`Z`
+from the linear behavior of ${\rm Im}\Sigma(i\omega)$ near
+$\omega=0$ in the metallic regime. The results are highlighted
+in the figure and the values of $Z$ are reported in the legend.
+
+Using the right hand side of the previous relation, we show in
+panel (C) the behavior of  ${\rm Re}\Sigma(\omega)$
+on the real axis around the Fermi level. Again, increasing $U$
+we observe the slope of the linear behavior to increase until the
+critical point is crossed and an insulating state is reached. On the
+real-axis this is signaled by the divergence of the imaginary part of
+the self-energy   ${\rm Im}\Sigma(\omega) \rightarrow -\infty$
+near the chemical potential, which here is set to zero by
+particle-hole symmetry. The corresponding real part shows a
+discontinuity visibile in the panel (C).
+
 \subsection{Attractive Hubbard model (Python API)}
+The second application has the twofold aim to demonstrate the
+superconductivity support of the \NAME library as well as to
+illustrate the Python API through a working example.
+
 \subsection{Multi-orbital Hubbard (Triqs)}
+
+\subsection{Some model (W2Dynamics)}
+
+\subsection{Interacting Bernevig-Hughes-Zhang (Fortran)}

### 2025-04-14 edipack2_examples/AHM_EDIpack2EDIpy/Python/ahm.py

@@ -1,0 +1,125 @@
+import numpy as np
+from edipy2 import global_env as ed
+import mpi4py
+from mpi4py import MPI
+import os,sys
+from aux_funx import *
+
+#INIT MPI 
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+print("I am process",rank,"of",comm.Get_size())
+master = (rank==0)
+
+#Functions
+
+
+def generate_kgrid(Nk):
+    b1=2*np.pi*np.array([1.0,0.0])
+    b2=2*np.pi*np.array([0.0,1.0])
+    n1, n2 = np.meshgrid(np.arange(Nk), np.arange(Nk))
+    n1=n1/Nk
+    n2=n2/Nk
+    gridout = np.stack([n1.ravel(), n2.ravel()], axis=-1)
+    return np.dot(gridout,[b1,b2])
+
+def h_square2d(k,t):
+  return -2*t*(np.cos(k[...,0,np.newaxis,np.newaxis])+np.cos(k[...,1,np.newaxis,np.newaxis]))*np.eye(ed.Norb)
+
+def test_dos(hk,plot=False):
+    result=np.histogram(hk[:,0,0], bins=100, density=True) #normalized to one, I will have to multiply
+    dx=result[1][2]-result[1][1]
+    np.savetxt('dos.dat', np.transpose([np.delete(np.add(result[1],dx/2),np.size(result[1])-1), result[0]]))
+    
+    if plot:
+        plt.xlabel('E')
+        plt.ylabel("D(E)")
+        plt.xlim(-3,3)
+        plt.ylim(0,1)
+        plt.plot(np.delete(np.add(result[1],dx/2),np.size(result[1])-1), result[0])
+        plt.show()
+    
+
+#READ ED INPUT:
+ed.read_input("inputAHM.conf")
+
+
+#Parameters
+wmixing = 0.5
+try:
+    Nk = int(sys.argv[1])
+except:
+    Nk=30
+    
+print(ed.Uloc)
+t_hop = 0.25
+
+#BUILD frequency arrays and k grid:
+wm = np.pi/ed.beta*(2*np.arange(ed.Lmats)+1)
+wr = np.linspace(ed.wini,ed.wfin,ed.Lreal,dtype=complex)
+
+kgrid = generate_kgrid(Nk)
+
+
+#Generate hk and hloc
[…]

### 2025-04-28 05_examples.tex
Updated draft. * added a section of parse_Umatrix (to be written) * drafting attractive HM, figure loaded.

@@
 
-\subsection{Bethe lattice DMFT (Fortran API)}
+\subsection{Bethe lattice DMFT (Fortran API)}\label{SecExamplesBetheDMFT}
 The description of the Mott or metal to insulator transition (MIT)
@@
 $$
-defined on a Bethe lattice with density of states
+where $c^+_{i\s}$ ($c_{i\s}$) is the creation (destruction) operator for an electron at site $i$
+and with spin $\s$, $n_{i\s}=c^+_{i\s}c_{i\s}$ is the occupation
+operator and the first sum is over the nearest neighbor sites $\langle
+ij\rangle$. 
+The system is defined on a Bethe lattice with density of states
 $\rho(x)=\frac{1}{2D}\sqrt{D^2-x^2}$, where $D=2t$ is the
@@
 
-\subsubsection{Results}
+\paragraph{Results}
 In the following we present some results obtained by executing this
@@
 
-\subsection{Attractive Hubbard model (Python API)}
+\subsection{Attractive Hubbard model (Python API)}\label{SecExamplesAHM}
 The second application has the twofold aim to demonstrate the
 superconductivity support of the \NAME library as well as to
-illustrate the Python API through a working example.
+illustrate the use of the Python API through a working example.
+We consider the simple, yet non-trivial, case of the attractive
+Hubbard model on a two-dimensional square lattice:
+
+$$
+H = \sum_{\ka\s} \e(\ka)c^+_{\ka\s}c_{\ka\s} -U\sum_i n_{i\up}n_{i\dw}
+$$
+where $U>0$, $c^+_{\ka\s}=\tfrac{1}{\sqrt{N}}\sum_i e^{-i\ka\cdot R_i} c^+_{i\s}$
+and $c^+_{i\s}$ is the creation operator for an electron at site $i$
+and with spin $\s$, $n_{i\s}=c^+_{i\s}c_{i\s}$ is the occupation
+operator and $\e(\ka)=-2t[\cos{(k_x a)}+ \cos{(k_y a)}]$ is the
+energy dispersion relation. In the following we the lattice distance
+$a=1$  and the energy unit as $4t=D=1$.
+
+The DMFT workflow for this case is very similar to the previous one
+provided works in the Nambu basis defined by the spinor
+$\psi_i=[c_{i\up}, c^+_{i\dw}]^t$.
+In this basis any correlation functions, e.g. the Green's function, takes the matrix form:
+\begin{equation}
+  G =
+  \begin{pmatrix}
+    \hat{G}_{\uparrow\uparrow} & \hat{F}_{\uparrow\downarrow}\\
+    \hat{\bar{F}}_{\downarrow\uparrow}  &    \hat{\bar{G}}_{\downarrow\downarrow} \\
+   \end{pmatrix}
+\end{equation}
+where the symbol $\hat{A}$ indicates the possible multi-orbital
+character which reduced to a scalar in the present case of a single
+orbital. The symbol $\hat{\bar{A}}$ indicates that the components in
+the second row are connect by particle-hole and time-reversal
+symmetries to the first row one. The specific relation depends on the
+symmetry of the order parameter (here $s$-wave) and the nature of the
+complex argument of the functions, i.e. Matsubara or real-axis:
+\begin{equation}
+\begin{array}{cc}
+  \hat{\bar{G}}(i\omega) = -\hat{G}^*(i\omega)\;; &  \hat{\bar{F}}(i\omega) = \hat{F}(i\omega)\\
+  \hat{\bar{G}}(\omega)  = -\hat{G}^*(-\omega) \;; & \hat{\bar{F}}(\omega) = \hat{F}^*(i\omega)\\
+\end{array}
+\end{equation}  
+The code implementation closely follows the previous structure, with
+some notable exceptions related to the Nambu structure for which,
+using the symmetries above, we only need to deal with the first row
+independent components. In the first part of the code we initialize
+the lattice structure and the solver:
+\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
+import numpy as np
+from edipy2 import global_env as ed
+import mpi4py
+from mpi4py import MPI
+import os,sys
+from aux_funx import * #include function to build $G_{loc}$ and Weiss fields
+
+comm = MPI.COMM_WORLD
+rank = comm.Get_rank()
+master = (rank==0)
+
+#Functions
+def generate_kgrid(Nk):
+    b1=2*np.pi*np.array([1.0,0.0])
+    b2=2*np.pi*np.array([0.0,1.0])
+    n1, n2 = np.meshgrid(np.arange(Nk), np.arange(Nk))
+    n1=n1/Nk;n2=n2/Nk
+    gridout = np.stack([n1.ravel(), n2.ravel()], axis=-1)
+    return np.dot(gridout,[b1,b2])
+
+def h_square2d(k,t):
+  return -2*t*(np.cos(k[...,0,np.newaxis,np.newaxis])+np.cos(k[...,1,np.newaxis,np.newaxis]))*np.eye(ed.Norb)
+
+ed.read_input("inputAHM.conf")
+
+kgrid = generate_kgrid(Nk)
+
+#Generate hk and hloc
+Hk   = h_square2d(kgrid,t_hop)
+HkNambu   = np.array([h_square2d(kgrid,t_hop),-np.conj(h_square2d(-kgrid,t_hop))])
+Hloc = np.sum(Hk,axis=0)/Nk**2
+Hloc = Hloc.astype(complex)
+ed.set_hloc(Hloc)
+
+#SETUP SOLVER
+Nb=ed.get_bath_dimension()
+bath = ed.init_solver()
+bath_prev = np.copy(bath)
+\end{lstlisting}
+
+The iterative scheme for the solution of DMFT closely follows the
+sequence discussed in \secu{SecExamplesBetheDMFT}:   
+\begin{enumerate}
+\item Call the exact diagonalization {\bf impurity solver} {\tt
+    ed\_solve} providing the set of parameters $\vec{x}$ as input. 
+\item Retrieve the self-energy functions
+  $\hat{\Sigma}_{\a\b\up\up}(i\omega)$ and $\hat{S}_{\a\b\up\dw}(i\omega)$ on the 
+  Matsubara axis using {\tt ed\_get\_sigma}.
+\item
+  Evaluate the interacting local Green's functions $\hat{G}_{loc}$ and
+  $\hat{F}_{loc}$:
+  \begin{equation}
+  G_{loc}(i\omega) =
+  \int_\RRR d\e \rho(\e)
+  \begin{pmatrix}
+    (i\omega +\mu)\hat{\11} - \hat{h}^0 - \hat{\Sigma}(i\omega) -\e & -\hat{S}(i\omega) \\
+    -\hat{S}(i\omega) & (i\omega +\mu)\hat{\11} + \hat{h}^0 +
+    \hat{\Sigma}^*(i\omega) +\e\\
+  \end{pmatrix}^{-1}
+\end{equation}
+\item Update the normal and anomalous Weiss fields, respectively 
+  $\GG^{-1}$ and $\Theta^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
+    relation: $\GG^{-1}_0(i\omega) = G_{loc}(i\omega) +
+    \Sigma(i\omega)$ in Nambu space. 
+  \item Optimize the bath parameters $\vec{x}$ to best describe the  updated
+    Weiss fields. 
+\end{enumerate}
+which is implemented in Python as follows:
+\begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
+#DMFT CYCLE
+converged=False;iloop=0
+while (not converged and iloop<ed.Nloop ):
+    iloop=iloop+1
+    #Solve the EFFECTIVE IMPURITY PROBLEM (first w/ a guess for the bath)
+    ed.solve(bath)
+    print(ed.get_phi())
+
+    #Use aux_funx procedures:
+    Smats = np.array([ed.get_sigma(axis="m",typ="n"),ed.get_sigma(axis="m",typ="a")])    
+    Gmats = get_gloc(wm*1j       ,ed.xmu,HkNambu,Smats,axis="m") 
+    Weiss = dmft_weiss_field(Gmats,Smats)
+
+    #Print...
+
+    #Fit
+    bath = ed.chi2_fitgf(Weiss[0],Weiss[1],bath)
+
+    if(iloop>1):
+        bath = wmixing*bath + (1.0-wmixing)*bath_prev
+    bath_prev=np.copy(bath) 
+    err,converged=ed.check_convergence(Weiss,ed.dmft_error)
+
+ed.finalize_solver()
+\end{lstlisting}
+
+\paragraph{Results}
+We showcase here some results for the attractive Hubbard model to
+illustrate the capabilities of \NAME to solve $s$-wave superconducting
+impurity problems at zero and finite temperatures. 
+In figure...
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
+    \caption{\label{fig2}%
+      \textbf{The BCS to BEC crossover.}
+      (a) Evolution of the spectral functions
+      $-\Im{G_{loc}(\omega)}/\pi$ as a function of increasing
+      attraction $U$. 
+      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
+      function of the attraction $U$. Data for BCS (gray) is compared
+      to DMFT results (blue line and symbols). 
+      (c) The correlation strength
+      $\Theta=\frac{|S(0)-S(\infty)|}{S(\infty)}$ as a function of the
+      attraction $U$ across the BCS-BEC crossover. 
+      (d) Comparison of the double occupation $D=\langle n_\up
+      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
+      solid line) and DMFT (blue solid line and symbols). 
+      (e) Superconducting order
+      parameter $\phi$ as a function of temperature across the
+      superconductor-to-normal phase transition. Data for $U=4$. The
+      fit highlights the critical behavior with a mean-field exponent
+      $\beta=1/2$ (red dashed line).       
+        }
+\end{figure}
 

### 2025-04-28 edipack2_examples/AHM_EDIpack2EDIpy/Python/ahm.py

@@ -12,8 +12,6 @@ print("I am process",rank,"of",comm.Get_size())
 master = (rank==0)
 
 #Functions
-
-
 def generate_kgrid(Nk):
     b1=2*np.pi*np.array([1.0,0.0])
     b2=2*np.pi*np.array([0.0,1.0])

### 2025-04-28 edipack2_examples/AHM_EDIpack2EDIpy/data/script_figAHM.py

@@ -1,0 +1,164 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+
+
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 24})
+plt.rcParams['figure.figsize'] = [35, 15]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    AADE
+    """
+)
+
+
+axs["A"].text(0.02, 0.98, r"(a)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.02, 0.98, r"(b)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.02, 0.98, r"(c)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+axs["D"].text(0.02, 0.98, r"(d)",transform=axs["D"].transAxes,fontsize=24, va='top', color='black')
+axs["E"].text(0.94, 0.98, r"(e)",transform=axs["E"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U0.6/Gloc_i1_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U1.0/Gloc_i1_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U1.5/Gloc_i1_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
+rho4 = np.genfromtxt('U2.0/Gloc_i1_realw.dat',skip_header=0);x4=rho4[:,0];y4=-rho4[:,1]/np.pi
[…]

### 2025-04-28 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_2d.f90

@@ -7,7 +7,7 @@ program ed_ahm_2d
   real(8),parameter                         :: D=1
   integer                                   :: iloop,i
   integer                                   :: Nb,Nso
-  logical                                   :: converged
+  logical                                   :: converged,get_sigma
   !Bath:
   real(8),allocatable,dimension(:)          :: Bath,Bath_Prev
   !The local functions:
@@ -26,6 +26,7 @@ program ed_ahm_2d
   !
   call parse_cmd_variable(finput,"FINPUT",default='inputAHM.conf')
   call parse_input_variable(wmixing,"wmixing",finput,default=0.5d0,comment="Mixing bath parameter")
+  call parse_input_variable(get_sigma,"get_sigma",finput,default=.false.)
   !
   call ed_read_input(trim(finput))
 
@@ -52,7 +53,7 @@ program ed_ahm_2d
   allocate(Sreal(2,Nso,Nso,Lreal))
 
 
-  
+
   !> Allocate the 2d DOS and dispersion for the Nambu structure in DMFT_TOOLS
   !  we ask for separate dispersions (or two H(k)) for the two elements on the diagonal
   allocate(Edos(2,1,Le))  
@@ -64,14 +65,26 @@ program ed_ahm_2d
   enddo
   Ddos= Ddos/simps(Ddos(1,:),-D,D)*de
 
-  
+
   !> Get local Hamiltonian (used in DMFT_TOOLS)
-  allocate(H0(2,1))
+  allocate(H0(2,Nso))
   H0=0d0
+  call ed_set_Hloc(zeros(Nso,Nso))
 
 
 
+  if(get_sigma)then
+     call ed_get_sigma(Smats(1,:,:,:),axis='m',type='n')
+     call ed_get_sigma(Smats(2,:,:,:),axis='m',type='a')
+     call write_gf(Smats(1,:,:,:),"Sigma",axis='mats',iprint=1)
+     call write_gf(Smats(2,:,:,:),"Self",axis='mats',iprint=1)
+     stop
+  end if
 
+  
+
+
+  
   !> Get bath dimension and allocate user bath to this size
   Nb=ed_get_bath_dimension()
   allocate(Bath(Nb))
@@ -79,7 +92,6 @@ program ed_ahm_2d
 
   !> Initialize the ED solver (bath is guessed or read from file) 
   call ed_init_solver(bath)
-
 
   !DMFT loop
   iloop=0;converged=.false.

### 2025-04-28 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_square.f90

@@ -1,0 +1,220 @@
+program ed_ahm_square
+  USE EDIPACK2
+  USE SCIFOR
+  USE DMFT_TOOLS
+  USE MPI
+  implicit none
+  integer                                       :: iloop,Lk,Nso,Nambu,Nno
+  logical                                       :: converged
+  !Bath:
+  integer                                       :: Nb,Nsym
+  real(8),allocatable                           :: Bath(:),Prev(:)
+  real(8),dimension(:,:),allocatable            :: LambdaVec
+  complex(8),dimension(:,:,:),allocatable       :: Hsym_basis
+  !variables for the model:
+  integer                                       :: Nx,Nkpath
+  real(8)                                       :: delta,lambda,wmixing,ts,alpha,D
+  character(len=16)                             :: finput
+  logical                                       :: phsym,normal_bath
+  !The local hybridization function:
+  complex(8),allocatable                        :: Hloc(:,:)
+  complex(8),allocatable,dimension(:,:,:,:,:,:) :: Gmats,Greal,Smats,Sreal,Weiss
+  complex(8),allocatable                        :: Hk(:,:,:,:)
+  !MPI
+  integer                                       :: comm,rank
+  logical                                       :: master
+
+
+  call init_MPI()
+  comm = MPI_COMM_WORLD
+  call StartMsg_MPI(comm)
+  rank = get_Rank_MPI(comm)
+  master = get_Master_MPI(comm)
+
+
+
+  call parse_cmd_variable(finput,"FINPUT",default='inputED.conf')
+  call parse_input_variable(Nsym,"NSYM",finput,default=2,comment="2: diagonal SC; 3: diag+off-diag SC")
+  call parse_input_variable(ts,"TS",finput,default=0.5d0,comment="hopping parameter")
+  call parse_input_variable(alpha,"ALPHA",finput,default=1d0,comment="bandwidth ratio t_2 = alpha*t_1")
[…]

### 2025-04-30 05_examples.tex
Updated AHM. Should we include 2orbital with replica bath? why not...

@@
 
-\subsection{Bethe lattice DMFT (Fortran API)}\label{SecExamplesBetheDMFT}
+\subsection{Bethe lattice DMFT}\label{SecExamplesBetheDMFT}
 The description of the Mott or metal to insulator transition (MIT)
@@
 In the following we present some results obtained by executing this
-simple program varying the interaction strenght :f:var:`uloc`.
+simple program varying the interaction strenght $U$. 
 Differently from the previous case of a quantum impurity embedded in a
@@
   \includegraphics[width=\linewidth]{figures/figBethe.pdf}
-    \caption{\label{fig1}%
-        \textbf{The Mott transition.}
+    \caption{\label{figEx1}%
+      \textbf{The Metal-Insulator Mott transition.}
+      (a) Evolution of the spectral function $-\Im{G}(\omega)/\pi$ as
+      a function of increasing interaction $U$. The critical
+      interaction $U_c\simeq 2.8D$ separates the correlated metal $U<U_c$ from
+      the Mott insulator $U>U_c$.
+      (b)-(c) The corresponding evolution of the Matsubara self-energy
+      $\Im\Sigma(i\omega)$ (b) and
+      real-axis one $\Re\Sigma(\omega)$ across the Mott
+      transition. For a particle-hole symmetric case both allow to
+      estimate the renormalization constant $Z$ (see main text), using
+      linear order expansion in frequency (blue solid lines). The
+      values of $Z$ are reported in the legend.
+      The Mott insulating solution is associated to a singularity at
+      $\omega=0$ of $\Im\Sigma$. 
         }
@@
 \begin{equation}
-  G =
+  {\mathbf G} =
   \begin{pmatrix}
@@
 \item Call the exact diagonalization {\bf impurity solver} {\tt
-    ed\_solve} providing the set of parameters $\vec{x}$ as input. 
-\item Retrieve the self-energy functions
-  $\hat{\Sigma}_{\a\b\up\up}(i\omega)$ and $\hat{S}_{\a\b\up\dw}(i\omega)$ on the 
-  Matsubara axis using {\tt ed\_get\_sigma}.
+    ed.solve} providing the set of bath parameters as input. 
+\item Using the dedicated
+  input/output procedures {\tt ed.get\_sigma} we retrieve the self-energy functions  
+  $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
+  Matsubara axis.
 \item
@@
   \begin{equation}
-  G_{loc}(i\omega) =
+  {\mathbf G}_{loc}(i\omega) =
   \int_\RRR d\e \rho(\e)
@@
 \item Update the normal and anomalous Weiss fields, respectively 
-  $\GG^{-1}$ and $\Theta^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
-    relation: $\GG^{-1}_0(i\omega) = G_{loc}(i\omega) +
-    \Sigma(i\omega)$ in Nambu space. 
-  \item Optimize the bath parameters $\vec{x}$ to best describe the  updated
-    Weiss fields. 
+  $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
+    relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_{loc}(i\omega) +
+    {\mathbf \Sigma}(i\omega)$ in Nambu space. 
+  \item Optimize the bath parameters  to best describe the  updated
+    Weiss fields using \NAME provided conjugate gradient  fit
+    procedure {\tt ed.chi2\_fitgf}.
 \end{enumerate}
@@
 iloop=iloop+1
-    #Solve the EFFECTIVE IMPURITY PROBLEM (first w/ a guess for the bath)
+
+    #Solve impurity problem
     ed.solve(bath)
-    print(ed.get_phi())
 
-    #Use aux_funx procedures:
+    #Self-consistency with aux_funx procedures:
     Smats = np.array([ed.get_sigma(axis="m",typ="n"),ed.get_sigma(axis="m",typ="a")])    
@@
 
-    #Print...
-
     #Fit
@@
 
-    if(iloop>1):
-        bath = wmixing*bath + (1.0-wmixing)*bath_prev
-    bath_prev=np.copy(bath) 
+    #Error check
     err,converged=ed.check_convergence(Weiss,ed.dmft_error)
@@
 \paragraph{Results}
-We showcase here some results for the attractive Hubbard model to
-illustrate the capabilities of \NAME to solve $s$-wave superconducting
-impurity problems at zero and finite temperatures. 
-In figure...
+We showcase here some results for the DMFT solution of the attractive
+Hubbard model across the BCS to BEC regime, with the aim of
+illustrating the capabilities of \NAME to deal with $s$-wave
+superconductivity at zero and finite temperatures.
+
+To beging with, we report in  panel (A) of \figu{figEx2} the
+evolution of the spectral density, obtained from the local normal
+Green's function $-\tfrac{1}{\pi}\Im{G}_{loc}(\omega)$, as a function
+of the attraction $U$. For any finite value of  $U$ the Van Hove peak
+at $\omega=0$ of the 2D square lattice (see $U=0$
+solution) gets split by the formation of a superconductive gap of
+width which increases with $U$.
+The existence of a gap is associated to the formation of a finite
+order parameter $\phi=\langle c_\up c_\dw\rangle$. The behavior of
+this quantity, shown in panel (B), highlights crossover from the BCS
+regime at weak coupling to a BEC one for large $U$.
+The former regime is characterized by the well known exponential increase of
+$\phi$, which is computationally the hardest regime to adress. At
+strong coupling or BEC regime the order parameter saturates to its
+limiting value $\phi\to 1/2$. The comparison with mean-field result
+(gray) underlines the effect of local quantum fluctuations in slightly
+suppressing the order parameter. This effect is particularly active in
+the intermediate regime, as captured by the behavior of the
+correlation strength
+$\theta=\frac{|S(i\omega\to9)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
+reported in panel (C). Assuming a monotonic behavior of the anomalous
+self-energy function, this quantity estimates the ``strength'' of
+quantum fluctuations comparing the mean-field-like behavior at high
+energy scale with that near the Fermi level. A large value of $\theta$
+indicates a more correlated system.
+Our results show that both weak and strong coupling regime are
+relatively weakly correlated, i.e. very near a mean-field solution. On
+the contrary, the inter-mediate regime is characterized by a large
+correlation, making the solution very different from that obtained in
+BCS description.  
+To further corroborate the distance between the DMFT and mean-field
+solution we report in panel (D) the evolution of the double occupancy
+$d=\langle n_\up n_\dw\rangle$. At half-filling the mean-field value is
+determined solely by the order parameter as $d=1/4 + \phi^2$.
+Our results show that the inclusion of quantum fluctuations in DMFT
+slightly increase the value of $d$ in the weak coupling
+regime. However, increasing the attraction the double occupations
+quickly get reduced below the mean-field value up to the BEC regime.
+
+Finally, we illustrate the capability of \NAME in
+exploring finite temperature physics. In panel (E) we show the
+temperature evolution of the order parameter $\phi(T)$ across the
+superconductor-to-normal transition. The mean-field nature of this
+transition is underlined by the scaling of  the solution near
+the critical point $\phi \simeq (T_c-T)^\beta$ with $\beta=1/2$ as
+predicted by mean-field calculations.
+
 \begin{figure}[t!]
   \includegraphics[width=\linewidth]{figures/figAHM.pdf}
-    \caption{\label{fig2}%
+    \caption{\label{figEx2}%
       \textbf{The BCS to BEC crossover.}
@@
       (c) The correlation strength
-      $\Theta=\frac{|S(0)-S(\infty)|}{S(\infty)}$ as a function of the
+      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
       attraction $U$ across the BCS-BEC crossover. 
@@
       fit highlights the critical behavior with a mean-field exponent
-      $\beta=1/2$ (red dashed line).       
+      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_c=0.61$.       
         }

### 2025-04-30 edipack2_examples/AHM_EDIpack2EDIpy/data/script_figAHM.py

@@ -27,11 +27,11 @@ axs = plt.figure(layout="constrained").subplot_mosaic(
 )
 
 
-axs["A"].text(0.02, 0.98, r"(a)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
-axs["B"].text(0.02, 0.98, r"(b)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
-axs["C"].text(0.02, 0.98, r"(c)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
-axs["D"].text(0.02, 0.98, r"(d)",transform=axs["D"].transAxes,fontsize=24, va='top', color='black')
-axs["E"].text(0.94, 0.98, r"(e)",transform=axs["E"].transAxes,fontsize=24, va='top', color='black')
+axs["A"].text(0.02, 0.98, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.02, 0.98, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.02, 0.98, r"(C)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+axs["D"].text(0.02, 0.98, r"(D)",transform=axs["D"].transAxes,fontsize=24, va='top', color='black')
+axs["E"].text(0.94, 0.98, r"(E)",transform=axs["E"].transAxes,fontsize=24, va='top', color='black')
 
 
 
@@ -44,12 +44,12 @@ rho2 = np.genfromtxt('U1.0/Gloc_i1_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rh
 rho3 = np.genfromtxt('U1.5/Gloc_i1_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
 rho4 = np.genfromtxt('U2.0/Gloc_i1_realw.dat',skip_header=0);x4=rho4[:,0];y4=-rho4[:,1]/np.pi
 rho5 = np.genfromtxt('U3.0/Gloc_i1_realw.dat',skip_header=0);x5=rho5[:,0];y5=-rho5[:,1]/np.pi
-
+dos = np.genfromtxt('DOS2d.dat',skip_header=0);xdos=dos[:,0];ydos=dos[:,1]
 
 ax.set_xlim([-2.5, 2.5])
 ax.set_ylim([0.00, 12])
 ax.set_xlabel(r'$\omega$')
[…]

### 2025-04-30 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_2d.f90

@@ -65,6 +65,7 @@ program ed_ahm_2d
   enddo
   Ddos= Ddos/simps(Ddos(1,:),-D,D)*de
 
+  call splot("DOS2d.dat",Edos(1,1,:),Ddos(1,:)/de)
 
   !> Get local Hamiltonian (used in DMFT_TOOLS)
   allocate(H0(2,Nso))

### 2025-05-02 05_examples.tex
Updated draft
- use subfiles, so we can compile in every subfile
- written something re. umatrix
- updated gitignore
Revised MIT section. No multi-band attractive with replica bath -> directly to interacting BHZ + replica for triplet exctions.

@@
 The system is defined on a Bethe lattice with density of states
-$\rho(x)=\frac{1}{2D}\sqrt{D^2-x^2}$, where $D=2t$ is the
+$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$, where $D=2t$ is the
 half-bandwidth~\cite{Georges1996}.
@@
 \paragraph{Results}
-In the following we present some results obtained by executing this
-simple program varying the interaction strenght $U$. 
-Differently from the previous case of a quantum impurity embedded in a
-given bath describing the progressive formation of a
-strongly renormalized Fermi liquid state, here the DMFT
-self-consistency allows to describe the transition from a correlated
-metal to a Mott insulating state.
+In the following we present some results obtained for the model
+introduced above. Specifically we focus on the testbed case of the interaction
+driven Mott transition, descriving the progressive
+transformation of a partially-filled band metallic state into a correlated insulator.
 
-To illustrate this point, in panel **A** we report the evolution of
-the spectral function $-{\rm Im}G(\omega)/\pi$ as a function of
-$U$. Despite the *spiky* nature of the spectrum, due to the
+To illustrate this point, we report in panel (A) the evolution of
+the spectral function $-{\rm Im}G_{loc}(\omega)/\pi$ as a function of
+the interaction strenght $U$. Despite the {\it spiky} nature of the spectrum, due to the
 finite size (i.e. number of poles) of the discretized effective bath,
-one can clearly distinguish the renormalization of the central
-quasi-particle peak at low-energy and the concomitant formation of
-rather incoherent  high-energy features which will develop into
-Hubbard bands for $U>U_c$, with $U_c\simeq 2.8D$.
+it is possible to clearly distinguish the characteristic features of
+the Mott transition. At low energy, we observe the renormalization of the 
+quasi-particle peak at the Fermi level ($\omega=0$). Concomitantly the
+system shows the formation of incoherent  high-energy features which
+will then develop into Hubbard bands in the Mott insulating state for $U>U_c$, with $U_c\simeq 2.8D$.
 
@@
 
-In the panels (B) and (C) we further discuss the metal-insulator
-transition by showing the evolution of the self-energy functions.
-In panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
+The formation of a spectral gap separating the Hubbard bands in the
+Mott insulator is supported by the divergence, at the Fermi level, of the imaginary part of
+the self-energy function. Causality imposes that the real-part of
+this quantity becomes large near the singularity making it impossible
+to satisfy the quasi-particles poles equations
+$\omega+\mu-h^0-\e-\Re{\Sigma}(\omega)=0$, i.e. preventing coherent
+quasi-particles excitations near the Fermi level. 
+In the panels (B) and (C) we discuss this point  showing the evolution
+of the self-energy functions $\Sigma$.
+Specifically, in panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
 on the Matsubara axis in the low energy regime. Increasing $U$
-we observe the progressive growth of this function until it takes a
-diverging behavior crossing the critical interaction strenght. We
-recall that this behavior can be observed on the Matsubara axis
-because of the particle-hole symmetry of the problem.
+we observe the progressive growth of this function until a
+diverging behavior is acheived crossing the critical interaction
+strenght $U>U_c$.
+We recall that this behavior can be observed on the Matsubara axis
+because of the particle-hole symmetry of the problem which pins the
+$\Im{\Sigma}$ singularity at $\omega=0$.
+In panel (C), we report the corresponding behavior of the
+$\Re{\Sigma}(\omega)$ in small energy regime around the Fermi
+level. Augmenting the interaction strength $U$ leads to a sudden
+increase of this self-energy component until a discontinuous behavior
+is reached, associated to the divergence of the corresponding
+imaginary part.
 
+A quantitative description of the transition is obtained from the
+quasi-particle renormalization constant $Z$, which correlates with the degree of
+localization of the electrons being equal to 1 for a non-interacting
+metal and 0 for the Mott insulator. This quantity is obtained from the
+linear term in the Fermi liquid expansion of the self-energy as
+$Z=(1-\tfrac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow
+    0}})^{-1}$.
 Using the relation:
-
 $$
@@
 $$
-we can extract the quasi-particle renormalization constant :math:`Z`
-from the linear behavior of ${\rm Im}\Sigma(i\omega)$ near
-$\omega=0$ in the metallic regime. The results are highlighted
-in the figure and the values of $Z$ are reported in the legend.
+we can extract $Z$ also from the linear behavior of ${\rm Im}\Sigma(i\omega)$ for 
+$\omega\to0$ in the metallic regime.
 
-Using the right hand side of the previous relation, we show in
-panel (C) the behavior of  ${\rm Re}\Sigma(\omega)$
-on the real axis around the Fermi level. Again, increasing $U$
-we observe the slope of the linear behavior to increase until the
-critical point is crossed and an insulating state is reached. On the
-real-axis this is signaled by the divergence of the imaginary part of
-the self-energy   ${\rm Im}\Sigma(\omega) \rightarrow -\infty$
-near the chemical potential, which here is set to zero by
-particle-hole symmetry. The corresponding real part shows a
-discontinuity visibile in the panel (C).
+The linear fit highlighted in the panels (B)-(C) and the corresponding values of $Z$ are reported in the legend.
+In both cases we observe that increasing $U$ the slope of the linear behavior of the
+self-energy at low-energy increases upon increasing $U$, either on the
+Matsubara or real-axis. At the transition point the slope becomes
+infinite according to the divergence of the imaginary part of
+the self-energy  ${\rm Im}\Sigma(\omega) \rightarrow -\infty$,
+corresponding to $Z\to 0$.
 
@@
 \item Call the exact diagonalization {\bf impurity solver} {\tt
-    ed.solve} providing the set of bath parameters as input. 
+    ed.solve} providing the set of bath parameters $\vec{x}=\{V,h\}$  as input. 
 \item Using the dedicated
@@
     {\mathbf \Sigma}(i\omega)$ in Nambu space. 
-  \item Optimize the bath parameters  to best describe the  updated
+  \item Optimize the bath parameters $\vec{x}$ to best describe the  updated
     Weiss fields using \NAME provided conjugate gradient  fit
@@
 
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
+    \caption{\label{figEx2}%
+      \textbf{The BCS to BEC crossover.}
+      (a) Evolution of the spectral functions
+      $-\Im{G_{loc}(\omega)}/\pi$ as a function of increasing
+      attraction $U$. 
+      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
+      function of the attraction $U$. Data for BCS (gray) is compared
+      to DMFT results (blue line and symbols). 
+      (c) The correlation strength
+      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
+      attraction $U$ across the BCS-BEC crossover. 
+      (d) Comparison of the double occupation $D=\langle n_\up
+      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
+      solid line) and DMFT (blue solid line and symbols). 
+      (e) Superconducting order
+      parameter $\phi$ as a function of temperature across the
+      superconductor-to-normal phase transition. Data for $U=4$. The
+      fit highlights the critical behavior with a mean-field exponent
+      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_c=0.61$.       
+        }
+\end{figure}
+
 \paragraph{Results}
@@
 correlation strength
-$\theta=\frac{|S(i\omega\to9)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
+$\theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
 reported in panel (C). Assuming a monotonic behavior of the anomalous
@@
 
-\begin{figure}[t!]
-  \includegraphics[width=\linewidth]{figures/figAHM.pdf}
-    \caption{\label{figEx2}%
-      \textbf{The BCS to BEC crossover.}
-      (a) Evolution of the spectral functions
-      $-\Im{G_{loc}(\omega)}/\pi$ as a function of increasing
-      attraction $U$. 
-      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
-      function of the attraction $U$. Data for BCS (gray) is compared
-      to DMFT results (blue line and symbols). 
-      (c) The correlation strength
-      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
-      attraction $U$ across the BCS-BEC crossover. 
-      (d) Comparison of the double occupation $D=\langle n_\up
-      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
-      solid line) and DMFT (blue solid line and symbols). 
-      (e) Superconducting order
-      parameter $\phi$ as a function of temperature across the
-      superconductor-to-normal phase transition. Data for $U=4$. The
-      fit highlights the critical behavior with a mean-field exponent
-      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_c=0.61$.       
-        }
-\end{figure}
-
 \subsection{Multi-orbital Hubbard (Triqs)}

### 2025-05-02 edipack2_examples/Bethe_EDIpack/data/script_figBethe.py

@@ -13,20 +13,38 @@ def dens_bethe(x,d):
   dens_bethe=(2/(np.pi*d))*root
   return dens_bethe.real
 
-    
+
+
+def zimS(x,z):
+  y = (1.0-1.0/z)*x#-1/z*x
+  return y
+
+
 plt.rcParams["font.family"] = "Times"
 plt.rcParams['text.usetex'] = True
 plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
 plt.rcParams.update({'font.size': 24})
-plt.rcParams['figure.figsize'] = [21, 10]
+plt.rcParams['figure.figsize'] = [35, 10]
 
 
 fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    """
+)
+
+
+axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.94, 0.04, r"(C)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+
+
 
 
 
 ##################################################################
-ax  = plt.gca()
+ax=axs["A"]
 
 print("Read Data DOS")
 rho1 = np.genfromtxt('U1.00/Gloc_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
@@ -59,34 +77,14 @@ ax.plot(x4    ,  y4+3*s    ,  lw=5, ls='solid',  c=c[3], label=r"$U=2.75$")
 ax.plot(x5    ,  y5+4*s    ,  lw=5, ls='solid',  c=c[4], label=r"$U=3.00$")
 
 ax.legend(loc='upper center', fontsize = '22', handlelength=1.5, framealpha=1,ncol=6);
-
-plt.savefig("figBetheDOS.pdf", bbox_inches='tight')
-plt.clf()
-plt.cla()
-plt.close()
 ##################################################################
 
 
 
 
 
-def zimS(x,z):
-  y = (1.0-1.0/z)*x#-1/z*x
-  return y
-
-
-axs = plt.figure(layout="constrained").subplot_mosaic(
-    """
-    AB
-    """
-)
-
[…]

### 2025-05-02 edipack2_examples/Bethe_EDIpack/data/script_figBethe_2.py

@@ -1,197 +1,0 @@
-import numpy as np
-import matplotlib.image as image
-import matplotlib.pyplot as plt
-from scipy.interpolate import griddata
-import pandas as pd
-import sys
-from matplotlib.colors import LinearSegmentedColormap
-from scipy import optimize
-
-def dens_bethe(x,d):
-  root=(1-(x/d)**2)+0.j
-  root=np.sqrt(root)
-  dens_bethe=(2/(np.pi*d))*root
-  return dens_bethe.real
-
-
-
-def zimS(x,z):
-  y = (1.0-1.0/z)*x#-1/z*x
-  return y
-
-
-plt.rcParams["font.family"] = "Times"
-plt.rcParams['text.usetex'] = True
-plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
-plt.rcParams.update({'font.size': 24})
-plt.rcParams['figure.figsize'] = [35, 10]
-
-
-fig = plt.figure()
-axs = plt.figure(layout="constrained").subplot_mosaic(
-    """
-    AABC
-    """
-)
-
-
-axs["A"].text(0.94, 0.04, r"(a)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
-axs["B"].text(0.94, 0.04, r"(b)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
-axs["C"].text(0.94, 0.04, r"(c)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
-
-
-
-
-
-##################################################################
-ax=axs["A"]
-
-print("Read Data DOS")
-rho1 = np.genfromtxt('U1.00/Gloc_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
-rho2 = np.genfromtxt('U2.00/Gloc_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
-rho3 = np.genfromtxt('U2.50/Gloc_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
[…]

### 2025-05-02 03_edipack2.tex
Updated draft. * added a section of parse_Umatrix (to be written) * drafting attractive HM, figure loaded.

@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Implementation}\label{SecEDIpack}
@@
 impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assuming for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian reads: 
+phonons. 
 \begin{equation}\label{Himp}
@@
     \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-    %
+\end{split}
+\end{equation}
+
+We assume for the moment that no particular symmetry
+holds. The impurity part of the Hamiltonian can, in principle, consist of any set of
+two-body quantum operators of the form $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
+
+A set of such operators is the celebrated Hubbard-Kanamori Hamiltonian:
+
+\begin{equation}\label{Hint}
+  \begin{split}
     \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
@@
       \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
-    % 
 \end{split}
@@
 apply\_Cops} functions within {\tt ED\_SECTORS}.
+
+\subsection{Interaction setup}
+\NAME offers two distinct ways to setup the interaction term in \equ{Himp}. 
+The Hubbard-Kanamori interaction \equ{Hint} is supported natively, via the user-accessible
+variables {\tt ULOC}$=U$, {\tt UST}$=U^{'}$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP
+}$=J_{p}$.These parameters can be specified in the input file, and they will be read and 
+set if the flag {\tt ED\_USE\_KANAMORI} is set to {\tt T}. This is the default option.
+If the interaction Hamiltonian is provided via {\tt ED\_USE\_KANAMORI}, {\tt NORB} is limited to a maximum of {\tt 5}.
+
+Alternatively, the list of two-body operators can be provided by the user in a properly
+formatted text file, the name of which is specified in the {\tt UMATRIX\_FILE} input variable. The file has to have the suffix {\tt \\.restart}.
+Such file needs to be formatted in the following way
+
+\begin{lstlisting}[style=mybash]
+NORB BANDS
+i1 j1 k1 l1 U_i1j1k1l1
+i2 j2 k2 l2 U_i2j2k2l2
+...
+\end{lstlisting}
+
+where {\tt NORB} is the numer of orbitals.
+Empty lines and lines starting with {\tt \#, \%, !} are ignored.
+Notice the swapped indices in the coefficient with respect to the standard 2-body operator formulation $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
+To enable reading an interaction matrix file, the flag {\tt ED\_READ\_UMATRIX} needs to be set in the input file.
+{\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI} are mutually exclusive, but they can be both false.
+Before the impurity problem is solved, the used can also provide interaction terms in the program or script. Extensive documentation is available at (\textcolor{red}{how should we do this?})
+All the interaction operators used in each call of the solver are listed and written in an output file. called {\tt UMATRIX\_FILE.used}.
 
@@
 defined in \NAME.
+
+\end{document}

### 2025-05-05 03_edipack2.tex
Fix a few compilation issues > mostly related to missing or duplicated bib entries

@@
 \paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{amaricci2022}, the inclusion of local phonons with
+\onlinecite{Amaricci2022}, the inclusion of local phonons with
 truncated dimensions ultimately amounts to a sequential application of
@@
 this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{KM} or
-in-plane spin-triplet exciton condensation~\cite{ExcitonPRB,Amaricci,Blason}.  
+$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{BellomiaKMH} or
+in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
 %
@@
 discussion about Fock basis organization in this case see
-\onlinecite{amaricci2022}.
+\onlinecite{Amaricci2022}.
 
@@
   normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{amaricci2022}.
+the product structure of the sector and its map~\cite{Amaricci2022}.
 The analysis of the spectrum is then reconducted to the inspection of
@@
 time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{amaricci2022} we covered in full details
+algorithms. In \onlinecite{Amaricci2022} we covered in full details
 some distrubuted memory massively parallel algorithms to address this
 specific issue.
-Here, using the same naming convention introduced in \cite{amaricci}, 
+Here, using the same naming convention introduced in \cite{Amaricci2022}, 
 we briefly outline the main strategy for the implementation of the MVP
@@
 The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{amaricci2022}, requires the
+which, as discussed in \onlinecite{Amaricci2022}, requires the
 reconstruction of the distributed input array any node producing a
@@
 
+%GBtodo placeholder: revise this subsection
 \subsection{Reduced impurity density matrix}\label{sSecRDM}
 This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), enabling the analysis of
+impurity Reduced Density Matrix (iRDM), extending the algorithm introduced in \onlinecite{BellomiaPhD} so to enable the analysis of
 entanglement properties of the quantum impurity for any value of {\tt
@@
 can choose between different norm defition.
+{\color{red} I (GB) can take care of this, as I introduced the "elemental" norm in the code.}
+%GBtodo placeholder
 

### 2025-05-05 edipack2.tex
Updated draft. * added a section of parse_Umatrix (to be written) * drafting attractive HM, figure loaded.
Updated AHM. Should we include 2orbital with replica bath? why not...
Updated draft
- use subfiles, so we can compile in every subfile
- written something re. umatrix
- updated gitignore
Fix a few compilation issues > mostly related to missing or duplicated bib entries
Few typos

@@
 \usepackage{makecell}
-
+\usepackage{array}
 \usepackage{stackengine}
@@
 \usepackage{makecell}
+\usepackage{subfiles}
 
@@
   language=fortran,
+  basicstyle=\footnotesize,
+  stringstyle=\ttfamily,
+  commentstyle=\itshape,
+  fontadjust=true,
+  keywordstyle=\color{red},
+  % morekeywords={*,...},
+  mathescape,
+  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
+}
+
+\lstdefinestyle{mypython}{
+  frame=lines,
+  language=python,
   basicstyle=\footnotesize,
@@
 \usepackage{ltablex}
+
+\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
 
@@
 \newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
+\newcommand{\TUW}{Institure of Solid State Physics, TU Wien, 1040 Vienna, Austria}
 
@@
 \address[d]{\SISSA}
-\address[e]{Politecnico di Torino, Turin, Italy}
-\address[f]{\Geneve}
-\address[g]{\UPISA}
-\address[h]{\ESPCI}
-\address[i]{\CNRIOM}
+\address[e]{\TUW}
+\address[f]{Politecnico di Torino, Turin, Italy}
+\address[g]{\Geneve}
+\address[h]{\UPISA}
+\address[i]{\ESPCI}
+\address[j]{\CNRIOM}
 % \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
@@
   %% keywords here, in the form: keyword \sep keyword
-  Exact diagonalization \sep
-  Quantum Impurity models\sep  
-  Strongly correlated electrons \sep  
+  Exact Diagonalization \sep
+  Quantum Impurity Models\sep  
+  Strongly Correlated Electrons \sep  
   Dynamical Mean-Field Theory
@@
 
-\input{01_intro.tex}
+\subfile{01_intro.tex}
 % ##################################################################
@@
 
-\input{02_install.tex}
+\subfile{02_install.tex}
 
@@
 
-\input{03_edipack2.tex}
+\subfile{03_edipack2.tex}
 
@@
 
-\input{04_cbinding.tex}
+\subfile{04_cbinding.tex}
 
@@
 
-\input{05_examples.tex}
+\subfile{05_examples.tex}
 

### 2025-05-06 03_edipack2.tex
GB pass on `sparse map` subsection (3.5.2 currently)
I don't like too much the formatting of the code snippets. But this is a wider issue that I will discuss with Adriano later.

@@
 $$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_{ph} + \hat{H}_{e-ph}
+\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_\mathrm{ph} + \hat{H}_{e-ph}
 $$
@@
 \end{equation}
-where $p=1,\dots,N_{bath}$ is an index running over a finite number of
+where $p=1,\dots,N_\mathrm{bath}$ is an index running over a finite number of
 bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
@@
   \begin{split}
-    \hat{H}_{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
+    \hat{H}_\mathrm{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
     % 
@@
 In the following we consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_{ph}$,
+of bath degrees of freedom and a finite number of available phonons $N_\mathrm{ph}$,
 to cut-off the unbounded dimensions of the local phonons Hilbert space.
@@
 the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_{ph}$
+mode. This includes a linear scaling of the dimensions with $N_\mathrm{ph}$
 and of course largely limit the available degrees of freedom to
@@
 
-More specifically, we consider a system composed of $N_{imp}=1$
-impurities, i.e. a single impurity problem, $N_{bath}$ bath elements
-and $N_{ph}$ phonons. The size of the system is determined by
+More specifically, we consider a system composed of $N_\mathrm{imp}=1$
+impurities, i.e. a single impurity problem, $N_\mathrm{bath}$ bath elements
+and $N_\mathrm{ph}$ phonons. The size of the system is determined by
 the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
 electronic Hilbert space
-$\HH_e=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
+$\HH_\mathrm{e}=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
 Due to is internal structure, the single impurity contains
@@
 The total number of levels is then determined by
-the electronic levels in the bath $N_b$. This is a function of the bath topology and $N_{bath}$,
+the electronic levels in the bath $N_\mathrm{b}$. This is a function of the bath topology and $N_\mathrm{bath}$,
 i.e. the number of bath elements. In the simplest case each bath
 element corresponds to an independent electronic levels coupled to the
-impurity, thus $N_b\equiv N_{bath}$. 
-We indicate with $N_s=N_i + N_b$ the total number of electronic levels.
+impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
+We indicate with $N_\mathrm{s}=N_i + N_\mathrm{b}$ the total number of electronic levels.
 
@@
 are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_{bath}$ in {\tt
+{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_\mathrm{bath}$ in {\tt
   ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_s$ and $N_b$, defined in the global
+determine the variables {\tt Ns}$=N_\mathrm{s}$ and $N_\mathrm{b}$, defined in the global
 memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
@@
 The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_e\otimes \FF_{ph}$, with $\FF_e=\bigoplus_{n=0}^{N_s}
-S_-\HH_e^{\otimes n}$ the electronic Fock space,  $\FF_{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_{ph}=\{\ket{0},\ket{1},\dots,\ket{N_{ph}}\}$ is the local phonon Hilbert space
+$\FF=\FF_\mathrm{e}\otimes \FF_\mathrm{ph}$, with $\FF_\mathrm{e}=\bigoplus_{n=0}^{N_\mathrm{s}}
+S_-\HH_\mathrm{e}^{\otimes n}$ the electronic Fock space,  $\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}$ the
+phonon Fock space,  $\HH_\mathrm{ph}=\{\ket{0},\ket{1},\dots,\ket{N_\mathrm{ph}}\}$ is the local phonon Hilbert space
 and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
 The total dimension of the Fock space is
-$D=D_e\cdot D_{ph}=4^{N_s}\cdot (N_{ph}+1)$ making the exponential
+$D=D_\mathrm{e}\cdot D_\mathrm{ph}=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)$ making the exponential
 growth with the number of electron levels transparent. 
@@
 i.e. the Fock basis.
-For a system of $N_s$ electrons each Fock state
+For a system of $N_\mathrm{s}$ electrons each Fock state
 reads $\ket{p}\ket{\vec{n}}$ with
-$$
-\ket{\vec{n}}=\ket{\vec{n}_\up}{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_s\up},n_{1\dw},\dots,n_{N_s\dw}}
-$$ 
-where $p=1,\dots,N_{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
+\begin{equation}
+    \ket{\vec{n}}=\ket{\vec{n}_\up}\ket{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_\mathrm{s}\up},n_{1\dw},\dots,n_{N_\mathrm{s}\dw}},
+    \label{eq:FockState_|nupndw>}
+\end{equation}
+where $p=1,\dots,N_\mathrm{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
 presence of an electron with spin $\sigma$ at the level $a$.
 The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_s$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_s$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_s}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
+zeros and ones of length $2N_\mathrm{s}$. Thus, any such state can  be encoded
+in a computer using a sequence of $2N_\mathrm{s}$ bits or, analogously, as a
+given integer $I=0,\dots 2^{2N_\mathrm{s}}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
 Together with the basis states one defines  destruction and creation 
@@
   {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
-                                                $\binom{N_s}{N_\up}\binom{N_s}{N_\dw}$
+                                                $\binom{N_\mathrm{s}}{N_\up}\binom{N_\mathrm{s}}{N_\dw}$
   \\
   \hline
-  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_s-S_z-2m}\binom{N_s}{N_s-S_z-2m}\binom{S_z+2m}{m}$
+  {\bf superc} & $S_z\equiv N_\up-N_\dw$ &  $\sum_m 2^{N_\mathrm{s}-S_z-2m}\binom{N_\mathrm{s}}{N_\mathrm{s}-S_z-2m}\binom{S_z+2m}{m}$
   \\
   \hline
-  {\bf nonsu2} & $N \equiv[N_\up+N_\dw$ & $\binom{2N_s}{N}$ \\ 
+  {\bf nonsu2} & $N \equiv N_\up+N_\dw$ & $\binom{2N_\mathrm{s}}{N}$ \\ 
  \hline
@@
 space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_e = \FF_{e\up}\otimes \FF_{e\dw}$.  
+$\HH=\HH_\up\otimes\HH_\dw$, $\FF_\mathrm{e} = \FF_{e\up}\otimes \FF_{e\dw}$.  
 Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
@@
 $\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_s}$. For a thorough
+$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_\mathrm{s}}$. For a thorough
 discussion about Fock basis organization in this case see
@@
 {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI} are mutually exclusive, but they can be both false.
-Before the impurity problem is solved, the used can also provide interaction terms in the program or script. Extensive documentation is available at (\textcolor{red}{how should we do this?})
-All the interaction operators used in each call of the solver are listed and written in an output file. called {\tt UMATRIX\_FILE.used}.
+Before the impurity problem is solved, the user can also provide interaction terms in the program or script. Extensive documentation is available at (\textcolor{red}{how should we do this?})
+All the interaction operators used in each call of the solver are listed and written in an output file, called {\tt UMATRIX\_FILE.used}.
 
@@
 
+%GBtodo placeholder: I passed on this already (except I don't like the minipage of the listings)
 \subsubsection{Sparse map}\label{CodeSparseMap}
@@
 Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into chunks of bit corresponding,
-for instance to impurity and bath degrees of freedom as 
-$\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$.  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt
-  sparse\_map}, which is included as an element in the {\tt sector} object and  
-which stores  for every impurity configurations $\vec{i}_\s$ (key) the
-bath states $\vec{b}_\s$ (values) corresponding to it.
-The {\tt sparse\_map} ${\cal S}$ elements are constructed upon call in {\tt
-  build\_sector} for any value of {\tt ed\_mode} using different
-algorithms.
+$\ket{\vec{n}}$ can be further split into arbitrarily grouped chunks of bits.
+For instance, we can choose to group the bits into impurity and bath degrees of freedom,
+as $\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$, where we 
+highlight the overall ordering in spin-up and spin-down parts underlying the whole
+codebase (see \equ{eq:FockState_|nupndw>} and the subsequent discussion).  
+The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt sparse\_map}, 
+as a component of the {\tt sector} object, which stores for every impurity 
+configuration $\vec{i}_\s$ (\emph{key}) all the possible bath states $\vec{b}_\s$ (\emph{values})
+that are compatible with the given conserved quantum numbers (see \secu{sSecQNs}).
+The {\tt sparse\_map} ${\cal S}$ objects are constructed upon call of the {\tt
+  build\_sector} subroutine, automatically dispatched to a different algorithm 
+for each value of {\tt ed\_mode}.
 In the {\bf normal} case, the sector object contains two {\tt
@@
 \ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
-The sparse maps are build as follows. 
-For any spin state $\ket{J_\s}=\ket{{vec{i}_{\s}\vec{b}_{\s}}$ of the sector
-the key is determined by the integer $I_\s$ corresponding to the
-impurity bit set $\vec{i}_\s$. The values are given by any 
-integer $B_\s$ corresponding to any bath bit set
-$\vec{b_\s}$ associated with $\vec{i}_\s$.
-Thus, any given combination of key-value
-reconstructs an integer $J_\s$ representing the Fock states in the
+The sparse maps are built as follows. 
+For any spin state of the sector $\ket{J_\s}=\ket{{\vec{i}_{\s}\vec{b}_{\s}}}$,
+the \emph{key} is determined by the integer $I_\s$ corresponding to the
+impurity bitset $\vec{i}_\s$. The \emph{values} are given by any
+integer $B_\s$ corresponding to any bath bitset
+$\vec{b_\s}$ associated with $\vec{i}_\s$ by the conservation law of the 
+given sector: $\mathtt{sum}(\vec{i}_\s) + \mathtt{sum}(\vec{b}_\s) = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
+Thus, any given \emph{key-value} combination 
+reconstructs an integer $J_\s$ representing a Fock state in the
 given spin sector according to the rule $J_s = I_\s +
-2^{N_{imp}}B_\s$, where $N_{imp}$ is the number of impurity bits.
+2^{N_\mathrm{imp}}B_\s$, where $N_\mathrm{imp}$ is the number of impurity bits.
 
@@
 state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bit sets
-$\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
+B_\dw$ corresponding, respectively, to the bitset
+$\ket{\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
 state. These integers fulfill the relation
 $
-J =I_\up +  B_\up2^{N_{imp}} + (I_\dw +  B_\dw2^{N_{imp}})2^{N_s}
+J =I_\up +  B_\up2^{N_\mathrm{imp}} + (I_\dw +  B_\dw2^{N_\mathrm{imp}})2^{N_\mathrm{s}}
 $
-To obtain a contiguous memory pattern we define as a key of the sparse
-map the combination $I_\up + I_\dw2^{N_{imp}}$ and as corresponding
-  values the integer $B_\up + B_\dw2^{N_b}$. Where needed the correct
-  bit sets and Fock state can be reconstructed with simple algebra at
-  no additional cost.
+To obtain a contiguous memory pattern we define as a \emph{key} of the sparse
+map the combination $I_\up + I_\dw2^{N_\mathrm{imp}}$ and as corresponding
+\emph{values} the integers $B_\up + B_\dw2^{N_\mathrm{b}}$, fulfilling the
+corresponding conservation laws: 
+$\mathtt{popcnt}(I_\up + I_\dw2^{N_\mathrm{imp}}) + \mathtt{popcnt}(B_\up + B_\dw2^{N_\mathrm{b}}) = N_\up + N_\dw$
+for the \textbf{nonsu2} case and
+$\mathtt{popcnt}(I_\up + B_\up2^{N_\mathrm{imp}}) - \mathtt{popcnt}(I_\dw + B_\dw2^{N_\mathrm{imp}}) = S_z$
+for the \textbf{superc} case.
+Where needed, the corresponding bitset and Fock state can be reconstructed 
+with simple algebra at no additional cost.
 
 \setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
+  \begin{minipage}{0.48\linewidth}
     \center{\bf normal}
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.5\linewidth}
+  \begin{minipage}{0.52\linewidth}
     \center{\bf superc/nonsu2}
@@
     nup_ = popcnt(iup)
-    !superc 
+    select case (ed_mode)
+      case('superc') 
         sz_  = nup_ - ndw_
         if(sz_ /= self%Sz)cycle
-    !nonsu2 
-    !nt_  = nup_ + ndw_
-    !if(nt_ /= self%Ntot)cycle 
+      case('nonsu2') 
+        nt_  = nup_ + ndw_
+        if(nt_ /= self%Ntot)cycle 
+    end select
     i=i+1 
@@
 parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_{bath}$.
+amplitudes $V^p$, for $p=1,\dots,N_\mathrm{bath}$.
 Internally, the bath is represented by a dedicated object {\tt
@@
 
-The bath topology, i.e. the links between the $N_b$ electronic levels
+The bath topology, i.e. the links between the $N_\mathrm{b}$ electronic levels
 assigned to the bath, is determined by the input variable {\tt
@@
 %
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_{bath}$
+\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_\mathrm{bath}$
 electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_b = N_\a N_{bath}$. The bath Hamiltonan
+count of bath levels is $N_\mathrm{b} = N_\a N_\mathrm{bath}$. The bath Hamiltonan
 matrices include a parametrization diagonal in the orbital and spin space: 
@@
 \paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_{bath}$ coupled to all the impurity levels, correspondingly
-$N_b\equiv N_{bath}$ is the total count of electronic bath levels. 
+$N_\mathrm{bath}$ coupled to all the impurity levels, correspondingly
+$N_\mathrm{b}\equiv N_\mathrm{bath}$ is the total count of electronic bath levels. 
 The main parametrization of the bath Hamiltonian matrices is still
@@
 The total number of electronic levels used to describe the bath is in
-this case: $N_b = N_{sym} N_{bath}$. 
+this case: $N_\mathrm{b} = N_{sym} N_\mathrm{bath}$. 
 For the {\bf replica}  topology the coupling between the impurity and
@@
 %   \hline
-%   {\bf normal} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_b],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_b], \vec{\Delta}[N_b],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_b], \vec{V}[N_b],\vec{W}[N_b]$ \\
+%   {\bf normal} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\a]$ & $\vec{\e}[N_\mathrm{b}],\vec{V}[N_\mathrm{b}]$ 
+%                     & $\vec{\e}[N_\mathrm{b}], \vec{\Delta}[N_\mathrm{b}],\vec{V}[N_\mathrm{b}]$
+%                                    &  $\vec{\e}[N_\mathrm{b}], \vec{V}[N_\mathrm{b}],\vec{W}[N_\mathrm{b}]$ \\
 %   \hline
-%   {\bf hybrid} $[N_b\!=\!N_{bath}N_\a]$ & $\vec{\e}[N_{bath}],\vec{V}[N_b]$ 
-%                     & $\vec{\e}[N_{bath}], \vec{\Delta}[N_{bath}],\vec{V}[N_b]$
-%                                    &  $\vec{\e}[N_{bath}], \vec{V}[N_b],\vec{W}[N_b]$ \\
+%   {\bf hybrid} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\a]$ & $\vec{\e}[N_\mathrm{bath}],\vec{V}[N_\mathrm{b}]$ 
+%                     & $\vec{\e}[N_\mathrm{bath}], \vec{\Delta}[N_\mathrm{bath}],\vec{V}[N_\mathrm{b}]$
+%                                    &  $\vec{\e}[N_\mathrm{bath}], \vec{V}[N_\mathrm{b}],\vec{W}[N_\mathrm{b}]$ \\
 %   \hline
-%   {\bf replica} $[N_b\!=\!N_{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
+%   {\bf replica} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
 %   \hline
-%   {\bf general} $[N_b\!=\!N_{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
+%   {\bf general} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
 %   \hline
@@
 the related eigenvalue problem represents an unsurmountable problem
-already with $N_s\simeq 8$. 
+already with $N_\mathrm{s}\simeq 8$. 
 In order to outwit this issue a number of
@@
 $$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_s}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_s}} \rho_{nm} \ket{n}\bra{m} 
+\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_\mathrm{s}}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_\mathrm{s}}} \rho_{nm} \ket{n}\bra{m} 
 $$
@@
   \begin{aligned}
-  \rho^i &=
+  \rho^\mathrm{imp} &=
   \sum_{\sigma=\up\dw}\sum_{b_\sigma=1}^{D_{b_\sigma}}
@@
 where the constant $C_{i,b}$ take care of the sign change due to
-exchanging bath and impurity bit sets. As effect of the Kronecker
+exchanging bath and impurity bitsets. As effect of the Kronecker
 delta symbols for bath and impurity these constants are identically 1.  
@@
           iBath = Bath(ib)
-          !Decompose iBath into B_Up, B_dw to reconstruct B bit set. 
+          !Decompose iBath into B_Up, B_dw to reconstruct B bitset. 
           !B --> {B_up,B_dw}
@@
 $$
-\chi = \sum_{n=1}^{L_{fit}}\frac{1}{W_n}||X(i\omega_n) - X^{QIM}(i\omega_n;\{V,h\})||_q
+\chi = \sum_{n=1}^{L_\mathrm{fit}}\frac{1}{W_n}||X(i\omega_n) - X^\mathrm{QIM}(i\omega_n;\{V,h\})||_q
 $$
@@
 supplied local functions and
-$X_{\a\b}^{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
+$X_{\a\b}^\mathrm{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
 quantum impurity model functions, defined above.
@@
 \texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_{fit}$ used in the fit procedure
+The number of Matsubara frequency $L_\mathrm{fit}$ used in the fit procedure
 is controlled  by the input parameter \texttt{cg\_Lfit}.
@@
 have universal behavior.
-Similarly, the weight  $W_n=1,1/L_{fit},1/\omega_n$ is used to
+Similarly, the weight  $W_n=1,1/L_\mathrm{fit},1/\omega_n$ is used to
 enhance the weight of low energy part with respect to the

### 2025-05-06 03_edipack2.tex
GB halfway through the iRDM section (currently 3.10) I found a seemingly wrong statement that I want to discuss with AA.

@@
 leveraging on the exponential cutoff from the Boltzmann factor:
-$$
+\begin{equation}
     \ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n}
-$$
+  E_n}\bra{\psi_n}\OO\ket{\psi_n},
+  \label{eq:thermal_average}
+\end{equation}
 where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
@@
 
-%GBtodo placeholder: revise this subsection
 \subsection{Reduced impurity density matrix}\label{sSecRDM}
 This version of the \NAME library features the calculation of the
-impurity Reduced Density Matrix (iRDM), extending the algorithm introduced in \onlinecite{BellomiaPhD} so to enable the analysis of
-entanglement properties of the quantum impurity for any value of {\tt
-  ed\_mode}.
+impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), extending 
+the algorithm introduced in \onlinecite{BellomiaPhD} so to enable the
+analysis of entanglement properties of the quantum impurity for any value
+of {\tt ed\_mode}.
 To simplify the discussion in this section we take the zero
@@
 The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward.
-The groundstate belongs to a given symmetry sector $\SS$ and it
-represented in the Fock basis as:  $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The density matrix $\rho$ is defined as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_\mathrm{s}}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_\mathrm{s}}} \rho_{nm} \ket{n}\bra{m} 
-$$
-The iRDM is obtained from this by tracing out the bath degrees of
-freedom: $\rho^{i}=Tr_{b}\rho$. The summation appearing in the
-previous expressions becomes quickly unmaneagable with the system
-size. To overcome this issue we implemented a fast algorithm
-leveraging on symmetry sector and map sparsity.
-Using quantum number conservation the summation extrema get reducedto
-the size $D_S$ of the sector $S$ to which the groundstate (or in
+temperature regime are straightforward, as it amounts to defining an
+average over degenerate/thermal states $\ibra\rho^\mathrm{imp}\iket$, 
+akin to \equ{eq:thermal_average}.
+The given pure state belongs to a unique symmetry sector $\SS$ and it
+is represented in the Fock basis as $\ket{\psi} = \sum_I a_I \ket{I}$. 
+The corresponding pure density matrix $\rho$ is thus explicitly decomposed as:
+$$
+\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_\mathrm{s}}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_\mathrm{s}}} \rho_{nm} \ket{n}\bra{m}.
+$$
+The iRDM is obtained from $\rho$ by tracing out the bath degrees of
+freedom: $\rho^\mathrm{imp}=\Tr_\mathrm{bath}\rho$. The summations appearing in the
+previous expressions become quickly unmanageable with the system
+size, as their extrema scale exponentially with $N_\mathrm{s}$. 
+To overcome this issue we implemented a fast algorithm
+leveraging on the decomposition of the Fock space into symmetry sectors
+and the subsequent map sparsity.
+Using quantum number conservation the summation extrema get reduced to
+the size $D_\SS$ of the sector $\SS$ to which the groundstate (or in
 general any eigenstate) belongs. 
@@
 their spin-dependent impurity and bath parts as $\ket{I} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bit
-set span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
-Finally, we store into the {\tt sparse\_map} ${\cal S}$, for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (key) the corresponding bath states $j\in[1,\dots,D^\s_{bath}]$
-(values) which contribute to that key, as detailed in
-\secu{CodeSparseMap}.
+  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bitset 
+span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
+Finally, as detailed in \secu{CodeSparseMap}, we store into the {\tt sparse\_map} ${\cal S}$, 
+for every impurity configuration 
+$i_\s =1,\dots,D^\s_{imp}$ (\emph{key}), the bath states 
+$j\in[1,\dots,D^\s_{bath}]$ (\emph{values}) that satisfy the conservation law defined
+by the \texttt{ed\_mode} variable.
 We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
@@
 
+%GBtodo placeholder: revise this subsection from this point onwards
 \paragraph{{\bf normal}}
-In this case we take advantage of the Fock and sector spin resolved
-factorization discussed in \secu{sSecQNs}. As such we can also split
-impurity and bath bits independently for each spin configuration:
+In this case we take advantage of the Fock space and sector spin-resolved
+factorization, discussed in depth in \secu{sSecQNs}. We can indeed split the
+global bitset in spin-resolved impurity and bath states, as
 $$
@@
 \ket{\vec{n}_\up}\otimes \ket{\vec{n}_\dw} =
-\ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}
-$$
-In addition it should be noted that creation (destruction) operators at
+\ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}.
+$$
+We note that creation (destruction) operators at
 position $p$ for spin $\sigma$  $c^+_{p\sigma}$ ($c^+_{p\sigma}$) do
-not operate on the opposite spin so that they pass through without
-taking any fermionic sign. Finally, we observe that local iRDM admits
-only diagonal terms in the {\bf normal} case. Thus we obtain for the iRDM:
+not operate on the opposite spin $\bar{\sigma}$ so that they pass through 
+the $\ket{n_{\bar{\sigma}}}$ bitset without taking any fermionic sign. 
+Finally, we observe that local iRDM admits
+only {\color{red} diagonal} terms in the {\bf normal} case. {\color{red} [GB: this is a wrong statement: do you mean \emph{spin-}diagonal?]}
+
+Thus we obtain for the iRDM:
 \begin{equation}
@@
 to the previous case. In particular it is important to recall that the
-ordering of the key-value pairs in the {\tt sparse\_map} in this case
-follow a contiguous ordering and that their decomposition is necessary
-to reconstruct the correct Fock state index, see the following
+ordering of the \emph{key-value} pairs in the {\tt sparse\_map} in this case
+follows a contiguous ordering and that their decomposition is necessary
+to reconstruct the correct Fock state index. See the following
 listing:

### 2025-05-07 03_edipack2.tex
GB: heavy rewrite of the iRDM (3.10) section
Summation indices were misleading, the normal case was written (in the formula) to be diagonal, which is not for Norb > 1. The listing were correct, so it was just a matter of notational mess. I also added a formal proof to why the normal iRDM is block-diagonal with respect to impurity Nup and Ndw sectors.
It should read pretty smooth now.

I also edited many sub- and super-scripts, adding the usual \mathrm{}, when they are words (bath, imp, int, e-ph, ...)

Finally, I did some light editing on the Attractive Hubbard example, just because I found so

@@
 $$
-\hat{H} = \hat{H}_{imp} + \hat{H}_{bath} + \hat{H}_{hyb} + \hat{H}_\mathrm{ph} + \hat{H}_{e-ph}
+\hat{H} = \hat{H}_\mathrm{imp} + \hat{H}_\mathrm{bath} + \hat{H}_\mathrm{hyb} + \hat{H}_\mathrm{ph} + \hat{H}_\mathrm{e-ph}
 $$
@@
   \begin{split}
-    \hat{H}_{imp} & = \hat{H}^0_{imp} + \hat{H}^{int}_{imp}\\
-    \hat{H}^0_{imp} & =
+    \hat{H}_\mathrm{imp} & = \hat{H}^0_\mathrm{imp} + \hat{H}^{int}_\mathrm{imp}\\
+    \hat{H}^0_\mathrm{imp} & =
     \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
@@
   \begin{split}
-    \hat{H}^{int}_{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
+    \hat{H}^\mathrm{int}_\mathrm{imp} &=U\sum_{\a}n_{\a\uparrow}n_{\a\downarrow}+U'\sum_{\a\neq \b}n_{\a\uparrow}n_{\b\downarrow}+(U'-J)\sum_{\a<\b,\sigma}n_{\a\sigma}n_{\b\sigma}\\
     &{\phantom =}- J_X\sum_{\a\neq
@@
 the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^{int}$ describes the  local multi-orbital
+$\hat{H}^\mathrm{int}$ describes the  local multi-orbital
 interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
@@
 couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_{orbital}\times SU(2)_{spin}\times
-U(1)_{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
+In the case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
+U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
 $J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
@@
   \begin{split}
-    \hat{H}_{bath} &=
+    \hat{H}_\mathrm{bath} &=
     \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
     %
-    \hat{H}_{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
+    \hat{H}_\mathrm{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
 \end{split}
@@
     % 
-    \hat{H}_{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
+    \hat{H}_\mathrm{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
 \end{split}
@@
 reduces of the Fock space into several symmetry sectors
-labelled by given quantum numbers $\vec{Q}$. 
+labeled by given quantum numbers $\vec{Q}$. 
 In the context of quantum impurity problems two symmetries are often considered: i)
@@
 Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labelled by two integers $[i_\up,i_\dw]$, 
+sector is labeled by two integers $[i_\up,i_\dw]$, 
 $i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
 D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labelled by two integers
+$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labeled by two integers
 $[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_\mathrm{s}}$. For a thorough
@@
 in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labelled by the quantum numbers $\vec{Q}$, has dimension
+Each block, labeled by the quantum numbers $\vec{Q}$, has dimension
 $D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
@@
 $\vec{b_\s}$ associated with $\vec{i}_\s$ by the conservation law of the 
-given sector: $\mathtt{sum}(\vec{i}_\s) + \mathtt{sum}(\vec{b}_\s) = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
+given sector: $\#\vec{i}_\s + \#\vec{b}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
 Thus, any given \emph{key-value} combination 
@@
 time, so its optimization is a crucial aspect in any diagonalization
-algorithms. In \onlinecite{Amaricci2022} we covered in full details
-some distrubuted memory massively parallel algorithms to address this
-specific issue.
-Here, using the same naming convention introduced in \cite{Amaricci2022}, 
+algorithm. In \onlinecite{Amaricci2022} we covered in full detail
+the distrubuted memory massively parallel algorithms we implement 
+to address this specific issue.
+Here, using the same naming convention introduced in \onlinecite{Amaricci2022}, 
 we briefly outline the main strategy for the implementation of the MVP
@@
 \begin{equation}
-H_\SS = H_d  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_{nd}\,.
+H_\SS = H_\mathrm{d}  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
+H_\dw + H_\mathrm{nd}\,.
 \label{HssNormal}
@@
 $$
-H_\SS = H_{imp} + H_{int} + H_{bath} + H_{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_{imp}$ encodes
+H_\SS = H_\mathrm{imp} + H_\mathrm{int} + H_\mathrm{bath} + H_\mathrm{imp-bath} 
+$$
+where, with almost obvious meaning of the labels, $H_\mathrm{imp}$ encodes
 the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_{int}$ the interaction term, $H_{bath}$ the
+$h^0_{\a\b\s\s'}$, $H_\mathrm{int}$ the interaction term, $H_\mathrm{bath}$ the
 effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_{imp-bath}$ describes the coupling between impurity and bath
+$H_\mathrm{imp-bath}$ describes the coupling between impurity and bath
 proportional to $V^p_{\a\b\s\s'}$. 
@@
 dimension $d_i$ of the vector chunk per each node such that
-$\sum_{i=1}^{N_{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
+$\sum_{i=1}^{N_\mathrm{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
 depends on the MPI algorithm used for the MVP function, which in turn
@@
 \subsection{Reduced impurity density matrix}\label{sSecRDM}
-This version of the \NAME library features the calculation of the
+The new \NAME version of the library features the calculation of the
 impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), extending 
@@
 $$
-\rho = \ket{\psi}\bra{\psi} = \sum_{nm=1}^{4^{N_\mathrm{s}}} a^*_ma_n \ket{n}\bra{m} =\sum_{nm=1}^{4^{N_\mathrm{s}}} \rho_{nm} \ket{n}\bra{m}.
+\rho = \ket{\psi}\bra{\psi} = \sum_{IJ=1}^{4^{N_\mathrm{s}}} a^*_J a_I \ket{I}\bra{J} =\sum_{IJ=1}^{4^{N_\mathrm{s}}} \rho_{IJ} \ket{I}\bra{J}.
 $$
@@
 their spin-dependent impurity and bath parts as $\ket{I} = \ket{
-  i_\uparrow\,  b_\uparrow\, i_\downarrow \, b_\downarrow}$. Each bitset 
-span a space of dimension $D^\a_{imp}$ or $D^\s_{bath}$. 
+  i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow \, b_\downarrow}$. Each bitset 
+span a space of dimension $D^\a_\mathrm{imp}$ or $D^\s_\mathrm{bath}$. 
 Finally, as detailed in \secu{CodeSparseMap}, we store into the {\tt sparse\_map} ${\cal S}$, 
@@
 $i_\s =1,\dots,D^\s_{imp}$ (\emph{key}), the bath states 
-$j\in[1,\dots,D^\s_{bath}]$ (\emph{values}) that satisfy the conservation law defined
+$b_\s\in[1,\dots,D^\s_\mathrm{bath}]$ (\emph{values}) that satisfy the conservation law defined
 by the \texttt{ed\_mode} variable.
-We indicate with ${\cal D}^\s_{i}$ the number of values for the key $i_\s$.
+We indicate with ${\cal D}_{i\s}$ the number of keys $i_\s$ and with 
+${\cal D}_{b\s}$ the number of values $b_\s$.
 The fast summation algorithm for the evaluation of the iRDM takes on a
@@
 
-%GBtodo placeholder: revise this subsection from this point onwards
 \paragraph{{\bf normal}}
@@
 Finally, we observe that local iRDM admits
-only {\color{red} diagonal} terms in the {\bf normal} case. {\color{red} [GB: this is a wrong statement: do you mean \emph{spin-}diagonal?]}
-
+only {spin-diagonal} blocks in the {\bf normal} case. This can be understood
+by observing that the conserved quantum numbers in the whole impurity model 
+are \emph{additive} $N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$ and so the
+corresponding generator of the symmetry group is factorized as 
+$U_{N_\s} = U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}}$. 
+Hence, as the iRDM acts by definition only on the impurity
+Fock space, we have 
+$$
+U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} = 
+U_{N_\s^\mathrm{bath}}^\dagger \otimes U_{N_\s^\mathrm{imp}}^\dagger
+\rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}} =
+U_{N_\s^\mathrm{imp}}^\dagger
+\rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} =
+\rho^\mathrm{imp},
+$$
+i.e. $U_{N_\s^\mathrm{imp}}$ defines a symmetry of $\rho^\mathrm{imp}$, making it
+block diagonal with respect to the impurity quantum numbers $N_\s^\mathrm{imp}$.
 Thus we obtain for the iRDM:
@@
   \begin{aligned}
-  \rho^\mathrm{imp} &=
-  \sum_{\sigma=\up\dw}\sum_{b_\sigma=1}^{D_{b_\sigma}}
+  \rho^\mathrm{imp} &= \Tr_{b_\up b_\dw}{\rho} = 
+  \sum_{b_\up=1}^{D_{b_\up}}
+  \sum_{b_\dw=1}^{D_{b_\dw}}
   \bra{b_\up}\otimes\bra{b_\dw}
@@
     %
-    &=\sum_{\sigma=\up\dw}
-    \sum_{b_\sigma=1}^{D_{b_\sigma}}
-    \sum_{i_\sigma=1}^{D_{i_\sigma}}
-    \sum_{p_\sigma=1}^{D_{p_\sigma}}
-    \sum_{j_\sigma=1}^{D_{j_\sigma}} 
-    \sum_{q_\sigma=1}^{D_{q_\sigma}}
+    &=
+    \sum_{b_\up=1}^{D_{b_\up}}
+    \sum_{i_\up=1}^{D_{i_\up}}
+    \sum_{p_\up=1}^{D_{p_\up}}
+    \sum_{j_\up=1}^{D_{j_\up}} 
+    \sum_{q_\up=1}^{D_{q_\up}}
+    \Bigg( \cr
+    %
+    &\qquad
+    \sum_{b_\dw=1}^{D_{b_\dw}}
+    \sum_{i_\dw=1}^{D_{i_\dw}}
+    \sum_{p_\dw=1}^{D_{p_\dw}}
+    \sum_{j_\dw=1}^{D_{j_\dw}} 
+    \sum_{q_\dw=1}^{D_{q_\dw}}
     C_{i,p}\,C_{j,q}\,a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw}
-    \langle b_\up| p_\up\rangle| i_\up\rangle\langle j_\up |\langle q_\up| b_\up\rangle   \otimes \langle b_\dw| p_\dw \rangle|i_\dw\rangle \langle j_\dw  |\langle q_\dw| b_\dw\rangle
+    \langle b_\up| p_\up\rangle| i_\up\rangle\langle j_\up |\langle q_\up| b_\up\rangle   \otimes \langle b_\dw| p_\dw \rangle|i_\dw\rangle \langle j_\dw  |\langle q_\dw| b_\dw\rangle \Bigg)
     \cr
 &=
-    \sum_{b_\sigma=1}^{D_{b_\sigma}}
-    \sum_{i_\sigma=1}^{D_{i_\sigma}}
-    a_{i_\up b_\up i_\dw b_\dw} a^*_{i_\up b_\up i_\dw b_\dw}
-    \ket{i_\up}\bra{i_\up}\otimes \ket{i_\dw}\bra{i_\dw}
+    \sum_{i_\up=1}^{D_{i_\up}}
+    \sum_{j_\up=1}^{D_{j_\up}}
+    \sum_{i_\dw=1}^{D_{i_\dw}}
+    \sum_{j_\dw=1}^{D_{j_\dw}}
+    \underbrace{\left(
+    \sum_{b_\up=1}^{D_{b_\up}}
+    \sum_{b_\dw=1}^{D_{b_\dw}}
+    a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
+    \right)}_{\rho^\mathrm{imp}_{i_\up j_\up} \otimes\, \rho^\mathrm{imp}_{i_\dw j_\dw} }
+    \ket{i_\up}\bra{j_\up}\otimes \ket{i_\dw}\bra{j_\dw},
   \end{aligned}
 \end{equation}
-where the constant $C_{i,b}$ take care of the sign change due to
-exchanging bath and impurity bitsets. As effect of the Kronecker
-delta symbols for bath and impurity these constants are identically 1.  
+where we recall that $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the expansion coefficients of the state $\ket{\psi}$ on the Fock basis 
+$\ket{I} = \ket{i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow \, b_\downarrow}$
+and the constants $C_{i,b}$, accounting for the fermionic sign associated to
+exchanging bath and impurity bitsets, are identically 1 as effect of the 
+Kronecker deltas for bath and impurity indices.  
 The numerical implementation relies on the use of the {\tt
@@
 \paragraph{{\bf superc/nonsu2}}
-In presence of these symmetries suitable modifications related to the
-absence of Fock space factorization have to be taken into account. To
-start with a generic Fock state appearing in the groundstate
-decomposition has the form:
-$$
-\ket{\vec{n}} =\ket{\vec{i}_\up\vec{b}_\up\vec{i}_\dw\vec{b}_\dw}
-%
-$$
-% where the second is just a formal identity.  
-Inserting this latter in the definition of iRDM we obtain:
+To treat these lowered-symmetry cases, some modifications related to the
+absence of Fock space factorization have to be taken into account. In particular, 
+the correct evaluation of the off-diagonal terms connecting the 
+$[N^\mathrm{imp}_\up,\,N^\mathrm{imp}_\dw]$ blocks, relies on 
+computing explicitly the fermionic permutation signs.
+
+Let us consider a generic Fock basis in the form
+$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, defining the target
+ground state again as $\ket{\psi} = \sum_I a_I \ket{I}$.
+From the definitions of pure density matrix $\rho = \ket{\psi}\bra{\psi}$ 
+and of iRDM we have:
 \begin{equation}
   \begin{aligned}
-    \Tr_{b_\up, b_\dw}{\rho} &=
+    \rho^\mathrm{imp} &= \Tr_{b_\up b_\dw}{\rho} =
     \sum_{b_\sigma=1}^{D_{b_\sigma}}
     \bra{b_\up\, b_\dw}
-    \rho
+    \,\rho\,
+    \ket{b_\dw\, b_\up} =
+    \sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \ibra{b_\up\, b_\dw}
+    \ket{\psi}\ibra{\psi}
     \ket{b_\dw\, b_\up}    \cr
@@
 In order to simplify this expression we should get rid of the sum with
-respect to the bath indices $p_\sigma$ and $q_\sigma$, ideally
+respect to the internal bath indices $p_\sigma$ and $q_\sigma$, ideally
 contracting them with the outer indices $b_\sigma$.
-However, this requires to bring all the bath bits so to preced the
-impurity ones:
+However, this requires to bring all the bath bitsets so to precede the
+impurity states:
 $$
@@
 where $C_{p_\up,i_\dw}  = (-1)^{\#\vec{n}_{p\up} \cdot
-  \#\vec{n}_{i\dw}}$ with   $\#\vec{n}=\sum_i n_i$ is an overall
-fermionic sign which depends on the occupation of the $p_\up$ and the
-$i_\dw$ bit configurations. Inserting this relation in the equation
-for the iRDM we obtain:
+\#\vec{n}_{i\dw}}$, with $\#\vec{n}_{\alpha\sigma}$ counting the bits set to
+1 in the occupation number vector $\vec{n}_{\alpha\sigma}$, is an overall
+fermionic sign depending on the $\ket{p_\up}$ and $\ket{i_\dw}$ bit configurations. 
+Inserting this relation in the equation for the iRDM we obtain:
 \begin{equation}
-  \begin{aligned}
-    \Tr_{b_\up, b_\dw}{\rho} &=
-    \sum_{i_\sigma=1}^{D_{i_\sigma}}
-    \sum_{j_\sigma=1}^{D_{j_\sigma}}
-    \left[\sum_{b_\sigma=1}^{D_{b_\sigma}}
+    \rho^\mathrm{imp} =
+    \sum_{i_\up=1}^{D_{i_\up}}
+    \sum_{j_\up=1}^{D_{j_\up}}
+    \sum_{i_\dw=1}^{D_{i_\dw}}
+    \sum_{j_\dw=1}^{D_{j_\dw}}
+    \underbrace{\left(
+    \sum_{b_\up=1}^{D_{b_\up}}
+    \sum_{b_\dw=1}^{D_{b_\dw}}
     a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
-    C_{b_\up,i_\dw}C_{b_\up,j_\dw}\right]
-    \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up}\cr
-&=
-    \sum_{i_\sigma=1}^{D_{i_\sigma}}
-    \sum_{j_\sigma=1}^{D_{j_\sigma}}
-    \rho^{i}_{i_\up i_\dw j_\dw j_\up}
+    C_{b_\up,i_\dw}C_{b_\up,j_\dw}\right)}_{
+    \rho^\mathrm{imp}_{i_\up i_\dw j_\dw j_\up}}
     \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up}
-  \end{aligned}
 \end{equation}
@@
 \end{lstlisting}
+%GBtodo placeholder: I checked and heavily edited all the iRDM section
 
@@
 can choose between different norm defition.
-{\color{red} I (GB) can take care of this, as I introduced the "elemental" norm in the code.}
+{\color{red} I (GB) can take care of this, as I introduced the ``elemental" norm in the code.}
 %GBtodo placeholder

### 2025-05-07 05_examples.tex
Few typos
GB: heavy rewrite of the iRDM (3.10) section
Summation indices were misleading, the normal case was written (in the formula) to be diagonal, which is not for Norb > 1. The listing were correct, so it was just a matter of notational mess. I also added a formal proof to why the normal iRDM is block-diagonal with respect to impurity Nup and Ndw sectors.
It should read pretty smooth now.

I also edited many sub- and super-scripts, adding the usual \mathrm{}, when they are words (bath, imp, int, e-ph, ...)

Finally, I did some light editing on the Attractive Hubbard example, just because

@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Examples}\label{SecExamples}
@@
 \item Evaluate the local interacting Green's function
-  $G_{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
+  $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
   $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
   \item Update the Weiss field through the {\bf self-consistency}
-    relation: $\GG^{-1}_0(i\omega) = G_{loc}(i\omega) + \Sigma(i\omega)$. 
+    relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) + \Sigma(i\omega)$. 
   \item Optimize the bath parameters $\vec{x}$ against the updated
@@
 To illustrate this point, we report in panel (A) the evolution of
-the spectral function $-{\rm Im}G_{loc}(\omega)/\pi$ as a function of
+the spectral function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of
 the interaction strenght $U$. Despite the {\it spiky} nature of the spectrum, due to the
@@
 system shows the formation of incoherent  high-energy features which
-will then develop into Hubbard bands in the Mott insulating state for $U>U_c$, with $U_c\simeq 2.8D$.
+will then develop into Hubbard bands in the Mott insulating state for $U>U_\mathrm{c}$, with $U_\mathrm{c}\simeq 2.8D$.
 
@@
       a function of increasing interaction $U$. The critical
-      interaction $U_c\simeq 2.8D$ separates the correlated metal $U<U_c$ from
-      the Mott insulator $U>U_c$.
+      interaction $U_\mathrm{c}\simeq 2.8D$ separates the correlated metal $U<U_\mathrm{c}$ from
+      the Mott insulator $U>U_\mathrm{c}$.
       (b)-(c) The corresponding evolution of the Matsubara self-energy
@@
 diverging behavior is acheived crossing the critical interaction
-strenght $U>U_c$.
+strenght $U>U_\mathrm{c}$.
 We recall that this behavior can be observed on the Matsubara axis
@@
 import os,sys
-from aux_funx import * #include function to build $G_{loc}$ and Weiss fields
+from aux_funx import * #include function to build $G_\mathrm{loc}$ and Weiss fields
 
@@
 \item
-  Evaluate the interacting local Green's functions $\hat{G}_{loc}$ and
-  $\hat{F}_{loc}$:
+  Evaluate the interacting local Green's functions $\hat{G}_\mathrm{loc}$ and
+  $\hat{F}_\mathrm{loc}$:
   \begin{equation}
-  {\mathbf G}_{loc}(i\omega) =
+  {\mathbf G}_\mathrm{loc}(i\omega) =
   \int_\RRR d\e \rho(\e)
@@
   $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
-    relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_{loc}(i\omega) +
+    relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_\mathrm{loc}(i\omega) +
     {\mathbf \Sigma}(i\omega)$ in Nambu space. 
@@
       (a) Evolution of the spectral functions
-      $-\Im{G_{loc}(\omega)}/\pi$ as a function of increasing
+      $-\Im{G_\mathrm{loc}(\omega)}/\pi$ as a function of increasing
       attraction $U$. 
@@
       fit highlights the critical behavior with a mean-field exponent
-      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_c=0.61$.       
+      $\beta=1/2$ (red dashed line) and parameters $A\simeq 3.7$, $T_\mathrm{c}=0.61$.       
         }
@@
 evolution of the spectral density, obtained from the local normal
-Green's function $-\tfrac{1}{\pi}\Im{G}_{loc}(\omega)$, as a function
+Green's function $-\tfrac{1}{\pi}\Im{G}_\mathrm{loc}(\omega)$, as a function
 of the attraction $U$. For any finite value of  $U$ the Van Hove peak
@@
 suppressing the order parameter. This effect is particularly active in
-the intermediate regime, as captured by the behavior of the
-correlation strength
-$\theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
+the intermediate regime, as captured by the behavior of the so-called
+\emph{correlation strength}
+$\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
 reported in panel (C). Assuming a monotonic behavior of the anomalous
-self-energy function, this quantity estimates the ``strength'' of
-quantum fluctuations comparing the mean-field-like behavior at high
-energy scale with that near the Fermi level. A large value of $\theta$
-indicates a more correlated system.
+self-energy function, this quantity estimates the ``strength'' of its
+dynamical fluctuations, comparing the mean-field-like behavior found
+at high energy scale, with the features at the Fermi level. 
+A large value of $\Theta$ indicates a more dynamical self-energy, hence
+a more correlated system.
 Our results show that both weak and strong coupling regime are
@@
 BCS description.  
-To further corroborate the distance between the DMFT and mean-field
-solution we report in panel (D) the evolution of the double occupancy
+To further corroborate the distance between the DMFT and the mean-field
+solutions, we report in panel (D) the evolution of the double occupancy
 $d=\langle n_\up n_\dw\rangle$. At half-filling the mean-field value is
 determined solely by the order parameter as $d=1/4 + \phi^2$.
-Our results show that the inclusion of quantum fluctuations in DMFT
+Our results show that the inclusion of dynamical fluctuations in DMFT
 slightly increase the value of $d$ in the weak coupling
@@
 transition is underlined by the scaling of the solution near
-the critical point $\phi \simeq (T_c-T)^\beta$ with $\beta=1/2$ as
+the critical point $\phi \simeq (T_\mathrm{c}-T)^\beta$ with $\beta=1/2$ as
 predicted by mean-field calculations.
 
-\subsection{Multi-orbital Hubbard (Triqs)}
+\subsection{Multi-orbital Hubbard (TRIQS)}
 
@@
 \subsection{Interacting Bernevig-Hughes-Zhang (Fortran)}
+
+\end{document}

### 2025-05-07 03_edipack2.tex
Updates from Overleaf

@@
 \section{Implementation}\label{SecEDIpack}
-Here we present an overview of the implementation of the
-different parts of the \NAME library.
+In this section we introduce the generic quantum impurity system and
+present a detailed overview of the \NAME library implementation.
 
@@
 impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. 
+phonons. We assume for the moment that no particular symmetry
+holds. We separate the impurity part of the Hamiltonian into a
+quadratic and interacting term: 
 \begin{equation}\label{Himp}
   \begin{split}
-    \hat{H}_\mathrm{imp} & = \hat{H}^0_\mathrm{imp} + \hat{H}^{int}_\mathrm{imp}\\
+    \hat{H}_\mathrm{imp} & = \hat{H}^0_\mathrm{imp} + \hat{H}^\mathrm{int}_\mathrm{imp}\\
     \hat{H}^0_\mathrm{imp} & =
@@
 \end{equation}
-
-We assume for the moment that no particular symmetry
-holds. The impurity part of the Hamiltonian can, in principle, consist of any set of
-two-body quantum operators of the form $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
-
-A set of such operators is the celebrated Hubbard-Kanamori Hamiltonian:
-
+where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
+second-quantization operators for impurity electrons in the
+orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
+with spin $\sigma=\up,\dw$ and whose occupation is described
+by the  operator  
+$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
+The internal structure of the non-interacting part is described by the
+$h^{0}_{\a\b\sigma\sigma'}$ matrix. 
+%
+The
+interaction term $\hat{H}^{\mathrm{int}}$ of the Hamiltonian can, in principle, consist of any set
+of two-body quantum operators of the form
+$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. However, we also
+consider the  local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ACMP}:   
 \begin{equation}\label{Hint}
@@
 \end{equation}
-
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The non-interacting internal structure of the impurity is described by
-the $h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-$\hat{H}^\mathrm{int}$ describes the  local multi-orbital
-interaction~\cite{Georges2013ACMP} which, for simplicity, we take as a
-generalized Hubbard-Kanamori form.  
 The first three terms represent the density-density part of the
@@
 $J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other values of
-$N_\a$~\cite{Georges2013ACMP}.
-
-The bath part and its coupling to the impurity has the form: 
+of the combined symmetry group, can be made for other number of orbitals~\cite{Georges2013ACMP}.
+
+The bath part and its coupling to the impurity have the form: 
 \begin{equation}\label{Hbath}
@@
 bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, with orbital $\alpha$ and
+the bath electrons with index $p$, orbital $\alpha$ and
 spin $\sigma$.
 The  properties of each bath level are described by the
-matrices $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology,
-which will be discussed further in the following.
+matrix $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
+composed of several electronic levels according the bath topology, which will be discussed further in the following.
 Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we allow to couple different orbital and
-opposite spins.
+$V^p_{\a\b\s\sigma'}$ which we assume to depend on all orbital and spins.
 
@@
 
-\paragraph{{\bf Remark}} As extensively discussed in
-\onlinecite{Amaricci2022}, the inclusion of local phonons with
-truncated dimensions ultimately amounts to a sequential application of
-the procedures defined for the electronic part, i.e. one per phonon
-mode. This includes a linear scaling of the dimensions with $N_\mathrm{ph}$
-and of course largely limit the available degrees of freedom to
-describe electronic states. In the rest of the paper we focus
-specifically on the electronic part of the quantum impurity problem,
-referring to the phonons in specific sections when their presence
-introduces non-trivial modifications.
-
-More specifically, we consider a system composed of $N_\mathrm{imp}=1$
+% \paragraph{{\bf Remark}} As extensively discussed in
+% \onlinecite{Amaricci2022}, the inclusion of local phonons with
+% truncated dimensions ultimately amounts to a sequential application of
+% the procedures defined for the electronic part, i.e. one per phonon
+% mode. This includes a linear scaling of the dimensions with $N_\mathrm{ph}$
+% and of course largely limit the available degrees of freedom to
+% describe electronic states. In the rest of the paper we focus
+% specifically on the electronic part of the quantum impurity problem,
+% referring to the phonons in specific sections when their presence
+% introduces non-trivial modifications.
+
+In the rest of this work we consider a system composed of $N_\mathrm{imp}=1$
 impurities, i.e. a single impurity problem, $N_\mathrm{bath}$ bath elements
 and $N_\mathrm{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of {\it electronic} levels, i.e. levels with a local
-electronic Hilbert space
-$\HH_\mathrm{e}=\{\ket{0},\ket{\up},\ket{\dw},\ket{\up\dw} \}$. 
-Due to is internal structure, the single impurity contains
-$N_i= N_\a$ electronic levels.
+the number of phonons (fixed) and that of electronic levels. 
+The single impurity contains $N_\a$ electronic levels.
 The total number of levels is then determined by
-the electronic levels in the bath $N_\mathrm{b}$. This is a function of the bath topology and $N_\mathrm{bath}$,
+the number of electronic levels $N_\mathrm{b}$ assigned to the bath.
+The latter number is a function of the bath topology and $N_\mathrm{bath}$,
 i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic levels coupled to the
+element corresponds to an independent electronic level coupled to the
 impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
-We indicate with $N_\mathrm{s}=N_i + N_\mathrm{b}$ the total number of electronic levels.
+We indicate with $N_\mathrm{s}=N_\a + N_\mathrm{b}$ the total number of electronic levels.
 
@@
 S_-\HH_\mathrm{e}^{\otimes n}$ the electronic Fock space,  $\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}$ the
-phonon Fock space,  $\HH_\mathrm{ph}=\{\ket{0},\ket{1},\dots,\ket{N_\mathrm{ph}}\}$ is the local phonon Hilbert space
+phonon Fock space,
+$\HH_\mathrm{e}$ is the local electronic Hilbert space, 
+$\HH_\mathrm{ph}=\{\ket{0},\ket{1},\dots,\ket{N_\mathrm{ph}}\}$ is the local phonon Hilbert space
 and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
 The total dimension of the Fock space is
-$D=D_\mathrm{e}\cdot D_\mathrm{ph}=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)$ making the exponential
-growth with the number of electron levels transparent. 
+$D=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)=D_\mathrm{e}\cdot
+D_\mathrm{ph}$, which spotligths the exponential
+growth with the number of electron levels. 
 The quantum states in the space $\FF$ are naturally represented in

### 2025-05-08 04_cbinding.tex
Short description and installation instructions for edipack2triqs

@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Interoperability}\label{SecInterop}
@@
 
-\subsubsection{Installation}\label{sSecInteropCbindingsInstallation}
+\subsubsection{Installation and inclusion}\label{sSecInteropCbindingsInstallation}
 The C-binding module in included in the build process of \NAME and
@@
 loading methods outlines in \secu{sSecInstallOSloading}.
+
+The C/C++ compatible functions and variables 
+are declared in the header file  {\tt edipack2\_cbinding.h}.
+Since {\tt ISO\_C\_BINDING} only provides, to date, C compatibility, the 
+functions and variables are declared with C linkage, which prevents name mangling.
+Function overloading is not supported, hence all interfaced Fortran functions,
+for example supporting multiple input variables combinations with different types
+and ranks, are here represented by multiple alternative functions.
+As an example, the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters, is callable in C++ in the following variants
+\begin{itemize}
+    \item  {\tt chi2\_fitgf\_single\_normal\_n3}: for {\tt ED\_MODE=NORMAL/NONSU2}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_normal\_n5}: for {\tt ED\_MODE=NORMAL/NONSU2}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n3}: for {\tt ED\_MODE=SUPERC}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n5}: for {\tt ED\_MODE=SUPERC}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
+\end{itemize}
+and analogous functions for the real-space DMFT case. All functions are listed and documented in the online manual.
+When using EDIpack2 functions in a C/C++ program, care must be taken in the way arrays are passed.
+Consistently with {\tt ISO\_C\_BINDING}, non-scalar parameters have to be passed as raw pointers.
+An array of integers containing the dimensions of the former need to be passed as well to allow for proper Fortran input parsing.
+A working C++ example is provided in the {\tt examples} folder of the EDIpack2 repository.
 
@@
 set the non-interacting part of the impurity Hamiltonian
-$h^0_{\a\b\s\s'}$ through the functions {\tt set\_Hloc}.
+$h^0_{\a\b\s\s'}$ through the functions {\tt set\_Hloc}, as well as the
+interaction Hamiltonian through {\tt add\_twobody\_operator}.
 
@@
 {\tt set\_Hreplica/general\_{site,lattice}\_d{3,5}}. 
-The crucial part in a DMFT framework is the optimization of the bath
+The crucial part in the DMFT-Lanczos self-consistency loop is the optimization of the bath
 through conjugate-gradient algorithm. To this end we interfaced a
@@
 user bath array.
-
-Finally, in order to ensure compatibility to C and C++ language the
-entire set of C-binding functions and variables is enclosed into a
-header file {\tt edipack2\_cbinding.h}.
 
@@
 \subsection{TRIQS interface}\label{sSecInteropTRIQS}
-{\color{red} Igor }
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
+A thin compatibility layer between \NAME and the Toolbox for Research on 
+Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called edipack2triqs 
+is available as a stand-alone project. It is a pure Python package that is 
+built upon \NAME's Python API  (Sec.~\ref{sSecInteropEDIpy}) and provides a 
+limited object-oriented interface to the most important features of \NAME. 
+edipack2triqs strives to offer seamless interoperability with other 
+tools based on TRIQS by adopting the data storage formats, conventions and 
+usage patterns common to other TRIQS-based impurity solvers, such as 
+TRIQS/CTHYB\cite{Seth2016CPC}.
+
+\subsubsection{Installation}\label{sSecInteropTRIQSInstallation}
+The package depends on \NAME (which ultimately depends on SciFortran), EDIpy2
+and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
+installed in the OS, the current development version of edipack2triqs can be 
+installed with {\tt pip} from its 
+\href{https://github.com/krivenko/edipack2triqs}{GitHub repository} as follows:
 
@@
 
+\paragraph{Anaconda}
+Another option for installing the package is by using the Anaconda package 
+manager on Unix/Linux systems.
+The following commands will create a new {\tt conda} environment named 
+`edipack' and install the most recently released version of edipack2triqs along 
+with its dependencies (\NAME, EDIpy2 and the TRIQS libraries).
+
+\begin{lstlisting}[style=mybash]
+conda create -n edipack
+conda activate edipack
+conda install -c conda-forge -c edipack edipack2triqs
+\end{lstlisting}
+
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-{\color{red} Giorgio, Alexander,?}
+\NAME is supported as alternative impurity solver by the w2dynamics DMFT package\cite{Wallerberger2019CPC}.
+The only prerequisite to use this option is the presence of a functioning EDIpy2 installation, which w2dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
+
+In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt   EDIPACK}.
+Configuration specific to the exact diagonalization solver can be performed through the parameters in section {\tt EDIPACK} of a w2dynamics parameter file.
+For most of the \NAME input variables, it provides a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set insofar as this is supported by the interface and not an option available through generic w2dynamics parameters.
+This thus includes some parameters that the user will ordinarily want to change from their defaults in a typical calculation such as the number of bath sites {\tt NBATH} and other parameters such as options for the bath fitting and diagonalization algorithms, but also specifically excludes other typically set input variables such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}.
+All of the these variables correspond to or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
+Note however in particular that if the \NAME solver is used, {\tt beta} is by default only used as cut-off and does not imply a finite temperature calculation unless the user explicitly sets the parameter {\tt   ED\_FINITE\_TEMP} in section {\tt EDIPACK} to {\tt True}.
+
+Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in mostly the same way as it would be for the CT-HYB solver.
+This e.g.
+means that results such as the Green's functions are stored into the w2dynamics HDF5 output file in the typical format, and that w2dynamics uses only its own code for e.g.
+calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+As a consequence of this, some functionality that would require specific support from w2dynamics that is not available as of the time of publication can not be used through the interface, e.g.
+calculations with superconductivity or with phonons.
 
 \subsection{EDIjl, the Julia API}\label{sSecInteropEDIjl}
-{\color{red} Lorenzo?}
+
+The c-bindings approach is extremely handy, in that is opens the way for interoperability 
+with a large number of languages and frameworks. As an example, an experimental Julia API 
+is provided in the EDIpack github repository. Rather than a fully functioning Julia package, 
+this is at present a proof of concept, capable of replicating the results of Fortran, C++ and
+python implementations for the Bethe lattice example driver.
+Its structure and operation mimicks that of the EDIpy2 layer, with minimal language-specific differences.
+
+The \NAME{} Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
+
+The library is searched upon loading the module, with the following order of priority:
+
+\begin{itemize}
+\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl2} will look there for the library first
+\item {\tt LD\_LIBRARY\_PATH}: for Linux systems
+\item {\tt DYLD\_LIBRARY\_PATH}: for Mac systems
+\end{itemize}
+
+\subsubsection{Structure}
+
+In partial analogy to the Python API, the global variables, but not the functions, are contained in a  {\tt struct} called {\tt global\_env}.
+
+Similarly to the C++ case, global variables and functions are loaded as raw pointers.
+As a consequence, it is important that the dimensions of the array-like variables (such as {\tt ULOC}) and, in general, the amount of memory occupied by each variable are correcty accounted for.
+This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
+Functions are called from the dynamic library, making use of the {\tt  ccall} procedure.
+As previously stated, as a consequence of the C linking conventions multiple alternative version of the interfaced Fortran procedures are present, to account for the different input variable combinations; the EDIjl2 wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+
+\subsubsection{Installation and usage}
+
+At present, the EDIpack Julia interface is not offered as a package. The git repository has to be cloned via
+
+\begin{lstlisting}[style=mybash]
+git clone https://github.com/EDIpack/EDIjl2.0.git
+\end{lstlisting}
+
+and the location of the source files needs to be included in the user program via
+
+\begin{lstlisting}[style=mybash]
+push!(LOAD_PATH, joinpath(@__DIR__, "PATH/TO/REPO/src"))
+\end{lstlisting}
+
+The EDIjl2 module can then be loaded via
+
+\begin{lstlisting}[style=mybash]
+using EDIjl2
+\end{lstlisting}
+
+The correct way to access global variables and functions is as in the following example:
+
+\begin{lstlisting}[style=mybash]
+EDIjl2.read_input("inputED.conf")
+ed = EDIjl2.global_env
+println("Nspin = ", ed.Nspin)
+ed.Nspin = 2
+\end{lstlisting}
+
+The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.
+
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
+At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
+If the \NAME{} library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
+The {\tt MPI\_COMM\_WORLD} communicator will need to be correctly initialized by the user as well, and the program will need to be run with {\tt  mpiexec/mpirun}.
+
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIjl2.0 repository.
+This script is intended to be run serially.
+Documentation of the API and further examples are being developed.
+\end{document}

### 2025-05-08 edipack2.tex
GB halfway through the iRDM section (currently 3.10) I found a seemingly wrong statement that I want to discuss with AA.
GB: heavy rewrite of the iRDM (3.10) section
Summation indices were misleading, the normal case was written (in the formula) to be diagonal, which is not for Norb > 1. The listing were correct, so it was just a matter of notational mess. I also added a formal proof to why the normal iRDM is block-diagonal with respect to impurity Nup and Ndw sectors.
It should read pretty smooth now.

I also edited many sub- and super-scripts, adding the usual \mathrm{}, when they are words

@@
 \llength=1.38ex\relax
-\usepackage{xcolor}
+\usepackage[dvipsnames]{xcolor}
 \usepackage{makecell}
 \usepackage{subfiles}
+\usepackage{comment}
+\newcommand{\fixme}[1]{{\color{BrickRed} #1}}
+\usepackage{xspace}
 
@@
 
+\definecolor{mymauve}{rgb}{0.58, 0, 0.82}
 \lstdefinestyle{mybash}{
@@
   keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
+  % It would be nice to have 'conda' here,
+  % but then 'conda-forge' gets highlighted too.
+  morekeywords={*,git,mkdir,cmake,make,pip},
+  mathescape,
+  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
+}
+
+\lstdefinestyle{cstyle}{
+  frame=lines,
+  language=c,
+  basicstyle=\footnotesize,
+  stringstyle=\ttfamily,
+  commentstyle=\itshape,
+  fontadjust=true,
+  keywordstyle=\color{red},
+  % morekeywords={*,...},
   mathescape,
@@
 
-\newcommand{\onlinecite}[1]{\nocite{#1}\hspace{-0.1cm}\citenum{#1}}
+\newcommand{\onlinecite}[1]{\nocite{#1}\!\!\!\citenum{#1}}
 
@@
 \newcommand{\equ}[1]
-{Eq.~(\ref{#1})}
+{Eq.\,(\ref{#1})}
 
 \newcommand{\figu}[1]
-{Fig.~\ref{#1}}
+{Fig.\,\ref{#1}}
 
 \newcommand{\secu}[1]
-{Sec.~\ref{#1}}
+{Sec.\,\ref{#1}}
 
@@
 \def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}\,}
+\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}}
 \def\det{{\rm det}\,}
@@
 \def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
+\def\NAME{{\rm EDIpack2}\xspace}
 
@@
 \author[d]{G.~Bellomia}
-\author[a,d,c,d,e,f,g,h,i]{...}
+ \author[c]{A.~Kowalski}
+\author[e]{F.~Petocchi}
+ \author[f]{M.~Wallerberger}
+ \author[g]{G.~Mazza}
+ \author[h]{L.~de Medici}
+ \author[c,b]{G.~Sangiovanni}
+ \author[d,i]{M.~Capone}
+\author[i]{A.~Amaricci}
 % \author[]{A.~Scazzola}
-% \author[]{F.~Petocchi}
-% \author[]{A.~Kowalski}
-% \author[]{M.~Wallerberger}
-% \author[]{G.~Mazza}
-% \author[]{L.~de Medici}
-% \author[]{G.~Sangiovanni}
-% \author[]{M.~Capone}
-\author[i]{A.~Amaricci}
 
@@
 \address[d]{\SISSA}
-\address[e]{\TUW}
-\address[f]{Politecnico di Torino, Turin, Italy}
-\address[g]{\Geneve}
-\address[h]{\UPISA}
-\address[i]{\ESPCI}
-\address[j]{\CNRIOM}
+\address[e]{\Geneve}
+\address[f]{\TUW}
+\address[g]{\UPISA}
+\address[h]{\ESPCI}
+\address[i]{\CNRIOM}
+% \address[]{Politecnico di Torino, Turin, Italy}
 % \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
@@
 \section{Conclusions}
+{\color{red} Tentative conclusions}
+We have presented EDIpack2, a versatile, high-performance solver for
+generic quantum impurity problems. Leveraging on the massively
+parallel algorithms introduced with its predecessor, this version of
+the library features new capabilities and symmetries within a unified
+framework, providing reliable evaluations of the dynamical correlation
+functions on arbitrary complex argument.
+This makes it particularly well-suited for capturing the sharp
+low-energy excitations and complex spectral features of strongly
+correlated systems. We have shown that this new version enables the evaluation of impurity
+reduced density matrices directly from Fock space quantities and thus unlock 
+quantum information analyses of correlated systems.
+
+A central feature of EDIpack2 is its strong focus on interoperability,
+achieved through modern Fortran constructs, C/C++-bindings, and
+comprehensive APIs for Python (EDIpy2). 
+These interfaces enable seamless integration with broader
+computational frameworks like TRIQS and W2Dynamics, expanding the
+functionality of these platforms and providing a robust foundation for
+reproducible research.
+
+We thoroughly discussed the implementation of the EDIpack2 library, the
+most important algorithms and classes. We presented in
+details the third-party interfaces which extend exact diagonalization
+capabilities beyond the realm of the library itself.   
+Finally, we showcased the use of the EDIpack2 software in different
+contexts via elaborated example which can serve as reference for the
+potential users.
+
+The modular and extensible design of EDIpack2 provides a
+natural foundation for future extensions, for instance to cluster-DMFT where the
+impurity problem is generalized to include clusters of interacting
+sites. This approach would enable the treatment of spatial
+correlations beyond the single-site approximation, capturing effects
+such as d-wave pairing in high-temperature superconductors, charge
+order, and complex spin textures in strongly correlated systems.
+We anticipate that EDIpack2 will become a valuable tool for the
+computational condensed matter community, supporting a wide range of
+studies on strongly correlated materials and providing a reliable
+reference platform for quantum impurity solvers.
 
@@
 
+(for the arXiv version only... ?)
+
+Lei ha clacsonato?
+
+Tu ha clacsonato?
+
+Tarapia tapioco, prematurata l'interfaccia, o scherziamo?
+Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico basato su C++ e utilizzante la toolchain di LLVM anche per Linux e Mac Os soltanto in due, oppure in quattro anche scribai con il file sorgente {\tt hm\_bethe.mc}?
+
+Come {\tt https://github.com/lcrippa/prematurata\_la\_dmft} per esempio.
+No dico, mi porga il file {\tt bagaglio.cpp}.
+Le vede le funzioni?
+Lo vede che interfacciano gli array, non supportati da Monicelli, e prematurano anche?
+Ora io le direi, anche con il rispetto per l'autorità, anche solo le due parole come install Monicelli from {\tt https://github.com/esseks/monicelli.git} and run Make which compiles and links the main file {\tt hm\_bethe.mc}, per esempio.
+Basta così, mi seguano nel programma di test.
+No no, Attenzione: loop dmft completo supportato secondo la ref.
+\cite{EDIpack} abbia pazienza.
+Se no, plotta i dati, anche un pochino Green's function e Self-energy in prefettura.
+Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.
+
+Si farà finta di passar da bischeri.
+
 %% References with bibTeX database:

### 2025-05-09 03_edipack2.tex
Updated text in 03_edipack2 till 1.7 Lanczos Diagonalization.

@@
 \subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem defined by the
-following Hamiltonian:
+We consider a general quantum impurity problem described by the Hamiltonian:
 $$
@@
 $$
-which describes a  multi-orbital interacting quantum
-impurity coupled to an electronic bath and to local, i.e. Holstein,
-phonons. We assume for the moment that no particular symmetry
-holds. We separate the impurity part of the Hamiltonian into a
-quadratic and interacting term: 
+which describes a multi-orbital quantum impurity
+coupled to an electronic bath and local phonons (e.g., Holstein
+modes). For now, we assume no specific symmetries.
+
+\subsubsection{Impurity Hamiltonian}
+The impurity Hamiltonian is split into a quadratic and an 
+interacting part:
 \begin{equation}\label{Himp}
-  \begin{split}
-    \hat{H}_\mathrm{imp} & = \hat{H}^0_\mathrm{imp} + \hat{H}^\mathrm{int}_\mathrm{imp}\\
-    \hat{H}^0_\mathrm{imp} & =
+  \hat{H}_\mathrm{imp}  = \hat{H}^0_\mathrm{imp} + \hat{H}^\mathrm{int}_\mathrm{imp}
+\end{equation}
+where
+\begin{equation}\label{H0imp}
+  \hat{H}^0_\mathrm{imp}  =
   \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
-\end{split}
 \end{equation}
-where $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the destruction (creation)
-second-quantization operators for impurity electrons in the
+represents the quadratic part, with $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the annihilation (creation)
+operators for impurity electrons in 
 orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-with spin $\sigma=\up,\dw$ and whose occupation is described
-by the  operator  
-$n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$. 
-The internal structure of the non-interacting part is described by the
-$h^{0}_{\a\b\sigma\sigma'}$ matrix. 
-%
-The
-interaction term $\hat{H}^{\mathrm{int}}$ of the Hamiltonian can, in principle, consist of any set
-of two-body quantum operators of the form
-$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. However, we also
-consider the  local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ACMP}:   
+and spin $\sigma=\up,\dw$.  The occupation number operator is defined
+as  $n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$.
+The internal structure of the non-interacting part is captured by the 
+matrix $h^{0}_{\a\b\sigma\sigma'}$, which can include 
+orbital-dependent on-site energies, spin-orbit coupling or other 
+single-particle terms.
+
+The interaction part of the impurity Hamiltonian, 
+ $\hat{H}^{\mathrm{int}}$ can in principle contain any 
+set of two-body operators of the form
+$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
+However, we typically 
+adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ACMP}:
 \begin{equation}\label{Hint}
@@
 $U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The remaining two terms are, respectively, the spin-exchange and
-pair-hopping which we considered with their respective independent
-couplings $J_X$ and $J_P$.
-In the case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
+The final two terms are, respectively, the spin-exchange ($J_X$) and
+the pair-hopping ($J_P$).
+In the three-orbital case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
 U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
@@
 
-The bath part and its coupling to the impurity have the form: 
+\subsubsection{Bath and Hybrization}
+The coupling between the impurity and the bath is described by
 \begin{equation}\label{Hbath}
@@
 \end{equation}
-where $p=1,\dots,N_\mathrm{bath}$ is an index running over a finite number of
-bath elements, $a_{p\alpha\sigma}$ ($a^+_{p\alpha\sigma}$) are the destruction (creation) operators for
-the bath electrons with index $p$, orbital $\alpha$ and
-spin $\sigma$.
-The  properties of each bath level are described by the
-matrix $h^p_{\a\b\sigma\sigma'}$. As such any bath element can be
-composed of several electronic levels according the bath topology, which will be discussed further in the following.
-Each bath level couples to the impurity with an amplitude
-$V^p_{\a\b\s\sigma'}$ which we assume to depend on all orbital and spins.
-
+where $p=1,\dots,N_\mathrm{bath}$ indexes the
+bath elements. The operators $a_{p\alpha\sigma}$
+($a^+_{p\alpha\sigma}$) correspond to the destruction (creation) of
+bath electrons with index $p$, orbital $\alpha$ and spin $\sigma$.
+Any bath element can be composed of several electronic levels
+according the chosen bath topology. The  properties of each bath level are described by the
+matrix $h^p_{\a\b\sigma\sigma'}$ and couples to the impurity through an amplitude
+$V^p_{\a\b\s\sigma'}$.
+
+\subsubsection{Electron-Phonon coupling}
 Finally, the electron-phonon part of the quantum impurity problems is
@@
 \end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, $b_q$
-($b_q^+$) are the destruction (creation) operators for the phonon $q$
-with frequency $\omega_{0q}$. The matrix  $g_{\a\b}$ expresses is the electron-phonon coupling. 
+where $q=1,\dots,N_q$ indexes the number of local phonons, and $b_q$
+($b_q^+$) are the destruction (creation) operators for a phonon with
+frequency $\omega_{0q}$.
+The matrix  $g_{\a\b}$ describe the electron-phonon coupling. 
 Although feasible, dealing with more than one phonon mode becomes
@@
 work we shall consider $N_q=1$.
-In the following we consider a bath discretized into a  number
+
+\subsubsection{System setup}
+We consider a bath discretized into a  number
 of bath degrees of freedom and a finite number of available phonons $N_\mathrm{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert space.
+to cut-off the unbounded dimensions of the local phonons Hilbert
+space.
+In the rest of this work we consider a system composed of $N_\mathrm{imp}=1$
+impurities, i.e. a single impurity problem, $N_\mathrm{bath}$ bath elements
+and $N_\mathrm{ph}$ phonons.
+The total size of the system is determined by the (fixed)
+number of phonons (fixed) $N_\mathrm{ph}$, the number of impurity orbitals 
+$N_\a$ and that of the bath levels  $N_\mathrm{b}$. The latter is a
+function of  the bath topology and $N_\mathrm{bath}$.
+In the simplest case each bath
+element corresponds to an independent electronic level coupled to the
+impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$.
+The total count of electronic levels is  $N_\mathrm{s}=N_\a +
+N_\mathrm{b}$.
+
+The setup of the quantum impurity problem is implemented in {\tt
+  ED\_SETUP} through the input variables {\tt Nspin}$=N_\sigma$,
+{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_\mathrm{bath}$ globally defined {\tt
+  ED\_INPUT\_VARS}. The {\tt Ns}$=N_\mathrm{s}$ variable, evaluated in
+{\tt ed\_setup\_dimensions}, corresponds to the total number of
+electronic levels. 
+The local non-interacting Hamiltonian
+$h^0_{\a\b\s\s'}$ is specified using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
+The setup of the bath matrices $h^p_{\a\b\s\s'}$
+requires a more involved procedure which will be illustrated in
+\secu{sSecBath}.
 
@@
 
-In the rest of this work we consider a system composed of $N_\mathrm{imp}=1$
-impurities, i.e. a single impurity problem, $N_\mathrm{bath}$ bath elements
-and $N_\mathrm{ph}$ phonons. The size of the system is determined by
-the number of phonons (fixed) and that of electronic levels. 
-The single impurity contains $N_\a$ electronic levels.
-The total number of levels is then determined by
-the number of electronic levels $N_\mathrm{b}$ assigned to the bath.
-The latter number is a function of the bath topology and $N_\mathrm{bath}$,
-i.e. the number of bath elements. In the simplest case each bath
-element corresponds to an independent electronic level coupled to the
-impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
-We indicate with $N_\mathrm{s}=N_\a + N_\mathrm{b}$ the total number of electronic levels.
-
-The setup of the general quantum impurity problem is implemented in
-different parts of the \NAME software. The dimensions of the system
-are controlled by input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_\mathrm{bath}$ in {\tt
-  ED\_INPUT\_VARS}. These are used to
-determine the variables {\tt Ns}$=N_\mathrm{s}$ and $N_\mathrm{b}$, defined in the global
-memory pool {\tt ED\_VARS\_GLOBAL}, using the functions contained
-in {\tt ED\_SETUP}. 
-The user can define the local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
-The matrix is then stored in the internal memory and shared throughout the
-code.
-On the other hand the setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
-\secu{sSecBath}.
-
 \subsection{The Fock basis states}\label{sSecBasis}
-The Fock space of the quantum impurity problems is defined as
-$\FF=\FF_\mathrm{e}\otimes \FF_\mathrm{ph}$, with $\FF_\mathrm{e}=\bigoplus_{n=0}^{N_\mathrm{s}}
-S_-\HH_\mathrm{e}^{\otimes n}$ the electronic Fock space,  $\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}$ the
-phonon Fock space,
-$\HH_\mathrm{e}$ is the local electronic Hilbert space, 
-$\HH_\mathrm{ph}=\{\ket{0},\ket{1},\dots,\ket{N_\mathrm{ph}}\}$ is the local phonon Hilbert space
-and ($S_-$)  $S_+$ the (anti-)symmetrization operator.  
+The Fock space of the quantum impurity problem is defined as
+$\FF=\FF_\mathrm{e}\otimes \FF_\mathrm{ph}$, where $\FF_\mathrm{e}=\bigoplus_{n=0}^{N_\mathrm{s}}
+S_-\HH_\mathrm{e}^{\otimes n}$ is the electronic Fock space built 
+from the local electronic Hilbert space $\HH_\mathrm{e}$, and 
+$\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}$
+is the
+phonon Fock space, with local phonon Hilbert space
+$\HH_\mathrm{ph}=\{\ket{0},\ket{1},\dots,\ket{N_\mathrm{ph}}\}$. 
+Here ($S_-$) $S_+$ is the (anti-)symmetrization operator.
+
 The total dimension of the Fock space is
 $D=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)=D_\mathrm{e}\cdot
-D_\mathrm{ph}$, which spotligths the exponential
-growth with the number of electron levels. 
+D_\mathrm{ph}$, highlighting the exponential
+growth with the number of electronic levels.
+
 The quantum states in the space $\FF$ are naturally represented in
-terms of occupation number formalism of the second quantization,
-i.e. the Fock basis.
-For a system of $N_\mathrm{s}$ electrons each Fock state
-reads $\ket{p}\ket{\vec{n}}$ with
-\begin{equation}
-    \ket{\vec{n}}=\ket{\vec{n}_\up}\ket{\vec{n}_\dw}=\ket{n_{1\up},\dots,n_{N_\mathrm{s}\up},n_{1\dw},\dots,n_{N_\mathrm{s}\dw}},
-    \label{eq:FockState_|nupndw>}
+the occupation number formalism of second quantization,
+i.e., the Fock basis.
+For a system of $N_\mathrm{s}$ electrons, each Fock state
+is given as $\ket{p}\ket{\vec{n}}$, with
+\begin{equation} \label{eq:FockState_|nupndw>}
+    \ket{\vec{n}}=\ket{n_{1\up},\dots,n_{N_\mathrm{s}\up},n_{1\dw},\dots,n_{N_\mathrm{s}\dw}},
 \end{equation}
-where $p=1,\dots,N_\mathrm{ph}$ is the number of local phonons while $n_{a\sigma}=0,1$ signals the absence or the
-presence of an electron with spin $\sigma$ at the level $a$.
-The electronic part of the Fock state $\ket{\vec{n}}$ is represented as a string of
-zeros and ones of length $2N_\mathrm{s}$. Thus, any such state can  be encoded
-in a computer using a sequence of $2N_\mathrm{s}$ bits or, analogously, as a
-given integer $I=0,\dots 2^{2N_\mathrm{s}}-1$ so that $\ket{\vec{n}}=\ket{I}$.  
-Together with the basis states one defines  destruction and creation 
-operators, respectively $c_{a\s}$ and $c^+_{a\s}$, which acts on the
-Fock space as: 
-$\ket{\vec{n}}$ as:  
+where $p=1,\dots,N_\mathrm{ph}$ is the number of local phonons and
+$n_{a\sigma}=0,1$ indicates the absence or 
+presence of an electron with spin $\sigma$ at level $a$.
+
+The electronic part of the Fock state $\ket{\vec{n}}$ is represented
+as a binary string of length $2N_\mathrm{s}$. Thus, any such state can be encoded
+in a computer using a sequence of $2N_\mathrm{s}$ bits, or equivalently, as an integer $I=0,\dots 2^{2N_\mathrm{s}}-1$ such that $\ket{\vec{n}}=\ket{I}$.
+
+Destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
+respectively, act on the Fock space as:
 \begin{align*}
@@
 \end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ takes care
-of the fermionic sign imposed by Pauli principle.
-
-The Fock states and operators implementation can be found in {\tt
-  ED\_AUX\_FUNX}. There we define the bitwise action of generic fermionic creation
-and annihilation operators {\tt CDG} and {\tt C}, the binary
-decomposition {\tt bdecomp} required to reconstruct the Fock state as
-bits sequence and other accessory functions.
+where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ accounts for the fermionic sign imposed by the Pauli principle.
+
+The implementation of Fock states and operators can be found in 
+{\tt ED\_AUX\_FUNX}. In particular, in this module we define the bitwise action 
+of fermionic creation and annihilation operators as functions 
+{\tt CDG} and {\tt C}, used throughout the code. Additionally, 
+we provide the function {\tt bdecomp} for reconstructing the Fock 
+state bit sequence from the integer representation.
 
 \subsection{Conserved quantum numbers}\label{sSecQNs}
-In order to circumvent the exponential scaling of the dimensions of
-the problem scales it is necessary to take into account suitable symmetries.
-Indeed, considering operators ${\cal Q}$ such that $[H, {\cal Q}]=0$
-reduces of the Fock space into several symmetry sectors
-labeled by given quantum numbers $\vec{Q}$. 
-In the context of quantum impurity problems two symmetries are often considered: i)
-conservation of the total occupation $N$ and ii) the
-conservation of the total magnetization $S_z$. Although the total spin
-operator $S^2$ can also be conserved, the difficult  implementation
-and the marginal gain makes it often non convenient to include this symmetry.
-In \NAME we consider three different cases which are controlled by the
-input variable {\tt ed\_mode}={\bf normal}, {\bf superc}, {\bf
-  nonsu2}.
-
-The {\bf normal} case deals with independent conservation of the total occupation $N$
-and the total magnetization $S_z$ or, equivalently, the total number of electrons with spin up $N_\up$ and down
-$N_\dw$. Optionally, we consider the case in which the symmetry
-applies separately for each orbital and spin,
-i.e. $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This special case has been
-extensively discussed in \onlinecite{Amaricci2022} so it won't be covered in
-this work.
+To mitigate the exponential scaling of the Fock space dimension, it 
+is essential to exploit suitable symmetries. Specifically, if the 
+Hamiltonian $H$ commutes with a set of operators ${\cal Q}$ such that 
+$[H, {\cal Q}] = 0$, the Fock space can be decomposed into smaller, 
+disjoint symmetry sectors labeled by quantum numbers $\vec{Q}$.
+
+In the context of quantum impurity problems, two commonly used 
+symmetries are: i) conservation of the total charge $N$ and ii) 
+conservation of the total magnetization $S_z$. Although the total 
+spin operator $S^2$ may also be conserved, its implementation is 
+computationally challenging and typically provides only marginal 
+gains, making it less practical in many cases.
+
+In \NAME, three different symmetry configurations are available, 
+controlled by the input variable {\tt ed\_mode} = {\bf normal}, 
+{\bf superc}, or {\bf nonsu2}:
+
+ - The {\bf normal} case conserves both the total occupation $N$
+and the total magnetization $S_z$, or equivalently, the total number
+of electrons with spin up $N_\up$ and down $N_\dw$.
+Optionally, the symmetry
+can be extended to act indipendently to each orbital and spin
+component, i.e., $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
+specific case is discussed extensively
+Ref.~[\onlinecite{Amaricci2022}] and will not be further covered here.
+
 %
-The {\bf superc} case deals with the conservation of the total
-magnetization only, so that total charge may not be conserved. This
-case includes a description of $s$-wave superconductivity, featuring
-intra- and inter-orbital components.
-%
-Finally, the {\bf nonsu2} case consider the conservation of the total
-charge, whereas the spin symmetry group is not fully
-conserved. Although there many possible realization of this scenario,
-this particularly applies to the presence of local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, the emergence of in-plane spin ordering~\cite{BellomiaKMH} or
+
+- The {\bf superc} case maintains onlu the $S_z$ conservation,
+allowing the total charge to not be conserved. This setting captures
+system with $s$-wave superconductivity, including 
+intra- and inter-orbital pairing.
+
+- The {\bf nonsu2} case conserves the total
+charge $N$ while allowing spin symmetry group to be not conserved.
+This scenario catpures effects such as local spin-orbit coupling
+$\vec{L}\cdot\vec{S}$~\cite{something}, in-plane spin ordering~\cite{BellomiaKMH} or
 in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.
-%
-From a computational point of view the construction of a symmetry
-sector corresponds to the determination of a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ relating the states $\ket{i}$
-belonging to the sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-Fock space. Operatively, the map corresponds to an integer rank-1
-array of dimension $D_\SS$ which is the {\it dimension} of the
-sector. 
-The table~\ref{TabSector} summarizes the properties of the symmetry
-sectors.
-
+
+From a computational perspective, constructing a symmetry
+sector amounts to defining a injective map
+$\MM:\SS_{\vec{Q}}\rightarrow \FF$ which relates the states $\ket{i}$
+within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
+full Fock space.
+This map is typically implemented as a rank-1
+integer array, whose size corresponds to the dimension of the sector.
+
+The {\bf normal} case deserves a special note. Since $N_\up$ and
+$N_\dw$ are conserved independently, the local Hilbert
+space and the electronic Fock space can be factorized as
+$\HH_e=\HH_{e\up}\otimes\HH_{e\dw}$ and $\FF_\mathrm{e} = \FF_{e\up}\otimes \FF_{e\dw}$, respectively.  
+Consequently, each Fock state can be written as a product
+$\ket{\vec{n}_\up} \ket{\vec{n}_\dw}$. This factorization splits the
+symmetry sector as $\SS_{\vec{Q}} = \SS_{N_\up}\otimes\SS_{N_\dw}$,
+and finally the sector map can be expressed as the product $\MM = \MM_\up
+\otimes \MM_\dw$.
+
+Each state $\ket{i}=\ket{i_\up} \ket{i_\dw}$ in this factorized basis
+is labeled by two integers $[i_\up,i_\dw]$, with 
+$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
+D_{\SS_\dw}$.
+The maps $\MM_\sigma$ then connect these basis states to Fock states
+$\ket{I}=\ket{I_\up}\ket{I_\dw}$, labeled by two integers
+$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_\mathrm{s}}$.
+For a more
+detailed discussion on the structure of the Fock basis in this case, see Ref.~[\onlinecite{Amaricci2022}].
+
+The presence of a symmetry reduces the Hamiltonian matrix to
+a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
+$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix.
+In the {\bf normal} case this block structure is particularly
+symmetric due to the factorized nature of the sectors as discussed
+above, see also Ref.~[\onlinecite{Amaricci2022}].
+The analysis of the spectrum is then reduced toinspecting the
+Hamiltonian within each symmetry sector, or to a subset thereof if a
+additional constraints are present.
+A summary of the sector properties is provided in
+Table~(\ref{TabSector}). 
 \begin{table}%[ht]
@@
 \end{center}
-\caption{Ciao}
+\caption{
+  {\bf Quantum Numbers Table}.
+A table summarizing the possible values of the input variable {\tt
+  ed\_mode} selecting the symmetries of the problem. To each value
+(first column) correspond different quantum numbers (second column).
+The third column report the dimension of the symmetry sector for a
+given realization of the quantum numbers.}
 \end{table}
 
-The {\bf normal} case requires a brief remark. Because of the
-independent conservation of $N_\up$ and $N_\dw$, the local Hilbert
-space and the electronic Fock can be factorizes as, respectively,
-$\HH=\HH_\up\otimes\HH_\dw$, $\FF_\mathrm{e} = \FF_{e\up}\otimes \FF_{e\dw}$.  
-Accordingly any Fock state is written as $\ket{\vec{n}_\up}\ket{\vec{n}_\dw}$, the symmetry sector can be written as  $\SS_{\vec{Q}} = \SS_{N_\up}\otimes
-\SS_{N_\dw}$ and, correspondingly, the sector map splits in two
-mutually exclusive ones $\MM = \MM_\up
-\otimes \MM_\dw$.
-Thus, each state $\ket{i}=\ket{i_\up}\ket{i_\dw}$ of the
-sector is labeled by two integers $[i_\up,i_\dw]$, 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$. The map $\MM$ connects any such state to a Fock state
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$ labeled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_\mathrm{s}}$. For a thorough
-discussion about Fock basis organization in this case see
-\onlinecite{Amaricci2022}.
-
-The presence of a symmetry induces a factorization of the Fock space,
-in turn inducing a block diagonal form to the Hamiltonian matrix.
-Each block, labeled by the quantum numbers $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix. In the {\bf
-  normal} case $H_\SS$ takes a particularly symmetric form thanks to
-the product structure of the sector and its map~\cite{Amaricci2022}.
-The analysis of the spectrum is then reconducted to the inspection of
-the Hamiltonian in each symmetry sector. Should particular constraint
-holds the search can be limited to only particular sector, further
-reducing the computational cost.
-
-Although the sectors have dimensions much smaller than the full Fock
-space, for large systems storing the Hamiltonian matrix in the memory
-can still be highly inefficient.
-In such cases, Krylov or Lanczos methods~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996} can
-be implemented using a storage-free algorithm, performing the
-necessary linear operations on-the-fly.
-This solution has generally a negative impact on the execution
-time, however this can be well compensated by scaling in a distributed 
-parallel framework.
-
-The object {\tt sector}, defined globally in {\tt
-  ED\_VARS\_GLOBAL}, contains all the informations characterizing the
-symmetry sector, its dimensions, its quantum numbers and an
-implementation of the map $\MM$. The constructor/destructor are defined {\tt
-  ED\_SECTORS} module with the function {\tt build\_sector}/{\tt
-  delete\_sector} using different algorithms according to the nature
-of the quantum numbers $\vec{Q}$ as reported in the following code
-snippet.
+% Although the sectors have dimensions much smaller than the full Fock
+% space, for large systems storing the Hamiltonian matrix in the memory
+% can still be highly inefficient. In such cases, any Krylov  subspace  
+% method~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996}
+% can be implemented using a storage-free algorithm, performing the
+% necessary linear operations on-the-fly.
+% This solution has generally a negative impact on the execution
+% time, however this can be well compensated by scaling in a distributed 
+% parallel framework.
+
+In \NAME the implementation of symmetry sectors is managed through the
+{\tt sector} object, which is defined in {\tt
+  ED\_VARS\_GLOBAL}. This object contains all the revelant
+informations for defining the symmetry, inclduing the sector
+dimensions, quantum numbers and the map $\MM$. The constructor
+(destructor) for this object is defined in the {\tt
+  ED\_SECTORS} module via the functions {\tt build\_sector}
+(constructor) and {\tt
+  delete\_sector} (destructor).
+These functions use different algorithms depending on the nature 
+of the quantum numbers $\vec{Q}$. The following  code
+snippet summarize the various available implementations:
 \setbox0=\hbox{%
@@
 \end{tabular}
-%
-Alongside these definitions, this module additional functions to
-retrieve sector index or quantum number informations. Another set of
-key functions concern the application of arbitrary linear combinations
-of Fock operators  to a given vector $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{\dagger(p_i)}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. These important operations which depend on
-the sector informations are implemented
-in the {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops} functions within {\tt ED\_SECTORS}.
+
+In addition to the basic construction and destruction routines, the
+{\tt ED\_SECTORS} module also includes functions to
+retrieve sector indices and quantum number
+informations. Furthermore, it provdes a set of
+essential functions for applying arbitrary linear combinations
+of operators to a given Fock state $\ket{v}\in\SS$, i.e.
+$\OO\ket{v} = \sum_i a_i C^{p_i\dagger}_{\a_i,\s_i}\ket{v}$ with
+$a_i\in\CCC$ and $p_i=0,1$. This functionality is implemented through
+the functions {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
+apply\_Cops}, which  are widely used throughout the code.
 
 \subsection{Interaction setup}
-\NAME offers two distinct ways to setup the interaction term in \equ{Himp}. 
-The Hubbard-Kanamori interaction \equ{Hint} is supported natively, via the user-accessible
-variables {\tt ULOC}$=U$, {\tt UST}$=U^{'}$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP
-}$=J_{p}$.These parameters can be specified in the input file, and they will be read and 
-set if the flag {\tt ED\_USE\_KANAMORI} is set to {\tt T}. This is the default option.
-If the interaction Hamiltonian is provided via {\tt ED\_USE\_KANAMORI}, {\tt NORB} is limited to a maximum of {\tt 5}.
-
-Alternatively, the list of two-body operators can be provided by the user in a properly
-formatted text file, the name of which is specified in the {\tt UMATRIX\_FILE} input variable. The file has to have the suffix {\tt \\.restart}.
-Such file needs to be formatted in the following way
-
+The \NAME code offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}. 
+The generalized Hubbard-Kanamori interaction, as defined in \equ{Hint}, is natively
+supported and controlled by the input parameters {\tt ULOC}$=U$, {\tt
+  UST}$=U^{'}$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP}$=J_{p}$.
+These quantities can be specified either in the input file or directly
+via the the command line, provided the logical input parameter {\tt
+  ED\_USE\_KANAMORI} is set to {\tt T}. In this mode, the maximum
+number of impurity orbitals {\tt NORB}$=N_\a$ is limited to $5$.
+
+Alternatively, a list of two-body operators can be provided by the user in a properly
+formatted text file, whose name is specified by the input variable {\tt
+  UMATRIX\_FILE}. The implementation of the list of interaction terms is contained in
+the class {\tt ED\_PARSE\_UMATRIX}.  
+The file mush have the suffix {\tt \\.restart} and should be formatted
+as follows: 
 \begin{lstlisting}[style=mybash]
@@
 \end{lstlisting}
-
-where {\tt NORB} is the numer of orbitals.
+where {\tt NORB} is the numer of orbitals $N_\a$ and each line
+defines a single two-body term of the form 
+$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. Note tha the
+coefficient indices are swapped compared to the standard two-body
+operator formulation.  
 Empty lines and lines starting with {\tt \#, \%, !} are ignored.
-Notice the swapped indices in the coefficient with respect to the standard 2-body operator formulation $U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
-To enable reading an interaction matrix file, the flag {\tt ED\_READ\_UMATRIX} needs to be set in the input file.
-{\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI} are mutually exclusive, but they can be both false.
-Before the impurity problem is solved, the user can also provide interaction terms in the program or script. Extensive documentation is available at (\textcolor{red}{how should we do this?})
-All the interaction operators used in each call of the solver are listed and written in an output file, called {\tt UMATRIX\_FILE.used}.
+
+To enable the reading an interaction matrix file, the flag {\tt
+  ED\_READ\_UMATRIX} must be set to {\tt T}.
+Note that {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI},
+are mutually exclusive but can both be set to {\tt F}. 
+In this case, the user must 
+provide the interaction terms to the solver through the function 
+{\tt add\_twobody\_operator} in the calling program or script, before 
+the impurity problem is solved.
+
+For reference and future use, the interaction operators used in each 
+call to the solver are saved in the output file 
+{\tt UMATRIX\_FILE.used}.
 
 \subsection{Classes}
-The use of suitable objects enormously simplifies the  implementation
-of crucial mathematical concepts aking to the diagonalization of the
-quantum impurity problems. Here we discuss three main classes which
-are used in the code.
+The use of objects and classes greatly simplifies the implementation 
+of critical mathematical concepts required for solving quantum 
+impurity problems. This section provides an overview of the main 
+classes used in \NAME, focusing on their structure and functionality.
 
 \subsubsection{Sparse matrix}\label{CodeSparseMatrix}
-A sparse matrix storage is performed using a
-dedicated custom class, contained in the \texttt{SPARSE\_MATRIX} module. 
-The class defines a \texttt{sparse\_matrix\_csr} object as a 
-simplified hash-table. The keys corresponds to the rows of the matrix
-while the value is associated to a pair dynamical arrays, containing values and
-columns location of the non-zero elements of the sparse matrix.
-The \texttt{sparse\_matrix\_csr} object can be stored either serially,
-i.e. one copy per process, or be parallel distributed assigning a number of keys/values to each
-process.
-The elements are progressively stored in the dynamic arrays using
-\texttt{sp\_insert\_element} procedure, ultimately making use of the Fortran intrinsic
-\texttt{move\_alloc}.
-This ensures a faster execution compared to implicit  
-reallocation, i.e. \texttt{vec=[vec,new\_element]}.
-This solution enables to deal with the a priori unknown number of
-non-zero elements on each row, to optimize the memory footprint and
-to guarantee $O(1)$ access  to any element of the matrix, which are
-crucial aspect to speed-up the execution of the MVP.
-
-%GBtodo placeholder: I passed on this already (except I don't like the minipage of the listings)
+Sparse matrix storage is handled through a dedicated class in the 
+{\tt SPARSE\_MATRIX} module. This module defines the 
+{\tt sparse\_matrix\_csr} object, which stores sparse matrices as 
+hash tables. Each key corresponds to a row index, while the associated 
+value contains a pair of dynamic arrays: one for the non-zero matrix 
+elements and one for their respective column indices.
+
+Each instance of {\tt sparse\_matrix\_csr} can be stored in either 
+a serial manner (one copy per process) or distributed across multiple 
+processes, with rows dynamically assigned to each process. 
+Matrix elements are inserted using the 
+{\tt sp\_insert\_element} procedure, which leverages the Fortran 
+intrinsic {\tt move\_alloc} for faster execution compared to 
+implicit reallocation, i.e., {\tt vec=[vec,new\_element]}.
+
+This approach offers several key advantages, including efficient 
+memory management for matrices with unknown numbers of non-zero 
+elements per row, and $O(1)$ element access time, both of which 
+are critical for the efficient implementation of Krylov subspace 
+methods.
+
+%GBtodo placeholder: I passed on this already (except I don't like the
+%minipage of the listings)
+
 \subsubsection{Sparse map}\label{CodeSparseMap}
-As it will be evident in the following \secu{sSecRDM}, there are cases in
-which the sector construction requires to store, for any sector state,
-disjoint information about the corresponding Fock state.
-Let's consider a Fock state $\ket{I}$. Its bit decomposition
-$\ket{\vec{n}}$ can be further split into arbitrarily grouped chunks of bits.
-For instance, we can choose to group the bits into impurity and bath degrees of freedom,
-as $\ket{\vec{n}}=\ket{\vec{i}_\up\,\vec{b}_\up\,\vec{i}_\dw\,\vec{b}_\dw}$, where we 
-highlight the overall ordering in spin-up and spin-down parts underlying the whole
-codebase (see \equ{eq:FockState_|nupndw>} and the subsequent discussion).  
-The module {\tt ED\_SPARSE\_MAP} implements an hash-table {\tt sparse\_map}, 
-as a component of the {\tt sector} object, which stores for every impurity 
-configuration $\vec{i}_\s$ (\emph{key}) all the possible bath states $\vec{b}_\s$ (\emph{values})
-that are compatible with the given conserved quantum numbers (see \secu{sSecQNs}).
-The {\tt sparse\_map} ${\cal S}$ objects are constructed upon call of the {\tt
-  build\_sector} subroutine, automatically dispatched to a different algorithm 
+\fixme{GB: I don't like the minipage of the listing below.}
+As discussed in \secu{sSecRDM}, the construction of a symmetry 
+sector often requires associating each sector state $\ket{i}$ with 
+disjoint information about the corresponding Fock state $\ket{I}$. 
+In this context, the Fock state can be decomposed into bit chunks, 
+e.g., $\ket{\vec{n}} = \ket{\vec{i}_\up\,\vec{b}_\up\,
+\vec{i}_\dw\,\vec{b}_\dw}$, reflecting a natural grouping into impurity 
+and bath components and where we highlight the overall ordering in
+spin-up and spin-down parts (see \equ{eq:FockState_|nupndw>}).
+
+The {\tt ED\_SPARSE\_MAP} module provides an efficient hash-table 
+implementation, {\tt sparse\_map} which is part part of the {\tt
+  sector} object and stores the relation between these bit chunks. 
+Specifically, for each impurity configuration 
+$\vec{i}_\s$ (key), it maintains a list of compatible bath 
+configurations $\vec{b}_\s$ (values) consistent with the conserved 
+quantum numbers of the given sector (see \secu{sSecQNs}).
+The {\tt sparse\_map} ${\cal P}$ objects are constructed upon call of the {\tt
+  build\_sector} ({\tt sector} constructor) using different algorithms 
 for each value of {\tt ed\_mode}.
-In the {\bf normal} case, the sector object contains two {\tt
-  sparse\_maps} ${\cal S}_{\s=\up,\dw}$, in line with the
-spin dependent factorization of the Fock and sector states: 
+
+In the {\bf normal} mode, the sector object contains two separate {\tt
+  sparse\_maps} objects ${\cal P}_{\s=\up,\dw}$, reflecting the
+factorization of the Fock and sector states into independent spin components: 
 $\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
@@
 The sparse maps are built as follows. 
-For any spin state of the sector $\ket{J_\s}=\ket{{\vec{i}_{\s}\vec{b}_{\s}}}$,
+For any spin state of the sector $\ket{J_\s}=\ket{{\vec{I}_{\s}\vec{B}_{\s}}}$,
 the \emph{key} is determined by the integer $I_\s$ corresponding to the
-impurity bitset $\vec{i}_\s$. The \emph{values} are given by any
+impurity bitset $\vec{I}_\s$. The \emph{values} are given by any
 integer $B_\s$ corresponding to any bath bitset
-$\vec{b_\s}$ associated with $\vec{i}_\s$ by the conservation law of the 
-given sector: $\#\vec{i}_\s + \#\vec{b}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
+$\vec{B_\s}$ associated with $\vec{I}_\s$ by the sector symmetry constraint: $\#\vec{I}_\s + \#\vec{B}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
 Thus, any given \emph{key-value} combination 
@@
 
-In the {\bf superc/nonsu2} case the construction of the unique sparse
-map is similar. For any Fock state $\ket{J}$ corresponding to sector
-state $\ket{j}$ we consider the four integers $I_\up, B_\up, I_\dw,
-B_\dw$ corresponding, respectively, to the bitset
-$\ket{\vec{i}_\up,\vec{b}_\up,\vec{i}_\dw,\vec{b}_\dw}$ decomposition the
-state. These integers fulfill the relation
-$
+In both {\bf superc} and {\bf nonsu2} modes a single sparse map is
+used.
+Here, each Fock state $\ket{J}$ is associated with four integers $I_\up, B_\up, I_\dw,
+B_\dw$ representing the bit decomposition of the state. 
+These integers satisfy the relationship
+$$
 J =I_\up +  B_\up2^{N_\mathrm{imp}} + (I_\dw +  B_\dw2^{N_\mathrm{imp}})2^{N_\mathrm{s}}
-$
-To obtain a contiguous memory pattern we define as a \emph{key} of the sparse
-map the combination $I_\up + I_\dw2^{N_\mathrm{imp}}$ and as corresponding
-\emph{values} the integers $B_\up + B_\dw2^{N_\mathrm{b}}$, fulfilling the
-corresponding conservation laws: 
-$\mathtt{popcnt}(I_\up + I_\dw2^{N_\mathrm{imp}}) + \mathtt{popcnt}(B_\up + B_\dw2^{N_\mathrm{b}}) = N_\up + N_\dw$
+$$
+where $N_\mathrm{imp}$ is the number of impurity bits and 
+$N_\mathrm{s}$ is the total number of spin components.
+To obtain a contiguous memory pattern we define the \emph{key} for the sparse
+map as $I=I_\up + I_\dw2^{N_\mathrm{imp}}$ and the corresponding
+\emph{values} as the integers $B=B_\up + B_\dw2^{N_\mathrm{b}}$.
+Note that these relations can be easily inverted to obtain $I_{\sigma=\up,\dw}$ from
+$I$ and $B_{\sigma=\up,\dw}$ from $B$ in order to reconstruct the Fock
+state $\ket{J}$.
+The four integers satisfy the symmetry constraints:   
+$\mathtt{popcnt}(I_\up + B_\up2^{N_\mathrm{imp}}) + \mathtt{popcnt}(I_\dw + B_\dw2^{N_\mathrm{imp}}) = N$
 for the \textbf{nonsu2} case and
@@
 for the \textbf{superc} case.
-Where needed, the corresponding bitset and Fock state can be reconstructed 
-with simple algebra at no additional cost.
-
+This structure ensures an efficient and compact representation 
+of the many-body Hilbert space, facilitating rapid state lookup 
+during the diagonalization process.
+
+An overview of the implementation is reported in the following listing:
 \setbox0=\hbox{%
-  \begin{minipage}{0.48\linewidth}
+  \begin{minipage}{0.465\linewidth}
     \center{\bf normal}
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.52\linewidth}
+  \begin{minipage}{0.505\linewidth}
     \center{\bf superc/nonsu2}
@@
 enddo
-
 \end{lstlisting}
@@
 \begin{tabular}{c|c}\label{list2}
-  \stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} 
+  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
 \end{tabular}
@@
 \subsubsection{Eigenspace}\label{CodeEigenspace}
-The module \texttt{ED\_EIGENSPACE} implements a list
-storing for the eigenvalues and eigenvectors of the quantum impurity
-Hamiltonian. 
-This class defines the object \texttt{sparse\_espace}, an  
-ordered linked list storing the eigenvalue (the sorting key), the
-eigenvector and the corresponding QNs. To save memory the eigenvectors
-are automatically distributed to all processors in shares of the right
-size according to the nature of the quantum numbers $\vec{Q}$.
-
-For zero temperature calculations only the groundstates (with degeneracies) are stored
-in the list.
-For a finite temperature the excited states need to be stored too.
-In order to avoid unbounded growth of the list we adopt an 
-truncation mechanism. In the first call we collect a number 
-\texttt{lanc\_nstates\_sector} of states from each sector, up to a
-given maximum number \texttt{lanc\_nstates\_total}, both set on input.  
-The list is truncated by keeping the states which
-fulfil the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
+The {\tt ED\_EIGENSPACE} module contains the implementation of the 
+{\tt sparse\_espace} class, which maintains an ordered linked list 
+of selected eigenvalues, eigenvectors, and quantum numbers for the 
+low-lying spectrum of the quantum impurity Hamiltonian. 
+Note that, to reduce the memory footprint each eigenvector 
+is automatically distributed among all processors in suitable shares
+according to the nature of the quantum numbers $\vec{Q}$.
+For zero-temperature calculations, only the groundstate (and its
+degenerate counterparts) are stored. For finite temperatures
+calculations, the list must also include excited states.
+
+To avoid unbounded growth of this list, a  
+truncation mechanism is used. On the first call, a fixed number of
+states per sector  
+\texttt{lanc\_nstates\_sector} is collected, up to a
+maximum total \texttt{lanc\_nstates\_total}, both set via input.  
+The list is then truncated to retain only the states satisfying the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
 $E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
@@
 is an input parameter fixing an a priori energy threshold.
-%  
-Annealing is achieved by successive diagonalization of the problem.
-The numbers of states required to any sector $\SS$ contributing to the list is increased by
-\texttt{lanc\_nstates\_step} or it is reduced otherwise. After few calls
-(of the order of ten) the distribution among the sectors of the
-numbers of states reaches a steady state.
-The corresponding annealed list contains all and just the states
-contributing to the spectrum up to the required energy threshold.
-A histogram of the number of states for each sector is produced after
-each diagonalization to check the evolution of their distribution.
+
+The list dynamically adjusts to optimize the distribution of states 
+across sectors, balancing memory use and computation time. The
+variable \texttt{lanc\_nstates\_step} controls the increase or
+decrease in the number of states per sector. 
+A histogram  of the number of states per sector is produced after each diagonalization 
+to monitor this distribution.
 
 \subsubsection{GFmatrix}
-One of the main goal of the code is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. As we shall see in the following, using Krylov method it is
-possible to express the dynamical correlations in terms of a suitably
-truncated Kallen-Lehmann spectral sum of the form
-$\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
-  - dE_{mn}}$ where $w_{mn}$ is a weight set by the 
-projection of the $m^{\rm th}$ eigenstate onto the $n^{\rm th}$
-component of the Krylov basis (which reduce the sector Hamiltonian
-into a partial tri-diagonal form) while $dE_{mn}=E_m-E_n$ is an excitation energy. 
-The {\tt ED\_GFMATRIX} module contains a class which efficiently store all
-the {\it weights} $w_{mn}$ and {\it poles} $dE_{mn}$ contributing to
-a specific correlation function. Specifically, the {\tt
-  gfmatrix} object implements a dynamical multi-layer data structure
-storing any DCF as the set of all the weights and poles,
-from any contributing eigenstate  and for any
-combination of operators appearing in its definition.
-The use of this class enables the istantantaneous evaluation of a
-given  DCF  $\GG(z)$ for any $z\in\CCC$ the complex frequency plane
-using a suitable compressed form.
+One of the main goal of the \NAME is to evaluate dynamical correlations
+functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,
+these DCFs can be expressed as truncated Kallen-Lehmann spectral sums of the form
+$
+\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
+  - dE_{mn}}
+$
+where $w_{mn}$ is the weight determined by the projection of the
+$m^{\rm th}$ eigenstate onto the $n^{\rm th}$ Krylov basis vector and
+$dE_{mn}=E_m-E_n$ is the corresponding excitation energy.
+
+The {\tt ED\_GFMATRIX} module implements the {\tt gfmatrix} class, 
+which provides an efficient, multi-layer data structure for storing 
+all weights and poles required for the evaluation of DCFs. This 
+class is designed to handle multiple operators and sectors, allowing 
+for rapid, on-the-fly evaluation of the DCF for any complex frequency 
+$z\in\CCC$.
+
+The use of this data structure significantly reduces the computational 
+cost of evaluating DCFs by minimizing redundant calculations and 
+avoiding repeated diagonalizations, making it a critical component 
+for the high-performance execution of \NAME.
 
 \subsection{Bath parametrization}\label{sSecBath}
-The bath parametrization is a key feature in determining the properties
-of the quantum impurity problem.
-Following the structure of Eq.~\ref{Hbath} the bath can be
-parametrized by two terms: the Hamiltonian matrices $h^p$ and the
-amplitudes $V^p$, for $p=1,\dots,N_\mathrm{bath}$.
-Internally, the bath is represented by a dedicated object {\tt
-  effective\_bath} defined in {\tt ED\_VARS\_GLOBAL}. 
-On the
-user side all parameters are packed into a rank-1 array of
-doubles handled using reverse communication strategy.
-This ensures that a local array is always conserved by the user, while
-it prevents direct access to the internal copy.
-
-The bath topology, i.e. the links between the $N_\mathrm{b}$ electronic levels
-assigned to the bath, is determined by the input variable {\tt
-  bath\_type} among 4 different choices: {\bf normal}, {\bf hybrid},
-{\bf replica} and {\bf general} (see Fig.\ref{figBaths}).  
-%
-\paragraph{{\tt bath\_type}={\bf normal}} The bath is formed out of $N_\mathrm{bath}$
-electronic levels coupled to each of the impurity orbital. The total
-count of bath levels is $N_\mathrm{b} = N_\a N_\mathrm{bath}$. The bath Hamiltonan
-matrices include a parametrization diagonal in the orbital and spin space: 
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-If {\tt ed\_mode}={\bf superc} one needs to account for anomalous
-amplitudes connecting bath levels with opposite spins. So we consider
+The quantum impurity problem is characterized by the coupling between
+a local impurity and a surrounding bath. Following the structure of
+Eq.~\ref{Hbath}, the bath is parametrized by two components: the
+Hamiltonian matrices, $h^p$, and the hybridization amplitudes,
+$V^p$, for $p = 1, \dots, N_\mathrm{bath}$.
+Internally, the bath is represented by a dedicated object, {\tt
+  effective\_bath}, defined in the {\tt ED\_VARS\_GLOBAL} module. From
+the user's perspective, all parameters are consolidated into a rank-1
+array of doubles, managed using a reverse communication strategy. This
+approach ensures that a local array remains accessible to the
+user while preventing direct access to the internal copy, thereby
+preserving data integrity and reducing memory overhead.
+
+The bath topology, which defines the connectivity between the
+$N_\mathrm{b}$ electronic levels assigned to the bath, is specified
+through the input variable {\tt bath\_type}. This variable can take
+one of four possible values: {\bf normal}, {\bf hybrid}, {\bf
+  replica}, and {\bf general} (see Fig.~\ref{figBaths}).
+
+\paragraph{{\tt bath\_type}={\bf normal}} In this configuration, the
+bath consists  of $N_\mathrm{bath}$
+electronic levels coupled to each of the impurity orbital, resulting
+in a total  $N_\mathrm{b} = N_\a N_\mathrm{bath}$ of bath levels.
+
+For {\tt ed\_mode}={\bf normal} the bath Hamiltonian is parametrized
+as diagonal matrices in both the orbital and spin spaces:
+$$
+h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'} .
+$$
+where $\varepsilon_{\a\s}$ represents  the on-site energies for each orbital and spin.
+If {\tt ed\_mode}={\bf superc},  anomalous
+amplitudes connecting bath levels with opposite spins must also be
+considered. In this case, the bath Hamiltonian gains 
 an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spins:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
-This choice corresponds to consider, for every orbital component,
-bath matrices with the following structure in the Nambu space:
-$\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x$. 
+off-diagonal in the spin one:
+$$
+h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}} .
+$$
+where $\Delta^p_\a$ represents the pairing amplitudes. 
+This choice corresponds to a Nambu representation for each orbital component,
+with the Hamiltonian matrices taking the form:
+$$
+\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
+\Delta_{\a}\delta_{\a\b}\tau_x .
+$$
+where $\tau_{i=0,x,y,z}$ are Pauli matrices.
+
 The hybridization amplitudes between the impurity and the bath levels
-include, for any value of {\tt ed\_mode} a set of parameters diagonal in both
+are similarly structured. For all values of {\tt ed\_mode} these
+parameters are diagonal in both
 spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
@@
 
-\paragraph{{\tt bath\_type}={\bf hybrid}} The bath is formed out of
-$N_\mathrm{bath}$ coupled to all the impurity levels, correspondingly
-$N_\mathrm{b}\equiv N_\mathrm{bath}$ is the total count of electronic bath levels. 
-The main parametrization of the bath Hamiltonian matrices is still
-diagonal in both orbital and spin space, i.e.
-$h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-As for the previous case, the {\bf superc} mode requires the inclusion
-of a further set of parameters taking care of the anomalous components:
-$h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}$.
-The key difference with respect to the {\bf normal} case lies in the
-off-diagonal nature of the hybridization amplitudes:
-$V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}$. If total magnetization
-is not conserved, i.e. for {\tt ed\_mode}={\bf nonsu2}, an additional
-set of parameters should be included to describe spin-flip processes:
+\paragraph{{\tt bath\_type}={\bf hybrid}}
+The bath is formed by $N_\mathrm{bath}$ levels coupled to all the
+impurity orbitals, resulting in a total of 
+$N_\mathrm{b}\equiv N_\mathrm{bath}$ electronic bath levels. 
+The parametrization of the bath Hamiltonian is 
+diagonal in both orbital and spin space, i.e.,
+$$
+h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'}.
+$$
+
+As for the previous case, the {\bf superc} mode introduces anomalous
+components with the form
+$$
+h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
+  \overline{\s}}.
+$$
+The key difference here is that the hybridization matrix elements are
+generally off-diagonal in the orbital indices:
+$$
+V^p_{\a\b\s\s'}=V^p_{\a\b\s}\delta_{\s\s'}.
+$$
+
+If spin group is not conserved, i.e., for {\tt ed\_mode}={\bf nonsu2}, an additional
+set of parameters must be specified to account for spin-flip processes:
 $V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$.
-These sets of hybridization parameters allow to capture the effects of locally
-hybridized impurity orbitals. This comes at the cost of a
-slightly harder optimization process (see \secu{sSecFit}) specially
-for systems with reduced number of available bath levels with respect
-to the impurity.
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}} A more flexible
-parametrization of the bath is represented by this topology. The
-original idea of this approach is to give to each bath element a structure which {\it replicates}
-that of the impurity while keeping a diagonal coupling between bath
-elements and impurity. This offloads the difficulties related to the
-representation and optimization of strucured quantum impurities to the
-bath Hamiltonan rather than the hybridizations.
-Taking a sligthly more general point of view we consider a user
-defined matrix basis $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
-space and parametrize any bath Hamiltonian as:
+
+This hybrid topology of the bath captures the effects of locally
+hybridized impurity orbitals, but typically requires a more
+challenging optimization process, specially
+with few available bath levels (see \secu{sSecFit}).
+
+\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}}
+This configuration provides a more flexible parametrization of the 
+bath. The core idea is to assign each bath element a structure 
+that {\it replicates} the internal structure of the impurity, while 
+maintaining diagonal coupling between bath elements and the impurity. 
+This offloads the complexity of representing structured quantum 
+impurities to the bath Hamiltonian rather than the hybridizations.
+
+From a broader perspective, this can be formalized by considering  
+a user-defined matrix basis
+$\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
+space, and expressing the bath Hamiltonian as
 $$
@@
 where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired either by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or be determined
-case-by-case by the properties of the problem.
-The total number of electronic levels used to describe the bath is in
-this case: $N_\mathrm{b} = N_{sym} N_\mathrm{bath}$. 
-For the {\bf replica}  topology the coupling between the impurity and
-each bath elements is diagonal in the spin, orbital and internal bath
-structure: $V^p_{\a\b\s\s'} = V^p$. The
-{\bf general} setup introduces a generalization introducing a
+The choice of the matrix basis can be inspired by the internal structure
+of the quantum impurity, i.e. $\hat{h}^0$, or determined
+case-by-case by based on the physical properties of the system.
+In this scheme, the total number of bath levels becomes: $N_\mathrm{b}
+= N_{sym} N_\mathrm{bath}$.
+
+For the {\bf replica} topology, the coupling between the impurity 
+and each bath element remains diagonal in spin, orbital, and internal 
+bath structure: $V^p_{\a\b\s\s'} = V^p$.
+In the {\bf general} case, this is generalized to include explicit 
 dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
@@
 internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their
-scope.
+wrapped by {\tt ED\_BATH}. We divided the set of modules in three
+categories, according to their scope.
+
 \paragraph{Bath Auxiliary Tools}
-This part contains some functions directed to the user as, for
-istance, the implementation of suitable conventional symmetry
-operations acting on the user bath array like, e.g., orbital symmetry,
-particle-hole symmetry, etc. found in {\tt ED\_BATH\_USER}
-However, the key functions of this group concerns the determination
-of the total dimension of the user bath array in {\tt ED\_BATH\_DIM}.
-Starting from the values
-of some input variables the function {\tt ed\_get\_bath\_dimension}
-returns the dimension $B$ to which the  user should allocate the bath
-array to contains all and just the bath parameters. Any following call
-to functions hosting the bath as an input will check that the user supplied
-bath array has the correct dimensions compared to the value of $B$
-using {\tt check\_bath\_dimension}.
+This module group provides user-oriented utilities, including 
+standard symmetry operations on the bath array, such as orbital 
+symmetry and particle-hole symmetry, available in 
+{\tt ED\_BATH\_USER}. The critical functionality here is the 
+determination of the total bath array dimension, implemented in 
+{\tt ED\_BATH\_DIM}. The function {\tt ed\_get\_bath\_dimension} 
+calculates the required dimension $B$ for user-allocated bath 
+arrays, ensuring they contain exactly the necessary number of 
+parameters. Any following call
+to functions hosting the bath as an input verify the array's 
+dimensionality using {\tt check\_bath\_dimension} to prevent 
+allocation errors.
 
 \paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} implements the class {\tt Hreplica}
-for the  the {\bf replica} ({\bf general}) bath parametrization. Beside the
-conventional operations of object construction, destructin, reading
-and saving the module includes the matrix basis $\{ \Gamma^\nu
-\}_{\nu=1,\dots,N_{sym}}$ and variatinal parameters 
-$\vec{\lambda}^p$ setup, i.e. {\tt set\_Hreplica} ({\tt
-  set\_Hgeneral}) as well as a dedicated function to build  the bath Hamiltonian $h^p =
-\vec{\lambda}^p\cdot \Gamma$ in {\tt build\_Hreplica} ({\tt
-  build\_Hgeneral}).
+The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica} 
+for the {\bf replica} and {\bf general} bath parametrizations. In 
+addition to standard object construction, destruction, reading, and 
+saving, this module provides matrix basis setup 
+$\{ \Gamma^\nu \}_{\nu=1,\dots,N_{sym}}$ and variational parameter 
+initialization through {\tt set\_Hreplica} (or {\tt set\_Hgeneral}). 
+The actual bath Hamiltonian is constructed with the function 
+{\tt build\_Hreplica} (or {\tt build\_Hgeneral}) via the relation
+$
+h^p = \vec{\lambda}^p \cdot \Gamma.
+$
 
 \paragraph{Effective Bath}
-The module {\tt ED\_BATH\_DMFT} implements a class for the object {\tt
-  effective\_bath} (already defined in {\tt ED\_VARS\_GLOBAL}). This
-data structure contains and handles all the actual parameters of the
-bath, for any choice of {\tt ed\_mode} and {\tt bath\_type},
-referencing the class {\tt Hreplica} only for the {\bf
-  replica/general} bath topology.
-A global instance of the class {\tt dmft\_bath}  containing the
-current bath parameters is shared throughout the code.   
-The class constructor is supplemented with a specific procedure initializing
-the effective bath {\tt init\_dmft\_bath} which guess the bath
-parameters or read them from a file specified by the input variable {\tt
-  Hfile}.
-The class also contains procedures to transform the instance
-{\tt dmft\_bath} to/from the user bath array: {\tt
-  get/set\_dmft\_bath}.
+The module {\tt ED\_BATH\_DMFT} implements the class 
+{\tt effective\_bath} (defined in {\tt ED\_VARS\_GLOBAL}), which 
+manages all the actual bath parameters for any choice of 
+{\tt ed\_mode} and {\tt bath\_type}. For the 
+{\bf replica/general} topologies, it directly references the 
+{\tt Hreplica} class. A global instance of this class, 
+{\tt dmft\_bath}, is shared throughout the code, providing a 
+centralized structure for bath parameter management.
+
+The constructor for this class includes the function 
+{\tt init\_dmft\_bath}, which either initializes bath parameters 
+from scratch or reads them from a file specified by the input 
+variable {\tt Hfile}. Additionally, the class offers methods to 
+translate bath parameters between the internal {\tt dmft\_bath} 
+representation and the user-defined bath arrays via 
+{\tt get/set\_dmft\_bath}.
 
@@
 span a space of dimension $D^\a_\mathrm{imp}$ or $D^\s_\mathrm{bath}$. 
-Finally, as detailed in \secu{CodeSparseMap}, we store into the {\tt sparse\_map} ${\cal S}$, 
+Finally, as detailed in \secu{CodeSparseMap}, we store into the {\tt sparse\_map} ${\cal P}$, 
 for every impurity configuration 

### 2025-05-09 04_cbinding.tex

--- 2025-04-12 04_cbinding.tex
@@
 {\color{red} Lorenzo?}
+
+\end{document}

### 2025-05-09 04_cbinding.tex
Updates from Overleaf

@@
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-{\color{red} Giorgio, Alexander,?}
+\NAME is supported as alternative impurity solver by the w2dynamics DMFT package\cite{Wallerberger2019CPC}.
+The only prerequisite to use this option is the presence of a functioning EDIpy2 installation, which w2dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
+In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt   EDIPACK}.
+Configuration specific to the exact diagonalization solver can be performed through the parameters in section {\tt EDIPACK} of a w2dynamics parameter file.
+For most of the \NAME input variables, it provides a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set insofar as this is supported by the interface and not an option available through generic w2dynamics parameters.
+This thus includes some parameters that the user will ordinarily want to change from their defaults in a typical calculation such as the number of bath sites {\tt NBATH} and other parameters such as options for the bath fitting and diagonalization algorithms, but also specifically excludes other typically set input variables such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}.
+All of the these variables correspond or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
+Note however in particular that if the \NAME solver is used, {\tt beta} is by default only used as cut-off and does not imply a finite temperature calculation unless the user explicitly sets the parameter {\tt   ED\_FINITE\_TEMP} in section {\tt EDIPACK} to {\tt True}.
+Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in mostly the same way as it would be for the CT-HYB solver.
+This e.g.
+means that results such as the Green's functions are stored into the w2dynamics HDF5 output file in the typical format, and that w2dynamics uses only its own code for e.g.
+calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+As a consequence of this, some functionality that would require specific support from w2dynamics that is not available as of the time of publication can not be used through the interface, e.g.
+calculations with superconductivity or with phonons.
 

### 2025-05-09 03_edipack2.tex

@@
 In presence of symmetries (see \secu{sSecQNs}) the matrix representing
-the Hamiltonian operator $\hat{H}$ takes a block diagonal form. Each block
-contains the Hamiltonian matrix $H_{\SS_{\vec{Q}}}$ for a
-given symmetry sector with quantum number $\vec{Q}$.
-The analysis of the energy spectrum of the quantum impurity problems
-thus reduces to the sequential solution of the sector secular problem
+the Hamiltonian operator $\hat{H}$ can be reduced to a block-diagonal form. Each block corresponds to a symmetry sector
+with a fixed set of quantum numbers $\vec{Q}$ and is represented by
+a Hamiltonian matrix $H_{\SS_{\vec{Q}}}$. 
+Consequently, the analysis of the quantum impurity energy spectrum reduces to solving
+the secular equation within each individual symmetry sector:
 $$
@@
 
-Although the dimension of any such sector $\SS$ are much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$ still the complete solution of
-the related eigenvalue problem represents an unsurmountable problem
-already with $N_\mathrm{s}\simeq 8$. 
-In order to outwit this issue a number of
-algorithms have been developed leveraging on the sparse nature of
-$H_\SS$, e.g. Krylov or similar sub-space methods \cite{Lanczos,Arnoldi,Feast}.   
-In \NAME the alghoritm of choice is P-ARPACK, which represents the
-state-of-the-art Lanczos-based eigensolver with distributed memory
-support~\cite{P-Arpack}. This method includes re-orthogonalization
-within a block Lanczos algorithm which ensures convergence of the
-requred eigenpairs. Using the input variable {\tt lanc\_method} it is
-however possible to select a simple, but not as efficient, parallel
-Lanczos algorithm.
-The core of Krylov-based diagonalization algorithms is the Matrix-Vector Product
-(MVP), i.e. the application of the Hamiltonian to a given input
-vector:
-$$
-H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}
-$$
-
-This operations easily takes over more than 80\% of the computation
-time, so its optimization is a crucial aspect in any diagonalization
-algorithm. In \onlinecite{Amaricci2022} we covered in full detail
-the distrubuted memory massively parallel algorithms we implement 
-to address this specific issue.
-Here, using the same naming convention introduced in \onlinecite{Amaricci2022}, 
-we briefly outline the main strategy for the implementation of the MVP
-according to the value of {\tt ed\_mode}.
-
-\paragraph{{\bf normal}}
-This case relies on the tensor structure of the Fock space and the
-symmetry sectors. In any given sector the electronic part of the
-Hamiltonian matrix reads:
-\begin{equation}
-H_\SS = H_\mathrm{d}  + H_\up\otimes \mathbb{I}_\dw + \mathbb{I}_\up\otimes
-H_\dw + H_\mathrm{nd}\,.
+Even though the dimension of a given sector $\SS$ is much smaller than the
+total Fock space dimension $D_\SS \ll D_\FF$, solving completely the
+corresponding eigenvalue problem remains a formidable challenge
+already for $N_\mathrm{s}\simeq 8$.
+To outwit this, various
+algorithms have been developed exploiting the sparse nature of
+$H_\SS$, including Krylov subspace methods and related approaches
+\cite{Lanczos,Arnoldi,Feast}.
+
+In \NAME, the preferred algorithm is P-ARPACK, a state-of-the-art
+Lanczos-based eigensolver with distributed memory support
+\cite{P-Arpack}. This method incorporates re-orthogonalization within
+a block Lanczos routine, ensuring the accurate convergence of the
+desired eigenpairs. However, it is also possible to select a simpler,
+though less efficient, parallel Lanczos algorithm using the input
+variable {\tt lanc\_method}.
+
+The core computational task in any Krylov-based diagonalization
+algorithm is the Matrix-Vector Product (MVP), i.e., the application
+of the Hamiltonian to a given input vector:
+\begin{equation}
+H_\SS \ket{v} \to \ket{w}\qquad \ket{v},\ket{w}\in \SS_{\vec{Q}}.
+\end{equation}
+This operation easily accounts for more than 80\% of the overall
+computational effort, making its optimization a critical aspect of
+high-performance diagonalization algorithms. In \onlinecite{Amaricci2022},
+the distributed-memory, massively parallel strategies employed in \NAME
+to optimize this step are discussed in full detail. Here, we provide
+a brief outline of the main ideas, following the notation introduced
+in \onlinecite{Amaricci2022}, and focusing on the impact of the choice
+of {\tt ed\_mode}.
+
+\paragraph{\bf normal}
+In this case, the tensor structure of the Fock space and the sector
+symmetries are fully leveraged. Within a given sector, the electronic
+part of the Hamiltonian can be expressed as:
+\begin{equation}
+H_\SS = H_\mathrm{d} + H_\up\otimes \mathbb{I}\dw + \mathbb{I}\up\otimes
+H_\dw + H_\mathrm{nd},
 \label{HssNormal}
 \end{equation}
-where $H_d$ is a diagonal term containing the local part of the
-Hamiltonian, there including the density-density terms of the
-interaction,  $H_\sigma$ describes the hopping processes of the
-electrons with spin $\sigma=\up,\dw$.
-The term $H_{nd}$ contains all the remaining non-diagonal
-elements which do not fit in the previous two components,
-e.g. the spin-exchange and pair-hopping interaction terms.
-Correspondingly, the any sector state $\ket{v}$ can be expressed in a matrix
-basis $\hat{v}$ with rows (columns) running over spin $\up$ ($\down$)
-configurations. Leveraging on this setup it is possible the MVP using the 
-{\tt MPI\_All2AllV} which aims at optimizing locality in the memory
-locality. Additional terms contained in $H_{nd}$ are treated using the
-{\tt MPI\_AllGatherV} algorithm which includes a slight communication
-overload ultimately reducing the parallel efficiency.
-
-\paragraph{{\bf superc/nonsu2}}
-In this two cases the symmetry enforce a specific relation between $\up$ and
-$\dw$ configurations ultimately suppressing the benefits arising from
-Fock space factorization.
-The electronic part of the Hamiltonian matrix is usually organized in this structure:
-$$
-H_\SS = H_\mathrm{imp} + H_\mathrm{int} + H_\mathrm{bath} + H_\mathrm{imp-bath} 
-$$
-where, with almost obvious meaning of the labels, $H_\mathrm{imp}$ encodes
-the non-interacting part of the impurity Hamiltonian determined by
-$h^0_{\a\b\s\s'}$, $H_\mathrm{int}$ the interaction term, $H_\mathrm{bath}$ the
-effective bath terms related to $h^p_{\a\b\s\s'}$ and finally
-$H_\mathrm{imp-bath}$ describes the coupling between impurity and bath
-proportional to $V^p_{\a\b\s\s'}$. 
-In an MPI setup the first three terms contains elements local in the
-memory of each node. These are stored separately from the non-local
-ones in any {\tt sparse\_matrix} representing $H_\SS$. 
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm
-which, as discussed in \onlinecite{Amaricci2022}, requires the
-reconstruction of the distributed input array any node producing a
-overflow in the MPI communication.
-
-The diagonalization procedure is divided in two main steps: a global
-setup and the actual diagonalization.
-%
-The setup step takes care of allocating the required memory,
-setup the MPI environment and allocate the correct 
-Matrix-Vector Product (MVP) procedure according to the symmetries of
-the problem. 
-This part is implemented in a set of independent modules  {\tt
-  ED\_HAMILTONIAN\_?}, where {\tt ed\_mode=?}.
-Specifically, any such module includes two functions.
-The first, {\tt  build\_Hv\_sector\_?}, builds the required sector and
-allocate the MVP function, i.e. point the abstract function {\tt
-  sphtimesv\_p} to the correct procedure determined by the value of
-{\tt ed\_sparse\_H=True/False}.
-If {\tt True} the Hamiltonian terms in $H_\SS$
-get evaluated and stored in a {\tt sparse\_matrix} instance, possibly
-using automatic parallel storage, and then used to perform
-the MVP. This part is implemented in the modules {\tt
+where $H_\mathrm{d}$ represents the diagonal (local) part of the
+Hamiltonian, including density-density interactions, while
+$H_\sigma$ captures hopping processes for electrons with spin
+$\sigma=\up,\dw$. The term $H_\mathrm{nd}$ encompasses all remaining
+non-diagonal contributions, such as spin-exchange and pair-hopping
+terms.
+
+In this formulation, a sector state $\ket{v}$ can be
+represented in a matrix basis $\hat{v}$ with rows (columns)
+corresponding to $\up$ ($\dw$) configurations. This structure allows
+for efficient MVP operations using {\tt MPI\_All2AllV}, which aims to
+optimize memory locality. However, terms in $H_\mathrm{nd}$ that
+break this structure require {\tt MPI\_AllGatherV}, introducing a
+slight communication overhead and reducing parallel efficiency.
+
+\paragraph{\bf superc/nonsu2}
+For these modes, symmetries enforce specific constraints between
+$\up$ and $\dw$ configurations, preventing the direct use of the
+factorized Fock space representation. The electronic
+part of the Hamiltonian is typically structured as:
+\begin{equation}
+H_\SS = H_\mathrm{imp} + H_\mathrm{int} + H_\mathrm{bath} + H_\mathrm{imp-bath},
+\end{equation}
+where $H_\mathrm{imp}$ encodes the local impurity Hamiltonian
+determined by $h^0_{\a\b\s\s'}$,
+$H_\mathrm{int}$ contains the interaction terms, $H_\mathrm{bath}$
+describes the effective bath contributions corresponding to
+$h^p_{\a\b\s\s'}$, and $H_\mathrm{imp-bath}$ accounts for the
+impurity-bath couplings $V^p_{\a\b\s\s'}$.
+In an MPI setup, the first three terms contains also elements local to each node and
+stored separately within each {\tt sparse\_matrix} instance representing $H_\SS$.
+The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm which, as noted in
+\onlinecite{Amaricci2022}, requires reconstruction of distributed
+arrays and incurs significant communication overhead.
+
+The diagonalization process itself is divided into two primary phases:
+
+\paragraph{\bf Global Setup}. This phase allocates the required memory, initializes
+the MPI environment, and configures the appropriate MVP procedure
+based on the symmetries of the problem. This logic is implemented in
+a set of independent modules, {\tt ED\_HAMILTONIAN\_?}, where
+{\tt ed\_mode=?}. Any module includes two functions: {\tt build\_Hv\_sector\_?} and  {\tt vecDim\_Hv\_sector\_?}.
+
+The {\tt build\_Hv\_sector\_?} function builds the symmetry sector and
+allocates the MVP function but setting the shared abstract function pointer {\tt
+  sphtimesv\_p}. This latter step is controlled by the value of
+{\tt ed\_sparse\_H=True/False}. If {\tt True} the Hamiltonian $H_\SS$
+gets stored in a {\tt sparse\_matrix} instance and used to perform
+the MVPs. The corresponding algorithms are implemented in the modules {\tt
   ED\_HAMILTONIAN\_?\_STORED\_HxV}
 If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
-i.e. each element of $H_\SS$ is direcrtly applied to the given input
-vector $\ket{v}$ to determine the outgoing vector $H_\SS\ket{v}$,
-either in serial or parallel mode as implemented in {\tt
+i.e. each element of $H_\SS$ is directly applied to the input
+vector $\ket{v}$, either in serial or parallel mode as implemented in {\tt
   ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
@@
 The function {\tt vecDim\_Hv\_sector\_?} returns the 
-dimension of the vector to be used in the
-MVP. In serial execution this number is just $D_\SS$ the dimension of
-the sector, whereas in a parallel mode the returned value is the
+dimension of the vector used in the
+MVP. In a MPI-parallel execution the returned value is the
 dimension $d_i$ of the vector chunk per each node such that
 $\sum_{i=1}^{N_\mathrm{nodes}}d_i = D_\SS$. Yet, the specific value of $d_i$
-depends on the MPI algorithm used for the MVP function, which in turn
-is determined by the symmetry of the problem, i.e. {\tt ed\_mode}.
-
-The sector-by-sector diagonalization for each
-value of {\tt ed\_mode} is implemented in the modules {\tt
-  ED\_DIAG\_?} through the main functions {\tt
-  diagonalize\_impurity\_?}. The diagonalization proceeds in three main
-steps: i) setup the diagonalization by selecting all or a sub-set of the
-sectors to analyze; ii) sequential diagonalization cycle over all the suitable symmetry
-sectors; iii) analysis of the resulting {\tt state\_list} containins
-all the eigensolutions to be conserved.
+depends on the MPI algorithm used for the MVP function.
+
+\paragraph{\bf Diagonalization}
+This step is managed by the {\tt ED\_DIAG\_?}
+modules, which contain the main functions {\tt diagonalize\_impurity\_?}.
+This phase includes: (i) selecting sectors for diagonalization, (ii)
+performing diagonalization within each sector, and (iii) analyzing
+the resulting {\tt state\_list} of conserved eigenstates.
 
@@
 The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of dynamical correlation functions using Krylov
+enables the evaluation of Dynamical Correlation Functions (DCF) using Krylov
 sub-space algorithm.
-This is a key part of the library when using \NAME as an impurity
-solver within DMFT framework.
-
-Before entering into the implementation details we briefly outline the
-generic algorithm. Let us consider the dynamical correlation function:
+This capability is central to the library when using \NAME as an
+impurity solver within the DMFT framework.
+
+Before delving into the implementation specifics, we outline the
+generic approach. Consider the generic DCF:
 \begin{equation}
@@
 \end{equation}
-where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering operator for fermions or
-bosons and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$,  $Z=\sum_ne^{-\beta E_n}$, is the thermodynamic
-average. Using spectral decomposition, the expression \equ{eqGaa} is reduced into Kallen-Lehman form:
+where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering
+operator for fermions ($-$) or
+bosons ($-$), and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
+      H}\AA \right]}$, with $Z=\sum_ne^{-\beta E_n}$, the thermodynamic
+average.
+Using spectral decomposition, the expression \equ{eqGaa} reduces to a
+K\"all\`en-Lehmann form:
 \begin{equation}\label{KLgf}
@@
 \end{equation}
-where $z\in\CCC$, 
-$\ket{\psi_n}$, $E_n$ are the eigenpairs of the
-Hamiltonian $H$ and $E_0$ is the groundstate energy.
-While appealing, the previous expression requires the knowledge of the
-entire Hamiltonian spectrum. A key simplification is obtained looking
-at the first line in \equ{KLgf},
-showing that the $C_\AA$ essentially corresponds to a given element of the inverse operator $(z-H)^{-1}$, i.e. the
-resolvant. The Krylov sub-space method provides a controlled
-approximation for this element, leveraging over the
-reduction of the (sector) Hamiltonian to a partial tri-diagonal
-form and returning an arbitrary number of amplitudes to (unknown)
-excited states. To illustrate the algorithm let's consider the normalized initial state: 
+where $z\in\CCC$,  $\ket{\psi_n}$, $E_n$ are the eigensolutions of the
+Hamiltonian $H$. 
+This form is appealing but computationally prohibitive, as it requires
+the full Hamiltonian spectrum. However, the first line in \equ{KLgf}
+highlights that the $C_\AA$ essentially corresponds to a specific
+matrix element of the resolvant operator $(z-H)^{-1}$, which can be
+efficiently approximated using the Krylov sub-space method.
+
+To illustrate this approach, consider the normalized initial state: 
 $$
@@
   \AA^+\ket{\psi_n}}$.
-We can construct the Krylov basis $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
+The Krylov basis is then constructed as $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
 H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$ by iteratively applying the (sector)
-Hamiltonian through MVP functions. 
-Any given eigenstate $\ket{\psi_n}$ has components along the Krylov basis $\mathcal{K}_{N} (\ket{\phi_n})$ which read: $\ket{\psi_n} =
-\sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$.   We can evaluate the operator components
-$=\bra{\psi_m}\AA^+ \ket{\psi_n}\equiv \langle\psi_m| \phi_n\rangle =
-\NN_n {a^{n*}_m}$. Inserting this expression into \equ{KLgf} we
-obtain the following approximation to $C_\AA$:
+\}$$ with $1 \ll N \ll \DD_\SS$, obtainaed by repeated applications of
+the (sector) Hamiltonian via MVP functions.
+
+Given that any eigenstate $\ket{\psi_n}$ can be expressed within the
+Krylov basis as
+$\ket{\psi_n} = \sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
+\sum_i a^n_i \ket{v^n_i}$. we can approximate the expression
+\equ{KLgf} as:  
 \begin{equation}
@@
 \end{equation}
-where we introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
+where the terms are grouped as a sum over spectral weights and
+poles. We introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
 for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
@@
 Krylov sub-space algorithm and for channel $\nu$.
-
-A stringent limitation of this procedure is to get applied to diagonal
-dynamical correlation functions of the form \equ{eqGaa}. However, as
-we will show in the following, many practical application requires to
-evaluate off-diagonal functions of the form:
+This approach significantly reduces the computational burden, as it
+relies on a much smaller set of basis states.
+
+However, this method is typically limited to diagonal DCF like
+\equ{eqGaa}. In practice, many applications requires also to build off-diagonal
+functions of the form:
 $C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-A direct extensin of the method is obtained considering suitable
-auxiliary operators prepared with independent linear combination of
-$\AA$ and $\BB$.
-A notable example is to consider the two auxiiary operators $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$. Using simple algebra it is then straightforward to
-obtain the desired function $C_{\AA \BB}$ from the evaluation of
-$C_\OO$ and $C_\PP$:
+This can addressed by introducing auxiliary operators, such as $\OO=\AA +\BB$ and
+$\PP=\AA-i\BB$, enabling the extraction of the desired function via
+simple algebraic combinations:
 $$
@@
 
-In \NAME the impurity Green's functions $G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t)
-c_{\b\s'}^+ ]\iket$,
-is contained in \texttt{ED\_GREENS\_NORMAL}. This wraps more
-specific methods according to the symmetry of the problem expressed by
-{\tt ed\_mode}. In the {\bf normal} mode also spin,
-charge, pair and excitonic susceptibilities functions. 
-Computationally, the construction of the Krylov basis
-$\mathcal{K}_N(\OO\ket{\psi_n})$ for any eigenstate of the low energy
-spectrum is the most time consuming step. As for the diagonalization
-part, here a crucial speed-up is obtained by the parallel execution of
-the MVP lying at the earth of the Hamiltonian tri-diaagonalization
-process. The input variable {\tt lanc\_gfniter} controls the largest order of
-the Krylov basis, i.e. the maximum number of excitations in
+In \NAME, the computation of impurity Green's functions, such as
+$G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket$,
+is handled by the \texttt{ED\_GREENS\_FUNCTIONS} module.
+This
+module integrates more specialized methods based on the symmetry
+classification defined by the \texttt{ed\_mode} parameter.
+Moreove, in the {\bf normal} mod, it also includes spin, charge, pair, and excitonic
+susceptibility functions, providing a comprehensive framework for
+dynamical response calculations.
+From a computational perspective, the construction of the Krylov basis
+$\mathcal{K}_N(\OO\ket{\psi_n})$ for each eigenstate within the low-energy
+spectrum is typically the most resource-intensive step.
+As with the
+diagonalization process, a significant performance gain is achieved through
+the parallel execution of the Matrix-Vector Product (MVP) at the core of
+the Hamiltonian tri-diagonalization algorithm.
+The input variable
+\texttt{lanc\_gfniter} regulates the maximum order of the Krylov basis,
+determining the upper limit on the number of excitations considered in
 \equ{eqGKrylov}.
-Operationally, each symmetry mode {\tt ed\_mode=?} requires a different construction of
-the Green's functions implemented in {\tt ED\_GF\_?}
+Operationally, each symmetry mode (\texttt{ed\_mode=?}) requires a distinct
+strategy for Green's function construction, implemented in the corresponding
+\texttt{ED\_GF\_?} modules.
 
 \paragraph{{\bf normal}}
-In this case the all the orbital dependent and spin-diagonal Green's
-functions $G_{\a\b\s\s}$ needs to be evaluated. The orbital diagonal case
-$\a=\b$ proceeds as discussed above considering $\AA=c_{\a\s}$. This
-step makes use of the {\tt apply\_op\_C/CDG} functions in {\tt
-  ED\_AUX\_FUNX} on any eigenstate $\ket{\psi_n}$ in the {\tt
-  state\_list}, i.e. a global instance of {\tt sparse\_espace}
-containing the low energy spectrum of the problem.
-The sector Hamiltonian matrix in this mode is assumed to be real
-symmetric. This brings a simplification in the evaluation of the
-off-diagonal components $G_{\a\b\s\s}=G_{\b\a\s\s}$.
-These components are thus evaluated considering the auxiliary operator
-$\OO=(c_{\a\s} + c_{\b\s})$ and using the relation
+In this mode, all orbital-dependent and spin-diagonal Green's 
+functions, $G_{\a\b\s\s}$, must be evaluated. The diagonal 
+case, where $\a=\b$, is straightforward and involves applying 
+the operator $\AA=c_{\a\s}$ to any eigenstate $\ket{\psi_n}$ 
+from the global {\tt state\_list} of the low-energy spectrum, 
+which is represented by the {\tt sparse\_espace} object. This 
+operation relies on the functions {\tt apply\_op\_C/CDG} in 
+{\tt ED\_AUX\_FUNX}.
+
+The sector Hamiltonian matrix in this mode is typically assumed 
+to be real symmetric, which significantly simplifies the evaluation 
+of the off-diagonal terms. In this case, the relation 
+$G_{\a\b\s\s}=G_{\b\a\s\s}$ holds, allowing the computation of 
+off-diagonal components using an auxiliary operator 
+$\OO = c_{\a\s} + c_{\b\s}$ and the identity:
 $G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
@@
 The diagonal spin, charge and pair susceptibility terms
-$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$ are
-evaluated employing, respectively, the operators $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^z_{\s\s'}c_{\a\s'}\equiv
-S^z_\a$, $\AA=\sum_{\s\s'}c^+_{\a\s}\tau^0_{\s\s'}c_{\a\s'}\equiv
-N_\a$) and $\AA=c_{\a\dw}c_{\a\up}\equiv
-\Delta_\a$, where
-$\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Similarly, yhe off-diagonal terms are obtained by considering the operator $\AA=S^z_\a
-+ S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-The excitonic susceptibility $\chi^T_{\a\b}$ is defined with respect
-to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, respectively, the spin-singlet
-($i=0$) and the spin-triplet excitons ($i=x,y,z$) operators.
+$\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$
+are constructed using the operators $\AA = \sum_{\s\s'} c^+_{\a\s}
+\tau^z_{\s\s'} c_{\a\s'} \equiv S^z_\a, $, 
+$\AA = \sum_{\s\s'} c^+_{\a\s} \tau^0_{\s\s'} c_{\a\s'} \equiv N_\a, $
+and $\AA = c_{\a\dw}c_{\a\up} \equiv \Delta_\a$,
+where $\tau^{a=0,x,y,z}$ are the Pauli matrices.
+Off-diagonal terms are similarly evaluated using the operators
+$\AA=S^z_\a + S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
+Excitonic susceptibilities, $\chi^T_{\a\b}$, are defined with 
+respect to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
+c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
+spin-singlet exciton, and $i=x,y,z$  correspond to the spin-triplet excitons.
 
 \paragraph{{\bf superc}}
-In the supercondutive case the Nambu orbital
-dependent $s$-wave Green's function reads:
+In the supercondutive case, the Nambu orbital-dependent $s$-wave
+Green's function reads:
 \begin{equation}
@@
 \end{equation}
-However, leveraging on the symmetries holding between the different
-components we can reduce to evaluate only the top row components plus
-auxiliary functions.
-The calculation of the diagonal normal component $G_{\a\a\up\up}$ follows the
-very same scheme of the {\bf normal} case. For the off-diagonal terms
-however we do not rely on any symmetry relation but we consider 
-two auxiliary functions $C_\OO$, $C_\PP$ with $\OO=c_{\a\up} +
-c_{\b\up}$, $\PP=c_{\a\up} -ic_{\b\up}$ so that:
+Exploiting symmetries between matrix components, it is 
+sufficient to compute only the top row elements along with 
+a few auxiliary functions.
+
+The diagonal normal component $G_{\a\a\up\up}$ can be 
+evaluated using the same approach as in the {\bf normal} 
+case. However, for the off-diagonal terms $G_{\a\b\up\up}$, 
+we forgo symmetry arguments and instead define two 
+auxiliary operators, $\OO = c_{\a\up} + c_{\b\up}$ and 
+$\PP = c_{\a\up} - i c_{\b\up}$. This allows us to express 
+the Green's function as::
 $G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
 (1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
-The diagonal and off-diagonal anomalous terms $F_{\a\b\up\dw}$ need to
-be evaluated using different combinations of creation/destruction
-operators. First we evaluate the $\bar{G}_{\a\a\dw\dw}$ component as
-an auxiliary term considering $\AA=c^+_{\a\dw}$. 
-Next, we consider the two linear combinations:
-$\TT = c_{\a\up} + c^+_{\b\dw}$, $\RR=c_{\a\up} -i c^+_{\b\dw}$
-contributing, respectively, to the auxiliary functions $C_\TT$,
-$C_\RR$. The searched anomalous functions reads:
-$F_{\a\b\up\dw} = \tfrac{1}{2}[ C_\TT + C_\RR - (1-i)(G_{\a\a\up\up} +
-\bar{G}_{\b\b\dw\dw})]$.
+
+Evaluating the diagonal and off-diagonal anomalous terms 
+$F_{\a\b\up\dw}$ requires distinct combinations of 
+creation and annihilation operators. First, the component 
+$\bar{G}_{\a\a\dw\dw}$ is evaluated as an auxiliary term 
+using $\AA = c^+_{\a\dw}$. Then, we construct two further 
+linear combinations:
+\begin{align*}
+\TT &= c_{\a\up} + c^+_{\b\dw}, \\
+\RR &= c_{\a\up} - i c^+_{\b\dw},
+\end{align*}
+which contribute to the auxiliary functions $C_\TT$ and 
+$C_\RR$, respectively. The final expression for the 
+anomalous function reads:
+\begin{equation}
+F_{\a\b\up\dw} = \tfrac{1}{2} \left[ C_\TT + C_\RR - 
+(1-i)(G_{\a\a\up\up} + \bar{G}_{\b\b\dw\dw}) \right].
+\end{equation}
 
 \paragraph{{\bf nonsu2}}
-In this case all the Green's functions components need
-to be evaluated. For the orbital and spin diagonal terms
-$G_{\a\a\s\s}$  we proceeds as in the {\bf normal} case.
-The remaining  off-diagonal components $G_{\a\b\s\s'}$ are
-evaluated using auxiliary operators $\OO=c_{\a\s}+c_{\b\s'}$,
-$\PP=c_{\a\s}-ic_{\b\s'}$ and the relation:
-$G_{\a\b\s\s'}=\tfrac{1}{2}[C_\OO+C_\PP -
-(1-i)(G_{\a\a\s\s}+G_{\b\b\s'\s'})]$.
+In the {\bf nonsu2} case, all Green's function components 
+must be explicitly evaluated, as the spin and orbital 
+symmetries are not conserved. For the diagonal terms 
+$G_{\a\a\s\s}$, the procedure follows the same approach 
+outlined in the {\bf normal} case.
+
+The off-diagonal components $G_{\a\b\s\s'}$, however, 
+require a more general treatment. These are computed using 
+auxiliary operators defined as:
+\begin{align*}
+\OO &= c_{\a\s} + c_{\b\s'}, \\
+\PP &= c_{\a\s} - i c_{\b\s'},
+\end{align*}
+which allows the Green's function to be expressed as:
+\begin{equation}
+G_{\a\b\s\s'} = \tfrac{1}{2} \left[ C_\OO + C_\PP - 
+(1-i)(G_{\a\a\s\s} + G_{\b\b\s'\s'}) \right].
+\end{equation}
+This approach effectively reduces the complexity of 
+evaluating the off-diagonal terms by leveraging auxiliary 
+functions, despite the absence of full spin symmetry.
 
 \subsection{Observables}\label{sSecObc}
-A number of predefined impurity observable or local static
-correlations, e.g. occupation, total energy, pair amplitude, excitonic
-order parameter ,etc.   are calculated in the module
-\texttt{OBSERVABLES}. As for the previous cases, this module wraps the
-different implementations and quantities to evaluate from the
-operational modes {\tt ed\_mode=?} implemented in {\tt
-  ED\_OBSERVABLES\_?}. 
-Local observables and correlations are defined by the thermal average  $\ibra \OO\iket =
-\Tr{\left[e^{-\beta H}\OO\right]}/Z$. This can be efficiently evaluated at zero and
-low temperature using the stored low energy part of the spectrum
-leveraging on the exponential cutoff from the Boltzmann factor:
-\begin{equation}
-    \ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta
-  E_n}\bra{\psi_n}\OO\ket{\psi_n},
+A wide range of predefined impurity observables and local 
+static correlations, such as occupation numbers, total 
+energy, pair amplitudes, and excitonic order parameters, 
+are computed in the \texttt{OBSERVABLES} module. Similar to 
+previous cases, this module wraps different implementations 
+depending on the operational mode specified by 
+{\tt ed\_mode=?} and is distributed across the corresponding 
+files {\tt ED\_OBSERVABLES\_?}.
+
+Local observables and correlations are generally defined 
+through the thermal average 
+$\ibra \OO\iket = \frac{\Tr\left[e^{-\beta H}\OO\right]}{Z}$, 
+where $Z = \sum_n e^{-\beta E_n}$ is the partition function. 
+At zero or low temperatures, this can be efficiently 
+evaluated using the stored low-energy part of the spectrum, 
+taking advantage of the exponential suppression provided by 
+the Boltzmann factor:
+\begin{equation}
+\ibra \OO\iket = \frac{1}{Z}\sum_n e^{-\beta E_n}
+\bra{\psi_n} \OO \ket{\psi_n},
+\label{eq:thermal_average}
+\end{equation}
+where $E_n$ and $\ket{\psi_n}$ are the low-lying eigenstates 
+of the system stored in the {\tt state\_list}. This approach 
+greatly reduces computational overhead by focusing on the 
+relevant, low-energy sector.
+\begin{equation}
+  \ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta  E_n}
+  \bra{\psi_n}\OO\ket{\psi_n},
   \label{eq:thermal_average}
@@
 \subsection{Reduced impurity density matrix}\label{sSecRDM}
-The new \NAME version of the library features the calculation of the
-impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), extending 
-the algorithm introduced in \onlinecite{BellomiaPhD} so to enable the
-analysis of entanglement properties of the quantum impurity for any value
-of {\tt ed\_mode}.
-To simplify the discussion in this section we take the zero
-temperature limit and consider the presence of a non-degenerate
-groundstate $\ket{\psi}$ populating the {\tt state\_list}.
-The generalization to the presence of degenerate states or the finite
-temperature regime are straightforward, as it amounts to defining an
-average over degenerate/thermal states $\ibra\rho^\mathrm{imp}\iket$, 
-akin to \equ{eq:thermal_average}.
-The given pure state belongs to a unique symmetry sector $\SS$ and it
-is represented in the Fock basis as $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The corresponding pure density matrix $\rho$ is thus explicitly decomposed as:
-$$
-\rho = \ket{\psi}\bra{\psi} = \sum_{IJ=1}^{4^{N_\mathrm{s}}} a^*_J a_I \ket{I}\bra{J} =\sum_{IJ=1}^{4^{N_\mathrm{s}}} \rho_{IJ} \ket{I}\bra{J}.
-$$
-The iRDM is obtained from $\rho$ by tracing out the bath degrees of
-freedom: $\rho^\mathrm{imp}=\Tr_\mathrm{bath}\rho$. The summations appearing in the
-previous expressions become quickly unmanageable with the system
-size, as their extrema scale exponentially with $N_\mathrm{s}$. 
-To overcome this issue we implemented a fast algorithm
-leveraging on the decomposition of the Fock space into symmetry sectors
-and the subsequent map sparsity.
-Using quantum number conservation the summation extrema get reduced to
-the size $D_\SS$ of the sector $\SS$ to which the groundstate (or in
-general any eigenstate) belongs. 
-Next we analyze the groundstate expansion on the Fock states, splitting the bit representation of any state $\ket{I}$ into
-their spin-dependent impurity and bath parts as $\ket{I} = \ket{
-  i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow \, b_\downarrow}$. Each bitset 
-span a space of dimension $D^\a_\mathrm{imp}$ or $D^\s_\mathrm{bath}$. 
-Finally, as detailed in \secu{CodeSparseMap}, we store into the {\tt sparse\_map} ${\cal P}$, 
-for every impurity configuration 
-$i_\s =1,\dots,D^\s_{imp}$ (\emph{key}), the bath states 
-$b_\s\in[1,\dots,D^\s_\mathrm{bath}]$ (\emph{values}) that satisfy the conservation law defined
-by the \texttt{ed\_mode} variable.
-We indicate with ${\cal D}_{i\s}$ the number of keys $i_\s$ and with 
-${\cal D}_{b\s}$ the number of values $b_\s$.
-The fast summation algorithm for the evaluation of the iRDM takes on a
-different form for the two cases {\bf normal} and {\bf superc/nonsu2},
-as outlined below.
+The latest version of \NAME introduces the calculation of the 
+impurity Reduced Density Matrix (iRDM, $\rho^\mathrm{imp}$), 
+extending the algorithm initially proposed in 
+Ref.~\onlinecite{BellomiaPhD} to support the analysis of entanglement 
+properties of quantum impurities for any value of  {\tt ed\_mode}.
+
+For simplicity, this section focuses on the zero-temperature limit, 
+assuming a non-degenerate ground state $\ket{\psi}$ present in the 
+{\tt state\_list}. The generalization to the finite-temperature regime 
+or degenerate ground states is straightforward, requiring only the 
+replacement of the pure state average with the thermal or degenerate 
+ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
+\equ{eq:thermal_average}.
+
+A pure quantum state $\ket{\psi}$ belonging to a unique symmetry 
+sector $\SS_{\vec{Q}}$ can be represented in the Fock basis as:
+$
+\ket{\psi} = \sum_I a_I \ket{I},
+$
+where the pure density matrix $\rho$ is then given by:
+\begin{equation}
+\rho = \ket{\psi}\bra{\psi} = \sum_{IJ=1}^{4^{N_\mathrm{s}}} 
+a^*_J a_I \ket{I}\bra{J} = \sum_{IJ=1}^{4^{N_\mathrm{s}}} 
+\rho_{IJ} \ket{I}\bra{J}.
+\end{equation}
+
+The iRDM is obtained by tracing out the bath degrees of freedom:
+\begin{equation}
+\rho^\mathrm{imp} = \Tr_\mathrm{bath}(\rho).
+\end{equation}
+However, the summations involved in this trace quickly become 
+computationally prohibitive, as their range scales exponentially 
+with the system size, i.e., $4^{N_\mathrm{s}}$.
+
+To address this, we implemented a fast algorithm that exploits the 
+block structure of the Fock space defined by the symmetry sectors and
+the subsequent map sparsity. 
+This approach significantly reduces the computational cost by limiting 
+the summation to the sector size $D_\SS$ of the symmetry sector 
+$\SS$ to which the ground state (or any eigenstate) belongs.
+
+Next, we decompose the Fock basis into spin-dependent impurity and 
+bath parts. Any Fock state $\ket{I}$ can be split as:
+$
+\ket{I} = \ket{i_\uparrow \, b_\uparrow} \otimes 
+\ket{i_\downarrow \, b_\downarrow},
+$
+where the impurity $i_\sigma$ and bath $b_\sigma$ states span subspaces of dimension 
+$D^\s_\mathrm{imp}$ and $D^\s_\mathrm{bath}$, respectively, for each 
+spin $\s = \uparrow, \downarrow$.
+
+To efficiently manage this decomposition, we introduce a 
+{\tt sparse\_map} ${\cal P}$, as detailed in \secu{CodeSparseMap}. 
+This structure stores, for each impurity configuration 
+$i_\s = 1, \dots, D^\s_\mathrm{imp}$ (the \emph{key}), the 
+corresponding bath configurations 
+$b_\s \in [1, \dots, D^\s_\mathrm{bath}]$ (the \emph{values}) that 
+satisfy the symmetry constraints over the sector quantum numbers
+imposed by the {\tt ed\_mode} variable.
+We denote the number of keys as ${\cal D}_{i\s}$ and the 
+number of values as ${\cal D}_{b\s}$.
+The fast summation algorithm for evaluating the iRDM differs 
+significantly between the {\bf normal} and {\bf superc/nonsu2} modes, 
+as outlined in the sections below.
 
 \paragraph{{\bf normal}}
-In this case we take advantage of the Fock space and sector spin-resolved
-factorization, discussed in depth in \secu{sSecQNs}. We can indeed split the
-global bitset in spin-resolved impurity and bath states, as
-$$
+In this case, we take advantage of the Fock space factorization and 
+sector spin-resolved decomposition, as discussed in detail in 
+\secu{sSecQNs}. 
+The global bitset can be split into spin-resolved 
+impurity and bath components as:
+\begin{equation}
 \ket{\vec{n}} =
@@
 \ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}.
-$$
-We note that creation (destruction) operators at
-position $p$ for spin $\sigma$  $c^+_{p\sigma}$ ($c^+_{p\sigma}$) do
-not operate on the opposite spin $\bar{\sigma}$ so that they pass through 
-the $\ket{n_{\bar{\sigma}}}$ bitset without taking any fermionic sign. 
-Finally, we observe that local iRDM admits
-only {spin-diagonal} blocks in the {\bf normal} case. This can be understood
-by observing that the conserved quantum numbers in the whole impurity model 
-are \emph{additive} $N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$ and so the
-corresponding generator of the symmetry group is factorized as 
+\end{equation}
+Here, creation (destruction) operators  $c^+_{p\sigma}$
+($c^+_{p\sigma}$) at position $p$ and for a given spin $\sigma$
+act only on the corresponding 
+spin subspace, i.e., they commute with the opposite spin 
+subspace $\ket{\vec{n}_{\bar{\s}}}$ without introducing any 
+fermionic sign.
+
+In the {\bf normal} mode, the iRDM is restricted to 
+{spin-diagonal} blocks. This follows from the observation 
+that the conserved quantum numbers are 
+\emph{additive} quantities, given by:
+$N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$
+where the corresponding generator of the symmetry group factorizes as
 $U_{N_\s} = U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}}$. 
-Hence, as the iRDM acts by definition only on the impurity
-Fock space, we have 
-$$
-U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} = 
+Since the iRDM acts only on the impurity Fock space, this implies:
+% $$
+% U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} = 
+% U_{N_\s^\mathrm{bath}}^\dagger \otimes U_{N_\s^\mathrm{imp}}^\dagger
+% \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}} =
+% U_{N_\s^\mathrm{imp}}^\dagger
+% \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} =
+% \rho^\mathrm{imp},
+% $$
+\begin{equation}
+\begin{aligned}
+U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} &= 
 U_{N_\s^\mathrm{bath}}^\dagger \otimes U_{N_\s^\mathrm{imp}}^\dagger 
-\rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}} =
-U_{N_\s^\mathrm{imp}}^\dagger
-\rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} =
+\rho^\mathrm{imp} 
+U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}} \\
+&= 
+U_{N_\s^\mathrm{imp}}^\dagger \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}}\\
+& = 
 \rho^\mathrm{imp},
-$$
-i.e. $U_{N_\s^\mathrm{imp}}$ defines a symmetry of $\rho^\mathrm{imp}$, making it
-block diagonal with respect to the impurity quantum numbers $N_\s^\mathrm{imp}$.
-Thus we obtain for the iRDM:
+\end{aligned}
+\end{equation}
+demonstrating that $U_{N_\s^\mathrm{imp}}$ defines a symmetry of 
+$\rho^\mathrm{imp}$, which is therefore block diagonal with respect to 
+the impurity quantum numbers $N_\s^\mathrm{imp}$.
+
+The resulting iRDM takes the form:
 \begin{equation}
@@
 \end{equation}
-where we recall that $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the expansion coefficients of the state $\ket{\psi}$ on the Fock basis 
-$\ket{I} = \ket{i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow \, b_\downarrow}$
-and the constants $C_{i,b}$, accounting for the fermionic sign associated to
-exchanging bath and impurity bitsets, are identically 1 as effect of the 
-Kronecker deltas for bath and impurity indices.  
+where the coefficients $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the
+expansion coefficients of the state on the Fock basis
+$\ket{\psi} = \sum_I a_I \ket{i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow
+  \, b_\downarrow}$.
+Notably, the factors $C_{i,b}$, which account for the potential 
+fermionic sign from reordering bath and impurity components, are 
+trivially 1 due to the absence of cross-spin interference in this 
+mode, as enforced by the Kronecker deltas for bath and impurity 
+indices.
+
 The numerical implementation relies on the use of the {\tt
-  sparse\_map} ($\%sp$) for the groundstate sector as reported in the
-listing below:  
+  sparse\_map} ($\%sp$) for the groundstate sector as reported in the listing below:  
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 \paragraph{{\bf superc/nonsu2}}
-To treat these lowered-symmetry cases, some modifications related to the
-absence of Fock space factorization have to be taken into account. In particular, 
-the correct evaluation of the off-diagonal terms connecting the 
-$[N^\mathrm{imp}_\up,\,N^\mathrm{imp}_\dw]$ blocks, relies on 
-computing explicitly the fermionic permutation signs.
-
-Let us consider a generic Fock basis in the form
-$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, defining the target
-ground state again as $\ket{\psi} = \sum_I a_I \ket{I}$.
-From the definitions of pure density matrix $\rho = \ket{\psi}\bra{\psi}$ 
-and of iRDM we have:
+For these lower-symmetry cases, the absence of a clean Fock space 
+factorization introduces additional complexities. Specifically, the 
+correct evaluation of the off-diagonal iRDM terms, which connect 
+different $[N^\mathrm{imp}_\up,\,N^\mathrm{imp}_\dw]$ blocks, 
+requires an explicit computation of fermionic permutation signs.
+
+Consider a generic Fock basis state in the form 
+$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, , and define the 
+ground state as $\ket{\psi} = \sum_I a_I \ket{I}$. 
+The pure density 
+matrix is then given by
+$\rho = \ket{\psi}\bra{\psi} = \sum_{IJ} a_I a^*_J \ket{I}\bra{J}$ 
+while the iRDM is obtained by tracing over the bath degrees of 
+freedom:
 \begin{equation}
@@
 \end{equation}
-In order to simplify this expression we should get rid of the sum with
-respect to the internal bath indices $p_\sigma$ and $q_\sigma$, ideally
-contracting them with the outer indices $b_\sigma$.
-However, this requires to bring all the bath bitsets so to precede the
-impurity states:
+where $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the expansion
+coefficient in the Fock basis.
+
+To further simplify this expression, it is essential to eliminate the 
+sums over the internal bath indices $p_\sigma$ and $q_\sigma$, ideally 
+contracting them with the outer bath indices $b_\sigma$. This requires 
+reorganizing the bit representation of the basis states to bring the 
+bath bitsets before the impurity states:
 $$
@@
 $$
-where $C_{p_\up,i_\dw}  = (-1)^{\#\vec{n}_{p\up} \cdot
-\#\vec{n}_{i\dw}}$, with $\#\vec{n}_{\alpha\sigma}$ counting the bits set to
-1 in the occupation number vector $\vec{n}_{\alpha\sigma}$, is an overall
-fermionic sign depending on the $\ket{p_\up}$ and $\ket{i_\dw}$ bit configurations. 
-Inserting this relation in the equation for the iRDM we obtain:
+where the fermionic sign factor
+$C_{p_\up,i_\dw}  = (-1)^{\#\vec{n}_{p\up} \cdot
+  \#\vec{n}_{i\dw}}$
+accounts for the exchange of the bath $\ket{p_\up}$  and impurity
+$\ket{i_\dw}$ bit configurations.
+Here, $\#\vec{n}_{\alpha\sigma}$ denotes the number of set bits in the 
+occupation vector $\vec{n}_{\alpha\sigma}$.
+
+Substituting this relation back into the iRDM expression yields:
 \begin{equation}
@@
   \end{equation}
-The numerical implementation requires few modifications with respect
-to the previous case. In particular it is important to recall that the
-ordering of the \emph{key-value} pairs in the {\tt sparse\_map} in this case
-follows a contiguous ordering and that their decomposition is necessary
-to reconstruct the correct Fock state index. See the following
-listing:
+where the term 
+$C_{b_\up,i_\dw}C_{b_\up,j_\dw}$ accounts for the fermionic 
+signs associated with the bath-impurity bitset exchange.
+
+In numerical implementations, this approach introduces a few 
+key differences with respect to the {\bf normal} mode.
+In particular, the 
+ordering of the \emph{key-value} pairs in the {\tt sparse\_map} 
+must reflect the contiguous bitset structure, which is critical 
+for correctly reconstructing the Fock state indices.
+See the following listing:
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 \end{lstlisting}
-%GBtodo placeholder: I checked and heavily edited all the iRDM section
 
 \subsection{Bath Functions}\label{sSecFunc}
-The module {\tt ED\_BATH\_FUNCTIONS} implements on-the-fly
-calculations of the hybridization function $\Delta_{\a\b\s\s'}(z)=\sum_\nu
-{V^\nu_{\a\s}}(z\11-h^\nu_{\a\b\s\s'})^{-1}V^\nu_{\b\s'}$ and the
-non-interacting Green's functions $G^0_{\a\b\s\s'}(z) =
-[(z + \mu)\delta_{\a\b\s\s'} - h^0_{\a\b\s\s'} -
-\Delta_{\a\b\s\s'}(z)]^{-1}$ for any frequency $z\in\CCC$. 
-The module contains implementations for any case according to the
-values of {\tt ed\_mode} and {\tt bath\_type}, either with supplied
-user bath (a rank-1 array of doubles) or using the allocated {\tt
-  effective\_bath} instance {\tt dmft\_bath}. 
-We provide different functions to get either $\Delta$, $G^0$ and its
-directly its inverse $[G^0]^{-1}$, which are used to evaluate the
-self-energy functions upon request, see \secu{sSecIO}.
-In the superconductive case {\tt ed\_mode}={\bf superc} different
-procedures can be used to retrieve the anomalous components of any
-function defined above in the Nambu basis.
+The module {\tt ED\_BATH\_FUNCTIONS} implements the on-the-fly 
+calculation of the hybridization function 
+$\Delta_{\a\b\s\s'}(z)$ and the non-interacting Green's functions 
+$G^0_{\a\b\s\s'}(z)$ for arbitrary complex frequencies $z \in \CCC$. 
+These are defined as
+\begin{equation}
+\Delta_{\a\b\s\s'}(z) = \sum_\nu V^\nu_{\a\s} 
+\left( z\11 - h^\nu_{\a\b\s\s'} \right)^{-1} V^\nu_{\b\s'},
+\end{equation}
+\begin{equation}
+G^0_{\a\b\s\s'}(z) = 
+\left[ (z + \mu)\delta_{\a\b\s\s'} - h^0_{\a\b\s\s'} - 
+\Delta_{\a\b\s\s'}(z) \right]^{-1},
+\end{equation}
+where $V^\nu_{\a\s}$ and $h^\nu_{\a\b\s\s'}$ are the bath coupling 
+and bath Hamiltonian matrices, respectively, and $\mu$ is the chemical 
+potential.
+
+The module supports all cases defined by the {\tt ed\_mode} and 
+{\tt bath\_type} variables, including both user-supplied baths (provided 
+as rank-1 arrays of doubles) and the internally allocated {\tt 
+effective\_bath} instance {\tt dmft\_bath}. This flexibility ensures 
+compatibility with a wide range of other solvers.
+
+Different routines are available for directly evaluating $\Delta$, 
+$G^0$, and its inverse $[G^0]^{-1}$, which are critical for computing 
+the self-energy functions on demand (see \secu{sSecIO}).
+
+In the superconducting case, where {\tt ed\_mode}={\bf superc}, 
+special care is needed to properly handle the anomalous (off-diagonal) 
+components within the Nambu basis. In this case, the bath functions 
+must include both the normal and anomalous components, 
+which can significantly alter the form of the self-energy.
 
 \subsection{Bath Optimization}\label{sSecFit}
-{\color{red} to be revised, copy\&paste from edipack paper: well it is
-  essentiall the same shit} 
-In the DMFT context the bath needs to be optimized
-against a given realization of the Weiss field
-${\GG^{-1}_{0}}_{\a\b\s\s'}(z)$, or the corresponding {\it hybridization} function
-$\Theta = (z + \mu)\11 - H^{loc} -\GG_0^{-1}](z)$. While the Weiss
-field is obtained from the DMFT self-consistency
-equation~\cite{Georges1996RMP}, bath discretization impose to  find an optimal
-description of the continuous Weiss field in terms of the finite
-number of parameters of the bath (see \secu{sSecBath}.
-Although different algorithms can be envisaged to perform this
-step~\cite{Garcia2004PRL,Taranto2012PRB} which are perfectly valid in
-some physical contexts.
-In order to enable the users to use their preferred 
-method in \NAME we keep the optimization implementation independent
-from the rest of the code. Yet, we offer a fully fledged optimization
-strategy based on the  conjugate gradient (CG) minimization of the cost function:
-$$
-\chi = \sum_{n=1}^{L_\mathrm{fit}}\frac{1}{W_n}||X(i\omega_n) - X^\mathrm{QIM}(i\omega_n;\{V,h\})||_q
-$$
-where the symbol $|| \cdot ||_q$ is a suitably defined $q$-norm in the
-matrix function space, $X_{\a\b}={\GG_{0}}_{\a\b\s\s'},\,\Theta_{\a\b\s\s'}$ are the user
-supplied local functions and
-$X_{\a\b}^\mathrm{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
-quantum impurity model functions, defined above.
-Notably, more sophisticated optimization algorithms have been
-recently implemented to better undertake the minimization of similar
-cost functions. However, these developments are designed to work with truncated
-algorithms, e.g. sCI or DMRG, describing systems with a larger number of
-bath levels.   
-In the ED context however, where the efficient and wise selection of
-the relatively few bath levels becomes crucial, the CG minimization of
-the local functions proved to be the most efficient and
-flexible optimization scheme so far.
-
-The fit procedure is entirely wrapped by the single function {\tt
-  ed\_chi2\_fitgf} contained in the module \texttt{ED\_BATH\_FIT}.   
-In order to exploit regularity of the functions the fit is 
-performed using imaginary Matsubara frequency. 
-The actual form of $X_{\a\b\s\s'}$ is controlled by the input parameter
-\texttt{cg\_Scheme=Weiss,Delta}.
-
-In order to fine tune the optimization step in \NAME\ we
-introduced a number of control parameters. To start with, we include
-two distinct CG algorithms in the library, controlled by the input variable
-\texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-Numerical Recipes~\cite{NumRec77}. Yet, in order to guarantee
-back-compatibility with respect to the past literature, we also provide the
-possibility of using the minimization procedure published in
-Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-community.
-
-The gradient $\nabla\chi$ required by the CG algorithm can be
-evaluated either analytically or numerically as
-controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-\texttt{cg\_method=1} only numerical gradient can be used.
-The number of Matsubara frequency $L_\mathrm{fit}$ used in the fit procedure
-is controlled  by the input parameter \texttt{cg\_Lfit}.
-This parameter can be used to restrict the fit to the low frequency
-part as the large frequency tails of the local Matsubara functions
-have universal behavior.
-Similarly, the weight  $W_n=1,1/L_\mathrm{fit},1/\omega_n$ is used to
-enhance the weight of low energy part with respect to the
-intermediate-to-large energy one in the cost function.
-This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-Another  factor contributing to determine the behavior
-of the fit is the power $q$ of the cost function $\chi$. By tuning
-this parameter, controlled by input variable \texttt{cg\_pow}, it is
-possible to enhance or suppress the differences in the $\chi$ in order
-to improve (or simplify) the optimization procedure.
-
-Finally, we introduced few additional parameters which aim to
-control the quality of the fit. The first is the fit tolerance,
-controlled by the input parameter \texttt{cg\_Ftol}, which
-determines the convergence threshold of the minimization procedure.
-The second is the maximum number of iterations \texttt{cg\_Niter}
-allowed for the CG algorithm to determine the minimum.
-The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-condition of the minimization procedure. We envisaged  three
-possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-$C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-$C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-the corresponding argument. Increasing the value of the stop
-parameter generally loosens up the exit conditions of the minimization.
+In the DMFT framework, the bath parameters must be optimized to 
+faithfully reproduce the Weiss field, 
+${\GG^{-1}_{0}}_{\a\b\s\s'}(z)$, or its corresponding hybridization 
+function 
+\begin{equation}
+\Theta(z) = (z + \mu)\11 - H^\mathrm{loc} - \GG_0^{-1}(z),
+\end{equation}
+where $\mu$ is the chemical potential and $H^\mathrm{loc}$ is the 
+local non-interacting Hamiltonian. The Weiss field is obtained from the DMFT 
+self-consistency equation~\cite{Georges1996RMP}, while the bath 
+discretization requires a careful fitting of this continuous function 
+using a finite set of bath parameters (see \secu{sSecBath}).
+
+Several algorithms have been proposed for this optimization 
+step~\cite{Garcia2004PRL,Taranto2012PRB}, each with strengths suited 
+to different physical contexts. To maintain flexibility in \NAME, 
+we provide a general optimization interface that is independent 
+from the core impurity solver. However, we also include a fully 
+integrated optimization routine based on the conjugate gradient (CG) 
+minimization of the cost function:
+\begin{equation}
+\chi = \sum_{n=1}^{L_\mathrm{fit}} 
+\frac{1}{W_n} \left\|X(i\omega_n) - 
+X^\mathrm{QIM}(i\omega_n; \{V, h\}) \right\|_q,
+\end{equation}
+where the $q$-norm is a suitably chosen distance metric in the 
+matrix function space. Here, $X_{\a\b} = {\GG_{0}}_{\a\b\s\s'}$ or 
+$\Theta_{\a\b\s\s'}$ are the user-supplied local functions, while 
+$X_{\a\b}^\mathrm{QIM} = G^0_{\a\b\s\s'}$ or 
+$\Delta_{\a\b\s\s'}$ are the corresponding functions for the quantum 
+impurity model, as defined in \secu{sSecFunc}.
+
+While more sophisticated optimization methods have been developed for 
+truncated algorithms like sCI or DMRG, which handle systems with a 
+larger number of bath levels, the CG minimization approach has proven 
+both efficient and flexible for the small to moderate bath sizes 
+typical in ED solvers.
+
+The entire fit procedure is encapsulated in the function 
+\texttt{ed\_chi2\_fitgf} provided by the module 
+\texttt{ED\_BATH\_FIT}. To exploit the regularity of the bath functions, 
+the fit is performed on the Matsubara frequency axis, where the functions 
+are smooth and rapidly decaying. The form of $X_{\a\b\s\s'}$ is controlled 
+by the input parameter \texttt{cg\_Scheme=Weiss,Delta}.
+
+To provide maximum control over the fitting process, we include several 
+tunable parameters:
+\begin{itemize}
+\item \texttt{cg\_method=0,1} - Chooses the CG algorithm: 
+\texttt{0} for a Fletcher-Reeves-Polak-Ribiere variant adapted from 
+Numerical Recipes~\cite{NumRec77}, and \texttt{1} for the original 
+algorithm described in Ref.\onlinecite{Georges1996RMP}, commonly used 
+in the DMFT community.
+\item \texttt{cg\_grad=0,1} - Sets the gradient calculation method: 
+\texttt{0} for analytical gradients (when available), \texttt{1} for 
+numerical gradients (required if \texttt{cg\_method=1}).
+\item \texttt{cg\_Lfit} - Sets the number of Matsubara frequencies 
+$L_\mathrm{fit}$ used in the fit. This can be used to restrict the 
+fit to the low-frequency regime, where the function behavior is 
+most relevant.
+\item \texttt{cg\_Weight=0,1,2} - Determines the frequency weighting 
+scheme: \texttt{0} for uniform, \texttt{1} for inverse frequency 
+weighting, and \texttt{2} for inverse Matsubara index weighting, which 
+can emphasize low-energy contributions.
+\item \texttt{cg\_pow} - Sets the power $q$ of the cost function, 
+allowing the user to fine-tune the sensitivity of the optimization 
+to outliers.
+\item \texttt{cg\_Ftol} - Controls the fit tolerance, setting the 
+convergence threshold for the CG minimization.
+\item \texttt{cg\_Niter} - Specifies the maximum number of allowed 
+iterations for the CG minimization.
+\item \texttt{cg\_stop=0,1,2} - Defines the exit condition of the 
+minimization. The options are:
+\begin{align*}
+C_1 & = |\chi^{n-1} - \chi^n| < \mathtt{cg\_Ftol} (1+\chi^n), \\
+C_2 & = \left\|x_{n-1} - x_n\right\| < 
+\mathtt{cg\_Ftol} (1+\left\|x_n\right\|),
+\end{align*}
+where $\chi^n$ is the cost function at the $n^\mathrm{th}$ step, and 
+$x_n$ the corresponding parameter vector. The stop condition is a 
+logical OR between these criteria, with the parameter value selecting 
+which condition to apply.
+\end{itemize}
+
+Together, these parameters provide precise control over the fitting 
+process, allowing users to balance speed and accuracy according to 
+their specific needs.
+
+% In the DMFT context the bath needs to be optimized
+% against a given realization of the Weiss field
+% ${\GG^{-1}_{0}}_{\a\b\s\s'}(z)$, or the corresponding {\it hybridization} function
+% $\Theta = (z + \mu)\11 - H^{loc} -\GG_0^{-1}](z)$. While the Weiss
+% field is obtained from the DMFT self-consistency
+% equation~\cite{Georges1996RMP}, bath discretization impose to  find an optimal
+% description of the continuous Weiss field in terms of the finite
+% number of parameters of the bath (see \secu{sSecBath}.
+% Although different algorithms can be envisaged to perform this
+% step~\cite{Garcia2004PRL,Taranto2012PRB} which are perfectly valid in
+% some physical contexts.
+% In order to enable the users to use their preferred 
+% method in \NAME we keep the optimization implementation independent
+% from the rest of the code. Yet, we offer a fully fledged optimization
+% strategy based on the  conjugate gradient (CG) minimization of the cost function:
+% $$
+% \chi = \sum_{n=1}^{L_\mathrm{fit}}\frac{1}{W_n}||X(i\omega_n) - X^\mathrm{QIM}(i\omega_n;\{V,h\})||_q
+% $$
+% where the symbol $|| \cdot ||_q$ is a suitably defined $q$-norm in the
+% matrix function space, $X_{\a\b}={\GG_{0}}_{\a\b\s\s'},\,\Theta_{\a\b\s\s'}$ are the user
+% supplied local functions and
+% $X_{\a\b}^\mathrm{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
+% quantum impurity model functions, defined above.
+% Notably, more sophisticated optimization algorithms have been
+% recently implemented to better undertake the minimization of similar
+% cost functions. However, these developments are designed to work with truncated
+% algorithms, e.g. sCI or DMRG, describing systems with a larger number of
+% bath levels.   
+% In the ED context however, where the efficient and wise selection of
+% the relatively few bath levels becomes crucial, the CG minimization of
+% the local functions proved to be the most efficient and
+% flexible optimization scheme so far.
+
+% The fit procedure is entirely wrapped by the single function {\tt
+%   ed\_chi2\_fitgf} contained in the module \texttt{ED\_BATH\_FIT}.   
+% In order to exploit regularity of the functions the fit is 
+% performed using imaginary Matsubara frequency. 
+% The actual form of $X_{\a\b\s\s'}$ is controlled by the input parameter
+% \texttt{cg\_Scheme=Weiss,Delta}.
+
+% In order to fine tune the optimization step in \NAME\ we
+% introduced a number of control parameters. To start with, we include
+% two distinct CG algorithms in the library, controlled by the input variable
+% \texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
+% Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
+% Numerical Recipes~\cite{NumRec77}. Yet, in order to guarantee
+% back-compatibility with respect to the past literature, we also provide the
+% possibility of using the minimization procedure published in
+% Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
+% community.
+
+% The gradient $\nabla\chi$ required by the CG algorithm can be
+% evaluated either analytically or numerically as
+% controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
+% \texttt{cg\_method=1} only numerical gradient can be used.
+% The number of Matsubara frequency $L_\mathrm{fit}$ used in the fit procedure
+% is controlled  by the input parameter \texttt{cg\_Lfit}.
+% This parameter can be used to restrict the fit to the low frequency
+% part as the large frequency tails of the local Matsubara functions
+% have universal behavior.
+% Similarly, the weight  $W_n=1,1/L_\mathrm{fit},1/\omega_n$ is used to
+% enhance the weight of low energy part with respect to the
+% intermediate-to-large energy one in the cost function.
+% This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
+% Another  factor contributing to determine the behavior
+% of the fit is the power $q$ of the cost function $\chi$. By tuning
+% this parameter, controlled by input variable \texttt{cg\_pow}, it is
+% possible to enhance or suppress the differences in the $\chi$ in order
+% to improve (or simplify) the optimization procedure.
+
+% Finally, we introduced few additional parameters which aim to
+% control the quality of the fit. The first is the fit tolerance,
+% controlled by the input parameter \texttt{cg\_Ftol}, which
+% determines the convergence threshold of the minimization procedure.
+% The second is the maximum number of iterations \texttt{cg\_Niter}
+% allowed for the CG algorithm to determine the minimum.
+% The last parameter \texttt{cg\_stop=0,1,2} selects the exit
+% condition of the minimization procedure. We envisaged  three
+% possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
+% $C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
+% $C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
+% is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
+% the corresponding argument. Increasing the value of the stop
+% parameter generally loosens up the exit conditions of the minimization.
 
@@
 \subsection{Input/Output}\label{sSecIO}
-The module {\tt ED\_IO} provides access to the results of the Lanczos
-diagonalization of the quantum impurity problem.
-As any single instance of the code is preserved in the memory until a
-new call is made, access to the memory pool is only possible through
-specific functions implemented in {\tt ED\_IO}. For instance, dynamical response functions, self-energy components or impurity
-observables can all be retrieved using dedicated functionalities.
-Additionally we provide procedures to perform on-the-fly
-re-calculation of the impurity Green's functions and self-energy on a
-given arbitrary set of points in the complex frequency domain
-exploiting their storage in terms of {\tt gfmatrix} objects.
-A long list of available functions is contained in the on-line
-documentation (see
-\href{https://edipack.github.io/EDIpack2.0/edipack2/13_io.html#ed-io}{https://edipack.github.io/EDIpack2.0/edipack2/13\_io.html\#ed$-$io})
-Here we limit the discussion to two paradigmatic examples.
-The first is the function {\tt ed\_get\_dens} which write on the
-provided input array the value of the orbital impurity occupations
-$\langle n_{\a\s}\rangle$. Analogously {\tt ed\_get\_sigma} is used to
-retrieve the normal or anomaous components of the Matsubara or
-Real-axis self-energy function $\Sigma(z)$. This latter represents the
-key output of the calculation in 
-any DMFT application.
+The \texttt{ED\_IO} module provides comprehensive access to the 
+results of the Lanczos diagonalization of the quantum impurity 
+problem. Since each instance of the code persists in memory until a 
+new calculation is initiated, access to the relevant data is managed 
+through a set of dedicated functions. These include routines for 
+extracting dynamical response functions, self-energy components, and 
+impurity observables, as well as for performing on-the-fly 
+recalculation of the impurity Green's functions and self-energies at 
+arbitrary points in the complex frequency domain. The latter 
+capability is enabled through the efficient use of \texttt{gfmatrix} 
+objects for data storage.
+
+A full list of available functions, including parameter descriptions 
+and usage examples, can be found in the online documentation 
+Here, we highlight two representative examples:
+The first is the function \texttt{ed\_get\_dens}, which populates the 
+provided input array with the orbital impurity occupations 
+$\langle n_{\a\s}\rangle$. This function is essential for extracting 
+local density information, a key diagnostic in many DMFT studies.
+
+The second example is \texttt{ed\_get\_sigma}, which retrieves the 
+normal or anomalous components of the Matsubara or real-axis 
+self-energy function $\Sigma(z)$. This function represents a central 
+output of any DMFT calculation, as the self-energy encapsulates the 
+full set of local electronic correlations and their frequency 
+dependence.
 

### 2025-05-11 02_install.tex
Updated draft
- use subfiles, so we can compile in every subfile
- written something re. umatrix
- updated gitignore
Finish polishing 03_edipack text Quick review of 02_install.

@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Installation}\label{SecInstall}
@@
 A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C programming language.
+specific bindings to the C/C++ programming language.
 
 \subsection{Structure}\label{sSecInstallStructure}
-\NAME is a modular library which contains three principal structures.
-At the core is the exact diagonalization solver: \NAME.
-Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
-inequivalent impurity problems. Finally, there we provide a Fortran-C/C++
-interface, which enables development of additional API or
-interoperability with other, external, software.
+\NAME is a modular library organized into three main components. At its 
+core is the exact diagonalization solver, which provides the primary 
+computational engine. Building on this, the library includes 
+{\tt EDIpack2ineq}, an extension for handling multiple inequivalent 
+impurity problems. Finally, a Fortran-C/C++ interface is provided for 
+seamless integration with external software and the development of 
+additional APIs.
 
@@
 \item{\bf EDIpack2.}
-This constitutes the  building block of the whole software. This part
-implement the  with the Lanczos-based solver for generic quantum
-impurity systems encoding different symmetries, i.e. quantum number
-conservations and apt to solve multi-orbital problems, also in
-presence of coupling to local phonons.  
-The \NAME solver has a hierarchical and modular structure: different
-sections of the library communicate through a shared memory layer. The
-top module of the library is {\tt EDIPACK2} which, once loaded,
-enables access to the Fortran API in terms of suitable procedures to
-initialize, execute and finalize the solver or to retrieve internal
-quantities while making opaque to the user the internal structure of
-the library. 
-A detailed presentation of the library can be found in
-Sec.\ref{SecEDIpack}.
+  This module forms the foundation of the library, implementing the 
+  Lanczos-based solver for general quantum impurity problems. It 
+  supports systems with a wide range of symmetries, including quantum 
+  number conservation, multi-orbital models, and even coupling to local 
+  phonons. The \NAME solver is structured hierarchically and modularly, 
+  with different sections of the library communicating through a shared 
+  memory layer. The top-level module, {\tt EDIPACK2}, provides access 
+  to the core Fortran API, exposing key procedures for initialization, 
+  execution, and finalization, while abstracting the underlying data 
+  structures. A detailed overview of this part of the library is 
+  provided in Sec.\ref{SecEDIpack}.
 
 \item{\bf EDIpack2ineq.}
-This part of the software, leveraging on the object oriented concepts
-available in modern Fortran, aims to extend the \NAME library to the
-case of multiple inequivalent and independent impurity problems. This
-is particularly useful while using \NAME as a solver for DMFT in
-presence of unit cells with inequivalent atoms, for systems with
-somehow broken translational symmetry (e.g. heterostructures, large
-supercells, etc.).
+  This extension, developed using modern Fortran constructs,
+  enables the treatment of multiple, independent quantum 
+impurities. It is particularly useful in DMFT applications involving 
+unit cells with inequivalent atomic sites or systems with broken 
+translational symmetry, such as heterostructures, large supercells, 
+or disordered materials. This module provides flexible memory 
+management and supports the simultaneous solution of multiple impurity 
+problems, as discussed in Sec.\ref{sSecIneq}.
 
 \item{\bf EDIpack2 C-bindings.}
-\NAME includes a single module implementing a Fortran-C/C++ interface of the main
-library procedures. The module is developed around the implicit {\tt
-  ISO\_C\_BINDING} capabilities of the most recent Fortran
-distributions, which enable to translate Fortran procedures directly
-to C. In order to overcome all the difficulties related to the internal
-structure of the library,  we interfaced all and just the
-procedures and the variables exposed to the user. 
-This module aims to foster interoperability of \NAME  with different
-third party softwares as well as to support development of additional
-API.
-
-% \subsection{Dependent software}
-% As a concrete example illustrating the interoperability of the
-% software we here illustrate the case of EDIpy2, i.e. the Python API for
-% \NAME and present an interface layer to Triqs (Toolbox
-% for Reasearch In Quantum Systems).
-
-% \item{\bf EDIpy2.}
-% This is a simple Python module which provides Python API to the
-% \NAME Fortran library. This interface is built around the Python
-% support to C-types, which allows to import the dynamic C-binding
-% library generated upon building \NAME. The module contains a specific
-% class, whose methods mirrors through  duck-typing all the available
-% procedures of \NAME as well as it gives access to relevant shared
-% control variables.
-
-% \item{\bf EDIpack2Triqs.}
-% This is a thin interface layer from \NAME to Triqs,
-% built around the Python API of the \NAME library. The exact
-% diagonalization solver is encapsulated in a dedicated class,
-% containing the necessary methods to initialize and run a single
-% instance of the solver. The interface also includes a specific class
-% encompassing the effective discretized bath structure as well as their 
-% optimization methods.
-
+  For enhanced interoperability, \NAME includes a dedicated module 
+implementing Fortran-C/C++ bindings for key library procedures. This 
+module relies on the {\tt ISO\_C\_BINDING} capabilities available in 
+modern Fortran, allowing direct translation of Fortran functions to C. 
+To ensure a straightforward user experience, only the functions and 
+variables directly exposed to the user are included in this binding, 
+shielding developers from the complexity of the library's internal 
+architecture. This interface is intended to facilitate integration 
+with third-party software and support the development of custom APIs.
 \end{itemize}
@@
 generated at the end of the installation procedure.
+
+\end{document}

### 2025-05-11 03_edipack2.tex
Finish polishing 03_edipack text Quick review of 02_install.

@@
 \subsection{EDIpack2ineq: inequivalent impurities}\label{sSecIneq}
-It is often necessary to solve systems with several, independent,
-quantum impurities. Paradigmatic examples arise in the DMFT
-framework when dealing with the effective description of lattices
-built out of unit cells hosting multiple inequivalent atoms or large
-super-cell systems with possibly broken translational symmetries,
-e.g. heterostructures of correlated materials, disordered systems,
-etc.
-As the structure of \NAME allows the presence of a single instance of
-the solver at any time, we implemented a suitable extension to deal
-with multiple impurities. Specifically {\tt EDIpack2Ineq} is a
-sub-library which complements \NAME, wrapping memory and procedures in
-order to enable simultaneous treatment of  inequivalent impurities. 
-Using standard Fortran interfaces it is possible to group all the
-\NAME and {\tt EDIpack2ineq} functions under the same name without
-compromising the software functionalities.  
-Here below we briefly discuss the main additions introduced by {\tt
-  EDIpack2ineq}.
+In many contexts, it is necessary to solve systems with multiple, 
+independent quantum impurities. This situation frequently arises in 
+DMFT when modeling lattices with complex unit cells containing 
+inequivalent atomic sites, or in supercell calculations where 
+translational symmetry is broken, as in heterostructures, disordered 
+systems, or multiorbital setups.
+
+Given that \NAME allows only a single instance of the solver at a 
+time, a dedicated extension is required to handle these more complex 
+cases. To address this, we developed the {\tt EDIpack2ineq} 
+sub-library, which extends the base functionality of \NAME by managing 
+memory and procedures for multiple impurities. This approach ensures 
+that all functions remain accessible through standard Fortran 
+interfaces, seamlessly integrating both \NAME and {\tt EDIpack2ineq} 
+without compromising overall software design.
+
+Below, we provide a brief overview of the main features introduced by 
+{\tt EDIpack2ineq}.
 
 \subsubsection{Structure}\label{ssSecIneqStructure}
-The sub-library is composed of a number of Fortran modules which are
-wrapped by {\tt EDIPACK2INEQ}. This latter represents the main user
-interface and gives access to all the available procedures and
-variables as needed to solve quantum impurity problems.
-The user needs to invoke use of this module alongside the \NAME one:
+The core of the {\tt EDIpack2ineq} sub-library consists of several 
+Fortran modules, all wrapped under the main interface module 
+{\tt EDIPACK2INEQ}. This module provides access to the full range of 
+procedures and variables required to solve inequivalent quantum 
+impurity problems. To use this extension, the user must include both 
+the main \NAME and the {\tt EDIpack2ineq} modules, as shown below:
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 
-A major part of the {\tt EDIpack2ineq} library is to define global
-variables which wrap and conserve the memory pool of \NAME.
-For instance we implement a number of
-globally shared arrays with an increased rank to store the
-variables in any memory instance of \NAME and accessible through
-the input/output procedures (see \secu{sSecIO}).
-Specific objects, e.g. {\tt effective\_bath} or {\tt gfmatrix}, in
-principle require dedicated MPI
-communication when parallel execution of the solver among independent
-impurities. However, we opt for the much simpler and economic solution
-of reading these objects from the file in which they get saved
-anyway.
+A significant part of the {\tt EDIpack2ineq} extension is the 
+definition of global variables that extend the memory pool of 
+\NAME. This includes higher-rank arrays for storing impurity-specific 
+data, ensuring that each impurity's state is maintained separately 
+during the computation. While dedicated MPI communication could be 
+used to manage specific objects in parallel, e.g. {\tt
+  effective\_bath} or {\tt gfmatrix}, we opted for a simpler and safer  
+file-based approach to maintain compatibility with the standard I/O 
+procedures described in \secu{sSecIO}.
 
 \subsubsection{Core routines}\label{ssSecIneqGlobal}
-The module {\tt E2I\_MAIN} wraps the extensions to the main algorithms
-of \NAME, namely: initialization, diagonalization and finalization,
-preserving the original naming convention.  
-The initialization process is handled by {\tt ed\_init} which is
-extended to accepts a bath array or rank-2 (as opposed to rank-1 array
-in the \NAME implementation). The leading dimension now determines the
-number of inequivalent impurity problems to be solved. This procedure
-initialize all the {\tt EDIpack2ineq} variables and prepare each bath
-for the diagonalization step. 
-In {\tt ed\_solve}, which accepts the same rank-2 bath array, performs the
-diagonalization of each quantum impurity problem in either serial of
-parallel mode. The parallel mode is further controlled by the input
-function {\tt mpi\_lanc=T/F}. If true Lanczos diagonalization is
-performed in parallel and inequivalent sites are treated
-sequentially. The inverse if false.   
-The finalization procedure with full memory release is performed in
-{\tt ed\_finalize}.
+The module {\tt E2I\_MAIN} wraps the key extensions to the main 
+algorithms of \NAME, including initialization, diagonalization, and 
+finalization, while preserving the original function names for 
+consistency.
+
+\paragraph{\bf Initialization} The function {\tt ed\_init} is extended to 
+  accept a rank-2 bath array, where the leading dimension specifies 
+  the number of inequivalent impurity problems. This ensures each bath 
+  is properly initialized for subsequent diagonalization.
+
+\paragraph{\bf Diagonalization} The function {\tt ed\_solve} also accepts this 
+  rank-2 bath array and manages the diagonalization of each impurity 
+  problem. Parallel execution is controlled by the input flag 
+  {\tt mpi\_lanc=T/F}, which determines whether the Lanczos 
+  diagonalization is performed in parallel or sequentially across 
+  different impurities.
+
+\paragraph{\bf Finalization} Memory release is handled through the extended 
+{\tt ed\_finalize} function, which clears the memory pool for all 
+inequivalent impurity instances.
 
 \subsubsection{Inequivalent Baths}\label{ssSecIneqBath}
-The inequivalent impurities extension is encoded in {\tt E2I\_BATH}
-which contains procedures to control the baths setup on the user side
-and the  implementation of conventional symmetry operations.
-In the {\tt E2I\_BATH\_REPLICA} module we extend all the functions
-which set the replica/general bath matrix basis 
-$\vec{\Gamma}$ and the corresponding initial variational parameters
-$\vec{\lambda}$. Although the variational parameters are generally
-different from site to site, in the current implementation the matrix
-basis is independent from the impurities number. This will possibly be
-relaxed in a future release. 
-Analogously, in the module {\tt E2I\_BATH\_FIT} we implement an extension of the generic
-function {\tt ed\_chi2\_fitgf} to perform multiple independent
-bath optimization for all inequivalent impurities in terms of an MPI iterative cycle.
+The bath setup for multiple impurities is managed by the 
+{\tt E2I\_BATH} module, which provides functions for defining 
+site-specific bath matrices and their corresponding variational 
+parameters. This includes support for conventional symmetry operations 
+and the handling of replica bath structures.
+
+In the module {\tt E2I\_BATH\_REPLICA}, we extend the 
+matrix basis definition for the variational parameters 
+$\vec{\lambda}$, allowing for flexible bath optimization across 
+multiple sites. Although the matrix basis is currently shared among 
+all impurities, future versions may allow for fully independent 
+bath parameterizations.
+
+Additionally, the {\tt E2I\_BATH\_FIT} module extends the generic 
+{\tt ed\_chi2\_fitgf} function to support simultaneous, independent 
+bath optimization for all impurities using MPI, thereby improving the 
+efficiency of large-scale calculations.
 
 \subsubsection{Input/Output}\label{ssSecIneqIO}
-A key part of the {\tt EDIpack2ineq} library is the extension for the
-input/output procedures to return observables or dynamical functions per inequivalent impurity.
-The module {\tt E2I\_IO} implements numerous functions which retrieve
-or evaluate on-the-fly any quantity accessible in \NAME for any given
-impurity (or all of them) using the same naming original convention
-defined in \NAME.
+A key component of the {\tt EDIpack2ineq} extension is the 
+enhanced I/O capability for handling impurity-specific observables. 
+The {\tt E2I\_IO} module includes a variety of functions for 
+retrieving site-resolved quantities, such as local Green's functions, 
+self-energies, and density matrices. These functions use the same 
+naming conventions as the core \NAME library, ensuring a consistent 
+user experience across single and multi-impurity calculations.
 

### 2025-05-11 03_edipack2.tex
Minor change in Quantum Numbers modes (essentially a test to sync OF with Gihub)

@@
 
- - The {\bf normal} case conserves both the total occupation $N$
+\begin{itemize}
+\item{} The {\bf normal} case conserves both the total occupation $N$
 and the total magnetization $S_z$, or equivalently, the total number
@@
 
-- The {\bf superc} case maintains onlu the $S_z$ conservation,
+\item{} The {\bf superc} case maintains onlu the $S_z$ conservation,
 allowing the total charge to not be conserved. This setting captures
@@
 
-- The {\bf nonsu2} case conserves the total
+\item{} The {\bf nonsu2} case conserves the total
 charge $N$ while allowing spin symmetry group to be not conserved.
@@
 in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
+\end{itemize}
 

### 2025-05-12 04_cbinding.tex
Added some Julia comments

@@
 The only prerequisite to use this option is the presence of a functioning EDIpy2 installation, which w2dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
+
 In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt   EDIPACK}.
@@
 This thus includes some parameters that the user will ordinarily want to change from their defaults in a typical calculation such as the number of bath sites {\tt NBATH} and other parameters such as options for the bath fitting and diagonalization algorithms, but also specifically excludes other typically set input variables such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}.
-All of the these variables correspond or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
+All of the these variables correspond to or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
 Note however in particular that if the \NAME solver is used, {\tt beta} is by default only used as cut-off and does not imply a finite temperature calculation unless the user explicitly sets the parameter {\tt   ED\_FINITE\_TEMP} in section {\tt EDIPACK} to {\tt True}.
+
 Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in mostly the same way as it would be for the CT-HYB solver.
@@
 \subsection{EDIjl, the Julia API}\label{sSecInteropEDIjl}
-{\color{red} Lorenzo?}
+
+The c-bindings approach is extremely handy, in that is opens the way for interoperability 
+with a large number of languages and frameworks. As an example, an experimental Julia API 
+is provided in the EDIpack github repository. Rather than a fully functioning Julia package, 
+this is at present a proof of concept, capable of replicating the results of Fortran, C++ and
+python implementations for the Bethe lattice example driver.
+Its structure and operation mimicks that of the EDIpy layer, with minimal language-specific differences.
+
+The EDIpack Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
+This is searched upon loading the module, with the following loading hierarchy:
+
+\begin{itemize}
+\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl} will look there for the library first
+\item {\tt LD\_LIBRARY\_PATH}: for Linux systems
+\item {\tt DYLD\_LIBRARY\_PATH}: for Mac systems
+\end{itemize}
+
+in complete analogy to the Python API, the global variables and functions are contained in a  {\tt struct} called {\tt global\_env}, and can be called and assigned in the following way:
+
+\begin{itemize}
+\item A variable symbol is retrieved from the library through {\tt Libdl.dlsym} and then read via {\tt unsafe\_load}
+\item Similarly, variable assignment is achieved through {\tt Libdl.dlsym} and  {\tt unsafe\_store}
+\item Functions are called via {\tt Libdl.dlsym} and  {\tt ccall}
+\end{itemize}
 

### 2025-05-12 04_cbinding.tex
First complete draft of the edipack2triqs implementation subsection

@@
 \subsection{TRIQS interface}\label{sSecInteropTRIQS}
-{\color{red} Igor }
-A purely Python \NAME to Triqs interface is available, leveraging on
-the C-bindings and Python API. The corresponding module depends on
-\NAME (which ultimately depends on SciFortran) and Triqs.
-Assuming the two software are correctly installed in the OS, the
-EDIpack2Triqs interface is installed as follows:
+A thin compatibility layer between \NAME and the Toolbox for Research on
+Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called edipack2triqs
+is available as a stand-alone project. It is a pure Python package
+built upon \NAME's Python API  (Sec.~\ref{sSecInteropEDIpy}) that provides a
+limited object-oriented interface to the most important features of \NAME.
+edipack2triqs strives to offer seamless interoperability with program tools
+based on TRIQS by adopting data types, conventions and usage patterns
+common to other TRIQS-based impurity solvers, such as
+TRIQS/CTHYB\cite{Seth2016CPC}. It also enables execution of \NAME calculations
+in the MPI parallel mode with no extra effort from the user.
+Detailed documentation of the package can be 
+found online at \href{https://krivenko.github.io/edipack2triqs/}
+{https://krivenko.github.io/edipack2triqs/}.
+
+\subsubsection{Installation}\label{sSecInteropTRIQSInstallation}
+The package depends on \NAME (which ultimately depends on SciFortran), EDIpy2
+and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
+installed in the OS, the current development version of edipack2triqs can be 
+installed with {\tt pip} from its 
+\href{https://github.com/krivenko/edipack2triqs}{GitHub repository} as follows:
 
@@
 \end{lstlisting}
+
+\paragraph{Anaconda}
+Another option for installing the package is by using the Anaconda package 
+manager on Unix/Linux systems.
+The following commands will create a new {\tt conda} environment named 
+`edipack' and install the most recently released version of edipack2triqs along 
+with its dependencies (\NAME, EDIpy2 and the TRIQS libraries).
+
+\begin{lstlisting}[style=mybash]
+conda create -n edipack
+conda activate edipack
+conda install -c conda-forge -c edipack edipack2triqs
+\end{lstlisting}
+
+\subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
+The programming interface of edipack2triqs is built around the singleton 
+Python class {\tt EDIpackSolver} (defined in the module
+{\tt edipack2triqs.solver}), whose instance represents the internal state of 
+the \NAME library and exposes its functionality through a number of 
+attributes and methods.
+
+\paragraph{{\bf Constructor}}
+Constructor of {\tt EDIpackSolver} accepts the Hamiltonian to be diagonalized
+in the form of a second-quantized fermionic operator, the TRIQS {\tt Operator}
+object described in Sec.~8.7 of Ref.~\onlinecite{Parcollet2015CPC} (impurity 
+problems involving bosons are not supported in the current version). In 
+addition to the Hamiltonian, four {\it fundamental operator sets}
+{\tt fops\_imp\_up}, {\tt fops\_imp\_dn}, {\tt fops\_bath\_up} and
+{\tt fops\_bath\_dn} must be provided.
+Each of the sets contains pairs of labels {\tt (b,j)} carried
+by the operators $c^\dagger_{b,i} / c_{b,i}$ corresponding to either impurity
+or bath electronic degrees of freedom with a certain spin projection.
+Having these two crucial pieces of information, the constructor initializes
+the underlying Fortran library and automatically selects the appropriate
+{\tt ed\_mode=normal,superc,nonsu2} (Sec.~\ref{sSecQNs}) and
+{\tt bath\_type=normal,hybrid,general} (Sec.~\ref{sSecBath}). Besides, the
+constructor accepts a vast array of keyword arguments that allow for fine-tuning
+the diagonalization process. Among others, these include the ED algorithm
+selection, the quantum numbers to be used, parameters of the Krylov space,
+the spectrum cutoff and various tolerance levels.
+
+\paragraph{{\bf Method {\tt solve}}}
+The method {\tt solve()} of {\tt EDIpackSolver} calls
+{\tt edipy2.global\_env.solve()} and therefore performs the bulk of
+calculations. It accepts the inverse temperature $\beta$ required to calculate
+the expectation value of physical observables, and parameters of energy grids
+for Green's function calculations.
+
+\paragraph{{\bf Input parameters}}
+It is possible to read off and change parameters of the Hamiltonian between
+successive calls to {\tt solve()} via respective attributes of {\tt 
+EDIpackSolver}. Note, however, that the changes that would necessitate a change of {\tt ed\_mode} or {\tt bath\_type} are disallowed. The relevant attributes
+are the following.
+\begin{itemize}
+    \item {\tt nspin} --- the number of non-equivalent spin projections 
+          (read-only).
+    \item {\tt norb} -- the number of impurity orbitals (read-only).
+    \item {\tt hloc} --- matrix $h^0_{\alpha\beta\s\s'}$ of
+          the quadratic impurity Hamiltonian (\ref{Himp}).
+    \item {\tt Uloc}, {\tt Ust}, {\tt Jh}, {\tt Jx}, {\tt Jp} ---
+          parameters $U, U', J, J_X \text{ and } J_P$ of the impurity
+          interaction term $\hat{H}^\mathrm{int}_\mathrm{imp}$ (\ref{Hint}).
+    \item {\tt bath} --- an object representing the bath. Depending on the
+          bath type selected upon solver object construction, this object is an
+          instance of {\tt BathNormal}, {\tt BathHybrid} or {\tt BathGeneral}
+          (all three classes are members of the module
+          {\tt EDIpackSolver.bath}). The bath objects support basic arithmetic
+          operations so that a mixing scheme within a DMFT calculation can be
+          easily implemented. The way to access individual bath parameters is
+          specific to each of the three classes, and is described in detail in the       \href{https://krivenko.github.io/edipack2triqs/documentation.html\#module-edipack2triqs.bath}{online API reference}.
+\end{itemize}
+
+\paragraph{{\bf Calculation results}}
+After a successful invocation of {\tt solve()}, one can extract results of the 
+calculation from the following attributes.
+\begin{itemize}
+    \item {\tt e\_pot}, {\tt e\_kin} --- thermal average of the potential 
+          (interaction) and kinetic energy respectively.
+    \item {\tt densities}, {\tt double\_occ} --- lists of average densities and
+          double occupancies of impurity orbitals.
+    \item {\tt magnetization} --- Cartesian components of the average impurity  
+          magnetization vectors, one row per orbital.
+    \item {\tt superconductive\_phi} --- Matrix of impurity superconductive
+          order parameters
+          $\phi_{\alpha\beta} = \langle c_{\alpha\up} c_{\beta\down}\rangle$
+          in orbital space. {\color{red} Is it defined elsewhere in the text?}
+    \item {\tt g\_iw}, {\tt g\_an\_iw} --- Normal and anomalous components of
+          the Matsubara impurity Green's function.
+    \item {\tt Sigma\_iw}, {\tt Sigma\_an\_iw} --- Normal and anomalous
+          components of the Matsubara impurity self-energy.
+    \item {\tt g\_w}, {\tt g\_an\_w} --- Normal and anomalous components of
+          the real-frequency impurity Green's function.
+    \item {\tt Sigma\_w}, {\tt Sigma\_an\_w} --- Normal and anomalous
+          components of the real-frequency impurity self-energy.
+\end{itemize}
+
+The Green's functions are returned as TRIQS {\tt BlockGf} containers
+with names of the individual blocks determined from the block labels {\tt 'b'}
+found in {\tt fops\_imp\_up}, {\tt fops\_imp\_dn} and from solver's
+{\tt ed\_mode}. The Matsubara and real-frequency meshes of the TRIQS GF 
+containers (see Sec.~8.2 of Ref.~\onlinecite{Parcollet2015CPC}) are constructed
+according to the parameters passed to {\tt solve()}.
+The anomalous components of the Green's functions and self-energies are only 
+available when anomalous bath terms are present in the Hamiltonian.
+If this is not the case, an attempt to access these attributes results in a
+{\tt RuntimeError}.
+
+\paragraph{{\bf Bath parameter fitting}}
+The method {\tt EDIpackSolver.chi2\_fit\_bath()} is essentially a wrapper around
+{\tt edipy2.global\_env.chi2\_fitgf()}. It accepts the function to fit (either
+the hybridization function or the Weiss field) in the {\tt BlockGf} format,
+and returns the parameter fit result as a {\tt Bath*} object along with a
+{\tt BlockGf} representation of the fitted function. In the superconducting
+case ({\tt ed\_mode=superc}), this method accepts and returns pairs of
+the {\tt BlockGf} containers corresponding to the normal and anomalous 
+components of the quantities in question.
 
@@
 python implementations for the Bethe lattice example driver.
-Its structure and operation mimicks that of the EDIpy layer, with minimal language-specific differences.
+Its structure and operation mimicks that of the EDIpy2 layer, with minimal language-specific differences.
 
-The EDIpack Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
-This is searched upon loading the module, with the following loading hierarchy:
+The \NAME{} Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
+
+The library is searched upon loading the module, with the following order of priority:
 
 \begin{itemize}
-\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl} will look there for the library first
+\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl2} will look there for the library first
 \item {\tt LD\_LIBRARY\_PATH}: for Linux systems
@@
 
-in complete analogy to the Python API, the global variables and functions are contained in a  {\tt struct} called {\tt global\_env}, and can be called and assigned in the following way:
+\subsubsection{Structure}
 
-\begin{itemize}
-\item A variable symbol is retrieved from the library through {\tt Libdl.dlsym} and then read via {\tt unsafe\_load}
-\item Similarly, variable assignment is achieved through {\tt Libdl.dlsym} and  {\tt unsafe\_store}
-\item Functions are called via {\tt Libdl.dlsym} and  {\tt ccall}
-\end{itemize}
+In partial analogy to the Python API, the global variables, but not the functions, are contained in a  {\tt struct} called {\tt global\_env}.
 
+Similarly to the C++ case, global variables and functions are loaded as raw pointers.
+As a consequence, it is important that the dimensions of the array-like variables (such as {\tt ULOC}) and, in general, the amount of memory occupied by each variable are correcty accounted for.
+This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
+Functions are called from the dynamic library, making use of the {\tt  ccall} procedure.
+As previously stated, as a consequence of the C linking conventions multiple alternative version of the interfaced Fortran procedures are present, to account for the different input variable combinations; the EDIjl2 wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+
+\subsubsection{Installation and usage}
+
+At present, the EDIpack Julia interface is not offered as a package. The git repository has to be cloned via
+
+\begin{lstlisting}[style=mybash]
+git clone https://github.com/EDIpack/EDIjl2.0.git
+\end{lstlisting}
+
+and the location of the source files needs to be included in the user program via
+
+\begin{lstlisting}[style=mybash]
+push!(LOAD_PATH, joinpath(@__DIR__, "PATH/TO/REPO/src"))
+\end{lstlisting}
+
+The EDIjl2 module can then be loaded via
+
+\begin{lstlisting}[style=mybash]
+using EDIjl2
+\end{lstlisting}
+
+The correct way to access global variables and functions is as in the following example:
+
+\begin{lstlisting}[style=mybash]
+EDIjl2.read_input("inputED.conf")
+ed = EDIjl2.global_env
+println("Nspin = ", ed.Nspin)
+ed.Nspin = 2
+\end{lstlisting}
+
+The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.
+
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
+At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
+If the \NAME{} library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
+The {\tt MPI\_COMM\_WORLD} communicator will need to be correctly initialized by the user as well, and the program will need to be run with {\tt  mpiexec/mpirun}.
+
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIjl2.0 repository.
+This script is intended to be run serially.
+Documentation of the API and further examples are being developed.
 \end{document}

### 2025-05-13 05_examples.tex
First draft of the edipack2triqs example subsection

@@
 In this section we illustrate the functioning of the \NAME
-library and their interfaces through specific examples, including
+library and their interfaces as solver for DMFT through specific examples, including
 discussion of relevant code snippets.
-Specifically, we show how the quantum impurity solver in \NAME can be used
-to address problems of different nature within the framework of DMFT.
 
 \subsection{Bethe lattice DMFT}\label{SecExamplesBetheDMFT}
-The description of the Mott or metal to insulator transition (MIT)
-within the Bethe lattice, i.e. Cayley tree with connection
-$z\to\infty$ is conventionally considered the test bed of any DMFT
-application. Here  we discuss a guided implementation based on the
-Fortran API of \NAME of the DMFT solution of the Bethe lattice at
-$T=0$. 
-We consider a Fermi-Hubbard model:
+The test bed for any DMFT application is conventionally considered 
+the description of the Mott or metal-to-insulator transition (MIT) 
+in a Bethe lattice, i.e., a Cayley tree with coordination number 
+$z\to\infty$~\cite{Georges1996}.
+Here, we present a guided implementation of the DMFT 
+solution for the Bethe lattice at $T=0$ using \NAME as impurity
+solver.
+The model under consideration is the Fermi-Hubbard Hamiltonian:
 $$
-H = -t \sum_{\langle ij\rangle\s}c^+_{i\s}c_{j\s} + U \sum_i n_{i\up}n_{i\dw}
+H = -t \sum_{\langle ij\rangle,\s} c^\dagger_{i\s} c_{j\s} + 
+    U \sum_i n_{i\up}n_{i\dw}
     $$
-where $c^+_{i\s}$ ($c_{i\s}$) is the creation (destruction) operator for an electron at site $i$
-and with spin $\s$, $n_{i\s}=c^+_{i\s}c_{i\s}$ is the occupation
-operator and the first sum is over the nearest neighbor sites $\langle
-ij\rangle$. 
+
+where $c^\dagger_{i\s}$ ($c_{i\s}$) are the creation (annihilation) 
+operators for an electron at site $i$ with spin $\s$, and 
+$n_{i\s} = c^\dagger_{i\s} c_{i\s}$ is the corresponding occupation 
+operator. The first sum runs over nearest-neighbor pairs 
+$\langle ij \rangle$.
+
 The system is defined on a Bethe lattice with density of states
-$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$, where $D=2t$ is the
-half-bandwidth~\cite{Georges1996}.
-In DMFT this model is mapped
-onto a quantum impurity problem with an effective electronic bath
-which needs to be determined self-consistently.
-\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$,
+where $D=2t$ is the half-bandwidth.
+In DMFT this lattice model is mapped onto a quantum impurity problem with 
+an effective electronic bath that must be determined
+self-consistently.
+
+Below, we present the key components of a basic DMFT implementation 
+using \NAME for the Bethe lattice, employing either the Fortran or 
+C++ APIs. Fully operational versions of the two codes can be found 
+in the {\tt examples} directory of the \NAME source code. Both 
+samples share a similar initial structure, including memory 
+allocation, Bethe lattice creation, and solver initialization.
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.465\linewidth}
+    \center{\bf Fortran}
+\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
 program ed_hm_bethe
@@
    implicit none
-   !> Number of discretization points for the Bethe DOS
-   integer,parameter                           :: Le=5000
-   !> Bethe half-bandwidth = energy unit
-   real(8),parameter                           :: D=1d0
-   !>Bath:
+   integer                :: Le=1000
+   real(8)                :: wmixing=0.5d0
+   real(8)                :: D=1d0
+   integer                :: Nb
    real(8),allocatable    :: Bath(:)
-   !> local dynamical functions, rank-5 [Nspin,Nspin,Norb,Norb,L]
-   complex(8),allocatable,dimension(:,:,:,:,:) :: Weiss,Smats,Sreal,Gmats,Greal,Weiss_
-   ... (omissis)
-   !> READ THE input using EDIpack procedure:
-   call ed_read_input(trim(finput))
-   !
-   !> Setup the Bethe DOS $\rho$ (linear dispersion)
-   Ene = linspace(-D,D,Le,mesh=de)
-   DOS = dens_bethe(Ene,D)
+   complex(8),allocatable :: Hloc(:,:,:,:)
+   real(8),allocatable    :: Ebands(:),Dbands(:)
+   complex(8),allocatable :: Smats(:,:,:,:,:)
+   complex(8),allocatable :: Delta(:,:,:,:,:)
+   ...  
+   !Read variables
+   call ed_read_input('inputED.conf')
+   !Solver-specific arays
+   allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
+   allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
+   allocate(Hloc(Nspin,Nspin,Norb,Norb));Hloc=0d0
+   ...
+   !Initialize Bethe arrays
+   allocate(Ebands(Le),Dbands(Le))
+   Ebands = linspace(-D,D,Le,mesh=de)
+   Dbands = dens_bethe(Ebands,Wband)*de
+   !Set local H
+   call ed_set_hloc(Hloc)
 \end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingA}{\box0}
 
-The bath is described
-by the (unknown) function $\GG^{-1}_0$, i.e. the Weiss field. Within \NAME
-exact diagonalization approach, where the bath is approximated with a
-finite number of levels, the function $\GG^{-1}_0$ is used to
-determine bath parameters $\vec{x}=\{V,h\}$ using the optimization method discussed in
+\setbox0=\hbox{%
+  \begin{minipage}{0.505\linewidth}
+    \center{\bf C++}
+\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+#include <edipack2_cbinding.h>
+using namespace std;
+...
+//Main variables
+int Le = 1000;
+int iloop = 0;
+double wmixing = 0.5;
+double D = 1.0;
+//Read  variables    
+char input[] = "inputED.conf"; 
+read_input(input);      
+//Dimensions
+int64_t d[4] = {Nspin,Nspin,Norb,Norb};
+int total_size = d[0] * d[1] * d[2] * d[3];
+int total_size_n5 = total_size * Lmats;    
+// Solver-specific arrays
+vector<complex<double>> Hloc(total_size);
+vector<complex<double>> Smats(total_size_n5);
+vector<complex<double>> Delta(total_size_n5);
+...
+// Initialize Bethe arrays
+vector<double> Ebands, Dbands;
+Ebands = linspace(-D,D,Le);
+Dbands = dens_bethe(Ebands,Wband,de);
+//set local H
+ed_set_Hloc_single_N4(Hloc.data(), d);
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingB}{\box0}
+
+\begin{tabular}{c|c}\label{list2}
+  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
+\end{tabular}
+
+The bath is described by the (unknown) function $\GG^{-1}_0$, known as 
+the Weiss field ({\tt Weiss}). In the ED approach implemented in \NAME, 
+the bath is approximated using a finite number of discrete energy levels. 
+The function $\GG^{-1}_0$ is then used to determine the bath parameters 
+$\vec{x} = \{V, h\}$ through the optimization method outlined in 
 \secu{sSecFit}.
-The starting point of any calculation is determined by a suitable
-guess of the Weiss field, or equivalently of the bath parameters.
-In \NAME this operations is accomplished by the function {\tt
-  ed\_init\_solver}.
 
-\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+The starting point for any calculation is a reasonable initial guess 
+for the Weiss field, or equivalently, the bath parameters. In \NAME, 
+this is accomplished using the function {\tt
+  ed\_init\_solver} (Fortran API) or {\tt init\_solver\_site} (C++ API).
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.465\linewidth}
+    \center
+    \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+   !Initialize solver
    Nb=ed_get_bath_dimension()
@@
 \end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingA}{\box0}
 
-The iterative algorithm proceeds as follows:
-\begin{enumerate}
-\item Call the exact diagonalization {\bf impurity solver} {\tt
-    ed\_solve} whose only input is the set of parameters $\vec{x}$. All other
-  options are controlled by input file specifications ({\tt
-    ed\_read\_input}).
-\item Retrieve at least the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
-  Matsubara axis using {\tt ed\_get\_sigma}.
-\item Evaluate the local interacting Green's function
+\setbox0=\hbox{%
+  \begin{minipage}{0.505\linewidth}
+    \center
+\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+// Initialize solver
+int Nb;
+vector<double> Bath(Nb);
+Nb = get_bath_dimension();
+int64_t bath_dim[1] = {Nb};
+init_solver_site(Bath.data(), bath_dim);
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingB}{\box0}
+
+\begin{tabular}{c|c}\label{list2}
+  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
+\end{tabular}
+
+The iterative algorithm to solve the DMFT problem is based on
+a reverse communication strategy and proceeds as follows:
+\begin{itemize}
+
+\item[{\tiny $\blacksquare$}] Call the exact diagonalization {\bf impurity solver}
+  whose only input is the set of parameters $\vec{x}$ contained in a
+  rank-1 array. All  \NAME options are controlled through input file
+  specifications.
+
+\item[{\tiny $\blacksquare$}] Retrieve the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
+  Matsubara axis using dedicated function provided by \NAME API.
+
+\item[{\tiny $\blacktriangleright$}] Evaluate the local interacting Green's function
   $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
   $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
-  \item Update the Weiss field through the {\bf self-consistency}
-    relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) + \Sigma(i\omega)$. 
-  \item Optimize the bath parameters $\vec{x}$ against the updated
-    Weiss field using, for instance, {\tt ed\_chi2\_fitgf}. Restart at 1.
-\end{enumerate}
-In agreement with Reverse Communication Strategy setup, the step 3-4
-are left to the user. In addition step 5 is kept separated to
-guarantee enough freedom in the bath optimization, though we remark
-this is a crucial step which can potentially compromise the whole
-calculation.
-An example of implementation is given in the following listings.
 
-\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
-iloop=0;converged=.false.
+\item[{\tiny $\blacktriangleright$}] Update the Weiss field via the {\bf self-consistency}
+  relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
+    \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
+    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$.
+
+  \item[{\tiny $\triangleright$}] Optimize the bath parameters $\vec{x}$ against the updated
+    Weiss field,  potentially using the conjugate gradient procedures 
+supplied by \NAME. Then, restart at step 1.
+\end{itemize}
+
+The first two steps, marked by the ${\tiny \blacksquare}$ symbol, 
+are handled directly by \NAME routines. In the subsequent steps, 
+indicated by the ${\tiny \blacktriangleright}$ symbol, control returns 
+to the user, who must implement the algebraic updates required to 
+close the self-consistency loop and optimize the bath.
+Given the 
+critical importance of this optimization, \NAME provides access to 
+well-tested functions, ensuring stability and reproducibility of 
+results. Alternative optimization methods can also be employed as 
+needed. 
+An example of implementation is provided in the following listings.
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.45\linewidth}
+    \center
+    \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+!DMFT loop
 do while(.not.converged.AND.iloop<nloop)
     iloop=iloop+1     
-     !> Solve the effective impurity problem
+    ! Call ED Solver
     call ed_solve(bath)     
-     !> Retrieve impurity Self-energy on Matsubara axis
+    ! Retrieve Self-energy on Matsubara axis
     call ed_get_sigma(Smats,'m')
-     !
-     !> Build a local Green's function:
-     wfreq = pi/beta*(2*arange(1,Lmats)-1)   !automatic Fortran allocation
-     do i=1,Lmats ! One can do better than this of course 
+    ! Build local Green's function
+    wfreq = pi/beta*(2*arange(1,Lmats)-1)
+    do i=1,Lmats
        zeta= xi*wfreq(i)+xmu - Smats(1,1,1,1,i)
-        Gmats(1,1,1,1,i) = sum(DOS(:)/( zeta-Ene(:) ))*de  
+       Gmats(1,1,1,1,i)=sum(DOS/(zeta-Ene))*de  
     enddo
-     !> Update Weiss field: Self-consistency
-     Weiss(1,1,1,1,:) = one/(one/Gmats(1,1,1,1,:) + Smats(1,1,1,1,:))
-     !> Close the self-consistency fitting the new bath:
+    ! Self-consistency
+    Delta = D/4d0*Gmats
+    ! Fitting -> new bath
     call ed_chi2_fitgf(Weiss,bath,ispin=1)     
-     !>Check convergence
-     converged =( sum(abs(Weiss(1,1,1,1,:)-Weiss_(1,1,1,1,:)))/sum(abs(Weiss(1,1,1,1,:))) )<dmft_error
-     Weiss_=Weiss     
+    ! Check convergence
+    converged=check_convergence(Delta,&
+          dmft_error,Nsuccess,Nloop)
 enddo
 \end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingA}{\box0}
+
+\setbox0=\hbox{%
+  \begin{minipage}{0.52\linewidth}
+    \center
+\begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+  // DMFT loop
+  while (iloop < Nloop && !converged) {
+    //  Call ED Solver
+    solve_site(Bath.data(),bath_dim,1,1);      
+    // Retrieve  Self-energy on Matsubara axis
+    get_sigma_site_n5(Smats.data(),//
+        0,0,wm.data(),Lmats,0);
+    //  Build a local Green's function:
+    for (int i=0;i<Lmats;++i) {
+      zeta= wm[i] + xmu - Smats[i];
+      Gmats[i] = complex<double>(0.0,0.0);
+      for (int j=0; j< Le; j++) {
+        Gmats[i]+=Dbands[j]/(zeta-Ebands[j]);
+      }
+    }
+    // Self-consistency
+    for (int i = 0; i < Lmats; ++i) {
+      Delta[i] = 0.25 * D * Gmats[i];
+    }
+    // Fit -> new bath
+    chi2_fitgf_single_normal_n5(Delta.data(),//
+        delta_dim,Bath.data(),bath_dim,1,0,1);
+    // Check convergence
+    converged = check_convergence(Delta,//
+        dmft_error, Nsuccess, Nloop, comm);  
+  }
+\end{lstlisting}
+\end{minipage}
+}
+\savestack{\listingB}{\box0}
+
+\begin{tabular}{c|c}\label{list2}
+  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
+\end{tabular}
 
 \paragraph{Results}
-In the following we present some results obtained for the model
-introduced above. Specifically we focus on the testbed case of the interaction
-driven Mott transition, descriving the progressive
-transformation of a partially-filled band metallic state into a correlated insulator.
-
-To illustrate this point, we report in panel (A) the evolution of
-the spectral function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of
-the interaction strenght $U$. Despite the {\it spiky} nature of the spectrum, due to the
-finite size (i.e. number of poles) of the discretized effective bath,
-it is possible to clearly distinguish the characteristic features of
-the Mott transition. At low energy, we observe the renormalization of the 
-quasi-particle peak at the Fermi level ($\omega=0$). Concomitantly the
-system shows the formation of incoherent  high-energy features which
-will then develop into Hubbard bands in the Mott insulating state for $U>U_\mathrm{c}$, with $U_\mathrm{c}\simeq 2.8D$.
+In the following, we present results for the interaction-driven Mott 
+transition in the Bethe lattice, which captures the gradual 
+transformation of a partially-filled metallic state into a correlated 
+insulator.
+To illustrate this, we report in panel (A) the evolution of the spectral 
+function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of the 
+interaction strength $U$. Despite the inherently {\it spiky} nature 
+of the spectrum, resulting from the finite number of poles in the 
+discretized effective bath, the characteristic features of the Mott 
+transition are clearly visible. At low energies, a renormalized 
+quasi-particle peak develops at the Fermi level ($\omega = 0$). 
+Simultaneously, the system exhibits the formation of incoherent 
+high-energy features, which eventually evolve into well-defined 
+Hubbard bands in the Mott insulating phase for $U > U_\mathrm{c}$, 
+with $U_\mathrm{c} \simeq 2.8D$.
 
@@
 The formation of a spectral gap separating the Hubbard bands in the 
-Mott insulator is supported by the divergence, at the Fermi level, of the imaginary part of
-the self-energy function. Causality imposes that the real-part of
-this quantity becomes large near the singularity making it impossible
-to satisfy the quasi-particles poles equations
-$\omega+\mu-h^0-\e-\Re{\Sigma}(\omega)=0$, i.e. preventing coherent
-quasi-particles excitations near the Fermi level. 
-In the panels (B) and (C) we discuss this point  showing the evolution
-of the self-energy functions $\Sigma$.
-Specifically, in panel (B) we report the self-energy ${\rm Im}\Sigma(i\omega)$
-on the Matsubara axis in the low energy regime. Increasing $U$
-we observe the progressive growth of this function until a
-diverging behavior is acheived crossing the critical interaction
-strenght $U>U_\mathrm{c}$.
-We recall that this behavior can be observed on the Matsubara axis
-because of the particle-hole symmetry of the problem which pins the
-$\Im{\Sigma}$ singularity at $\omega=0$.
-In panel (C), we report the corresponding behavior of the
-$\Re{\Sigma}(\omega)$ in small energy regime around the Fermi
-level. Augmenting the interaction strength $U$ leads to a sudden
-increase of this self-energy component until a discontinuous behavior
-is reached, associated to the divergence of the corresponding
-imaginary part.
+Mott insulating phase is associated with the divergence of the 
+imaginary part of the self-energy at the Fermi level. This divergence 
+reflects the complete localization of the electrons, effectively 
+suppressing coherent quasi-particle excitations. Specifically, 
+causality dictates that the real part of the self-energy must also 
+grow significantly near the singularity, making it impossible to 
+satisfy the quasi-particle pole equation
+$$
+\omega+\mu-h^0-\e-\Re{\Sigma}(\omega)=0,
+$$
+which governs the formation of coherent excitations near the Fermi 
+level.
 
-A quantitative description of the transition is obtained from the
-quasi-particle renormalization constant $Z$, which correlates with the degree of
-localization of the electrons being equal to 1 for a non-interacting
-metal and 0 for the Mott insulator. This quantity is obtained from the
-linear term in the Fermi liquid expansion of the self-energy as
-$Z=(1-\tfrac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow
-    0}})^{-1}$.
-Using the relation:
+Panels (B) and (C) illustrate this phenomenon by showing the evolution 
+of the self-energy $\Sigma$. In panel (B), we present the Matsubara 
+self-energy ${\rm Im}\Sigma(i\omega)$ in the low-energy regime. As the 
+interaction strength $U$ increases, this function progressively 
+grows, eventually diverging as the critical interaction threshold 
+$U > U_\mathrm{c}$ is crossed.
+This divergence along the Matsubara axis is directly linked to the
+particle-hole symmetry of the Bethe lattice, which pins the  ${\rm
+  Im}\Sigma$ singularity at $\omega = 0$.
+
+Panel (C) complements this picture by displaying the real part 
+$\Re{\Sigma}(\omega)$ in the same low-energy regime. Here, increasing 
+$U$ leads to a rapid rise of this component, culminating in a 
+discontinuous behavior as the critical point is approached. This 
+discontinuity directly reflects the divergence in the imaginary part
+on the real-axis,  confirming the transition to the Mott insulating state.
+
+A quantitative measure of this transition is provided by the 
+quasi-particle renormalization factor $Z$, which can be used to capture the degree 
+of electron delocalization. This parameter ranges from 1 for a 
+non-interacting metal to 0 for a fully localized Mott insulator. It is 
+defined through the low-energy expansion of the self-energy as
+$$
+Z=(1-\tfrac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow
+    0}})^{-1}.
+$$
+which can also be estimated from the linear behavior of ${\rm Im}\Sigma(i\omega)$ for 
+$\omega\to0$ in the metallic regime using the relation:
 $$
@@
 $$
-we can extract $Z$ also from the linear behavior of ${\rm Im}\Sigma(i\omega)$ for 
-$\omega\to0$ in the metallic regime.
 
-The linear fit highlighted in the panels (B)-(C) and the corresponding values of $Z$ are reported in the legend.
-In both cases we observe that increasing $U$ the slope of the linear behavior of the
-self-energy at low-energy increases upon increasing $U$, either on the
-Matsubara or real-axis. At the transition point the slope becomes
-infinite according to the divergence of the imaginary part of
-the self-energy  ${\rm Im}\Sigma(\omega) \rightarrow -\infty$,
-corresponding to $Z\to 0$.
+The linear fits highlighted in panels (B) and (C), along with the 
+corresponding $Z$ values provided in the legends, clearly indicate that 
+the slope of the self-energy at low energy increases with $U$ on both 
+the Matsubara and real axes. At the transition point, this slope 
+diverges, reflecting the onset of complete electron localization as 
+$Z \to 0$, consistent with the divergence 
+${\rm Im}\Sigma(\omega) \rightarrow -\infty$.
 
-\subsection{Attractive Hubbard model (Python API)}\label{SecExamplesAHM}
-The second application has the twofold aim to demonstrate the
-superconductivity support of the \NAME library as well as to
-illustrate the use of the Python API through a working example.
-We consider the simple, yet non-trivial, case of the attractive
-Hubbard model on a two-dimensional square lattice:
+\subsection{Attractive Hubbard model}\label{SecExamplesAHM}
+The second example we present concerns the DMFT description of the 
+attractive Hubbard model on a two-dimensional square lattice. This 
+example has a twofold aim: (i) to demonstrate the support of \NAME 
+for ($s$-wave) superconductivity, and (ii) to illustrate the use of 
+the library's Python API through a concrete working example. The 
+model Hamiltonian is given by:
+$$
+H = \sum_{\ka,\s} \epsilon(\ka) c^\dagger_{\ka\s} c_{\ka\s} 
+    - U \sum_i n_{i\up} n_{i\dw},
+$$
+where $U > 0$, $c^\dagger_{\ka\s} = \tfrac{1}{\sqrt{N}} 
+\sum_i e^{-i\ka \cdot R_i} c^\dagger_{i\s}$, and $c^\dagger_{i\s}$ 
+is the creation operator for an electron at site $i$ with spin $\s$. 
+The occupation operator is $n_{i\s} = c^\dagger_{i\s} c_{i\s}$, and 
+the energy dispersion relation is $\e(\ka)=-2t[\cos{(k_x a)}+
+\cos{(k_y a)}]$, where we set the lattice spacing 
+$a=1$  and the choose the energy unit such as $4t=D=1$ for convenience.
 
+The DMFT workflow for this case is largely similar to the previous 
+example, but it now operates in the Nambu basis defined by the spinor
 $$
-H = \sum_{\ka\s} \e(\ka)c^+_{\ka\s}c_{\ka\s} -U\sum_i n_{i\up}n_{i\dw}
+\psi_i=\begin{bmatrix} c_{i\up} \\ c^\dagger_{i\dw} \end{bmatrix}. 
 $$
-where $U>0$, $c^+_{\ka\s}=\tfrac{1}{\sqrt{N}}\sum_i e^{-i\ka\cdot R_i} c^+_{i\s}$
-and $c^+_{i\s}$ is the creation operator for an electron at site $i$
-and with spin $\s$, $n_{i\s}=c^+_{i\s}c_{i\s}$ is the occupation
-operator and $\e(\ka)=-2t[\cos{(k_x a)}+ \cos{(k_y a)}]$ is the
-energy dispersion relation. In the following we the lattice distance
-$a=1$  and the energy unit as $4t=D=1$.
-
-The DMFT workflow for this case is very similar to the previous one
-provided works in the Nambu basis defined by the spinor
-$\psi_i=[c_{i\up}, c^+_{i\dw}]^t$.
-In this basis any correlation functions, e.g. the Green's function, takes the matrix form:
+In this basis, the Green's function takes the matrix form:
 \begin{equation}
@@
 \end{equation}
-where the symbol $\hat{A}$ indicates the possible multi-orbital
-character which reduced to a scalar in the present case of a single
-orbital. The symbol $\hat{\bar{A}}$ indicates that the components in
-the second row are connect by particle-hole and time-reversal
-symmetries to the first row one. The specific relation depends on the
-symmetry of the order parameter (here $s$-wave) and the nature of the
-complex argument of the functions, i.e. Matsubara or real-axis:
+where the symbol $\hat{A}$ indicates the potential multi-orbital 
+nature of the system, which reduces to a scalar in the present 
+single-orbital case. The components in the second row, denoted 
+by $\hat{\bar{A}}$, are connected to the first row by particle-hole 
+and time-reversal symmetries. The specific relations depend on the 
+symmetry of the order parameter (here, $s$-wave) and whether the 
+functions are defined on the Matsubara or real-frequency axis:
 \begin{equation}
@@
 \end{equation}
-The code implementation closely follows the previous structure, with
-some notable exceptions related to the Nambu structure for which,
-using the symmetries above, we only need to deal with the first row
-independent components. In the first part of the code we initialize
-the lattice structure and the solver:
+
+The code implementation closely follows the structure of the previous 
+example, with some notable adjustments related to the Nambu basis. 
+Specifically, the above symmetries allow one to compute only the 
+independent components from the first row, significantly reducing 
+the computational effort. The initial part of the code handles the 
+lattice structure and solver initialization, as described below.
+
 \begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 import os,sys
-from aux_funx import * #include function to build $G_\mathrm{loc}$ and Weiss fields
-
+from aux_funx import * #include function to build $G_\mathrm{loc}$ 
 comm = MPI.COMM_WORLD
@@
 master = (rank==0)
-
 #Functions
@@
     return np.dot(gridout,[b1,b2])
-
 def h_square2d(k,t):
@@
 
+#Read input
 ed.read_input("inputAHM.conf")
 
+#Generate Hk and  set Hloc
 kgrid = generate_kgrid(Nk)
-
-#Generate hk and hloc
 Hk   = h_square2d(kgrid,t_hop)
@@
 Hloc = np.sum(Hk,axis=0)/Nk**2
-Hloc = Hloc.astype(complex)
-ed.set_hloc(Hloc)
+ed.set_hloc(Hloc.astype(complex))
 
-#SETUP SOLVER
+#Setup ED Solver
 Nb=ed.get_bath_dimension()
 bath = ed.init_solver()
-bath_prev = np.copy(bath)
 \end{lstlisting}
@@
 The iterative scheme for the solution of DMFT closely follows the
-sequence discussed in \secu{SecExamplesBetheDMFT}:   
-\begin{enumerate}
+sequence already discussed in \secu{SecExamplesBetheDMFT}:   
+\begin{itemize}
 \item Call the exact diagonalization {\bf impurity solver} {\tt
     ed.solve} providing the set of bath parameters $\vec{x}=\{V,h\}$  as input.
-\item Using the dedicated
-  input/output procedures {\tt ed.get\_sigma} we retrieve the self-energy functions  
+
+\item Use the dedicated
+  input/output \NAME procedures to retrieve the self-energy functions  
   $\hat{\Sigma}(i\omega)$ and $\hat{S}(i\omega)$ on the 
   Matsubara axis.
+
 \item
@@
 \end{equation}
-\item Update the normal and anomalous Weiss fields, respectively 
+
+\item Update the Weiss fields components, respectively 
   $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
@@
   {\mathbf \Sigma}(i\omega)$ in Nambu space.
+
 \item Optimize the bath parameters $\vec{x}$ to best describe the updated
-    Weiss fields using \NAME provided conjugate gradient  fit
-    procedure {\tt ed.chi2\_fitgf}.
-\end{enumerate}
-which is implemented in Python as follows:
+    Weiss fields, potentially using \NAME provided conjugate gradient  fit
+    procedures.
+  \end{itemize}
+%
+The corresponding implementation in Python reads:
 \begin{lstlisting}[style=mypython,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
     iloop=iloop+1
-
     #Solve impurity problem
     ed.solve(bath)    
-
     #Self-consistency with aux_funx procedures:
@@
     Weiss = dmft_weiss_field(Gmats,Smats)                            
-
     #Fit
     bath = ed.chi2_fitgf(Weiss[0],Weiss[1],bath)
-
     #Error check
     err,converged=ed.check_convergence(Weiss,ed.dmft_error)
-
 ed.finalize_solver()
@@
 \paragraph{Results}
-We showcase here some results for the DMFT solution of the attractive
-Hubbard model across the BCS to BEC regime, with the aim of
-illustrating the capabilities of \NAME to deal with $s$-wave
-superconductivity at zero and finite temperatures.
+Here we showcase some results for the DMFT solution of the 
+attractive Hubbard model across the BCS to BEC crossover regime, 
+illustrating the capability of \NAME to handle $s$-wave 
+superconductivity at both zero and finite temperatures.
 
-To beging with, we report in  panel (A) of \figu{figEx2} the
-evolution of the spectral density, obtained from the local normal
-Green's function $-\tfrac{1}{\pi}\Im{G}_\mathrm{loc}(\omega)$, as a function
-of the attraction $U$. For any finite value of  $U$ the Van Hove peak
-at $\omega=0$ of the 2D square lattice (see $U=0$
-solution) gets split by the formation of a superconductive gap of
-width which increases with $U$.
-The existence of a gap is associated to the formation of a finite
-order parameter $\phi=\langle c_\up c_\dw\rangle$. The behavior of
-this quantity, shown in panel (B), highlights crossover from the BCS
-regime at weak coupling to a BEC one for large $U$.
-The former regime is characterized by the well known exponential increase of
-$\phi$, which is computationally the hardest regime to adress. At
-strong coupling or BEC regime the order parameter saturates to its
-limiting value $\phi\to 1/2$. The comparison with mean-field result
-(gray) underlines the effect of local quantum fluctuations in slightly
-suppressing the order parameter. This effect is particularly active in
-the intermediate regime, as captured by the behavior of the so-called
+To begin, panel (A) of \figu{figEx2} shows the evolution of the 
+spectral density, obtained from the local normal Green's function as 
+$-\tfrac{1}{\pi}\Im G_\mathrm{loc}(\omega)$, as a function of the 
+attraction $U$. For any finite $U$, the Van Hove peak at 
+$\omega = 0$ characteristic of the 2D square lattice (visible at 
+$U = 0$) is split by the formation of a superconducting gap, whose 
+width increases with $U$. This gap reflects the emergence of a finite 
+order parameter $\phi = \langle c_\up c_\dw \rangle$, signaling the 
+onset of superconducting coherence.
+
+The evolution of this order parameter is presented in panel (B), 
+highlighting the crossover from the weak-coupling BCS regime to the 
+strong-coupling BEC regime. In the BCS limit, $\phi$ shows the 
+characteristic exponential growth with $U$, reflecting the formation 
+of weakly bound Cooper pairs. This regime is known to be 
+computationally challenging. In the opposite, strong-coupling, limit 
+$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$, 
+indicating tightly bound local pairs. Comparison with the mean-field result 
+(gray line) reveals the effect of local quantum fluctuations, which 
+slightly suppress the order parameter, particularly in the intermediate 
+regime.
+
+To quantify these correlation effects, we plot in panel (C) the 
 \emph{correlation strength}
 $\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
-reported in panel (C). Assuming a monotonic behavior of the anomalous
-self-energy function, this quantity estimates the ``strength'' of its
-dynamical fluctuations, comparing the mean-field-like behavior found
-at high energy scale, with the features at the Fermi level. 
-A large value of $\Theta$ indicates a more dynamical self-energy, hence
-a more correlated system.
-Our results show that both weak and strong coupling regime are
-relatively weakly correlated, i.e. very near a mean-field solution. On
-the contrary, the inter-mediate regime is characterized by a large
-correlation, making the solution very different from that obtained in
-BCS description.  
-To further corroborate the distance between the DMFT and the mean-field
-solutions, we report in panel (D) the evolution of the double occupancy
-$d=\langle n_\up n_\dw\rangle$. At half-filling the mean-field value is
-determined solely by the order parameter as $d=1/4 + \phi^2$.
-Our results show that the inclusion of dynamical fluctuations in DMFT
-slightly increase the value of $d$ in the weak coupling
-regime. However, increasing the attraction the double occupations
-quickly get reduced below the mean-field value up to the BEC regime.
+where $S(i\omega)$ is the anomalous self-energy.
+This ratio statically captures 
+the maximum amplitude of its dynamical dependence by comparing the high-energy 
+mean-field-like limit with the low-energy behavior at the Fermi level. 
+Large values of $\Theta$ indicate a strongly correlated state with 
+significant dynamical effects, hence a more correlated state.
+Our results show that both the weak 
+and strong coupling limits are relatively close to the mean-field 
+description, while the intermediate regime is marked by strong 
+correlations, significantly departing from the BCS picture.
 
-Finally, we illustrate the capability of \NAME in
-exploring finite temperature physics. In panel (E) we show the
-temperature evolution of the order parameter $\phi(T)$ across the
-superconductor-to-normal transition. The mean-field nature of this
-transition is underlined by the scaling of the solution near
-the critical point $\phi \simeq (T_\mathrm{c}-T)^\beta$ with $\beta=1/2$ as
-predicted by mean-field calculations.
+To further illustrate the impact of dynamical correlations, we 
+present in panel (D) the evolution of the double occupancy 
+$d = \langle n_\up n_\dw \rangle$ as a function of $U$. At half-filling, 
+the mean-field expression for this quantity is $d = 1/4 + \phi^2$, 
+reflecting the sole contribution of the order parameter. Our DMFT 
+results show a slight increase in $d$ over the mean-field prediction 
+in the weak coupling regime, indicating enhanced local correlations. 
+However, as $U$ increases, the double occupancy quickly drops below 
+the mean-field result, reflecting the onset of strong pairing and 
+pair localization in the BEC limit.
 
-\subsection{Multi-orbital Hubbard (TRIQS)}
+Finally, we demonstrate the ability of \NAME to capture finite 
+temperature effects. Panel (E) shows the temperature dependence of 
+the order parameter $\phi(T)$ across the superconducting-to-normal 
+transition. The mean-field nature of this transition is evident from 
+the scaling near the critical temperature 
+$\phi \sim (T_\mathrm{c} - T)^\beta$ with $\beta = 1/2$, consistent 
+with classical Ginzburg-Landau theory.
 
-\subsection{Some model (W2Dynamics)}
+These results collectively illustrate the versatility of \NAME in 
+handling both ground state and finite temperature superconducting 
+phases, capturing the complex physics of the BCS-BEC crossover with 
+high accuracy.
+
+\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction (TRIQS)}
+\label{SecExamplesTRIQS}
+
+The third example demonstrates how to use the edipack2triqs compatibility
+layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
+3-orbital correlated impurity coupled to a few non-interacting bath sites.
+The interaction term of the impurity Hamiltonian has the Hubbard-Kanamori
+form (\ref{Hint}).
+
+A Python script implementing a calculation that makes use of edipack2triqs
+generally begins with a few module imports.
+\lstinputlisting[style=mypython,
+                 numbers=none,
+                 basicstyle={\scriptsize\ttfamily},
+                 firstline=1, lastline=13]
+{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+
+One then proceeds to defining the system under consideration. In this case we
+consider an impurity atom with three correlated orbitals and two bath states
+per each impurity orbital. This information must be encoded in the fundamental
+set objects that are later used to construct the solver.
+\lstinputlisting[style=mypython,
+                 numbers=none,
+                 basicstyle={\scriptsize\ttfamily},
+                 firstline=15, lastline=26]
+{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+The next step is to define a TRIQS many-body operator expression that represents
+the Hamiltonian to be diagonalized.
+\lstinputlisting[style=mypython,
+                 numbers=none,
+                 basicstyle={\scriptsize\ttfamily},
+                 firstline=28, lastline=67]
+{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+Finally, one creates a solver object and performs the actual calculation by
+calling its method {\tt solve()}. This is normally the most time- and
+memory-consuming step.
+\lstinputlisting[style=mypython,
+                 numbers=none,
+                 basicstyle={\scriptsize\ttfamily},
+                 firstline=69, lastline=83]
+{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+The computation results are readily available as attributes of the solver
+object. The following code snippet shows how to access measured expectation
+values of the static observables, and how to employ the plotting framework of
+TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
+functions (Fig.~\ref{figEx3}).
+\lstinputlisting[style=mypython,
+                 mathescape=false,
+                 numbers=none,
+                 basicstyle={\scriptsize\ttfamily},
+                 firstline=85, lastline=112]
+{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+
+\begin{figure}[t!]
+    \includegraphics[width=0.5\linewidth]
+        {edipack2_examples/edipack2triqs/G_iw.pdf}
+    \includegraphics[width=0.5\linewidth]
+        {edipack2_examples/edipack2triqs/A_w.pdf}
+    \caption{\label{figEx3}%
+        Imaginary part of the Matsubara Green's function (left) and the
+        corresponding orbital-resolved spectral function (right) computed for a
+        three-orbital impurity model with an interaction of the Hubbard-Kanamori
+        type (\ref{Hint}). This illustration is produced by the edipack2triqs
+        example script presented in Sec.~\ref{SecExamplesTRIQS}.
+    }
+\end{figure}
+
+\subsection{Bethe lattice DMFT (w2dynamics)}\label{SecExamplesBetheDMFTw2d}
+Let us revisit the example of Sec.~\ref{SecExamplesBetheDMFT} to
+demonstrate usage of the w2dynamics interface how to perform such a
+calculation instead. Unlike when the Fortran API is used, none of the
+five steps of the iterative algorithm listed there are left to the
+user to implement themselves. Instead, in addition to possibly
+non-default values for \NAME input variables, the model specification
+must also be added to a w2dynamics parameter file and depending on the
+model, further input files might need to be provided. Further
+differences are that initialization is performed in w2dynamics by
+starting from a self-energy of zero or reading a self-energy value
+from an old file, which results in the initial Weiss field that the
+initial bath parameters are fitted to, and that automatic convergence
+checking is not currently available. Finally, using the same settings
+as for the Fortran example we arrive at the w2dynamics parameter file
+shown in the following listing.
+
+\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
+[General]
+DOS             = Bethe           # support for the Bethe lattice is built-in
+half-bandwidth  = 1               # list of half-bandwidths per orbital
+NAt             = 1               # number of impurities
+beta            = 1000            # inverse temperature, defines Matsubara grid spacing
+mu              = 1.0             # chemical potential set to achieve half-filling
+EPSN            = 0.0             # turns off filling-based chemical potential search
+DMFTsteps       = 100             # given no convergence checking, we might want fewer
+magnetism       = para            # symmetrize self-energies per spin
+FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
+fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
+readold         = 0               # iteration number to read initial self-energy from, 0 turns off
+mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
+mixing_strategy = linear          # linear mixing as in the Fortran example
+solver          = EDIPACK         # use EDIpack2 as impurity solver, not default CTHYB
+
+[Atoms]
+[[1]]                             # one subsection per impurity
+Nd              = 1               # number of orbitals
+Hamiltonian     = Kanamori        # create a Hubbard-Kanamori interaction Hamiltonian
+Udd             = 2.0             # equivalent to ULOC
+Vdd             = 1.0             # equivalent to UST, meaningless for 1 orbital
+Jdd             = 0.5             # equivalent to JH, JX and JP, also meaningless here
+
+[QMC]                             # Parameters for some grid sizes are part of this section
+Ntau            = 1024            # imaginary time grid size
+Niw             = 4096            # number of positive Matsubara frequencies
+
+[EDIPACK]                         # further non-default parameters, also taken from Fortran example
+NBATH           = 7               # number of bath sites
+ED_TWIN         = True            # use twin symmetry
+LFIT            = 2048            # number of Matsubara frequencies used for the bath fit
+LANC_NGFITER    = 500             # number of Lanczos iterations for Green's function
+CG_FTOL         = 1e-10           # conjugate-gradient tolerance
+CG_NITER        = 2048            # maximum number of conjugate-gradient iterations
+\end{lstlisting}
+
+With this parameter file, we can use the {\tt DMFT.py} script of
+w2dynamics to perform the execution and find the results in form of
+both a typical w2dynamics HDF5 output file whose name starts with {\tt
+  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
+name of the HDF5 output file that contain unavoidable or explicitly
+requested \NAME input and output files for each individual DMFT
+iteration. We can extract results from the HDF5 output file e.g. using
+the {\tt hgrep} script of w2dynamics. The following listing shows how
+to perform a calculation with 10 parallel MPI processes and print the
+impurity self-energy result of the last DMFT iteration to the terminal
+assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
+directory and w2dynamics installed to {\tt /opt/w2dynamics}.
+
+\begin{lstlisting}[style=mybash]
+mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
+python /opt/w2dynamics/hgrep latest siw-full -1
+\end{lstlisting}
 

### 2025-05-13 edipack2_examples/edipack2triqs/hubbard_kanamori.py
First draft of the edipack2triqs example subsection

@@ -1,0 +1,112 @@
+# Import common Python modules
+from itertools import product
+import numpy as np
+
+# Initialize the MPI library before creating the solver object
+from mpi4py import MPI
+
+# Import TRIQS many-body operator objects: annihilation, creation and
+# occupation number operators
+from triqs.operators import c, c_dag, n
+
+# Import the solver object
+from edipack2triqs.solver import EDIpackSolver
+
+spins = ['up', 'dn']    # Names of spin projections
+orbs = [0, 1, 2]        # List of impurity orbitals
+bath_sites = [0, 1]     # List of bath sites, each carrying 3 orbitals
+
+# Fundamental sets for impurity spin up/down degrees of freedom
+fops_imp_up = [('up', orb) for orb in orbs]
+fops_imp_dn = [('dn', orb) for orb in orbs]
+
+# Fundamental sets for bath spin up/down degrees of freedom
+# There are a total of 6 bath states for each spin projection
+fops_bath_up = [('B_up', i) for i in range(3 * 2)]
+fops_bath_dn = [('B_dn', i) for i in range(3 * 2)]
+
+# Non-interacting part of the impurity Hamiltonian
+h_loc = np.diag([-0.7, -0.5, -0.7])
+H = sum(h_loc[o1, o2] * c_dag(spin, o1) * c(spin, o2)
+for spin, o1, o2 in product(spins, orbs, orbs))
+
+# Interaction part
+U = 3.0     # Local intra-orbital interactions U
+Ust = 1.2   # Local inter-orbital interaction U'
+Jh = 0.2    # Hund's coupling
+Jx = 0.15   # Spin-exchange coupling constant
+Jp = 0.1    # Pair-hopping coupling constant
+
+H += U * sum(n('up', o) * n('dn', o) for o in orbs)
+H += Ust * sum(int(o1 != o2) * n('up', o1) * n('dn', o2)
+               for o1, o2 in product(orbs, orbs))
+
+H += (Ust - Jh) * sum(int(o1 < o2) * n(s, o1) * n(s, o2)
+                      for s, o1, o2 in product(spins, orbs, orbs))
+H -= Jx * sum(int(o1 != o2) * c_dag('up', o1) * c('dn', o1) * c_dag('dn', o2) * c('up', o2)
+              for o1, o2 in product(orbs, orbs))
+H += Jp * sum(int(o1 != o2) * c_dag('up', o1) * c_dag('dn', o1) * c('dn', o2) * c('up', o2)
[…]

### 2025-05-14 01_intro.tex
Updated text: * Revised Repulsive Hubbard * Revised Attractive Hubbard * Introduction draft * Conclusions draft
Converging...

@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Introduction and Motivation}\label{SecIntro}
+{\color{red} A tentative Introduction scheme}
 
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
+\paragraph{intro} Quantum impurity models play a central role in condensed matter
+physics, providing the theoretical foundation for understanding
+of strongly correlated electrons systems.
+These models describe a small
+number of interacting electronic degrees of freedom coupled to 
+a non-interacting bath.
+Notably, quantum impurity problems lie at the core of dynamical mean-field theory
+(DMFT). By  reducing the lattice many-body problem to a
+self-consistent quantum impurity problem,  retaining essential local
+correlations, the DMFT enabled a  successful effective description of the
+complex physics of correlated materials, including Mott insulators,
+heavy fermion compounds, and high-temperature superconductors.  
+However, solving the quantum impurity problems emerging in the DMFT context accurately and efficiently remains a
+critical challenge, particularly for multi-orbital systems, systems
+at low temperatures or endowed with lower symmetry.
 
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
+\paragraph{what is new, what is inside: modes, RDM, ineq}
+  In this work we introduced EDIpack2: a flexible, high-performance numerical library designed to
+address these challenges, providing an exact diagonalization solver
+for generic quantum impurity problems. 
+The library builds on the foundations of
+its predecessor featuring massively parallel Lanczos-based algorithms while including several significant
+improvements. EDIpack2 supports both zero and finite temperature
+calculations for different symmetries of the problem  
+within a unified framework, making it suitable for a wide
+range of physical phenomena, from spin-orbit coupling effect in
+quantum materials to multi-orbital superconductivity. It also provides direct
+access to well-approximated dynamical correlation functions across the
+entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and
+other response properties.
 
-* zero and low finite temperatures
+Additionally, EDIpack2 offers access to the Fock space of
+the impurity system and thus, for instance, the possibility to
+evaluate the impurity reduced density matrix
+(iRDM). This capability enables quantum information-inspired analyses,
+providing insights into the entanglement properties, subsystem purity,
+and quantum correlations of interacting electron systems. These
+features are increasingly recognized as essential for understanding
+the emergent behavior in correlated matter, including quantum
+criticality and superconductivity.
 
-* direct access to (well approximated) analytic dynamical functions
+This new version includes support for systems with inequivalent
+impurities, a critical feature for studying heterostructures,
+superlattices, and disordered systems, where the local environment
+varies significantly across different sites. This capability makes it
+possible to explore a wide range of inhomogeneous systems, including
+oxide interfaces or disordered systems, where
+translational symmetry is broken.
 
-* direct access to impurity Fock space quantities
+\paragraph{Interoperability}
+Interoperability is a core design principle of this version of 
+EDIpack. The library is implemented using modern Fortran constructs, with comprehensive
+C-bindings that enable integration with other programming
+languages. In particular, EDIpack2 includes native  C and C++
+interface layer which enable development of third-party
+extensions. A significant contribution is realized via the Python API, EDIpy2, which provides a
+high-level interface for defining and solving impurity problems. The
+Python bindings also enable integration with established scientific
+libraries, such as NumPy and SciPy, facilitating data analysis and
+rapid prototyping.
 
-bla bla bla
+The development of such Python API unlocked construction of direct interfaces to the TRIQS
+(Toolbox for Research on Interacting Quantum Systems)  as
+well as to the W2Dynamics software.
+This integration provides EDIpack2 users with access to the
+extensive data handling and analysis tools in the TRIQS ecosystem,
+while also allowing TRIQS and W2Dynamics users to benefit from the
+flexibility and performance of EDIpack2. This dual functionality
+extends the capabilities of these platforms, supporting
+reproducibility and cross-validation of numerical results, and sets a
+new standard for interoperability in quantum impurity solvers.
+
+\paragraph{closure}
+In this paper, we present the mathematical framework, implementation
+details, and key features of EDIpack2, along with several illustrative
+applications. We aim to demonstrate how this flexible,
+high-performance solver can be used to tackle a wide range of
+challenging impurity problems.
+
+\end{document}

### 2025-05-14 05_examples.tex
Updated text: * Revised Repulsive Hubbard * Revised Attractive Hubbard * Introduction draft * Conclusions draft
Converging...

@@
 
-\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction (TRIQS)}
-\label{SecExamplesTRIQS}
+\subsection{Multi-orbital Hubbard (TRIQS)}
 
-The third example demonstrates how to use the edipack2triqs compatibility
-layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
-3-orbital correlated impurity coupled to a few non-interacting bath sites.
-The interaction term of the impurity Hamiltonian has the Hubbard-Kanamori
-form (\ref{Hint}).
-
-A Python script implementing a calculation that makes use of edipack2triqs
-generally begins with a few module imports.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=1, lastline=13]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-
-One then proceeds to defining the system under consideration. In this case we
-consider an impurity atom with three correlated orbitals and two bath states
-per each impurity orbital. This information must be encoded in the fundamental
-set objects that are later used to construct the solver.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=15, lastline=26]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-The next step is to define a TRIQS many-body operator expression that represents
-the Hamiltonian to be diagonalized.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=28, lastline=67]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-Finally, one creates a solver object and performs the actual calculation by
-calling its method {\tt solve()}. This is normally the most time- and
-memory-consuming step.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=69, lastline=83]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-The computation results are readily available as attributes of the solver
-object. The following code snippet shows how to access measured expectation
-values of the static observables, and how to employ the plotting framework of
-TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
-functions (Fig.~\ref{figEx3}).
-\lstinputlisting[style=mypython,
-                 mathescape=false,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=85, lastline=112]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-
-\begin{figure}[t!]
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/G_iw.pdf}
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/A_w.pdf}
-    \caption{\label{figEx3}%
-        Imaginary part of the Matsubara Green's function (left) and the
-        corresponding orbital-resolved spectral function (right) computed for a
-        three-orbital impurity model with an interaction of the Hubbard-Kanamori
-        type (\ref{Hint}). This illustration is produced by the edipack2triqs
-        example script presented in Sec.~\ref{SecExamplesTRIQS}.
-    }
-\end{figure}
-
-\subsection{Bethe lattice DMFT (w2dynamics)}\label{SecExamplesBetheDMFTw2d}
-Let us revisit the example of Sec.~\ref{SecExamplesBetheDMFT} to
-demonstrate usage of the w2dynamics interface how to perform such a
-calculation instead. Unlike when the Fortran API is used, none of the
-five steps of the iterative algorithm listed there are left to the
-user to implement themselves. Instead, in addition to possibly
-non-default values for \NAME input variables, the model specification
-must also be added to a w2dynamics parameter file and depending on the
-model, further input files might need to be provided. Further
-differences are that initialization is performed in w2dynamics by
-starting from a self-energy of zero or reading a self-energy value
-from an old file, which results in the initial Weiss field that the
-initial bath parameters are fitted to, and that automatic convergence
-checking is not currently available. Finally, using the same settings
-as for the Fortran example we arrive at the w2dynamics parameter file
-shown in the following listing.
-
-\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
-[General]
-DOS             = Bethe           # support for the Bethe lattice is built-in
-half-bandwidth  = 1               # list of half-bandwidths per orbital
-NAt             = 1               # number of impurities
-beta            = 1000            # inverse temperature, defines Matsubara grid spacing
-mu              = 1.0             # chemical potential set to achieve half-filling
-EPSN            = 0.0             # turns off filling-based chemical potential search
-DMFTsteps       = 100             # given no convergence checking, we might want fewer
-magnetism       = para            # symmetrize self-energies per spin
-FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
-fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
-readold         = 0               # iteration number to read initial self-energy from, 0 turns off
-mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
-mixing_strategy = linear          # linear mixing as in the Fortran example
-solver          = EDIPACK         # use EDIpack2 as impurity solver, not default CTHYB
-
-[Atoms]
-[[1]]                             # one subsection per impurity
-Nd              = 1               # number of orbitals
-Hamiltonian     = Kanamori        # create a Hubbard-Kanamori interaction Hamiltonian
-Udd             = 2.0             # equivalent to ULOC
-Vdd             = 1.0             # equivalent to UST, meaningless for 1 orbital
-Jdd             = 0.5             # equivalent to JH, JX and JP, also meaningless here
-
-[QMC]                             # Parameters for some grid sizes are part of this section
-Ntau            = 1024            # imaginary time grid size
-Niw             = 4096            # number of positive Matsubara frequencies
-
-[EDIPACK]                         # further non-default parameters, also taken from Fortran example
-NBATH           = 7               # number of bath sites
-ED_TWIN         = True            # use twin symmetry
-LFIT            = 2048            # number of Matsubara frequencies used for the bath fit
-LANC_NGFITER    = 500             # number of Lanczos iterations for Green's function
-CG_FTOL         = 1e-10           # conjugate-gradient tolerance
-CG_NITER        = 2048            # maximum number of conjugate-gradient iterations
-\end{lstlisting}
-
-With this parameter file, we can use the {\tt DMFT.py} script of
-w2dynamics to perform the execution and find the results in form of
-both a typical w2dynamics HDF5 output file whose name starts with {\tt
-  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
-name of the HDF5 output file that contain unavoidable or explicitly
-requested \NAME input and output files for each individual DMFT
-iteration. We can extract results from the HDF5 output file e.g. using
-the {\tt hgrep} script of w2dynamics. The following listing shows how
-to perform a calculation with 10 parallel MPI processes and print the
-impurity self-energy result of the last DMFT iteration to the terminal
-assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
-directory and w2dynamics installed to {\tt /opt/w2dynamics}.
-
-\begin{lstlisting}[style=mybash]
-mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
-python /opt/w2dynamics/hgrep latest siw-full -1
-\end{lstlisting}
+\subsection{Some model (W2Dynamics)}
 

### 2025-05-14 edipack2.tex
Updated text in 03_edipack2 till 1.7 Lanczos Diagonalization.
Updates from Overleaf
Finish polishing 03_edipack text Quick review of 02_install.
Updated text: * Revised Repulsive Hubbard * Revised Attractive Hubbard * Introduction draft * Conclusions draft
Converging...

@@
 \newcommand{\fixme}[1]{{\color{BrickRed} #1}}
-\usepackage{xspace}
 
@@
 
-\definecolor{mymauve}{rgb}{0.58, 0, 0.82}
 \lstdefinestyle{mybash}{
@@
   keywordstyle=\bfseries,
-  % It would be nice to have 'conda' here,
-  % but then 'conda-forge' gets highlighted too.
-  morekeywords={*,git,mkdir,cmake,make,pip},
+  morekeywords={*,git,mkdir,cmake,make},
   mathescape,
@@
 \def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2}\xspace}
+\def\NAME{{\rm EDIpack2 }}
 
@@
 
-(for the arXiv version only... ?)
-
-Lei ha clacsonato?
-
-Tu ha clacsonato?
-
-Tarapia tapioco, prematurata l'interfaccia, o scherziamo?
-Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico basato su C++ e utilizzante la toolchain di LLVM anche per Linux e Mac Os soltanto in due, oppure in quattro anche scribai con il file sorgente {\tt hm\_bethe.mc}?
-
-Come {\tt https://github.com/lcrippa/prematurata\_la\_dmft} per esempio.
-No dico, mi porga il file {\tt bagaglio.cpp}.
-Le vede le funzioni?
-Lo vede che interfacciano gli array, non supportati da Monicelli, e prematurano anche?
-Ora io le direi, anche con il rispetto per l'autorità, anche solo le due parole come install Monicelli from {\tt https://github.com/esseks/monicelli.git} and run Make which compiles and links the main file {\tt hm\_bethe.mc}, per esempio.
-Basta così, mi seguano nel programma di test.
-No no, Attenzione: loop dmft completo supportato secondo la ref.
-\cite{EDIpack} abbia pazienza.
-Se no, plotta i dati, anche un pochino Green's function e Self-energy in prefettura.
-Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.
-
-Si farà finta di passar da bischeri.
-
 %% References with bibTeX database:

### 2025-05-14 edipack2_examples/AHM_EDIpack2EDIpy/data/script_figAHM.py

@@ -14,7 +14,7 @@ from scipy import optimize
 plt.rcParams["font.family"] = "Times"
 plt.rcParams['text.usetex'] = True
 plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
-plt.rcParams.update({'font.size': 24})
+plt.rcParams.update({'font.size': 30})
 plt.rcParams['figure.figsize'] = [35, 15]
 
 
@@ -119,7 +119,7 @@ x2=d2[:,0];y2=d2[:,1];y2=0.25+y2**2
 
 ax.set_xlim([0, 5])
 # ax.set_ylim([0, 0.5])
-ax.set_xlabel(r'$T$')
+ax.set_xlabel(r'$U$')
 ax.set_ylabel(r'$\langle n_\uparrow n_\downarrow \rangle$')
 ax.tick_params(length=6, width=2,direction='out')
 

### 2025-05-14 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_2d.f90

@@ -7,7 +7,7 @@ program ed_ahm_2d
   real(8),parameter                         :: D=1
   integer                                   :: iloop,i
   integer                                   :: Nb,Nso
-  logical                                   :: converged,get_sigma
+  logical                                   :: converged,get_sigma,get_dos
   !Bath:
   real(8),allocatable,dimension(:)          :: Bath,Bath_Prev
   !The local functions:
@@ -27,6 +27,7 @@ program ed_ahm_2d
   call parse_cmd_variable(finput,"FINPUT",default='inputAHM.conf')
   call parse_input_variable(wmixing,"wmixing",finput,default=0.5d0,comment="Mixing bath parameter")
   call parse_input_variable(get_sigma,"get_sigma",finput,default=.false.)
+  call parse_input_variable(get_dos,"get_dos",finput,default=.false.)
   !
   call ed_read_input(trim(finput))
 
@@ -82,10 +83,21 @@ program ed_ahm_2d
      stop
   end if
 
-  
+
+  if(get_dos)then
+     call ed_get_sigma(Sreal(1,:,:,:),axis='r',type='n')
+     call ed_get_sigma(Sreal(2,:,:,:),axis='r',type='a')
+     call get_gloc(Edos,Ddos,H0,Greal,Sreal,axis='r')
+     call write_gf(Greal(1,:,:,:),"Gloc",axis='real',iprint=1)
+     call write_gf(Greal(2,:,:,:),"Floc",axis='real',iprint=1)
+     stop 
+  endif
 
 
-  
+
+
+
+
   !> Get bath dimension and allocate user bath to this size
   Nb=ed_get_bath_dimension()
   allocate(Bath(Nb))

### 2025-05-14 04_cbinding.tex
some tweaks to Julia part

--- 2025-05-12 04_cbinding.tex
@@
 The EDIpack Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
-This is searched upon loading the module, with the following loading hierarchy:
+
+The library is searched upon loading the module, with the following order of priority:
 
@@
 
-in complete analogy to the Python API, the global variables and functions are contained in a  {\tt struct} called {\tt global\_env}, and can be called and assigned in the following way:
+in complete analogy to the Python API, the global variables and functions are contained in a  {\tt struct} called {\tt global\_env}.
 
-\begin{itemize}
-\item A variable symbol is retrieved from the library through {\tt Libdl.dlsym} and then read via {\tt unsafe\_load}
-\item Similarly, variable assignment is achieved through {\tt Libdl.dlsym} and  {\tt unsafe\_store}
-\item Functions are called via {\tt Libdl.dlsym} and  {\tt ccall}
-\end{itemize}
+Similarly to the C++ case, global variables are loaded as raw pointers.
+As a consequence, it is important that the dimensions of the array variables (such as {\tt ULOC}) and, in general, the size of the memory sector occupied by each variable are correcty accounted for.
+This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
+Functions are directly called from the library, making use of the {\tt  ccall} procedure.
+As previously stated, as a consequence of the C linking conventions multiple calls to {\tt  ccall} are necessary to account for the different input options of each interfaced Fortran procedure; the Julia wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.
 
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory shearing through multi-threading.
+At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
+If the library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
+The {\tt MPI\_COMM\_WORLD} communicator will need to be correctly initialized by the user as well, and the program will need to be run with {\tt  mpiexec/mpirun}.
+
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIjl2.0 repository.
+Documentation of the API and further examples are being developed.
 \end{document}

### 2025-05-14 04_cbinding.tex
Some more Julia tweaks

@@
 
-in complete analogy to the Python API, the global variables and functions are contained in a  {\tt struct} called {\tt global\_env}.
+in partial analogy to the Python API, the global variable, but not the functions, are contained in a  {\tt struct} called {\tt global\_env}.
 
@@
 This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
-Functions are directly called from the library, making use of the {\tt  ccall} procedure.
+Functions are directly called from the dynamic library, making use of the {\tt  ccall} procedure.
 As previously stated, as a consequence of the C linking conventions multiple calls to {\tt  ccall} are necessary to account for the different input options of each interfaced Fortran procedure; the Julia wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+
+\subsubsection{Installation as usage}
+
+At present, the EDIpack Julia interface is not offered as a package. The git repository has to be cloned via
+
+\begin{lstlisting}[style=mybash]
+git clone https://github.com/EDIpack/EDIjl2.0.git
+\end{lstlisting}
+
+and the location of the source files needs to be included in the user program via
+
+\begin{lstlisting}
+push!(LOAD_PATH, joinpath(@__DIR__, "PATH_TO_REPO/EDIjl2/src"))
+\end{lstlisting}
+
+The EDIjl2 module can then be loaded via
+
+\begin{lstlisting}
+using EDIjl2
+\end{lstlisting}
+
+The correct way to access global variables and functions is then as in the following example:
+
+\begin{lstlisting}
+EDIjl2.read_input("inputED.conf")
+ed = EDIjl2.global_env
+println("Nspin = ", ed.Nspin)
+ed.Nspin = 2
+\end{lstlisting}
+
 The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.

### 2025-05-14 04_cbinding.tex
Minimal tweak

@@
 
-\begin{lstlisting}
-push!(LOAD_PATH, joinpath(@__DIR__, "PATH_TO_REPO/EDIjl2/src"))
+\begin{lstlisting}[style=mybash]
+push!(LOAD_PATH, joinpath(@__DIR__, "PATH/TO/REPO/src"))
 \end{lstlisting}
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[style=mybash]
 using EDIjl2
@@
 
-\begin{lstlisting}
+\begin{lstlisting}[style=mybash]
 EDIjl2.read_input("inputED.conf")

### 2025-05-14 05_examples.tex
Minimal tweak

--- 2025-05-13 05_examples.tex
@@
 
-\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction (TRIQS)}
-\label{SecExamplesTRIQS}
-
-The third example demonstrates how to use the edipack2triqs compatibility
-layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
-3-orbital correlated impurity coupled to a few non-interacting bath sites.
-The interaction term of the impurity Hamiltonian has the Hubbard-Kanamori
-form (\ref{Hint}).
-
-A Python script implementing a calculation that makes use of edipack2triqs
-generally begins with a few module imports.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=1, lastline=13]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-
-One then proceeds to defining the system under consideration. In this case we
-consider an impurity atom with three correlated orbitals and two bath states
-per each impurity orbital. This information must be encoded in the fundamental
-set objects that are later used to construct the solver.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=15, lastline=26]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-The next step is to define a TRIQS many-body operator expression that represents
-the Hamiltonian to be diagonalized.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=28, lastline=67]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-Finally, one creates a solver object and performs the actual calculation by
-calling its method {\tt solve()}. This is normally the most time- and
-memory-consuming step.
-\lstinputlisting[style=mypython,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=69, lastline=83]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-The computation results are readily available as attributes of the solver
-object. The following code snippet shows how to access measured expectation
-values of the static observables, and how to employ the plotting framework of
-TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
-functions (Fig.~\ref{figEx3}).
-\lstinputlisting[style=mypython,
-                 mathescape=false,
-                 numbers=none,
-                 basicstyle={\scriptsize\ttfamily},
-                 firstline=85, lastline=112]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
-
-\begin{figure}[t!]
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/G_iw.pdf}
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/A_w.pdf}
-    \caption{\label{figEx3}%
-        Imaginary part of the Matsubara Green's function (left) and the
-        corresponding orbital-resolved spectral function (right) computed for a
-        three-orbital impurity model with an interaction of the Hubbard-Kanamori
-        type (\ref{Hint}). This illustration is produced by the edipack2triqs
-        example script presented in Sec.~\ref{SecExamplesTRIQS}.
-    }
-\end{figure}
+\subsection{Multi-orbital Hubbard (TRIQS)}
 

### 2025-05-14 04_cbinding.tex
Some more fixes

@@
 python implementations for the Bethe lattice example driver.
-Its structure and operation mimicks that of the EDIpy layer, with minimal language-specific differences.
+Its structure and operation mimicks that of the EDIpy2 layer, with minimal language-specific differences.
 
-The EDIpack Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
+The \NAME{} Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
 
@@
 \begin{itemize}
-\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl} will look there for the library first
+\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl2} will look there for the library first
 \item {\tt LD\_LIBRARY\_PATH}: for Linux systems
@@
 
-in partial analogy to the Python API, the global variable, but not the functions, are contained in a  {\tt struct} called {\tt global\_env}.
+\subsubsection{Structure}
 
-Similarly to the C++ case, global variables are loaded as raw pointers.
-As a consequence, it is important that the dimensions of the array variables (such as {\tt ULOC}) and, in general, the size of the memory sector occupied by each variable are correcty accounted for.
+In partial analogy to the Python API, the global variables, but not the functions, are contained in a  {\tt struct} called {\tt global\_env}.
+
+Similarly to the C++ case, global variables and functions are loaded as raw pointers.
+As a consequence, it is important that the dimensions of the array-like variables (such as {\tt ULOC}) and, in general, the amount of memory occupied by each variable are correcty accounted for.
 This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
-Functions are directly called from the dynamic library, making use of the {\tt  ccall} procedure.
-As previously stated, as a consequence of the C linking conventions multiple calls to {\tt  ccall} are necessary to account for the different input options of each interfaced Fortran procedure; the Julia wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+Functions are called from the dynamic library, making use of the {\tt  ccall} procedure.
+As previously stated, as a consequence of the C linking conventions multiple alternative version of the interfaced Fortran procedures are present, to account for the different input variable combinations; the EDIjl2 wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
 
-\subsubsection{Installation as usage}
+\subsubsection{Installation and usage}
 
@@
 
-The correct way to access global variables and functions is then as in the following example:
+The correct way to access global variables and functions is as in the following example:
 
@@
 
-Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory shearing through multi-threading.
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
 At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
-If the library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
+If the \NAME{} library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
 The {\tt MPI\_COMM\_WORLD} communicator will need to be correctly initialized by the user as well, and the program will need to be run with {\tt  mpiexec/mpirun}.
@@
 We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIjl2.0 repository.
+This script is intended to be run serially.
 Documentation of the API and further examples are being developed.

### 2025-05-14 edipack2.tex
Minimal tweak
Very relevant commit

@@
 
+(scherzo eh)
+
+Tarapia tapioco, prematurata l'interfaccia, o scherziamo?
+Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico basato su C++ e utilizzante la toolchain di LLVM anche per Linux e Mac Os soltanto in due, oppure in quattro anche scribai con il file sorgente {\tt hm\_bethe.mc}?
+
+Come {\tt https://github.com/lcrippa/prematurata\_la\_dmft} per esempio.
+No dico, mi porga il file {\tt bagaglio.cpp}.
+Le vede le funzioni?
+Lo vede che interfacciano gli array, non supportati da Monicelli, e prematurano anche?
+Ora io le direi, anche con il rispetto per l'autorità, anche solo le due parole come install Monicelli from {\tt https://github.com/esseks/monicelli.git} and run Make which compiles and links the main file {\tt hm\_bethe.mc}, per esempio.
+Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.
+
+Si farà finta di passar da bischeri.
+
 %% References with bibTeX database:

### 2025-05-16 05_examples.tex
Updates from Overleaf

--- 2025-05-13 05_examples.tex
@@
 
+\subsection{Holstein model on the Bethe lattice (Fortran)}
+
+One of the features introduced in \NAME is the possibility of treating local phonons in the superconductive case (i.e.
+\textbf{ed\_mode=superc} ).
+In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT.
+The phononic and electron-phonon part of the Holstein hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
+\begin{equation} \label{eqex:H_Holstein}
+    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i + b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2})\Big]
+\end{equation}
+
+This interaction in two limits takes two simpler forms, for $\omega_0 \rightarrow \infty$ with $g^2/\omega_0=\lambda$ constant, also known as anti-adiabatic limit, the interaction becomes a Hubbard attraction:
+\begin{equation}
+    H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
+\end{equation}
+
+Meanwhile in the opposite limit, $\omega_0 \rightarrow 0$ with $g^2/\omega_0=\lambda$ constant, also known as adiabatic limit, the phonons are condensed and the creation/annihilation operators can be considered as a scalar number to be determined self-consistently.
+In that case the interaction at equation \eqref{eqex:H_Holstein} for uniform solution vanishes and one recovers the non-interacting limit.
+
+THE FOLLOWING MAYBE IN THE E-PH SECTION
+
+The phonon's frequency is passed to the \NAME program via the variable W0\_PH to be read from the input file.
+The displacement field acting on the phonon is passed thorugh the variable A\_PH from the input file.
+The electron-phonon coupling matrix $g_{\alpha \beta}$ instead can be passed in two different ways.
+If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable G\_PH.
+For any general shape one can pass to the input file a GPHfile variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.
+If GPHfile=NONE the matrix $g_{\alpha \beta}$ is read from the variable G\_PH, else it is read from the GPHfile.
+
+In the following we show for a fixed value of $\lambda=2$ the adiabatic to anti-adiabatic crossover for the uniform solution of the Holstein problem.
+
+PLOT docc vs W0, superc and normal
+PLT delta vs w0, superc
+
 \end{document}

### 2025-05-16 edipack2.tex
More relevant content
Important stuff part 3
Important changes part 4
Updates from Overleaf

--- 2025-05-08 edipack2.tex
@@
 \def\NAME{{\rm EDIpack2}\xspace}
+\newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}
 
@@
 
-\section{Appendix A: Monicelli interface}
+\section[appA]{Appendix A: Monicelli interface
+\footnote{Monicelli is an esoteric programming language based on the LLVM toolchain.
+It is written in C++ and offers wrappers for the basic types and operations thereof.
+The syntax replicates a cultural italian phenomenon known as ``supercazzola", a rambling nonsensical discourse which gives the false impression of carrying an actual meaning.
+As an interoperability showcase we present a fully functioning DMFT code for the Bethe lattice written in Monicelli.
+It requires a minimal C++ interface to handle arrays, complex numbers and properly interfacing the EDIpack functions.
+}}
 
@@
 No no, Attenzione: loop dmft completo supportato secondo la ref.
-\cite{EDIpack} abbia pazienza.
+~\cite{Georges1996RMP} abbia pazienza.
 Se no, plotta i dati, anche un pochino Green's function e Self-energy in prefettura.

### 2025-05-18 edipack2.tex
Updated Appendix A. Keep the idea, made it feasible.
Quick STATUS:
* missing BHZ part (my fault).
* missing e-ph data part (Samuele is working on that)
* missing W2Dyn example results

--- 2025-05-14 edipack2.tex
@@
 \newcommand{\fixme}[1]{{\color{BrickRed} #1}}
+\usepackage{xspace}
 
@@
   keywordstyle=\bfseries,
-  morekeywords={*,git,mkdir,cmake,make},
+  % It would be nice to have 'conda' here,
+  % but then 'conda-forge' gets highlighted too.
+  morekeywords={*,git,mkdir,cmake,make,pip},
   mathescape,
@@
 \def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2 }}
+\def\NAME{{\rm EDIpack2}\xspace}
+\newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}
 
@@
 
-\section{Appendix A: Monicelli interface}
+\section{Appendix A: Monicelli interface}\label{appendixA}
+In order to further showcase the interoperability capabilities of
+\NAME provided by the C-bindings module, we describe a simple interface to {\tt Monicelli}, see
+\href{github.com/esseks/monicelli.git}{ttps://github.com/esseks/monicelli.git}.
+
+{\tt Monicelli} is an esoteric programming language based on the LLVM
+toolchain.
+It is written in C++ and offers wrappers for the basic
+types and operations thereof. The syntax replicates a cultural italian
+phenomenon known as ``supercazzola", a rambling nonsensical discourse
+which gives the false impression of carrying an actual meaning,
+introduced in the trilogy movies ``Amici Miei'', directed by Mario
+Monicelli (see
+\href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\_miei}).
+
+The {\tt Monicelli} language can be found at
+\href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
+and can be installed using CMake. The software depends on C++
+compiler with {\tt stdlib}, LLVM and in some cases {\tt libz} library. The installation gives access to the {\tt
+  Monicelli} compiler {\tt mcc}, which statically links LLVM. 
+Before entering into the details of the code implementation, to get 
+acquainted with the typical supercazzola construct we rephrase
+this same introduction along the lines of the first supercazzola, i.e.
+an epic dialogue between a traffic policeman (V), count Mascetti
+(M) and G.Perozzi (P) (see
+\href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
+and \href{https://www.youtube.com/watch?v=SF8YUFdP6eU}{Movie Scene}).
+
+\noindent
+V: Lei ha clacsonato?\\
+P: Tu ha clacsonato?\\
+M: Tarapia tapioco, prematurata l'interfaccia, o scherziamo?\\
+V: Prego?\\
+M: Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
+basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
+Unix soltanto in due, oppure in quattro anche scribai con il file
+sorgente {\tt hm\_bethe.mc}?  Come {\tt
+  https://github.com/lcrippa/prematurata\_la\_dmft}, per esempio?\\
+V: Ma che DMFT, mi faccia il piacere! Questi signori stavano
+programmano loro, non si intrometta!\\
+M: Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
+funzioni? Lo vede che interfacciano gli array, non supportati da
+Monicelli, e prematurano anche! 
+Ora io le direi, anche con il rispetto per l'autorità, anche solo le
+due parole come install {\tt Monicelli} from
+\href{github.com/esseks/monicelli.git}{https://github.com/esseks/monicelli.git}
+e compila il file {\tt hm\_bethe.mc}, per esempio.\\
+V: Basta così! Mi seguano nel programma di test!\\
+P: No, no, no, attenzione! Il loop dmft completo \`e supportato
+secondo la Ref.~\cite{Georges1996RMP}, abbia pazienza,
+senn\`o.... Plotta i dati, anche un pochino di Green's function e
+Self-energy in prefettura.
+Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.\\
+V: Ho bello che capito. Si farà finta di passar da bischeri!\\
+
+We shall now present a fully functioning DMFT code for
+the solution of the Bethe lattice written in Monicelli. It requires a minimal C++
+interface to handle arrays, complex numbers and properly interfacing
+the EDIpack functions.
+The first part of the DMFT code load all the required functions from
+{\tt bagaglio.cpp}, in particular it loads the interface to the \NAME
+solver functions {\tt ed\_init\_solver} and {\tt ed\_solve}:
+
+\begin{lstlisting}[style=cstyle]
+bituma le funzioni ausiliarie che vengono dal bagaglio
+...
+blinda la supercazzola leggi o scherziamo?
+blinda la supercazzola iniziailsolver o scherziamo?
+blinda la supercazzola risolvi o scherziamo?
+blinda la supercazzola prendilasigma o scherziamo?
+blinda la supercazzola prendilbagno con l`elemento Necchi, il valore Sassaroli o scherziamo?
+...
+\end{lstlisting}
+
+After a long initialization, we follow the structure already presented
+in \secu{SecExamplesBetheDMFT} for the Fortran implementation.
+The DMFT code starts with the opening {\tt Lei ha clacsonato} (see
+above). Next, we read the input file and set the dimensions of some
+array describing the bath, the self-energy and Green's
+functions. We start a DMFT iteration loop using the command {\tt
+  stuzzica}, which includes an internal frequency loop as {\tt
+  Monicelli} does not support array algebra.
+The loop contains a call to the \NAME solver function, then proceeds
+by retrieving the self-energy function which is used to obtain the
+local Green's function. These enters the self-consistency equation
+which update the Weiss field. Finally bath optimization is performed
+and if error condition is met the loop exit.
+The main step of the implementation reads:
+
+\begin{lstlisting}[style=cstyle]
+Lei ha clacsonato
+#Read the input file
+    prematurata la supercazzola dimmilfile o scherziamo?
+    prematurata la supercazzola leggi o scherziamo? 
+...                                                  
+#Init the ED solver:
+    voglio il sapone, Necchi come se fosse
+               prematurata la supercazzola ilbagnoepronto o scherziamo?
+    prematurata la supercazzola lavati con il sapone o scherziamo?
+
+    prematurata la supercazzola prendilah o scherziamo?
+    prematurata la supercazzola iniziailsolver o scherziamo?
+...
+#DMFT loop:
+stuzzica    
+      prematurata la supercazzola risolvi o scherziamo?
+
+      prematurata la supercazzola prendilag o scherziamo?
+      prematurata la supercazzola prendilasigma o scherziamo?
+#Get $G_{loc}$ and update $\GG^{-1}$: frequency loop
+      stuzzica                   
+          il contatoredue come fosse 0
+          prematurata la supercazzola prendi con 108, contatore, 0.0, 0.0, 0 o scherziamo?
+...
+      e brematura anche, se il contatore minore di frequenze
+...      
+      prematurata la supercazzola lavatiancora o scherziamo?
+#Fit the bath:       
+      prematurata la supercazzola spiaccica o scherziamo?
+#Mix the bath           
+      prematurata la supercazzola failmischiotto con il sapone, il frullatore o scherziamo?
+#Check error      
+      la fine come se fosse prematurata la supercazzola cisiamo o scherziamo?         
+ e brematura anche, se la fine minore di 1
+\end{lstlisting}
+
+\paragraph{Usage}.
+The source code can be retrieved from
+\href{https://github.com/lcrippa/prematurata_la_dmft}{github.com/lcrippa/prematurata\_la\_dmft}. 
+The {\tt src} directory contains several files, including the source
+code {\tt hm\_bethe.mc} implementing the DMFT algorithm, an auxiliary file {\tt bagaglio.cpp} which
+contains a number of functions implementing complex algebra, array
+costruction and interfacing the \NAME procedures. The directory also
+contains an example of input file and a converged bath parametrization
+for the Bethe lattice solution at $U=2$.
+
+The code is compiled using standard Make invocation in the source
+directory:
+\begin{lstlisting}[style=mybash]
+git clone https://github.com/lcrippa/prematurata_la_dmft
+cd prematurata_la_dmft/src
+make
+\end{lstlisting}
+A simple run using provided input file {\tt inputED.conf} will
+re-converge the solution within few loops.
 

### 2025-05-18 05_examples.tex

@@
 In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT.
-The phononic and electron-phonon part of the Holstein hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
+The phononic and electron-phonon part of the Holstein Hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
 \begin{equation} \label{eqex:H_Holstein}

### 2025-05-18 edipack2.tex
Updates from Overleaf

@@
   Monicelli} compiler {\tt mcc}, which statically links LLVM. 
-Before entering into the details of the code implementation, to get 
-acquainted with the typical supercazzola construct we rephrase
-this same introduction along the lines of the first supercazzola, i.e.
-an epic dialogue between a traffic policeman (V), count Mascetti
-(M) and G.Perozzi (P) (see
+We believe the discourse flow of this language is best captured by 
+illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G.Perozzi (P) (see
 \href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
@@
 senn\`o.... Plotta i dati, anche un pochino di Green's function e
-Self-energy in prefettura.
-Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.\\
+Self-energy in prefettura.\\
+M: Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.\\
 V: Ho bello che capito. Si farà finta di passar da bischeri!\\

### 2025-05-20 edipack2_examples/BHZ/ed_exct_bhz_2d.f90
Intermediate commit. Adding BHZ nonSU2

@@ -4,7 +4,7 @@ program ed_bhz
   USE DMFT_TOOLS
   USE MPI
   implicit none
-  
+
   integer                                 :: iloop,Lk,Nso
   logical                                 :: converged
   !Bath:
@@ -56,7 +56,7 @@ program ed_bhz
   call add_ctrl_var(Norb,"norb")
   call add_ctrl_var(Nspin,"nspin")
   call add_ctrl_var(beta,"beta")
- call add_ctrl_var(xmu,"xmu")
+  call add_ctrl_var(xmu,"xmu")
   call add_ctrl_var(wini,'wini')
   call add_ctrl_var(wfin,'wfin')
   call add_ctrl_var(eps,"eps")
@@ -166,7 +166,7 @@ program ed_bhz
   call finalize_MPI()
 
 
-  
+
 
 contains
 

### 2025-05-20 05_examples.tex
Intermediate commit. Adding BHZ nonSU2

@@
 
+\subsubsection{W2Dynamics solution}\label{SecExamplesBetheDMFTw2d}
+To demonstrate use of the w2dynamics interface, here we briefly
+discuss how to solve the DMFT problem for the Bethe lattice using
+W2Dynamics interface. \fixme{For definitiness we compare the finite low
+temperature results obtained via the two solvers: ED and CTQMC.  }
+
+Unlike when the Fortran API is used, none of the
+five steps of the iterative algorithm listed there are left to the
+user to implement themselves. Instead, in addition to possibly
+non-default values for \NAME input variables, the model specification
+must also be added to a w2dynamics parameter file and depending on the
+model, further input files might need to be provided. Further
+differences are that initialization is performed in w2dynamics by
+starting from a self-energy of zero or reading a self-energy value
+from an old file, which results in the initial Weiss field that the
+initial bath parameters are fitted to, and that automatic convergence
+checking is not currently available. Finally, using the same settings
+as for the Fortran example we arrive at the w2dynamics parameter file
+shown in the following listing.
+
+\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
+[General]
+DOS             = Bethe           # support for the Bethe lattice is built-in
+half-bandwidth  = 1               # list of half-bandwidths per orbital
+NAt             = 1               # number of impurities
+beta            = 1000            # inverse temperature, defines Matsubara grid spacing
+mu              = 1.0             # chemical potential set to achieve half-filling
+EPSN            = 0.0             # turns off filling-based chemical potential search
+DMFTsteps       = 100             # given no convergence checking, we might want fewer
+magnetism       = para            # symmetrize self-energies per spin
+FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
+fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
+readold         = 0               # iteration number to read initial self-energy from, 0 turns off
+mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
+mixing_strategy = linear          # linear mixing as in the Fortran example
+solver          = EDIPACK         # use EDIpack2 as impurity solver, not default CTHYB
+
+[Atoms]
+[[1]]                             # one subsection per impurity
+Nd              = 1               # number of orbitals
+Hamiltonian     = Kanamori        # create a Hubbard-Kanamori interaction Hamiltonian
+Udd             = 2.0             # equivalent to ULOC
+Vdd             = 1.0             # equivalent to UST, meaningless for 1 orbital
+Jdd             = 0.5             # equivalent to JH, JX and JP, also meaningless here
+
+[QMC]                             # Parameters for some grid sizes are part of this section
+Ntau            = 1024            # imaginary time grid size
+Niw             = 4096            # number of positive Matsubara frequencies
+
+[EDIPACK]                         # further non-default parameters, also taken from Fortran example
+NBATH           = 7               # number of bath sites
+ED_TWIN         = True            # use twin symmetry
+LFIT            = 2048            # number of Matsubara frequencies used for the bath fit
+LANC_NGFITER    = 500             # number of Lanczos iterations for Green's function
+CG_FTOL         = 1e-10           # conjugate-gradient tolerance
+CG_NITER        = 2048            # maximum number of conjugate-gradient iterations
+\end{lstlisting}
+
+With this parameter file, we can use the {\tt DMFT.py} script of
+w2dynamics to perform the execution and find the results in form of
+both a typical w2dynamics HDF5 output file whose name starts with {\tt
+  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
+name of the HDF5 output file that contain unavoidable or explicitly
+requested \NAME input and output files for each individual DMFT
+iteration. We can extract results from the HDF5 output file e.g. using
+the {\tt hgrep} script of w2dynamics. The following listing shows how
+to perform a calculation with 10 parallel MPI processes and print the
+impurity self-energy result of the last DMFT iteration to the terminal
+assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
+directory and w2dynamics installed to {\tt /opt/w2dynamics}.
+
+\begin{lstlisting}[style=mybash]
+mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
+python /opt/w2dynamics/hgrep latest siw-full -1
+\end{lstlisting}
+
 \subsection{Attractive Hubbard model}\label{SecExamplesAHM}
@@
 
-\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction (TRIQS)}
+\begin{figure}[t!]
+    \includegraphics[width=0.5\linewidth]
+        {edipack2_examples/edipack2triqs/G_iw.pdf}
+    \includegraphics[width=0.5\linewidth]
+        {edipack2_examples/edipack2triqs/A_w.pdf}
+    \caption{\label{figEx3}%
+        Imaginary part of the Matsubara Green's function (left) and the
+        corresponding orbital-resolved spectral function (right) computed for a
+        three-orbital impurity model with an interaction of the Hubbard-Kanamori
+        type (\ref{Hint}). This illustration is produced by the edipack2triqs
+        example script presented in Sec.~\ref{SecExamplesTRIQS}.
+    }
+\end{figure}
+
+\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction}
 \label{SecExamplesTRIQS}
@@
 form (\ref{Hint}).
+
+\fixme{Add Hamiltonian?}
+\fixme{}
 
@@
 
+\subsection{Interacting Bernevig-Hughes-Zhang model}
+In this section we focus on the DMFT solution of the interacting
+Bernevig-Hughes-Zhang (BHZ).
+As shown in Ref.~\onlinecite{AmaricciPRB2022}, at moderate
+interactions this model admits an excitonic phase in which opposite
+orbitals electrons and holes across the band gap bound into a coherent phase.
+
+We consider a system of two-orbital electrons on a square
+lattice interacting through a Hubbard-Kanamori term and describing
+a quantum spin Hall insulator.
+We consider a suitable matrix basis in terms of the Dirac
+matrices $\Gamma_{a\a}=\sigma_a\otimes \tau_\a$, where $\sigma_a$ and
+$\tau_\a$ are Pauli matrices, respectively, in the spin and orbital
+pseudo-spin space. The  model Hamiltonian reads
+$$
+H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int}
+$$
+where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
+c_{1\downarrow k}, c_{2\downarrow k} ]$ is the spinor collecting
+annihilation operator $c_{a\sigma k}$ destructing an electrons at
+orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
+$k$. The non-interacting part of the Hamiltonian is:
+$$
+H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
+   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02}
+$$
+where $M$ is the mass term, which plays the role of a crystal
+field splitting among the orbitals. The presence of this term breaks
+the symmetry in the orbital pseudo-spin channel.
+The  interaction reads: 
+$$
+   H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
+   \hat{S_z}^2 - 2 \hat{T_z}^2\right)
+ $$
+ where $\hat{N}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{00}\psi_i$ is the
+total density operator,
+$\hat{S_z}=\tfrac{1}{2}\psi_i^\dagger \Gamma_{30}\psi_i$ is the total
+spin polarization operator and $\hat{T_z}=\tfrac{1}{2}\psi_i^\dagger
+\Gamma_{03}\psi_i$ is the orbital pseudo-spin polarization operator.
+This form corresponds to the density-density part of the
+Kanamori interaction. We neglect the pair-hopping and spin-flip purely
+for numerical reasons.
+
+In the non-interacting regime, i.e. $U=J=0$ this model describes a
+quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
+Insulator (BI) for $M>4t$.
+The transition point at $M=4t$ describes the formation of a gapless
+Dirac state with linear band crossing at $k=[0,0]$.
+
+The code implementation follows the same guidelines discusses above
+for the other examples. There are two specific modifications requied
+to the  user. The first is to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone in
+order to obtain both the local non-intearcing Hamiltonian
+$H_{loc}=\tfrac{1}{N_k}\sum_k H(k)$ and get the local interacting
+Green's function
+$$
+G_{loc}(z) = \tfrac{1}{N_k}\sum_k \left[z+\mu-H(k)-\Sigma(z) \right]^{-1}
+$$
+where $\z\in\CCC$, $\Sigma(z)$ is the self-energy function obtained from the DMFT
+solution of the problem and $N_k$ is the number of $k$-points. 
+The second is to  construct the ``renormalized'' topological
+Hamiltonian
+$$
+H_{top} = \sqrt{Z}[H(k) + \Re\Sigma(\omega\to0)]\sqrt{Z}, 
+$$
+where $Z$ is the renormalization constant. $H_{top}$ describes the
+low-energy properties of many-body problem and can be used to obtain a 
+topological characterization of the interacting system.
+
+\subsubsection{Results}
+To capture the possible symmetry breaking in any excitonic channel
+driven by the local interaction, we consider the vector order
+parameter
+$\vec{E}=[E_0,E_x,E_y,E_z]$ where $E_a=\langle\psi^\dagger
+\Gamma_{a1}\psi \rangle$.
+The first component $E_0$ describes the singlet excitonic state,
+whereas the remaing ones correspond to the triplet states with
+different spin orientation.   
+The analysis of the strong-coupling regime as well as impurity
+excitonic susceptibility available in \NAME suggest the possible
+instability to an in-plane spin-triplet exciton phase, i.e. with $E_x$
+and/or $E_y$ different from zero.
+Interestingly, this state breakes several symmetries including
+time-reversal and spin SU(2) which protect the topological state.
+
+Thus, here we illustrate the DMFT solution of the excitonic phase as a way to
+illustrate the ability of \NAME to capture matter phases with broken
+spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
+  bath\_type=replica}.
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+   !> Set $H_{loc}$ in \NAME
+   allocate(Hloc(Nso,Nso))
+   Hloc = sum(Hk,dim=3)/Lk
+   where(abs(dreal(Hloc))<1d-6)Hloc=zero
+   call ed_set_hloc(Hloc)
+   !> Setup the replica bath basis using  $M$, $E_0$, $E_z$ and $E_x$ as symmetries
+   allocate(lambdasym_vector(Nbath,4))
+   allocate(Hsym_basis(Nso,Nso,4))
+   Hsym_basis(:,:,1)=Gamma03  ;lambdasym_vector(:,1)= Mh
+   Hsym_basis(:,:,2)=Gamma01 ;lambdasym_vector(:,2)= sb_field
+   Hsym_basis(:,:,3)=Gamma31 ;lambdasym_vector(:,3)= sb_field
+   Hsym_basis(:,:,4)=Gamma11 ;lambdasym_vector(:,4)=-sb_field
+   !> Set the replica bath
+   call ed_set_Hreplica(Hsym_basis,lambdasym_vector)
+   !> Get bath dimension and allocate user bath to this size
+   Nb=ed_get_bath_dimension(4)   !There are 4 symmetries
+   allocate(Bath(Nb))
+   !
+   !> Initialize the ED solver (bath is guessed or read from file) 
+   call ed_init_solver(bath)
+\end{lstlisting}
+
+In the following we consider the case of $M=1$ which corresponds to a
+QSHI in the non-interacting limit and $J/U=0.25$. 
+%
+The main effect of the interaction is enclosed in the renormalized
+mass term $M_{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
+real-part of the self-energy being proportional to $\Gamma_{03}$
+corrects the mass term with respect to its bare value. To leading
+order this correction is given proportional to $\tfrac{U-5J}{4}\langle
+\hat{T}_z\rangle$. So, for our choice of parameters, the effect of
+interaction would be to reduce the (effective) mass term and thus
+reducing the topological band gap. In the strong-coupling limit the
+two orbitals get populated with one electron per site, reaching the
+conditions for the formation of a Mott insulating state.
+In between, at inter-mediate coupling, we observe the formation of a
+region of exciton condensation.
+In panel (A) of \figu{figEx4} we report the evolution of the order
+parameter
+
 \begin{figure}[t!]
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/G_iw.pdf}
-    \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/A_w.pdf}
-    \caption{\label{figEx3}%
-        Imaginary part of the Matsubara Green's function (left) and the
-        corresponding orbital-resolved spectral function (right) computed for a
-        three-orbital impurity model with an interaction of the Hubbard-Kanamori
-        type (\ref{Hint}). This illustration is produced by the edipack2triqs
-        example script presented in Sec.~\ref{SecExamplesTRIQS}.
+  \includegraphics[width=\linewidth]{figures/figBHZ.pdf}
+    \caption{\label{figEx4}%
+      \textbf{Topological and Exciton Transition.}
+      (a)
     }
 \end{figure}
-
-\subsection{Bethe lattice DMFT (w2dynamics)}\label{SecExamplesBetheDMFTw2d}
-Let us revisit the example of Sec.~\ref{SecExamplesBetheDMFT} to
-demonstrate usage of the w2dynamics interface how to perform such a
-calculation instead. Unlike when the Fortran API is used, none of the
-five steps of the iterative algorithm listed there are left to the
-user to implement themselves. Instead, in addition to possibly
-non-default values for \NAME input variables, the model specification
-must also be added to a w2dynamics parameter file and depending on the
-model, further input files might need to be provided. Further
-differences are that initialization is performed in w2dynamics by
-starting from a self-energy of zero or reading a self-energy value
-from an old file, which results in the initial Weiss field that the
-initial bath parameters are fitted to, and that automatic convergence
-checking is not currently available. Finally, using the same settings
-as for the Fortran example we arrive at the w2dynamics parameter file
-shown in the following listing.
-
-\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
-[General]
-DOS             = Bethe           # support for the Bethe lattice is built-in
-half-bandwidth  = 1               # list of half-bandwidths per orbital
-NAt             = 1               # number of impurities
-beta            = 1000            # inverse temperature, defines Matsubara grid spacing
-mu              = 1.0             # chemical potential set to achieve half-filling
-EPSN            = 0.0             # turns off filling-based chemical potential search
-DMFTsteps       = 100             # given no convergence checking, we might want fewer
-magnetism       = para            # symmetrize self-energies per spin
-FileNamePrefix  = bethe_dmft_U2   # prefix for the output file name
-fileold         = bethe_dmft*hdf5 # file to read an initial self-energy from
-readold         = 0               # iteration number to read initial self-energy from, 0 turns off
-mixing          = 0.5             # mixing, but mixes self-energies and not Weiss fields
-mixing_strategy = linear          # linear mixing as in the Fortran example
-solver          = EDIPACK         # use EDIpack2 as impurity solver, not default CTHYB
-
-[Atoms]
-[[1]]                             # one subsection per impurity
-Nd              = 1               # number of orbitals
-Hamiltonian     = Kanamori        # create a Hubbard-Kanamori interaction Hamiltonian
-Udd             = 2.0             # equivalent to ULOC
-Vdd             = 1.0             # equivalent to UST, meaningless for 1 orbital
-Jdd             = 0.5             # equivalent to JH, JX and JP, also meaningless here
-
-[QMC]                             # Parameters for some grid sizes are part of this section
-Ntau            = 1024            # imaginary time grid size
-Niw             = 4096            # number of positive Matsubara frequencies
-
-[EDIPACK]                         # further non-default parameters, also taken from Fortran example
-NBATH           = 7               # number of bath sites
-ED_TWIN         = True            # use twin symmetry
-LFIT            = 2048            # number of Matsubara frequencies used for the bath fit
-LANC_NGFITER    = 500             # number of Lanczos iterations for Green's function
-CG_FTOL         = 1e-10           # conjugate-gradient tolerance
-CG_NITER        = 2048            # maximum number of conjugate-gradient iterations
-\end{lstlisting}
-
-With this parameter file, we can use the {\tt DMFT.py} script of
-w2dynamics to perform the execution and find the results in form of
-both a typical w2dynamics HDF5 output file whose name starts with {\tt
-  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
-name of the HDF5 output file that contain unavoidable or explicitly
-requested \NAME input and output files for each individual DMFT
-iteration. We can extract results from the HDF5 output file e.g. using
-the {\tt hgrep} script of w2dynamics. The following listing shows how
-to perform a calculation with 10 parallel MPI processes and print the
-impurity self-energy result of the last DMFT iteration to the terminal
-assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
-directory and w2dynamics installed to {\tt /opt/w2dynamics}.
-
-\begin{lstlisting}[style=mybash]
-mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
-python /opt/w2dynamics/hgrep latest siw-full -1
-\end{lstlisting}
-
-\subsection{Interacting Bernevig-Hughes-Zhang (Fortran)}
 

### 2025-05-20 03_edipack2.tex
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>

@@
   \begin{split}
-    \hat{H}_\mathrm{ph}&=\sum_q \omega_{0q} b_q^+b_q\\
+    \hat{H}_\mathrm{ph}&=\sum_q \omega_{0q} b_q^+b_q + \sum_q \sqrt{2}A_{q}(b^\dagger_q + b_q)  \\
     % 
@@
 work we shall consider $N_q=1$.
+The phonon's frequency is passed to the \NAME program via the variable { \tt W0\_PH } to be read from the input file.
+The displacement field acting on the phonon is passed through the variable {\tt A\_PH} from the input file.
+The electron-phonon coupling matrix $g_{\alpha \beta}$ instead can be passed in two different ways.
+If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable {\tt G\_PH }.
+For any general shape one can pass to the input file a {\tt GPHfile } variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.
+If {\tt GPHfile=NONE} the matrix $g_{\alpha \beta}$ is read from the variable {\tt G\_PH}, else it is read from the {\tt GPHfile}.
 

### 2025-05-20 05_examples.tex
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>

--- 2025-05-18 05_examples.tex
@@
 
-This interaction in two limits takes two simpler forms, for $\omega_0 \rightarrow \infty$ with $g^2/\omega_0=\lambda$ constant, also known as anti-adiabatic limit, the interaction becomes a Hubbard attraction:
+In the following we show for a fixed value of $\lambda/D=1.0$ the adiabatic to anti-adiabatic crossover for the uniform solution of the Holstein problem on the Bethe lattice.
+
+The Holstein interaction takes a simpler form for $\omega_0 \rightarrow \infty$ with $g^2/\omega_0=\lambda/2$ constant, also known as anti-adiabatic limit, for which it becomes a Hubbard attraction:
 \begin{equation}
@@
 
-Meanwhile in the opposite limit, $\omega_0 \rightarrow 0$ with $g^2/\omega_0=\lambda$ constant, also known as adiabatic limit, the phonons are condensed and the creation/annihilation operators can be considered as a scalar number to be determined self-consistently.
-In that case the interaction at equation \eqref{eqex:H_Holstein} for uniform solution vanishes and one recovers the non-interacting limit.
+Meanwhile, in the opposite limit, $\omega_0 \rightarrow 0$ with $g^2/\omega_0=\lambda/2$ constant, also known as adiabatic limit, the system is in a phase of Bipolaronic insulator~\citep{Capone2006PRB} for $\lambda=1$.
 
-THE FOLLOWING MAYBE IN THE E-PH SECTION
-
-The phonon's frequency is passed to the \NAME program via the variable W0\_PH to be read from the input file.
-The displacement field acting on the phonon is passed thorugh the variable A\_PH from the input file.
-The electron-phonon coupling matrix $g_{\alpha \beta}$ instead can be passed in two different ways.
-If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable G\_PH.
-For any general shape one can pass to the input file a GPHfile variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.
-If GPHfile=NONE the matrix $g_{\alpha \beta}$ is read from the variable G\_PH, else it is read from the GPHfile.
-
-In the following we show for a fixed value of $\lambda=2$ the adiabatic to anti-adiabatic crossover for the uniform solution of the Holstein problem.
-
-PLOT docc vs W0, superc and normal
-PLT delta vs w0, superc
+\begin{figure}[ht!]
+    \includegraphics[width=\linewidth]{edipack2_examples/Bethe_Holstein/figBethe_Holstein.pdf}
+    \caption{\label{figEx5}Plots of the double occupancy (A) and the superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda/D=1$ in the normal (orange) and superconductive (red) phase.
+The horizontal broken line are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
+\end{figure}
 

### 2025-05-20 edipack2_examples/Bethe_Holstein/ed_holstein.f90

@@ -1,0 +1,248 @@
+program ed_holstein
+  USE EDIPACK2
+  USE SCIFOR
+  USE DMFT_TOOLS
+  USE MPI
+  USE SF_MPI
+  implicit none
+  integer                                     :: i,iloop,Le,Nso,Nsom,Mnambu
+  logical                                     :: converged, phsym
+  !Bath:
+  integer                                     :: Nb,print_mode
+  real(8),allocatable                         :: Bath(:),Bath_(:)
+  !The local hybridization function:
+  complex(8),allocatable                      :: Weiss(:,:,:,:,:,:),Weiss_(:,:,:,:,:,:)
+  complex(8),allocatable                      :: Smats(:,:,:,:,:,:),Sreal(:,:,:,:,:,:)
+  complex(8),allocatable                      :: Gmats(:,:,:,:,:,:),Greal(:,:,:,:,:,:)
+  complex(8),allocatable                      :: Gtest(:,:)
+  !hamiltonian input:
+  complex(8),allocatable                      :: Hloc(:,:,:,:)
+  real(8),dimension(2)                        :: Wband,de
+  real(8),dimension(:,:),allocatable          :: Dbands
+  real(8),dimension(:,:,:),allocatable        :: Ebands ![Nso][Le]
+  real(8),dimension(:,:),allocatable          :: H0     ![Nso]
+  !variables for the model:
+  real(8)                                     :: ts, wmixing
+  character(len=16)                           :: finput
+  logical                                     :: mixG0,scflag
+  !
+  !MPI Vars:
+  integer                                     :: irank,comm,rank,size2,ierr
+  logical                                     :: master
+
+  call init_MPI()
+  comm = MPI_COMM_WORLD
+  call StartMsg_MPI(comm)
+  rank = get_Rank_MPI(comm)
+  size2 = get_Size_MPI(comm)
+  master = get_Master_MPI(comm)
+  
+
+  !Parse additional variables && read Input
+  call parse_cmd_variable(finput,"FINPUT",default="inputED.in")
[…]

### 2025-05-20 edipack2_examples/Bethe_Holstein/script_figBethe.py
Co-authored-by: Samuele Giuli <sgiuli@sissa.it>

@@ -1,0 +1,97 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+W0_list = ["0.2","0.5","1.0","2.0","4.0","32.0","50.0","200.0","infty"]
+W0_plot = np.float64(W0_list[:-1])
+#W0_list = ["0.2","0.5","1.0","2.0","32.0","50.0","200.0","infty"]
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 40})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AB
+    """
+)
+
+
+axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+
+
+##################################################################
+#Plot docc
+ax=axs["A"]
+n_docc_list=np.zeros(len(W0_list))
+s_docc_list=np.zeros(len(W0_list))
+print("Read Data docc...")
+for iW,W0 in enumerate(W0_list):
+  print("w0:",W0)
+  n_docc_list[iW] = np.loadtxt(f'normal/W{W0}/observables_last.ed',unpack=True)[1]
+  s_docc_list[iW] = np.loadtxt(f'superc/W{W0}/observables_last.ed',unpack=True)[1]
+
+ax.set_xscale("log")
+ax.set_xlabel(r'$\omega_0$/D')
+ax.set_ylabel(r'$ \langle n_\uparrow n_\downarrow \rangle$')
+ax.set_ylim(0.4,0.5)
+
+ax.plot(W0_plot,n_docc_list[:-1],label="ed_mode=normal",c="orange",marker="o",linewidth=3)
[…]

### 2025-05-20 05_examples.tex
Intermediate commit. Finishing BHZ

@@
 to the  user. The first is to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone in
-order to obtain both the local non-intearcing Hamiltonian
-$H_{loc}=\tfrac{1}{N_k}\sum_k H(k)$ and get the local interacting
-Green's function
+order to obtain the local interacting Green's function, used in the
+implementation of the self-consistency conditions:
+$\GG^{-1}=G_{loc}^{-1}+\Sigma$, with: 
 $$
-G_{loc}(z) = \tfrac{1}{N_k}\sum_k \left[z+\mu-H(k)-\Sigma(z) \right]^{-1}
+G_{loc}(z) = \tfrac{1}{N_k}\sum_k \left[z+\mu-H(k)-\Sigma(z)
+\right]^{-1}, 
 $$
-where $\z\in\CCC$, $\Sigma(z)$ is the self-energy function obtained from the DMFT
-solution of the problem and $N_k$ is the number of $k$-points. 
+where $\z\in\CCC$  and $\Sigma(z)$ is the self-energy function obtained from the DMFT
+solution of the proble.  $N_k$ is the number of $k$-points. 
 The second is to  construct the ``renormalized'' topological
@@
 
-\subsubsection{Results}
+\begin{figure}[t!]
+  \includegraphics[width=\linewidth]{figures/figBHZ.pdf}
+    \caption{\label{figEx4}%
+      \textbf{Topological and Exciton Transition.}
+      (A) Evolution of the spin-triplet,
+      in-plane excitonic order parameter $\langle E_x\rangle$ (black solid line) and
+      orbital polarization $\langle T_z\rangle$ (orange dashed line) as a function of the
+      interaction $U$.
+      (B-D) Spectral functions of the two orbital electrons for three
+      values of the interaction $U=2.00$ (red circle), $4.00$ (red
+      square) and $6.00$ (red diamond) capturing, respectively, the
+      QSHI (B), the Excitonic Insulator (C) and the Mott Insulator
+      (D). 
+    }
+\end{figure}
+
+\paragraph{Results}
 To capture the possible symmetry breaking in any excitonic channel
@@
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
-   !> Set $H_{loc}$ in \NAME
+   !> Set $H_{loc}$
    allocate(Hloc(Nso,Nso))
@@
    call ed_set_hloc(Hloc)
-   !> Setup the replica bath basis using  $M$, $E_0$, $E_z$ and $E_x$ as symmetries
+   !> Setup the replica bath basis:
    allocate(lambdasym_vector(Nbath,4))
@@
 \end{lstlisting}
+where we use the local non-interacting Hamiltonian 
+$H_{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
+$h^0_{\a\b\s\s'}$, i.e. the impurity Hamiltonian. To anticipate the
+possibility of forming an excitonic ordered phase, the replica bath
+is constructed out of matrix basis with 4 distinct elements
+$\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which
+are proportional, respectively, to the mass term, the exciton singlet
+$E_0$, the exciton triplet along easy-axis $E_z$ and in-plane
+$E_x$ (we assume $E_y=0$ levaraging on residual $U(1)$ in-plane
+symmetry.
 
@@
 conditions for the formation of a Mott insulating state.
-In between, at inter-mediate coupling, we observe the formation of a
-region of exciton condensation.
-In panel (A) of \figu{figEx4} we report the evolution of the order
-parameter
+As reported in panel (A) of \figu{figEx4}, at intermediate coupling,
+the DMFT solutions features the formation of a
+region of exciton condensation with $\langle E_x\rangle>0$, $\langle
+E_0\rangle=\langle E_z\rangle=0$. 
+Unlike the static mean-field description~\cite{Blason2021}, the
+transition from the QSHI topological state to the Excitonic Insulator 
+(EI) becomes of first-order in presence of quantum fluctuations
+corrections~\cite{Continentino,Paoletti} contained in DMFT. On the
+other hand, the EI continuously evolves into a Mott Insulator (MI)
+for larger interaction (neglecting for simplicity any 
+anti-ferromagnetic ordering that would naturally occurr in this
+regime).
+In the same panel we report the evolution of 
+$\langle T_z\rangle$ to illustrate the progressive reduction of the
+orbital polarization and, thus, of the effective mass.
 
-\begin{figure}[t!]
-  \includegraphics[width=\linewidth]{figures/figBHZ.pdf}
-    \caption{\label{figEx4}%
-      \textbf{Topological and Exciton Transition.}
-      (a)
-    }
-\end{figure}
+To further illustrate the nature of the three distinct phases of this
+system, we leverage on the direct access to real-axis spectral
+function provided by \NAME solver. In panels (B)-(D) of \figu{figEx4}
+we report the spectral functions $-\Im{G}_{a,loc}(\omega)/\pi$ for
+$a=1,2$, $\sigma=\up$ and three distinct values of the interaction
+$U$ placing the solution, respectively, in the QSHI, the EI and the MI.
+The correlated QSHI is characterized by the presence of an 
+inverted band gap featuring a substantial orbital spectral mixing. The
+EI spectrum is instead characterized by a narrow gap, related to the
+finite order parameter, flanked by two sharp resonances and featuring
+larger high-energy weight.
+Finally, in the MI the two orbital spectral function describes the two 
+characteristic Hubbard bands separated by a large Mott gap.
 

### 2025-05-20 edipack2.tex
Intermediate commit. Adding BHZ nonSU2
Intermediate commit. Finishing BHZ

@@
 \def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack2}\xspace}
+\def\NAME{{\rm EDIpack}\xspace}
 \newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}
@@
 
-\title{EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems}
-\author[a,b,c]{L.~Crippa}
-\author[a]{I.~Krivenko}
-\author[d]{S.~Giuli}
-\author[d]{G.~Bellomia}
+\title{EDIpack 2.0: A generic and interoperable Lanczos-based solver for quantum impurity problems}
+\author[a,b,c]{L.~Crippa*}
+\author[a]{I.~Krivenko*}
+\author[d]{S.~Giuli*}
+\author[d]{G.~Bellomia*}
 \author[c]{A.~Kowalski}
@@
 \author[c,b]{G.~Sangiovanni}
- \author[d,i]{M.~Capone}
-\author[i]{A.~Amaricci}
+\author[d,i]{M.~Capone*}
+\author[i]{A.~Amaricci*}
 % \author[]{A.~Scazzola}
@@
 % \address[]{Politecnico di Torino, Turin, Italy}
-% \cortext[AA]{Corresponding author:lorenzo.crippa@uni-hamburg.de}
-% \cortext[BB] {Corresponding author:giuli@sissa.it}
-% \cortext[CC]{Corresponding author:bellomia@sissa.it}
+\cortext[1]{Corresponding authors}
+% \cortext[*] {Corresponding author:giuli@sissa.it}
+% \cortext[*]{Corresponding author:bellomia@sissa.it}
 
@@
   \\
-  {\em Program Title:}  EDIpack2                                        \\
+  {\em Program Title:}  EDIpack                                        \\
   {\em Licensing provisions:} GPLv3\\
-{\em Programming language:}  Fortran, Python \\
+  {\em Programming language:}  Fortran, Python, C/C++\\
   {\em Classification:} 6.5, 7.4, 20 \\
-{\em Required dependencies:} CMake ($>=3.0.0$), Scifortran, MPI\\
+  {\em Required dependencies:} CMake ($>=3.10.0$), Scifortran, MPI\\
   {\em Nature of problem:}. \\

### 2025-05-20 05_examples.tex
Iterated examples parts. Ready to share.
* To be iterated Intro and Conclusions (that is on me)
* Missing discussion of the conjugate gradient fit of matrix GF norms (on Gabriel)
* Totally incomplete bibliograpy.
* Missing finite Temperature comparison between EDIpack and W2Dyn (on Alexander+Lorenzo?)

@@
 
-\subsection{Bethe lattice DMFT}\label{SecExamplesBetheDMFT}
+\subsection{Hubbard model on the Bethe lattice (Fortran API)}\label{SecExamplesBetheDMFT}
 The test bed for any DMFT application is conventionally considered 
@@
 
-\subsubsection{W2Dynamics solution}\label{SecExamplesBetheDMFTw2d}
+\subsubsection{Finite temperature solution (W2Dynamics interface)}\label{SecExamplesBetheDMFTw2d}
 To demonstrate use of the w2dynamics interface, here we briefly
@@
 
-\subsection{Attractive Hubbard model}\label{SecExamplesAHM}
+\subsection{Attractive Hubbard model (Python API, {\tt ed\_mode=superc})}\label{SecExamplesAHM}
 The second example we present concerns the DMFT description of the 
@@
 
-\subsection{Multi-orbital impurity with Hubbard-Kanamori interaction}
+\subsection{Multi-orbital quantum impurity with Hubbard-Kanamori
+  interaction (TRIQS interface)}
 \label{SecExamplesTRIQS}
@@
 
-\subsection{Interacting Bernevig-Hughes-Zhang model}
+\subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
 In this section we focus on the DMFT solution of the interacting
@@
 QSHI in the non-interacting limit and $J/U=0.25$.
+The implemention is nearly identical to the cases discussed above and
+we report it here for completeness:
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+   iloop=0;converged=.false.
+   do while(.not.converged.AND.iloop<nloop)
+     iloop=iloop+1
+     !> Solve the impurity problem, retrieve $\Sigma(i\omega)$
+     call ed_solve(bath)
+     call ed_get_sigma(Smats,axis='mats')
+     !> Get $G_{loc}$ (assume to have a function for this task)
+     call get_gloc(Hk,Gmats,Smats,axis='m')
+     !> Update the Weiss field $\GG^{-1}=G^{-1}_{loc}+\Sigma$ +  Linear mixing.
+     call dmft_self_consistency(Gmats,Smats,Weiss)
+     if(iloop>1)Weiss = wmixing*Weiss + (1.d0-wmixing)*Weiss_;Weiss_=Weiss
+     !> Fit to updated the bath
+     call ed_chi2_fitgf(Weiss,bath,ispin=1)
+     !Check convergence (using DMFT_TOOLS)
+     converged = check_convergence(Weiss(1,1,:),dmft_error,nsuccess,nloop)
+   enddo  
+\end{lstlisting}
+
 %
@@
 
-\subsection{Holstein model on the Bethe lattice (Fortran)}
+\subsection{Holstein model on the Bethe lattice (Fortran API, {\tt electron-phonons})}
+One of the features introduced in \NAME is the possibility of treating
+local phonons in conjunction with the superconductive phase,
+i.e. \textbf{ed\_mode=superc}. 
+In this example discuss  the normal and
+superconductive solution of the pure Holstein model on the Bethe
+lattice within DMFT.
+We stress that, using Fortran API, the code
+implementation for this specific case is essentially identical to the listing reported in the sections
+\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
+\ref{SecExamplesAHM} ({\tt ed\_mode=superc}).
 
-One of the features introduced in \NAME is the possibility of treating local phonons in the superconductive case (i.e.
-\textbf{ed\_mode=superc} ).
-In this example we show how to get the normal and superconductive solutions of the Holstein model on the Bethe lattice within DMFT.
-The phononic and electron-phonon part of the Holstein Hamiltonian at half-filling for particle-hole symmetric density of states like in the Bethe lattice reads:
+So we consider the model introduced in \secu{SecExamplesBetheDMFT}
+with $U=0$ and the additional phononic and electron-phonon terms:
 \begin{equation} \label{eqex:H_Holstein}
-    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i + b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2})\Big]
+    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
+    b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma}
+    -\frac{1}{2})\Big]. 
 \end{equation}
+We consider the half-filling regime of the particle-hole symmetric
+Bethe lattice density of states. We set the half-bandwidth as our
+energy unit $D=1$ and introduced the electron-phonon coupling $\lambda
+= \tfrac{2g^2}{\omega_0D}$.  
+The iterative DMFT solution algorithm follows the same principles
+illustrated in the previous sections.
 
-In the following we show for a fixed value of $\lambda/D=1.0$ the adiabatic to anti-adiabatic crossover for the uniform solution of the Holstein problem on the Bethe lattice.
+\paragraph{Results}
+In the following we discuss the adiabatic ($\omega_0\to0$) to
+anti-adiabatic ($\omega_0\to\infty$) crossover for
+the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
 
-The Holstein interaction takes a simpler form for $\omega_0 \rightarrow \infty$ with $g^2/\omega_0=\lambda/2$ constant, also known as anti-adiabatic limit, for which it becomes a Hubbard attraction:
-\begin{equation}
+In the anti-adiabatic limit, the Holstein interaction takes a
+particularly simple form:
+\begin{equation}\label{HlikeAttraction}
     H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
 \end{equation}
+which describes a local Hubbard-like attraction among electrons
+(mediated by local phonons).
+In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
+enters in a Bipolaronic Insulating phase~\citep{Capone2006PRB} for our
+choice of the coupling.
 
-Meanwhile, in the opposite limit, $\omega_0 \rightarrow 0$ with $g^2/\omega_0=\lambda/2$ constant, also known as adiabatic limit, the system is in a phase of Bipolaronic insulator~\citep{Capone2006PRB} for $\lambda=1$.
+We characterize the model solution by showin the evolution of the
+double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
+phonon frequency $\omega_0$, see panel (A). In this panel we compare
+the behavior for {\tt ed\_mode=normal} against the superconductive
+solution ({\tt ed\_mode=superc}). Our results capture the whole
+crossover from adiabatic to anti-adiabatic regime. In the former
+regime, the double occupation takes a similar value for the two
+phases. However, approaching the anti-adiabatic regime, the two
+solutions reach the limiting values corresponding to the residual
+attraction \equ{HlikeAttraction}.   
+To better characterize the nature of the superconducting
+phase in the Holstein model we report the evolution of the anomalous order
+parameter $\phi$ in the adiabatic to anti-adiabatc crossover.
+The DMFT results obtained with \NAME show the rapid increase of the
+superconducting order parameter as phonon frequency grows
+large. Finally, in the anti-adiabatic regime $\phi$ saturates to a
+finite value corresponding to the attractive Hubbard-like interaction
+of strenght $\lambda/2$.
 
 \begin{figure}[ht!]
-    \includegraphics[width=\linewidth]{edipack2_examples/Bethe_Holstein/figBethe_Holstein.pdf}
-    \caption{\label{figEx5}Plots of the double occupancy (A) and the superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda/D=1$ in the normal (orange) and superconductive (red) phase.
+    \includegraphics[width=\linewidth]{figures/figBethe_Holstein.pdf}
+    \caption{\label{figEx5}
+      Evolution of the  double occupation (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
 The horizontal broken line are the values for the corresponding Hubbard model in the anti-adiabatic limit.}

### 2025-05-20 edipack2_examples/Bethe_Holstein/script_figBethe.py

@@ -33,11 +33,11 @@ axs = plt.figure(layout="constrained").subplot_mosaic(
 )
 
 
-axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
-axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["A"].text(0.96, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.96, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
 
 
-
+ms=20
 
 
 ##################################################################
@@ -56,14 +56,14 @@ ax.set_xlabel(r'$\omega_0$/D')
 ax.set_ylabel(r'$ \langle n_\uparrow n_\downarrow \rangle$')
 ax.set_ylim(0.4,0.5)
 
-ax.plot(W0_plot,n_docc_list[:-1],label="ed_mode=normal",c="orange",marker="o",linewidth=3)
-ax.plot(W0_plot,s_docc_list[:-1],label="ed_mode=superc",c="red",marker="o",linewidth=3)
+ax.plot(W0_plot,n_docc_list[:-1],label="normal",c="orange",marker="o",lw=6,markersize=ms,zorder=1)
+ax.plot(W0_plot,s_docc_list[:-1],label="superc",c="red",marker="s",lw=6,markersize=ms,zorder=1)
 #AntiAdiabatic
-ax.axhline(n_docc_list[-1],linestyle="--",c="orange",linewidth=6,alpha=.5)
-ax.axhline(s_docc_list[-1],linestyle="--",c="red",linewidth=6,alpha=0.5)
+ax.axhline(n_docc_list[-1],linestyle="--",c="orange",linewidth=8,alpha=.5,zorder=2)
+ax.axhline(s_docc_list[-1],linestyle="--",c="red",linewidth=8,alpha=0.5,zorder=2)
 
 
-ax.legend(loc='upper center') #, fontsize = '22', handlelength=1.5, framealpha=1)
+ax.legend(loc='upper right') #, fontsize = '22', handlelength=1.5, framealpha=1)
 
 ##################################################################
 
@@ -81,9 +81,9 @@ ax.set_xlabel(r'$\omega_0 /D$')
[…]

### 2025-05-20 01_intro.tex
Iterated introduction. Ready to update W2Dyn section with T>0 results.
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>

--- 2025-04-09 01_intro.tex
@@
+\documentclass[edipack2.tex]{subfiles}
+\begin{document}
+
 \section{Introduction and Motivation}\label{SecIntro}
+\fixme{A tentative Introduction scheme}
 
-A few words about the motivations who led us to develop this
-software, possible applications and advantages:
+Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with extended non-interacting environment.
+Originally introduced to describe magnetic impurities in metallic hosts, i.e.
+Kondo problem, these systems progressively became powerful tools for exploring a wide range of quantum many-body phenomena.
+More recently, their importance extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cod atomic systems.
 
-* flexibility: can address generic cases including multi-orbital,
-superconducting or spin-non-conserving regimes
+At the heart of quantum impurity models is the interaction between a localized impurity, possibly including lattice, orbital and spin states, and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
+This setup capture many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
+Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
+By retaining essential local correlations, the DMFT enabled a successful effective description of the most important physical aspects of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
 
-* zero and low finite temperatures
+However, solving the quantum impurity problems emerging in the DMFT context accurately and efficiently remains a
+critical challenge, particularly for multi-orbital systems, systems
+at low temperatures or endowed with lower symmetry.
+During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load.
 
-* direct access to (well approximated) analytic dynamical functions
+%EDIPACK 2.0
+In this work we introduce  EDIpack 2.0: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+The library builds on the foundations of
+its predecessor, featuring massively parallel Lanczos-based algorithms while including several significant extensions and 
+improvements.
+The library now supports both zero and finite temperature calculations for different symmetries of the problem within a unified framework, making it suitable for a wide range of physical phenomena, from spin-orbit coupling effect in quantum materials to multi-orbital superconductivity.
+It also provides direct
+access to well-approximated dynamical correlation functions across the
+entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and
+other response properties.
 
-* direct access to impurity Fock space quantities
+Additionally, \NAME offers access to the Fock space of
+the impurity system and thus, for instance, the possibility to
+evaluate the impurity reduced density matrix
+(iRDM).
+This capability enables quantum information-inspired analyses, providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems.
+These
+features are increasingly recognized as essential for understanding the emergent behavior in correlated matter, including quantum criticality and superconductivity.
 
-bla bla bla
+This new version also includes support for systems with non-equivalent impurities , a critical feature to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
+This capability makes it
+possible to explore a wide range of inhomogeneous systems, including
+oxide interfaces or disordered systems, where
+translational symmetry is broken.
+
+%\paragraph{Interoperability}\\
+With the growing importance of  quantum impurity models in the study of correlated materials, ensuring compatibility among different methods and developments has become a key challenge.
+In this context, interoperability became a core design principle of this new updated version of \NAME.
+The library is implemented using modern Fortran constructs, with comprehensive C-bindings that enable integration with other programming languages.
+In particular, \NAME includes native C and C++
+interface layer which enable development of third-party
+extensions. A significant contribution is realized via the Python API, EDIpy, which provides a high-level interface for defining and solving impurity problems. The
+Python bindings also enable integration with established scientific
+libraries, such as NumPy and SciPy, facilitating data analysis and
+rapid prototyping.
+
+A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, is the direct  interfaces to the TRIQS
+(Toolbox for Research on Interacting Quantum Systems)  as
+well as to the W2Dynamics software, which are two of the most important and used computational tools in the field. 
+This integration provides \NAME users with access to the
+extensive data handling and analysis tools in the TRIQS ecosystem,
+while also allowing TRIQS and W2Dynamics users to benefit from the
+flexibility and performance of \NAME solver. This dual functionality
+extends the capabilities of these platforms, supporting
+reproducibility and cross-validation of numerical results, and sets a
+new standard for interoperability in quantum impurity solvers.
+
+%\paragraph{closure}
+In this paper, we present the mathematical framework, implementation
+details, and key features of \NAME, along with several illustrative
+applications. We aim to demonstrate how this flexible,
+high-performance solver can be used to tackle a wide range of
+challenging impurity problems. 
+The rest of this work has the following structure. In \secu{SecInstall} we 
+briefly illustrate the overall structure of \NAME together with its dependencies, configuration and installation procedures.
+In the following  \secu{SecEDIpack} we present the quantum impurity problem and review the software implementation in full details.
+In the following \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the interoperability capabilities of \NAME.
+In this section we also discuss 4 interface layers: i) the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) a basic Julia API.
+Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and all the discussed extensions with a series of illustrative examples.
+
+\end{document}

### 2025-05-20 04_cbinding.tex
Iterated introduction. Ready to update W2Dyn section with T>0 results.
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>

@@
 
+\paragraph{Anaconda}
+Another option for installing the package is by using the Anaconda package 
+manager on Unix/Linux systems.
+The following commands will create a new {\tt conda} environment named 
+`edipack' and install the most recently released version of edipack2triqs along 
+with its dependencies (\NAME, EDIpy2 and the TRIQS libraries).
+
+\begin{lstlisting}[style=mybash]
+conda create -n edipack
+conda activate edipack
+conda install -c conda-forge -c edipack edipack2triqs
+\end{lstlisting}
+
+\subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
+The programming interface of edipack2triqs is built around the singleton 
+Python class {\tt EDIpackSolver} (defined in the module
+{\tt edipack2triqs.solver}), whose instance represents the internal state of 
+the \NAME library and exposes its functionality through a number of 
+attributes and methods.
+
+\paragraph{{\bf Constructor}}
+Constructor of {\tt EDIpackSolver} accepts the Hamiltonian to be diagonalized
+in the form of a second-quantized fermionic operator, the TRIQS {\tt Operator}
+object described in Sec.~8.7 of Ref.~\onlinecite{Parcollet2015CPC} (impurity 
+problems involving bosons are not supported in the current version). In 
+addition to the Hamiltonian, four {\it fundamental operator sets}
+{\tt fops\_imp\_up}, {\tt fops\_imp\_dn}, {\tt fops\_bath\_up} and
+{\tt fops\_bath\_dn} must be provided.
+Each of the sets contains pairs of labels {\tt (b,j)} carried
+by the operators $c^\dagger_{b,i} / c_{b,i}$ corresponding to either impurity
+or bath electronic degrees of freedom with a certain spin projection.
+Having these two crucial pieces of information, the constructor initializes
+the underlying Fortran library and automatically selects the appropriate
+{\tt ed\_mode=normal,superc,nonsu2} (Sec.~\ref{sSecQNs}) and
+{\tt bath\_type=normal,hybrid,general} (Sec.~\ref{sSecBath}). Besides, the
+constructor accepts a vast array of keyword arguments that allow for fine-tuning
+the diagonalization process. Among others, these include the ED algorithm
+selection, the quantum numbers to be used, parameters of the Krylov space,
+the spectrum cutoff and various tolerance levels.
+
+\paragraph{{\bf Method {\tt solve}}}
+The method {\tt solve()} of {\tt EDIpackSolver} calls
+{\tt edipy2.global\_env.solve()} and therefore performs the bulk of
+calculations. It accepts the inverse temperature $\beta$ required to calculate
+the expectation value of physical observables, and parameters of energy grids
+for Green's function calculations.
+
+\paragraph{{\bf Input parameters}}
+It is possible to read off and change parameters of the Hamiltonian between
+successive calls to {\tt solve()} via respective attributes of {\tt 
+EDIpackSolver}. Note, however, that the changes that would necessitate a change of {\tt ed\_mode} or {\tt bath\_type} are disallowed. The relevant attributes
+are the following.
+\begin{itemize}
+    \item {\tt nspin} --- the number of non-equivalent spin projections 
+          (read-only).
+    \item {\tt norb} -- the number of impurity orbitals (read-only).
+    \item {\tt hloc} --- matrix $h^0_{\alpha\beta\s\s'}$ of
+          the quadratic impurity Hamiltonian (\ref{Himp}).
+    \item {\tt Uloc}, {\tt Ust}, {\tt Jh}, {\tt Jx}, {\tt Jp} ---
+          parameters $U, U', J, J_X \text{ and } J_P$ of the impurity
+          interaction term $\hat{H}^\mathrm{int}_\mathrm{imp}$ (\ref{Hint}).
+    \item {\tt bath} --- an object representing the bath. Depending on the
+          bath type selected upon solver object construction, this object is an
+          instance of {\tt BathNormal}, {\tt BathHybrid} or {\tt BathGeneral}
+          (all three classes are members of the module
+          {\tt EDIpackSolver.bath}). The bath objects support basic arithmetic
+          operations so that a mixing scheme within a DMFT calculation can be
+          easily implemented. The way to access individual bath parameters is
+          specific to each of the three classes, and is described in detail in the       \href{https://krivenko.github.io/edipack2triqs/documentation.html\#module-edipack2triqs.bath}{online API reference}.
+\end{itemize}
+
+\paragraph{{\bf Calculation results}}
+After a successful invocation of {\tt solve()}, one can extract results of the 
+calculation from the following attributes.
+\begin{itemize}
+    \item {\tt e\_pot}, {\tt e\_kin} --- thermal average of the potential 
+          (interaction) and kinetic energy respectively.
+    \item {\tt densities}, {\tt double\_occ} --- lists of average densities and
+          double occupancies of impurity orbitals.
+    \item {\tt magnetization} --- Cartesian components of the average impurity  
+          magnetization vectors, one row per orbital.
+    \item {\tt superconductive\_phi} --- Matrix of impurity superconductive
+          order parameters
+          $\phi_{\alpha\beta} = \langle c_{\alpha\up} c_{\beta\down}\rangle$
+          in orbital space. {\color{red} Is it defined elsewhere in the text?}
+    \item {\tt g\_iw}, {\tt g\_an\_iw} --- Normal and anomalous components of
+          the Matsubara impurity Green's function.
+    \item {\tt Sigma\_iw}, {\tt Sigma\_an\_iw} --- Normal and anomalous
+          components of the Matsubara impurity self-energy.
+    \item {\tt g\_w}, {\tt g\_an\_w} --- Normal and anomalous components of
+          the real-frequency impurity Green's function.
+    \item {\tt Sigma\_w}, {\tt Sigma\_an\_w} --- Normal and anomalous
+          components of the real-frequency impurity self-energy.
+\end{itemize}
+
+The Green's functions are returned as TRIQS {\tt BlockGf} containers
+with names of the individual blocks determined from the block labels {\tt 'b'}
+found in {\tt fops\_imp\_up}, {\tt fops\_imp\_dn} and from solver's
+{\tt ed\_mode}. The Matsubara and real-frequency meshes of the TRIQS GF 
+containers (see Sec.~8.2 of Ref.~\onlinecite{Parcollet2015CPC}) are constructed
+according to the parameters passed to {\tt solve()}.
+The anomalous components of the Green's functions and self-energies are only 
+available when anomalous bath terms are present in the Hamiltonian.
+If this is not the case, an attempt to access these attributes results in a
+{\tt RuntimeError}.
+
+\paragraph{{\bf Bath parameter fitting}}
+The method {\tt EDIpackSolver.chi2\_fit\_bath()} is essentially a wrapper around
+{\tt edipy2.global\_env.chi2\_fitgf()}. It accepts the function to fit (either
+the hybridization function or the Weiss field) in the {\tt BlockGf} format,
+and returns the parameter fit result as a {\tt Bath*} object along with a
+{\tt BlockGf} representation of the fitted function. In the superconducting
+case ({\tt ed\_mode=superc}), this method accepts and returns pairs of
+the {\tt BlockGf} containers corresponding to the normal and anomalous 
+components of the quantities in question.
+
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-\NAME is supported as alternative impurity solver by the w2dynamics DMFT package\cite{Wallerberger2019CPC}.
+\NAME is supported as alternative impurity solver by the w2dynamics DMFT package\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{GitHub}.
 The only prerequisite to use this option is the presence of a functioning EDIpy2 installation, which w2dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.

### 2025-05-20 edipack2_examples/W2Dynamics2EDIpack/script_figBetheW2D.py
Adding W2Dyn comparision, included figure.

@@ -1,0 +1,116 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+
+def zimS(x,z):
+  y = (1.0-1.0/z)*x#-1/z*x
+  return y
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 24})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AB
+    """
+)
+
+
+axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Gimp")
+gf = np.genfromtxt('w2d_cthyb/giw.dat',skip_header=0);x1=gf[:,0];y1=gf[:,2]
+gf = np.genfromtxt('w2d_ed/giw.dat',skip_header=0)   ;x2=gf[:,0];y2=gf[:,2]
+gf = np.genfromtxt('ed_for/impG_l11_s1_iw.ed',skip_header=0);x3=gf[:,0];y3=gf[:,1]
+
+ax.set_xlim([0, 2])
+ax.set_ylim([-2,0])
+ax.set_xlabel(r'$\omega_n$')
+ax.set_ylabel(r'${\rm Im}G(i\omega_n)$')
+# ax.yaxis.set_tick_params(labelleft=False)
+# ax.set_yticks([])
+
+ax.tick_params(length=6, width=2,direction='out')
+#ax.yaxis.grid(True, which='both', alpha=0.5)
+#ax.yaxis.set_major_locator(mticker.LogLocator(base=10, numticks=10))
+
+lw=5
+
[…]

### 2025-05-20 01_intro.tex
Updates from Overleaf

@@
 Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with extended non-interacting environment.
-Originally introduced to describe magnetic impurities in metallic hosts, i.e.
-Kondo problem, these systems progressively became powerful tools for exploring a wide range of quantum many-body phenomena.
-More recently, their importance extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cod atomic systems.
+Originally introduced to describe magnetic impurities in metallic hosts and leading to the solution of the Kondo problem, these systems progressively became powerful tools for exploring a wide range of quantum many-body phenomena.
+More recently, their importance has extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cold atomic systems.
 
-At the heart of quantum impurity models is the interaction between a localized impurity, possibly including lattice, orbital and spin states, and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
-This setup capture many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
+At the heart of quantum impurity models is the interaction between a localized ``impurity"  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
+The definition of the impurity is rather generic, and it can contain lattice (i.e.
+inequivalent sites), orbital and spin local degrees of freedom.
+This setup captures many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
 Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
-By retaining essential local correlations, the DMFT enabled a successful effective description of the most important physical aspects of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
+By accounting for local quantum fluctuations, DMFT can successfully describe of the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
 
-However, solving the quantum impurity problems emerging in the DMFT context accurately and efficiently remains a
+Accurately and efficiently solving the DMFT quantum impurity problem remains a
 critical challenge, particularly for multi-orbital systems, systems
@@
 %EDIPACK 2.0
-In this work we introduce  EDIpack 2.0: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+In this work we introduce  \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
 The library builds on the foundations of
@@
 improvements.
-The library now supports both zero and finite temperature calculations for different symmetries of the problem within a unified framework, making it suitable for a wide range of physical phenomena, from spin-orbit coupling effect in quantum materials to multi-orbital superconductivity.
+The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effect in quantum materials to multi-orbital superconductivity.
 It also provides direct
 access to well-approximated dynamical correlation functions across the
-entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and
-other response properties.
+entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and other response properties.
 
@@
 %\paragraph{Interoperability}\\
-With the growing importance of  quantum impurity models in the study of correlated materials, ensuring compatibility among different methods and developments has become a key challenge.
-In this context, interoperability became a core design principle of this new updated version of \NAME.
-The library is implemented using modern Fortran constructs, with comprehensive C-bindings that enable integration with other programming languages.
-In particular, \NAME includes native C and C++
-interface layer which enable development of third-party
-extensions. A significant contribution is realized via the Python API, EDIpy, which provides a high-level interface for defining and solving impurity problems. The
+With the growing importance of  quantum impurity models in the study of correlated materials,
+standardizazion and interoperability between solution software suites has
+become a critical necessity.
+\NAME has been expressly designed following this guiding principle. 
+While the library itself is implemented using modern Fortran constructs, it also provides an extensive set of C-bindings that enable integration with other programming languages,
+be they compiled (C, C++), JIT-compiled (Julia) or interpreted (python). 
+A significant contribution is realized via the Python API, EDIpy, which provides a high-level interface for defining and solving impurity problems. The
 Python bindings also enable integration with established scientific
@@
 
-A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, is the direct  interfaces to the TRIQS
-(Toolbox for Research on Interacting Quantum Systems)  as
-well as to the W2Dynamics software, which are two of the most important and used computational tools in the field. 
-This integration provides \NAME users with access to the
-extensive data handling and analysis tools in the TRIQS ecosystem,
-while also allowing TRIQS and W2Dynamics users to benefit from the
-flexibility and performance of \NAME solver. This dual functionality
-extends the capabilities of these platforms, supporting
-reproducibility and cross-validation of numerical results, and sets a
-new standard for interoperability in quantum impurity solvers.
+A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, 
+is the direct  interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems)  as
+well as to the W2Dynamics software, which are two of the most 
+important and used computational tools in the field. \NAME seamlessly slots in as an alternative
+solver to the native Quantum Monte Carlo implementations, greatly extending the parameter (and 
+especially temperature) range reachable by the simulation while minimizing code production from 
+the end user.
+At the same time, this integration provides \NAME users with access to the
+extensive data handling and analysis tools in the TRIQS ecosystem. 
+Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
+enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of achieving standardization for quantum impurity solvers.
 
@@
 The rest of this work has the following structure. In \secu{SecInstall} we 
-briefly illustrate the overall structure of \NAME together with its dependencies, configuration and installation procedures.
-In the following  \secu{SecEDIpack} we present the quantum impurity problem and review the software implementation in full details.
-In the following \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the interoperability capabilities of \NAME.
-In this section we also discuss 4 interface layers: i) the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) a basic Julia API.
-Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and all the discussed extensions with a series of illustrative examples.
+briefly illustrate the overall structure of \NAME together with its dependencies, configuration
+and installation procedures. In the following  \secu{SecEDIpack} we present the quantum impurity
+problem and review the software implementation in full details. In the following 
+\secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
+interoperability capabilities of \NAME. In this section we also discuss 4 interface layers: i) 
+the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) a basic Julia API.
+Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and 
+all the discussed extensions with a series of illustrative examples.
 

### 2025-05-20 01_intro.tex
Updates from Overleaf

@@
 While the library itself is implemented using modern Fortran constructs, it also provides an extensive set of C-bindings that enable integration with other programming languages,
-be they compiled (C, C++), JIT-compiled (Julia) or interpreted (python). 
-A significant contribution is realized via the Python API, EDIpy, which provides a high-level interface for defining and solving impurity problems. The
-Python bindings also enable integration with established scientific
-libraries, such as NumPy and SciPy, facilitating data analysis and
+be they compiled (C, C++), JIT-compiled (Julia) or interpreted (Python). 
+Especially notable in this sense is the Python API, EDIpy which, beyond providing a 
+high-level interface for defining and solving impurity problems, also allows integration with established scientific libraries, such as NumPy and SciPy, facilitating data analysis and
 rapid prototyping.
@@
 A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, 
-is the direct  interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems)  as
-well as to the W2Dynamics software, which are two of the most 
-important and used computational tools in the field. \NAME seamlessly slots in as an alternative
-solver to the native Quantum Monte Carlo implementations, greatly extending the parameter (and 
-especially temperature) range reachable by the simulation while minimizing code production from 
-the end user.
+is the direct  interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems) and
+W2Dynamics software suites, which are two of the most important and used computational tools in
+the field. \NAME seamlessly slots in as an alternative solver to the native Quantum Monte Carlo 
+implementations, greatly extending the parameter (and especially temperature) range reachable by 
+the simulation while minimizing the cfor the end user.
 At the same time, this integration provides \NAME users with access to the

### 2025-05-20 01_intro.tex
Read introduction ad install (LC)

@@
 implementations, greatly extending the parameter (and especially temperature) range reachable by 
-the simulation while minimizing the cfor the end user.
+the simulation while minimizing the coding requirements for the end user.
 At the same time, this integration provides \NAME users with access to the
@@
 Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
-enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of achieving standardization for quantum impurity solvers.
+enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of a
+chieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat.
 

### 2025-05-20 02_install.tex
Added some Julia comments
Read introduction ad install (LC)

@@
 \section{Installation}\label{SecInstall}
-The installation of \NAME is available through CMake which ensures
+The configuration and installation of \NAME is handled by CMake, which ensures
 multi-platforms compabitility and dependencies resolution.  
 The software builds into two distinct libraries.
-The main one is {\tt  libedipack.a} which, alongside the generated Fortan
-modules, wraps the \NAME software possibly including support for  
-inequivalent impurities.
-A second dynamic library, {\tt libedipack\_cbinding.so}, enables interoperability through
-specific bindings to the C/C++ programming language.
+The main one is a static Fortran library calledc{\tt  libedipack.a} which, alongside the compiled
+modules, wraps the \NAME software in both its single- and multi-impurity variants.
+A second dynamic library, {\tt libedipack\_cbinding.so}, together with the associated header
+file{\tt edipack2\_cbinding.h}, enables interoperability with other programming languages.
 
@@
 \NAME is a modular library organized into three main components. At its 
-core is the exact diagonalization solver, which provides the primary 
-computational engine. Building on this, the library includes 
+core, constituting the primary computational engine, 
+is the exact diagonalization solver for the quantum single-impurity Hamiltonian.
+Building on this, the library includes 
 {\tt EDIpack2ineq}, an extension for handling multiple inequivalent 
-impurity problems. Finally, a Fortran-C/C++ interface is provided for 
+impurity problems. Finally, the Fortran-C/C++ interface is provided for 
 seamless integration with external software and the development of 
@@
 \subsection{Dependencies}\label{sSecInstallDependencies}
-\NAME essentially depends on two external libraries.
+\NAME directly depends on two external libraries.
 \begin{itemize}
@@
 \subsection{Build and Install}\label{sSecInstallBuildInstall}
-\subsubsection{Source}
-The software can be installed from source as follows. The source can
+\subsubsection{Compilation from source}
+The software can be installed from source as follows. The source code can
 be retrieved directly from its GitHub repository, for instance using:
@@
 \end{lstlisting}
-Then, assuming to be in the software directoru, a conventional
-out-of-source building is performed using two different compilations
-backends.
+Then, assuming to be in the software directory, a conventional
+out-of-source building can be performed using two alternative compilation backends.
 
@@
 \noindent
-The CMake configurations can be further tuned using the following variables:
+The CMake configuration can be further tuned using the following variables:
 \begin{center}
@@
 
-The default target builds and install either the main library and the C-binding.
-However, a specific building for each library is available specifying
-the required target. A recap message is printed at the end of the
+The default target builds and install both the main library and the C-bindings.
+Separate build targets for either are available. A recap message is printed at the end of the
 CMake configuration step.
@@
 \subsubsection{Anaconda}
-As an alternative we provide for both Linux and OSx systems
+As an alternative we provide for both Linux and Mac Os systems
 installation through Anaconda packages into a virtual
@@
 \noindent
-which installs a bundle of Scifor and \NAME libraries together with
-specific {\tt pkg-config} configurations files which can be used to
-retrieve compilation and linking flags.
+which installs a bundle of SciFortran and \NAME libraries together with
+specific {\tt pkg-config} configurations files, which can be used to
+retrieve compilation and linking flags. In order to compile Fortran/C++ 
+drivers, the {\tt compilers} conda package will need to be installed.
 
 \subsection{OS Loading}\label{sSecInstallOSloading}
-In oder to avoid possible conflicts or require administrative
-privileges, the building step results get installed by default in a user home
+In order to avoid possible conflicts or the requirement for administrative
+privileges, the building step results are installed by default in the user's {\tt HOME}
 directory, specified by the CMake variable {\tt PREFIX}.
-In doing so, however, one misses the chance of automatic loading into
-the operative system.
+As a consequence, the system library and include paths will need to be updated by the user.
 
-We offer different strategies to perform this action:
+We offer different ways to perform this action:
 \begin{enumerate}
-\item  A CMake generated configuration file for environment module
+\item  A CMake-generated configuration file for an environment module
   which allows to load and unload the library at any time. This is
   preferred solution for HPC systems. 
-\item A CMake generated bash script to be sourced (once or
+\item A CMake-generated bash script to be sourced (once or
   permanently) in any shell session to add \NAME library to the
   default environment.
-\item A CMake generated pkg-config configuration file to be added in
-  the pkg-config path itself.  
+\item A CMake generated {\tt pkg-config} file to be added in
+  the {\tt PKG\_CONFIG\_PATH} itself.  
 \end{enumerate}

### 2025-05-21 02_install.tex
GB wide pass on many parts of the text

@@
 
-The default target builds and install both the main library and the C-bindings.
+The default target builds and installs both the main library and the C-bindings.
 Separate build targets for either are available. A recap message is printed at the end of the
@@
 \subsubsection{Anaconda}
-As an alternative we provide for both Linux and Mac Os systems
+As an alternative, we provide for both Linux and macOS systems
 installation through Anaconda packages into a virtual

### 2025-05-21 03_edipack2.tex
GB wide pass on many parts of the text

@@
 the occupation number formalism of second quantization,
-i.e., the Fock basis.
+i.e.~the Fock basis.
 For a system of $N_\mathrm{s}$ electrons, each Fock state
@@
 can be extended to act indipendently to each orbital and spin
-component, i.e., $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
+component, i.e.~$\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
 specific case is discussed extensively
@@
   UMATRIX\_FILE}. The implementation of the list of interaction terms is contained in
-the class {\tt ED\_PARSE\_UMATRIX}.  
+the module {\tt ED\_PARSE\_UMATRIX}.  
 The file mush have the suffix {\tt \\.restart} and should be formatted
@@
 intrinsic {\tt move\_alloc} for faster execution compared to 
-implicit reallocation, i.e., {\tt vec=[vec,new\_element]}.
+implicit reallocation, i.e.~{\tt vec=[vec,new\_element]}.
 
@@
 \subsubsection{Sparse map}\label{CodeSparseMap}
-\fixme{GB: I don't like the minipage of the listing below.}
 As discussed in \secu{sSecRDM}, the construction of a symmetry 
@@
 where $N_\mathrm{imp}$ is the number of impurity bits and 
-$N_\mathrm{s}$ is the total number of spin components.
-To obtain a contiguous memory pattern we define the \emph{key} for the sparse
+$N_\mathrm{s}$ is the total number of spin orbitals.
+% To obtain a contiguous memory pattern %%> What? They are pointed lists...
+We define the \emph{key} for the sparse
 map as $I=I_\up + I_\dw2^{N_\mathrm{imp}}$ and the corresponding
@@
 This structure ensures an efficient and compact representation 
-of the many-body Hilbert space, facilitating rapid state lookup 
+of the many-body Hilbert space, enabling a rapid state lookup 
 during the diagonalization process.
@@
   replica}, and {\bf general} (see Fig.~\ref{figBaths}).
+  \fixme{This figure looks quite annoying to generate, especially to cover
+  all possible \texttt{ed\_mode} values. I'd pass...}
 
@@
 bath consists of $N_\mathrm{bath}$
-electronic levels coupled to each of the impurity orbital, resulting
-in a total  $N_\mathrm{b} = N_\a N_\mathrm{bath}$ of bath levels.
+electronic sites coupled to each of the impurity orbital, resulting
+in a total  $N_\mathrm{b} = N_\sigma N_\a N_\mathrm{bath}$ of bath levels.
+% Ocio!
 
@@
 where $\varepsilon_{\a\s}$ represents  the on-site energies for each orbital and spin.
+
 If {\tt ed\_mode}={\bf superc},  anomalous
@@
 spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
+
 If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
@@
 \paragraph{{\tt bath\_type}={\bf hybrid}}
-The bath is formed by $N_\mathrm{bath}$ levels coupled to all the
-impurity orbitals, resulting in a total of 
-$N_\mathrm{b}\equiv N_\mathrm{bath}$ electronic bath levels. 
+The bath is formed by $N_\mathrm{bath}$ sites coupled to all the
+impurity orbitals, resulting in a total of % Ocio!
+$N_\mathrm{b}\equiv N_\sigma N_\alpha N_\mathrm{bath}$ electronic bath levels. 
 The parametrization of the bath Hamiltonian is 
@@
 
-If spin group is not conserved, i.e., for {\tt ed\_mode}={\bf nonsu2}, an additional
+If full spin symmetry is not preserved, i.e.~for {\tt ed\_mode}={\bf nonsu2}, an additional
 set of parameters must be specified to account for spin-flip processes:
@@
 hybridized impurity orbitals, but typically requires a more
-challenging optimization process, specially
+challenging optimization process, especially
 with few available bath levels (see \secu{sSecFit}).
@@
 This configuration provides a more flexible parametrization of the 
-bath. The core idea is to assign each bath element a structure 
+bath. The original core idea \cite{Capone2004PRB,Civelli2006}
+is to assign each bath element a structure 
 that {\it replicates} the internal structure of the impurity, while 
@@
 a user-defined matrix basis
-$\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_{sym}}$ in the (Nambu-)spin-orbital
+$\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_\mathrm{sym}}$ in the (Nambu-)spin-orbital
 space, and expressing the bath Hamiltonian as
 $$
-h^p = \sum_{\nu=1}^{N_{sym}} \lambda^p_\nu
+h^p = \sum_{\nu=1}^{N_\mathrm{sym}} \lambda^p_\nu
 \Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
 $$
-where $\vec{\lambda}^p\in\RRR^{N_{sym}}$ is a vector of variational parameters. 
+where $\vec{\lambda}^p\in\RRR^{N_\mathrm{sym}}$ is a vector of variational parameters. 
 The choice of the matrix basis can be inspired by the internal structure
 of the quantum impurity, i.e. $\hat{h}^0$, or determined
-case-by-case by based on the physical properties of the system.
-In this scheme, the total number of bath levels becomes: $N_\mathrm{b}
-= N_{sym} N_\mathrm{bath}$.
+case-by-case, depending on the desired properties of the solution.
+In this scheme, the total number of bath levels becomes $N_\mathrm{b}
+= N_\mathrm{imp} N_\mathrm{bath}$, while the number of independent bath
+parameters to optimize is (excluding the hybridization amplitudes)
+$N_\mathrm{params} = N_\mathrm{sym} N_\mathrm{bath}$.
+% Ocio!
 
 For the {\bf replica} topology, the coupling between the impurity 
-and each bath element remains diagonal in spin, orbital, and internal 
+and each bath element is independent on spin, orbital, and internal 
 bath structure: $V^p_{\a\b\s\s'} = V^p$.
 In the {\bf general} case, this is generalized to include explicit 
+diagonal
 dependence on the internal spin and orbital indices: $V^p_{\a\b\s\s'}
@@
 saving, this module provides matrix basis setup 
-$\{ \Gamma^\nu \}_{\nu=1,\dots,N_{sym}}$ and variational parameter 
+$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ and variational parameter 
 initialization through {\tt set\_Hreplica} (or {\tt set\_Hgeneral}). 
@@
 %   \hline
-%   {\bf replica} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
+%   {\bf replica} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\mathrm{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
 %   \hline
-%   {\bf general} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_{sym}]$ & \cline{2-4} & b&  c  \cr
+%   {\bf general} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\mathrm{sym}]$ & \cline{2-4} & b&  c  \cr
 %   \hline
@@
 The core computational task in any Krylov-based diagonalization
-algorithm is the Matrix-Vector Product (MVP), i.e., the application
+algorithm is the Matrix-Vector Product (MVP), i.e.~the application
 of the Hamiltonian to a given input vector:
@@
 extending the algorithm initially proposed in 
-Ref.~\onlinecite{BellomiaPhD} to support the analysis of entanglement 
+Ref.~\onlinecite{BellomiaPhD}, to support the analysis of entanglement 
 properties of quantum impurities for any value of  {\tt ed\_mode}.
@@
 or degenerate ground states is straightforward, requiring only the 
-replacement of the pure state average with the thermal or degenerate 
+% replacement of the pure state average %%> What is a pure state average?
+introduction of a thermal or degenerate 
 ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
@@
 $
-where the pure density matrix $\rho$ is then given by:
+where the corresponding pure density matrix $\rho$ is given by:
 \begin{equation}
@@
 \end{equation}
-However, the summations involved in this trace quickly become 
-computationally prohibitive, as their range scales exponentially 
-with the system size, i.e., $4^{N_\mathrm{s}}$.
-
-To address this, we implemented a fast algorithm that exploits the 
+However, the memory footprint of $\rho$, as well as the CPU footprint 
+of the summations involved in this trace scales exponentially 
+with the system size, i.e.~$4^{N_\mathrm{s}}$, quickly becoming prohibitive.
+
+To overcome the issue, we implement a fast algorithm that exploits the 
 block structure of the Fock space defined by the symmetry sectors and
-the subsequent map sparsity. 
+the subsequent map sparsity, to perform the trace \emph{on-the-flight}. 
 This approach significantly reduces the computational cost by limiting 
 the summation to the sector size $D_\SS$ of the symmetry sector 
-$\SS$ to which the ground state (or any eigenstate) belongs.
-
-Next, we decompose the Fock basis into spin-dependent impurity and 
-bath parts. Any Fock state $\ket{I}$ can be split as:
-$
-\ket{I} = \ket{i_\uparrow \, b_\uparrow} \otimes 
-\ket{i_\downarrow \, b_\downarrow},
-$
-where the impurity $i_\sigma$ and bath $b_\sigma$ states span subspaces of dimension 
-$D^\s_\mathrm{imp}$ and $D^\s_\mathrm{bath}$, respectively, for each 
-spin $\s = \uparrow, \downarrow$.
-
+$\SS$ to which the ground state (or any eigenstate) belongs, and avoiding
+the storage of the large matrix associated with $\rho$.
+
+%%% ATTENZIONE: this is true only for the normal case!
+%
+%Next, we decompose the Fock basis into spin-dependent impurity and 
+%bath parts. Any Fock state $\ket{I}$ can be split as:
+%$
+%\ket{I} = \ket{i_\uparrow \, b_\uparrow} \otimes 
+%\ket{i_\downarrow \, b_\downarrow},
+%$
+%where the impurity $i_\sigma$ and bath $b_\sigma$ states span subspaces of dimension 
+%$D^\s_\mathrm{imp}$ and $D^\s_\mathrm{bath}$, respectively, for each 
+%spin $\s = \uparrow, \downarrow$.
+%
+%%% I WOULD SAY THAT WE DON'T NEED TO REPEAT OURSELVES< THE SECTOR
+%%% SECTION IS THERE FOR A REASON. I try to edit below:
 To efficiently manage this decomposition, we introduce a 
@@
 This structure stores, for each impurity configuration 
-$i_\s = 1, \dots, D^\s_\mathrm{imp}$ (the \emph{key}), the 
+(the \emph{key}), the 
 corresponding bath configurations 
-$b_\s \in [1, \dots, D^\s_\mathrm{bath}]$ (the \emph{values}) that 
+(the \emph{values}) that 
 satisfy the symmetry constraints over the sector quantum numbers
 imposed by the {\tt ed\_mode} variable.
-We denote the number of keys as ${\cal D}_{i\s}$ and the 
-number of values as ${\cal D}_{b\s}$.
+We denote the number of (spin-dependent) keys and values respectively
+as ${\cal D}_{i\s}$ and ${\cal D}_{b\s}$.
 The fast summation algorithm for evaluating the iRDM differs 
@@
 \paragraph{{\bf normal}}
-In this case, we take advantage of the Fock space factorization and 
-sector spin-resolved decomposition, as discussed in detail in 
+In this case, we take advantage of spin-resolved sector decomposition, 
+as discussed in detail in 
 \secu{sSecQNs}. 
@@
 act only on the corresponding 
-spin subspace, i.e., they commute with the opposite spin 
+spin subspace, i.e.~they commute with the opposite spin 
 subspace $\ket{\vec{n}_{\bar{\s}}}$ without introducing any 
@@
 
-In the {\bf normal} mode, the iRDM is restricted to 
+In the {normal} mode, the iRDM is restricted to 
 {spin-diagonal} blocks. This follows from the observation 
 that the conserved quantum numbers are 
-\emph{additive} quantities, given by:
-$N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$
-where the corresponding generator of the symmetry group factorizes as
+\emph{additive} quantities, given by
+$N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$,
+so that the corresponding generator of the symmetry group factorizes as
 $U_{N_\s} = U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}}$. 
@@
 \begin{aligned}
-U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} &= 
+\rho^\mathrm{imp} &= U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} = 
 U_{N_\s^\mathrm{bath}}^\dagger \otimes U_{N_\s^\mathrm{imp}}^\dagger 
@@
 &= 
-U_{N_\s^\mathrm{imp}}^\dagger \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}}\\
-& = 
-\rho^\mathrm{imp},
+U_{N_\s^\mathrm{imp}}^\dagger \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}},
 \end{aligned}
@@
 reorganizing the bit representation of the basis states to bring the 
-bath bitsets before the impurity states:
+bath bitsets before the impurity ones:
 $$
@@
 $\ket{i_\dw}$ bit configurations.
-Here, $\#\vec{n}_{\alpha\sigma}$ denotes the number of set bits in the 
+Here, $\#\vec{n}_{\alpha\sigma}$ denotes the number of ones in the 
 occupation vector $\vec{n}_{\alpha\sigma}$.
@@
 $C_{b_\up,i_\dw}C_{b_\up,j_\dw}$ accounts for the fermionic 
-signs associated with the bath-impurity bitset exchange.
+sign associated with the bath-impurity bitset exchange.
 
@@
 While more sophisticated optimization methods have been developed for 
-truncated algorithms like sCI or DMRG, which handle systems with a 
+truncated algorithms like sCI\cite{Mejuto_Bath_ASCI-DMFT} or DMRG\cite{boh}, 
+which handle systems with a 
 larger number of bath levels, the CG minimization approach has proven 
@@
 can choose between different norm defition.
-{\color{red} I (GB) can take care of this, as I introduced the ``elemental" norm in the code.}
+\fixme{There's no actual reason to not provide the ``elemental" norm for
+the normal and hybrid bath parametrizations, as it is relevant or not
+depending on the off-diagonal structure of $\Theta(z)$, which depends
+only on \texttt{ed\_mode}, not \texttt{bath\_type}. What do we do? I would
+vote for describing what the different norms do and vaguely mention that
+they do not work for all possible \texttt{bath\_type} values, without 
+entering any detail on the reason why. Or even not mention it, and slowly
+start to update the code to make it work with all possible combinations...}
 %GBtodo placeholder

### 2025-05-21 05_examples.tex
Adding W2Dyn comparision, included figure.
GB wide pass on many parts of the text

@@
 
+\begin{figure}%[t!]
+  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
+    \caption{\label{figEx1W}%
+        }
+\end{figure}
+
 \subsubsection{Finite temperature solution (W2Dynamics interface)}\label{SecExamplesBetheDMFTw2d}
@@
 indicating tightly bound local pairs. Comparison with the mean-field result 
-(gray line) reveals the effect of local quantum fluctuations, which 
+(gray line) reveals the effect of local dynamical fluctuations, which 
 slightly suppress the order parameter, particularly in the intermediate 
@@
 
-To quantify these correlation effects, we plot in panel (C) the 
+To quantify these dynamical effects, we plot in panel (C) the 
 \emph{correlation strength}
@@
 where $S(i\omega)$ is the anomalous self-energy.
-This ratio statically captures 
-the maximum amplitude of its dynamical dependence by comparing the high-energy 
-mean-field-like limit with the low-energy behavior at the Fermi level. 
-Large values of $\Theta$ indicate a strongly correlated state with 
-significant dynamical effects, hence a more correlated state.
+This ratio encapsulates, in a single positive number, % sorry, but "statically captures" sounded quite mysterious to me (I guess it refers to having just a single number, but it requires hard mental processing, imho)
+the amplitude of the dynamical dependence of $S(i\omega)$ by comparing its 
+BCS-like limit at high energy with the low-energy behavior at the Fermi level. 
+Large values of $\Theta$ indicate an anomalous self-energy with 
+significant dynamical effects, hence a more correlated superconducting state.
 Our results show that both the weak 
-and strong coupling limits are relatively close to the mean-field 
-description, while the intermediate regime is marked by strong 
-correlations, significantly departing from the BCS picture.
-
-To further illustrate the impact of dynamical correlations, we 
+and strong coupling limits are relatively close to the BCS results, 
+while the intermediate regime is marked by strong 
+correlations, significantly departing from the mean-field picture.
+
+To further illustrate the impact of dynamical fluctuations, we 
 present in panel (D) the evolution of the double occupancy 
@@
 results show a slight increase in $d$ over the mean-field prediction 
-in the weak coupling regime, indicating enhanced local correlations. 
-However, as $U$ increases, the double occupancy quickly drops below 
-the mean-field result, reflecting the onset of strong pairing and 
-pair localization in the BEC limit.
+in the weak coupling regime, corresponding to a steep growth of
+the correlation strength $\Theta$. 
+However, as $U$ increases, the double occupancy drops below 
+the BCS result, reflecting the onset of strong pairing and 
+pair localization in the BEC limit. Correspondingly, $\Theta$ 
+progressively decreases at large $U$ attraction strength.
 

### 2025-05-21 03_edipack2.tex
Version 1.0 completed. Ready to share with all authors. Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 can choose between different norm defition.
-\fixme{There's no actual reason to not provide the ``elemental" norm for
-the normal and hybrid bath parametrizations, as it is relevant or not
-depending on the off-diagonal structure of $\Theta(z)$, which depends
-only on \texttt{ed\_mode}, not \texttt{bath\_type}. What do we do? I would
-vote for describing what the different norms do and vaguely mention that
-they do not work for all possible \texttt{bath\_type} values, without 
-entering any detail on the reason why. Or even not mention it, and slowly
-start to update the code to make it work with all possible combinations...}
+\fixme{After careful inspection, I (GB) realize that the elemental norm 
+was never really ported from CDFMT-ED to EDIpack (there's no different
+matrix weight than all ones, which is the standard chi2, of course). 
+Hence the \texttt{cg\_norm} options is really not doing anything significant,
+as with "elemental" it gives the usual $\chi^2$ (or $\chi^q$, if you change the
+\texttt{cg\_pow}...) and for "Frobenius" it gives again the usual $\chi^2$,
+unless you put $q\neq2$, which gives an ill-defined matrix norm...
+(it mixes an effective $q=2$ coming from the matrix multiplication with 
+$q\neq2$ when you do the explicit $q$-root). I think we
+should just get rid of \texttt{cg\_norm} and do the traditional $\chi^q$, as 
+indeed we are already doing by default. Implemented like this, it is just random
+no-consequence code.}
 %GBtodo placeholder

### 2025-05-21 05_examples.tex
Version 1.0 completed. Ready to share with all authors. Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 
-\begin{figure}%[t!]
-  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
-    \caption{\label{figEx1W}%
-        }
-\end{figure}
-
 \subsubsection{Finite temperature solution (W2Dynamics interface)}\label{SecExamplesBetheDMFTw2d}
-To demonstrate use of the w2dynamics interface, here we briefly
-discuss how to solve the DMFT problem for the Bethe lattice using
-W2Dynamics interface. \fixme{For definitiness we compare the finite low
-temperature results obtained via the two solvers: ED and CTQMC.  }
-
-Unlike when the Fortran API is used, none of the
-five steps of the iterative algorithm listed there are left to the
-user to implement themselves. Instead, in addition to possibly
-non-default values for \NAME input variables, the model specification
-must also be added to a w2dynamics parameter file and depending on the
-model, further input files might need to be provided. Further
-differences are that initialization is performed in w2dynamics by
-starting from a self-energy of zero or reading a self-energy value
-from an old file, which results in the initial Weiss field that the
-initial bath parameters are fitted to, and that automatic convergence
-checking is not currently available. Finally, using the same settings
-as for the Fortran example we arrive at the w2dynamics parameter file
-shown in the following listing.
-
-\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
+To demonstrate the capabilities of the W2Dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT W2Dynamics. 
+In order to showcase the capabilities of the \NAME to address low-temperature problems comaring the W2Dynamics  Continuous-Time Quantum Monte Carlo (CTQMC) with hybridization expansion method against the \NAME solver at finite temperature.
+
+As we have seen the \NAME API, enabling access to the impurity solver and bath optimization procedures, requires the user to implement (using different methods) the DMFT algorithm.
+W2Dynamics offers a structurally different solution, providing a single Python script {\tt DMFT.py} which takes care of the whole DMFT calculation via dedicated classes to implement generic self-consistency.
+The W2Dynamics is then entirely controlled by model-dependent parameters file {\tt Parameters.in} which contains a number of variable specifications, including non-default ones controlling the ED solver inherited from \NAME interface.
+Further information about the functioning of W2Dynamics can be found in Ref.\onlinecite{W2DynWallerberger}
+The two methods have another important difference. 
+The first concerns the initial point of the iterative DMFT solution algorithm. 
+While \NAME starts from a given discrete bath, W2Dynamics is initialized with a zero Self-energy function or, in alternative, read this quantity from a converged solution.
+When using \NAME ED interface, the initial Weiss is determined using self-consistency and finally an initial discrete bath is obtained through the \NAME bath optimization procedure.
+
+The W2Dynamics configuration file for the solution of the Bethe lattice problem at finite temperature  reads: 
+\begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
 [General]
@@
 \end{lstlisting}
-
-With this parameter file, we can use the {\tt DMFT.py} script of
-w2dynamics to perform the execution and find the results in form of
-both a typical w2dynamics HDF5 output file whose name starts with {\tt
-  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
-name of the HDF5 output file that contain unavoidable or explicitly
-requested \NAME input and output files for each individual DMFT
-iteration. We can extract results from the HDF5 output file e.g. using
-the {\tt hgrep} script of w2dynamics. The following listing shows how
-to perform a calculation with 10 parallel MPI processes and print the
-impurity self-energy result of the last DMFT iteration to the terminal
-assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
-directory and w2dynamics installed to {\tt /opt/w2dynamics}.
-
-\begin{lstlisting}[style=mybash]
+Following W2Dynamics  specifics, we run the {\tt DMFT.py} script as:
+\begin{lstlisting}[style=mybash,numbers=noneccd ]
 mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
@@
 \end{lstlisting}
+Where, as for W2Dyanamics, the results are collected into a HDF5 archive, including the output files inherited from \NAME which is inspected using the provided script {\tt hgrep}.
+In this example we extract the Matsubara self-energy function $\Sigma(i\omega_n)$ for the last DMFT iteration.
+
+\begin{figure}%[t!]
+  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
+    \caption{\label{figEx1W}%
+    \textbf{Finite temperature DMFT solution.}
+    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and Self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT.
+Data are for $T/D=0.01$ and $U/D=2.0$.
+The results are obtained using original W2Dynamics CT-QMC solver and compared against the \NAME solver, either independently or using the W2Dynamics interface.
+        }
+\end{figure}
+
+In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC solver in W2Dynamics, the \NAME ED method available as solver W2Dynamics as well as independent calculation (Fortran API).
+Using DMFT, we solve the Hubbard model on a Bethe lattice for $T/D=0.01$ and $U=2.00$, corresponding to a correlated metallic state.
+In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ (note that W2Dynamics does not have access to real-axis Green's function).
+In panel (B) we show the same comparison for $\Im{\Sigma}(i\omega_n)$.
+The results obtained with the three methods are nearly identical already for a small number of bath levels ({\tt NBATH=7}) or low QMC statistics.
 

### 2025-05-21 04_cbinding.tex
Fixing EDIpack and packages names in the paper: EDIpack EDIpack2ineq ----> libedipack.a EDIpack_C ----> libedipack_cbindings.so EDIpack2py EDIpack2jl EDIpack2Triqs EDIpack-Conda
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 complete interface from the Fortran code to C/C++, i.e. {\tt
-  EDIpack2C}.
+  EDIPACK\_C}.
 
@@
 compiled into a dynamical library {\tt
-  libedipack2\_cbinding.so/.dylib}. As dicussed in the
+  libedipack\_cbindings.so/.dylib}. As dicussed in the
 \secu{sSecInstallBuildInstall}, the support for inequivalent
@@
 The C/C++ compatible functions and variables 
-are declared in the header file  {\tt edipack2\_cbinding.h}.
+are declared in the header file  {\tt edipack\_cbindings.h}.
 Since {\tt ISO\_C\_BINDING} only provides, to date, C compatibility, the 
@@
 and analogous functions for the real-space DMFT case. All functions are listed and documented in the online manual.
-When using EDIpack2 functions in a C/C++ program, care must be taken in the way arrays are passed.
+When using \NAME functions in a C/C++ program, care must be taken in the way arrays are passed.
 Consistently with {\tt ISO\_C\_BINDING}, non-scalar parameters have to be passed as raw pointers.
 An array of integers containing the dimensions of the former need to be passed as well to allow for proper Fortran input parsing.
-A working C++ example is provided in the {\tt examples} folder of the EDIpack2 repository.
+A working C++ example is provided in the {\tt examples} folder of the \NAME repository.
 
@@
 The interface layer is contained in the Fortran module {\tt
-  EDIpack2\_C}. This contains a common part and two set of functions,
+  EDIPACK\_C}. This contains a common part and two set of functions,
 one to interface the procedures from \NAME and a second
@@
   bind(C)} constructs. These are implicitly loaded into the C-binding module {\tt
-  EDIpack2\_C} through the Fortran {\tt USE EDIPACK2} statement and
+  EDIPACK\_C} through the Fortran {\tt USE EDIPACK} statement and
 then further interfaced in the C++ header file.
@@
 
-\subsection{EDIpy2, the Python API}\label{sSecInteropEDIpy}
+\subsection{EDIpack2py, the Python API}\label{sSecInteropEDIpy}
 As a first application of the \NAME C-bindings we implemented a
-complete Python interface, i.e. EDIpy2. This is a Python module which
+complete Python interface, i.e. EDIpack2py. This is a Python module which
 enables access to all the library features and unlock implementation of
@@
 \subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
-EDIpy2 is available as a stand-alone
+EDIpack2py is available as a stand-alone
 module which only depends on \NAME and SciFortran.
 The Python package can be obtained from the repository
-\href{https://github.com/EDIpack/EDIpy2.0}{EDIpy2}.
+\href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py}.
 
 \begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpy2 EDIpy2
-cd EDIpy2
+git clone https://github.com/edipack/EDIpack2py EDIpack2py
+cd EDIpack2py
 pip install . 
@@
 \paragraph{PyPi}
-The EDIpy2 package is also available in PyPi at
-\href{https://pypi.org/project/edipy2/}{pypi.org/edipy2}. As such
+The EDIpack2py package is also available in PyPi at
+\href{https://pypi.org/project/EDIpack2py/}{pypi.org/EDIpack2py}. As such
 EDIpy2 can be conveniently installed in any system supporting {\tt pip} as:
@@
 \begin{lstlisting}[style=mybash]
-pip install edipy2
+pip install edipack2py
 \end{lstlisting}
@@
 \paragraph{Anaconda}
-As for \NAME, the Python API in EDIpy2 is available through
+As for \NAME, the Python API in EDIpack2py is available through
 Anaconda packaging for Unix/Linux systems. Packages are available for
-Python version $>3.10$. The EDIpack2.0 package contains the {\tt
-  edipy2} Python module as well as the EDIpack2.0 and SciFortran
+Python version $>3.10$. The \NAME package contains the {\tt
+  EDIpack2py} Python module as well as \NAME and SciFortran
 libraries. In this case the resolution of the dependencies is
@@
 conda activate edipack
-conda install -c conda-forge -c edipack edipack2
+conda install -c conda-forge -c edipack edipack
 \end{lstlisting}
 
-Once installed, any loading of the {\tt edipy2} module resolves in the
+Once installed, any loading of the {\tt EDIpack2py} module resolves in the
 attempt to load the dynamic library {\tt
-  libedipack2\_cbinding.so/.dylib} containing the Fortran-C bindings
+  libedipack\_cbindings.so/.dylib} containing the Fortran-C bindings
 for \NAME. By default the library is searched proceeds as follow: 
@@
 \subsubsection{Implementation}\label{sSecInteropEDIpyImplementation}
-The Python API provided in the edipy2 module consists essentially of a
+The Python API provided in the EDIpack2py module consists essentially of a
 suitable class called for convenience {\tt global\_env}.
@@
 from mpi4py import MPI
-from edipy2 import global_env as ed
+from edipack2py import global_env as ed
 import os,sys
@@
 
-The EDIpy2 supports the solution of problems with independent
+The EDIpack2py supports the solution of problems with independent
 impurities, interfacing with the the EDIpack2ineq extension of the
@@
 The user can check the availability of the inequivalent impurities
-interface by querying the value of  {\tt edipy2.global\_env.has\_ineq}.
+interface by querying the value of  {\tt edipack2py.global\_env.has\_ineq}.
 
@@
 are used to control the calculation.
-The variables are loaded globally in {\tt EDIpy2} and can be accessed
+The variables are loaded globally in {\tt EDIpack2py} and can be accessed
 or set locally as properties of the class {\tt
@@
 default input variables, through a call to procedure {\tt
-  edipy2.global\_env.read\_input} which interface the {\tt
+  edipack2py.global\_env.read\_input} which interface the {\tt
   ed\_read\_input} function in \NAME. 
@@
 import numpy as np
-from edipy2 import global_env as ed
+from edipack2py import global_env as ed
 ed.Nspin = 1            # set a global variable
@@
 
-\subsection{TRIQS interface}\label{sSecInteropTRIQS}
+\subsection{EDIpack2Triqs, the TRIQS interface}\label{sSecInteropTRIQS}
 A thin compatibility layer between \NAME and the Toolbox for Research on
@@
 \subsubsection{Installation}\label{sSecInteropTRIQSInstallation}
-The package depends on \NAME (which ultimately depends on SciFortran), EDIpy2
+The package depends on \NAME (which ultimately depends on SciFortran), EDIpack2py
 and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
@@
 `edipack' and install the most recently released version of edipack2triqs along 
-with its dependencies (\NAME, EDIpy2 and the TRIQS libraries).
+with its dependencies (\NAME, EDIpack2py and the TRIQS libraries).
 
@@
 The method {\tt solve()} of {\tt EDIpackSolver} calls
-{\tt edipy2.global\_env.solve()} and therefore performs the bulk of
+{\tt edipack2py.global\_env.solve()} and therefore performs the bulk of
 calculations. It accepts the inverse temperature $\beta$ required to calculate
@@
 The method {\tt EDIpackSolver.chi2\_fit\_bath()} is essentially a wrapper around
-{\tt edipy2.global\_env.chi2\_fitgf()}. It accepts the function to fit (either
+{\tt edipack2py.global\_env.chi2\_fitgf()}. It accepts the function to fit (either
 the hybridization function or the Weiss field) in the {\tt BlockGf} format,
@@
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-\NAME is supported as alternative impurity solver by the w2dynamics DMFT package\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{GitHub}.
-The only prerequisite to use this option is the presence of a functioning EDIpy2 installation, which w2dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
+\NAME is supported as alternative impurity solver by the w2dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{GitHub}.
+The only prerequisite to use this option is the presence of a functioning EDIpack2py installation, which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
 
-In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt   EDIPACK}.
-Configuration specific to the exact diagonalization solver can be performed through the parameters in section {\tt EDIPACK} of a w2dynamics parameter file.
+In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to \NAME.
+Configuration specific to the exact diagonalization solver can be performed through the parameters in section \NAME of a w2dynamics parameter file.
 For most of the \NAME input variables, it provides a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set insofar as this is supported by the interface and not an option available through generic w2dynamics parameters.
@@
 
-\subsection{EDIjl, the Julia API}\label{sSecInteropEDIjl}
+\subsection{EDIpack2jl, the Julia API}\label{sSecInteropEDIjl}
 
@@
 python implementations for the Bethe lattice example driver.
-Its structure and operation mimicks that of the EDIpy2 layer, with minimal language-specific differences.
+Its structure and operation mimicks that of the EDIpack2py layer, with minimal language-specific differences.
 
-The \NAME{} Julia api consists of a module called {\tt EDIjl2}, which provides access to the global variables and functions contained in {\tt  libedipack2\_cbinding.so/.dylib}.
+The \NAME{} Julia api consists of a module called {\tt EDIpack2jl}, which provides access to the global variables and functions contained in {\tt  libedipack\_cbindings.so/.dylib}.
 
@@
 \begin{itemize}
-\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIjl2} will look there for the library first
+\item {\tt EDIPACK\_PATH}: if this environment variable is set, {\tt EDIpack2jl} will look there for the library first
 \item {\tt LD\_LIBRARY\_PATH}: for Linux systems
@@
 Functions are called from the dynamic library, making use of the {\tt  ccall} procedure.
-As previously stated, as a consequence of the C linking conventions multiple alternative version of the interfaced Fortran procedures are present, to account for the different input variable combinations; the EDIjl2 wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
+As previously stated, as a consequence of the C linking conventions multiple alternative version of the interfaced Fortran procedures are present, to account for the different input variable combinations; the EDIpack2jl wrapper functions take care of selecting the appropriate Fortran procedure depending on the set of input parameters provided by the user.
 
@@
 
-At present, the EDIpack Julia interface is not offered as a package. The git repository has to be cloned via
+At present, the \NAME Julia interface is not offered as a package. The git repository has to be cloned via
 
 \begin{lstlisting}[style=mybash]
-git clone https://github.com/EDIpack/EDIjl2.0.git
+git clone https://github.com/EDIpack/EDIpack2jl.git
 \end{lstlisting}
@@
 
-The EDIjl2 module can then be loaded via
+The EDIpack2jl module can then be loaded via
 
 \begin{lstlisting}[style=mybash]
-using EDIjl2
+using EDIpack2jl
 \end{lstlisting}
@@
 \begin{lstlisting}[style=mybash]
-EDIjl2.read_input("inputED.conf")
-ed = EDIjl2.global_env
+EDIpack2jl.read_input("inputED.conf")
+ed = EDIpack2jl.global_env
 println("Nspin = ", ed.Nspin)
@@
 
-We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIjl2.0 repository.
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIpack2jl repository.
 This script is intended to be run serially.

### 2025-05-21 05_examples.tex
Fixing EDIpack and packages names in the paper: EDIpack EDIpack2ineq ----> libedipack.a EDIpack_C ----> libedipack_cbindings.so EDIpack2py EDIpack2jl EDIpack2Triqs EDIpack-Conda
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

--- 2025-05-21 05_examples.tex
@@
 program ed_hm_bethe
-   USE EDIPACK2
+   USE EDIPACK
    USE SCIFOR
@@
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-#include <edipack2_cbinding.h>
+#include <edipack_cbindings.h>
 using namespace std;
@@
 
-\begin{figure}%[t!]
-  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
-    \caption{\label{figEx1W}%
-        }
-\end{figure}
-
-\subsubsection{Finite temperature solution (W2Dynamics interface)}\label{SecExamplesBetheDMFTw2d}
-To demonstrate use of the w2dynamics interface, here we briefly
-discuss how to solve the DMFT problem for the Bethe lattice using
-W2Dynamics interface. \fixme{For definitiness we compare the finite low
-temperature results obtained via the two solvers: ED and CTQMC.  }
-
-Unlike when the Fortran API is used, none of the
-five steps of the iterative algorithm listed there are left to the
-user to implement themselves. Instead, in addition to possibly
-non-default values for \NAME input variables, the model specification
-must also be added to a w2dynamics parameter file and depending on the
-model, further input files might need to be provided. Further
-differences are that initialization is performed in w2dynamics by
-starting from a self-energy of zero or reading a self-energy value
-from an old file, which results in the initial Weiss field that the
-initial bath parameters are fitted to, and that automatic convergence
-checking is not currently available. Finally, using the same settings
-as for the Fortran example we arrive at the w2dynamics parameter file
-shown in the following listing.
-
-\begin{lstlisting}[style=fstyle,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
+\subsubsection{Finite temperature solution (w2dynamics interface)}\label{SecExamplesBetheDMFTw2d}
+To demonstrate the usage of the w2dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
+In order to showcase the capabilities of \NAME to address low-temperature problems we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in w2dynamics against the \NAME solver at finite temperature.
+
+In contrast to the \NAME API that only enables access to the impurity solver and bath optimization procedures, but requires the user to implement (using different methods) the DMFT algorithm themselves, the standard way to use w2dynamics is fundamentally different: a single Python script {\tt DMFT.py} is provided that takes care of the whole DMFT calculation via dedicated classes to implement generic self-consistency.
+The w2dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
+Further information about the functioning of w2dynamics can be found in Ref.~\onlinecite{Wallerberger2019CPC}
+
+Another important difference concerns the initial point of the iterative DMFT solution algorithm: while \NAME starts from a given discrete bath, w2dynamics is initialized with a zero self-energy function or alternatively reads this quantity from a converged solution file.
+When using the \NAME ED interface, the initial Weiss field is determined using self-consistency and finally an initial discrete bath is obtained through the \NAME bath optimization procedure.
+
+The w2dynamics configuration file for the solution of the Bethe lattice problem at finite temperature reads: 
+\begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
 [General]
@@
 NAt             = 1               # number of impurities
-beta            = 1000            # inverse temperature, defines Matsubara grid spacing
+beta            = 100             # inverse temperature
 mu              = 1.0             # chemical potential set to achieve half-filling
@@
 mixing_strategy = linear          # linear mixing as in the Fortran example
-solver          = EDIPACK         # use EDIpack2 as impurity solver, not default CTHYB
+FTType          = none            # (for CT-HYB): use the NFFT-measured G
+solver          = EDIPACK         # use EDIpack as impurity solver, not default CTHYB
 
@@
 
-[QMC]                             # Parameters for some grid sizes are part of this section
-Ntau            = 1024            # imaginary time grid size
-Niw             = 4096            # number of positive Matsubara frequencies
-
-[EDIPACK]                         # further non-default parameters, also taken from Fortran example
+[EDIPACK]                         # further ED parameters, as in the Fortran example
 NBATH           = 7               # number of bath sites
@@
 CG_NITER        = 2048            # maximum number of conjugate-gradient iterations
-\end{lstlisting}
-
-With this parameter file, we can use the {\tt DMFT.py} script of
-w2dynamics to perform the execution and find the results in form of
-both a typical w2dynamics HDF5 output file whose name starts with {\tt
-  bethe\textunderscore{}dmft\textunderscore{}U2} and a number of folders whose names start with the
-name of the HDF5 output file that contain unavoidable or explicitly
-requested \NAME input and output files for each individual DMFT
-iteration. We can extract results from the HDF5 output file e.g. using
-the {\tt hgrep} script of w2dynamics. The following listing shows how
-to perform a calculation with 10 parallel MPI processes and print the
-impurity self-energy result of the last DMFT iteration to the terminal
-assuming that the parameter file is {\tt bethe\textunderscore{}dmft.in} in the working
-directory and w2dynamics installed to {\tt /opt/w2dynamics}.
-
-\begin{lstlisting}[style=mybash]
+ED_FINITE_TEMP  = True            # at finite temperature T = 1/beta
+
+[QMC]                             # Parameters for some grid sizes and the CT-HYB calculation
+Ntau            = 1024            # imaginary time grid size
+Niw             = 4096            # number of positive Matsubara frequencies
+# parameters only relevant for CT-HYB follow
+MeasGiw         = 1               # enable NFFT measurement of G
+NCorr           = 175             # estimate of the autocorrelation length
+Nmeas           = 200000          # number of measurements / sample size
+Nwarmups        = 1000000         # number of initial warmup steps for Markov chain thermalization
+\end{lstlisting}
+Assuming that w2dynamics is installed to {\tt /opt/w2dynamics} and the preceding parameters file saved as {\tt bethe\textunderscore{}dmft.in}, we can start the calculation by running the {\tt DMFT.py} script:
+\begin{lstlisting}[style=mybash,numbers=none]
 mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
-python /opt/w2dynamics/hgrep latest siw-full -1
-\end{lstlisting}
+\end{lstlisting}
+
+The results are collected into an HDF5 archive in the usual w2dynamics format, including output quantities inherited from \NAME.
+Results can be viewed using the script {\tt hgrep} provided with w2dynamics or with other HDF5 tools.
+In this example we extract the Matsubara self-energy function $\Sigma(i\omega_n)$ for the last DMFT iteration:
+\begin{lstlisting}[style=mybash,numbers=none]
+/opt/w2dynamics/hgrep latest siw-full -1
+\end{lstlisting}
+
+\begin{figure}%[t!]
+  \includegraphics[width=\linewidth]{figures/figBetheW2D.pdf}
+    \caption{\label{figEx1W}%
+    \textbf{Finite temperature DMFT solution.}
+    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and Self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT.
+Data are for $T/D=0.01$ and $U/D=2.0$.
+CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
+        }
+\end{figure}
+
+In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC solver in w2dynamics and using the \NAME ED method both as a solver in w2dynamics and with a program using the Fortran API directly as shown in the previous subsection.
+Using DMFT, we solve the Hubbard model on a Bethe lattice for $T/D=0.01$ and $U/D=2.00$, corresponding to a correlated metallic state.
+In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ (note that w2dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver).
+In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$.
+The results obtained from the three calculations are in this case nearly identical already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics.
 
@@
 E_0\rangle=\langle E_z\rangle=0$. 
-Unlike the static mean-field description~\cite{Blason2021}, the
+Unlike the static mean-field description~\cite{Blason}, the
 transition from the QSHI topological state to the Excitonic Insulator 

### 2025-05-21 edipack2.tex
Fixing EDIpack and packages names in the paper: EDIpack EDIpack2ineq ----> libedipack.a EDIpack_C ----> libedipack_cbindings.so EDIpack2py EDIpack2jl EDIpack2Triqs EDIpack-Conda
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 
-\title{EDIpack 2.0: A generic and interoperable Lanczos-based solver for quantum impurity problems}
+\title{EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems}
 \author[a,b,c]{L.~Crippa*}
@@
 {\color{red} Tentative conclusions}
-We have presented EDIpack2, a versatile, high-performance solver for
+We have presented \NAME{}, a versatile, high-performance solver for
 generic quantum impurity problems. Leveraging on the massively
@@
 
-A central feature of EDIpack2 is its strong focus on interoperability,
+A central feature of \NAME is its strong focus on interoperability,
 achieved through modern Fortran constructs, C/C++-bindings, and
@@
 
-We thoroughly discussed the implementation of the EDIpack2 library, the
+We thoroughly discussed the implementation of the \NAME library, the
 most important algorithms and classes. We presented in
@@
 capabilities beyond the realm of the library itself.   
-Finally, we showcased the use of the EDIpack2 software in different
+Finally, we showcased the use of the \NAME software in different
 contexts via elaborated example which can serve as reference for the
@@
 
-The modular and extensible design of EDIpack2 provides a
+The modular and extensible design of \NAME provides a
 natural foundation for future extensions, for instance to cluster-DMFT where the
@@
 order, and complex spin textures in strongly correlated systems.
-We anticipate that EDIpack2 will become a valuable tool for the
+We anticipate that \NAME will become a valuable tool for the
 computational condensed matter community, supporting a wide range of

### 2025-05-22 edipack2_examples/W2Dynamics2EDIpack/script_figBetheW2D.py
Updated Fig Bethe+W2Dyn at T>0

@@ -23,7 +23,7 @@ def zimS(x,z):
 plt.rcParams["font.family"] = "Times"
 plt.rcParams['text.usetex'] = True
 plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
-plt.rcParams.update({'font.size': 24})
+plt.rcParams.update({'font.size': 28})
 plt.rcParams['figure.figsize'] = [35, 10]
 
 
@@ -35,8 +35,8 @@ axs = plt.figure(layout="constrained").subplot_mosaic(
 )
 
 
-axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
-axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["A"].text(0.01, 0.98, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.01, 0.98, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
 
 
 
@@ -54,8 +54,6 @@ ax.set_xlim([0, 2])
 ax.set_ylim([-2,0])
 ax.set_xlabel(r'$\omega_n$')
 ax.set_ylabel(r'${\rm Im}G(i\omega_n)$')
-# ax.yaxis.set_tick_params(labelleft=False)
-# ax.set_yticks([])
 
 ax.tick_params(length=6, width=2,direction='out')
 #ax.yaxis.grid(True, which='both', alpha=0.5)
@@ -63,10 +61,10 @@ ax.tick_params(length=6, width=2,direction='out')
 
 lw=5
 
-ax.plot(x3,  y3, lw=lw, ls='solid',  c='black', marker='s', markersize=25, label=r"EDIpack", alpha=0.75)
-ax.plot(x1,  y1, lw=lw, ls='',  c='red', marker='o', markersize=20, label=r"W2Dynamics CT-HYB", alpha=1.0, fillstyle='none', markeredgewidth=3)
-ax.plot(x2,  y2, lw=lw, ls='',  c='green'  , marker='x', markersize=20, label=r"W2Dynamics EDIpack", alpha=1.0, fillstyle='none', markeredgewidth=3)
 
[…]

### 2025-05-22 02_install.tex

@@
 modules, wraps the \NAME software in both its single- and multi-impurity variants.
-A second dynamic library, {\tt libedipack\_cbinding.so}, together with the associated header
-file{\tt edipack2\_cbinding.h}, enables interoperability with other programming languages.
+A second dynamic library, {\tt libedipack\_cbindings.so}, together with the associated header
+file{\tt edipack\_cbindings.h}, enables interoperability with other programming languages.
 
@@
 \begin{itemize}
-\item{\bf EDIpack2.}
+\item{\bf EDIpack.}
   This module forms the foundation of the library, implementing the 
@@
   with different sections of the library communicating through a shared 
-  memory layer. The top-level module, {\tt EDIPACK2}, provides access 
+  memory layer. The top-level module, {\tt EDIPACK}, provides access 
   to the core Fortran API, exposing key procedures for initialization, 
@@
 
-\item{\bf EDIpack2 C-bindings.}
+\item{\bf EDIpack C-bindings.}
   For enhanced interoperability, \NAME includes a dedicated module 
@@
 \begin{lstlisting}[style=mybash]
-git clone https://github.com/edipack/EDIpack2.0 EDIpack2
+git clone https://github.com/edipack/EDIpack 
 \end{lstlisting}
@@
   \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack2/TAG/PLAT/BRANCH\\
+  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack/TAG/PLAT/BRANCH\\
   -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
@@
 conda activate edipack
-conda install -c conda-forge -c edipack edipack2
+conda install -c conda-forge -c edipack edipack
 \end{lstlisting}

### 2025-05-22 03_edipack2.tex

@@
 program test
-  !Load EDIpack2 library 
-  USE EDIPACK2 
+  !Load EDIpack library 
+  USE EDIPACK
   !Load the Inequivalent impurities extension

### 2025-05-22 05_examples.tex
Updates from Overleaf

@@
 CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
+\fixme{Are we sure we want to use these
+    fancy markers?
+As I saw the earlier version, I know what they are doing and I understand that all data coincide perfectly and how this can make for a fancy plot.
+But I suspect that looking at it without any prior knowledge, at a glance, I would just desume that the w2d and edipack calculations are not matching.
+I would probably just go with the usual "x", "." and "+" markers, that all together make for a fancy multicolor "*".
+The dot in front of everything, with the most fluo color (e.g.
+bright green).
+The "x" and "+" in complementary colors, like blue and red, not in fluo version, so that they do not "hide" the dot.
+Something like that.}
         }
@@
 The main effect of the interaction is enclosed in the renormalized
-mass term $M_{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
+mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
 real-part of the self-energy being proportional to $\Gamma_{03}$
@@
 \begin{equation} \label{eqex:H_Holstein}
-    H_{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
+    H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
     b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma}
@@
 \begin{equation}\label{HlikeAttraction}
-    H_{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
+    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
 \end{equation}

### 2025-05-22 05_examples.tex
Added SciPost Physics Codebased (SPC) format to edipack_sp.tex Moved conclusions, acknowledgements and appendix to 06_....tex file.
SPC compiles: 55pages
CPC compiles: 49pages

--- 2025-05-21 05_examples.tex
@@
 In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
-enters in a Bipolaronic Insulating phase~\citep{Capone2006PRB} for our
+enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
 choice of the coupling.

### 2025-05-22 06_conclusions_acknowledgement_appendix.tex
Added SciPost Physics Codebased (SPC) format to edipack_sp.tex Moved conclusions, acknowledgements and appendix to 06_....tex file.
SPC compiles: 55pages
CPC compiles: 49pages

--- 2025-05-21 edipack2.tex
@@
-%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or
-%% 5p,twocolumn, preprint, review
-\documentclass[preprint,3p,10pt]{elsarticle}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage[english]{babel}
-\usepackage{amsmath,amssymb,amsfonts,amsthm}
-\usepackage{makecell}
-\usepackage{array}
-\usepackage{stackengine}
-\newlength\llength
-\llength=1.38ex\relax
-\usepackage[dvipsnames]{xcolor}
-\usepackage{makecell}
-\usepackage{subfiles}
-\usepackage{comment}
-\newcommand{\fixme}[1]{{\color{BrickRed} #1}}
-\usepackage{xspace}
-
-%% natbib.sty is loaded by default. natbib options with \biboptions{...}
-\biboptions{sort&compress,super}
-
-% Hypelinks in the document; settings
-\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
-% \usepackage[normalem]{ulem}
-
-\usepackage{listings}
-\lstdefinestyle{fstyle}{
-  frame=lines,
-  language=fortran,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{mypython}{
-  frame=lines,
-  language=python,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\definecolor{mymauve}{rgb}{0.58, 0, 0.82}
-\lstdefinestyle{mybash}{
-  frame=lines,
-  language=bash,
-  basicstyle=\footnotesize,
-  captionpos=b,
-  stringstyle=\color{mymauve},%\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\bfseries,
-  % It would be nice to have 'conda' here,
-  % but then 'conda-forge' gets highlighted too.
-  morekeywords={*,git,mkdir,cmake,make,pip},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-\lstdefinestyle{cstyle}{
-  frame=lines,
-  language=c,
-  basicstyle=\footnotesize,
-  stringstyle=\ttfamily,
-  commentstyle=\itshape,
-  fontadjust=true,
-  keywordstyle=\color{red},
-  % morekeywords={*,...},
-  mathescape,
-  numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=3pt
-}
-
-% % MINTED:
-% % \usepackage[cache=true,cachedir=minted-cache]{minted}
-% % \usepackage[finalizecache=true,cachedir=minted-cache]{minted}
-% \usepackage[frozencache=true,cachedir=minted-cache]{minted}
-% \setminted[fortran]{linenos,mathescape,frame=lines,style=bw,framesep=1mm,
-%   baselinestretch=1,fontsize=\footnotesize}
-
-\usepackage{array}
-\usepackage{tabularx}
-\usepackage{ltablex}
-
-\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-\renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
-\newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{D}[1]{>{\it\footnotesize\raggedright\arraybackslash}p{#1}}
-\newcolumntype{M}[1]{>{\scriptsize\raggedright\arraybackslash}p{#1}}
-
-\newcommand{\onlinecite}[1]{\nocite{#1}\!\!\!\citenum{#1}}
-
-\newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
-\newcommand {\aac}[1]{{\color{red} [{\bf AA}: \bf #1]}}
-\newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
-
-\usepackage[inline]{showlabels}
-
-%Reference to a given labelled equation
-%and definition of a bib. element.
-%-------------------------------------------
-\newcommand{\equ}[1]
-{Eq.\,(\ref{#1})}
-
-\newcommand{\figu}[1]
-{Fig.\,\ref{#1}}
-
-\newcommand{\secu}[1]
-{Sec.\,\ref{#1}}
-
-\newcommand{\ket}[1]
-{|#1\rangle}
-
-\newcommand{\bra}[1]
-{\langle #1|}
-
-\newcommand{\sgn}
-{\mathop{\mathrm{sgn}}}
-
-%SIMBOLI VARI
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
-\def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
-\def\e{\varepsilon}  \def\z{\zeta}   \def\h{\eta}     \def\th{\theta}
-\def\k{\kappa}       \def\l{\lambda} \def\m{\mu}      \def\n{\nu}
-\def\x{\xi}          \def\p{\pi}     \def\r{\rho}     \def\s{\sigma}
-\def\t{\tau}         \def\f{\varphi} \def\ph{\varphi} \def\c{\chi}
-\def\ps{\pi}        \def\y{\upsilon}\def\o{\omega}   \def\si{\varsigma}
-\def\G{\Gamma}       \def\D{\Delta}  \def\Th{\Theta}  \def\L{\Lambda}
-\def\X{\Xi}          \def\P{\Pi}     \def\Si{\Sigma}  \def\F{\Phi}
-\def\Ps{\Psi}        \def\O{\Omega}  \def\Y{\Upsilon} \def\lg{\langle}
-
-\def\PP{{\cal P}}\def\EE{{\cal E}}\def\MM{{\cal M}} \def\VV{{\cal V}}
-\def\CC{{\cal C}}\def\FF{{\cal F}}\def\HH{{\cal H}}\def\WW{{\cal W}}
-\def\TT{{\cal T}}\def\NN{{\cal N}}\def\BB{{\cal B}} \def\II{{\cal I}}
-\def\RR{{\cal R}}\def\LL{{\cal L}}\def\JJ{{\cal J}} \def\OO{{\cal O}}
-\def\DD{{\cal D}}
-\def\AA{{\cal A}}
-\def\GG{{\cal G}} \def\SS{{\cal S}}
-\def\ZZ{{\cal Z}} \def\UU{{\cal U}}
-\def\SB{{\cal S}{\cal B}}
-\def\aa{{\V \a}}
-\def\hh{{\V h}}\def\HHH{{\V H}}
-%\def\AA{{\V A}}
-%\def\GG{{\V G}}\def\BB{{\V B}}\def\aaa{{\V a}}\def\bbb{{\V b}}
-\def\nn{{\V \n}}\def\pp{{\V p}}\def\mm{{\V m}}\def\qq{{\bf q}}
-\def\RRR{\mathbb{R}} \def\CCC{\mathbb{C}} \def\NNN{\mathbb{N}}
-\def\ZZZ{\mathbb{Z}}
-%\def\TTT{\hbox{\msytw T}}
-
-\def\ul{\underline}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}}
-\def\lft{\left} \def\rgt{\right} \def\dpr{\partial} \def\der{{\rm d}}
-\def\us{\underline \s} \def\ue{{\underline \e}}
-\def\la{\left\langle}
-\def\ra{\right\rangle}
-\def\qed{\raise1pt\hbox{\vrule height5pt width5pt depth0pt}}
-\def\iome{i\omega_n} \def\iom{i\omega} \def\iom#1{i\omega_{#1}}
-\def\iomn{i\omega_n}
-\def\epsk{\epsilon({\bf k})} \def\Ga{\Gamma_{\alpha}}
-\def\Seff{S_{eff}}  \def\dinf{$d\rightarrow\infty\,$}
-\def\cG0{{\cal G}_0}
-\def\cG{{\cal G}}  \def\cU{{\cal U}}  \def\cS{{\cal S}}
-\def\spinup{\uparrow} \def\spindown{\downarrow} \def\spindw{\downarrow}
-\def\up{\uparrow} \def\down{\downarrow} \def\dw{\downarrow}
-
-\def\Ak{{\bf A}} \def\Akt{{\bf A}(t)} \def\Ek{{\mathbf E}}
-% \def\Im{\mbox{Im}}
-\def\=={\equiv}
-\def\defi{{\buildrel def \over =}} \def\nt{\widetilde{n}}
-\def\Im{{\rm Im}} \def\Re{{\rm Re}} \def\Tr{{\rm Tr}}
-\def\det{{\rm det}\,}
-
-\def\ibra{\langle}
-\def\iket{\rangle}
-
-\def\ka{{\bf k}}
-\def\vk{{\bf k}}
-\def\qa{{\bf q}}
-\def\vQ{{\bf Q}}
-\def\vr{{\bf r}}
-\def\q{{\bf q}}
-\def\R{{\bf R}}
-\def\vR{{\bf R}}
-\def\kx{{ k_x}}
-\def\ia{{\bf i}}
-\def\ja{{\bf j}}
-
-\usepackage{bbold}
-\def\11{\mathbb{1}}
-\def\00{\mathbf{0}}
-\def\NAME{{\rm EDIpack}\xspace}
-\newcommand{\shortrightarrow}{\mathrel{\mkern3mu\rightarrow\mkern}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Computer Physics Communications}
-
+\documentclass[edipack2.tex]{subfiles}
 \begin{document}
-
-\begin{frontmatter}
-
-\title{EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems}
-\author[a,b,c]{L.~Crippa*}
-\author[a]{I.~Krivenko*}
-\author[d]{S.~Giuli*}
-\author[d]{G.~Bellomia*}
-\author[c]{A.~Kowalski}
-\author[e]{F.~Petocchi}
-\author[f]{M.~Wallerberger}
-\author[g]{G.~Mazza}
-\author[h]{L.~de Medici}
-\author[c,b]{G.~Sangiovanni}
-\author[d,i]{M.~Capone*}
-\author[i]{A.~Amaricci*}
-% \author[]{A.~Scazzola}
-
-% \cortext[author] {Corresponding author.\\\textit{E-mail address:} amaricci@iom.cnr.it}
-\newcommand{\CNRIOM}{CNR-IOM, Istituto Officina dei Materiali,
-  Consiglio Nazionale delle Ricerche, Via Bonomea 265, 34136
-  Trieste, Italy}
-\newcommand{\SISSA}{Scuola Internazionale Superiore di Studi Avanzati (SISSA),
-  Via Bonomea 265, 34136 Trieste, Italy}
-\newcommand{\ITPHamburg}{I. Institute of Theoretical Physics,
-  University of Hamburg, Notkestrasse 9, 22607 Hamburg, Germany}
-\newcommand{\WZBURG}{Institut f\"ur Theoretische Physik und
-  Astrophysik,Universit\"at W\"urzburg, 97074 W\"urzburg, Germany}
-\newcommand{\CTQMAT}{W\"urzburg-Dresden Cluster of Excellence ct.qmat, 01062 Dresden, Germany}
-\newcommand{\Geneve}{Department of Quantum Matter Physics, University of
-  Geneva, Quai Ernest-Ansermet 24, 1211 Geneva, Switzerland}
-\newcommand{\UPISA}{Department of Physics ``E. Fermi'' University of
-  Pisa, Largo B. Pontecorvo 3, 56127 Pisa, Italy}
-\newcommand{\ESPCI}{LPEM, ESPCI Paris, PSL Research University, CNRS, Sorbonne Universit\'e, 75005 Paris, France}
-\newcommand{\TUW}{Institure of Solid State Physics, TU Wien, 1040 Vienna, Austria}
-
-\address[a]{\ITPHamburg}
-\address[b]{\CTQMAT}
-\address[c]{\WZBURG}
-\address[d]{\SISSA}
-\address[e]{\Geneve}
-\address[f]{\TUW}
-\address[g]{\UPISA}
-\address[h]{\ESPCI}
-\address[i]{\CNRIOM}
-% \address[]{Politecnico di Torino, Turin, Italy}
-\cortext[1]{Corresponding authors}
-% \cortext[*] {Corresponding author:giuli@sissa.it}
-% \cortext[*]{Corresponding author:bellomia@sissa.it}
-
-\begin{abstract}
-
-\end{abstract}
-
-\begin{keyword}
-  %% keywords here, in the form: keyword \sep keyword
-  Exact Diagonalization \sep
-  Quantum Impurity Models\sep  
-  Strongly Correlated Electrons \sep  
-  Dynamical Mean-Field Theory
-\end{keyword}
-
-\end{frontmatter}
-
-% Computer program descriptions should contain the following
-% PROGRAM SUMMARY.
-\noindent
-{\bf PROGRAM SUMMARY}
-\begin{small}
-  \noindent
-  \\
-  {\em Program Title:}  EDIpack                                        \\
-  {\em Licensing provisions:} GPLv3\\
-  {\em Programming language:}  Fortran, Python, C/C++\\
-  {\em Classification:} 6.5, 7.4, 20 \\
-  {\em Required dependencies:} CMake ($>=3.10.0$), Scifortran, MPI\\
-  {\em Nature of problem:}. \\
-  {\em Solution method:} .\\
-\end{small}
-
-\tableofcontents
-
-\subfile{01_intro.tex}
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\subfile{02_install.tex}
-
-% ##################################################################
-% ##################################################################
-% ##################################################################
-
-\subfile{03_edipack2.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subfile{04_cbinding.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subfile{05_examples.tex}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-%% References with bibTeX database:
-% \section*{References}
-\bibliographystyle{elsarticle-num}
-\bibliography{references}
-
 \end{document}

### 2025-05-22 05_examples.tex
Updates from Overleaf

--- 2025-05-22 05_examples.tex
@@
 CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
-\fixme{Are we sure we want to use these
-    fancy markers?
+    % \fixme{Are we sure we want to use these
+    % fancy markers?
 As I saw the earlier version, I know what they are doing and I understand that all data coincide perfectly and how this can make for a fancy plot.

### 2025-05-22 02_install.tex
GB pass
- fix a few typos and minor things
- move Holstein example after the Attractive Hubbard example (I feel like clustering the superc example is a nice idea).

Currently deciding if I will add a Edipack2ineq example (as we never give any example for using that module). Probably some nonsu2 stuff with the KMH model, so it fits well just after the BHZ excitons. We might want also a Julia API example, but I'm really not in the mood to install the Julia runtime and start tinkering with it.

@@
 The software builds into two distinct libraries.
-The main one is a static Fortran library calledc{\tt  libedipack.a} which, alongside the compiled
+The main one is a static Fortran library called {\tt  libedipack.a} which, alongside the compiled
 modules, wraps the \NAME software in both its single- and multi-impurity variants.

### 2025-05-22 03_edipack2.tex
Added SciPost Physics Codebased (SPC) format to edipack_sp.tex Moved conclusions, acknowledgements and appendix to 06_....tex file.
SPC compiles: 55pages
CPC compiles: 49pages
GB pass
- fix a few typos and minor things
- move Holstein example after the Attractive Hubbard example (I feel like clustering the superc example is a nice idea).

Currently deciding if I will add a Edipack2ineq example (as we never give any example for using that module). Probably some nonsu2 stuff with the KMH model, so it fits well just after the BHZ excitons. We might want also a Julia API example, but I'm really no

@@
   \hat{H}^0_\mathrm{imp}  =
-  \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}\\
+  \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}
 \end{equation}
@@
 
-\subsection{Interaction setup}
+\subsection{Interaction setup}\label{sSecIntSetup}
 The \NAME code offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}. 
@@
 % replacement of the pure state average %%> What is a pure state average?
-introduction of a thermal or degenerate 
+introduction of an
 ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 

### 2025-05-22 05_examples.tex
GB pass
- fix a few typos and minor things
- move Holstein example after the Attractive Hubbard example (I feel like clustering the superc example is a nice idea).

Currently deciding if I will add a Edipack2ineq example (as we never give any example for using that module). Probably some nonsu2 stuff with the KMH model, so it fits well just after the BHZ excitons. We might want also a Julia API example, but I'm really not in the mood to install the Julia runtime and start tinkering with it.

@@
 
-  \item[{\tiny $\triangleright$}] Optimize the bath parameters $\vec{x}$ against the updated
+  \item[{\tiny $\blacktriangleright$}] Optimize the bath parameters $\vec{x}$ against the updated
     Weiss field,  potentially using the conjugate gradient procedures 
@@
 $$
-Z=(1-\tfrac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow
-    0}})^{-1}.
+Z=\left(1-\frac{\partial\Re\Sigma}{\partial\omega}\Biggr|_{\omega\rightarrow
+    0}\right)^{-1}.
 $$
@@
 $$
-   \frac{\Im\Sigma(i\omega_n)}{\omega_n}_{|_{\omega_n\rightarrow 0}}=
+   \frac{\Im\Sigma(i\omega_n)}{\omega_n}\Biggr|_{\omega_n\rightarrow 0}=
    \frac{1}{\pi}\int_{\mathbb R}d\epsilon \frac{\Re\Sigma(\epsilon)}{\epsilon^2}=
-   \frac{\partial\Re\Sigma}{\partial\omega}_{|_{\omega\rightarrow 0}}.
+   \frac{\partial\Re\Sigma}{\partial\omega}\Biggr|_{\omega\rightarrow 0}.
 $$
@@
 Something like that.}
+    % NOW I LOVE IT :)
         }
@@
 import numpy as np
-from edipy2 import global_env as ed
+from edipack2py import global_env as ed
 import mpi4py
@@
 
+\subsection{Holstein model on the Bethe lattice (Fortran API, {\tt electron-phonons})}
+One of the features introduced in \NAME is the possibility of treating
+local phonons in conjunction with the superconductive phase,
+i.e. \textbf{ed\_mode=superc}. 
+In this example discuss  the normal and
+superconductive solution of the pure Holstein model on the Bethe
+lattice within DMFT.
+We stress that, using Fortran API, the code
+implementation for this specific case is essentially identical to the listing reported in the sections
+\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
+\ref{SecExamplesAHM} ({\tt ed\_mode=superc}).
+
+So we consider the model introduced in \secu{SecExamplesBetheDMFT}
+with $U=0$ and the additional phononic and electron-phonon terms:
+\begin{equation} \label{eqex:H_Holstein}
+    H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
+    b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma}
+    -\frac{1}{2})\Big]. 
+\end{equation}
+We consider the half-filling regime of the particle-hole symmetric
+Bethe lattice density of states. We set the half-bandwidth as our
+energy unit $D=1$ and introduced the electron-phonon coupling $\lambda
+= \tfrac{2g^2}{\omega_0D}$.  
+The iterative DMFT solution algorithm follows the same principles
+illustrated in the previous sections.
+
+\paragraph{Results}
+In the following we discuss the adiabatic ($\omega_0\to0$) to
+anti-adiabatic ($\omega_0\to\infty$) crossover for
+the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
+
+In the anti-adiabatic limit, the Holstein interaction takes a
+particularly simple form:
+\begin{equation}\label{HlikeAttraction}
+    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
+\end{equation}
+which describes a local Hubbard-like attraction among electrons
+(mediated by local phonons).
+In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
+enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
+choice of the coupling.
+
+We characterize the model solution by showin the evolution of the
+double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
+phonon frequency $\omega_0$, see panel (A). In this panel we compare
+the behavior for {\tt ed\_mode=normal} against the superconductive
+solution ({\tt ed\_mode=superc}). Our results capture the whole
+crossover from adiabatic to anti-adiabatic regime. In the former
+regime, the double occupation takes a similar value for the two
+phases. However, approaching the anti-adiabatic regime, the two
+solutions reach the limiting values corresponding to the residual
+attraction \equ{HlikeAttraction}.   
+To better characterize the nature of the superconducting
+phase in the Holstein model we report the evolution of the anomalous order
+parameter $\phi$ in the adiabatic to anti-adiabatc crossover.
+The DMFT results obtained with \NAME show the rapid increase of the
+superconducting order parameter as phonon frequency grows
+large. Finally, in the anti-adiabatic regime $\phi$ saturates to a
+finite value corresponding to the attractive Hubbard-like interaction
+of strenght $\lambda/2$.
+
+\begin{figure}[ht!]
+    \includegraphics[width=\linewidth]{figures/figBethe_Holstein.pdf}
+    \caption{\label{figEx5}
+      Evolution of the  double occupation (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
+The horizontal broken line are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
+\end{figure}
+
 \begin{figure}[t!]
@@
 
-\subsection{Multi-orbital quantum impurity with Hubbard-Kanamori
+\subsection{Multi-orbital impurity with Kanamori
   interaction (TRIQS interface)}
@@
 
-The third example demonstrates how to use the edipack2triqs compatibility
+We proceed to demonstrate how to use the edipack2triqs compatibility
 layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
 3-orbital correlated impurity coupled to a few non-interacting bath sites.
-The interaction term of the impurity Hamiltonian has the Hubbard-Kanamori
+The interaction term of the impurity Hamiltonian is in the Hubbard-Kanamori
 form (\ref{Hint}).
@@
 implementation of the self-consistency conditions:
-$\GG^{-1}=G_{loc}^{-1}+\Sigma$, with: 
-$$
-G_{loc}(z) = \tfrac{1}{N_k}\sum_k \left[z+\mu-H(k)-\Sigma(z)
+$\GG^{-1}=G_\mathrm{loc}^{-1}+\Sigma$, with: 
+$$
+G_\mathrm{loc}(z) = \tfrac{1}{N_k}\sum_k \left[z+\mu-H(k)-\Sigma(z)
 \right]^{-1}, 
@@
 $$
-H_{top} = \sqrt{Z}[H(k) + \Re\Sigma(\omega\to0)]\sqrt{Z}, 
-$$
-where $Z$ is the renormalization constant. $H_{top}$ describes the
+H_\mathrm{top} = \sqrt{Z}[H(k) + \Re\Sigma(\omega\to0)]\sqrt{Z}, 
+$$
+where $Z$ is the renormalization constant. $H_\mathrm{top}$ describes the
 low-energy properties of many-body problem and can be used to obtain a 
@@
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
-   !> Set $H_{loc}$
+   !> Set $H_\mathrm{loc}$
    allocate(Hloc(Nso,Nso))
@@
 where we use the local non-interacting Hamiltonian 
-$H_{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
+$H_\mathrm{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
 $h^0_{\a\b\s\s'}$, i.e. the impurity Hamiltonian. To anticipate the
@@
      call ed_get_sigma(Smats,axis='mats')
-     !> Get $G_{loc}$ (assume to have a function for this task)
+     !> Get $G_\mathrm{loc}$ (assume to have a function for this task)
      call get_gloc(Hk,Gmats,Smats,axis='m')
-     !> Update the Weiss field $\GG^{-1}=G^{-1}_{loc}+\Sigma$ +  Linear mixing.
+     !> Update the Weiss field $\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma$ +  Linear mixing.
      call dmft_self_consistency(Gmats,Smats,Weiss)
@@
 function provided by \NAME solver. In panels (B)-(D) of \figu{figEx4}
-we report the spectral functions $-\Im{G}_{a,loc}(\omega)/\pi$ for
-$a=1,2$, $\sigma=\up$ and three distinct values of the interaction
+we report the spectral functions $-\Im{G}_{a\up,\mathrm{loc}}(\omega)/\pi$ for
+$a=1,2$, and three distinct values of the interaction
 $U$ placing the solution, respectively, in the QSHI, the EI and the MI.
@@
 
-\subsection{Holstein model on the Bethe lattice (Fortran API, {\tt electron-phonons})}
-One of the features introduced in \NAME is the possibility of treating
-local phonons in conjunction with the superconductive phase,
-i.e. \textbf{ed\_mode=superc}. 
-In this example discuss  the normal and
-superconductive solution of the pure Holstein model on the Bethe
-lattice within DMFT.
-We stress that, using Fortran API, the code
-implementation for this specific case is essentially identical to the listing reported in the sections
-\ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
-\ref{SecExamplesAHM} ({\tt ed\_mode=superc}).
-
-So we consider the model introduced in \secu{SecExamplesBetheDMFT}
-with $U=0$ and the additional phononic and electron-phonon terms:
-\begin{equation} \label{eqex:H_Holstein}
-    H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
-    b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma}
-    -\frac{1}{2})\Big]. 
-\end{equation}
-We consider the half-filling regime of the particle-hole symmetric
-Bethe lattice density of states. We set the half-bandwidth as our
-energy unit $D=1$ and introduced the electron-phonon coupling $\lambda
-= \tfrac{2g^2}{\omega_0D}$.  
-The iterative DMFT solution algorithm follows the same principles
-illustrated in the previous sections.
-
-\paragraph{Results}
-In the following we discuss the adiabatic ($\omega_0\to0$) to
-anti-adiabatic ($\omega_0\to\infty$) crossover for
-the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
-
-In the anti-adiabatic limit, the Holstein interaction takes a
-particularly simple form:
-\begin{equation}\label{HlikeAttraction}
-    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
-\end{equation}
-which describes a local Hubbard-like attraction among electrons
-(mediated by local phonons).
-In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
-enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
-choice of the coupling.
-
-We characterize the model solution by showin the evolution of the
-double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
-phonon frequency $\omega_0$, see panel (A). In this panel we compare
-the behavior for {\tt ed\_mode=normal} against the superconductive
-solution ({\tt ed\_mode=superc}). Our results capture the whole
-crossover from adiabatic to anti-adiabatic regime. In the former
-regime, the double occupation takes a similar value for the two
-phases. However, approaching the anti-adiabatic regime, the two
-solutions reach the limiting values corresponding to the residual
-attraction \equ{HlikeAttraction}.   
-To better characterize the nature of the superconducting
-phase in the Holstein model we report the evolution of the anomalous order
-parameter $\phi$ in the adiabatic to anti-adiabatc crossover.
-The DMFT results obtained with \NAME show the rapid increase of the
-superconducting order parameter as phonon frequency grows
-large. Finally, in the anti-adiabatic regime $\phi$ saturates to a
-finite value corresponding to the attractive Hubbard-like interaction
-of strenght $\lambda/2$.
-
-\begin{figure}[ht!]
-    \includegraphics[width=\linewidth]{figures/figBethe_Holstein.pdf}
-    \caption{\label{figEx5}
-      Evolution of the  double occupation (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
-The horizontal broken line are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
-\end{figure}
-
 \end{document}

### 2025-05-22 06_conclusions_acknowledgement_appendix.tex
GB pass
- fix a few typos and minor things
- move Holstein example after the Attractive Hubbard example (I feel like clustering the superc example is a nice idea).

Currently deciding if I will add a Edipack2ineq example (as we never give any example for using that module). Probably some nonsu2 stuff with the KMH model, so it fits well just after the BHZ excitons. We might want also a Julia API example, but I'm really not in the mood to install the Julia runtime and start tinkering with it.

@@
 We believe the discourse flow of this language is best captured by 
-illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G.Perozzi (P) (see
+illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
 \href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
@@
 \noindent
-V: Lei ha clacsonato?\\
-P: Tu ha clacsonato?\\
-M: Tarapia tapioco, prematurata l'interfaccia, o scherziamo?\\
-V: Prego?\\
-M: Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
+V: {\it Lei ha clacsonato?}\\
+P: {\it Tu ha clacsonato?}\\
+M: {\it Tarapia tapioco, prematurata l'interfaccia, o scherziamo?}\\
+V: {\it Prego}?\\
+M: {\it Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
 basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
@@
 sorgente {\tt hm\_bethe.mc}?  Come {\tt
-  https://github.com/lcrippa/prematurata\_la\_dmft}, per esempio?\\
-V: Ma che DMFT, mi faccia il piacere! Questi signori stavano
-programmano loro, non si intrometta!\\
-M: Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
+  github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}\\
+V: {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano
+programmano loro, non si intrometta!}\\
+M: {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
 funzioni? Lo vede che interfacciano gli array, non supportati da
@@
 \href{github.com/esseks/monicelli.git}{https://github.com/esseks/monicelli.git}
-e compila il file {\tt hm\_bethe.mc}, per esempio.\\
-V: Basta così! Mi seguano nel programma di test!\\
-P: No, no, no, attenzione! Il loop dmft completo \`e supportato
-secondo la Ref.~\cite{Georges1996RMP}, abbia pazienza,
+e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
+V: {\it Basta così! Mi seguano nel programma di test!}\\
+P: {\it No, no, no, attenzione! Il loop dmft completo \`e supportato
+secondo la Ref.~\onlinecite{Georges1996RMP}, abbia pazienza,
 senn\`o.... Plotta i dati, anche un pochino di Green's function e
-Self-energy in prefettura.\\
-M: Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.\\
-V: Ho bello che capito. Si farà finta di passar da bischeri!\\
+Self-energy in prefettura.}\\
+M: {\it Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.}\\
+V: {\it Ho bello che capito. Si farà finta di passar da bischeri!}\\
 

### 2025-05-23 03_edipack2.tex
Finally implemented the cg_norm part I updated accordingly the EDIpack code. We might want to further change the code, and so the description here, but I think for now this reads as honest and clear.

@@
 must include both the normal and anomalous components, 
-which can significantly alter the form of the self-energy.
+which can significantly alter the form of the self-energy. Similar issues arise in the {\bf nonsu2} case, where spin off-diagonal components usually drive the physics of the problem.
 
 \subsection{Bath Optimization}\label{sSecFit}
-In the DMFT framework, the bath parameters must be optimized to 
+In the DMFT-ED framework, the bath parameters must be optimized to 
 faithfully reproduce the Weiss field, 
@@
 Several algorithms have been proposed for this optimization 
-step~\cite{Garcia2004PRL,Taranto2012PRB}, each with strengths suited 
+step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto_Bath_ASCI-DMFT}, each with strengths suited 
 to different physical contexts. To maintain flexibility in \NAME, 
@@
 X^\mathrm{QIM}(i\omega_n; \{V, h\}) \right\|_q,
+\label{eq:chiq}
 \end{equation}
@@
 matrix function space. Here, $X_{\a\b} = {\GG_{0}}_{\a\b\s\s'}$ or 
-$\Theta_{\a\b\s\s'}$ are the user-supplied local functions, while 
+$\Theta_{\a\b\s\s'}$ are the user-supplied functions of the bath parameters, while 
 $X_{\a\b}^\mathrm{QIM} = G^0_{\a\b\s\s'}$ or 
-$\Delta_{\a\b\s\s'}$ are the corresponding functions for the quantum 
+$\Delta_{\a\b\s\s'}$ are the corresponding quantities for the quantum 
 impurity model, as defined in \secu{sSecFunc}.
@@
 Numerical Recipes~\cite{NumRec77}, and \texttt{1} for the original 
-algorithm described in Ref.\onlinecite{Georges1996RMP}, commonly used 
+algorithm described in Ref. \cite{Georges1996RMP}, commonly used 
 in the DMFT community.
@@
 to outliers.
+\item \texttt{cg\_norm=elemental,frobenius} - Sets the matrix norm to be used to define the cost function in \equ{eq:chiq}.
+The default value (\texttt{elemental}) corresponds to a generic element-wise $\chi^q$ norm, defined as
+\begin{equation*}
+    ||X-X^\mathrm{QIM}||_q \equiv {\sum_{ij} \left|X_{ij}-X^\mathrm{QIM}_{ij}\right|^q}.
+\end{equation*}
+The \texttt{frobenius} option implements instead the matrix distance induced by the Frobenius inner product as
+\begin{equation*}
+    ||X-X^\mathrm{QIM}||_q \equiv 
+    \sqrt[q]{\Tr\left[(X-X^\mathrm{QIM})^\dagger(X-X^\mathrm{QIM})\right]} =
+    \left(\sum_{ij} \left|X_{ij}-X^\mathrm{QIM}_{ij}\right|^2 \right)^{\!\!\!\frac{1}{q}}.
+\end{equation*}
+For $q=2$ (see \texttt{cg\_pow}) the Frobenius norm is equivalent
+to the Euclidean distance in matrix space. 
+%For $q\neq2$ we are implementing something that is not a matrix norm (better to not comment on it explicitly)
+We prospect to expand the choices for \texttt{cg\_norm} in future updates of \NAME, as the \textbf{nonsu2} and \textbf{superc}
+diagonalization modes entail nontrivial subtleties in optimizing 
+the off-diagonal components of $X$.
 \item \texttt{cg\_Ftol} - Controls the fit tolerance, setting the 
@@
 
-% In the DMFT context the bath needs to be optimized
-% against a given realization of the Weiss field
-% ${\GG^{-1}_{0}}_{\a\b\s\s'}(z)$, or the corresponding {\it hybridization} function
-% $\Theta = (z + \mu)\11 - H^{loc} -\GG_0^{-1}](z)$. While the Weiss
-% field is obtained from the DMFT self-consistency
-% equation~\cite{Georges1996RMP}, bath discretization impose to  find an optimal
-% description of the continuous Weiss field in terms of the finite
-% number of parameters of the bath (see \secu{sSecBath}.
-% Although different algorithms can be envisaged to perform this
-% step~\cite{Garcia2004PRL,Taranto2012PRB} which are perfectly valid in
-% some physical contexts.
-% In order to enable the users to use their preferred 
-% method in \NAME we keep the optimization implementation independent
-% from the rest of the code. Yet, we offer a fully fledged optimization
-% strategy based on the  conjugate gradient (CG) minimization of the cost function:
-% $$
-% \chi = \sum_{n=1}^{L_\mathrm{fit}}\frac{1}{W_n}||X(i\omega_n) - X^\mathrm{QIM}(i\omega_n;\{V,h\})||_q
-% $$
-% where the symbol $|| \cdot ||_q$ is a suitably defined $q$-norm in the
-% matrix function space, $X_{\a\b}={\GG_{0}}_{\a\b\s\s'},\,\Theta_{\a\b\s\s'}$ are the user
-% supplied local functions and
-% $X_{\a\b}^\mathrm{QIM}=G^0_{\a\b\s\s'},\,\Delta_{\a\b\s\s'}$ the
-% quantum impurity model functions, defined above.
-% Notably, more sophisticated optimization algorithms have been
-% recently implemented to better undertake the minimization of similar
-% cost functions. However, these developments are designed to work with truncated
-% algorithms, e.g. sCI or DMRG, describing systems with a larger number of
-% bath levels.   
-% In the ED context however, where the efficient and wise selection of
-% the relatively few bath levels becomes crucial, the CG minimization of
-% the local functions proved to be the most efficient and
-% flexible optimization scheme so far.
-
-% The fit procedure is entirely wrapped by the single function {\tt
-%   ed\_chi2\_fitgf} contained in the module \texttt{ED\_BATH\_FIT}.   
-% In order to exploit regularity of the functions the fit is 
-% performed using imaginary Matsubara frequency. 
-% The actual form of $X_{\a\b\s\s'}$ is controlled by the input parameter
-% \texttt{cg\_Scheme=Weiss,Delta}.
-
-% In order to fine tune the optimization step in \NAME\ we
-% introduced a number of control parameters. To start with, we include
-% two distinct CG algorithms in the library, controlled by the input variable
-% \texttt{cg\_method=0,1}. The value \texttt{0} corresponds to a
-% Fletcher-Reeves-Polak-Ribiere minimisation algorithm, adapted from
-% Numerical Recipes~\cite{NumRec77}. Yet, in order to guarantee
-% back-compatibility with respect to the past literature, we also provide the
-% possibility of using the minimization procedure published in
-% Ref.\onlinecite{Georges1996RMP} which has been largely used in the DMFT
-% community.
-
-% The gradient $\nabla\chi$ required by the CG algorithm can be
-% evaluated either analytically or numerically as
-% controlled by the value of the input parameter \texttt{cg\_grad=0,1}. For
-% \texttt{cg\_method=1} only numerical gradient can be used.
-% The number of Matsubara frequency $L_\mathrm{fit}$ used in the fit procedure
-% is controlled  by the input parameter \texttt{cg\_Lfit}.
-% This parameter can be used to restrict the fit to the low frequency
-% part as the large frequency tails of the local Matsubara functions
-% have universal behavior.
-% Similarly, the weight  $W_n=1,1/L_\mathrm{fit},1/\omega_n$ is used to
-% enhance the weight of low energy part with respect to the
-% intermediate-to-large energy one in the cost function.
-% This is controlled by the input parameter \texttt{cg\_Weight=0,1,2}.
-% Another  factor contributing to determine the behavior
-% of the fit is the power $q$ of the cost function $\chi$. By tuning
-% this parameter, controlled by input variable \texttt{cg\_pow}, it is
-% possible to enhance or suppress the differences in the $\chi$ in order
-% to improve (or simplify) the optimization procedure.
-
-% Finally, we introduced few additional parameters which aim to
-% control the quality of the fit. The first is the fit tolerance,
-% controlled by the input parameter \texttt{cg\_Ftol}, which
-% determines the convergence threshold of the minimization procedure.
-% The second is the maximum number of iterations \texttt{cg\_Niter}
-% allowed for the CG algorithm to determine the minimum.
-% The last parameter \texttt{cg\_stop=0,1,2} selects the exit
-% condition of the minimization procedure. We envisaged  three
-% possible conditions: $C_1\cup C_2$, $C_1$, $C_2$ with 
-% $C_1=|\chi^{n-1} -\chi^n|<\mathtt{cg\_Ftol}(1+\chi^n)$ and
-% $C_2=||x_{n-1} -x_n||<\mathtt{cg\_Ftol}(1+||x_n||)$, where $\chi^n$
-% is the cost function evaluated at the $n^{\rm th}$-step and $x_n$
-% the corresponding argument. Increasing the value of the stop
-% parameter generally loosens up the exit conditions of the minimization.
-
-{\bf REMARK TODO}
-Notes on the norm function: a) the definition for conventional
-matrices, ;b) the definition for the replica/general case where you
-can choose between different norm defition.
-\fixme{After careful inspection, I (GB) realize that the elemental norm 
-was never really ported from CDFMT-ED to EDIpack (there's no different
-matrix weight than all ones, which is the standard chi2, of course). 
-Hence the \texttt{cg\_norm} options is really not doing anything significant,
-as with "elemental" it gives the usual $\chi^2$ (or $\chi^q$, if you change the
-\texttt{cg\_pow}...) and for "Frobenius" it gives again the usual $\chi^2$,
-unless you put $q\neq2$, which gives an ill-defined matrix norm...
-(it mixes an effective $q=2$ coming from the matrix multiplication with 
-$q\neq2$ when you do the explicit $q$-root). I think we
-should just get rid of \texttt{cg\_norm} and do the traditional $\chi^q$, as 
-indeed we are already doing by default. Implemented like this, it is just random
-no-consequence code.}
-%GBtodo placeholder
-
 \subsection{Input/Output}\label{sSecIO}

### 2025-05-23 05_examples.tex
Finally implemented the cg_norm part I updated accordingly the EDIpack code. We might want to further change the code, and so the description here, but I think for now this reads as honest and clear.

@@
 In this section we illustrate the functioning of the \NAME
-library and their interfaces as solver for DMFT through specific examples, including
+library and their interfaces as solver for DMFT through a variety of examples, including
 discussion of relevant code snippets.

### 2025-05-23 03_edipack2.tex
Slight amend My bad, I misread and so misedited.

@@
 matrix function space. Here, $X_{\a\b} = {\GG_{0}}_{\a\b\s\s'}$ or 
-$\Theta_{\a\b\s\s'}$ are the user-supplied functions of the bath parameters, while 
+$\Theta_{\a\b\s\s'}$ are the user-supplied local functions, while 
 $X_{\a\b}^\mathrm{QIM} = G^0_{\a\b\s\s'}$ or 

### 2025-05-23 05_examples.tex
Intermediate Writing the KM example

@@
 
-\subsection{Hubbard model on the Bethe lattice (Fortran API)}\label{SecExamplesBetheDMFT}
+\subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
 The test bed for any DMFT application is conventionally considered 
@@
 
-\subsubsection{Finite temperature solution (w2dynamics interface)}\label{SecExamplesBetheDMFTw2d}
+\subsubsection{Finite temperature solution (w2dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTw2d}
 To demonstrate the usage of the w2dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
@@
 
-\subsection{Holstein model on the Bethe lattice (Fortran API, {\tt electron-phonons})}
+\subsection{Holstein model on the Bethe lattice (electron-phonon coupling)}
 One of the features introduced in \NAME is the possibility of treating
@@
 phase in the Holstein model we report the evolution of the anomalous order
-parameter $\phi$ in the adiabatic to anti-adiabatc crossover.
-The DMFT results obtained with \NAME show the rapid increase of the
+parameter $\phi$ in the adiabatic to anti-adiabatic crossover.
+The DMFT results obtained with \NAME show a rapid increase in the
 superconducting order parameter as phonon frequency grows
-large. Finally, in the anti-adiabatic regime $\phi$ saturates to a
+large. Finally, in the anti-adiabatic regime, $\phi$ saturates to a
 finite value corresponding to the attractive Hubbard-like interaction
-of strenght $\lambda/2$.
+of strength $\lambda/2$.
 
@@
     \caption{\label{figEx5}
-      Evolution of the  double occupation (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
-The horizontal broken line are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
+      Evolution of the double occupancy (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
+The horizontal broken lines are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
 \end{figure}
@@
 Thus, here we illustrate the DMFT solution of the excitonic phase as a way to
-illustrate the ability of \NAME to capture matter phases with broken
+illustrate the ability of \NAME to capture matter phases with lowered
 spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
@@
 transition from the QSHI topological state to the Excitonic Insulator 
-(EI) becomes of first-order in presence of quantum fluctuations
-corrections~\cite{Continentino,Paoletti} contained in DMFT. On the
+(EI) becomes of first-order in the presence of the dynamical fluctuations~\cite{Continentino,Paoletti,BellomiaKMH} contained in DMFT. On the
 other hand, the EI continuously evolves into a Mott Insulator (MI)
 for larger interaction (neglecting for simplicity any 
-anti-ferromagnetic ordering that would naturally occurr in this
+antiferromagnetic ordering that would naturally occur in this
 regime).
-In the same panel we report the evolution of 
+In the same panel, we report the evolution of 
 $\langle T_z\rangle$ to illustrate the progressive reduction of the
@@
 
+\subsection{Interacting Kane-Mele model (Fortran API, EDIpack2ineq layer)}
+
+To complete the overview of \NAME capabilities, we consider another
+model for interacting quantum spin-Hall insulators, defined on the honeycomb lattice, with two inequivalent sites in the unit-cell.
+
+Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit-cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
+\begin{align*}
+    \mathbf{H}_\mathrm{KM} = \sum_{{k}} \psi^\dagger_{{k}} \mathbf{H}({k}) \psi_{{k}},
+\end{align*}
+with $\psi_{{k}} = [c_{{k},\mathrm{A},\up},\,c_{{k},\mathrm{B},\up},\,c_{{k},\mathrm{A},\dw},\,c_{{k},\mathrm{B},\dw}]$ and
+    \begin{align}
+    \mathbf{H}({k}) 
+    &= x_{{k}}\Gamma_{01} + y_{{k}}\Gamma_{02} + \delta_{{k}}\Gamma_{33}, \label{eq:Hk_kanemele}\\[1mm]
+   x_{{k}}&=t\bigl[\cos({k}\cdot{u})+\cos({k}\cdot{v})+1\bigr],\nonumber\\
+   y_{{k}}&=t\bigl[\sin({k}\cdot{u})+\sin({k}\cdot{v})\bigr],\nonumber \\
+   \delta_{{k}}&=2\lambda_\mathrm{so}\bigl[\sin({k}\cdot{u})-\sin({k}\cdot{v}) - \sin({k}\cdot{u} -{k}\cdot{v})\bigr], \nonumber
+\end{align}
+where ${u} = (3/2, \sqrt{3}/2)$, and ${v} = (3/2, -\sqrt{3}/2)$
+are suitable basis vectors for the honeycomb lattice, $t$ is the
+nearest-neighbor hopping amplitude and $\lambda_\mathrm{so}$ is 
+the amplitude of a complex next-nearest-neighbor hopping amplitude,
+with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling and well-known to stabilize a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
+The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$, are 
+defined in terms of $\sigma_a$ and $\tau_\ell$ Pauli matrices, respectively 
+referred to spin and sublattice degrees of freedom, with the convention that 
+$\sigma_0$ and $\tau_0$ are $2\times2$ identity matrices.
+
+To investigate the effects of electron-electron repulsion on the
+Kane-Mele model we include a local interaction, 
+leading to the Kane-Mele-Hubbard Hamiltonian \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}
+\begin{equation}
+    \mathbf{H}_\mathrm{KMH} = \mathbf{H}_\mathrm{KM} 
+    + U\sum_{i}\Biggl[
+                        \left(n_{i,\up} - \frac{1}{2}\right)
+                        \left(n_{i,\dw} - \frac{1}{2}\right)
+                      \Biggr],
+    \label{eq:KMHmodel}
+\end{equation}
+where $n_{i,\sigma}=c^\dagger_{i,\sigma}c_{i,\sigma}$ are the 
+local spin-density operators. The interaction is written in an explicitly 
+particle-hole symmetric form so that the model is at half-filling for zero
+chemical potential.
+
+The essential features of the groundstate phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
+For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio
+\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
+at the Fermi level renders ineffective the logarithmic instability, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
+With a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.
+Furthermore, the long-range ordering
+eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization.
+\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRBa,Rachel2010PRB} and
+later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
+simulations \cite{Hohenadler2013ROPIP}.
+
+To treat the in-plane Néel ordering with \NAME, we can once again
+exploit the \texttt{ed\_mode=nonsu2} option, allowing off-diagonal 
+spin amplitudes in all dynamical matrices and so eventually in the
+resulting impurity self-energy.
+Referring to the two inequivalent sublattices as
+A and B, whereas a standard off-plane ($S_z$)
+calculation would enforce Néel symmetry (AFM$_\perp$)  as
+$\Sigma^\mathrm{A}_{\up\up} = \Sigma^\mathrm{B}_{\dw\dw}$, 
+$\Sigma^\mathrm{A}_{\dw\dw} = \Sigma^\mathrm{B}_{\up\up}$,
+with
+$\Sigma^\mathrm{A}_{\up\dw} = \Sigma^\mathrm{A}_{\dw\up} = \Sigma^\mathrm{B}_{\up\dw} = \Sigma^\mathrm{B}_{\dw\up} = 0$,
+an in-plane magnetization (AFM$_\parallel$) corresponds to
+$\Sigma^\mathrm{A}_{\up\up} = \Sigma^\mathrm{B}_{\up\up}$, 
+$\Sigma^\mathrm{A}_{\dw\dw} = \Sigma^\mathrm{B}_{\dw\dw}$,
+$\Sigma^\mathrm{A}_{\up\dw} = -\Sigma^\mathrm{B}_{\dw\up}$, 
+$\Sigma^\mathrm{A}_{\dw\up} = -\Sigma^\mathrm{B}_{\up\dw}$.
+
+The same off-diagonal spin symmetry must be realized also in
+the bath Hamiltonian, which can be conveniently achieved with
+either the \texttt{replica} and \texttt{general} choices for 
+the \texttt{bath\_type} option. The most stable strategy to 
+verify that the groundstate of the model is magnetized in the
+plane also in DMFT is to allow either an $S_z$ or an $S_x$ (equivalently $S_y$) magnetization in the bath, and then 
+compare the energies of the respective solutions at $T=0$. 
+The corresponding Hamiltonian forms are:
+\begin{align}
+    \mathbf{H}^\mathrm{bath}_\perp &= 
+        \sum_{p=1}^{N_\mathrm{b}}(\epsilon_p \sigma_0 + m_p \sigma_z), 
+        \label{eq:afmz_dmft_ansatz} \\[1mm]
+    \mathbf{H}^\mathrm{bath}_\parallel &= 
+        \sum_{p=1}^{N_\mathrm{b}}(\epsilon_p \sigma_0 + m_p \sigma_x).
+        \label{eq:afmx_dmft_ansatz}
+\end{align}
+comparing with \ref{eq:replica_bath_sym}, it is clear 
+that this amount to having $N_\mathrm{sym}=2$, with
+$\lambda_{1,p} \equiv \epsilon_p$ describing average
+bath levels and $\lambda_{2,p} \equiv m_p$ allowing 
+a magnetic split, respectively in the $S_z$ and $S_x$ spin bases.
+
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+  !Setup bath and solver for anisotropic AFM phases
+  !> define the symmetry-basis:
+  Nineq = 2
+  Nsym = 2
+  allocate(Hsym_basis(Nspin*Norb,Nspin*Norb,Nsym))
+  Hsym_basis(:,:,1) = pauli_0
+  select case(ansatz)
+    case('off-plane')
+        Hsym_basis(:,:,2) = pauli_z
+    case('in-plane')
+        Hsym_basis(:,:,2) = pauli_x
+  end select
+  !> initialize the symmetry parameters
+  allocate(lambdasym_vectors(Nineq,Nbath,Nsym))
+  call build_replica_band(onsite_band,ed_hw_bath,Nbath)
+  lambdasym_vectors(:,:,1) = onsite_band
+  lambdasym_vectors(:,:,2) = 0d0 ! paramagnetic
+  !> define a symmetry-breaking AFM kick, to help numerics
+  if(afmkick)then
+     lambdasym_vectors(1,:,2) = +sb_field
+     lambdasym_vectors(2,:,2) = -sb_field
+  endif
+  !> setup H_bath inside the solver
+  select case(bath_type)
+    case('replica')
+        call ed_set_Hreplica(Hsym_basis,lambdasym_vectors)
+    case('general')
+        call ed_set_Hgeneral(Hsym_basis,lambdasym_vectors)
+  end select
+  !> finally initialize the two solver instances, one per sublattice
+  !  (the EDIpack2ineq layer automatically dispatches it for the two
+  !   impurity models, if we feed a Bath with the [Nineq,Nb] shape!)
+  Nb = ed_get_bath_dimension(Hsym_basis)
+  allocate(Bath(Nineq,Nb))
+  call ed_init_solver(Bath)
+  .
+  .
+  .
+  contains
+  .
+  .
+  .
+  subroutine build_replica_band(epsilons,bandwidth,Nreplica)
+  !> Initialization of the (average) bath levels, suitable to
+  !  describe a weakly interacting metal or a band insulator
+      real(8),allocatable,dimension(:,:),intent(out)   :: epsilons
+      real(8),intent(in)                               :: bandwidth
+      integer,intent(in)                               :: Nreplica
+      integer                                          :: ireplica
+      real(8),dimension(Nreplica)                      :: tempvec
+      real(8)                                          :: tempval
+      !
+      allocate(epsilons(Nineq,Nbath))
+      !
+      do ireplica=1,Nreplica
+         tempval = ireplica - 1 - (Nreplica-1)/2d0       ![-(N-1)/2 : (N-1)/2]
+         tempval = tempval * 2 * bandwidth/(Nreplica-1)  !-bandwidth:bandwidth
+         tempvec(ireplica) = tempval
+      enddo
+      !
+      if(mod(Nreplica,2)==0)then
+         tempvec(Nreplica/2) = -1d-1  !Much needed small energies around the
+         tempvec(Nreplica/2+1) = 1d-1 !Fermi level (if EF itself not present)
+      endif
+      !
+      do ilat=1,Nineq
+         epsilons(ilat,:) = tempvec
+      enddo
+      !
+   end subroutine build_replica_band
+\end{lstlisting}
+
+The DMFT loop can then be implemented, with the explicit solution of two
+independent impurity problems (prone to numerical noise) or by solving
+only one impurity problem and building the full solution by exploiting 
+the appropriate Néel symmetry:
+
+\begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+   iloop=0;converged=.false.
+   do while(.not.converged.AND.iloop<nloop)
+      iloop=iloop+1
+      !
+      !> Solve the two inequivalent impurity problems
+      if(neelsym)then
+        !> solve just one sublattice and get the other by Neel symmetry
+        call ed_solve(comm,Bath(1,:),Hloc(1,:,:,:,:))
+        call ed_get_sigma_matsubara(Smats(1,:,:,:,:,:))
+        select case(ansatz)
+            case('off-plane')
+             Smats(2,2,2,:,:,:) = Smats(1,1,1,:,:,:) 
+             Smats(2,1,1,:,:,:) = Smats(1,2,2,:,:,:) 
+             if(master)write(*,*) ">>> Enforcing AFMz symmetry"
+            case('in-plane')
+             Smats(2,1,1,:,:,:) = Smats(1,1,1,:,:,:)   
+             Smats(2,2,2,:,:,:) = Smats(1,2,2,:,:,:)   
+             Smats(2,1,2,:,:,:) = -Smats(1,1,2,:,:,:)  
+             Smats(2,2,1,:,:,:) = -Smats(1,2,1,:,:,:) 
+             if(master)write(*,*) ">>> Enforcing AFMx symmetry"
+        end select
+      else
+         !> solve both sublattices independently with the RDMFT wrapper:
+         !  mpi_lanc=T => MPI lanczos, mpi_lanc=F => MPI for ineq sites
+         call ed_solve(Bath,Hloc,mpi_lanc=.true.)
+         !> retrieve all self-energies:
+         call ed_get_sigma_matsubara(Smats,Nlat)
+         !
+      endif
+      !
+      !> Compute the local Green's function
+      call dmft_gloc_matsubara(Hk,Gmats,Smats)
+      !
+      !> Compute the two inequivalent Weiss fields
+      call dmft_self_consistency(Gmats,Smats,Weiss)
+      !
+      !> Fit the new bath
+      !  this behaves differently depending on the ed_mode input:
+      !  - for the normal mode: normal/AFMz phase is solved, so we 
+      !    can fit spin1 and spin2 components independently
+      !  - for the nonsu2 mode: Sz-conservation can be broken, so a 
+      !    unique fit for both spin components is needed
+      select case(ed_mode)
+       case("normal")
+         call ed_chi2_fitgf(Bath,Weiss,ispin=1)
+         call ed_chi2_fitgf(Bath,Weiss,ispin=2)
+       case("nonsu2")
+         call ed_chi2_fitgf(Bath,Weiss,Hloc)
+      end select
+      !
+      !> linear mixing (aids convergence near transition points)
+      if(iloop>1) Bath = wmixing*Bath + (1.d0-wmixing)*Bath_prev
+      Bath_prev = Bath
+      !
+      !> check convergence
+      converged = check_convergence(Weiss(:,1,1,1,1,:),dmft_error,nsuccess,nloop)
+      !
+   enddo
+\end{lstlisting}
+
+After reaching convergence, we can
+
 \end{document}

### 2025-05-23 03_edipack2.tex

@@
 \Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
+\label{eq:replica_bath_sym}
 $$
@@
 relevant, low-energy sector.
+\textcolor{red}{what's the difference with the one above}
 \begin{equation}

### 2025-05-23 04_cbinding.tex
GB pass
- fix a few typos and minor things
- move Holstein example after the Attractive Hubbard example (I feel like clustering the superc example is a nice idea).

Currently deciding if I will add a Edipack2ineq example (as we never give any example for using that module). Probably some nonsu2 stuff with the KMH model, so it fits well just after the BHZ excitons. We might want also a Julia API example, but I'm really not in the mood to install the Julia runtime and start tinkering with it.

@@
 An array of integers containing the dimensions of the former need to be passed as well to allow for proper Fortran input parsing.
-A working C++ example is provided in the {\tt examples} folder of the \NAME repository.
+A working C++ example is provided in the {\tt examples} folder of the \NAME repository and discussed in Section \ref{SecExamples}.
 
@@
 \subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
-EDIpack2py is available as a stand-alone
+\paragraph{From source}
+EDIpack2py is available as a Python
 module which only depends on \NAME and SciFortran.
@@
 \end{lstlisting}
-In some more recent Python distribution the flag {\tt
-  --break-system-packages} might be required to complete
-installation or a virtual environment should be used instead.
 
@@
 The EDIpack2py package is also available in PyPi at
-\href{https://pypi.org/project/EDIpack2py/}{pypi.org/EDIpack2py}. As such
-EDIpy2 can be conveniently installed in any system supporting {\tt pip} as:
+\href{https://pypi.org/project/EDIpack2py/}{pypi.org/EDIpack2py}. The package can be easily installed in any system supporting {\tt pip} as:
 
@@
 \end{lstlisting}
+
+%In some more recent GNU/Linux and Mac Os versions the flag {\tt
+%  --break-system-packages} might be required to complete
+%installation in system paths. Alternatively, and preferrably, 
+%a virtual Python environment can be used.
 

### 2025-05-23 edipack2.tex

@@
 \usepackage{comment}
-\newcommand{\fixme}[1]{{\color{BrickRed} #1}}
+
 \usepackage{xspace}
@@
 \renewcommand{\arraystretch}{1.4}
-% \newcolumntype{T}[1]{>{\tt\footnotesize}m{{#1}}}
-% \newcolumntype{D}[1]{>{\it\footnotesize}m{#1}}
-% \newcolumntype{M}[1]{>{\scriptsize}m{#1}}
-
 \newcolumntype{T}[1]{>{\tt\footnotesize\raggedright\arraybackslash}p{#1}}
@@
 \newcommand{\onlinecite}[1]{\nocite{#1}\!\!\!\citenum{#1}}
-
+\newcommand{\fixme}[1]{{\color{BrickRed} #1}}
 \newcommand {\note}[1]{{\color{blue} [{\bf NOTE}: \bf #1]}}
@@
 \newcommand {\new}[1]{{\color{blue}\it #1}}
-%\newcommand {\new}[1]{{#1}}
-% \DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\def\bcen{\begin{center}}
-\def\ecen{\end{center}}
-
 \def\a{\alpha}       \def\b{\beta}   \def\g{\gamma}   \def\d{\delta}
@@
 
-\subfile{01_intro.tex}
 % ##################################################################
 % ##################################################################
+% ##################################################################
+%
+%                              PAPER HERE BELOW
+%                              
+% ##################################################################
+% ##################################################################
+% ##################################################################
+
+\subfile{01_intro.tex}
+
 % ##################################################################
@@
 % ##################################################################
-% ##################################################################
-% ##################################################################
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ##################################################################
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% ##################################################################
 
-\section{Conclusions}
-{\color{red} Tentative conclusions}
-We have presented \NAME{}, a versatile, high-performance solver for
-generic quantum impurity problems. Leveraging on the massively
-parallel algorithms introduced with its predecessor, this version of
-the library features new capabilities and symmetries within a unified
-framework, providing reliable evaluations of the dynamical correlation
-functions on arbitrary complex argument.
-This makes it particularly well-suited for capturing the sharp
-low-energy excitations and complex spectral features of strongly
-correlated systems. We have shown that this new version enables the evaluation of impurity
-reduced density matrices directly from Fock space quantities and thus unlock 
-quantum information analyses of correlated systems.
+\subfile{06_conclusions_acknowledgement_appendix.tex}
 
-A central feature of \NAME is its strong focus on interoperability,
-achieved through modern Fortran constructs, C/C++-bindings, and
-comprehensive APIs for Python (EDIpy2). 
-These interfaces enable seamless integration with broader
-computational frameworks like TRIQS and W2Dynamics, expanding the
-functionality of these platforms and providing a robust foundation for
-reproducible research.
-
-We thoroughly discussed the implementation of the \NAME library, the
-most important algorithms and classes. We presented in
-details the third-party interfaces which extend exact diagonalization
-capabilities beyond the realm of the library itself.   
-Finally, we showcased the use of the \NAME software in different
-contexts via elaborated example which can serve as reference for the
-potential users.
-
-The modular and extensible design of \NAME provides a
-natural foundation for future extensions, for instance to cluster-DMFT where the
-impurity problem is generalized to include clusters of interacting
-sites. This approach would enable the treatment of spatial
-correlations beyond the single-site approximation, capturing effects
-such as d-wave pairing in high-temperature superconductors, charge
-order, and complex spin textures in strongly correlated systems.
-We anticipate that \NAME will become a valuable tool for the
-computational condensed matter community, supporting a wide range of
-studies on strongly correlated materials and providing a reliable
-reference platform for quantum impurity solvers.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-
-\section{Appendix A: Monicelli interface}\label{appendixA}
-In order to further showcase the interoperability capabilities of
-\NAME provided by the C-bindings module, we describe a simple interface to {\tt Monicelli}, see
-\href{github.com/esseks/monicelli.git}{ttps://github.com/esseks/monicelli.git}.
-
-{\tt Monicelli} is an esoteric programming language based on the LLVM
-toolchain.
-It is written in C++ and offers wrappers for the basic
-types and operations thereof. The syntax replicates a cultural italian
-phenomenon known as ``supercazzola", a rambling nonsensical discourse
-which gives the false impression of carrying an actual meaning,
-introduced in the trilogy movies ``Amici Miei'', directed by Mario
-Monicelli (see
-\href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\_miei}).
-
-The {\tt Monicelli} language can be found at
-\href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
-and can be installed using CMake. The software depends on C++
-compiler with {\tt stdlib}, LLVM and in some cases {\tt libz} library. The installation gives access to the {\tt
-  Monicelli} compiler {\tt mcc}, which statically links LLVM. 
-We believe the discourse flow of this language is best captured by 
-illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G.Perozzi (P) (see
-\href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
-and \href{https://www.youtube.com/watch?v=SF8YUFdP6eU}{Movie Scene}).
-
-\noindent
-V: Lei ha clacsonato?\\
-P: Tu ha clacsonato?\\
-M: Tarapia tapioco, prematurata l'interfaccia, o scherziamo?\\
-V: Prego?\\
-M: Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
-basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
-Unix soltanto in due, oppure in quattro anche scribai con il file
-sorgente {\tt hm\_bethe.mc}?  Come {\tt
-  https://github.com/lcrippa/prematurata\_la\_dmft}, per esempio?\\
-V: Ma che DMFT, mi faccia il piacere! Questi signori stavano
-programmano loro, non si intrometta!\\
-M: Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
-funzioni? Lo vede che interfacciano gli array, non supportati da
-Monicelli, e prematurano anche! 
-Ora io le direi, anche con il rispetto per l'autorità, anche solo le
-due parole come install {\tt Monicelli} from
-\href{github.com/esseks/monicelli.git}{https://github.com/esseks/monicelli.git}
-e compila il file {\tt hm\_bethe.mc}, per esempio.\\
-V: Basta così! Mi seguano nel programma di test!\\
-P: No, no, no, attenzione! Il loop dmft completo \`e supportato
-secondo la Ref.~\cite{Georges1996RMP}, abbia pazienza,
-senn\`o.... Plotta i dati, anche un pochino di Green's function e
-Self-energy in prefettura.\\
-M: Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.\\
-V: Ho bello che capito. Si farà finta di passar da bischeri!\\
-
-We shall now present a fully functioning DMFT code for
-the solution of the Bethe lattice written in Monicelli. It requires a minimal C++
-interface to handle arrays, complex numbers and properly interfacing
-the EDIpack functions.
-The first part of the DMFT code load all the required functions from
-{\tt bagaglio.cpp}, in particular it loads the interface to the \NAME
-solver functions {\tt ed\_init\_solver} and {\tt ed\_solve}:
-
-\begin{lstlisting}[style=cstyle]
-bituma le funzioni ausiliarie che vengono dal bagaglio
-...
-blinda la supercazzola leggi o scherziamo?
-blinda la supercazzola iniziailsolver o scherziamo?
-blinda la supercazzola risolvi o scherziamo?
-blinda la supercazzola prendilasigma o scherziamo?
-blinda la supercazzola prendilbagno con l`elemento Necchi, il valore Sassaroli o scherziamo?
-...
-\end{lstlisting}
-
-After a long initialization, we follow the structure already presented
-in \secu{SecExamplesBetheDMFT} for the Fortran implementation.
-The DMFT code starts with the opening {\tt Lei ha clacsonato} (see
-above). Next, we read the input file and set the dimensions of some
-array describing the bath, the self-energy and Green's
-functions. We start a DMFT iteration loop using the command {\tt
-  stuzzica}, which includes an internal frequency loop as {\tt
-  Monicelli} does not support array algebra.
-The loop contains a call to the \NAME solver function, then proceeds
-by retrieving the self-energy function which is used to obtain the
-local Green's function. These enters the self-consistency equation
-which update the Weiss field. Finally bath optimization is performed
-and if error condition is met the loop exit.
-The main step of the implementation reads:
-
-\begin{lstlisting}[style=cstyle]
-Lei ha clacsonato
-#Read the input file
-    prematurata la supercazzola dimmilfile o scherziamo?
-    prematurata la supercazzola leggi o scherziamo? 
-...                                                  
-#Init the ED solver:
-    voglio il sapone, Necchi come se fosse
-    prematurata la supercazzola ilbagnoepronto o scherziamo?
-    prematurata la supercazzola lavati con il sapone o scherziamo?
-
-    prematurata la supercazzola prendilah o scherziamo?
-    prematurata la supercazzola iniziailsolver o scherziamo?
-...
-#DMFT loop:
-stuzzica    
-      prematurata la supercazzola risolvi o scherziamo?
-
-      prematurata la supercazzola prendilag o scherziamo?
-      prematurata la supercazzola prendilasigma o scherziamo?
-#Get $G_{loc}$ and update $\GG^{-1}$: frequency loop
-      stuzzica                   
-          il contatoredue come fosse 0
-          prematurata la supercazzola prendi con 108, contatore, 0.0, 0.0, 0 o scherziamo?
-...
-      e brematura anche, se il contatore minore di frequenze
-...      
-      prematurata la supercazzola lavatiancora o scherziamo?
-#Fit the bath:       
-      prematurata la supercazzola spiaccica o scherziamo?
-#Mix the bath           
-      prematurata la supercazzola failmischiotto con il sapone, il frullatore o scherziamo?
-#Check error      
-      la fine come se fosse prematurata la supercazzola cisiamo o scherziamo?         
- e brematura anche, se la fine minore di 1
-\end{lstlisting}
-
-\paragraph{Usage}.
-The source code can be retrieved from
-\href{https://github.com/lcrippa/prematurata_la_dmft}{github.com/lcrippa/prematurata\_la\_dmft}. 
-The {\tt src} directory contains several files, including the source
-code {\tt hm\_bethe.mc} implementing the DMFT algorithm, an auxiliary file {\tt bagaglio.cpp} which
-contains a number of functions implementing complex algebra, array
-costruction and interfacing the \NAME procedures. The directory also
-contains an example of input file and a converged bath parametrization
-for the Bethe lattice solution at $U=2$.
-
-The code is compiled using standard Make invocation in the source
-directory:
-\begin{lstlisting}[style=mybash]
-git clone https://github.com/lcrippa/prematurata_la_dmft
-cd prematurata_la_dmft/src
-make
-\end{lstlisting}
-A simple run using provided input file {\tt inputED.conf} will
-re-converge the solution within few loops.
+% ##################################################################
+% ##################################################################
+% ##################################################################
 

### 2025-05-23 04_cbinding.tex

@@
 \paragraph{From source}
-EDIpack2py is available as a Python
-module which only depends on \NAME and SciFortran.
-The Python package can be obtained from the repository
-\href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py}.
+EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
+The source code can be obtained from the git repository \href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py} and installed via
 
@@
 \paragraph{Anaconda}
-As for \NAME, the Python API in EDIpack2py is available through
-Anaconda packaging for Unix/Linux systems. Packages are available for
+As for \NAME, the Python API in EDIpack2py is available as an
+Anaconda package for GNU/Linux and Mac Os systems. Packages are available for
 Python version $>3.10$. The \NAME package contains the {\tt

### 2025-05-23 02_install.tex
Intermediate GB almost finished with the KMH example LC doing something here and there, as I see

@@
-\documentclass[edipack2.tex]{subfiles}
+\documentclass[edipack_sp.tex]{subfiles}
 \begin{document}
@@
 A second dynamic library, {\tt libedipack\_cbindings.so}, together with the associated header
-file{\tt edipack\_cbindings.h}, enables interoperability with other programming languages.
+file {\tt edipack\_cbindings.h}, enables interoperability with other programming languages.
 
@@
   Lanczos-based solver for general quantum impurity problems. It 
-  supports systems with a wide range of symmetries, including quantum 
-  number conservation, multi-orbital models, and even coupling to local 
+  supports systems with a wide range of symmetries leveraging different quantum numbers conservation, multi-orbital models, and even coupling to local 
   phonons. The \NAME solver is structured hierarchically and modularly, 

### 2025-05-23 04_cbinding.tex
Intermediate GB almost finished with the KMH example LC doing something here and there, as I see

@@
 As a first application of the \NAME C-bindings we implemented a
-complete Python interface, i.e. EDIpack2py. This is a Python module which
+complete Python interface called EDIpack2py. This is a Python module which
 enables access to all the library features and unlock implementation of
 further interfaces of \NAME as a plug-in solver for external Python
-based software.
+based software. Detailed documentation can be found online at \href{https://edipack.github.io/EDIpack2py}
+{https://edipack.github.io/EDIpack2py}.
 
@@
   EDIpack2py} Python module as well as \NAME and SciFortran
-libraries. In this case the resolution of the dependencies is
-taken care from Conda itself. 
-Using conda the installation reads:
+libraries. 
+%In this case the resolution of the dependencies is
+%taken care from Conda itself. 
+Using conda or mamba the installation proceeds as following:
 \begin{lstlisting}[style=mybash]
-conda create -n edipack
-conda activate edipack
-conda install -c conda-forge -c edipack edipack
+conda create -n edipack  #creation of a virtual environment (name can be changed)
+conda activate edipack   #activation of the virtual environment
+conda install -c conda-forge -c edipack edipack #installation from the edipack channel
 \end{lstlisting}
 
-Once installed, any loading of the {\tt EDIpack2py} module resolves in the
-attempt to load the dynamic library {\tt
+When the{\tt EDIpack2py} module is imported, it attempts to load the dynamic library {\tt
   libedipack\_cbindings.so/.dylib} containing the Fortran-C bindings
-for \NAME. By default the library is searched proceeds as follow: 
+for \NAME. By default the library search proceeds as follow: 
 \begin{enumerate}
@@
 The Python API provided in the EDIpack2py module consists essentially of a
-suitable class called for convenience {\tt global\_env}.
-The class incorporates all the global variables inherited from \NAME
-C-bindings library and implements a number of interface functions
+class called for convenience {\tt global\_env}.
+This class contains all the global variables inherited from the \NAME
+C-bindings library, and implements a number of interface functions
 leveraging the Python duck typing to \NAME.  
@@
 are accessed as properties and
-methods of the {\tt global\_env} claass, which needs to be imported at the beginning
-of the python script, along with other useful modules. For instance Numpy is
+methods of the {\tt global\_env} class.
+
+The {\tt global\_env} class needs to be imported at the beginning
+of the python script, along with other useful modules. Numpy is
 necessary, while mpi4py is strongly recommended.
@@
 
-The EDIpack2py supports the solution of problems with independent
-impurities, interfacing with the the EDIpack2ineq extension of the
+The EDIpack2py module supports the solution of problems with independent
+impurities, interfacing to the EDIpack2ineq extension of the
 library, if present. Should the inequivalent impurities package not be
@@
 or set locally as properties of the class {\tt
-  global\_env}. Differently these are initialized, alongside the remaining
+  global\_env}. The global variables are initialized, alongside the remaining
 default input variables, through a call to procedure {\tt
@@
 print(ed.Nspin)         # all functions can have global variables as arguments
-np.arange(ed.Nspin)
+np.arange(ed.Nspin)     # array of integers from 0 to Nspin-1
 \end{lstlisting}
@@
 This group includes a number of functions enabling initialization,
-execution and finalization  functionalities for the diagonalization
-solver.
+execution and finalization  of the \NAME solver.
 \begin{itemize}
@@
     calculates the observables and any dynamical correlation
-    function. All results remain stored in the memory and get accessed
+    function. All results remain stored in the memory and can be accessed
     through input/output functions.
@@
 {\tt ed\_mode=normal,superc,nonsu2} (Sec.~\ref{sSecQNs}) and
-{\tt bath\_type=normal,hybrid,general} (Sec.~\ref{sSecBath}). Besides, the
+{\tt bath\_type=normal,hybrid,general} (Sec.~\ref{sSecBath}). In addition, the
 constructor accepts a vast array of keyword arguments that allow for fine-tuning
@@
 In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to \NAME.
-Configuration specific to the exact diagonalization solver can be performed through the parameters in section \NAME of a w2dynamics parameter file.
-For most of the \NAME input variables, it provides a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set insofar as this is supported by the interface and not an option available through generic w2dynamics parameters.
-This thus includes some parameters that the user will ordinarily want to change from their defaults in a typical calculation such as the number of bath sites {\tt NBATH} and other parameters such as options for the bath fitting and diagonalization algorithms, but also specifically excludes other typically set input variables such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}.
-All of the these variables correspond to or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
+
+The  behavior of the w2dynamics solver is controlled by means of an input file, by default called
+{\tt Parameters.in}. In order to configure the ED solver, the content of a specific section in the parameters file, called {\tt [EDIPACK]}, has to be modified.
+
+For most of the \NAME input variables, w2dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt EDIPACK} section of the parameters file.
+This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath sites {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
+
+A second set of input variables, including phyisical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the w2dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
+An example of a properly formatted input file is provided in~\ref{SecExamples}.
+See~\cite{Wallerberger2019CPC}
+for further details.
+
+%All of the these variables correspond to or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
 Note however in particular that if the \NAME solver is used, {\tt beta} is by default only used as cut-off and does not imply a finite temperature calculation unless the user explicitly sets the parameter {\tt   ED\_FINITE\_TEMP} in section {\tt EDIPACK} to {\tt True}.
 
-Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in mostly the same way as it would be for the CT-HYB solver.
-This e.g.
-means that results such as the Green's functions are stored into the w2dynamics HDF5 output file in the typical format, and that w2dynamics uses only its own code for e.g.
-calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
-As a consequence of this, some functionality that would require specific support from w2dynamics that is not available as of the time of publication can not be used through the interface, e.g.
-calculations with superconductivity or with phonons.
+Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in a way closely resembling the standard the CT-HYB code.
+For example, results such as the Green's functions are stored into the w2dynamics HDF5 output file in the typical format, and that w2dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+As a consequence of this, some functionality that would require specific support from w2dynamics that is not available as of the time of publication can not be used through the interface, for instance calculations with {\tt ED\_MODE=SUPERC} or with phonons.
 

### 2025-05-23 05_examples.tex
Intermediate GB almost finished with the KMH example LC doing something here and there, as I see

@@
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
+program dmft_kane_mele_hubbard
+  !Load EDIpack library 
+  USE EDIpack
+  !Load the inequivalent impurities extension
+  USE EDIpack2ineq
+  .
+  .
+  .
   !Setup bath and solver for anisotropic AFM phases
@@
         !> solve just one sublattice and get the other by Neel symmetry
-        call ed_solve(comm,Bath(1,:),Hloc(1,:,:,:,:))
+        call ed_solve(Bath(1,:))
         call ed_get_sigma_matsubara(Smats(1,:,:,:,:,:))
@@
          !  mpi_lanc=T => MPI lanczos, mpi_lanc=F => MPI for ineq sites
-         call ed_solve(Bath,Hloc,mpi_lanc=.true.)
+         call ed_solve(Bath,mpi_lanc=.true.)
          !> retrieve all self-energies:
-         call ed_get_sigma_matsubara(Smats,Nlat)
+         call ed_get_sigma_matsubara(Smats,Nineq)
          !
@@
    enddo
-\end{lstlisting}
-
-After reaching convergence, we can
+   !
+   !> Compute Kinetic Energy
+   call dmft_kinetic_energy(Hk,Smats)
+\end{lstlisting}
+
+We observe that, after convergence is reached, we can perform some 
+post-processing to get quantities of interest, e.g. computing the 
+lattice kinetic energy (as implemented in the \texttt{dmft\_tools} 
+library). The potential energy, as well as the AFM order parameters
+and most impurity observables are automatically computed by \NAME, 
+and saved with an appropriate inequivalent-impurity filename suffix 
+by the EDIpack2ineq layer.
+
+Hence, we can readily evaluate the total energy of both the AFM$_\perp$
+and AFM$_\parallel$ calculations and compare them to establish which 
+is favored as the groundstate of the system. In \figu{fig:KMenergy}(a)
+we show results for the energy difference $E_\parallel-E_\perp$ across
+a wide range of $U/t$ and $\lambda_\mathrm{so}$ values. To assess the
+degree of accuracy of our total energy calculation, we benchmark against
+Hartree-Fock (simple static mean-field, but inherently variational), 
+DMFT with NRG solver and lattice AFQMC data, as taken from 
+Ref.\,\cite{Racz2020}. The total energy comparison is reported in 
+\figu{fig:KMenergy}(b), for $\lambda_\mathrm{so}=0$.
+
+\begin{figure}
+\hspace{1cm} (a) \hspace{7.25cm} (b)\\
+    \includegraphics[width=0.47\linewidth,trim={0 0 0 5mm},clip]{figures/KMH_energy.pdf}\hfill
+    \includegraphics[width=0.45\linewidth]{figures/benchEnergy_honey.pdf}\\
+    \caption{In panel (a) the total energy difference between the in-plane 
+    and off-plane AFM solutions found in DMFT-ED at $T=0$. Negative values
+    signal a groundstate with in-plane magnetization. The plateau at zero
+    energy difference marks the topological phase of the model (a 
+    paramagnetic quantum spin-Hall insulator), at all points except on the $\lambda_\mathrm{so}=0$ line, where the groundstate is an interacting
+    Dirac liquid, at weak coupling, or an isotropic antiferromagnet at strong coupling. In panel (b) we compare the total energies across the 
+    $\lambda_\mathrm{so}=0$ line to published data for Hartree-Fock,
+    DMFT-NRG and AFQMC solutions \cite{Racz2020}.}
+    \label{fig:KMenergy}
+\end{figure}
 

### 2025-05-24 02_install.tex
Updates from Overleaf

@@
   structures. A detailed overview of this part of the library is 
-  provided in Sec.\ref{SecEDIpack}.
+  provided in \secu{SecEDIpack}.
 
@@
 be retrieved directly from its GitHub repository, for instance using:
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 git clone https://github.com/edipack/EDIpack 
@@
 This is the default CMake workflow:
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 mkdir build
@@
 multi-threaded building:
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 mkdir build
@@
 The Conda package installation procedure reads:
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 conda create -n edipack

### 2025-05-24 03_edipack2.tex
Updates from Overleaf

@@
-\documentclass[edipack2.tex]{subfiles}
+\documentclass[edipack_sp.tex]{subfiles}
+\usepackage{multirow}
 \begin{document}
@@
 matrix $h^{0}_{\a\b\sigma\sigma'}$, which can include 
-orbital-dependent on-site energies, spin-orbit coupling or other 
-single-particle terms.
+orbital-dependent on-site energies or amplitudes, spin-orbit coupling or other single-particle terms.
 
@@
  $\hat{H}^{\mathrm{int}}$ can in principle contain any 
-set of two-body operators of the form
-$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$.
+set of two-body operators: 
+$$
+\hat{H}^\mathrm{int}_\mathrm{imp} =  \sum_{ijkl} U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}. 
+$$
 However, we typically 
@@
 \subsubsection{System setup}
-We consider a bath discretized into a  number
-of bath degrees of freedom and a finite number of available phonons $N_\mathrm{ph}$,
-to cut-off the unbounded dimensions of the local phonons Hilbert
-space.
-In the rest of this work we consider a system composed of $N_\mathrm{imp}=1$
-impurities, i.e. a single impurity problem, $N_\mathrm{bath}$ bath elements
-and $N_\mathrm{ph}$ phonons.
-The total size of the system is determined by the (fixed)
-number of phonons (fixed) $N_\mathrm{ph}$, the number of impurity orbitals 
-$N_\a$ and that of the bath levels  $N_\mathrm{b}$. The latter is a
-function of  the bath topology and $N_\mathrm{bath}$.
-In the simplest case each bath
+We consider a quantum impurity system composed by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
+The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the number of phonons $N_\mathrm{ph}$.
+The latter is fixed to set a cut-off to the unbounded dimensions of the local phonons Hilbert space.
+The number of bath degrees of freedom $N_\mathrm{b}$ is a
+function of the bath topology and of $N_\mathrm{bath}$, which is determined internally by \NAME.
+In the simplest case, each bath
 element corresponds to an independent electronic level coupled to the
 impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$.
-The total count of electronic levels is  $N_\mathrm{s}=N_\a +
-N_\mathrm{b}$.
+The number of electronic levels in the quantum impurity systems is indicated with $N_\mathrm{s}$.
 
@@
 The Fock space of the quantum impurity problem is defined as
-$\FF=\FF_\mathrm{e}\otimes \FF_\mathrm{ph}$, where $\FF_\mathrm{e}=\bigoplus_{n=0}^{N_\mathrm{s}}
-S_-\HH_\mathrm{e}^{\otimes n}$ is the electronic Fock space built 
+$\FF=\FF_\mathrm{e}\otimes \FF_\mathrm{ph}$, where: $$
+\FF_\mathrm{e}=\bigoplus_{n=0}^{N_\mathrm{s}}
+S_-\HH_\mathrm{e}^{\otimes n}
+$$ 
+is the electronic Fock space built 
 from the local electronic Hilbert space $\HH_\mathrm{e}$, and 
-$\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}$
+$$
+\FF_\mathrm{ph}=\bigoplus_{n=0}^{N_q}S_+\HH_\mathrm{ph}^{\otimes n}
+$$
 is the
@@
 Here ($S_-$) $S_+$ is the (anti-)symmetrization operator.  
-
+%
 The total dimension of the Fock space is
-$D=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)=D_\mathrm{e}\cdot
-D_\mathrm{ph}$, highlighting the exponential
+$$
+D=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)=D_\mathrm{e}\cdot
+D_\mathrm{ph},
+$$ 
+highlighting the exponential
 growth with the number of electronic levels.
@@
       0 &\text{otherwise}
-    \end{cases};\qquad
+    \end{cases};\\
     c^{+}_{a\sigma}\ket{\vec{n}} &=
@@
 
+\begin{lstlisting}[style=fstyle,numbers=none]
+  subroutine C(pos,in,out,fsgn) !$c_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle$
+    integer,intent(in)    :: pos  !Position to be set to 1
+    integer,intent(in)    :: in   !Input index
+    integer,intent(inout) :: out  !Output index
+    real(8),intent(inout) :: fsgn !Fermionic sign   
+    integer               :: l
+    if(.not.btest(in,pos-1))stop "C error: C_i|...0_i...>"
+    fsgn=1d0
+    do l=1,pos-1
+       if(btest(in,l-1))fsgn=-fsgn
+    enddo
+    out = ibclr(in,pos-1)
+  end subroutine C
+\end{lstlisting}
+
+\begin{lstlisting}[style=fstyle,numbers=none]
+  subroutine CDG(pos,in,out,fsgn) !$c^\dagger_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle$
+    integer,intent(in)    :: pos  !Position to be set to 1
+    integer,intent(in)    :: in   !Input index
+    integer,intent(inout) :: out  !Output index
+    real(8),intent(inout) :: fsgn !Fermionic sign   
+    integer               :: l
+    if(btest(in,pos-1))stop "C^+ error: C^+_i|...1_i...>"
+    fsgn=1d0
+    do l=1,pos-1
+       if(btest(in,l-1))fsgn=-fsgn
+    enddo
+    out = ibset(in,pos-1)
+  end subroutine CDG
+\end{lstlisting}
+
+\begin{lstlisting}[style=fstyle,numbers=none]
+ !Binary decomposition of the ${\color{comment-color} i\in\NNN}$ with Ntot-bits
+ function Bdecomp(i,Ntot) result(ivec)
+    integer :: Ntot,ivec(Ntot),l,i
+    logical :: busy
+    do l=0,Ntot-1
+       busy=btest(i,l)
+       ivec(l+1)=0
+       if(busy)ivec(l+1)=1
+    enddo
+  end function Bdecomp
+\end{lstlisting}
+
 \subsection{Conserved quantum numbers}\label{sSecQNs}
@@
 is essential to exploit suitable symmetries. Specifically, if the 
-Hamiltonian $H$ commutes with a set of operators ${\cal Q}$ such that 
-$[H, {\cal Q}] = 0$, the Fock space can be decomposed into smaller, 
+Hamiltonian $H$ commutes with a set of operators ${\cal \vec{Q}}=[{\cal Q}_1,{\cal Q}_2,\dots,{\cal Q}_M]$ such that 
+$[H, {\cal Q}_i] = 0$, the Fock space can be decomposed into smaller, 
 disjoint symmetry sectors labeled by quantum numbers $\vec{Q}$.
@@
 specific case is discussed extensively
-Ref.~[\onlinecite{Amaricci2022}] and will not be further covered here.
+Ref.~\cite{Amaricci2022} so we will not be further cover it here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
 
@@
 
-\item{} The {\bf superc} case maintains onlu the $S_z$ conservation,
+\item{} The {\bf superc} case maintains only the $S_z$ conservation,
 allowing the total charge to not be conserved. This setting captures
-system with $s$-wave superconductivity, including 
+systems with $s$-wave superconductivity, including 
 intra- and inter-orbital pairing.
@@
 This map is typically implemented as a rank-1
-integer array, whose size corresponds to the dimension of the sector.
+integer array whose size corresponds to the dimension of the sector $D_{\SS_\vec{Q}}$$.
 
@@
 \otimes \MM_\dw$.
-
+%
 Each state $\ket{i}=\ket{i_\up} \ket{i_\dw}$ in this factorized basis
@@
 For a more
-detailed discussion on the structure of the Fock basis in this case, see Ref.~[\onlinecite{Amaricci2022}].
+detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022}.
 
@@
 a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
-$D_{\SS(\vec{Q})}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+$D_{\SS_\vec{Q}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
 basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix.
@@
 symmetric due to the factorized nature of the sectors as discussed
-above, see also Ref.~[\onlinecite{Amaricci2022}].
-The analysis of the spectrum is then reduced toinspecting the
+above, see also Ref.~\cite{Amaricci2022}.
+The analysis of the spectrum is then reduced to inspecting the
 Hamiltonian within each symmetry sector, or to a subset thereof if a
@@
 {\tt sector} object, which is defined in {\tt
-  ED\_VARS\_GLOBAL}. This object contains all the revelant
-informations for defining the symmetry, inclduing the sector
+  ED\_VARS\_GLOBAL}. This object contains all the relevant
+information for defining the symmetry, including the sector
 dimensions, quantum numbers and the map $\MM$. The constructor
 (destructor) for this object is defined in the {\tt
-  ED\_SECTORS} module via the functions {\tt build\_sector}
-(constructor) and {\tt
-  delete\_sector} (destructor).
+  ED\_SECTORS} module via the function {\tt build\_sector} ({\tt
+  delete\_sector}).
 These functions use different algorithms depending on the nature 
-of the quantum numbers $\vec{Q}$. The following  code
-snippet summarize the various available implementations:
+of the quantum numbers $\vec{Q}$, i.e. the value of {\tt ed\_mode}. The following  code snippet summarize the various available implementations:
+
 \setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf normal}
+  \begin{minipage}{0.27\linewidth}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-    \center{\bf superc}
+  \begin{minipage}{0.27\linewidth}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
   \begin{minipage}{0.3\linewidth}
-    \center{\bf nonsu2}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
     nt_  = nup_ + ndw_
-    if(nt_ /= self%Ntot)cycle
+    if(nt_/=self%Ntot)cycle
     i=i+1
@@
 \begin{tabular}{c|c|c}\label{list1}
+    {\bf normal} & {\bf superc} & {\bf nonsu2}\\
+    \hline
 \stackinset{l}{}{t}{}{}{\listingA} &
@@
 \end{tabular}
+\vspace{2mm}
 
@@
 retrieve sector indices and quantum number
-informations. Furthermore, it provdes a set of
-essential functions for applying arbitrary linear combinations
-of operators to a given Fock state $\ket{v}\in\SS$, i.e.
-$\OO\ket{v} = \sum_i a_i C^{p_i\dagger}_{\a_i,\s_i}\ket{v}$ with
-$a_i\in\CCC$ and $p_i=0,1$. This functionality is implemented through
-the functions {\tt apply\_op\_C}, {\tt apply\_op\_CDG}, {\tt
-apply\_Cops}, which  are widely used throughout the code.
+information. Furthermore, it provides a set of
+essential functions for applying creation ({\tt apply\_op\_CDG}), destruction ({\tt apply\_op\_C}) or arbitrary linear combinations
+({\tt apply\_Cops}) of these to a given Fock state $\ket{v}\in\SS$, i.e.:
+$$
+\OO\ket{v} = \sum_i a_i C_{\a_i,\s_i}+ b_i C^{\dagger}_{\b_i,\r_i}\ket{v}
+$$ 
+with $a_i, b_i \in\CCC$, $\a_i,\b_i=1,\dots,N_\a$ and $\s_i,\r_i=\up,\dw$. These functions are widely used throughout the code.
 
 \subsection{Interaction setup}\label{sSecIntSetup}
-The \NAME code offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}. 
+The \NAME code offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}, which are controlled by the input variables {\tt
+  ED\_USE\_KANAMORI} and {\tt ED\_READ\_UMATRIX}.
+
 The generalized Hubbard-Kanamori interaction, as defined in \equ{Hint}, is natively
 supported and controlled by the input parameters {\tt ULOC}$=U$, {\tt
-  UST}$=U^{'}$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP}$=J_{p}$.
+  UST}$=U'$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP}$=J_{p}$.
 These quantities can be specified either in the input file or directly
-via the the command line, provided the logical input parameter {\tt
-  ED\_USE\_KANAMORI} is set to {\tt T}. In this mode, the maximum
-number of impurity orbitals {\tt NORB}$=N_\a$ is limited to $5$.
-
-Alternatively, a list of two-body operators can be provided by the user in a properly
-formatted text file, whose name is specified by the input variable {\tt
-  UMATRIX\_FILE}. The implementation of the list of interaction terms is contained in
+via the the command line, provided the logical input parameter {\tt ED\_USE\_KANAMORI=T} and setting {\tt ED\_READ\_UMATRIX=F}.
+In this mode, the maximum number of impurity orbitals {\tt NORB}$=N_\a$ is limited to $5$.
+
+Alternatively, setting {\tt ED\_READ\_UMATRIX=T} and {\tt ED\_USE\_KANAMORI=F}, a list of two-body operators can be supplied by the user in a properly
+formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}. The implementation of the list of interaction terms is contained in
 the module {\tt ED\_PARSE\_UMATRIX}.  
-The file mush have the suffix {\tt \\.restart} and should be formatted
+The file must have the suffix {\tt <UMATRIX\_FILE>.re\-star\-t} and should be formatted
 as follows: 
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 NORB BANDS
@@
 defines a single two-body term of the form 
-$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. Note tha the
+$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. Note that the
 coefficient indices are swapped compared to the standard two-body
-operator formulation.  
+operator formulation \cite{??}.  
 Empty lines and lines starting with {\tt \#, \%, !} are ignored.
 
-To enable the reading an interaction matrix file, the flag {\tt
-  ED\_READ\_UMATRIX} must be set to {\tt T}.
-Note that {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI},
-are mutually exclusive but can both be set to {\tt F}. 
+While {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI}
+are mutually exclusive, we allow to set both to {\tt F}. 
 In this case, the user must 
 provide the interaction terms to the solver through the function 
-{\tt add\_twobody\_operator} in the calling program or script, before 
-the impurity problem is solved.
-
-For reference and future use, the interaction operators used in each 
-call to the solver are saved in the output file 
-{\tt UMATRIX\_FILE.used}.
+{\tt add\_twobody\_operator} in the calling program or script, before  the impurity problem is solved.
+
+For reference and future use, a list of the interaction operators used in each call to the solver are saved in the output file 
+{\tt <UMATRIX\_FILE>.used}.
 
 \subsection{Classes}
-The use of objects and classes greatly simplifies the implementation 
-of critical mathematical concepts required for solving quantum 
+The use of objects and classes greatly simplifies the implementation of critical mathematical concepts required for solving quantum 
 impurity problems. This section provides an overview of the main 
@@
 hash tables. Each key corresponds to a row index, while the associated 
-value contains a pair of dynamic arrays: one for the non-zero matrix 
+value contains a pair of dynamic arrays: one for the non-zero (NNZ) matrix 
 elements and one for their respective column indices.
+
+\begin{lstlisting}[style=fstyle,numbers=none]
+! sparse row: contains the NNZ elements on anyrow of the sparse matrix.
+type sparse_row_csr
+   integer                                   :: size  !size of the row = NNZ
+   real(8),dimension(:),allocatable          :: dvals !rank-1 array for double precision
+   complex(8),dimension(:),allocatable       :: cvals !rank-1 array for double complex
+   integer,dimension(:),allocatable          :: cols  !rank-1 array for column indices
+end type sparse_row_csr
+! Sparse Matrix: allocatable array of sparse rows
+type sparse_matrix_csr
+   type(sparse_row_csr),dimension(:),pointer :: row  !array of {\tt sparse\_row\_csr} 
+   integer                                   :: Nrow !total number of rows
+   integer                                   :: Ncol !total number of columns
+   logical                                   :: status=.false. !Allocation status
+#ifdef _MPI
+   type(sparse_row_csr),dimension(:),pointer :: loc      !array for the diagonal blocks
+   integer                                   :: istart=0 !start index MPI range
+   integer                                   :: iend=0   !end index MPI range
+   integer                                   :: ishift=0 !shift index MPI range
+   logical                                   :: mpi=.false.
+#endif
+end type sparse_matrix_csr
+\end{lstlisting}
 
@@
 for each value of {\tt ed\_mode}.
+
+\begin{lstlisting}[style=fstyle,numbers=none]
+!sparse row: contains bath states values for each impurity key 
+type sparse_row
+   integer                               :: size          !current size
+   integer                               :: bath_state_min!smallest bath state
+   integer                               :: bath_state_max!largest bath state
+   integer,dimension(:),allocatable      :: bath_state    !rank-1 bath states
+   integer,dimension(:),allocatable      :: sector_indx   !bath state sector indices
+end type sparse_row
+!Sparse Map: array of sparse rows 
+type sparse_map
+   type(sparse_row),dimension(:),pointer :: imp_state     !Key: impurity states
+   integer                               :: Nimp_state    !Key upper limit 
+   logical                               :: status=.false.!allocation status
+end type sparse_map
+\end{lstlisting}
 
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.465\linewidth}
-    \center{\bf normal}
+  \begin{minipage}{0.42\linewidth}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
   iBath = ibits(iup,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(1)%sp,iImp,iBath,i)
+  call sp_insert_state(self%H(1)%sp,
+                       iImp,&
+                       iBath,&
+                       i)
 enddo
@@
   iBATH = ibits(idw,Norb,Norb*Nbath)
-  call sp_insert_state(self%H(2)%sp,iImp,iBath,dim) 
+  call sp_insert_state(self%H(2)%sp,&
+                       iImp,&
+                       iBath,&
+                       i) 
 enddo
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.505\linewidth}
-    \center{\bf superc/nonsu2}
+  \begin{minipage}{0.45\linewidth}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
     iImpDw = ibits(idw,0,Norb)
-    iBathUp = ibits(iup,Norb,Norb*Nbath)
-    iBathDw = ibits(idw,Norb,Norb*Nbath)
+    iBathUp= ibits(iup,Norb,Norb*Nbath)
+    iBathDw= ibits(idw,Norb,Norb*Nbath)
     iImp   = iImpUp  + iImpDw*(2**Norb)
     iBath  = iBathUp + iBathDw*(2**(Norb*Nbath))
-    call sp_insert_state(self%H(1)%sp,iImp,iBath,dim)
+    call sp_insert_state(self%H(1)%sp,&
+                         iImp,&
+                         iBath,&
+                         dim)
   enddo
@@
 \begin{tabular}{c|c}\label{list2}
+{\bf normal} & {\bf superc/nonsu2}\\
+\hline
   \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
@@
 
+\begin{lstlisting}[style=fstyle,numbers=none]    
+!Single element of the list: contains a single eigen-solution.
+!Twin states are just pointers, no memory.
+!double or cmplx vector are automatically MPI distributed.
+type sparse_estate
+   integer                             :: sector        !Symmetry sector index
+   real(8)                             :: e             !eigenvalue: ordering key
+   real(8),dimension(:),allocatable    :: dvec          !double  eigen-vector
+   complex(8),dimension(:),allocatable :: cvec          !complex eigen-vector
+   logical                             :: itwin=.false. !twin sector logical label
+   type(sparse_estate),pointer         :: twin=>null()  !link to twin state in the list
+   type(sparse_estate),pointer         :: next=>null()  !List next pointer
+end type sparse_estate
+!Ordered  list storing the lower part of the Hamiltonian spectrum: 
+type sparse_espace
+   integer                     :: size               !Current list
+   real(8)                     :: emax               !Max energy  fixed by ${\color{}e^{-\beta {\tt emax}}<{\tt cutoff}}$
+   real(8)                     :: emin               !Min energy:the groundstate energy
+   logical                     :: status=.false.     !Allocation status
+   type(sparse_estate),pointer :: root=>null()       !Root of the linked list
+end type sparse_espace
+
+\end{lstlisting}
+
 To avoid unbounded growth of this list, a  
@@
 One of the main goal of the \NAME is to evaluate dynamical correlations
-functions (DCF) $\ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,
+functions (DCF), e.g. $D(t) = \ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,
 these DCFs can be expressed as truncated Kallen-Lehmann spectral sums of the form
-$
-\tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
+$$
+D(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
   - dE_{mn}}
-$
+$$
 where $w_{mn}$ is the weight determined by the projection of the
@@
 for the high-performance execution of \NAME.
+
+\begin{lstlisting}[style=fstyle,numbers=none]   
+!The contributions to the GF Kallen-Lehmann sum are stored as
+!GF_{ab,sr}%state%channel%{w,e}.
+!A couple of weight,poles {w,e} is stored: 
+!for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
+!
+!Sub-class: contains the actual weight and poles:
+type GFspectrum
+   complex(8),dimension(:),allocatable       :: weight
+   real(8),dimension(:),allocatable          :: poles
+end type GFspectrum
+!
+!N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
+!Sub-class: contains a given set of weights and poles.
+!Each instance of this sub-class correponds to a given input state 
+!and a given operator in the Kallen-Lehman representation.  
+type GFchannel
+   type(GFspectrum),dimension(:),allocatable :: channel 
+end type GFchannel
+!
+!Main class: stores  weights and poles of a given DCF 
+!obtained through the dynamical Lanczos algorithm.
+!state_list%size = # of state in the spectrum 
+type GFmatrix
+   type(GFchannel),dimension(:),allocatable  :: state
+   logical                                   :: status=.false.!Allocation status
+end type GFmatrix
+\end{lstlisting}
 
@@
 The bath topology, which defines the connectivity between the
-$N_\mathrm{b}$ electronic levels assigned to the bath, is specified
-through the input variable {\tt bath\_type}. This variable can take
-one of four possible values: {\bf normal}, {\bf hybrid}, {\bf
-  replica}, and {\bf general} (see Fig.~\ref{figBaths}).
-  \fixme{This figure looks quite annoying to generate, especially to cover
-  all possible \texttt{ed\_mode} values. I'd pass...}
-
-\paragraph{{\tt bath\_type}={\bf normal}} In this configuration, the
+electronic levels assigned to the bath, is specified
+through the input variable {\tt bath\_type}. In \NAME this variable can take one of four possible values: {\bf normal}, {\bf hybrid}, {\bf replica}, and {\bf general}.
+
+\paragraph{{\tt bath\_type}={\bf normal}.} In this configuration, the
 bath consists of $N_\mathrm{bath}$
-electronic sites coupled to each of the impurity orbital, resulting
-in a total  $N_\mathrm{b} = N_\sigma N_\a N_\mathrm{bath}$ of bath levels.
-% Ocio!
-
-For {\tt ed\_mode}={\bf normal} the bath Hamiltonian is parametrized
-as diagonal matrices in both the orbital and spin spaces:
+electronic sites coupled to each impurity orbital, resulting
+in $N_\mathrm{b} = N_\a N_\mathrm{bath}$ bath levels and a total size of $N_\mathrm{s}=(N_\mathrm{bath}+1)N_\a$.
+For {\tt ed\_mode}={\bf normal} the bath Hamiltonian is parametrized as diagonal matrices in both the orbital and spin spaces:
 $$
@@
 where $\varepsilon_{\a\s}$ represents  the on-site energies for each orbital and spin. 
-
+%
 If {\tt ed\_mode}={\bf superc},  anomalous
@@
 considered. In this case, the bath Hamiltonian gains 
-an additional set of parameters, diagonal in orbital space but
-off-diagonal in the spin one:
-$$
-h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}} .
-$$
-where $\Delta^p_\a$ represents the pairing amplitudes. 
+an additional set of parameters $\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$, diagonal in orbital space but
+off-diagonal in the spin, where $\Delta^p_\a$ represents the pairing amplitudes. 
 This choice corresponds to a Nambu representation for each orbital component,
@@
 where $\tau_{i=0,x,y,z}$ are Pauli matrices.
-
+%
 The hybridization amplitudes between the impurity and the bath levels
@@
 spin and orbital space: $V^p_{\a\b\s\s'}=V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$.
-
-If {\tt ed\_mode}={\bf nonsu2} the an additional set including terms
-describing spin-flip processes (as total magnetization is not
-conserved) should be included $V^p_{\a\b\s\s'} =
+%
+If {\tt ed\_mode}={\bf nonsu2}  an additional set including terms describing spin-flip processes (as total magnetization is not conserved) should be included $V^p_{\a\b\s\s'} =
 W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$.
 
-\paragraph{{\tt bath\_type}={\bf hybrid}}
+Thus, the total number of parameters used to determine the bath is $N_\mathrm{param}=2N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal} or $N_\mathrm{param}=3N_\a N_\mathrm{bath}$ for the other two values of {\tt ed\_mode}.
+
+\paragraph{{\tt bath\_type}={\bf hybrid}.}
+This hybrid topology is the simplest generalization of the bath pa\-ra\-me\-tri\-za\-tion which captures the effects of locally
+coupled impurity orbitals. However this setup typically requires a more challenging optimization process, especially
+with few available bath levels (see \secu{sSecFit}). 
 The bath is formed by $N_\mathrm{bath}$ sites coupled to all the
-impurity orbitals, resulting in a total of % Ocio!
-$N_\mathrm{b}\equiv N_\sigma N_\alpha N_\mathrm{bath}$ electronic bath levels. 
+impurity orbitals, so that there are $N_\mathrm{b}\equiv  N_\mathrm{bath}$ bath levels and   $N_\mathrm{s}=N_\mathrm{bath}+N_\a$. 
 The parametrization of the bath Hamiltonian is 
@@
 $$
-
-As for the previous case, the {\bf superc} mode introduces anomalous
-components with the form
-$$
-h^p_{\a\b\s\s'}=\Delta^p_{\a}\delta_{\a\b}\delta_{\s
-  \overline{\s}}.
-$$
-The key difference here is that the hybridization matrix elements are
-generally off-diagonal in the orbital indices:
+%
+The key difference with respect to the previous case is that the hybridization matrix elements are generally off-diagonal in the orbital indices:
 $$
@@
 $$
-
-If full spin symmetry is not preserved, i.e.~for {\tt ed\_mode}={\bf nonsu2}, an additional
+Moreover, the {\tt ed\_mode}={\bf superc} introduces additional anomalous components 
+$\Delta^p_{\a\b}\delta_{\s\overline{\s}}$, including intra- and inter-orbital pairings.
+%
+If full spin symmetry is not preserved, i.e. for {\tt ed\_mode} = {\bf nonsu2}, a further 
 set of parameters must be specified to account for spin-flip processes:
@@
 
-This hybrid topology of the bath captures the effects of locally
-hybridized impurity orbitals, but typically requires a more
-challenging optimization process, especially
-with few available bath levels (see \secu{sSecFit}).
-
-\paragraph{{\tt bath\_type}={\bf replica}/{\bf general}}
+The resulting total number of available bath parameters are 
+ $N_\mathrm{param}=N_\mathrm{bath}+ N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal},  
+ $N_\mathrm{param}=2N_\mathrm{bath}+ N_\a N_\mathrm{bath}$ if  {\tt ed\_mode}={\bf superc} or 
+$N_\mathrm{param}=N_\mathrm{bath}+ 2N_\a N_\mathrm{bath}$ for  {\tt ed\_mode}={\bf nonsu2}.
+
+\paragraph{{\tt bath\_type}={\bf replica},{\bf general}.}
 This configuration provides a more flexible parametrization of the 
@@
 where $\vec{\lambda}^p\in\RRR^{N_\mathrm{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired by the internal structure
+The choice of the matrix basis can be inspired by symmetry group considerations \cite{Senechal}, by the internal structure
 of the quantum impurity, i.e. $\hat{h}^0$, or determined
 case-by-case, depending on the desired properties of the solution.
-In this scheme, the total number of bath levels becomes $N_\mathrm{b}
-= N_\mathrm{imp} N_\mathrm{bath}$, while the number of independent bath
-parameters to optimize is (excluding the hybridization amplitudes)
-$N_\mathrm{params} = N_\mathrm{sym} N_\mathrm{bath}$.
-% Ocio!
+In this scheme, the total number of bath levels is  $N_\mathrm{b}
+= N_\a N_\mathrm{bath}$.
 
@@
 bath structure: $V^p_{\a\b\s\s'} = V^p$.
-In the {\bf general} case, this is generalized to include explicit 
+In the {\bf general} case, the coupling includes explicit 
 diagonal
@@
 = V^p_{\a\s}\delta_{\a\b}\delta_{\s\s'}$. 
-
-All the procedures concerning the bath, either on the user side or the
-internal {\tt effective\_bath}, are grouped into a set of modules
-wrapped by {\tt ED\_BATH}. We divided the set of modules in three
-categories, according to their scope.
+%
+The number of independent bath parameters to optimize is either 
+$N_\mathrm{params} = (N_\mathrm{sym}+1)N_\mathrm{bath}$ for {\tt bath\_type}={\bf replica} or 
+$N_\mathrm{params} = (N_\mathrm{sym}+N_\a N_\s)N_\mathrm{bath}$ for {\tt bath\_type}={\bf general}.
+
+We summarize the total number $N_s$ of electronic levels of the quantum impurity system according to the value of $N_\a$, $N_\mathrm{bath}$ and the bath topology in the following table:
+\begin{center}
+\begin{tabular}{ |c||c|c|c|c| } 
+ \hline     
+{\tt bath\_type} & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
+ \hline 
+  \hline    
+  $N_s$ & 
+ $(N_\mathrm{bath}+1)N_\a$ & 
+ $N_\mathrm{bath}+N_\a$ & 
+ $N_\a(N_\mathrm{bath}+1)$ & 
+ $N_\a(N_\mathrm{bath}+1)$  \\ 
+ \hline
+\end{tabular}
+\end{center}
+
+\vspace{2mm}
+All the procedures concerning the bath, either on the user side or concerning the internal {\tt effective\_bath}, are grouped into a set of modules wrapped by {\tt ED\_BATH}.
+We divided the set of modules in three categories, according to their scope.
 
@@
 {\tt ED\_BATH\_DIM}. The function {\tt ed\_get\_bath\_dimension} 
-calculates the required dimension $B$ for user-allocated bath 
+calculates the required dimension $N_\mathrm{params}$ for user-allocated bath 
 arrays, ensuring they contain exactly the necessary number of 
@@
 
-\paragraph{Bath Replica (General)}
-The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica} 
-for the {\bf replica} and {\bf general} bath parametrizations. In 
-addition to standard object construction, destruction, reading, and 
-saving, this module provides matrix basis setup 
-$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ and variational parameter 
-initialization through {\tt set\_Hreplica} (or {\tt set\_Hgeneral}). 
-The actual bath Hamiltonian is constructed with the function 
-{\tt build\_Hreplica} (or {\tt build\_Hgeneral}) via the relation
-$
-h^p = \vec{\lambda}^p \cdot \Gamma.
-$
-
-\paragraph{Effective Bath}
+The following table summarizes the total number of parameters $N_\mathrm{params}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:
+
+\begin{center}
+\begin{tabular}{ |c||c|c|c|c| } 
+ \hline     
+ $N_\mathrm{params}$ & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
+ \hline 
+ \hline    
+ {\bf normal} & 
+ $2N_\a N_\mathrm{bath}$ & 
+ $(N_\a+1)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+N_\a)N_\mathrm{bath}$\\
+ \hline
+   {\bf superc} & $3N_\a N_\mathrm{bath}$ & 
+ $(N_\a+2)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+N_\a)N_\mathrm{bath}$\\
+ \hline
+   {\bf nonsu2} & $3N_\a N_\mathrm{bath}$ & 
+ $(2N_\a+1)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
+ $(N_\mathrm{sym}+N_\a)N_\mathrm{bath}$\\
+ \hline
+\end{tabular}
+\end{center}
+
+\paragraph{Bath Replica (General).}
+The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica} ({\tt Hge\-ne\-ral}) for the {\bf replica}  ({\bf general}) bath parametrizations.
+In  addition to standard object construction, destruction, reading, and saving, this module provides matrix basis
+$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ setup as well as  the variational parameters $\vec{\lambda}$ initialization through {\tt set\_Hreplica} ({\tt set\_Hge\-ne\-ral}).
+
+The bath Hamiltonian is constructed with the function 
+{\tt build\_Hreplica} ({\tt build\_Hge\-ne\-ral}) via the relation:
+$$
+h^p = \vec{\lambda}^p \cdot \vec{\Gamma}.
+$$
+
+\paragraph{Effective Bath.}
 The module {\tt ED\_BATH\_DMFT} implements the class 
@@
 from scratch or reads them from a file specified by the input 
-variable {\tt Hfile}. Additionally, the class offers methods to 
+variable {\tt Hfile} as {\tt <Hfile>.restart}. Additionally, the class offers methods to 
 translate bath parameters between the internal {\tt dmft\_bath} 
@@
 {\tt get/set\_dmft\_bath}.
-
-% \begin{table}%[ht]
-%   \label{TabBath}
-% \begin{center}
-% \begin{tabularx}{\linewidth}{ |X|X|X|X| } 
-%   \hline
-%   c  & {\bf normal} & {\bf superc} & {\bf  nonsu2} \\
-%   \hline
-%   {\bf normal} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\a]$ & $\vec{\e}[N_\mathrm{b}],\vec{V}[N_\mathrm{b}]$ 
-%                     & $\vec{\e}[N_\mathrm{b}], \vec{\Delta}[N_\mathrm{b}],\vec{V}[N_\mathrm{b}]$
-%                                    &  $\vec{\e}[N_\mathrm{b}], \vec{V}[N_\mathrm{b}],\vec{W}[N_\mathrm{b}]$ \\
-%   \hline
-%   {\bf hybrid} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\a]$ & $\vec{\e}[N_\mathrm{bath}],\vec{V}[N_\mathrm{b}]$ 
-%                     & $\vec{\e}[N_\mathrm{bath}], \vec{\Delta}[N_\mathrm{bath}],\vec{V}[N_\mathrm{b}]$
-%                                    &  $\vec{\e}[N_\mathrm{bath}], \vec{V}[N_\mathrm{b}],\vec{W}[N_\mathrm{b}]$ \\
-%   \hline
-%   {\bf replica} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\mathrm{sym}]$ & \multicolumn{3}{*{\hat{h} } \cr
-%   \hline
-%   {\bf general} $[N_\mathrm{b}\!=\!N_\mathrm{bath}N_\mathrm{sym}]$ & \cline{2-4} & b&  c  \cr
-%   \hline
-% \end{tabularx}
-% \end{center}
-% \caption{Ciao}
-% \end{table}
 
@@
 \cite{P-Arpack}. This method incorporates re-orthogonalization within
-a block Lanczos routine, ensuring the accurate convergence of the
-desired eigenpairs. However, it is also possible to select a simpler,
-though less efficient, parallel Lanczos algorithm using the input
-variable {\tt lanc\_method}.
+a block-Lanczos routine, ensuring the accurate convergence of the desired eigen-pairs. However, it is also possible to select a simpler,
+though less efficient, parallel Lanczos algorithm using the input variable {\tt lanc\_method}.
 
@@
 \end{equation}
-This operation easily accounts for more than 80\% of the overall
+This operation accounts for more than 80\% of the overall
 computational effort, making its optimization a critical aspect of
-high-performance diagonalization algorithms. In \onlinecite{Amaricci2022},
-the distributed-memory, massively parallel strategies employed in \NAME
-to optimize this step are discussed in full detail. Here, we provide
-a brief outline of the main ideas, following the notation introduced
-in \onlinecite{Amaricci2022}, and focusing on the impact of the choice
-of {\tt ed\_mode}.
-
-\paragraph{\bf normal}
+high-performance diagonalization algorithms. In \onlinecite{Amaricci2022} we discussed in full details 
+the distributed-memory, massively parallel strategies currently employed in \NAME
+to optimize this step. Here, we provide
+a brief outline of the main ideas for the purely electronic case (i.e. neglecting electron-phonon part), following the notation introduced
+in \onlinecite{Amaricci2022}, and focusing on the impact of the choice of {\tt ed\_mode}.
+
+\paragraph{\bf normal}.
 In this case, the tensor structure of the Fock space and the sector
@@
 \begin{equation}
-H_\SS = H_\mathrm{d} + H_\up\otimes \mathbb{I}\dw + \mathbb{I}\up\otimes
+H_\SS = H_\mathrm{d} + H_\up\otimes \11_\dw + \11_\up\otimes
 H_\dw + H_\mathrm{nd},
@@
 break this structure require {\tt MPI\_AllGatherV}, introducing a
-slight communication overhead and reducing parallel efficiency.
-
-\paragraph{\bf superc/nonsu2}
+slight communication overhead which partially reduces the parallel efficiency.
+
+\paragraph{\bf superc/nonsu2.}
 For these modes, symmetries enforce specific constraints between
@@
 In an MPI setup, the first three terms contains also elements local to each node and
-stored separately within each {\tt sparse\_matrix} instance representing $H_\SS$.
-The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm which, as noted in
+stored separately within each {\tt sparse\_matrix} instance representing $H_\SS$ (see \secu{CodeSparseMatrix}).
+The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm which, as noted  
 \onlinecite{Amaricci2022}, requires reconstruction of distributed
 arrays and incurs significant communication overhead.
-
+\vspace{2mm}
+
+\noindent
 The diagonalization process itself is divided into two primary phases:
-
-\paragraph{\bf Global Setup}. This phase allocates the required memory, initializes
+\paragraph{\bf Global Setup.} This phase allocates the required memory, initializes
 the MPI environment, and configures the appropriate MVP procedure
@@
 The {\tt build\_Hv\_sector\_?} function builds the symmetry sector and
-allocates the MVP function but setting the shared abstract function pointer {\tt
-  sphtimesv\_p}. This latter step is controlled by the value of
-{\tt ed\_sparse\_H=True/False}. If {\tt True} the Hamiltonian $H_\SS$
+allocates the MVP function by setting the shared abstract function pointer {\tt
+  spHtimesV\_p} to the correct MVP function. 
+  This latter step is controlled by the value of
+{\tt ed\_sparse\_H=T/F}. If {\tt T} the Hamiltonian $H_\SS$
 gets stored in a {\tt sparse\_matrix} instance and used to perform
@@
   ED\_HAMILTONIAN\_?\_STORED\_HxV}
-If {\tt ed\_sparse\_H} is {\tt False} the MVP is operated on-the-fly,
+If {\tt ed\_sparse\_H} is {\tt F} the MVP is operated on-the-fly,
 i.e. each element of $H_\SS$ is directly applied to the input
@@
 The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of Dynamical Correlation Functions (DCF) using Krylov
-sub-space algorithm.
+enables the evaluation of the Dynamical Correlation Functions (DCFs) using Krylov sub-space algorithm.
 This capability is central to the library when using \NAME as an
@@
 \end{equation}
-where $z\in\CCC$,  $\ket{\psi_n}$, $E_n$ are the eigensolutions of the
+where $z\in\CCC$,  $\ket{\psi_n}$, $E_n$ are the eigen-solutions of the
 Hamiltonian $H$. 
@@
 $$
-where  $\ket{\psi_n}\in\SS$ and $\NN_n=\sqrt{\bra{\psi_n}\AA
+where  $\ket{\psi_n}\in\SS$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
   \AA^+\ket{\psi_n}}$.
-The Krylov basis is then constructed as $$\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
+The Krylov basis is constructed by repetead applications of the secctor Hamiltonian via MVP: 
+$$
+\mathcal{K}_{N} (\ket{\phi_n})=\{\ket{\phi_n}, H\ket{\phi_n}, \dots,
 H^N\ket{\phi_n}\}\equiv \{\ket{v^n_0}, \ket{v^n_1},\dots, \ket{v^n_N}
-\}$$ with $1 \ll N \ll \DD_\SS$, obtainaed by repeated applications of
-the (sector) Hamiltonian via MVP functions.
-
-Given that any eigenstate $\ket{\psi_n}$ can be expressed within the
-Krylov basis as
-$\ket{\psi_n} = \sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
-\sum_i a^n_i \ket{v^n_i}$. we can approximate the expression
-\equ{KLgf} as:  
+\}
+$$ 
+with $1 \ll N \ll \DD_\SS$..
+Given that any eigenstate $\ket{\psi_n}$ can be expressed within the Krylov basis as
+$$
+\ket{\psi_n} = \sum_i  \ibra v^n_i|\psi_n \iket  \ket{ v^n_i} =
+\sum_i a^n_i \ket{v^n_i}, 
+$$
+we can approximate the expression \equ{KLgf} as:  
 \begin{equation}
@@
 $C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
-This can addressed by introducing auxiliary operators, such as $\OO=\AA +\BB$ and
+This can be addressed by introducing auxiliary operators, e.g.  $\OO=\AA +\BB$ and
 $\PP=\AA-i\BB$, enabling the extraction of the desired function via
@@
 
-In \NAME, the computation of impurity Green's functions, such as
-$G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket$,
+In \NAME, the computation of the impurity Green's functions 
+$G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket$
 is handled by the \texttt{ED\_GREENS\_FUNCTIONS} module.
-This
-module integrates more specialized methods based on the symmetry
+This integrates more specialized methods based on the symmetry
 classification defined by the \texttt{ed\_mode} parameter.
-Moreove, in the {\bf normal} mod, it also includes spin, charge, pair, and excitonic
-susceptibility functions, providing a comprehensive framework for
-dynamical response calculations.
+Moreover, in the {\bf normal} mode, \NAME also includes spin, charge, pair, and excitonic susceptibility functions, providing a comprehensive framework for dynamical response calculations.
 From a computational perspective, the construction of the Krylov basis
@@
 diagonalization process, a significant performance gain is achieved through
-the parallel execution of the Matrix-Vector Product (MVP) at the core of
+the parallel execution of the MVP at the core of
 the Hamiltonian tri-diagonalization algorithm.
@@
 
-\paragraph{{\bf normal}}
+\paragraph{{\bf normal}.}
 In this mode, all orbital-dependent and spin-diagonal Green's 
-functions, $G_{\a\b\s\s}$, must be evaluated. The diagonal 
+functions $G_{\a\b\s\s}$ must be evaluated. The diagonal 
 case, where $\a=\b$, is straightforward and involves applying 
@@
 
-The sector Hamiltonian matrix in this mode is typically assumed 
-to be real symmetric, which significantly simplifies the evaluation 
-of the off-diagonal terms. In this case, the relation 
+The sector Hamiltonian matrix in this mode is assumed 
+to be real symmetric, which significantly simplifies the evaluation of the off-diagonal terms. In this case, the following symmetry relation 
 $G_{\a\b\s\s}=G_{\b\a\s\s}$ holds, allowing the computation of 
 off-diagonal components using an auxiliary operator 
-$\OO = c_{\a\s} + c_{\b\s}$ and the identity:
+$\OO=c_{\a\s}+c_{\b\s}$ and the identity:
 $G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
@@
 $\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$
-are constructed using the operators $\AA = \sum_{\s\s'} c^+_{\a\s}
-\tau^z_{\s\s'} c_{\a\s'} \equiv S^z_\a, $, 
-$\AA = \sum_{\s\s'} c^+_{\a\s} \tau^0_{\s\s'} c_{\a\s'} \equiv N_\a, $
-and $\AA = c_{\a\dw}c_{\a\up} \equiv \Delta_\a$,
+are constructed using the operators $S^z_\a = \sum_{\s\s'} c^+_{\a\s}
+\tau^z_{\s\s'} c_{\a\s'}$, 
+$N_\a = \sum_{\s\s'} c^+_{\a\s} \tau^0_{\s\s'} c_{\a\s'}$
+and $\Delta_\a = c_{\a\dw}c_{\a\up}$,
 where $\tau^{a=0,x,y,z}$ are the Pauli matrices.
-Off-diagonal terms are similarly evaluated using the operators
-$\AA=S^z_\a + S^z_\b$, $\AA=N_\a + N_\b$ or $\AA=\Delta_\a + \Delta_\b$. 
-Excitonic susceptibilities, $\chi^T_{\a\b}$, are defined with 
+Off-diagonal terms are  evaluated using the operators
+$(S^z_\a + S^z_\b)$, $(N_\a + N_\b)$ or $(\Delta_\a + \Delta_\b)$. 
+The Excitonic susceptibilities, $\chi^\vec{T}_{\a\b}$, are defined with 
 respect to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
 c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
-spin-singlet exciton, and $i=x,y,z$  correspond to the spin-triplet excitons.
-
-\paragraph{{\bf superc}}
+spin-singlet exciton, and $i=x,y,z$  correspond to the spin-triplet exciton.
+
+\paragraph{{\bf superc}.}
 In the supercondutive case, the Nambu orbital-dependent $s$-wave
-Green's function reads:
+Green's function has the form:
 \begin{equation}
@@
 
-\paragraph{{\bf nonsu2}}
-In the {\bf nonsu2} case, all Green's function components 
+\paragraph{{\bf nonsu2}.}
+In this case, all Green's function components 
 must be explicitly evaluated, as the spin and orbital 
-symmetries are not conserved. For the diagonal terms 
+symmetries are in general not conserved. For the diagonal terms 
 $G_{\a\a\s\s}$, the procedure follows the same approach 
@@
 through the thermal average 
-$\ibra \OO\iket = \frac{\Tr\left[e^{-\beta H}\OO\right]}{Z}$, 
+$\ibra \OO\iket = \tfrac{1}{Z}\Tr\left[e^{-\beta H}\OO\right]$, 
 where $Z = \sum_n e^{-\beta E_n}$ is the partition function. 
@@
 \ibra \OO\iket = \frac{1}{Z}\sum_n e^{-\beta E_n}
+\bra{\psi_n} \OO \ket{\psi_n}\simeq \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
 \bra{\psi_n} \OO \ket{\psi_n},
@@
 relevant, low-energy sector.
-\textcolor{red}{what's the difference with the one above}
-\begin{equation}
-  \ibra \OO\iket  = \tfrac{1}{Z}\sum_n e^{-\beta  E_n}
-  \bra{\psi_n}\OO\ket{\psi_n},
-  \label{eq:thermal_average}
-\end{equation}
-where $E_n$ and $\ket{\psi_n}$ are the low lying eigenstates of the
-system stored in the {\tt state\_list}.
-
-\subsection{Reduced impurity density matrix}\label{sSecRDM}
+
+\subsection{Impurity reduced density matrix}\label{sSecRDM}
 The latest version of \NAME introduces the calculation of the 
@@
 
-For simplicity, this section focuses on the zero-temperature limit, 
+For sake of simplicity, this section focuses on the zero-temperature limit, 
 assuming a non-degenerate ground state $\ket{\psi}$ present in the 
 {\tt state\_list}. The generalization to the finite-temperature regime 
-or degenerate ground states is straightforward, requiring only the 
-% replacement of the pure state average %%> What is a pure state average?
-introduction of an
+or degenerate ground states is straightforward, requiring only the  introduction of an
 ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
@@
 \end{equation}
-
 The iRDM is obtained by tracing out the bath degrees of freedom:
@@
 block structure of the Fock space defined by the symmetry sectors and
-the subsequent map sparsity, to perform the trace \emph{on-the-flight}. 
+the subsequent map sparsity, to perform the trace \emph{on-the-fly}. 
 This approach significantly reduces the computational cost by limiting 
@@
 
-%%% ATTENZIONE: this is true only for the normal case!
-%
-%Next, we decompose the Fock basis into spin-dependent impurity and 
-%bath parts. Any Fock state $\ket{I}$ can be split as:
-%$
-%\ket{I} = \ket{i_\uparrow \, b_\uparrow} \otimes 
-%\ket{i_\downarrow \, b_\downarrow},
-%$
-%where the impurity $i_\sigma$ and bath $b_\sigma$ states span subspaces of dimension 
-%$D^\s_\mathrm{imp}$ and $D^\s_\mathrm{bath}$, respectively, for each 
-%spin $\s = \uparrow, \downarrow$.
-%
-%%% I WOULD SAY THAT WE DON'T NEED TO REPEAT OURSELVES< THE SECTOR
-%%% SECTION IS THERE FOR A REASON. I try to edit below:
-To efficiently manage this decomposition, we introduce a 
+To efficiently manage this decomposition, we employ a 
 {\tt sparse\_map} ${\cal P}$, as detailed in \secu{CodeSparseMap}. 
@@
 
-\paragraph{{\bf normal}}
+\paragraph{{\bf normal}.}
 In this case, we take advantage of spin-resolved sector decomposition, 
@@
 
-In the {normal} mode, the iRDM is restricted to 
+In the {\bf normal} mode, the iRDM is restricted to 
 {spin-diagonal} blocks. This follows from the observation 
 that the conserved quantum numbers are 
-\emph{additive} quantities, given by
+\emph{additive} quantities, i.e. 
 $N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$,
@@
 Since the iRDM acts only on the impurity Fock space, this implies:
-% $$
-% U_{N_\s}^\dagger \rho^\mathrm{imp} U_{N_\s} = 
-% U_{N_\s^\mathrm{bath}}^\dagger \otimes U_{N_\s^\mathrm{imp}}^\dagger
-% \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} \otimes U_{N_\s^\mathrm{bath}} =
-% U_{N_\s^\mathrm{imp}}^\dagger
-% \rho^\mathrm{imp} U_{N_\s^\mathrm{imp}} =
-% \rho^\mathrm{imp},
-% $$
 \begin{equation}
@@
 \end{equation}
-demonstrating that $U_{N_\s^\mathrm{imp}}$ defines a symmetry of 
+showing that $U_{N_\s^\mathrm{imp}}$ defines a symmetry of 
 $\rho^\mathrm{imp}$, which is therefore block diagonal with respect to 
 the impurity quantum numbers $N_\s^\mathrm{imp}$.
-
 The resulting iRDM takes the form:
@@
     \sum_{q_\up=1}^{D_{q_\up}}
-    \Bigg( \cr
-    %
-    &\qquad
-    \sum_{b_\dw=1}^{D_{b_\dw}}
+    \Bigg(    \sum_{b_\dw=1}^{D_{b_\dw}}
     \sum_{i_\dw=1}^{D_{i_\dw}}
@@
     \sum_{q_\dw=1}^{D_{q_\dw}}
-    C_{i,p}\,C_{j,q}\,a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw}
+    C_{i,p}\,C_{j,q}\,a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw} \cr
+    %
+    &\qquad    
     \langle b_\up| p_\up\rangle| i_\up\rangle\langle j_\up |\langle q_\up| b_\up\rangle   \otimes \langle b_\dw| p_\dw \rangle|i_\dw\rangle \langle j_\dw  |\langle q_\dw| b_\dw\rangle \Bigg)
@@
 
-\paragraph{{\bf superc/nonsu2}}
+\paragraph{{\bf superc/nonsu2}.}
 For these lower-symmetry cases, the absence of a clean Fock space 
@@
 \begin{equation}
-\Delta_{\a\b\s\s'}(z) = \sum_\nu V^\nu_{\a\s} 
-\left( z\11 - h^\nu_{\a\b\s\s'} \right)^{-1} V^\nu_{\b\s'},
+\Delta_{\a\b\s\s'}(z) = \sum_p V^p_{\a\s} 
+\left( z\11 - h^p_{\a\b\s\s'} \right)^{-1} V^p_{\b\s'},
 \end{equation}
@@
 \end{equation}
-where $V^\nu_{\a\s}$ and $h^\nu_{\a\b\s\s'}$ are the bath coupling 
+where $V^p_{\a\s}$ and $h^p_{\a\b\s\s'}$ are the bath coupling 
 and bath Hamiltonian matrices, respectively, and $\mu$ is the chemical 
@@
 to different physical contexts. To maintain flexibility in \NAME, 
-we provide a general optimization interface that is independent 
+we keep the optimization part independent 
 from the core impurity solver. However, we also include a fully 
@@
 $\Delta_{\a\b\s\s'}$ are the corresponding quantities for the quantum 
-impurity model, as defined in \secu{sSecFunc}.
+impurity model, see \secu{sSecFunc}.
 
@@
 \item \texttt{cg\_stop=0,1,2} - Defines the exit condition of the 
-minimization. The options are:
+minimization corresponding, respectively, to the options  $C_1+C_2$, $C_1$ and $C_2$, with:
 \begin{align*}
@@
 algorithms of \NAME, including initialization, diagonalization, and 
-finalization, while preserving the original function names for 
-consistency.
-
-\paragraph{\bf Initialization} The function {\tt ed\_init} is extended to 
+finalization, while preserving the original function names for consistency:
+
+\paragraph{{\tt ed\_init}.} {\bf Initialization} of the solver. This function  extends the corresponding one in \NAME  to 
   accept a rank-2 bath array, where the leading dimension specifies 
@@
 
-\paragraph{\bf Diagonalization} The function {\tt ed\_solve} also accepts this 
-  rank-2 bath array and manages the diagonalization of each impurity 
+\paragraph{{\tt ed\_solve}.} {\bf Diagonalization} of the inequivalent quantum impurity problems. This function is extended to  accept a  
+  rank-2 bath array and to manage the diagonalization of each impurity 
   problem. Parallel execution is controlled by the input flag 
@@
 
-\paragraph{\bf Finalization} Memory release is handled through the extended 
-{\tt ed\_finalize} function, which clears the memory pool for all 
-inequivalent impurity instances.
+\paragraph{{\tt ed\_finalize}.} {\bf Finalization} of the solver.
+This handles the global memory release extending the corresponding  function in \NAME, which clears the memory pool for all inequivalent impurity instances.
 

### 2025-05-24 04_cbinding.tex
Merge updated from GitHub into OverLeaf. Co-authorhed-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 The recent growing availability of state-of-the-art software dedicated
-to the solution of quantum impurity problems using different methods
-poses a serious challenge to test accuracy and realiability of the
+to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}
+poses a serious challenge to test accuracy and reliability of the
 results.
@@
 compiled into a dynamical library {\tt
-  libedipack\_cbindings.so/.dylib}. As dicussed in the
+  libedipack\_cbindings.so (.dylib)}. As discussed in the
 \secu{sSecInstallBuildInstall}, the support for inequivalent
@@
 The C/C++ compatible functions and variables 
-are declared in the header file  {\tt edipack\_cbindings.h}.
+are declared in the header file {\tt e\-di\-pack\_c\-bin\-din\-gs.h}.
 Since {\tt ISO\_C\_BINDING} only provides, to date, C compatibility, the 
 functions and variables are declared with C linkage, which prevents name mangling.
-Function overloading is not supported, hence all interfaced Fortran functions,
-for example supporting multiple input variables combinations with different types
-and ranks, are here represented by multiple alternative functions.
-As an example, the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters, is callable in C++ in the following variants
+Function overloading is also not supported, hence all interfaced Fortran functions, for example supporting multiple input variables combinations with different types and ranks, are here represented by multiple alternative functions.
+As an example, the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters, is callable in C++ in the following variants:
 \begin{itemize}
-    \item  {\tt chi2\_fitgf\_single\_normal\_n3}: for {\tt ED\_MODE=NORMAL/NONSU2}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_normal\_n5}: for {\tt ED\_MODE=NORMAL/NONSU2}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_superc\_n3}: for {\tt ED\_MODE=SUPERC}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_superc\_n5}: for {\tt ED\_MODE=SUPERC}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_normal\_n3}: for {\tt ed\_mode=normal/nonsu2}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_normal\_n5}: for {\tt ed\_mode=normal/nonsu2}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n3}: for {\tt ed\_mode=superc}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n5}: for {\tt ed\_mode=superc}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
 \end{itemize}
-and analogous functions for the real-space DMFT case. All functions are listed and documented in the online manual.
+and analogous functions for the inequivalent impurities case, i.e. EDIpack2Ineq. All functions are thorougly listed and documented in the online manual.
 When using \NAME functions in a C/C++ program, care must be taken in the way arrays are passed.
@@
 procedures composing the Fortran API of \NAME, i.e. contained in {\tt
-  ED\_MAIN}. The procedures and shared variables can be divided in four main groups:
+  ED\_MAIN}. The procedures and shared variables can be divided in four main groups (note that contrary to the Fortran API the functions here lose the prefix {\tt ed\_}):
 
-\paragraph{{\bf Variables}}
+\paragraph{{\bf Variables}.}
 A number of relevant input and shared variables which are normally
@@
 
-\paragraph{{\bf Main}} This group contains interface to the exact
+\paragraph{{\bf Main}.} This group contains interface to the exact
 digonalization solver, interfacing the solver itself {\tt
@@
 
-\paragraph{{\bf Bath}} In this group we implement a number of
+\paragraph{{\bf Bath}.} In this group we implement a number of
 procedures dealing with bath initialization, symmetry operations and
@@
   get\_bath\_dimension} as well as the setup of the matrix basis
-$\vec{\Gamma}$ for the replica/general bath via different instances of
-{\tt set\_Hreplica/general\_{site,lattice}\_d{3,5}}. 
-The crucial part in the DMFT-Lanczos self-consistency loop is the optimization of the bath
-through conjugate-gradient algorithm. To this end we interfaced a
+$\vec{\Gamma}$ for the replica (general) bath via different instances of
+{\tt set\_Hreplica(general)\_\-\{site,lattice\}\_d\{3,5\}}. 
+A crucial part of the DMFT self-consistency loop is the optimization of the bath through CG algorithm (see \secu{sSecFit}). To this end we interfaced a
 number of functions {\tt
-  chi2\_fitgf\_{single,lattice}\_{normal,superc}\_n{3,4,5,6}} which
+  chi2\_fitgf\_\{single,lattice\}\_\{normal,superc\}\_n\{3,4,5,6\}} which
 cover all the cases supported in \NAME. Note that, because the actual
@@
 
-\paragraph{{\bf Input/Output}}
+\paragraph{{\bf Input/Output}.}
 The input and output part of the software is interfaced in this group
-of functions. In particular, {\tt read\_input} expose to C the input
-reading procedure of \NAME which set essentially set all the internal
+of functions. In particular, {\tt read\_input} exposes to C the input
+reading procedure of \NAME which set all the internal
 variables of \NAME.
-Next, in {\tt edipack{2ineq}\_c\_binding\_io} we interface all the
+Next, in {\tt edipack\{2ineq\}\_c\_binding\_io} we interface all the
 functions implementing the communication from the \NAME instance to
@@
   get\_dens}), the impurity Green's functions and self-energies
-(e.g. {\tt get\_Sigma\_{site,lattice}\_n{3,5}}), the
+(e.g. {\tt get\_Sigma\_\{site,lattice\}\_n\{3,5\}}), the
 impurity susceptibilities (e.g. {\tt get\_spinChi}), the impurity reduced density matrix as well
-as the non-interacting Green's and hybridization functions starting from the
-user bath array.
+as the non-interacting Green's and hybridization functions starting from the user bath array.
 
@@
 based software. Detailed documentation can be found online at \href{https://edipack.github.io/EDIpack2py}
-{https://edipack.github.io/EDIpack2py}.
+{edipack.github.io/EDIpack2py}.
 
 \subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
-\paragraph{From source}
+\paragraph{From source.}
 EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
@@
 
-\paragraph{PyPi}
+\paragraph{PyPi.}
 The EDIpack2py package is also available in PyPi at
@@
 
-\paragraph{Anaconda}
+\paragraph{Anaconda.}
 As for \NAME, the Python API in EDIpack2py is available as an
@@
 %taken care from Conda itself. 
-Using conda or mamba the installation proceeds as following:
+Using Conda or Mamba the installation proceeds as following:
 \begin{lstlisting}[style=mybash]
-conda create -n edipack  #creation of a virtual environment (name can be changed)
-conda activate edipack   #activation of the virtual environment
-conda install -c conda-forge -c edipack edipack #installation from the edipack channel
+conda create -n edipack  #create a virtual environment
+conda activate edipack   #activate it
+conda install -c conda-forge -c edipack edipack #install edipack
 \end{lstlisting}
 
-When the{\tt EDIpack2py} module is imported, it attempts to load the dynamic library {\tt
-  libedipack\_cbindings.so/.dylib} containing the Fortran-C bindings
+\noindent
+When the {\tt EDIpack2py}    module is imported, it attempts to load the dynamic library {\tt
+  libedipack\-\_cbindings.so (.dylib)} containing the Fortran-C bindings
 for \NAME. By default the library search proceeds as follow: 
@@
 
-\paragraph{{\bf Global variables}}
+\paragraph{{\bf Global variables}.}
 This includes a subset of the input variables available in \NAME which
@@
 
-\begin{lstlisting}[language=python,  frame=lines]
+\begin{lstlisting}[style=mypython,frame=lines]
 import numpy as np
@@
 
-\paragraph{{\bf Solver functions}}
+\paragraph{{\bf Solver functions}.}
 This group includes a number of functions enabling initialization,
@@
 
-\paragraph{{\bf Bath functions}}
+\paragraph{{\bf Bath functions}.}
 This set covers the implementation of utility functions handling the
@@
 
-\paragraph{{\bf Input/Output functions}}
+\paragraph{{\bf Input/Output functions}.}
 This group includes functions which return to the userspace
@@
 
-\paragraph{{\bf Auxiliary functions}}
+\paragraph{{\bf Auxiliary functions}.}
 This group include some auxiliary functions, either interfacing \NAME
@@
 
-\subsection{EDIpack2Triqs, the TRIQS interface}\label{sSecInteropTRIQS}
+\subsection{EDIpack2Triqs: the TRIQS interface}\label{sSecInteropTRIQS}
 A thin compatibility layer between \NAME and the Toolbox for Research on
-Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called edipack2triqs
-is available as a stand-alone project. It is a pure Python package
-built upon \NAME's Python API  (Sec.~\ref{sSecInteropEDIpy}) that provides a
+Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called EDIpack2Triqs
+is available as a stand-alone project. This is a pure Python package
+built upon \NAME's Python API EDIpack2py (see \secu{sSecInteropEDIpy}) that provides a
 limited object-oriented interface to the most important features of \NAME.
-edipack2triqs strives to offer seamless interoperability with program tools
+EDIpack2Triqs strives to offer seamless interoperability with program tools
 based on TRIQS by adopting data types, conventions and usage patterns
@@
 found online at \href{https://krivenko.github.io/edipack2triqs/}
-{https://krivenko.github.io/edipack2triqs/}.
+{krivenko.github.io/edipack2triqs/}.
 
@@
 and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
-installed in the OS, the current development version of edipack2triqs can be 
+installed in the OS, the current development version of EDIpack2triqs can be 
 installed with {\tt pip} from its 
@@
 
-\paragraph{Anaconda}
+\paragraph{Anaconda.}
 Another option for installing the package is by using the Anaconda package 
@@
 The following commands will create a new {\tt conda} environment named 
-`edipack' and install the most recently released version of edipack2triqs along 
+`edipack' and install the most recently released version of EDIpack2triqs along 
 with its dependencies (\NAME, EDIpack2py and the TRIQS libraries).
@@
 \subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
-The programming interface of edipack2triqs is built around the singleton 
-Python class {\tt EDIpackSolver} (defined in the module
-{\tt edipack2triqs.solver}), whose instance represents the internal state of 
+The programming interface of EDIpack2triqs is built around the singleton 
+Python class {\tt EDIpackSolver}, defined in the module
+{\tt edipack2triqs.solver}, whose instance represents the internal state of 
 the \NAME library and exposes its functionality through a number of 
@@
 
-\paragraph{{\bf Constructor}}
+\paragraph{{\bf Constructor}.}
 Constructor of {\tt EDIpackSolver} accepts the Hamiltonian to be diagonalized
@@
 the underlying Fortran library and automatically selects the appropriate
-{\tt ed\_mode=normal,superc,nonsu2} (Sec.~\ref{sSecQNs}) and
-{\tt bath\_type=normal,hybrid,general} (Sec.~\ref{sSecBath}). In addition, the
+{\tt ed\_mode} (see Sec.~\ref{sSecQNs}) and
+{\tt bath\_type} (see Sec.~\ref{sSecBath}). In addition, the
 constructor accepts a vast array of keyword arguments that allow for fine-tuning
@@
 
-\paragraph{{\bf Method {\tt solve}}}
+\paragraph{{\bf Method {\tt solve}}.}
 The method {\tt solve()} of {\tt EDIpackSolver} calls
@@
 
-\paragraph{{\bf Input parameters}}
+\paragraph{{\bf Input parameters}.}
 It is possible to read off and change parameters of the Hamiltonian between
@@
     \item {\tt hloc} --- matrix $h^0_{\alpha\beta\s\s'}$ of
-          the quadratic impurity Hamiltonian (\ref{Himp}).
+          the quadratic impurity Hamiltonian \equ{Himp}.
     \item {\tt Uloc}, {\tt Ust}, {\tt Jh}, {\tt Jx}, {\tt Jp} ---
           parameters $U, U', J, J_X \text{ and } J_P$ of the impurity
-          interaction term $\hat{H}^\mathrm{int}_\mathrm{imp}$ (\ref{Hint}).
+          interaction term $\hat{H}^\mathrm{int}_\mathrm{imp}$ \equ{Hint}.
     \item {\tt bath} --- an object representing the bath. Depending on the
@@
 
-\paragraph{{\bf Calculation results}}
+\paragraph{{\bf Calculation results}.}
 After a successful invocation of {\tt solve()}, one can extract results of the 
@@
           $\phi_{\alpha\beta} = \langle c_{\alpha\up} c_{\beta\down}\rangle$
-          in orbital space. {\color{red} Is it defined elsewhere in the text?}
+          in orbital space.
     \item {\tt g\_iw}, {\tt g\_an\_iw} --- Normal and anomalous components of
@@
 
-\paragraph{{\bf Bath parameter fitting}}
+\paragraph{{\bf Bath parameter fitting}.}
 The method {\tt EDIpackSolver.chi2\_fit\_bath()} is essentially a wrapper around
@@
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-\NAME is supported as alternative impurity solver by the w2dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{GitHub}.
+\NAME is supported as alternative impurity solver in the W2Dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
 The only prerequisite to use this option is the presence of a functioning EDIpack2py installation, which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
 
-In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to \NAME.
+In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
 
-The  behavior of the w2dynamics solver is controlled by means of an input file, by default called
+The  behavior of the W2Dynamics solver is controlled by means of an input file, by default called
 {\tt Parameters.in}. In order to configure the ED solver, the content of a specific section in the parameters file, called {\tt [EDIPACK]}, has to be modified.
 
-For most of the \NAME input variables, w2dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt EDIPACK} section of the parameters file.
-This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath sites {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
+For most of the \NAME input variables, W2Dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt EDIPACK} section of the parameters file.
+This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath elements {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
 
-A second set of input variables, including phyisical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the w2dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
-An example of a properly formatted input file is provided in~\ref{SecExamples}.
+A second set of input variables, including phyisical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the W2Dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
+An example of a properly formatted input file is provided in \secu{SecExamples}.
 See~\cite{Wallerberger2019CPC}
@@
 
-Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by w2dynamics in a way closely resembling the standard the CT-HYB code.
-For example, results such as the Green's functions are stored into the w2dynamics HDF5 output file in the typical format, and that w2dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
-As a consequence of this, some functionality that would require specific support from w2dynamics that is not available as of the time of publication can not be used through the interface, for instance calculations with {\tt ED\_MODE=SUPERC} or with phonons.
+Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard the CT-HYB code.
+For example, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format, and that W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+As a consequence, functionalities that would require specific support from W2Dynamics and which are currently under development can not yet be used through the interface.
+For instance the solution of impurity problems in the superconductive phase, i.e.
+{\tt ed\_mode=superc}, or in presence of local phonons will only be available in the next future through an updated of W2Dynamics package.
 
 \subsection{EDIpack2jl, the Julia API}\label{sSecInteropEDIjl}
-
-The c-bindings approach is extremely handy, in that is opens the way for interoperability 
-with a large number of languages and frameworks. As an example, an experimental Julia API 
-is provided in the EDIpack github repository. Rather than a fully functioning Julia package, 
-this is at present a proof of concept, capable of replicating the results of Fortran, C++ and
-python implementations for the Bethe lattice example driver.
+The C-binding approach is extremely handy, in that it opens the way for interoperability  with a large number of languages and frameworks. 
+As a further significant example, an experimental Julia API 
+is provided for \NAME. Although this is at the present a proof of concept, it is capable of replicating the results of Fortran, C++ and
+Python implementations for the Bethe lattice example driver.
 Its structure and operation mimicks that of the EDIpack2py layer, with minimal language-specific differences.
 
-The \NAME{} Julia api consists of a module called {\tt EDIpack2jl}, which provides access to the global variables and functions contained in {\tt  libedipack\_cbindings.so/.dylib}.
+The \NAME{} Julia API consists of a module called {\tt EDIpack2jl}, which provides access to the global variables and functions contained in {\tt  libedipack\_cbindings.so (.dylib)}.
 
@@
 and the location of the source files needs to be included in the user program via
-
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=myjulia]
 push!(LOAD_PATH, joinpath(@__DIR__, "PATH/TO/REPO/src"))
@@
 The EDIpack2jl module can then be loaded via
-
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=myjulia]
 using EDIpack2jl
@@
 The correct way to access global variables and functions is as in the following example:
-
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=myjulia]
 EDIpack2jl.read_input("inputED.conf")

### 2025-05-24 05_examples.tex
Merge updated from GitHub into OverLeaf. Co-authorhed-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
   \begin{minipage}{0.465\linewidth}
-    \center{\bf Fortran}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
    complex(8),allocatable :: Delta(:,:,:,:,:)
-   ...  
+   !...  
    !Read variables
@@
    allocate(Delta(Nspin,Nspin,Norb,Norb,Lmats))
-   allocate(Hloc(Nspin,Nspin,Norb,Norb));Hloc=0d0
-   ...
+   allocate(Hloc(Nspin,Nspin,Norb,Norb))
+   Hloc=0d0
+   !...
    !Initialize Bethe arrays
@@
   \begin{minipage}{0.505\linewidth}
-    \center{\bf C++}
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 using namespace std;
-...
+!...
 //Main variables
@@
 \begin{tabular}{c|c}\label{list2}
+{\bf Fortran} & {\bf C++}\\
   \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
@@
 
-\item[{\tiny $\blacksquare$}] Call the exact diagonalization {\bf impurity solver}
+\item[{\tiny {\bf EDIpack}}] Call the exact diagonalization {\bf impurity solver}
   whose only input is the set of parameters $\vec{x}$ contained in a
@@
 
-\item[{\tiny $\blacksquare$}] Retrieve the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
+\item[{\tiny {\bf EDIpack}}] Retrieve the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
   Matsubara axis using dedicated function provided by \NAME API.
 
-\item[{\tiny $\blacktriangleright$}] Evaluate the local interacting Green's function
+\item[{\tiny {\it User}}] Evaluate the local interacting Green's function
   $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
@@
 
-\item[{\tiny $\blacktriangleright$}] Update the Weiss field via the {\bf self-consistency}
+\item[{\tiny {\it User}}] Update the Weiss field via the {\bf self-consistency}
   relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
@@
 
-  \item[{\tiny $\blacktriangleright$}] Optimize the bath parameters $\vec{x}$ against the updated
+  \item[{\tiny ${\it User} $>$ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
     Weiss field,  potentially using the conjugate gradient procedures 
@@
 
-The first two steps, marked by the ${\tiny \blacksquare}$ symbol, 
-are handled directly by \NAME routines. In the subsequent steps, 
-indicated by the ${\tiny \blacktriangleright}$ symbol, control returns 
-to the user, who must implement the algebraic updates required to 
+The first two steps are handled directly by \NAME routines, while during the subsequent steps the 
+ control returns to the user, who must implement the algebraic updates required to 
 close the self-consistency loop and optimize the bath.
@@
 
-\paragraph{Results}
+\paragraph{Results.}
 In the following, we present results for the interaction-driven Mott 
@@
 def h_square2d(k,t):
-  return -2*t*(np.cos(k[...,0,np.newaxis,np.newaxis])+np.cos(k[...,1,np.newaxis,np.newaxis]))*np.eye(ed.Norb)
+  return -2*t*( np.cos(k[...,0,np.newaxis,np.newaxis])+
+                np.cos(k[...,1,np.newaxis,np.newaxis]))*np.eye(ed.Norb)
 
@@
 
-\paragraph{Results}
+\paragraph{Results.}
 Here we showcase some results for the DMFT solution of the 
@@
 
-\subsection{Interacting Kane-Mele model (Fortran API, EDIpack2ineq layer)}
+\subsection{Interacting Kane-Mele model (Fortran API, EDIpack2ineq layer, iRDM)}
 
@@
 model for interacting quantum spin-Hall insulators, defined on the honeycomb lattice, with two inequivalent sites in the unit-cell.
-
 Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit-cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
@@
 nearest-neighbor hopping amplitude and $\lambda_\mathrm{so}$ is 
-the amplitude of a complex next-nearest-neighbor hopping amplitude,
-with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling and well-known to stabilize a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
+the amplitude of a complex next-nearest-neighbor hopping,
+with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling, which is well-known to open a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
 The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$, are 
@@
 The essential features of the groundstate phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
-For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio
-\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
+For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
 at the Fermi level renders ineffective the logarithmic instability, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
@@
 Furthermore, the long-range ordering
-eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization.
+eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
 \cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRBa,Rachel2010PRB} and
@@
 comparing with \ref{eq:replica_bath_sym}, it is clear 
-that this amount to having $N_\mathrm{sym}=2$, with
-$\lambda_{1,p} \equiv \epsilon_p$ describing average
-bath levels and $\lambda_{2,p} \equiv m_p$ allowing 
-a magnetic split, respectively in the $S_z$ and $S_x$ spin bases.
+that this amounts to having $N_\mathrm{sym}=2$, with
+$\lambda_{1,p} \equiv \epsilon_p$ as the degenerate
+bath levels that are Zeeman split by $\lambda_{2,p} \equiv m_p$, respectively in the $S_z$ and $S_x$ bases.
 
@@
 a wide range of $U/t$ and $\lambda_\mathrm{so}$ values. To assess the
-degree of accuracy of our total energy calculation, we benchmark against
+degree of accuracy of our total energy calculation, we report in
+\figu{fig:KMenergy}(b) a $\lambda_\mathrm{so}=0$ benchmark against
 Hartree-Fock (simple static mean-field, but inherently variational), 
 DMFT with NRG solver and lattice AFQMC data, as taken from 
-Ref.\,\cite{Racz2020}. The total energy comparison is reported in 
-\figu{fig:KMenergy}(b), for $\lambda_\mathrm{so}=0$.
+Ref.\,\cite{Racz2020}.
 
@@
     \includegraphics[width=0.45\linewidth]{figures/benchEnergy_honey.pdf}\\
-    \caption{In panel (a) the total energy difference between the in-plane 
-    and off-plane AFM solutions found in DMFT-ED at $T=0$. Negative values
+    \caption{In panel (a) we report the total energy difference between 
+    the in-plane and the
+    off-plane AFM solutions found with \NAME at $T=0$. Negative values
     signal a groundstate with in-plane magnetization. The plateau at zero
@@
     paramagnetic quantum spin-Hall insulator), at all points except on the $\lambda_\mathrm{so}=0$ line, where the groundstate is an interacting
-    Dirac liquid, at weak coupling, or an isotropic antiferromagnet at strong coupling. In panel (b) we compare the total energies across the 
-    $\lambda_\mathrm{so}=0$ line to published data for Hartree-Fock,
+    Dirac liquid, at weak coupling, or an isotropic antiferromagnet at strong coupling. In panel (b) we compare the total energies, across the 
+    $\lambda_\mathrm{so}=0$ line, to published data for Hartree-Fock,
     DMFT-NRG and AFQMC solutions \cite{Racz2020}.}
@@
 
+\begin{figure}
+    \centering
+    (a) \hspace{12cm} (b) \\
+    \includegraphics[width=0.8\linewidth]{figures/flakes_edipack.pdf}\\[3mm]
+    (c) \hspace{12cm} (d) \\
+    \hspace{1.2cm}
+    \includegraphics[width=0.33\linewidth]{figures/3NflakeU4.5_x.pdf} \hspace{1.2cm}
+    \includegraphics[width=0.33\linewidth]{figures/3NflakeU6_x.pdf} \vspace{3mm}
+    \caption{Kane-Mele-Hubbard model at the nanoscale.
+    In (a) the local in-plane
+    magnetization $n_{i,\rightarrow}-n_{i,\leftarrow}$. In
+    (b) the local correlation as measured by the mutual 
+    information between local in-plane spin eigenstates
+    $I(\rightarrow:\leftarrow)$ \cite{BellomiaPhD}. Both the
+    (a)-(b) panels mark the edge and "bulk" sites in lighter 
+    and darker colors, respectively.
+    In (c) and (d) a visual representation of the given 
+    nano-system at different values of $U/t$, as marked 
+    respectively by the orange and red vertical lines 
+    in panels (a) and (b). The area of the 
+    circles is proportional to $I(\rightarrow:\leftarrow)$, 
+    the length of the arrows to the local magnetization.
+    All data are taken at $\lambda_\mathrm{so}=0.3t$ and $T=0$.}
+    \label{fig:KMflake}
+\end{figure}
+
+\subsubsection{Kane-Mele Nanoflakes}
+The capabilities of the EDIpack2ineq layer go well beyond the
+simple case of a two-site unit-cell. We can readily adapt the
+code to deal with nanoscopic systems such as hexagonal flakes
+\cite{Valli2016PRB,Valli2018NL}, by building a
+$N_\mathrm{ineq}\times N_\mathrm{ineq}$ local Hamiltonian 
+$H_\mathrm{loc}$ with open boundary conditions, and implementing
+the self-consistent equations with a trivial single momentum 
+$k=0$. With respect to the infinite lattice, it is expected that
+the system develops an inhomogeneous magnetization, so the number
+of impurity models to solve cannot be halved by imposing the usual
+Néel symmetry. Some lowered point symmetry can be found, but a 
+safer approach of solving all the $N_\mathrm{ineq}$ impurity models
+leads to good results, with fair control of spatial numerical noise.
+
+In \figu{fig:KMflake} we report results for a nanosystem of 
+$N_\mathrm{ineq}=54$ sites, solved with the bath parametrization 
+described in \equ{eq:afmx_dmft_ansatz}, for the in-plane 
+antiferromagnetic state.
+Panel (a) shows the interaction dependence of the local magnetization,
+computed from the impurity groundstate as  
+$ \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket$,
+so that we can define the $S_x$ spin-occupation numbers as
+\begin{equation*}
+    n_{i,\rightarrow} \equiv \frac{n_{i,\up} + n_{i,\dw} +
+    \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket}{2},
+    \qquad
+    n_{i,\leftarrow} \equiv \frac{n_{i,\up} + n_{i,\dw} -
+    \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket}{2},
+\end{equation*}
+which trivially satisfy the conservation of the local average charge $n_{i,\rightarrow} + n_{i,\leftarrow} = n_{i,\up} + n_{i,\dw}$.
+Having a direct expression for $n_{i,\rightarrow}$ and $n_{i,\leftarrow}$
+we can verify that the impurity reduced density matrix, computed by 
+tracing the bath states in the \texttt{ed\_mode=nonsu2} representation 
+(see \ref{sSecRDM}), once diagonalized, takes the familiar form
+\cite{XiDai2013,WalshLetter2019,BellomiaPhD,BellomiaKMH,Bellomia_intracorr} 
+\begin{equation}
+    \rho^\mathrm{imp} = 
+     \begin{pmatrix}
+            \left\ibra\left(1-n_{i,\rightarrow}\right)\left(1-n_{i,\leftarrow}\right)\right\iket   &    0          &       0       &   0 \\
+                    0       &    \left\ibra n_{i,\rightarrow}\left(1-n_{i,\leftarrow}\right)\right\iket  &       0       &   0 \\
+                   0       &       0   &    \left\ibra\left(1-n_{i,\rightarrow}\right)n_{i,\leftarrow}\right\iket      &   0 \\
+                    0       &       0   &       0          &    \left\ibra n_{i,\rightarrow} n_{i,\leftarrow}\right\iket
+        \end{pmatrix} 
+\end{equation}
+in the basis of the \emph{natural} spin-orbitals, whose occupation numbers
+are given by $n_{i,\rightarrow}$ and $n_{i,\leftarrow}$.
+
+As extensively discussed in \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr},
+by defining the spin traces of $\rho^\mathrm{imp}$, as
+\begin{equation}
+    \rho^\mathrm{imp}_\sigma = 
+    \Tr_{\bar{\sigma}} \left[\rho^\mathrm{imp}\right] =
+    \begin{pmatrix}
+        \ibra n_{i,\sigma} \iket & 0 \\
+        0 & \ibra n_{i,\bar{\sigma}} \iket
+    \end{pmatrix}
+\end{equation}
+we can directly measure local correlations by defining the mutual information
+between the impurity spin-orbitals
+$I(\rightarrow:\leftarrow) = 
+    S(\rho^\mathrm{imp}_{\rightarrow}) + 
+    S(\rho^\mathrm{imp}_{\leftarrow}) -
+    S(\rho^\mathrm{imp})$,
+where $S(\cdot)$ denotes the von Neumann entropy of its argument.
+
+In panel (b) of \figu{fig:KMflake} we report the spatially resolved
+interaction dependency of $I(\rightarrow:\leftarrow)$, as a direct 
+observation of the enhanced local correlations at the boundary of the
+finite system. While it is usually assumed that edge sites must be
+more correlated than internal ("bulk") sites, based on the reduced
+lattice coordination, the inter-spin mutual information beautifully
+highlights in a quantitative fashion the phenomenon: the edge correlations,
+marked in lighter green, are decidedly higher as long as the system 
+remains in a weakly magnetized regime. When the local magnetization
+exceeds half of its saturation value, all local correlations start to decrease,
+as spin fluctuations are damped by ordering. Significantly, the edge 
+correlations get lower than the bulk correlations as the maximum is 
+crossed, consistently with the observation that their magnetization
+is always higher and so their fluctuations are frozen faster.
+Finally, we observe that the nanosystem of \figu{fig:KMflake} has 
+finite local magnetization for arbitrary low interaction strengths,
+in striking contrast with the infinite lattice. This is a well-known
+effect of quantum confinement, as proposed in early works on graphene
+flakes \cite{Valli2016PRB,Valli2018NL}.
+
 \end{document}

### 2025-05-24 06_conclusions_acknowledgement_appendix.tex
Intermediate Writing the KM example
Added my funding information
Updated Manuscript. Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% TODO: include author contributions
+\paragraph{Author contributions}
+This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section*{Acknowledgements}
+We acknowledge helpful discussions, occurring at diverse stages of development of \NAME, with: Carlos Mejuto Zaera, Pablo Villar Arribi, Maria Chatzieleftheriou, Marcello Dalmonte, Mario Collura, Cedric Weber, Alberto Camjayi, Marcelo Rozenberg, ...
+
+% TODO: include author contributions
+% This will be used to better attribute supervision of each part of the code, e.g.
+LC for part of the code, C-binding, Py, Julia, Monicelli, etc, IK for EDIpack2Triqs, AK+MW+GS for W2Dyn support, etc.
+\paragraph{Author contributions}
+This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
+
+% TODO: include funding information
+\paragraph{Funding information}
+L.C.
+acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994).
+Ratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb.
+NHR funding is provided by federal and Bavarian state authorities.
+NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
+I.K. acknowledge support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
+%S.G.
+%G.B
+%A.K.
+%F.P
+%M.W.
+%G.M.
+%L.dM.
+%G.S.
+%M.C.
+%A.A.
 
@@
 In order to further showcase the interoperability capabilities of
-\NAME provided by the C-bindings module, we describe a simple interface to {\tt Monicelli}, see
-\href{github.com/esseks/monicelli.git}{ttps://github.com/esseks/monicelli.git}.
+\NAME provided by the C-bindings module, we describe a simple interface to {\tt Monicelli}.
 

### 2025-05-24 03_edipack2.tex
Updates from Overleaf

@@
 This map is typically implemented as a rank-1
-integer array whose size corresponds to the dimension of the sector $D_{\SS_\vec{Q}}$$.
+integer array whose size corresponds to the dimension of the sector $D_{SS_{\vec{Q}}}$.
 
@@
 a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
-$D_{\SS_\vec{Q}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+$D_{\SS_{\vec{Q}}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
 basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix.
@@
 coefficient indices are swapped compared to the standard two-body
-operator formulation \cite{??}.  
+operator formulation $$
+\frac{1}{2}\sum_{i,j,k,l} c^{\dagger}_i c^{\dagger}_j U_{ijkl} c_l c_k
+$$ 
 Empty lines and lines starting with {\tt \#, \%, !} are ignored.
@@
    integer                     :: size               !Current list
-   real(8)                     :: emax               !Max energy  fixed by ${\color{}e^{-\beta {\tt emax}}<{\tt cutoff}}$
+   real(8)                     :: emax               !Max energy  fixed by ${e^{-\beta {\tt emax}}<{\tt cutoff}}$
    real(8)                     :: emin               !Min energy:the groundstate energy
@@
 $(S^z_\a + S^z_\b)$, $(N_\a + N_\b)$ or $(\Delta_\a + \Delta_\b)$. 
-The Excitonic susceptibilities, $\chi^\vec{T}_{\a\b}$, are defined with 
+The Excitonic susceptibilities, $\chi^{\vec{T}}_{\a\b}$, are defined with 
 respect to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}

### 2025-05-24 05_examples.tex
Updates from Overleaf

@@
 
-  \item[{\tiny ${\it User} $>$ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
+  \item[{\tiny {\it User} \textgreater\ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
     Weiss field,  potentially using the conjugate gradient procedures 

### 2025-05-26 03_edipack2.tex
Updates from Overleaf

@@
 which describes a multi-orbital quantum impurity
-coupled to an electronic bath and local phonons (e.g., Holstein
-modes). For now, we assume no specific symmetries.
+coupled to an electronic bath and local \fixme{phonons (e.g., Holstein
+modes)}. For now, we assume no specific symmetries.
 
@@
 
-Destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
-respectively, act on the Fock space as:
+\fixme{Destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
+respectively, act on the Fock space as}:
 \begin{align*}
@@
 \subsection{Conserved quantum numbers}\label{sSecQNs}
-To mitigate the exponential scaling of the Fock space dimension, it 
+To mitigate the exponential scaling of the \fixme{Fock space dimension}, it 
 is essential to exploit suitable symmetries. Specifically, if the 
@@
 This map is typically implemented as a rank-1
-integer array whose size corresponds to the dimension of the sector $D_{SS_{\vec{Q}}}$.
+integer array whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$.
 
@@
 (first column) correspond different quantum numbers (second column).
-The third column report the dimension of the symmetry sector for a
-given realization of the quantum numbers.}
+The third column report the dimension of the electronic symmetry sector $\SS_{\vec{Q}}$ for a
+given value of the quantum numbers $\vec{Q}$.}
 \end{table}
@@
 One of the main goal of the \NAME is to evaluate dynamical correlations
-functions (DCF), e.g. $D(t) = \ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,
-these DCFs can be expressed as truncated Kallen-Lehmann spectral sums of the form
-$$
-D(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
+functions (DCF), e.g. $C(t) = \ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,  
+these DCFs can be expressed as truncated K\"all\'en-Lehmann spectral sums of the form
+$$
+C(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
   - dE_{mn}}
@@
 \begin{lstlisting}[style=fstyle,numbers=none]   
-!The contributions to the GF Kallen-Lehmann sum are stored as
+!The contributions to the GF K\"all\'en-Lehmann sum are stored as
 !GF_{ab,sr}%state%channel%{w,e}.
@@
 !Each instance of this sub-class correponds to a given input state 
-!and a given operator in the Kallen-Lehman representation.  
+!and a given operator in the K\"all\'en-Lehmann representation.  
 type GFchannel
@@
 \subsection{Lanczos based Diagonalization}\label{sSecHam}
+
 In presence of symmetries (see \secu{sSecQNs}) the matrix representing
@@
 
-\paragraph{\bf normal}.
-In this case, the tensor structure of the Fock space and the sector
+\fixme{Again: this discussion is only for the electronic part. We need to state we focus on that here and discuss the modifications requied to deal with phonons at the end of this section}
+
+In the {\bf normal} case, the tensor structure of the Fock space and the sector
 symmetries are fully leveraged. Within a given sector, the electronic
@@
 \begin{equation}
-H_\SS = H_\mathrm{d} + H_\up\otimes \11_\dw + \11_\up\otimes
+H^e_{\SS} = H_\mathrm{d} + H_\up\otimes \11_\dw + \11_\up\otimes
 H_\dw + H_\mathrm{nd},
@@
 terms.
-
+%
 In this formulation, a sector state $\ket{v}$ can be
@@
 
-\paragraph{\bf superc/nonsu2.}
-For these modes, symmetries enforce specific constraints between
+For the {\bf superc/nonsu2} modes, symmetries enforce specific constraints between
 $\up$ and $\dw$ configurations, preventing the direct use of the
@@
 \begin{equation}
-H_\SS = H_\mathrm{imp} + H_\mathrm{int} + H_\mathrm{bath} + H_\mathrm{imp-bath},
+H^e_\SS = H_\mathrm{imp} + H_\mathrm{int} + H_\mathrm{bath} + H_\mathrm{imp-bath},
 \end{equation}
@@
 functions of the form:
-$C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket$.
+$$
+C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket\, .
+$$
 This can be addressed by introducing auxiliary operators, e.g.  $\OO=\AA +\BB$ and
@@
 $\ibra \OO\iket = \tfrac{1}{Z}\Tr\left[e^{-\beta H}\OO\right]$, 
-where $Z = \sum_n e^{-\beta E_n}$ is the partition function. 
+where $\OO$ can be any local operator and  $Z = \sum_n e^{-\beta E_n}$ is the partition function. 
 At zero or low temperatures, this can be efficiently 
@@
 \end{equation}
-where $E_n$ and $\ket{\psi_n}$ are the low-lying eigenstates 
+where $E_n$ and $\ket{\psi_n}$ are the $N_{\tt state\_list}$ low-lying eigenstates 
 of the system stored in the {\tt state\_list}. This approach 
@@
 
+%% References with bibTeX database:
+\bibliography{references}
 \end{document}

### 2025-05-26 04_cbinding.tex
Updates from Overleaf

@@
 \subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
-The programming interface of EDIpack2triqs is built around the singleton 
+The programming interface of EDIpack2triqs is built around the  
 Python class {\tt EDIpackSolver}, defined in the module
@@
 Documentation of the API and further examples are being developed.
+
+%% References with bibTeX database:
+\bibliography{references}
 \end{document}

### 2025-05-26 05_examples.tex
Updates from Overleaf

@@
 \subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
-The test bed for any DMFT application is conventionally considered 
+The test bed for any DMFT implementation is conventionally considered 
 the description of the Mott or metal-to-insulator transition (MIT) 
@@
 
-\begin{tabular}{c|c}\label{list2}
+\begin{tabular}{c|c}\label{list3}
 {\bf Fortran} & {\bf C++}\\
@@
 
-\begin{tabular}{c|c}\label{list2}
+\begin{tabular}{c|c}\label{list4}
   \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
@@
 
-\begin{tabular}{c|c}\label{list2}
+\begin{tabular}{c|c}\label{list5}
   \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
@@
 \begin{align*}
-    \mathbf{H}_\mathrm{KM} = \sum_{{k}} \psi^\dagger_{{k}} \mathbf{H}({k}) \psi_{{k}},
+    H_\mathrm{KM} = \sum_{{k}} \psi^\dagger_{{k}} H({k}) \psi_{{k}},
 \end{align*}
@@
     \begin{align}
-    \mathbf{H}({k}) 
+    H({k}) 
     &= x_{{k}}\Gamma_{01} + y_{{k}}\Gamma_{02} + \delta_{{k}}\Gamma_{33}, \label{eq:Hk_kanemele}\\[1mm]
@@
 \begin{equation}
-    \mathbf{H}_\mathrm{KMH} = \mathbf{H}_\mathrm{KM} 
+    H_\mathrm{KMH} = H_\mathrm{KM} 
     + U\sum_{i}\Biggl[
@@
 \begin{align}
-    \mathbf{H}^\mathrm{bath}_\perp &= 
+    H^\mathrm{bath}_\perp &= 
         \sum_{p=1}^{N_\mathrm{b}}(\epsilon_p \sigma_0 + m_p \sigma_z), 
         \label{eq:afmz_dmft_ansatz} \\[1mm]
-    \mathbf{H}^\mathrm{bath}_\parallel &= 
+    H^\mathrm{bath}_\parallel &= 
         \sum_{p=1}^{N_\mathrm{b}}(\epsilon_p \sigma_0 + m_p \sigma_x).

### 2025-05-26 06_conclusions_acknowledgement_appendix.tex
Updates from Overleaf

@@
 NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
-I.K. acknowledge support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
+I.K. acknowledges support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
+G.S.
+and A.K.
+acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
 %S.G.
@@
 which gives the false impression of carrying an actual meaning,
-introduced in the trilogy movies ``Amici Miei'', directed by Mario
+introduced in the movies trilogy ``Amici Miei'', directed by Mario
 Monicelli (see
@@
 We believe the discourse flow of this language is best captured by 
-illustrating its features via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
+illustrating its features and \NAME interface via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
 \href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}
@@
 due parole come install {\tt Monicelli} from
-\href{github.com/esseks/monicelli.git}{https://github.com/esseks/monicelli.git}
+\url{https://github.com/esseks/monicelli.git}
 e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
@@
 
+\lstset{breaklines=true, breakindent=1em}
 \begin{lstlisting}[style=cstyle]
@@
 
-\paragraph{Usage}.
+\paragraph{Usage.}
 The source code can be retrieved from

### 2025-05-26 03_edipack2.tex
fixed compilation errors

@@
 \subsection{The quantum impurity problem}\label{sSecQIM}
-We consider a general quantum impurity problem described by the Hamiltonian:
+We consider a quantum impurity problem described by the Hamiltonian:
 $$
@@
 $$
-which describes a multi-orbital quantum impurity
-coupled to an electronic bath and local \fixme{phonons (e.g., Holstein
-modes)}. For now, we assume no specific symmetries.
+which characterizes a multi-orbital quantum impurity
+coupled to an electronic bath and local phonons (e.g., Holstein
+modes). For now, we assume no specific symmetries.
 
@@
 \begin{equation}\label{Himp}
-  \hat{H}_\mathrm{imp}  = \hat{H}^0_\mathrm{imp} + \hat{H}^\mathrm{int}_\mathrm{imp}
-\end{equation}
-where
+  \hat{H}_\mathrm{imp}  = \hat{H}^0_\mathrm{imp} + \hat{H}^\mathrm{int}_\mathrm{imp}.
+\end{equation}
+The first term has the form: 
 \begin{equation}\label{H0imp}
@@
 \end{equation}
-represents the quadratic part, with $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the annihilation (creation)
+and represents the quadratic part, with $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the annihilation (creation)
 operators for impurity electrons in 
 orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
-and spin $\sigma=\up,\dw$.  The occupation number operator is defined
-as  $n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$.
+and spin $\sigma=\up,\dw$. 
 The internal structure of the non-interacting part is captured by the 
@@
 \end{equation}
+where we introduced the occupation number operator   $n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$.
 The first three terms represent the density-density part of the
@@
 $U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
-The final two terms are, respectively, the spin-exchange ($J_X$) and
+The last two terms are, respectively, the spin-exchange ($J_X$) and
 the pair-hopping ($J_P$).
@@
 Any bath element can be composed of several electronic levels
-according the chosen bath topology. The  properties of each bath level are described by the
-matrix $h^p_{\a\b\sigma\sigma'}$ and couples to the impurity through an amplitude
-$V^p_{\a\b\s\sigma'}$.
+according to the chosen bath topology (see \secu{sSecBath}). The  properties of each bath element are described by the
+matrix $h^p_{\a\b\sigma\sigma'}$ while the amplitude
+$V^p_{\a\b\s\sigma'}$ desribes the coupling with the impurity.
 
@@
 \begin{table}%[ht]
-  \label{TabSector}
 \begin{center}
@@
  \hline
+  \label{TabSector}
 \end{tabularx}
@@
 %% References with bibTeX database:
+\ifSubfilesClassLoaded{
   \bibliography{references}
+}{}
 \end{document}

### 2025-05-26 05_examples.tex
fixed compilation errors
Updates from Overleaf

@@
 in a Bethe lattice, i.e., a Cayley tree with coordination number 
-$z\to\infty$~\cite{Georges1996}.
+$z\to\infty$~\cite{Georges1996RMP}.
 Here, we present a guided implementation of the DMFT 

### 2025-05-26 06_conclusions_acknowledgement_appendix.tex
fixed compilation errors
Updates from Overleaf

@@
 Monicelli (see
-\href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\_miei}).
+\url{https://it.wikipedia.org/wiki/Amici_miei}).
 
@@
 Unix soltanto in due, oppure in quattro anche scribai con il file
-sorgente {\tt hm\_bethe.mc}?  Come {\tt
+sorgente {\tt hm\_bethe.mc}? \\ Come {\tt
   github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}\\

### 2025-05-26 04_cbinding.tex
fixed compilation errors
Improved w2dynamics section a bit

--- 2025-05-24 04_cbinding.tex
@@
 
-\subsection{C-bindings}\label{sSecInteropCbindings}
+\subsection{C bindings}\label{sSecInteropCbindings}
 The interoperability with C language is provided by the
@@
 \begin{lstlisting}[style=mybash]
-conda create -n edipack  #create a virtual environment
-conda activate edipack   #activate it
+conda create -n myenv  #create a virtual environment called "myenv"
+conda activate myenv   #activate it
 conda install -c conda-forge -c edipack edipack #install edipack
@@
 \begin{enumerate}
-\item First the user can override the location of the library
-  (determined during \NAME build configuration) by exporting an
+\item The user can override the location of the library
+  (determined during the \NAME build configuration) by exporting an
   environment variable called {\tt EDIPACK\_PATH} .
 \item By default, the Python module detects the position of the
-  Fortran libraries via {\tt pkg-config}. Any of the OS loading method
-  outlined in \secu{sSecInstallOSloading} automatically push the
+  Fortran libraries via {\tt pkg-config}. Any of the loading method
+  outlined in \secu{sSecInstallOSloading} automatically pushes the
   correct configuration to the {\tt PKG\_CONFIG\_PATH}. 
@@
 
-\begin{lstlisting}[language=python,  frame=lines]
+\begin{lstlisting}[style=mypython]
 import numpy as np
@@
 
-\begin{lstlisting}[style=mypython,frame=lines]
+\begin{lstlisting}[style=mypython]
 import numpy as np
@@
     {\tt set\_Hloc} sets the
-    non-interacting part of the impurity Hamiltonian $\h^0_{\a\b\s\s'}$. 
+    non-interacting part of the impurity Hamiltonian $h^0_{\a\b\s\s'}$. 
     Either function take different argument combinations there
@@
 procedures or defined locally in Python to provide specific new
-functionalities. Among the latter we include {\tt get\_ed\_mode} which
-return the value of the variable {\tt ed\_mode=normal,superc,nosu2}
-and {\tt get\_bath\_type} which similarly returns the value of {\tt bath\_type}.
+functionalities. Among the latter we include {\tt get\_ed\_mode} which return an integer index depending onthe value of the variable {\tt ed\_mode=normal,superc,nosu2}
+and {\tt get\_bath\_type} which works similarly for {\tt bath\_type}.
 
@@
 \subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
-The programming interface of EDIpack2triqs is built around the singleton 
-Python class {\tt EDIpackSolver}, defined in the module
+The programming interface of EDIpack2triqs is built around the  
+singleton Python class {\tt EDIpackSolver}, defined in the module
 {\tt edipack2triqs.solver}, whose instance represents the internal state of 
@@
 \NAME is supported as alternative impurity solver in the W2Dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
-The only prerequisite to use this option is the presence of a functioning EDIpack2py installation, which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameter.
+The only prerequisite to use this option is the presence of a functioning EDIpack2py installation, which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameters.
 
-In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
+The  behavior of W2Dynamics is controlled by means of an input file, by default called
+{\tt Parameters.in}.
+First, in order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
 
-The  behavior of the W2Dynamics solver is controlled by means of an input file, by default called
-{\tt Parameters.in}. In order to configure the ED solver, the content of a specific section in the parameters file, called {\tt [EDIPACK]}, has to be modified.
+Then, in order to configure the ED solver, the content of a specific section in the parameters file, called {\tt [EDIPACK]}, has to be specified.
 
-For most of the \NAME input variables, W2Dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt EDIPACK} section of the parameters file.
+For most of the \NAME input variables, W2Dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt [EDIPACK]} section of the parameters file.
 This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath elements {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
@@
 An example of a properly formatted input file is provided in \secu{SecExamples}.
-See~\cite{Wallerberger2019CPC}
+The full set of configuration options can be found in the {\tt configspec} file, contained in the subfolder {\tt w2dyn/auxiliaries} of the W2Dynamics repository.
+See also~\cite{Wallerberger2019CPC}
 for further details.
@@
 Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard the CT-HYB code.
-For example, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format, and that W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+For example, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format.
+Moreover, W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
 As a consequence, functionalities that would require specific support from W2Dynamics and which are currently under development can not yet be used through the interface.
-For instance the solution of impurity problems in the superconductive phase, i.e.
-{\tt ed\_mode=superc}, or in presence of local phonons will only be available in the next future through an updated of W2Dynamics package.
+For instance, the solution of impurity problems in the superconductive phase, i.e.
+{\tt ed\_mode=superc}, or in presence of phonon modes will only be available in the near future through an update of the W2Dynamics package.
 
@@
 
-Similarly to the C++ case, global variables and functions are loaded as raw pointers.
-As a consequence, it is important that the dimensions of the array-like variables (such as {\tt ULOC}) and, in general, the amount of memory occupied by each variable are correcty accounted for.
+Similarly to the C++ case, global variables and functions are accessed as raw pointers.
+As a consequence, it is important that the dimensions of the array-like variables (such as {\tt ULOC}) and, in general, the amount of memory occupied by each variable are correctly accounted for.
 This is achieved within the Julia module by appropriately casting the variables to compatible types, such as {\tt  Cint, Cbool, Cdouble}.
@@
 Documentation of the API and further examples are being developed.
+
+%% References with bibTeX database:
+\ifSubfilesClassLoaded{
+  \bibliography{references}
+}{}
 \end{document}

### 2025-05-28 01_intro.tex
Updates from Overleaf
fixed compilation errors
Updated KMflake figure

@@
 Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with extended non-interacting environment.
-Originally introduced to describe magnetic impurities in metallic hosts and leading to the solution of the Kondo problem, these systems progressively became powerful tools for exploring a wide range of quantum many-body phenomena.
+Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem, thereby progressively becoming powerful tools for exploring a wide range of quantum many-body phenomena.
 More recently, their importance has extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cold atomic systems.
+%Asymptotic freedom
 
 At the heart of quantum impurity models is the interaction between a localized ``impurity"  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
-The definition of the impurity is rather generic, and it can contain lattice (i.e.
-inequivalent sites), orbital and spin local degrees of freedom.
+In this context, the definition of the impurity can taken as rather general, in order to contain lorbital and spin local degrees of freedom as well as a finite number of lattice sites.
+%MC eliminated inequivalent to avoid confusion with the last point
 This setup captures many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
 Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
-By accounting for local quantum fluctuations, DMFT can successfully describe of the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
+By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
 
-Accurately and efficiently solving the DMFT quantum impurity problem remains a
+Accurately and efficiently solving a quantum impurity problem and computing the Green's functions which are central in the DMFT framework, remains a
 critical challenge, particularly for multi-orbital systems, systems
@@
 
-%EDIPACK 2.0
+%EDIPACK
 In this work we introduce  \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
 The library builds on the foundations of
-its predecessor, featuring massively parallel Lanczos-based algorithms while including several significant extensions and 
-improvements.
+its predecessor, featuring massively parallel Lanczos-based algorithms while including several significant extensions and  improvements.
 The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effect in quantum materials to multi-orbital superconductivity.
 It also provides direct
-access to well-approximated dynamical correlation functions across the
+access to well-approximated %MC why? I would say numerically exact 
+dynamical correlation functions across the
 entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and other response properties.
@@
 Additionally, \NAME offers access to the Fock space of
-the impurity system and thus, for instance, the possibility to
-evaluate the impurity reduced density matrix
+the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix
 (iRDM).
@@
 
+%MC this last point is intrinsically DMFT (or embedding) and it has no connection with impurity physics
 This new version also includes support for systems with non-equivalent impurities , a critical feature to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
@@
 W2Dynamics software suites, which are two of the most important and used computational tools in
-the field. \NAME seamlessly slots in as an alternative solver to the native Quantum Monte Carlo 
+the field. \NAME seamlessly %MC ?
+slots in as an alternative solver to the native Quantum Monte Carlo 
 implementations, greatly extending the parameter (and especially temperature) range reachable by 
@@
 
+%% References with bibTeX database:
+\ifSubfilesClassLoaded{
+  \bibliography{references}
+}{}
 \end{document}

### 2025-05-28 02_install.tex
Updates from Overleaf
fixed compilation errors
Updated KMflake figure

@@
 
-The Conda package installation procedure reads:
+The Conda package installation procedure for a virtual environment called {\tt myenv} reads:
 \begin{lstlisting}[style=mybash,numbers=none]
-conda create -n edipack
-conda activate edipack
+conda create -n myenv
+conda activate myenv
 conda install -c conda-forge -c edipack edipack
@@
 
+%% References with bibTeX database:
+\ifSubfilesClassLoaded{
+  \bibliography{references}
+}{}
+
 \end{document}

### 2025-05-28 03_edipack2.tex
Updates from Overleaf
Updated KMflake figure

@@
 set of two-body operators: 
-$$
-\hat{H}^\mathrm{int}_\mathrm{imp} =  \sum_{ijkl} U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}. 
-$$
+\begin{equation}
+\hat{H}^\mathrm{int}_\mathrm{imp} = \frac{1}{2} \sum_{ijkl} c^{\dagger}_{i}c^{\dagger}_{j}U_{ijkl}c_{l}c_{k}.\label{HintUmat}
+\end{equation}
 However, we typically 
 adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ACMP}:
-\begin{equation}\label{Hint}
+\begin{equation}
   \begin{split}
@@
 \end{split}
+\label{Hint}
 \end{equation}
@@
 \subsubsection{Electron-Phonon coupling}
-Finally, the electron-phonon part of the quantum impurity problems is
+Finally, we include a local electron-phonon coupling on the impurity site
 described by the Hamiltonian terms: 
@@
   \begin{split}
-    \hat{H}_\mathrm{ph}&=\sum_q \omega_{0q} b_q^+b_q + \sum_q \sqrt{2}A_{q}(b^\dagger_q + b_q)  \\
+    \hat{H}_\mathrm{ph}&=\sum_m \omega_{0m} b_m^+b_m   \\
     % 
-    \hat{H}_\mathrm{e-ph} &= \sum_q\sum_{\a\b\sigma} g_{\a\b} d^+_{\a\sigma}d_{\b\sigma}(b_q+b_q^+)
+    \hat{H}_\mathrm{e-ph} &= \sum_m g_m[\hat{O}_m - A_m](b_m+b_m^+) \\
 \end{split}
 \end{equation}
-where $q=1,\dots,N_q$ indexes the number of local phonons, and $b_q$
-($b_q^+$) are the destruction (creation) operators for a phonon with
-frequency $\omega_{0q}$.
-The matrix  $g_{\a\b}$ describe the electron-phonon coupling. 
-Although feasible, dealing with more than one phonon mode becomes
-quickly computationally very demanding, thus in the rest of the this
-work we shall consider $N_q=1$.
-The phonon's frequency is passed to the \NAME program via the variable { \tt W0\_PH } to be read from the input file.
+where $m=1,\dots,M$ indexes the number of local phonon modes, and $b_m$
+($b_m^+$) are the destruction (creation) operators for a phonon with
+frequency $\omega_{0m}$.
+Each phonon mode is coupled to a bilinear fermionic operator $\hat{O}_m$ on the impurity, while $A_m$ is a constant acting as a displacement field.
+%Indeed, if the expectation value of the bosonic displacement operator $\langle b_q^\dagger + b_q\rangle$ is non-zero, a change of variables from the bosons $b^{(\dagger)}_q$ leads to new effective bosons $\tilde{b}^{(\dagger)}_q = b^{(\dagger)}_q- A_q$ for which the displacement operator has a smaller expectation value (ideally zero if we can impose $A_m = \langle \hat{O}_m\rangle$).
+For single-orbital impurities, the relevant case is $O_1 = n_d = \sum_{\sigma} d^{\dagger}_{\sigma}d_{\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
+For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $O_2 = n_1 - n_2$\cite{Scazzola2023PRB} and $O_3 = \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ h.c.)$.
+For each phonon mode, one has to introduce a cut-off in the phonon number which has to be chosen according to the value electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL_2,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}.
+The larger the number of excited phonons in the groundstate, the larger the cut-off.
+For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime\cite{Capone2003PRL}.
+Choosing properly the shift $A_m$ one can reduce the number of excited phonons in the groundstate and consequently the required cut-off. 
+Although feasible, dealing with more than one phonon mode becomes quickly computationally very demanding, thus in the rest of the this work we will consider only one mode.
+
+The phonon frequency is passed to the \NAME program via the variable { \tt W0\_PH } to be read from the input file.
 The displacement field acting on the phonon is passed through the variable {\tt A\_PH} from the input file.
-The electron-phonon coupling matrix $g_{\alpha \beta}$ instead can be passed in two different ways.
+For every phonon mode, the $g_m$ coupling can be written as a matrix $g_{\alpha \beta}$ which can be passed in two different ways.
 If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable {\tt G\_PH }.
@@
 We consider a quantum impurity system composed by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
-The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the number of phonons $N_\mathrm{ph}$.
-The latter is fixed to set a cut-off to the unbounded dimensions of the local phonons Hilbert space.
+The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cut-off to the unbounded dimensions of the local phonon Hilbert space.
 The number of bath degrees of freedom $N_\mathrm{b}$ is a
 function of the bath topology and of $N_\mathrm{bath}$, which is determined internally by \NAME.
-In the simplest case, each bath
+For instance, for a simple case of a purely electronic problem, each bath
 element corresponds to an independent electronic level coupled to the
 impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
-The number of electronic levels in the quantum impurity systems is indicated with $N_\mathrm{s}$.
+The total number of electronic levels in the quantum impurity systems is indicated with $N_\mathrm{s}$.
 
@@
 
-% \paragraph{{\bf Remark}} As extensively discussed in
-% \onlinecite{Amaricci2022}, the inclusion of local phonons with
-% truncated dimensions ultimately amounts to a sequential application of
-% the procedures defined for the electronic part, i.e. one per phonon
-% mode. This includes a linear scaling of the dimensions with $N_\mathrm{ph}$
-% and of course largely limit the available degrees of freedom to
-% describe electronic states. In the rest of the paper we focus
-% specifically on the electronic part of the quantum impurity problem,
-% referring to the phonons in specific sections when their presence
-% introduces non-trivial modifications.
-
 \subsection{The Fock basis states}\label{sSecBasis}
@@
 $$
-D=4^{N_\mathrm{s}}\cdot (N_\mathrm{ph}+1)=D_\mathrm{e}\cdot
-D_\mathrm{ph},
+D=4^{N_\mathrm{s}} (N_\mathrm{ph}+1)=D_\mathrm{e}D_\mathrm{ph},
 $$ 
@@
 in a computer using a sequence of $2N_\mathrm{s}$ bits, or equivalently, as an integer $I=0,\dots 2^{2N_\mathrm{s}}-1$ such that $\ket{\vec{n}}=\ket{I}$.  
-
-\fixme{Destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
-respectively, act on the Fock space as}:
+The electornic destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
+respectively, act on the Fock space as:
 \begin{align*}
@@
 where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ accounts for the fermionic sign imposed by the Pauli principle.
-
+The bosonic operators $b$ and $b^\dagger$ act on the phonon part of $\ket{p}$ of the Fock state as:
+\begin{align*}
+  b\ket{p} &= \sqrt{p-1}\ket{p} \\
+  b^\dagger\ket{p} &= \sqrt{p}\ket{p} \\
+\end{align*}
 The implementation of Fock states and operators can be found in 
@@
 {\tt CDG} and {\tt C}, used throughout the code. Additionally, 
-we provide the function {\tt bdecomp} for reconstructing the Fock 
-state bit sequence from the integer representation.
+we provide the function {\tt bdecomp} for reconstructing the Fock  state bit sequence from the integer representation.
 
@@
     enddo
-    out = ibclr(in,pos-1)
+    out = ibclr(in,pos-1)         !Set bit at pos to 0
   end subroutine C
@@
     enddo
-    out = ibset(in,pos-1)
+    out = ibset(in,pos-1)         !Set bit at pos to 1
   end subroutine CDG
@@
 \subsection{Conserved quantum numbers}\label{sSecQNs}
-To mitigate the exponential scaling of the \fixme{Fock space dimension}, it 
+To mitigate the exponential scaling of the Fock space dimension, it 
 is essential to exploit suitable symmetries. Specifically, if the 
@@
 gains, making it less practical in many cases.
+As the symmetries applies to the electronic terms, here we discuss the organization of the electronic Fock states only.
+The presence of phonon is accounted for exploiting the tensor structure of the global Fock space.
 
@@
 controlled by the input variable {\tt ed\_mode} = {\bf normal}, 
-{\bf superc}, or {\bf nonsu2}:
+{\bf superc}, or {\bf nonsu2}. A summary of the sector properties is provided in
+Table~(\ref{TabSector}).
 
 \begin{itemize}
-\item{} The {\bf normal} case conserves both the total occupation $N$
-and the total magnetization $S_z$, or equivalently, the total number
+\item{} The {\bf normal} case conserves both the electrons total occupation $N$
+and total magnetization $S_z$, or equivalently, the total number
 of electrons with spin up $N_\up$ and down $N_\dw$.
 Optionally, the symmetry
-can be extended to act indipendently to each orbital and spin
+can be extended to act independently to each orbital and spin
 component, i.e.~$\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
@@
 charge $N$ while allowing spin symmetry group to be not conserved.
-This scenario catpures effects such as local spin-orbit coupling
+This scenario captures effects such as local spin-orbit coupling
 $\vec{L}\cdot\vec{S}$~\cite{something}, in-plane spin ordering~\cite{BellomiaKMH} or
@@
 
-From a computational perspective, constructing a symmetry
-sector amounts to defining a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF$ which relates the states $\ket{i}$
-within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I}$ in the
-full Fock space.
-This map is typically implemented as a rank-1
-integer array whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$.
-
-The {\bf normal} case deserves a special note. Since $N_\up$ and
-$N_\dw$ are conserved independently, the local Hilbert
-space and the electronic Fock space can be factorized as
-$\HH_e=\HH_{e\up}\otimes\HH_{e\dw}$ and $\FF_\mathrm{e} = \FF_{e\up}\otimes \FF_{e\dw}$, respectively.  
-Consequently, each Fock state can be written as a product
-$\ket{\vec{n}_\up} \ket{\vec{n}_\dw}$. This factorization splits the
-symmetry sector as $\SS_{\vec{Q}} = \SS_{N_\up}\otimes\SS_{N_\dw}$,
-and finally the sector map can be expressed as the product $\MM = \MM_\up
-\otimes \MM_\dw$.
-%
-Each state $\ket{i}=\ket{i_\up} \ket{i_\dw}$ in this factorized basis
-is labeled by two integers $[i_\up,i_\dw]$, with 
-$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
-D_{\SS_\dw}$.
-The maps $\MM_\sigma$ then connect these basis states to Fock states
-$\ket{I}=\ket{I_\up}\ket{I_\dw}$, labeled by two integers
-$[I_\up,I_\dw]$ as $I=I_\up +   I_\dw 2^{N_\mathrm{s}}$.
-For a more
-detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022}.
-
-The presence of a symmetry reduces the Hamiltonian matrix to
-a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
-$D_{\SS_{\vec{Q}}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
-basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix.
-In the {\bf normal} case this block structure is particularly
-symmetric due to the factorized nature of the sectors as discussed
-above, see also Ref.~\cite{Amaricci2022}.
-The analysis of the spectrum is then reduced to inspecting the
-Hamiltonian within each symmetry sector, or to a subset thereof if a
-additional constraints are present.
-A summary of the sector properties is provided in
-Table~(\ref{TabSector}). 
 \begin{table}%[ht]
@@
 A table summarizing the possible values of the input variable {\tt
-  ed\_mode} selecting the symmetries of the problem. To each value
-(first column) correspond different quantum numbers (second column).
-The third column report the dimension of the electronic symmetry sector $\SS_{\vec{Q}}$ for a
+  ed\_mode} selecting the symmetries of the problem (first column). To each value
+correspond different quantum numbers listed in the second column.
+The third column reports the dimension of the electronic symmetry sector $\SS_{\vec{Q}}$ for a
 given value of the quantum numbers $\vec{Q}$.}
 \end{table}
+From a computational perspective, constructing a symmetry
+sector amounts to defining a injective map
+$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ which relates the electronic states $\ket{i}$
+within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I_e}$ in the Fock space.
+This map is typically implemented as a rank-1
+integer array whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
+The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p 2^{2 N_s}$.
+
+The {\bf normal} case deserves a special note. Since $N_\up$ and
+$N_\dw$ are conserved independently, the local Hilbert
+space and the electronic Fock space can be factorized as
+$\HH_e=\HH_{e\up}\otimes\HH_{e\dw}$ and $\FF_\mathrm{e} = \FF_{e\up}\otimes \FF_{e\dw}$, respectively.  
+Consequently, each electronic Fock state can be written as a product $\ket{\vec{n}_\up}\otimes \ket{\vec{n}_\dw}$. This factorization splits the
+symmetry sector as $\SS_{\vec{Q}} = \SS_{N_\up}\otimes\SS_{N_\dw}$,
+and finally the sector map can be expressed as the product $\MM = \MM_\up
+\otimes \MM_\dw$.
+%
+The electronic part of each sector state $\ket{i}=\ket{i_\up} \otimes \ket{i_\dw}$ in this factorized basis
+is labeled by two integers $[i_\up,i_\dw]$, with 
+$i_\sigma=1,\dots,D_{\SS_\sigma}$ such that $i=i_\up + i_\dw
+D_{\SS_\dw}$.
+The maps $\MM_\sigma$ then connect these basis states to Fock states
+$\ket{I_e}=\ket{I_\up}\ket{I_\dw}$, labeled by two integers
+$[I_\up,I_\dw]$ as $I_e=I_\up +   I_\dw 2^{N_\mathrm{s}}$.
+For a more detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022}.
+
+The presence of a symmetry reduces the electronic Hamiltonian matrix to
+a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
+$D_{\SS_{\vec{Q}}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
+basis $\ket{i}\in\SS_{\vec{Q}}$ as a sparse matrix.
+In the {\bf normal} case this block structure is particularly
+symmetric due to the factorized nature of the sectors as discussed
+above, see also Ref.~\cite{Amaricci2022}.
+The analysis of the spectrum is then reduced to inspecting the
+Hamiltonian within each symmetry sector, or to a subset thereof if a
+additional constraints are present.
 
@@
 These functions use different algorithms depending on the nature 
-of the quantum numbers $\vec{Q}$, i.e. the value of {\tt ed\_mode}. The following  code snippet summarize the various available implementations:
+of the quantum numbers $\vec{Q}$, i.e.
+the value of {\tt ed\_mode}.
+The following  code snippet summarize the various available implementations.
+The core idea is to loop of necessary Fock states through the integers $I_\sigma=1,\dots,2^{N_s}$ and enforce the quantum number constraint:
 
@@
 
+\vspace{2mm}
 \begin{tabular}{c|c|c}\label{list1}
@@
 \subsection{Interaction setup}\label{sSecIntSetup}
-The \NAME code offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}, which are controlled by the input variables {\tt
+\NAME offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}, which are controlled by the input variables {\tt
   ED\_USE\_KANAMORI} and {\tt ED\_READ\_UMATRIX}.
@@
 
-Alternatively, setting {\tt ED\_READ\_UMATRIX=T} and {\tt ED\_USE\_KANAMORI=F}, a list of two-body operators can be supplied by the user in a properly
-formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}. The implementation of the list of interaction terms is contained in
-the module {\tt ED\_PARSE\_UMATRIX}.  
-The file must have the suffix {\tt <UMATRIX\_FILE>.re\-star\-t} and should be formatted
-as follows: 
+Alternatively, setting {\tt ED\_USE\_KANAMORI=F} and {\tt ED\_READ\_UMATRIX=T}, a list of two-body operators can be supplied by the user in a properly
+formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}.  
+The file must have the suffix {\tt <UMATRIX\_FILE>.re\-star\-t} and should be formatted as follows: 
 \begin{lstlisting}[style=mybash,numbers=none]
-NORB BANDS
+<NORB> BANDS
 i1 j1 k1 l1 U_i1j1k1l1
@@
 \end{lstlisting}
-where {\tt NORB} is the numer of orbitals $N_\a$ and each line
-defines a single two-body term of the form 
-$U_{ijkl}c^{\dagger}_{i}c^{\dagger}_{j}c_{l}c_{k}$. Note that the
-coefficient indices are swapped compared to the standard two-body
-operator formulation $$
-\frac{1}{2}\sum_{i,j,k,l} c^{\dagger}_i c^{\dagger}_j U_{ijkl} c_l c_k
-$$ 
+where {\tt NORB} is the numer of orbitals $N_\a$.\\
+Each line defines a two-body second-quantized operator of the form 
+$$
+\hat{H}^{\mathrm{int}}=\frac{1}{2}c^{\dagger}_{i}c^{\dagger}_{j}U_{ijkl}c_{l}c_{k}.
+$$
+Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement.
+The $\tfrac{1}{2}$ prefactor is applied internally by the parsing routine and need not be accounted for by the user.
 Empty lines and lines starting with {\tt \#, \%, !} are ignored.
@@
 While {\tt ED\_READ\_UMATRIX} and {\tt ED\_USE\_KANAMORI}
-are mutually exclusive, we allow to set both to {\tt F}. 
-In this case, the user must 
-provide the interaction terms to the solver through the function 
-{\tt add\_twobody\_operator} in the calling program or script, before  the impurity problem is solved.
-
-For reference and future use, a list of the interaction operators used in each call to the solver are saved in the output file 
+are mutually exclusive, it is allowed to set both to {\tt F}. 
+In any case, the user can specify additional interaction terms in the calling program or script by means of the procedure {\tt add\_twobody\_operator}, before the impurity problem is solved.
+The input of this function has the same form of each line of the {\tt UMATRIX} file.
+The list of user-provided interaction terms will be added to those read from file or from the Hubbard-Kanamori coefficients in case the relative flags are {\tt T}.
+To clear the list, the procedure {\tt reset\_umatrix} has to be called.\\
+For reference and future use, when the impurity problem is solved a list of the interaction operators used in each call to the solver is saved in the output file 
 {\tt <UMATRIX\_FILE>.used}.
+The reading, writing, parsing and initialization of the two-body interaction terms are implemented in the module {\tt ED\_PARSE\_UMATRIX}.
 
@@
 
-%GBtodo placeholder: I passed on this already (except I don't like the
-%minipage of the listings)
-
 \subsubsection{Sparse map}\label{CodeSparseMap}
@@
 sector often requires associating each sector state $\ket{i}$ with 
-disjoint information about the corresponding Fock state $\ket{I}$. 
-In this context, the Fock state can be decomposed into bit chunks, 
+disjoint information about the corresponding electronic Fock state $\ket{I_e}$. 
+In this context, the electronic Fock state can be decomposed into bit chunks, 
 e.g., $\ket{\vec{n}} = \ket{\vec{i}_\up\,\vec{b}_\up\,
@@
 factorization of the Fock and sector states into independent spin components: 
-$\ket{J}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
+$\ket{J_e}=\ket{J_\up}\otimes\ket{J_\dw} \xleftarrow{\MM}
 \ket{j_\up}\otimes\ket{j_\dw}=\ket{j}$.
 The sparse maps are built as follows. 
-For any spin state of the sector $\ket{J_\s}=\ket{{\vec{I}_{\s}\vec{B}_{\s}}}$,
+For any spin Fock state appearing in the sector $\ket{J_\s}=\ket{{\vec{I}_{\s}\vec{B}_{\s}}}$,
 the \emph{key} is determined by the integer $I_\s$ corresponding to the
@@
 used.
-Here, each Fock state $\ket{J}$ is associated with four integers $I_\up, B_\up, I_\dw,
+Here, each electronic Fock state $\ket{J_e}$ is associated with four integers $I_\up, B_\up, I_\dw,
 B_\dw$ representing the bit decomposition of the state. 
 These integers satisfy the relationship
-$$
-J =I_\up +  B_\up2^{N_\mathrm{imp}} + (I_\dw +  B_\dw2^{N_\mathrm{imp}})2^{N_\mathrm{s}}
-$$
+\begin{equation}\label{spMapEq1}
+J_e =I_\up +  B_\up2^{N_\mathrm{imp}} + (I_\dw +  B_\dw2^{N_\mathrm{imp}})2^{N_\mathrm{s}}
+\end{equation}
 where $N_\mathrm{imp}$ is the number of impurity bits and 
@@
 \emph{values} as the integers $B=B_\up + B_\dw2^{N_\mathrm{b}}$.
-Note that these relations can be easily inverted to obtain $I_{\sigma=\up,\dw}$ from
+Note that, for the purpose of storing the key-value pairs, the impurity and bath indices are determined using an algorithm different from \equ{spMapEq1}.   
+These relations ensure a better scalign and can be easily inverted to obtain $I_{\sigma=\up,\dw}$ from
 $I$ and $B_{\sigma=\up,\dw}$ from $B$ in order to reconstruct the Fock
@@
 
-An overview of the implementation is reported in the following listing:
+An overview of the implementation, complementing the symmetry sector construction, is reported in the following listing:
 \setbox0=\hbox{%
@@
   !...
+  !Key: impurity bitset.
   iImp  = ibits(iup,0,Norb)
@@
 \end{tabular}
-%
+\vspace{1mm}
+
+leveraging the Fortran intrinsic function {\tt ibits(I,pos,len)} which returns the integer representation of the bit subset of length {\tt len} starting from {\tt pos} of the  integer {\tt I}.
 
@@
 low-lying spectrum of the quantum impurity Hamiltonian. 
-Note that, to reduce the memory footprint each eigenvector 
-is automatically distributed among all processors in suitable shares
+In MPI mode, the memory footprint of each eigenvector 
+is minimized by automatically distributing it among all processors in suitable shares
 according to the nature of the quantum numbers $\vec{Q}$.
-For zero-temperature calculations, only the groundstate (and its
-degenerate counterparts) are stored. For finite temperatures
-calculations, the list must also include excited states.
+While for zero-temperature calculations only the ground-state (with its
+degeneracy) is stored, for finite temperatures the list  also include all the necessary excited states.
 
@@
 \end{lstlisting}
-
-To avoid unbounded growth of this list, a  
-truncation mechanism is used. On the first call, a fixed number of
+A truncation mechanism is put in place to avoid the unbounded growth of this list. On the first call, a fixed number of
 states per sector  
@@
 maximum total \texttt{lanc\_nstates\_total}, both set via input.  
-The list is then truncated to retain only the states satisfying the condition $e^{-\beta(E_i-E_0)} < \mathtt{cutoff}$, where
+The list is then truncated to retain only the states satisfying the condition 
+$$
+e^{-\beta(E_i-E_0)} < \mathtt{cutoff}, 
+$$
+where
 $E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff}
-is an input parameter fixing an a priori energy threshold.
+groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff} is an input parameter fixing an {\it a-priori} energy threshold.
 
@@
 decrease in the number of states per sector. 
-A histogram  of the number of states per sector is produced after each diagonalization 
-to monitor this distribution.
+A histogram  of the number of states per sector is produced after each diagonalization to monitor this distribution.
 
@@
 a local impurity and a surrounding bath. Following the structure of
-Eq.~\ref{Hbath}, the bath is parametrized by two components: the
+\equ{Hbath}, the bath is parametrized by two components: the
 Hamiltonian matrices, $h^p$, and the hybridization amplitudes,
@@
 W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$. 
-
+%
 Thus, the total number of parameters used to determine the bath is $N_\mathrm{param}=2N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal} or $N_\mathrm{param}=3N_\a N_\mathrm{bath}$ for the other two values of {\tt ed\_mode}.
@@
 $V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
-
+%
 The resulting total number of available bath parameters are 
@@
 This configuration provides a more flexible parametrization of the 
-bath. The original core idea \cite{Capone2004PRB,Civelli2006}
+bath. The original core idea \cite{Capone2004PRB,Civelli2006,Koch2008PRB}
 is to assign each bath element a structure 
@@
 From a broader perspective, this can be formalized by considering  
-a user-defined matrix basis
+a user-defined matrix basis of dimension $N_\mathrm{sys}$ 
 $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_\mathrm{sym}}$ in the (Nambu-)spin-orbital
@@
 where $\vec{\lambda}^p\in\RRR^{N_\mathrm{sym}}$ is a vector of variational parameters. 
-The choice of the matrix basis can be inspired by symmetry group considerations \cite{Senechal}, by the internal structure
+The choice of the matrix basis can be inspired by symmetry group considerations \cite{Koch2008PRB,Senechal2010PRB}, by the internal structure
 of the quantum impurity, i.e. $\hat{h}^0$, or determined
@@
 
-\paragraph{Bath Auxiliary Tools}
+\paragraph{Bath Auxiliary Tools.}
 This module group provides user-oriented utilities, including 
@@
 
-\paragraph{Bath Replica (General).}
-The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica} ({\tt Hge\-ne\-ral}) for the {\bf replica}  ({\bf general}) bath parametrizations.
+\paragraph{Bath Replica/General.}
+The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica}/{\tt Hge\-ne\-ral} for the {\bf replica}/{\bf general} bath parametrizations.
 In  addition to standard object construction, destruction, reading, and saving, this module provides matrix basis
-$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ setup as well as  the variational parameters $\vec{\lambda}$ initialization through {\tt set\_Hreplica} ({\tt set\_Hge\-ne\-ral}).
-
+$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ setup as well as  the variational parameters $\vec{\lambda}$ initialization through {\tt set\_Hreplica}/{\tt set\_Hge\-ne\-ral}. 
+%
 The bath Hamiltonian is constructed with the function 
-{\tt build\_Hreplica} ({\tt build\_Hge\-ne\-ral}) via the relation:
+{\tt build\_Hreplica}/{\tt build\_Hge\-ne\-ral} via the relation:
 $$
@@
 
-Even though the dimension of a given sector $\SS$ is much smaller than the
+Even though the dimension of a given sector $\SS_{\vec{Q}}$ is much smaller than the
 total Fock space dimension $D_\SS \ll D_\FF$, solving completely the
@@
 $H_\SS$, including Krylov subspace methods and related approaches
-\cite{Lanczos,Arnoldi,Feast}.
-
-In \NAME, the preferred algorithm is P-ARPACK, a state-of-the-art
+\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996,Siro2012CPC,Siro2016CPC}.
+
+In \NAME, the preferred algorithm is P-ARPACK, a state of the art
 Lanczos-based eigensolver with distributed memory support
-\cite{P-Arpack}. This method incorporates re-orthogonalization within
+\cite{Lehoucq1998}. This method incorporates re-orthogonalization within
 a block-Lanczos routine, ensuring the accurate convergence of the desired eigen-pairs. However, it is also possible to select a simpler,
@@
 computational effort, making its optimization a critical aspect of
-high-performance diagonalization algorithms. In \onlinecite{Amaricci2022} we discussed in full details 
-the distributed-memory, massively parallel strategies currently employed in \NAME
-to optimize this step. Here, we provide
-a brief outline of the main ideas for the purely electronic case (i.e. neglecting electron-phonon part), following the notation introduced
+high-performance diagonalization algorithms.
+In \onlinecite{Amaricci2022} we discussed in greater details the distributed-memory massively parallel strategies currently employed in \NAME to optimize this step and present various benchmarks of the parallel scaling.
+Here, we provide a brief outline of the main ideas following the notation introduced
 in \onlinecite{Amaricci2022}, and focusing on the impact of the choice of {\tt ed\_mode}.
-
-\fixme{Again: this discussion is only for the electronic part. We need to state we focus on that here and discuss the modifications requied to deal with phonons at the end of this section}
+For sake of clarity, here we focus on the purely electronic case, i.e.
+neglecting the electron-phonon part.
+The product structure of the electron and phonon Fock spaces ensure that the following approach applies with few algorithmic modifications in presence of electron-phonon coupling.
 
@@
 based on the symmetries of the problem. This logic is implemented in
-a set of independent modules, {\tt ED\_HAMILTONIAN\_?}, where
-{\tt ed\_mode=?}. Any module includes two functions: {\tt build\_Hv\_sector\_?} and  {\tt vecDim\_Hv\_sector\_?}.
-
-The {\tt build\_Hv\_sector\_?} function builds the symmetry sector and
+a set of independent modules, {\tt ED\_HAMILTONIAN\_<ed\_mode>}. Any module includes two functions: {\tt build\_Hv\_sector\_<ed\_mode>} and  {\tt vecDim\-\_\-Hv\-\_\-sector\-\_\-<ed\_mode>}.
+
+The {\tt build\_Hv\_sector\_<ed\_mode>} function builds the symmetry sector and
 allocates the MVP function by setting the shared abstract function pointer {\tt
@@
 the MVPs. The corresponding algorithms are implemented in the modules {\tt
-  ED\_HAMILTONIAN\_?\_STORED\_HxV}
+  ED\_HAMILTONIAN\-\_\-<ed\_mode>\-\_\-STORED\-\_HxV}.
 If {\tt ed\_sparse\_H} is {\tt F} the MVP is operated on-the-fly,
@@
 vector $\ket{v}$, either in serial or parallel mode as implemented in {\tt
-  ED\_HAMILTONIAN\_?\_DIRECT\_HxV}.
-
-The function {\tt vecDim\_Hv\_sector\_?} returns the 
+  ED\_HAMILTONIAN\_<ed\_mode>\_DIRECT\_HxV}.
+
+The function {\tt vecDim\_Hv\_sector\_<ed\_mode>} returns the 
 dimension of the vector used in the
@@
 
-\paragraph{\bf Diagonalization}
-This step is managed by the {\tt ED\_DIAG\_?}
-modules, which contain the main functions {\tt diagonalize\_impurity\_?}.
+\paragraph{\bf Diagonalization.}
+This step is managed by the {\tt ED\_DIAG\_<ed\_mode>}
+modules, which contain the main functions {\tt diagonalize\_impurity\_<ed\_mode>}.
 This phase includes: (i) selecting sectors for diagonalization, (ii)
@@
 where $\AA(t)=e^{iHt}\AA e^{-iHt}$, $\TT_\pm$ is the time-ordering
-operator for fermions ($-$) or
-bosons ($-$), and $\ibra \AA \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\AA \right]}$, with $Z=\sum_ne^{-\beta E_n}$, the thermodynamic
+operator for fermions ($+$) or
+bosons ($-$), and $\ibra \cdot \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
+      H}\cdot \right]}$, with $Z=\sum_ne^{-\beta E_n}$, the thermodynamic
 average.
@@
 $$
-where  $\ket{\psi_n}\in\SS$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
+where  $\ket{\psi_n}\in\SS_{\vec{Q}}$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
   \AA^+\ket{\psi_n}}$.
-The Krylov basis is constructed by repetead applications of the secctor Hamiltonian via MVP: 
+The Krylov basis is constructed by repeated applications of the sector Hamiltonian via MVP: 
 $$
@@
 In \NAME, the computation of the impurity Green's functions 
-$G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket$
+$$
+G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket
+$$
 is handled by the \texttt{ED\_GREENS\_FUNCTIONS} module.
@@
 \equ{eqGKrylov}.
-Operationally, each symmetry mode (\texttt{ed\_mode=?}) requires a distinct
+Operationally, each symmetry mode (\texttt{ed\_mode}) requires a distinct
 strategy for Green's function construction, implemented in the corresponding
-\texttt{ED\_GF\_?} modules.
+\texttt{ED\_GF\_<ed\_mode>} modules.
 
@@
 $(S^z_\a + S^z_\b)$, $(N_\a + N_\b)$ or $(\Delta_\a + \Delta_\b)$. 
-The Excitonic susceptibilities, $\chi^{\vec{T}}_{\a\b}$, are defined with 
-respect to the vector operator: $T^i_{\a\b} = \sum_{\s\s'}
+The excitonic susceptibilities, $\chi^{\vec{E}}_{\a\b}$, are defined with 
+respect to the vector operator: $E^i_{\a\b} = \sum_{\s\s'}
 c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
@@
 \paragraph{{\bf superc}.}
-In the supercondutive case, the Nambu orbital-dependent $s$-wave
+In the supercondutive case, the orbital-dependent Nambu $s$-wave
 Green's function has the form:
@@
     G_{\a\b\up\up} & F_{\a\b\up\dw} \\
-    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}
+    \bar{F}_{\a\b\dw\up} & \bar{G}_{\a\b\dw\dw}.
   \end{bmatrix}  
@@
 sufficient to compute only the top row elements along with 
-a few auxiliary functions.
-
-The diagonal normal component $G_{\a\a\up\up}$ can be 
-evaluated using the same approach as in the {\bf normal} 
+a few auxiliary functions\cite{Capone2001PRL,Capone2002Science,Capone2004sc,Toschi2005NJP,Toschi2005PRB,Capone2009RMP}.
+%
+The diagonal, normal, component $G_{\a\a\up\up}$ can be 
+evaluated using the same approach as in the {\tt ed\_mode=}{\bf normal} 
 case. However, for the off-diagonal terms $G_{\a\b\up\up}$, 
@@
 $F_{\a\b\up\dw}$ requires distinct combinations of 
-creation and annihilation operators. First, the component 
+creation and annihilation operators\cite{Capone2001PRL,Capone2002Science,Capone2004sc,Toschi2005NJP,Toschi2005PRB}. First, the component 
 $\bar{G}_{\a\a\dw\dw}$ is evaluated as an auxiliary term 
-using $\AA = c^+_{\a\dw}$. Then, we construct two further 
+using $\AA = c^+_{\a\dw}$. Then, we construct the two  
 linear combinations:
@@
 depending on the operational mode specified by 
-{\tt ed\_mode=?} and is distributed across the corresponding 
-files {\tt ED\_OBSERVABLES\_?}.
+{\tt ed\_mode} and is distributed across the corresponding 
+files {\tt ED\_OBSERVABLES\_<ed\_mode>}.
 
@@
 \Delta_{\a\b\s\s'}(z) = \sum_p V^p_{\a\s} 
-\left( z\11 - h^p_{\a\b\s\s'} \right)^{-1} V^p_{\b\s'},
+\left( z\11 - \hat{h}^p \right)_{\a\b\s\s'}^{-1} V^p_{\b\s'},
 \end{equation}
@@
 G^0_{\a\b\s\s'}(z) = 
-\left[ (z + \mu)\delta_{\a\b\s\s'} - h^0_{\a\b\s\s'} - 
-\Delta_{\a\b\s\s'}(z) \right]^{-1},
+\left[ (z + \mu)\11 - \hat{h}^0 - 
+\Delta(z) \right]_{\a\b\s\s'}^{-1},
 \end{equation}
@@
 
-While more sophisticated optimization methods have been developed for 
-truncated algorithms like sCI\cite{Mejuto_Bath_ASCI-DMFT} or DMRG\cite{boh}, 
+While different optimization methods have been developed for 
+truncated algorithms like sCI~\cite{Mejuto_Bath_ASCI-DMFT} or DMRG~\cite{dmrg}, 
 which handle systems with a 
@@
 A full list of available functions, including parameter descriptions 
-and usage examples, can be found in the online documentation 
+and usage examples, can be found in the online documentation (see \href{https://edipack.github.io/EDIpack/}{edipack.github.io/EDIpack}).  
 Here, we highlight two representative examples:
@@
 time, a dedicated extension is required to handle these more complex 
-cases. To address this, we developed the {\tt EDIpack2ineq} 
+cases. To address this, we developed the \NAME{2ineq} 
 sub-library, which extends the base functionality of \NAME by managing 
@@
 that all functions remain accessible through standard Fortran 
-interfaces, seamlessly integrating both \NAME and {\tt EDIpack2ineq} 
+interfaces, seamlessly integrating both \NAME and \NAME{2ineq} 
 without compromising overall software design.
@@
 Below, we provide a brief overview of the main features introduced by 
-{\tt EDIpack2ineq}.
+\NAME{2ineq}.
 
 \subsubsection{Structure}\label{ssSecIneqStructure}
-The core of the {\tt EDIpack2ineq} sub-library consists of several 
+The core of the \NAME{2ineq} sub-library consists of several 
 Fortran modules, all wrapped under the main interface module 
@@
 impurity problems. To use this extension, the user must include both 
-the main \NAME and the {\tt EDIpack2ineq} modules, as shown below:
+the main \NAME and the \NAME{2ineq} modules, as shown below:
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 
-A significant part of the {\tt EDIpack2ineq} extension is the 
+A significant part of the \NAME{2ineq} extension is the 
 definition of global variables that extend the memory pool of 
@@
 \subsubsection{Input/Output}\label{ssSecIneqIO}
-A key component of the {\tt EDIpack2ineq} extension is the 
+A key component of the \NAME{2ineq} extension is the 
 enhanced I/O capability for handling impurity-specific observables. 

### 2025-05-28 04_cbinding.tex
Updated KMflake figure

@@
 A crucial part of the DMFT self-consistency loop is the optimization of the bath through CG algorithm (see \secu{sSecFit}). To this end we interfaced a
-number of functions {\tt
-  chi2\_fitgf\_\{single,lattice\}\_\{normal,superc\}\_n\{3,4,5,6\}} which
-cover all the cases supported in \NAME. Note that, because the actual
+number of functions which
+cover all the cases supported in \NAME, conveniently called {\tt
+  chi2\_fitgf\_\{single,lattice\}\_\{normal,superc\}\_n\{3,4,5,6\}} . Note that, because the actual
 optimization is still performed through the Fortran code, no changes
@@
 
-\paragraph{{\bf Method {\tt solve}}.}
-The method {\tt solve()} of {\tt EDIpackSolver} calls
+\paragraph{{\bf Method {\tt solve()}}.}
+The method {\tt solve()} calls
 {\tt edipack2py.global\_env.solve()} and therefore performs the bulk of
@@
           (read-only).
-    \item {\tt norb} -- the number of impurity orbitals (read-only).
+    \item {\tt norb} --- the number of impurity orbitals (read-only).
     \item {\tt hloc} --- matrix $h^0_{\alpha\beta\s\s'}$ of
           the quadratic impurity Hamiltonian \equ{Himp}.
-    \item {\tt Uloc}, {\tt Ust}, {\tt Jh}, {\tt Jx}, {\tt Jp} ---
-          parameters $U, U', J, J_X \text{ and } J_P$ of the impurity
-          interaction term $\hat{H}^\mathrm{int}_\mathrm{imp}$ \equ{Hint}.
+    \item {\tt U} --- 8-dimensional array $U_{\alpha\sigma_1,\beta\sigma_2,\gamma\sigma_3,\delta\sigma_4}$
+          of two-particle interactions as defined in Eq.~(\ref{HintUmat}).
     \item {\tt bath} --- an object representing the bath. Depending on the
@@
 Moreover, W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
-As a consequence, functionalities that would require specific support from W2Dynamics and which are currently under development can not yet be used through the interface.
-For instance, the solution of impurity problems in the superconductive phase, i.e.
-{\tt ed\_mode=superc}, or in presence of phonon modes will only be available in the near future through an update of the W2Dynamics package.
+As a consequence, functionalities that would require specific support from W2Dynamics and are currently not available can not be used through the interface, including e.g.\ the solution of impurity problems in the superconductive phase, i.e.
+{\tt ed\_mode=superc}.
 

### 2025-05-28 05_examples.tex
Updated KMflake figure

@@
 library and their interfaces as solver for DMFT through a variety of examples, including
-discussion of relevant code snippets.
+discussion of relevant code snippets. As some tasks are inherently agnostic on the impurity
+solver (and the impurity solver is agnostic about them), the user is expected to implement
+them, or interface to existing utilities. For instance, all the Fortran subroutines with 
+naming convention \texttt{dmft\_do\_something()} refer to implementations that can be found
+in the {DMFTtools} package\footnote{\url{https://github.com/aamaricci/DMFTtools}},
+the example based on w2dynamics relies on the internal facilities provided by the \texttt{DMFT.py} script \cite{Wallerberger2019CPC} and the TRIQS library provides an 
+extensive toolbox for the manipulation of Green's functions and related quantities
+\cite{Parcollet2015CPC}.
 
@@
 vector<double> Bath(Nb);
-Nb = get_bath_dimension();
+Nb = get_bath_dimension_direct();
 int64_t bath_dim[1] = {Nb};
@@
 \end{lstlisting}
-Assuming that w2dynamics is installed to {\tt /opt/w2dynamics} and the preceding parameters file saved as {\tt bethe\textunderscore{}dmft.in}, we can start the calculation by running the {\tt DMFT.py} script:
+Assuming the parameters are listed in a plain text file called 
+{\tt bethe\_dmft.in}, the DMFT simulation can then by run on {\tt NC} cores via:
 \begin{lstlisting}[style=mybash,numbers=none]
-mpiexec -n 10 /opt/w2dynamics/DMFT.py bethe_dmft.in
+mpiexec -n NC /path/to/w2dynamics/DMFT.py bethe_dmft.in
 \end{lstlisting}
@@
 \begin{lstlisting}[style=mybash,numbers=none]
-/opt/w2dynamics/hgrep latest siw-full -1
+/path/to/w2dynamics/hgrep latest siw-full -1
 \end{lstlisting}
@@
 
+\begin{figure}[ht!]
+    \includegraphics[width=\linewidth]{figures/figBethe_Holstein.pdf}
+    \caption{\label{figEx5}
+      Evolution of the double occupancy (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
+The horizontal broken lines are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
+\end{figure}
+
 \subsection{Holstein model on the Bethe lattice (electron-phonon coupling)}
@@
 
-\begin{figure}[ht!]
-    \includegraphics[width=\linewidth]{figures/figBethe_Holstein.pdf}
-    \caption{\label{figEx5}
-      Evolution of the double occupancy (A) and superconductive order parameter (B) as a function of $\omega_0/D$ for $\lambda=1$ in the normal (orange) and superconductive (red) phase.
-The horizontal broken lines are the values for the corresponding Hubbard model in the anti-adiabatic limit.}
-\end{figure}
-
 \begin{figure}[t!]
@@
 form (\ref{Hint}).
-
-\fixme{Add Hamiltonian?}
-\fixme{}
 
@@
 %
-The main effect of the interaction is enclosed in the renormalized
-mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
+The main effect of the interaction to the topological properties can be captured by the renormalized mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
 real-part of the self-energy being proportional to $\Gamma_{03}$
@@
 
-\subsection{Interacting Kane-Mele model (Fortran API, EDIpack2ineq layer, iRDM)}
+\subsection{Interacting Kane-Mele model (Fortran API, EDIpack2ineq, iRDM)}
 
@@
 \end{align}
-comparing with \ref{eq:replica_bath_sym}, it is clear 
-that this amounts to having $N_\mathrm{sym}=2$, with
+which corresponds to $N_\mathrm{sym}=2$, with
 $\lambda_{1,p} \equiv \epsilon_p$ as the degenerate
@@
   !Load EDIpack library 
-  USE EDIpack
+  USE EDIPACK
   !Load the inequivalent impurities extension
-  USE EDIpack2ineq
-  .
-  .
-  .
+  USE EDIPACK2INEQ
+  ...
   !Setup bath and solver for anisotropic AFM phases
@@
   select case(ansatz)
-    case('off-plane')
-        Hsym_basis(:,:,2) = pauli_z
-    case('in-plane')
-        Hsym_basis(:,:,2) = pauli_x
+    case('off-plane');Hsym_basis(:,:,2) = pauli_z
+    case('in-plane') ;Hsym_basis(:,:,2) = pauli_x
   end select
@@
   call build_replica_band(onsite_band,ed_hw_bath,Nbath)
+  ! (user-built guess of the starting bath levels)
   lambdasym_vectors(:,:,1) = onsite_band 
@@
   call ed_init_solver(Bath)
-  .
-  .
-  .
-  contains
-  .
-  .
-  .
-  subroutine build_replica_band(epsilons,bandwidth,Nreplica)
-  !> Initialization of the (average) bath levels, suitable to
-  !  describe a weakly interacting metal or a band insulator
-      real(8),allocatable,dimension(:,:),intent(out)   :: epsilons
-      real(8),intent(in)                               :: bandwidth
-      integer,intent(in)                               :: Nreplica
-      integer                                          :: ireplica
-      real(8),dimension(Nreplica)                      :: tempvec
-      real(8)                                          :: tempval
-      !
-      allocate(epsilons(Nineq,Nbath))
-      !
-      do ireplica=1,Nreplica
-         tempval = ireplica - 1 - (Nreplica-1)/2d0       ![-(N-1)/2 : (N-1)/2]
-         tempval = tempval * 2 * bandwidth/(Nreplica-1)  !-bandwidth:bandwidth
-         tempvec(ireplica) = tempval
-      enddo
-      !
-      if(mod(Nreplica,2)==0)then
-         tempvec(Nreplica/2) = -1d-1  !Much needed small energies around the
-         tempvec(Nreplica/2+1) = 1d-1 !Fermi level (if EF itself not present)
-      endif
-      !
-      do ilat=1,Nineq
-         epsilons(ilat,:) = tempvec
-      enddo
-      !
-   end subroutine build_replica_band
+  ... 
 \end{lstlisting}
@@
     \centering
-    (a) \hspace{12cm} (b) \\
-    \includegraphics[width=0.8\linewidth]{figures/flakes_edipack.pdf}\\[3mm]
-    (c) \hspace{12cm} (d) \\
+    \includegraphics[width=0.8\linewidth]{figures/flakes_edipack.pdf}\\[1mm]
+    (c) \hspace{10cm} (d) \\
     \hspace{1.2cm}
@@
 computed from the impurity groundstate as  
-$ \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket$,
+$ \ibra S_x \iket = \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket$,
 so that we can define the $S_x$ spin-occupation numbers as
 \begin{equation*}
-    n_{i,\rightarrow} \equiv \frac{n_{i,\up} + n_{i,\dw} +
+    \ibra n_{i,\rightarrow} \iket \equiv \frac{\ibra n_{i,\up} + n_{i,\dw} \iket +
     \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket}{2},
     \qquad
-    n_{i,\leftarrow} \equiv \frac{n_{i,\up} + n_{i,\dw} -
+    \ibra n_{i,\leftarrow} \iket \equiv \frac{\ibra n_{i,\up} + n_{i,\dw} \iket -
     \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket}{2},
 \end{equation*}
-which trivially satisfy the conservation of the local average charge $n_{i,\rightarrow} + n_{i,\leftarrow} = n_{i,\up} + n_{i,\dw}$.
-Having a direct expression for $n_{i,\rightarrow}$ and $n_{i,\leftarrow}$
+which trivially satisfy the conservation of the local average charge $\ibra n_{i,\rightarrow} + n_{i,\leftarrow} \iket = \ibra n_{i,\up} + n_{i,\dw} \iket$.
+Having a direct expression for $\ibra n_{i,\rightarrow} \iket$ and $\ibra n_{i,\leftarrow} \iket$
 we can verify that the impurity reduced density matrix, computed by 

### 2025-05-28 06_conclusions_acknowledgement_appendix.tex
Updated KMflake figure

@@
 achieved through modern Fortran constructs, C/C++-bindings, and
-comprehensive APIs for Python (EDIpy2). 
+comprehensive APIs for Python (EDIpack2py). 
 These interfaces enable seamless integration with broader
@@
 
-% TODO: include author contributions
-\paragraph{Author contributions}
-This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
+\section*{Acknowledgements}
+We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, A.~Scazzola, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, A.~Camjayi, M.~Rozenberg.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section*{Acknowledgements}
-We acknowledge helpful discussions, occurring at diverse stages of development of \NAME, with: Carlos Mejuto Zaera, Pablo Villar Arribi, Maria Chatzieleftheriou, Marcello Dalmonte, Mario Collura, Cedric Weber, Alberto Camjayi, Marcelo Rozenberg, ...
-
-% TODO: include author contributions
-% This will be used to better attribute supervision of each part of the code, e.g.
+% % TODO: include author contributions
+% % This will be used to better attribute supervision of each part of the code, e.g.
 LC for part of the code, C-binding, Py, Julia, Monicelli, etc, IK for EDIpack2Triqs, AK+MW+GS for W2Dyn support, etc.
-\paragraph{Author contributions}
-This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
+% \paragraph{Author contributions}
+% This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
 
@@
 L.C.
-acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994).
-Ratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb.
+acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994) and gratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb.
 NHR funding is provided by federal and Bavarian state authorities.
@@
 acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
-%S.G.
-%G.B
-%A.K.
-%F.P
+%F.P.
 %M.W.
 %G.M.
-%L.dM.
-%G.S.
-%M.C.
-%A.A.
+G.M. acknowledges support from the MUR - Italian Ministry of University and Research - through the Rita-Levi Montalcini program.
+L.dM. acknowledges support by the European Commission through the ERC-CoG2016, StrongCoPhy4Energy, GA No. 724177.
+M.C., S.G. and G.B. acknowledge financial support from the National Recovery and Resilience Plan PNRR
+MUR Project No.~CN00000013-ICSC and by MUR via PRIN 2020 (Prot.~2020JLZ52N-002) and PRIN 2022 (Prot.~20228YCYY7) programmes.
+A.A. and M.C. acknowledge financial support from the National Recovery and Resilience Plan PNRR MUR Project No.~PE0000023-NQSTI.
 
@@
 V: {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano
-programmano loro, non si intrometta!}\\
+programmando loro, non si intrometta!}\\
 M: {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
@@
 \lstset{breaklines=true, breakindent=1em}
-\begin{lstlisting}[style=cstyle]
+\begin{lstlisting}[style=cstyle,numbers=none]
 bituma le funzioni ausiliarie che vengono dal bagaglio
@@
 
-\begin{lstlisting}[style=cstyle]
+\begin{lstlisting}[style=cstyle,numbers=none]
 Lei ha clacsonato
@@
 directory:
-\begin{lstlisting}[style=mybash]
+\begin{lstlisting}[style=mybash,numbers=none]
 git clone https://github.com/lcrippa/prematurata_la_dmft

### 2025-05-28 01_intro.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \section{Introduction and Motivation}\label{SecIntro}
-\fixme{A tentative Introduction scheme}
-
-Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with extended non-interacting environment.
-Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem, thereby progressively becoming powerful tools for exploring a wide range of quantum many-body phenomena.
+Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with an extended non-interacting environment.
+Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem, and beyond that they have progressively become powerful tools for exploring a wide range of quantum many-body phenomena.
 More recently, their importance has extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cold atomic systems.
@@
 
-At the heart of quantum impurity models is the interaction between a localized ``impurity"  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
-In this context, the definition of the impurity can taken as rather general, in order to contain lorbital and spin local degrees of freedom as well as a finite number of lattice sites.
+At the heart of quantum impurity models is the interaction between a localized ``impurity''  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
+In this context, the definition of the impurity can be taken as rather general, in order to contain orbital and spin local degrees of freedom as well as a finite number of lattice sites.
 %MC eliminated inequivalent to avoid confusion with the last point
 This setup captures many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
-Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
+Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem \cite{Georges1996RMP}.
 By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
 
-Accurately and efficiently solving a quantum impurity problem and computing the Green's functions which are central in the DMFT framework, remains a
+Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
 critical challenge, particularly for multi-orbital systems, systems
@@
 %EDIPACK
-In this work we introduce  \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+In this work we present the renewed and improved \NAME{}, version number \textcolor{red}{5.0}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
 The library builds on the foundations of
-its predecessor, featuring massively parallel Lanczos-based algorithms while including several significant extensions and  improvements.
-The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effect in quantum materials to multi-orbital superconductivity.
+its predecessor~\cite{Amaricci2022}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
+The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.
 It also provides direct
-access to well-approximated %MC why? I would say numerically exact 
+access to numerically exact
 dynamical correlation functions across the
-entire complex plane, thus enabling calculations of spectral functions, local susceptibilities, and other response properties.
+entire frequency complex plane, thus enabling calculations of spectral functions, local susceptibilities, and other response properties.
 
@@
 %MC this last point is intrinsically DMFT (or embedding) and it has no connection with impurity physics
-This new version also includes support for systems with non-equivalent impurities , a critical feature to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
+This new version also includes support for systems with non-equivalent impurities.
+This is a critical feature in DMFT or, more generally, in quantum embedding methods, to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
 This capability makes it
@@
 With the growing importance of  quantum impurity models in the study of correlated materials,
-standardizazion and interoperability between solution software suites has
+standardization and interoperability between solution software suites has
 become a critical necessity.
@@
 be they compiled (C, C++), JIT-compiled (Julia) or interpreted (Python). 
-Especially notable in this sense is the Python API, EDIpy which, beyond providing a 
+Especially notable in this sense is the Python API, EDIpack2py, which beyond providing a 
 high-level interface for defining and solving impurity problems, also allows integration with established scientific libraries, such as NumPy and SciPy, facilitating data analysis and
@@
 
-A key development feature in \NAME, unlocked by the introduction of Python and C/C++ API, 
-is the direct interfaces to the TRIQS (Toolbox for Research on Interacting Quantum Systems) and
-W2Dynamics software suites, which are two of the most important and used computational tools in
-the field. \NAME seamlessly %MC ?
-slots in as an alternative solver to the native Quantum Monte Carlo 
-implementations, greatly extending the parameter (and especially temperature) range reachable by 
+A key development feature in \NAME, unlocked by the introduction of the Python API, 
+is the possibility to directly interface to the TRIQS (Toolbox for Research on Interacting Quantum Systems) and
+W2Dynamics software suites, which are two of the most important and widely used computational tools in
+the field. \NAME slots in as an alternative solver to the native Quantum Monte Carlo 
+implementations, extending the parameter (and especially temperature) range reachable by 
 the simulation while minimizing the coding requirements for the end user.
@@
 Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
-enhancing reproducibility and cross-validation of numerical results, with the ultimate aim of a
-chieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat.
+enhancing reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat, see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}.
 
@@
 In this paper, we present the mathematical framework, implementation
-details, and key features of \NAME, along with several illustrative
+details, and key features of \NAME \textcolor{red}{5.0}, along with several illustrative
 applications. We aim to demonstrate how this flexible,
@@
 and installation procedures. In the following  \secu{SecEDIpack} we present the quantum impurity
-problem and review the software implementation in full details. In the following 
-\secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
+problem and review the software implementation in full detail. In \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
 interoperability capabilities of \NAME. In this section we also discuss 4 interface layers: i) 

### 2025-05-28 02_install.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 The configuration and installation of \NAME is handled by CMake, which ensures
-multi-platforms compabitility and dependencies resolution.  
+multi-platform compatibility and dependencies resolution.  
 The software builds into two distinct libraries.
@@
 \item{\bf EDIpack2ineq.}
-  This extension, developed using modern Fortran constructs,
+  This extension, developed using suitable Fortran interfaces,
   enables the treatment of multiple, independent quantum 
@@
 management and supports the simultaneous solution of multiple impurity 
-problems, as discussed in Sec.\ref{sSecIneq}.
+problems, as discussed in \secu{sSecIneq}.
 
@@
 \begin{itemize}
-\item {\bf SciFortran}: an open-source Fortran library to support
-  mathematical and scientific software development. 
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support to modern Fortran compiler.
+\item {\bf SciFortran}: an open-source Fortran library that provides support
+for mathematical and scientific software development.
+\item {\bf MPI} (optional): a distributed memory parallel communication layer with support for modern Fortran compiler.
 \end{itemize}
@@
 many algorithms and functions, including standard linear algebra
-operations and high-performance Lanczos based algorithms. This
+operations and high-performance Lanczos-based algorithms. This
 greatly reduces code clutter and development time.
 The use of distributed memory parallel environment, although optional,
-is required to access scalable parallel diagonalization algorithms
-which speed up calculations for large dimensional systems.
+is required to access scalable parallel diagonalization algorithms,
+which speed up calculations for large systems.
 
@@
 The software can be installed from source as follows. The source code can
-be retrieved directly from its GitHub repository, for instance using:
+be retrieved directly from its GitHub repository, for instance using
 \begin{lstlisting}[style=mybash,numbers=none]
@@
 \end{lstlisting}
-Then, assuming to be in the software directory, a conventional
+Then, assuming being in the software source directory, a conventional
 out-of-source building can be performed using two alternative compilation backends.
@@
 Fortran support. Ninja is generally faster and automatically supports
-multi-threaded building:
+parallel compilation:
 \begin{lstlisting}[style=mybash,numbers=none]
@@
   \hline
-  -D{\bf PREFIX}          & Install directory  & $\sim$/opt/EDIpack/TAG/PLAT/BRANCH\\
+  -D{\bf PREFIX}          & Install directory  & {\color{red} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
   -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & Inequivalent impurities support & {\color{red}True}/{False}\\
+  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{red}True}/{False}\\
   -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG/AGGRESSIVE \\
+  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG \\
  \hline
@@
 installation through Anaconda packages into a virtual
-environment containing Python ($>3.10$).
+environment containing Python ($\geq3.10$).
 
-The Conda package installation procedure for a virtual environment called {\tt myenv} reads:
+The Conda package installation procedure for a virtual environment called {\tt myenv} reads
 \begin{lstlisting}[style=mybash,numbers=none]
@@
 which installs a bundle of SciFortran and \NAME libraries together with
-specific {\tt pkg-config} configurations files, which can be used to
+specific {\tt pkg-config} configuration files, which can be used to
 retrieve compilation and linking flags. In order to compile Fortran/C++ 
@@
 
-\subsection{OS Loading}\label{sSecInstallOSloading}
+\subsection{Environment Variables}\label{sSecInstallOSloading}
 In order to avoid possible conflicts or the requirement for administrative
-privileges, the building step results are installed by default in the user's {\tt HOME}
+privileges, the results of the building step are installed by default in user's {\tt HOME}
 directory, specified by the CMake variable {\tt PREFIX}.
-As a consequence, the system library and include paths will need to be updated by the user.
-
+As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
 We offer different ways to perform this action:

### 2025-05-28 03_edipack2.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \section{Implementation}\label{SecEDIpack}
-In this section we introduce the generic quantum impurity system and
+In this section we introduce the generic quantum impurity problem and
 present a detailed overview of the \NAME library implementation.
@@
 which characterizes a multi-orbital quantum impurity
-coupled to an electronic bath and local phonons (e.g., Holstein
+coupled to an electronic bath and local phonons (e.g. Holstein
 modes). For now, we assume no specific symmetries.
@@
 The impurity Hamiltonian is split into a quadratic and an 
-interacting part:
+interacting part,
 \begin{equation}\label{Himp}
@@
 \end{equation}
-The first term has the form: 
+The first term has the form
 \begin{equation}\label{H0imp}
   \hat{H}^0_\mathrm{imp}  =
-  \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}d_{\b\sigma'}
-\end{equation}
-and represents the quadratic part, with $d_{\a\sigma}$ ($d^+_{\a\sigma}$) are the annihilation (creation)
+  \sum_{\a\b\sigma\sigma'}h^{0}_{\a\b\sigma\sigma'}d^\dagger_{\a\sigma}d_{\b\sigma'}
+\end{equation}
+and represents the quadratic part, with $d_{\a\sigma}$ ($d^\dagger_{\a\sigma}$) being the annihilation (creation)
 operators for impurity electrons in 
-orbital $\alpha=1,\dots,N_\a$, with $N_\a$ the number of orbitals,
+orbital $\alpha=1,\dots,N_\a$, with the number of orbitals $N_\a$,
 and spin $\sigma=\up,\dw$.
@@
 \begin{equation}
-\hat{H}^\mathrm{int}_\mathrm{imp} = \frac{1}{2} \sum_{ijkl} c^{\dagger}_{i}c^{\dagger}_{j}U_{ijkl}c_{l}c_{k}.\label{HintUmat}
+\hat{H}^\mathrm{int}_\mathrm{imp} = \frac{1}{2} \sum_{ijkl} d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.\label{HintUmat}
 \end{equation}
@@
     &{\phantom =}- J_X\sum_{\a\neq
-      \b}d^{+}_{\a\uparrow}d_{\a\downarrow}d^{+}_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
+      \b}d^\dagger_{\a\uparrow}d_{\a\downarrow}d^\dagger_{\b\downarrow}d_{\b\uparrow}+J_P\sum_{\a
       \neq
-      \b}d^{+}_{\a\uparrow}d^{+}_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow}\\
+      \b}d^\dagger_{\a\uparrow}d^\dagger_{\a\downarrow}d_{\b\downarrow}d_{\b\uparrow},\\
 \end{split}
@@
 \end{equation}
-where we introduced the occupation number operator   $n_{\alpha\sigma}=d^{+}_{\alpha\sigma}d_{\alpha\sigma}$.
+where we introduced the occupation number operator $n_{\alpha\sigma}=d^\dagger_{\alpha\sigma}d_{\alpha\sigma}$.
 The first three terms represent the density-density part of the
@@
 $J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other number of orbitals~\cite{Georges2013ACMP}.
+of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ACMP}.
 
@@
     \hat{H}_\mathrm{bath} &=
-    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^{+}_{p\a\sigma}a_{p\b\sigma'}\\
+    \sum_p\sum_{\a\b\sigma\sigma'}h^p_{\a\b\sigma\sigma'}a^\dagger_{p\a\sigma}a_{p\b\sigma'},\\
     %
-    \hat{H}_\mathrm{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^{+}_{\a\sigma}a_{p\b\sigma'}+H.c. \\
+    \hat{H}_\mathrm{hyb} &= \sum_p\sum_{\a\b\sigma\sigma'}V^p_{\a\b\sigma\sigma'}d^\dagger_{\a\sigma}a_{p\b\sigma'}+H.c., \\
 \end{split}
@@
 bath elements. The operators $a_{p\alpha\sigma}$
-($a^+_{p\alpha\sigma}$) correspond to the destruction (creation) of
+($a^\dagger_{p\alpha\sigma}$) correspond to the destruction (creation) of
 bath electrons with index $p$, orbital $\alpha$ and spin $\sigma$.
@@
 matrix $h^p_{\a\b\sigma\sigma'}$ while the amplitude
-$V^p_{\a\b\s\sigma'}$ desribes the coupling with the impurity.
+$V^p_{\a\b\s\sigma'}$ describes the coupling with the impurity.
 
@@
   \begin{split}
-    \hat{H}_\mathrm{ph}&=\sum_m \omega_{0m} b_m^+b_m   \\
+    \hat{H}_\mathrm{ph}&=\sum_m \omega_{0m} b_m^\dagger b_m,   \\
     % 
-    \hat{H}_\mathrm{e-ph} &= \sum_m g_m[\hat{O}_m - A_m](b_m+b_m^+) \\
+    \hat{H}_\mathrm{e-ph} &= \sum_m [ \hat{O}_m - A_m](b_m+b_m^\dagger), \\
 \end{split}
@@
 where $m=1,\dots,M$ indexes the number of local phonon modes, and $b_m$
-($b_m^+$) are the destruction (creation) operators for a phonon with
+($b_m^\dagger$) are the destruction (creation) operators for a phonon with
 frequency $\omega_{0m}$.
-Each phonon mode is coupled to a bilinear fermionic operator $\hat{O}_m$ on the impurity, while $A_m$ is a constant acting as a displacement field.
+Each phonon mode is coupled to a bilinear fermionic operator $\hat{O}_m= \sum_{\alpha \beta, \sigma }g^{m}_{\alpha \beta} d^\dagger_{\alpha, \sigma} d_{\beta, \sigma}$ on the impurity, while $A_m$ is a constant acting as a displacement field.
 %Indeed, if the expectation value of the bosonic displacement operator $\langle b_q^\dagger + b_q\rangle$ is non-zero, a change of variables from the bosons $b^{(\dagger)}_q$ leads to new effective bosons $\tilde{b}^{(\dagger)}_q = b^{(\dagger)}_q- A_q$ for which the displacement operator has a smaller expectation value (ideally zero if we can impose $A_m = \langle \hat{O}_m\rangle$).
-For single-orbital impurities, the relevant case is $O_1 = n_d = \sum_{\sigma} d^{\dagger}_{\sigma}d_{\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
-For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $O_2 = n_1 - n_2$\cite{Scazzola2023PRB} and $O_3 = \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ h.c.)$.
-For each phonon mode, one has to introduce a cut-off in the phonon number which has to be chosen according to the value electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL_2,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}.
-The larger the number of excited phonons in the groundstate, the larger the cut-off.
+For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_d = g_1 \sum_{\sigma} d^{\dagger}_{\sigma}d_{\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
+For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_1 - n_2)$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ h.c.)$.
+For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL_2,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}\fixme{Broken ref}.
+The larger the number of excited phonons in the ground state, the larger the cutoff.
 For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime\cite{Capone2003PRL}.
-Choosing properly the shift $A_m$ one can reduce the number of excited phonons in the groundstate and consequently the required cut-off. 
-Although feasible, dealing with more than one phonon mode becomes quickly computationally very demanding, thus in the rest of the this work we will consider only one mode.
+Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
+Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.
 
@@
 The displacement field acting on the phonon is passed through the variable {\tt A\_PH} from the input file.
-For every phonon mode, the $g_m$ coupling can be written as a matrix $g_{\alpha \beta}$ which can be passed in two different ways.
-If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable {\tt G\_PH }.
-For any general shape one can pass to the input file a {\tt GPHfile } variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.
-If {\tt GPHfile=NONE} the matrix $g_{\alpha \beta}$ is read from the variable {\tt G\_PH}, else it is read from the {\tt GPHfile}.
+For every phonon mode, the $g$ coupling can be written as a matrix $g_{\alpha \beta}$ which can be passed in two different ways.
+If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable {\tt G\_PH}.
+For any general shape one can pass to the input file a {\tt GPHfile } variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.\fixme{I don't seem to understand the last two sentences at all\ldots}
+If {\tt GPHfile=NONE}, the matrix $g_{\alpha\beta}$ is read from the variable {\tt G\_PH}, otherwise it is read from the {\tt GPHfile}.
 
 \subsubsection{System setup}
-We consider a quantum impurity system composed by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
-The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cut-off to the unbounded dimensions of the local phonon Hilbert space.
+We consider a quantum impurity system comprised by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
+The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cutoff to the unbounded dimension of the local phonon Hilbert space.
 The number of bath degrees of freedom $N_\mathrm{b}$ is a
@@
 impurity, thus $N_\mathrm{b}\equiv N_\mathrm{bath}$. 
-The total number of electronic levels in the quantum impurity systems is indicated with $N_\mathrm{s}$.
+The total number of electronic levels in quantum impurity systems is indicated with $N_\mathrm{s}$.
 
@@
   ED\_SETUP} through the input variables {\tt Nspin}$=N_\sigma$,
-{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_\mathrm{bath}$ globally defined {\tt
-  ED\_INPUT\_VARS}. The {\tt Ns}$=N_\mathrm{s}$ variable, evaluated in
+{\tt Norb}$=N_\a$ and {\tt Nbath}$=N_\mathrm{bath}$ globally defined in {\tt
+  ED\_INPUT\_VARS}. The variable {\tt Ns}$=N_\mathrm{s}$, evaluated in
 {\tt ed\_setup\_dimensions}, corresponds to the total number of
@@
 The local non-interacting Hamiltonian
-$h^0_{\a\b\s\s'}$ is specified using the function {\tt ed\_set\_hloc} in {\tt ED\_AUX\_FUNX}.
+$h^0_{\a\b\s\s'}$ is specified using the function {\tt ed\_set\_hloc} from {\tt ED\_AUX\_FUNX}.
 The setup of the bath matrices $h^p_{\a\b\s\s'}$
-requires a more involved procedure which will be illustrated in
+requires a more involved procedure, which will be illustrated in
 \secu{sSecBath}.
@@
 in a computer using a sequence of $2N_\mathrm{s}$ bits, or equivalently, as an integer $I=0,\dots 2^{2N_\mathrm{s}}-1$ such that $\ket{\vec{n}}=\ket{I}$.  
-The electornic destruction and creation operators, $c_{a\sigma}$ and $c^+_{a\sigma}$ 
+The electronic destruction and creation operators, $c_{a\sigma}$ and $c^\dagger_{a\sigma}$ 
 respectively, act on the Fock space as:
@@
     \end{cases};\\
-    c^{+}_{a\sigma}\ket{\vec{n}} &=
+    c^\dagger_{a\sigma}\ket{\vec{n}} &=
      \begin{cases}
@@
 where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ accounts for the fermionic sign imposed by the Pauli principle.
-The bosonic operators $b$ and $b^\dagger$ act on the phonon part of $\ket{p}$ of the Fock state as:
+The bosonic operators $b$ and $b^\dagger$ act on the phonon part $\ket{p}$ of the Fock state as
 \begin{align*}
-  b\ket{p} &= \sqrt{p-1}\ket{p} \\
-  b^\dagger\ket{p} &= \sqrt{p}\ket{p} \\
+  b\ket{p} &= \sqrt{p-1}\ket{p}, \\
+  b^\dagger\ket{p} &= \sqrt{p}\ket{p}. \\
 \end{align*}
 The implementation of Fock states and operators can be found in 
-{\tt ED\_AUX\_FUNX}. In particular, in this module we define the bitwise action 
-of fermionic creation and annihilation operators as functions 
+{\tt ED\_AUX\_FUNX}. In particular, in that module we define the bitwise action 
+of the fermionic creation and annihilation operators as functions 
 {\tt CDG} and {\tt C}, used throughout the code. Additionally, 
@@
 \begin{lstlisting}[style=fstyle,numbers=none]
- !Binary decomposition of the ${\color{comment-color} i\in\NNN}$ with Ntot-bits
+ !Binary decomposition of the ${\color{comment-color} i\in\NNN}$ with Ntot bits
  function Bdecomp(i,Ntot) result(ivec)
@@
 gains, making it less practical in many cases.
-As the symmetries applies to the electronic terms, here we discuss the organization of the electronic Fock states only.
-The presence of phonon is accounted for exploiting the tensor structure of the global Fock space.
-
-In \NAME, three different symmetry configurations are available, 
+As the symmetries apply to the electronic terms, here we discuss the organization of the electronic Fock states only.
+The presence of phonons is accounted for by exploiting the tensor structure of the global Fock space.
+
+In \NAME, three different symmetry configurations 
 controlled by the input variable {\tt ed\_mode} = {\bf normal}, 
-{\bf superc}, or {\bf nonsu2}. A summary of the sector properties is provided in
+{\bf superc}, {\bf nonsu2} are available. A summary of the sector properties is provided in
 Table~(\ref{TabSector}).
@@
 \begin{itemize}
-\item{} The {\bf normal} case conserves both the electrons total occupation $N$
+\item{} The {\bf normal} case conserves both the electrons' total occupation $N$
 and total magnetization $S_z$, or equivalently, the total number
@@
 Optionally, the symmetry
-can be extended to act independently to each orbital and spin
+can be extended to act independently on each orbital and spin
 component, i.e.~$\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
 specific case is discussed extensively
-Ref.~\cite{Amaricci2022} so we will not be further cover it here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
+Ref.~\cite{Amaricci2022}, so we will cover it no further here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
 
@@
 \item{} The {\bf nonsu2} case conserves the total
-charge $N$ while allowing spin symmetry group to be not conserved.
+charge $N$ while allowing the spin symmetry group to be broken.
 This scenario captures effects such as local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}, in-plane spin ordering~\cite{BellomiaKMH} or
+$\vec{L}\cdot\vec{S}$~\cite{something}\fixme{Missing citation}, in-plane spin ordering~\cite{BellomiaKMH} or
 in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
@@
 \begin{table}%[ht]
-\begin{center}
 \begin{tabularx}{\linewidth}{ |X|X|X| }
@@
   \hline
-  {\bf normal} & $[N,S_z]\equiv[N_\up,N_\dw]$ &
+  {\bf normal} & $[N,S_z]\Leftrightarrow[N_\up,N_\dw]$ &
                                                 $\binom{N_\mathrm{s}}{N_\up}\binom{N_\mathrm{s}}{N_\dw}$
@@
  \hline  
-  \label{TabSector}
 \end{tabularx}
-\end{center}
-\caption{
-  {\bf Quantum Numbers Table}.
+\vspace{2mm}
+\caption{\label{TabSector}
+  {\bf Quantum Numbers}.
 A table summarizing the possible values of the input variable {\tt
@@
 \end{table}
+
 From a computational perspective, constructing a symmetry
-sector amounts to defining a injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ which relates the electronic states $\ket{i}$
+sector amounts to defining an injective map
+$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the electronic states $\ket{i}$
 within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I_e}$ in the Fock space.
 This map is typically implemented as a rank-1
-integer array whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
+integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
 The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p 2^{2 N_s}$.
@@
 The presence of a symmetry reduces the electronic Hamiltonian matrix to
-a block diagonal form, where each block, labeled by $\vec{Q}$, has dimension
+a block-diagonal form, where each block labeled by $\vec{Q}$ has dimension
 $D_{\SS_{\vec{Q}}}$. The sector Hamiltonian matrix $H_\SS$ is represented in the
@@
 The analysis of the spectrum is then reduced to inspecting the
-Hamiltonian within each symmetry sector, or to a subset thereof if a
+Hamiltonian within each symmetry sector, or to a subset thereof if
 additional constraints are present.
@@
 
-In \NAME the implementation of symmetry sectors is managed through the
+In \NAME, the implementation of symmetry sectors is managed through the
 {\tt sector} object, which is defined in {\tt
@@
 the value of {\tt ed\_mode}.
-The following  code snippet summarize the various available implementations.
-The core idea is to loop of necessary Fock states through the integers $I_\sigma=1,\dots,2^{N_s}$ and enforce the quantum number constraint:
+The following code snippets summarize the various available implementations.
+The core idea is to loop over the necessary Fock states through the integers $I_\sigma=1,\dots,2^{N_s}$ and to enforce the quantum number constraint:
 
@@
 \subsection{Interaction setup}\label{sSecIntSetup}
-\NAME offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}$ in \equ{Himp}, which are controlled by the input variables {\tt
+\NAME offers two distinct methods to setup the interaction terms $\hat{H}^\mathrm{int}_\mathrm{imp}$ in \equ{Himp}, which are controlled by the input variables {\tt
   ED\_USE\_KANAMORI} and {\tt ED\_READ\_UMATRIX}.
@@
 These quantities can be specified either in the input file or directly
-via the the command line, provided the logical input parameter {\tt ED\_USE\_KANAMORI=T} and setting {\tt ED\_READ\_UMATRIX=F}.
+via the command line, provided the logical input parameter {\tt ED\_USE\_KANAMORI=T} and setting {\tt ED\_READ\_UMATRIX=F}.
 In this mode, the maximum number of impurity orbitals {\tt NORB}$=N_\a$ is limited to $5$.
 
-Alternatively, setting {\tt ED\_USE\_KANAMORI=F} and {\tt ED\_READ\_UMATRIX=T}, a list of two-body operators can be supplied by the user in a properly
+Alternatively, setting {\tt ED\_USE\_KANAMORI=F} and {\tt ED\_READ\_UMATRIX=T}, a list of two-body interaction operators can be supplied by the user in a properly
 formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}.  
@@
 \end{lstlisting}
-where {\tt NORB} is the numer of orbitals $N_\a$.\\
+where {\tt NORB} is the number of orbitals $N_\a$.\\
 Each line defines a two-body second-quantized operator of the form 
 $$
-\hat{H}^{\mathrm{int}}=\frac{1}{2}c^{\dagger}_{i}c^{\dagger}_{j}U_{ijkl}c_{l}c_{k}.
+\hat{H}^{\mathrm{int}}=\frac{1}{2}d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.
 $$
@@
 To clear the list, the procedure {\tt reset\_umatrix} has to be called.\\
-For reference and future use, when the impurity problem is solved a list of the interaction operators used in each call to the solver is saved in the output file 
+For reference and future use, when the impurity problem is solved, a list of the interaction operators used in each call to the solver is saved in the output file 
 {\tt <UMATRIX\_FILE>.used}.
@@
 \begin{lstlisting}[style=fstyle,numbers=none]
-! sparse row: contains the NNZ elements on anyrow of the sparse matrix.
+! sparse row: contains the NNZ elements on any row of the sparse matrix.
 type sparse_row_csr
@@
 \subsubsection{Sparse map}\label{CodeSparseMap}
+\fixme{General question: Could it be more instructive to use the left bit shift notation in some expression, e.g. $A \ll N$ instead of $A \cdot 2^N$?}
 As discussed in \secu{sSecRDM}, the construction of a symmetry 
 sector often requires associating each sector state $\ket{i}$ with 
-disjoint information about the corresponding electronic Fock state $\ket{I_e}$. 
+information about the corresponding electronic Fock state $\ket{I_e}$. 
 In this context, the electronic Fock state can be decomposed into bit chunks, 
-e.g., $\ket{\vec{n}} = \ket{\vec{i}_\up\,\vec{b}_\up\,
+e.g. $\ket{\vec{n}} = \ket{\vec{i}_\up\,\vec{b}_\up\,
 \vec{i}_\dw\,\vec{b}_\dw}$, reflecting a natural grouping into impurity 
@@
 
-The {\tt ED\_SPARSE\_MAP} module provides an efficient hash-table 
-implementation, {\tt sparse\_map} which is part part of the {\tt
+The module {\tt ED\_SPARSE\_MAP} provides an efficient hash table 
+implementation, {\tt sparse\_map} which is part of the {\tt
   sector} object and stores the relation between these bit chunks. 
@@
 quantum numbers of the given sector (see \secu{sSecQNs}).
-The {\tt sparse\_map} ${\cal P}$ objects are constructed upon call of the {\tt
+The {\tt sparse\_map} objects ${\cal P}$ are constructed upon call of the {\tt
   build\_sector} ({\tt sector} constructor) using different algorithms 
@@
 \begin{lstlisting}[style=fstyle,numbers=none]
-!sparse row: contains bath states values for each impurity key 
+!sparse row: contains bath state values for each impurity key 
 type sparse_row
@@
 Note that, for the purpose of storing the key-value pairs, the impurity and bath indices are determined using an algorithm different from \equ{spMapEq1}.   
-These relations ensure a better scalign and can be easily inverted to obtain $I_{\sigma=\up,\dw}$ from
+These relations ensure a better scaling and can be easily inverted to obtain $I_{\sigma=\up,\dw}$ from
 $I$ and $B_{\sigma=\up,\dw}$ from $B$ in order to reconstruct the Fock
@@
   !...
-  !Key: impurity bitset.
   iImp  = ibits(iup,0,Norb)
@@
 
-leveraging the Fortran intrinsic function {\tt ibits(I,pos,len)} which returns the integer representation of the bit subset of length {\tt len} starting from {\tt pos} of the  integer {\tt I}.
+It leverages the Fortran intrinsic function {\tt ibits(I,pos,len)} which returns the integer representation of the bit subset of length {\tt len} starting from {\tt pos} of the  integer {\tt I}.
 
 \subsubsection{Eigenspace}\label{CodeEigenspace}
-The {\tt ED\_EIGENSPACE} module contains the implementation of the 
-{\tt sparse\_espace} class, which maintains an ordered linked list 
+The module {\tt ED\_EIGENSPACE} contains the implementation of the 
+class {\tt sparse\_espace}, which maintains a linked list 
 of selected eigenvalues, eigenvectors, and quantum numbers for the 
@@
 according to the nature of the quantum numbers $\vec{Q}$.
-While for zero-temperature calculations only the ground-state (with its
-degeneracy) is stored, for finite temperatures the list  also include all the necessary excited states.
+While for zero-temperature calculations only the ground state (with its
+degeneracy) is stored, for finite temperatures the list also includes all the necessary excited states.
 
 \begin{lstlisting}[style=fstyle,numbers=none]    
-!Single element of the list: contains a single eigen-solution.
+!Single element of the list: contains a single eigenpair.
 !Twin states are just pointers, no memory.
-!double or cmplx vector are automatically MPI distributed.
+!double or cmplx vectors are automatically MPI distributed.
 type sparse_estate
@@
    real(8)                             :: e             !eigenvalue: ordering key
-   real(8),dimension(:),allocatable    :: dvec          !double  eigen-vector
-   complex(8),dimension(:),allocatable :: cvec          !complex eigen-vector
+   real(8),dimension(:),allocatable    :: dvec          !double  eigenvector
+   complex(8),dimension(:),allocatable :: cvec          !complex eigenvector
    logical                             :: itwin=.false. !twin sector logical label
@@
    integer                     :: size               !Current list
-   real(8)                     :: emax               !Max energy  fixed by ${e^{-\beta {\tt emax}}<{\tt cutoff}}$
-   real(8)                     :: emin               !Min energy:the groundstate energy
+   real(8)                     :: emax               !Max energy fixed by ${\color{comment-color}e^{-\beta {\tt emax}}\!<\!{\tt cutoff}}$
+   real(8)                     :: emin               !Min energy: the ground state energy
    logical                     :: status=.false.     !Allocation status
@@
 $E_i$ is the energy of the $i^{\rm th}$ state in the list, $E_0$ is the
-groundstate energy,  $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff} is an input parameter fixing an {\it a-priori} energy threshold.
+ground state energy, $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff} is an input parameter fixing an {\it a priori} energy threshold.
 
@@
 \subsubsection{GFmatrix}
-One of the main goal of the \NAME is to evaluate dynamical correlations
-functions (DCF), e.g. $C(t) = \ibra \TT[ A(t) A^+ ]\iket$. Using Krylov methods,  
+One of the main goals of the \NAME is to evaluate dynamical correlations
+functions (DCF), e.g. $C(t) = \ibra \TT[ A(t) A^\dagger ]\iket$. Using Krylov methods,
 these DCFs can be expressed as truncated K\"all\'en-Lehmann spectral sums of the form
@@
 $m^{\rm th}$ eigenstate onto the $n^{\rm th}$ Krylov basis vector and
-$dE_{mn}=E_m-E_n$ is the corresponding excitation energy.
-
-The {\tt ED\_GFMATRIX} module implements the {\tt gfmatrix} class, 
+$dE_{mn}=E_m-E_n$ is the corresponding excitation energy.\fixme{How does the operator $A$ enter this expression?}
+
+The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, 
 which provides an efficient, multi-layer data structure for storing 
@@
 \begin{lstlisting}[style=fstyle,numbers=none]   
-!The contributions to the GF K\"all\'en-Lehmann sum are stored as
+!The contributions to the GF Kallen-Lehmann sum are stored as
 !GF_{ab,sr}%state%channel%{w,e}.
@@
 !N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
-!Sub-class: contains a given set of weights and poles.
-!Each instance of this sub-class correponds to a given input state 
-!and a given operator in the K\"all\'en-Lehmann representation.  
+!Subclass: contains a given set of weights and poles.
+!Each instance of this subclass corresponds to a given input state 
+!and a given operator in the Kallen-Lehmann representation.  
 type GFchannel
@@
 !obtained through the dynamical Lanczos algorithm.
-!state_list%size = # of state in the spectrum 
+!state_list%size = Number of states in the spectrum 
 type GFmatrix
    type(GFchannel),dimension(:),allocatable  :: state
-   logical                                   :: status=.false.!Allocation status
+   logical                                   :: status=.false. !Allocation status
 end type GFmatrix
@@
 $$
-h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'} .
+h^p_{\a\b\s\s'}=\varepsilon_{\a\s}\delta_{\a\b}\delta_{\s\s'},
 $$
@@
 considered. In this case, the bath Hamiltonian gains 
-an additional set of parameters $\Delta^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$, diagonal in orbital space but
+an additional set of parameters $\Delta^p_{\a}\delta_{\a\b}\delta_{\s \bar{\s}}$, diagonal in orbital space but
 off-diagonal in the spin, where $\Delta^p_\a$ represents the pairing amplitudes. 
@@
 %
-If {\tt ed\_mode}={\bf nonsu2}  an additional set including terms describing spin-flip processes (as total magnetization is not conserved) should be included $V^p_{\a\b\s\s'} =
-W^p_{\a}\delta_{\a\b}\delta_{\s \overline{\s}}$. 
+If {\tt ed\_mode}={\bf nonsu2}  an additional set including terms describing spin-flip processes (as total magnetization is not conserved) should be included, $V^p_{\a\b\s\s'} =
+W^p_{\a}\delta_{\a\b}\delta_{\s \bar{\s}}$. 
 %
@@
 This hybrid topology is the simplest generalization of the bath pa\-ra\-me\-tri\-za\-tion which captures the effects of locally
-coupled impurity orbitals. However this setup typically requires a more challenging optimization process, especially
+coupled impurity orbitals. However, this setup typically requires a more challenging optimization process, especially
 with few available bath levels (see \secu{sSecFit}). 
@@
 The parametrization of the bath Hamiltonian is 
-diagonal in both orbital and spin space, i.e.,
+diagonal in both orbital and spin space, i.e.
 $$
@@
 %
-The key difference with respect to the previous case is that the hybridization matrix elements are generally off-diagonal in the orbital indices:
+The key difference compared to the previous case is that the hybridization matrix elements are generally off-diagonal in the orbital indices:
 $$
@@
 Moreover, the {\tt ed\_mode}={\bf superc} introduces additional anomalous components 
-$\Delta^p_{\a\b}\delta_{\s\overline{\s}}$, including intra- and inter-orbital pairings.
+$\Delta^p_{\a\b}\delta_{\s\bar{\s}}$, including intra- and inter-orbital pairings.
 %
@@
 set of parameters must be specified to account for spin-flip processes:
-$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \overline{\s}}$. 
+$V^p_{\a\b\s\s'} = W^p_{\a\b}\delta_{\s \bar{\s}}$. 
 %
-The resulting total number of available bath parameters are 
+The resulting total numbers of available bath parameters are 
  $N_\mathrm{param}=N_\mathrm{bath}+ N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal},  
@@
 
-\paragraph{{\tt bath\_type}={\bf replica},{\bf general}.}
+\paragraph{{\tt bath\_type}={\bf replica}, {\bf general}.}
 This configuration provides a more flexible parametrization of the 
@@
 From a broader perspective, this can be formalized by considering  
-a user-defined matrix basis of dimension $N_\mathrm{sys}$ 
+a user-defined matrix basis of dimension $N_\mathrm{sym}$, 
 $\vec{\Gamma}=\{ \Gamma^\nu_{\a\b\s\s'} \}_{\nu=1,\dots,N_\mathrm{sym}}$ in the (Nambu-)spin-orbital
@@
 h^p = \sum_{\nu=1}^{N_\mathrm{sym}} \lambda^p_\nu
-\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma}
+\Gamma^\nu\equiv \vec{\lambda}^p\cdot \vec{\Gamma},
 \label{eq:replica_bath_sym}
@@
 All the procedures concerning the bath, either on the user side or concerning the internal {\tt effective\_bath}, are grouped into a set of modules wrapped by {\tt ED\_BATH}.
-We divided the set of modules in three categories, according to their scope.
+We divided the set of modules into three categories, according to their scope.
 
 \paragraph{Bath Auxiliary Tools.}
-This module group provides user-oriented utilities, including 
+This group of modules provides user-oriented utilities, including 
 standard symmetry operations on the bath array, such as orbital 
@@
 
-\paragraph{Bath Replica/General.}
+\paragraph{Bath replica/general.}
 The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica}/{\tt Hge\-ne\-ral} for the {\bf replica}/{\bf general} bath parametrizations.
@@
 The bath Hamiltonian is constructed with the function 
-{\tt build\_Hreplica}/{\tt build\_Hge\-ne\-ral} via the relation:
+{\tt build\_Hreplica}/{\tt build\_Hge\-ne\-ral} via the relation
 $$
@@
 a Hamiltonian matrix $H_{\SS_{\vec{Q}}}$. 
-Consequently, the analysis of the quantum impurity energy spectrum reduces to solving
+Consequently, the analysis of the energy spectrum of the quantum impurity reduces to solving
 the secular equation within each individual symmetry sector:
@@
 Even though the dimension of a given sector $\SS_{\vec{Q}}$ is much smaller than the
-total Fock space dimension $D_\SS \ll D_\FF$, solving completely the
-corresponding eigenvalue problem remains a formidable challenge
+total Fock space dimension $D_\SS \ll D_\FF$, solving the
+corresponding eigenvalue problem completely remains a formidable challenge
 already for $N_\mathrm{s}\simeq 8$.
 To outwit this, various
-algorithms have been developed exploiting the sparse nature of
-$H_\SS$, including Krylov subspace methods and related approaches
+algorithms exploiting the sparse nature of
+$H_\SS$ have been developed, including Krylov subspace methods and related approaches
 \cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996,Siro2012CPC,Siro2016CPC}.
@@
 \cite{Lehoucq1998}. This method incorporates re-orthogonalization within
-a block-Lanczos routine, ensuring the accurate convergence of the desired eigen-pairs. However, it is also possible to select a simpler,
+a block-Lanczos routine, ensuring the accurate convergence of the desired eigenpairs. However, it is also possible to select a simpler,
 though less efficient, parallel Lanczos algorithm using the input variable {\tt lanc\_method}.
@@
 \end{equation}
-This operation accounts for more than 80\% of the overall
+This operation amounts to more than 80\% of the overall
 computational effort, making its optimization a critical aspect of
 high-performance diagonalization algorithms.
-In \onlinecite{Amaricci2022} we discussed in greater details the distributed-memory massively parallel strategies currently employed in \NAME to optimize this step and present various benchmarks of the parallel scaling.
+In \onlinecite{Amaricci2022} we discussed in greater details the distributed-memory massively parallel strategies currently employed in \NAME to optimize this step and presented various benchmarks of the parallel scaling.
 Here, we provide a brief outline of the main ideas following the notation introduced
@@
   This latter step is controlled by the value of
-{\tt ed\_sparse\_H=T/F}. If {\tt T} the Hamiltonian $H_\SS$
+{\tt ed\_sparse\_H=T/F}. If {\tt T}, the Hamiltonian $H_\SS$
 gets stored in a {\tt sparse\_matrix} instance and used to perform
@@
   ED\_HAMILTONIAN\-\_\-<ed\_mode>\-\_\-STORED\-\_HxV}.
-If {\tt ed\_sparse\_H} is {\tt F} the MVP is operated on-the-fly,
+If {\tt ed\_sparse\_H} is {\tt F}, the MVP is operated on-the-fly,
 i.e. each element of $H_\SS$ is directly applied to the input
@@
 dimension of the vector used in the
-MVP. In a MPI-parallel execution the returned value is the
+MVP. In an MPI-parallel execution the returned value is the
 dimension $d_i$ of the vector chunk per each node such that
@@
 \ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}.
-\end{equation}
-Here, creation (destruction) operators  $c^+_{p\sigma}$
-($c^+_{p\sigma}$) at position $p$ and for a given spin $\sigma$
+\label{eq:decomposition_for_rdm_normal}
+\end{equation}
+Here, creation (destruction) operators  $c^\dagger_{p\sigma}$
+($c^\dagger_{p\sigma}$) at position $p$ and for a given spin $\sigma$
 act only on the corresponding 
@@
   \begin{aligned}
-  \rho^\mathrm{imp} &= \Tr_{b_\up b_\dw}{\rho} = 
+  \rho^\mathrm{imp} &= {\color{Plum}\Tr_{b_\up b_\dw}}{\rho} = 
+  {\color{Plum}
   \sum_{b_\up=1}^{D_{b_\up}}
   \sum_{b_\dw=1}^{D_{b_\dw}}
+  }
   \bra{b_\up}\otimes\bra{b_\dw}
@@
     &=
+    {\color{Plum}
     \sum_{b_\up=1}^{D_{b_\up}}
+    }
     \sum_{i_\up=1}^{D_{i_\up}}
@@
     \sum_{q_\up=1}^{D_{q_\up}}
-    \Bigg(    \sum_{b_\dw=1}^{D_{b_\dw}}
+    \Bigg(    
+    {\color{Plum}
+    \sum_{b_\dw=1}^{D_{b_\dw}}
+    }
     \sum_{i_\dw=1}^{D_{i_\dw}}
@@
     \underbrace{\left(
+    {\color{Plum}
     \sum_{b_\up=1}^{D_{b_\up}}
     \sum_{b_\dw=1}^{D_{b_\dw}}
+    }
     a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
@@
 mode, as enforced by the Kronecker deltas for bath and impurity 
-indices.
+indices.\fixme{(igor and lorenzo) to be honest we took a while to understand this equation.
+There are a lot of indices...
+could it be rewritten more compactly e.g.
+by not explicitly writing |p><q|?
+Or perhaps by only showing one spin species, since the Fock space factorizes?
+Or alternatively, maybe color-code the parts?
+I get that
+sum\_p sum\_q <b|p><q|b> is a trace... but it's not immediate}
+{\color{teal}(Gabriele) Mmm, if I recall it correctly, surely writing it for just
+one spin species (after saying that the final rho factorizes), would look 
+cleaner, but the fermionic signs will need to be computed explicitly. Cause
+they cancel to 1 only after actually doing the product between the up and the
+dw part. Color coding the parts could be very pretty and easy to follow,
+\sout{I can think about that, thanks for the feedback!} I tried, by highlighting
+the summations involved in the trace. All the remaining indices come from the
+full impurity-bath and up-dw decomposition of the state, that is clearlly written
+in equation (\ref{eq:decomposition_for_rdm_normal})}
 

### 2025-05-28 04_cbinding.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 the underlying Fortran library and automatically selects the appropriate
-{\tt ed\_mode} (see Sec.~\ref{sSecQNs}) and
-{\tt bath\_type} (see Sec.~\ref{sSecBath}). In addition, the
+{\tt ed\_mode} (see \secu{sSecQNs}) and
+{\tt bath\_type} (see \secu{sSecBath}). In addition, the
 constructor accepts a vast array of keyword arguments that allow for fine-tuning
@@
           the quadratic impurity Hamiltonian \equ{Himp}.
-    \item {\tt U} --- 8-dimensional array $U_{\alpha\sigma_1,\beta\sigma_2,\gamma\sigma_3,\delta\sigma_4}$
-          of two-particle interactions as defined in Eq.~(\ref{HintUmat}).
+    \item {\tt U} --- 8-dimensional array $U_{\alpha\s_1,\beta\s_2,\gamma\s_3,\delta\s_4}$
+          of two-particle interactions as defined in \equ{HintUmat}.
     \item {\tt bath} --- an object representing the bath. Depending on the

### 2025-05-28 05_examples.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \subsection{Holstein model on the Bethe lattice (electron-phonon coupling)}
-One of the features introduced in \NAME is the possibility of treating
-local phonons in conjunction with the superconductive phase,
+
+One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
 i.e. \textbf{ed\_mode=superc}. 
-In this example discuss  the normal and
+In this example, we discuss  the normal and
 superconductive solution of the pure Holstein model on the Bethe
@@
 \end{equation}
-We consider the half-filling regime of the particle-hole symmetric
-Bethe lattice density of states. We set the half-bandwidth as our
-energy unit $D=1$ and introduced the electron-phonon coupling $\lambda
-= \tfrac{2g^2}{\omega_0D}$.  
+We consider the half-filling regime of the particle-hole symmetric Bethe lattice density of states.
+We set the half-bandwidth as our energy unit $D=1$ and introduced the electron-phonon coupling $\lambda = \tfrac{2g^2}{\omega_0D}$.
 The iterative DMFT solution algorithm follows the same principles
@@
 phonon frequency $\omega_0$, see panel (A). In this panel we compare
-the behavior for {\tt ed\_mode=normal} against the superconductive
+the behavior for the normal solution ({\tt ed\_mode=normal}) against the superconductive
 solution ({\tt ed\_mode=superc}). Our results capture the whole
@@
         type (\ref{Hint}). This illustration is produced by the edipack2triqs
-        example script presented in Sec.~\ref{SecExamplesTRIQS}.
+        example script presented in \secu{SecExamplesTRIQS}.
     }
@@
 We proceed to demonstrate how to use the edipack2triqs compatibility
-layer (Sec.~\ref{sSecInteropTRIQS}) to solve a quantum system comprised by a
+layer (\secu{sSecInteropTRIQS}) to solve a quantum system comprised by a
 3-orbital correlated impurity coupled to a few non-interacting bath sites.
 The interaction term of the impurity Hamiltonian is in the Hubbard-Kanamori
-form (\ref{Hint}).
+form (\equ{Hint}).
 
@@
 TRIQS to visualize the obtained Matsubara and real-frequency impurity Green's
-functions (Fig.~\ref{figEx3}).
+functions (\figu{figEx3}).
 \lstinputlisting[style=mypython,

### 2025-05-28 06_conclusions_acknowledgement_appendix.tex
Huge iteration
- Igor passed through a major part of the manuscript
- Samuele edited some parts of the e-ph section (response to Massimo)
- Adriano added author contributions
- Gabriele answered some comments by Igor and Lorenzo on the iRDM

--------

Co-authored-by: Igor Krivenko <iskrivenko@proton.me>
Co-authored-by: Lorenzo Crippa <crippa.lorenzo@gmail.com>
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>
Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \section*{Acknowledgements}
-We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, A.~Scazzola, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, A.~Camjayi, M.~Rozenberg.
+We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou,  M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, A.~Camjayi, M.~Rozenberg.
 
-% % TODO: include author contributions
-% % This will be used to better attribute supervision of each part of the code, e.g.
-LC for part of the code, C-binding, Py, Julia, Monicelli, etc, IK for EDIpack2Triqs, AK+MW+GS for W2Dyn support, etc.
-% \paragraph{Author contributions}
-% This is optional. If desired, contributions should be succinctly described in a single short paragraph, using author initials.
+\paragraph{Author contributions}
+A.A. designed the project, developed the main structure of the software and conceived the computational algorithms in the core library. 
+L.C., G.M., F.P.
+A.S., S.G.
+and G.B.
+equally contributed to the development and implementation of many different aspects of the  software, including code writing, configuration, installation, testing and continuous integration procedures.
+L.C. devised and developed the C-binding layer, the Python, Julia and Monicelli interface together with Python specific deployment and installation tools. 
+I.K. developed the Triqs interface and contributed to the testing part. 
+A.K., M.W. and G.S. developed the integration with W2Dynamics.  
+A.A. and M.C. conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library. M.C. devised the inclusion of the electron-phonon coupling. 
+A.A., M.C., L.d.M. and G.S designed additional algorithms extending functionalities of the core software.   
+A.A., L.C., I.K., A.K., S.G. and G.B. performed the calculations, analyzed the results and prepared the data presentation in the examples.
+A.A. and L.C. wrote the backbone of the manuscript.
+All authors participated in the writing and revision process.
 
@@
 L.C.
-acknowledge support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994) and gratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb.
+acknowledges support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994) and gratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb.
 NHR funding is provided by federal and Bavarian state authorities.
@@
 acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
-%F.P.
+F.P. acknowledges support from the Swiss National Science Foundation via NCCR Marvel and SNSF Grant No. 200021-196966.
 %M.W.
@@
 introduced in the movies trilogy ``Amici Miei'', directed by Mario
-Monicelli (see
-\url{https://it.wikipedia.org/wiki/Amici_miei}).
+Monicelli (see \href{https://it.wikipedia.org/wiki/Amici_miei}{it.wikipedia.org/wiki/Amici\-\_\-miei}).
 
@@
 due parole come install {\tt Monicelli} from
-\url{https://github.com/esseks/monicelli.git}
+\href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
+%\url{https://github.com/esseks/monicelli.git}
 e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
@@
 \lstset{breaklines=true, breakindent=1em}
-\begin{lstlisting}[style=cstyle,numbers=none]
+\begin{lstlisting}[style=MonicelliStyle,numbers=none]
 bituma le funzioni ausiliarie che vengono dal bagaglio
@@
 
-\begin{lstlisting}[style=cstyle,numbers=none]
+\begin{lstlisting}[style=MonicelliStyle,numbers=none]
 Lei ha clacsonato

### 2025-05-29 03_edipack2.tex
Some fixme comments
Co-authored-by: Samuele Giuli <samuele.giuli@gmail.com>

@@
 If the matrix is diagonal ($g_{\alpha \beta} = g_\alpha \delta_{\alpha \beta}$), from the input file one can simply write in order the values $g_\alpha$ in the variable {\tt G\_PH}.
-For any general shape one can pass to the input file a {\tt GPHfile } variable containing the name of the file storing the $g_{\alpha \beta}$ array in Fortran style.\fixme{I don't seem to understand the last two sentences at all\ldots}
+For any general shape one can pass to the input file a {\tt GPHfile } variable containing the name of the file storing the $g_{\alpha \beta}$ array.
 If {\tt GPHfile=NONE}, the matrix $g_{\alpha\beta}$ is read from the variable {\tt G\_PH}, otherwise it is read from the {\tt GPHfile}.
@@
 with the Hamiltonian matrices taking the form:
+
 $$
@@
 $$
+
+\fixme{ (Samuele) Here and before h with or without hat? I would say without since it is how we wrote it in 3.1.1}
+\fixme{The superc h should have tau\_z instead of tau\_0 in nambu repr}
 where $\tau_{i=0,x,y,z}$ are Pauli matrices.

### 2025-05-29 edipack2_examples/edipack2triqs/hubbard_kanamori.py
Fix example script following 68a9eb3936c9a2e2f00016fe7d0c5e11c4537578

@@ -96,9 +96,9 @@ if MPI.COMM_WORLD.Get_rank() == 0:
     # Plot the Matsubara Green's functions (imaginary part)
     plt.figure(figsize=(4, 4))
     for orb in orbs:
-        oplot(solver.g_iw['up'][orb, orb], mode='I', label=f"$\\Im G_%i(i\\omega_n)$" % orb)
+        oplot(solver.g_iw['up'][orb, orb], mode='I', label=f"${\\rm Im} G_%i(i\\omega_n)$" % orb)
     plt.xlim((-3, 3))
-    plt.ylabel(r"$\Im G(i\omega_n)$")
+    plt.ylabel(r"${\rm Im} G(i\omega_n)$")
     plt.legend()
     plt.savefig("G_iw.pdf")
 

### 2025-05-30 01_intro.tex

@@
 %EDIPACK
-In this work we present the renewed and improved \NAME{}, version number \textcolor{red}{5.0}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+In this work we present the renewed and improved \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
 The library builds on the foundations of
@@
 translational symmetry is broken.
+%Repetition
 
@@
 In this paper, we present the mathematical framework, implementation
-details, and key features of \NAME \textcolor{red}{5.0}, along with several illustrative
+details, and key features of \NAME \textcolor{red}{2.0 i get that we want to say this is the updated edipack, but now it is version 5.0.5...
+i believe this could create confusion}, along with several illustrative
 applications. We aim to demonstrate how this flexible,

### 2025-05-30 03_edipack2.tex

@@
 However, we typically 
-adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ACMP}:
+adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013AROCMP}:
 \begin{equation}
@@
 interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013ACMP}.  
+$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013AROCMP}.  
 The last two terms are, respectively, the spin-exchange ($J_X$) and
@@
 U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ACMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ACMP}.
+$J_X=J_P=J$~\cite{Georges2013AROCMP}. Different choices, preserving part
+of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013AROCMP}.
 
@@
 For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_1 - n_2)$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ h.c.)$.
-For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL_2,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}\fixme{Broken ref}.
+For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}.
 The larger the number of excited phonons in the ground state, the larger the cutoff.
@@
 This scenario captures effects such as local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$~\cite{something}\fixme{Missing citation}, in-plane spin ordering~\cite{BellomiaKMH} or
+$\vec{L}\cdot\vec{S}$, in-plane spin ordering~\cite{BellomiaKMH} or
 in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
@@
 \subsubsection{Sparse map}\label{CodeSparseMap}
-\fixme{General question: Could it be more instructive to use the left bit shift notation in some expression, e.g. $A \ll N$ instead of $A \cdot 2^N$?}
+% \fixme{General question: Could it be more instructive to use the left bit shift notation in some expression, e.g. $A \ll N$ instead of $A \cdot 2^N$?}
 As discussed in \secu{sSecRDM}, the construction of a symmetry 
@@
 $$
-C(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}|^2}{ z
+C(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}(\AA)|^2}{ z
   - dE_{mn}}
 $$
-where $w_{mn}$ is the weight determined by the projection of the
-$m^{\rm th}$ eigenstate onto the $n^{\rm th}$ Krylov basis vector and
-$dE_{mn}=E_m-E_n$ is the corresponding excitation energy.\fixme{How does the operator $A$ enter this expression?}
+where $w_{mn}(\AA)$ is the weight determined by the amplitude of operator $\AA$ between the
+$m^{\rm th}$ eigenstate and the $n^{\rm th}$ Krylov basis vector and
+$dE_{mn}=E_m-E_n$ is the corresponding excitation energy.
+% \fixme{How does the operator $A$ enter this expression?}
 
@@
 off-diagonal in the spin, where $\Delta^p_\a$ represents the pairing amplitudes. 
-This choice corresponds to a Nambu representation for each orbital component,
-with the Hamiltonian matrices taking the form:
-
-$$
-\hat{h}^p_{\a\b} = \e_{\a}\delta_{\a\b}\tau_0 +
-\Delta_{\a}\delta_{\a\b}\tau_x .
-$$
-
-\fixme{ (Samuele) Here and before h with or without hat? I would say without since it is how we wrote it in 3.1.1}
-\fixme{The superc h should have tau\_z instead of tau\_0 in nambu repr}
+This choice corresponds to a Nambu representation for each  component, with the Hamiltonian matrices taking the Nambu form:
+
+$$
+\hat{h}^p = \e^p\tau_z + \Delta^p\tau_x .
+$$
+
+% \fixme{ (Samuele) Here and before h with or without hat? I would say without since it is how we wrote it in 3.1.1}
+% \fixme{The superc h should have tau\_z instead of tau\_0 in nambu repr}
 where $\tau_{i=0,x,y,z}$ are Pauli matrices.
@@
 Moreover, the {\tt ed\_mode}={\bf superc} introduces additional anomalous components 
-$\Delta^p_{\a\b}\delta_{\s\bar{\s}}$, including intra- and inter-orbital pairings.
+$\Delta^p\delta_{\a\b}\delta_{\s\bar{\s}}$ diagonal in the orbital basis.
 %
@@
 \subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian spectrum
-enables the evaluation of the Dynamical Correlation Functions (DCFs) using Krylov sub-space algorithm.
+The determination of the low energy part of the Hamiltonian's spectrum
+enables evaluation of the Dynamical Correlation Functions (DCFs) using Krylov subspace algorithm.
 This capability is central to the library when using \NAME as an
@@
   \label{eqGaa}
-  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^+ ]\iket
+  C_\AA = \ibra \TT_\pm[ \AA(t) \AA^\dagger ]\iket,
 \end{equation}
@@
     C_\AA(z) 
-    &=  \ibra \AA \frac{1}{z-H} \AA^+\iket
-    \mp \ibra \AA^+ \frac{1}{z+H} \AA\iket \cr
+    &=  \ibra \AA \frac{1}{z-H} \AA^\dagger\iket
+    \mp \ibra \AA^\dagger \frac{1}{z+H} \AA\iket \cr
     %
     & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
-  \frac{ |\bra{\psi_m}\AA^+ \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
+  \frac{ |\bra{\psi_m}\AA^\dagger \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
   \mp
-  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)}\cr
+  \frac{ |\bra{\psi_m}\AA \ket{\psi_n}|^2 }  {z+(E_m-E_n)},\cr
 \end{split}
 \end{equation}
-where $z\in\CCC$,  $\ket{\psi_n}$, $E_n$ are the eigen-solutions of the
+where $z\in\CCC$, and $\{\ket{\psi_n}, E_n\}$ are the eigenpairs of the
 Hamiltonian $H$. 
 This form is appealing but computationally prohibitive, as it requires
-the full Hamiltonian spectrum. However, the first line in \equ{KLgf}
+the full spectrum of the Hamiltonian. However, the first line in \equ{KLgf}
 highlights that the $C_\AA$ essentially corresponds to a specific
-matrix element of the resolvant operator $(z-H)^{-1}$, which can be
-efficiently approximated using the Krylov sub-space method.
-
-To illustrate this approach, consider the normalized initial state: 
-$$
-\ket{\phi_n}=\AA^+\ket{\psi_n}/\NN_n
+matrix element of the resolvent operator $(z-H)^{-1}$, which can be
+efficiently approximated using the Krylov subspace method.
+
+To illustrate this approach, consider the normalized initial state
+$$
+\ket{\phi_n}=\AA^\dagger\ket{\psi_n}/\NN_n,
 $$
 where  $\ket{\psi_n}\in\SS_{\vec{Q}}$ is an eigenstate of the sector Hamiltonian and $\NN_n=\sqrt{\bra{\psi_n}\AA
-  \AA^+\ket{\psi_n}}$.
+  \AA^\dagger\ket{\psi_n}}$.
 The Krylov basis is constructed by repeated applications of the sector Hamiltonian via MVP: 
@@
 $$ 
-with $1 \ll N \ll \DD_\SS$..
+with $1 \ll N \ll \DD_\SS$.
 Given that any eigenstate $\ket{\psi_n}$ can be expressed within the Krylov basis as
@@
     C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
-    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^+\ket{\psi_n} |a^n_m|^2}{
-      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^+ \AA\ket{\psi_n}
+    \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^\dagger\ket{\psi_n} |a^n_m|^2}{
+      z - (E_m-E_n)} \mp \frac{\bra{\psi_n}\AA^\dagger \AA\ket{\psi_n}
       |a^n_m|^2}{ z + (E_m-E_n)}\cr
@@
     = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}) \cr
+    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
   \end{split}
@@
 where the terms are grouped as a sum over spectral weights and
-poles. We introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$
+poles. We introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$ does $g$ also depend on $z$?
 for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
@@
 contributing to the low energy spectrum, for every order $m$ of the
-Krylov sub-space algorithm and for channel $\nu$.
+Krylov subspace algorithm and for channel $\nu$.
 This approach significantly reduces the computational burden, as it
-relies on a much smaller set of basis states.
+requires a much smaller set of basis states.
 
 However, this method is typically limited to diagonal DCF like
-\equ{eqGaa}. In practice, many applications requires also to build off-diagonal
-functions of the form:
-$$
-C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^+]\iket\, .
+\equ{eqGaa}. In practice, many applications also require building off-diagonal
+functions of the form
+$$
+C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^\dagger]\iket\, .
 $$
 This can be addressed by introducing auxiliary operators, e.g.  $\OO=\AA +\BB$ and
-$\PP=\AA-i\BB$, enabling the extraction of the desired function via
+$\PP=\AA-i\BB$, enabling extraction of the desired function via
 simple algebraic combinations:
@@
 $$
-G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^+ ]\iket
-$$
-is handled by the \texttt{ED\_GREENS\_FUNCTIONS} module.
-This integrates more specialized methods based on the symmetry
+G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^\dagger ]\iket
+$$
+is handled by the module \texttt{ED\_GREENS\_FUNCTIONS}.
+It integrates more specialized methods based on the symmetry
 classification defined by the \texttt{ed\_mode} parameter.
@@
 $\chi^{S^z}_{\a\a}$, $\chi^N_{\a\a}$ and $\chi^\Delta_{\a\a}$
-are constructed using the operators $S^z_\a = \sum_{\s\s'} c^+_{\a\s}
+are constructed using the operators $S^z_\a = \sum_{\s\s'} c^\dagger_{\a\s}
 \tau^z_{\s\s'} c_{\a\s'}$, 
-$N_\a = \sum_{\s\s'} c^+_{\a\s} \tau^0_{\s\s'} c_{\a\s'}$
+$N_\a = \sum_{\s\s'} c^\dagger_{\a\s} \tau^0_{\s\s'} c_{\a\s'}$
 and $\Delta_\a = c_{\a\dw}c_{\a\up}$,
@@
 The excitonic susceptibilities, $\chi^{\vec{E}}_{\a\b}$, are defined with 
-respect to the vector operator: $E^i_{\a\b} = \sum_{\s\s'}
-c^+_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
-spin-singlet exciton, and $i=x,y,z$  correspond to the spin-triplet exciton.
+respect to the vector operator $E^i_{\a\b} = \sum_{\s\s'}
+c^\dagger_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
+spin-singlet exciton\cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton.
 
@@
 $\PP = c_{\a\up} - i c_{\b\up}$. This allows us to express 
-the Green's function as::
+the Green's function as
 $G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
@@
 $\bar{G}_{\a\a\dw\dw}$ is evaluated as an auxiliary term 
-using $\AA = c^+_{\a\dw}$. Then, we construct the two  
-linear combinations:
+using $\AA = c^\dagger_{\a\dw}$. Then, we construct the two  
+linear combinations
 \begin{align*}
@@
 $C_\RR$, respectively. The final expression for the 
-anomalous function reads:
+anomalous function reads
 \begin{equation}
@@
 must be explicitly evaluated, as the spin and orbital 
-symmetries are in general not conserved. For the diagonal terms 
+symmetries are in general broken. For the diagonal terms 
 $G_{\a\a\s\s}$, the procedure follows the same approach 
@@
 energy, pair amplitudes, and excitonic order parameters, 
-are computed in the \texttt{OBSERVABLES} module. Similar to 
+are computed in the \texttt{OBSERVABLES} module. Similar to the
 previous cases, this module wraps different implementations 
@@
 ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
-\equ{eq:thermal_average}.
+\equ{eq:thermal_average}.What is the meaning of $\langle\rangle$ here?
+\equ{eq:thermal_average} contains a weighted sum over the states of the full system, while $\rho^\mathrm{imp}$ is already reduced over the bath degrees of freedom.
 
@@
 the summation to the sector size $D_\SS$ of the symmetry sector 
-$\SS$ to which the ground state (or any eigenstate) belongs, and avoiding
+$\SS$, to which the ground state (or any eigenstate) belongs, and avoiding
 the storage of the large matrix associated with $\rho$.
@@
 The global bitset can be split into spin-resolved 
-impurity and bath components as:
+impurity and bath components as
 \begin{equation}
@@
 mode, as enforced by the Kronecker deltas for bath and impurity 
-indices.\fixme{(igor and lorenzo) to be honest we took a while to understand this equation.
+indices.
+% \fixme{(igor and lorenzo) to be honest we took a while to understand this equation.
 There are a lot of indices...
@@
 I get that
-sum\_p sum\_q <b|p><q|b> is a trace... but it's not immediate}
-{\color{teal}(Gabriele) Mmm, if I recall it correctly, surely writing it for just
-one spin species (after saying that the final rho factorizes), would look 
-cleaner, but the fermionic signs will need to be computed explicitly. Cause
-they cancel to 1 only after actually doing the product between the up and the
-dw part. Color coding the parts could be very pretty and easy to follow,
-\sout{I can think about that, thanks for the feedback!} I tried, by highlighting
-the summations involved in the trace. All the remaining indices come from the
-full impurity-bath and up-dw decomposition of the state, that is clearlly written
-in equation (\ref{eq:decomposition_for_rdm_normal})}
+% sum\_p sum\_q <b|p><q|b> is a trace... but it's not immediate}
+% {\color{teal}(Gabriele) Mmm, if I recall it correctly, surely writing it for just
+% one spin species (after saying that the final rho factorizes), would look 
+% cleaner, but the fermionic signs will need to be computed explicitly. Cause
+% they cancel to 1 only after actually doing the product between the up and the
+% dw part. Color coding the parts could be very pretty and easy to follow,
+% \sout{I can think about that, thanks for the feedback!} I tried, by highlighting
+% the summations involved in the trace. All the remaining indices come from the
+% full impurity-bath and up-dw decomposition of the state, that is clearlly written
+% in equation (\ref{eq:decomposition_for_rdm_normal})}
 
 The numerical implementation relies on the use of the {\tt
-  sparse\_map} ($\%sp$) for the groundstate sector as reported in the listing below:  
+  sparse\_map} ($\%sp$) for the ground state sector as reported in the listing below:  
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 Consider a generic Fock basis state in the form 
-$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, , and define the 
+$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, and define the 
 ground state as $\ket{\psi} = \sum_I a_I \ket{I}$. 
@@
 matrix is then given by
-$\rho = \ket{\psi}\bra{\psi} = \sum_{IJ} a_I a^*_J \ket{I}\bra{J}$ 
+$\rho = \sum_{IJ} a_I a^*_J \ket{I}\bra{J}$ ,
 while the iRDM is obtained by tracing over the bath degrees of 
@@
     \langle{b_\up\, b_\dw}|{i_\up\, p_\up\, i_\dw\, p_\dw}\rangle
-    \langle{q_\dw \,  j_\dw \, q_\up\, j_\up }|{b_\dw\, b_\up}\rangle\, .
+    \langle{q_\dw \,  j_\dw \, q_\up\, j_\up }|{b_\dw\, b_\up}\rangle\, ,
   \end{aligned}
@@
 $$
-\ket{i_\up\, p_\up\, i_\dw\, p_\dw} \rightarrow C_{p_\up,i_\dw} \ket{i_\up\, i_\dw \,p_\up\,p_\dw}
+\ket{i_\up\, p_\up\, i_\dw\, p_\dw} \rightarrow C_{p_\up,i_\dw} \ket{i_\up\, i_\dw \,p_\up\,p_\dw},
 $$
@@
     \rho^\mathrm{imp}_{i_\up i_\dw j_\dw j_\up}}
-    \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up}
+    \ket{i_\up\, i_\dw}\bra{j_\dw \, j_\up},
   \end{equation}
@@
           j = binary_search(sectorI%H(1)%map,jj)
-          !Build the signs of each components of RDM(io,jo)
+          !Build the signs of each component of RDM(io,jo)
           nBup  = popcnt(Ibits(ii,Norb,Norb*Nbath))
@@
 integrated optimization routine based on the conjugate gradient (CG) 
-minimization of the cost function:
+minimization of the cost function
 \begin{equation}
@@
 \item \texttt{cg\_stop=0,1,2} - Defines the exit condition of the 
-minimization corresponding, respectively, to the options  $C_1+C_2$, $C_1$ and $C_2$, with:
+minimization corresponding, respectively, to the options  $C_1\land C_2$, $C_1$ and $C_2$, with
 \begin{align*}
-C_1 & = |\chi^{n-1} - \chi^n| < \mathtt{cg\_Ftol} (1+\chi^n), \\
-C_2 & = \left\|x_{n-1} - x_n\right\| < 
+C_1 & : |\chi^{n-1} - \chi^n| < \mathtt{cg\_Ftol} (1+\chi^n), \\
+C_2 & : \left\|x_{n-1} - x_n\right\| < 
 \mathtt{cg\_Ftol} (1+\left\|x_n\right\|),
@@
 logical OR between these criteria, with the parameter value selecting 
-which condition to apply.
+which condition to apply. Is the actual stop condition the logical or between $C_1$ and $C_2$? What is meant here?
 \end{itemize}
@@
 The second example is \texttt{ed\_get\_sigma}, which retrieves the 
-normal or anomalous components of the Matsubara or real-axis 
+normal or anomalous components of the Matsubara or real-frequency 
 self-energy function $\Sigma(z)$. This function represents a central 
@@
 
-Given that \NAME allows only a single instance of the solver at a 
+Given that \NAME allows for only a single instance of the solver at a 
 time, a dedicated extension is required to handle these more complex 
@@
 algorithms of \NAME, including initialization, diagonalization, and 
-finalization, while preserving the original function names for consistency:
+finalization, while preserving the original function names for consistency.
 
@@
 
-Additionally, the {\tt E2I\_BATH\_FIT} module extends the generic 
-{\tt ed\_chi2\_fitgf} function to support simultaneous, independent 
+Additionally, the module {\tt E2I\_BATH\_FIT} extends the generic 
+function {\tt ed\_chi2\_fitgf} to support simultaneous, independent 
 bath optimization for all impurities using MPI, thereby improving the 

### 2025-05-30 04_cbinding.tex

@@
 The recent growing availability of state-of-the-art software dedicated
-to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}
+to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}Unfinished list of references
 poses a serious challenge to test accuracy and reliability of the
 results.
-As such, complex softwares are requested to develop a higher level of
-interoperability, i.e. the possibility to operate with other software
-possibly using different programming language.
+As such, complex software packages are expected to develop a higher level of interoperability, i.e. the capability to operate with other software, possibly written in different programming languages.
 Modern Fortran, which is the language of choice for \NAME, since many
@@
 constants, types and procedures for C interoperability.
-Alongside, a second key feature essential to expose to C any Fortran
-entity is the {\tt BIND(C)} intrinsic function.
+Alongside, a second key feature essential to expose any Fortran entity to C is the {\tt BIND(C)} intrinsic function.
 In \NAME we exploit these features of the language to provide a
-complete interface from the Fortran code to C/C++, i.e. {\tt
+complete interface from the Fortran code to C/C++ named {\tt
   EDIPACK\_C}.
@@
 \subsubsection{Installation and inclusion}\label{sSecInteropCbindingsInstallation}
-The C-binding module in included in the build process of \NAME and
+The C-binding module is included in the build process of \NAME and
 compiled into a dynamical library {\tt
   libedipack\_cbindings.so (.dylib)}. As discussed in the
-\secu{sSecInstallBuildInstall}, the support for inequivalent
+\secu{sSecInstallBuildInstall}, support for inequivalent
 impurities is configured at the build level and propagates to the
 C-bindings library as well. An exported variable {\tt has\_ineq} is
-defined and export to C/C++ as a way to query the presence of
-inequivalent impurities support. 
+defined and exported to C/C++ as a way to query the presence of support for the inequivalent impurities. 
 The generated library and header files get installed in the include
@@
   LD\_LIBRARY\_PATH}, valid of any Unix/Linux system, via any of the
-loading methods outlines in \secu{sSecInstallOSloading}.
+loading methods outlined in \secu{sSecInstallOSloading}.
 
@@
 functions and variables are declared with C linkage, which prevents name mangling.
-Function overloading is also not supported, hence all interfaced Fortran functions, for example supporting multiple input variables combinations with different types and ranks, are here represented by multiple alternative functions.
+Function overloading is also not supported, hence all interfaced Fortran functions, for example supporting multiple input variable combinations with different types and ranks, are here represented by multiple alternative functions.
 As an example, the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters, is callable in C++ in the following variants:
@@
 \end{itemize}
-and analogous functions for the inequivalent impurities case, i.e. EDIpack2Ineq. All functions are thorougly listed and documented in the online manual.
+and analogous functions for the inequivalent impurities case, i.e. EDIpack2Ineq. All functions are listed and thorougly documented in the online manual.
 When using \NAME functions in a C/C++ program, care must be taken in the way arrays are passed.
@@
 An array of integers containing the dimensions of the former need to be passed as well to allow for proper Fortran input parsing.
-A working C++ example is provided in the {\tt examples} folder of the \NAME repository and discussed in Section \ref{SecExamples}.
+A working C++ example is provided in the {\tt examples} directory of the \NAME repository and is discussed in Section \ref{SecExamples}.
 
@@
 The interface layer is contained in the Fortran module {\tt
-  EDIPACK\_C}. This contains a common part and two set of functions,
+  EDIPACK\_C}. It contains a common part and two set of functions,
 one to interface the procedures from \NAME and a second
@@
 \paragraph{{\bf Variables}.}
-A number of relevant input and shared variables which are normally
-required to setup or to control the calculation are interfaced to C
-directly in the \NAME modules {\tt ED\_INPUT\_VARIABLES} using {\tt
+A number of relevant input and shared variables, which are normally
+required to setup or to control the calculation, are interfaced to C
+directly in the \NAME modules {\tt ED\_INPUT\_VARIABLES} using the {\tt
   bind(C)} constructs. These are implicitly loaded into the C-binding module {\tt
@@
 procedures dealing with bath initialization, symmetry operations and
-optimization. In particular it contains the function returning the
-dimension of the bath array on the user side {\tt
-  get\_bath\_dimension} as well as the setup of the matrix basis
+optimization. In particular it contains the function {\tt
+  get\_bath\_dimension} returning the
+dimension of the bath array on the user side as well as the setup of the matrix basis
 $\vec{\Gamma}$ for the replica (general) bath via different instances of
@@
 cover all the cases supported in \NAME, conveniently called {\tt
-  chi2\_fitgf\_\{single,lattice\}\_\{normal,superc\}\_n\{3,4,5,6\}} . Note that, because the actual
+  chi2\_fitgf\_\{single,lattice\}\_\{normal,superc\}\_n\{3,4,5,6\}}. Note that, because the actual
 optimization is still performed through the Fortran code, no changes
@@
 \paragraph{{\bf Input/Output}.}
-The input and output part of the software is interfaced in this group
+The input and output parts of the software are interfaced in this group
 of functions. In particular, {\tt read\_input} exposes to C the input
-reading procedure of \NAME which set all the internal
+reading procedure of \NAME, which sets all the internal
 variables of \NAME.
@@
 complete Python interface called EDIpack2py. This is a Python module which
-enables access to all the library features and unlock implementation of
-further interfaces of \NAME as a plug-in solver for external Python
-based software. Detailed documentation can be found online at \href{https://edipack.github.io/EDIpack2py}
+enables access to all the library features and unlocks implementation of
+further interfaces of \NAME as a plug-in solver for external Python-based software. Detailed documentation can be found online at \href{https://edipack.github.io/EDIpack2py}
 {edipack.github.io/EDIpack2py}.
@@
 \paragraph{Anaconda.}
-As for \NAME, the Python API in EDIpack2py is available as an
-Anaconda package for GNU/Linux and Mac Os systems. Packages are available for
-Python version $>3.10$. The \NAME package contains the {\tt
+Similarly to \NAME, the Python API in EDIpack2py is available as an
+Anaconda package for GNU/Linux and macOS systems. Packages are available for
+Python version 3.10 and newer. The \NAME package contains the {\tt
   EDIpack2py} Python module as well as \NAME and SciFortran
@@
   (determined during the \NAME build configuration) by exporting an
-  environment variable called {\tt EDIPACK\_PATH} .
-\item By default, the Python module detects the position of the
-  Fortran libraries via {\tt pkg-config}. Any of the loading method
+  environment variable called {\tt EDIPACK\_PATH}.
+\item By default, the Python module detects the location of the
+  Fortran libraries via {\tt pkg-config}. Any of the loading methods
   outlined in \secu{sSecInstallOSloading} automatically pushes the
-  correct configuration to the {\tt PKG\_CONFIG\_PATH}. 
-\item As a last resort the environment variables {\tt
+  correct configuration to {\tt PKG\_CONFIG\_PATH}. 
+\item As a last resort, the environment variables {\tt
     LD\_LIBRARY\_PATH} and {\tt DYLD\_LIBRARY\_PATH} are analyzed to
-  retrieve the correct position. 
+  retrieve the correct location. 
 \end{enumerate}
-If none of the previous attempts succeeds, the module will not not load correctly and an error message will be printed.
+If none of the previous attempts succeeds, the module will not load correctly and an error message will be printed.
 
@@
 The {\tt global\_env} class needs to be imported at the beginning
-of the python script, along with other useful modules. Numpy is
+of the Python script, along with other useful modules. Numpy is
 necessary, while mpi4py is strongly recommended.
@@
 library, if present. Should the inequivalent impurities package not be
-built, the Python module silently disable the support to it, so that
+built, the Python module silently disables the support to it, so that
 invoking any related procedure  will result in a {\tt RuntimeError}.
@@
 
-The implementation of the Python API is divided in two main parts. The
+The implementation of the Python API is divided into two main parts. The
 first is a set of global variables, the second includes 4 groups of
@@
     solution, sets the effective bath either reading it from a file or
-    initializing it from flat band model. Once this function is
+    initializing it from a flat band model. Once this function is
     called, it is not possible to allocate a second instance of the solver.
@@
     non-interacting part of the impurity Hamiltonian $h^0_{\a\b\s\s'}$. 
-    Either function take different argument combinations there
+    Either function takes different argument combinations there
     including support for inequivalent impurities.
@@
   \item {\tt finalize\_solver} This function cleans up the \NAME
-    environment, free the memory deallocating all relevant arrays or
-    data structure. A call to this functions enables a new
+    environment, frees the memory deallocating all relevant arrays and
+    data structures. A call to this functions enables a new
     initialization of the solver, i.e. a new call to {\tt
@@
 \begin{itemize}
-\item {\tt bath\_inspect}This function translates between the
+\item {\tt bath\_inspect} This function translates between the
   user-accessible continuous bath array and the bath components
-  (energy level, hybridization and so on). It functions in both ways,
+  (energy levels, hybridization and so on). It functions in both ways,
   given the array returns the components and vice-versa. It
@@
 \item {\tt chi2\_fitgf}
-  This function fits the Weiss field or Hybridization function (delta)
-  with a discrete set of level. The fit parameters are the bath
+  This function fits the Weiss field or hybridization function ($\Delta$)
+  with a discrete set of levels. The fit parameters are the bath
   parameters contained in the user-accessible array. Depending on the
   type of system we are considering (normal, superconductive,
-  non-SU(2)) a different set of inputs has to be passed. The specifics
+  non-SU(2) symmteric) a different set of inputs has to be passed. The specifics
   of the numerical fitting routines are controlled in the input file.
@@
 dimension for the user bath array to be allocated and {\tt
-  set\_H{replica/general}} which set the matrix basis
-$\vec{\Gamma}$ and init the bath variational parameters
+  set\_H{replica/general}}, which sets the matrix basis
+$\vec{\Gamma}$ and initializes the bath variational parameters
 $\vec{\lambda}$ for {\tt bath\_type=replica,general}.
@@
 \paragraph{{\bf Input/Output functions}.}
-This group includes functions which return to the userspace
+This group includes functions that return to the userspace
 observables or dynamical correlation functions evaluated in \NAME and
-conserved in the corresponding memory instance. Each function
-provides a general interface which encompass all dimension of the
-input array there including inequivalent impurities support.
-For instance, the function {\tt get\_sigma} returns the self-energy
+stored in the corresponding memory instance. Each function
+provides a general interface, which encompasses all dimension of the
+input array there including inequivalent impurities support. Not sure what is meant here
+For example, the function {\tt get\_sigma} returns the self-energy
 function array (evaluated on-the-fly) for a specified supported shape,
@@
 \paragraph{{\bf Auxiliary functions}.}
-This group include some auxiliary functions, either interfacing \NAME
+This group includes some auxiliary functions, either interfacing \NAME
 procedures or defined locally in Python to provide specific new
-functionalities. Among the latter we include {\tt get\_ed\_mode} which return an integer index depending onthe value of the variable {\tt ed\_mode=normal,superc,nosu2}
-and {\tt get\_bath\_type} which works similarly for {\tt bath\_type}.
+functionalities. Among the latter we include {\tt get\_ed\_mode}, which returns an integer index depending on the value of the variable {\tt ed\_mode=normal,superc,nosu2},
+and {\tt get\_bath\_type}, which works similarly for {\tt bath\_type}.
 
@@
 
-\subsection{EDIpack2Triqs: the TRIQS interface}\label{sSecInteropTRIQS}
+\subsection{EDIpack2TRIQS: the TRIQS interface}\label{sSecInteropTRIQS}
 A thin compatibility layer between \NAME and the Toolbox for Research on
-Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called EDIpack2Triqs
+Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called EDIpack2TRIQS
 is available as a stand-alone project. This is a pure Python package
@@
 limited object-oriented interface to the most important features of \NAME.
-EDIpack2Triqs strives to offer seamless interoperability with program tools
+EDIpack2TRIQS strives to offer seamless interoperability with program tools
 based on TRIQS by adopting data types, conventions and usage patterns
@@
 and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
-installed in the OS, the current development version of EDIpack2triqs can be 
+installed in the OS, the current development version of EDIpack2TRIQS can be 
 installed with {\tt pip} from its 
@@
 The following commands will create a new {\tt conda} environment named 
-`edipack' and install the most recently released version of EDIpack2triqs along 
+`edipack' and install the most recently released version of EDIpack2TRIQS along 
 with its dependencies (\NAME, EDIpack2py and the TRIQS libraries).
@@
 \subsubsection{Implementation}\label{sSecInteropTRIQSImplementation}
-The programming interface of EDIpack2triqs is built around the  
+The programming interface of EDIpack2TRIQS is built around the  
 singleton Python class {\tt EDIpackSolver}, defined in the module
@@
 Each of the sets contains pairs of labels {\tt (b,j)} carried
-by the operators $c^\dagger_{b,i} / c_{b,i}$ corresponding to either impurity
+by the operators $c^\dagger_{b,j} / c_{b,j}$ corresponding to either impurity
 or bath electronic degrees of freedom with a certain spin projection.
@@
 {\tt bath\_type} (see \secu{sSecBath}). In addition, the
-constructor accepts a vast array of keyword arguments that allow for fine-tuning
+constructor accepts a vast array of keyword arguments that allow for fine-tuning of
 the diagonalization process. Among others, these include the ED algorithm
@@
 
-A second set of input variables, including phyisical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the W2Dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
+A second set of input variables, including physical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the W2Dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
 An example of a properly formatted input file is provided in \secu{SecExamples}.
@@
 
-Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard the CT-HYB code.
+Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard CT-HYB code.
 For example, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format.
@@
 Python implementations for the Bethe lattice example driver.
-Its structure and operation mimicks that of the EDIpack2py layer, with minimal language-specific differences.
+Its structure and operation mimic that of the EDIpack2py layer, with minimal language-specific differences.
 
@@
 \item {\tt LD\_LIBRARY\_PATH}: for Linux systems
-\item {\tt DYLD\_LIBRARY\_PATH}: for Mac systems
+\item {\tt DYLD\_LIBRARY\_PATH}: for macOS systems
 \end{itemize}
@@
 
-Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multithreading.
 At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.

### 2025-05-30 05_examples.tex

@@
 \section{Examples}\label{SecExamples}
-In this section we illustrate the functioning of the \NAME
-library and their interfaces as solver for DMFT through a variety of examples, including
-discussion of relevant code snippets. As some tasks are inherently agnostic on the impurity
-solver (and the impurity solver is agnostic about them), the user is expected to implement
-them, or interface to existing utilities. For instance, all the Fortran subroutines with 
-naming convention \texttt{dmft\_do\_something()} refer to implementations that can be found
-in the {DMFTtools} package\footnote{\url{https://github.com/aamaricci/DMFTtools}},
-the example based on w2dynamics relies on the internal facilities provided by the \texttt{DMFT.py} script \cite{Wallerberger2019CPC} and the TRIQS library provides an 
-extensive toolbox for the manipulation of Green's functions and related quantities
-\cite{Parcollet2015CPC}.
+In this section we illustrate and benchmark the functionalities and of the \NAME
+library and its interfaces as solver for DMFT through a variety of examples. We also discuss in detailed the relevant code snippets from different programming languages. 
+Some tasks --particularly those associated to the implementation of the DMFT self-consistency--  are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
+In the implementation using Fortran, Python or other \NAME API we adopt a reverse communication strategy, which requires the user to independently implement these parts or, equivalently, to exploit existing utilities.
+In our examples based on the Fortran APIs  we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors) to perform specific tasks, including the evaluation of the local Green's function, the implementation of the self-consistency, the construction of the tight-binding model or the calculation of the kinetic energy.
+Where appropriate, we include comments that reference these external procedures.
+On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself—see the \texttt{DMFT.py} script~\cite{Wallerberger2019CPC}—which handles all these tasks seamlessly.
+Similarly, the TRIQS library offers an extensive toolbox for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
 
@@
    allocate(Ebands(Le),Dbands(Le))
+   !From SciFortran:
    Ebands = linspace(-D,D,Le,mesh=de)
@@
 vector<double> Ebands, Dbands;
+//Locally defined functions:
 Ebands = linspace(-D,D,Le);
@@
 \item[{\tiny {\it User}}] Evaluate the local interacting Green's function
-  $G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e$ with
-  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
+$$
+G_\mathrm{loc}(i\omega) = \int_{-D}^D \frac{\rho(\e)}{\zeta -\e}d\e
+$$ 
+with  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
 
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.45\linewidth}
+  \begin{minipage}{0.46\linewidth}
     \center
@@
     iloop=iloop+1     
-    ! Call ED Solver
+    !Call ED Solver
     call ed_solve(bath)     
-    ! Retrieve Self-energy on Matsubara axis
+    !Retrieve $\Sigma(i\omega_n)$
     call ed_get_sigma(Smats,'m')
-    ! Build local Green's function
+    !Build local Green's function
     wfreq = pi/beta*(2*arange(1,Lmats)-1)
@@
     enddo
-    ! Self-consistency
+    !Self-consistency
     Delta = D/4d0*Gmats
-    ! Fitting -> new bath
+    !Fitting -> new bath
     call ed_chi2_fitgf(Weiss,bath,ispin=1)     
-    ! Check convergence
+    !Check convergence: from $\mathrm{DMFTtools}$
     converged=check_convergence(Delta,&
@@
 \setbox0=\hbox{%
-  \begin{minipage}{0.52\linewidth}
+  \begin{minipage}{0.51\linewidth}
     \center
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-  // DMFT loop
+//DMFT loop
 while (iloop < Nloop && !converged) {
-    //  Call ED Solver
+  //Call ED Solver
   solve_site(Bath.data(),bath_dim,1,1);      
-    // Retrieve  Self-energy on Matsubara axis
+  //Retrieve $\Sigma(i\omega_n)$
   get_sigma_site_n5(Smats.data(),//
       0,0,wm.data(),Lmats,0);
-    //  Build a local Green's function:
+  //Build a local Green's function:
   for (int i=0;i<Lmats;++i) {
@@
   }
-    // Self-consistency
+  //Self-consistency
   for (int i = 0; i < Lmats; ++i) {
@@
   }
-    // Fit -> new bath
+  //Fit -> new bath
   chi2_fitgf_single_normal_n5(Delta.data(),//
       delta_dim,Bath.data(),bath_dim,1,0,1);
-    // Check convergence
+  //Check convergence: local functions
   converged = check_convergence(Delta,//
@@
 symmetry. 
-
+%
 In the following we consider the case of $M=1$ which corresponds to a
@@
      call ed_get_sigma(Smats,axis='mats')
-     !> Get $G_\mathrm{loc}$ (assume to have a function for this task)
+     !> Get $G_\mathrm{loc}$ using $\color{comment-color}\mathrm{DMFTtools}$
      call get_gloc(Hk,Gmats,Smats,axis='m')
-     !> Update the Weiss field $\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma$ +  Linear mixing.
+     !> Update the Weiss field ${\color{comment-color}\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma}$ +  Linear mixing: using $\color{comment-color}\mathrm{DMFTtools}$
      call dmft_self_consistency(Gmats,Smats,Weiss)
@@
      call ed_chi2_fitgf(Weiss,bath,ispin=1)
-     !Check convergence (using DMFT_TOOLS)
+     !Check convergence: using $\color{comment-color}\mathrm{DMFTtools}$
      converged = check_convergence(Weiss(1,1,:),dmft_error,nsuccess,nloop)
@@
 eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
-\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRBa,Rachel2010PRB} and
+\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and there were two references to the same paper
 later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
@@
         call ed_solve(Bath(1,:))
-        call ed_get_sigma_matsubara(Smats(1,:,:,:,:,:))
+        call ed_get_sigma(Smats(1,:,:,:,:,:),axis='m')
         select case(ansatz)
@@
       else
-         !> solve both sublattices independently with the RDMFT wrapper:
+         !> solve both sublattices independently using EDIpack2ineq:
          !  mpi_lanc=T => MPI lanczos, mpi_lanc=F => MPI for ineq sites
@@
          !> retrieve all self-energies:
-         call ed_get_sigma_matsubara(Smats,Nineq)
+         call ed_get_sigma(Smats,Nineq,axis='m')
          !
@@
       !
-      !> Compute the local Green's function
+      !> Get ${\color{comment-color}G_{loc}(i\omega_n) }$ : using ${\color{comment-color}\mathrm{DMFTtools}}$
       call dmft_gloc_matsubara(Hk,Gmats,Smats)
       !
-      !> Compute the two inequivalent Weiss fields
+      !> Update local Weiss fields ${\color{comment-color}\GG^{-1}_0 = G_{loc} + \Sigma}$ :using ${\color{comment-color}\mathrm{DMFTtools}}$
       call dmft_self_consistency(Gmats,Smats,Weiss)
       !
-      !> Fit the new bath
-      !  this behaves differently depending on the ed_mode input:
-      !  - for the normal mode: normal/AFMz phase is solved, so we 
-      !    can fit spin1 and spin2 components independently
-      !  - for the nonsu2 mode: Sz-conservation can be broken, so a 
-      !    unique fit for both spin components is needed
+      !> Fit the new bath:
+      !  - normal mode: normal/AFMz and we fit spin-components independently
+      !  - nonsu2 mode: broken Sz-conservation and we fit both spin components altogether
       select case(ed_mode)
@@
       !
-      !> linear mixing (aids convergence near transition points)
+      !> linear mixing and check convergence: using ${\color{comment-color}\mathrm{DMFTtools}}$
       if(iloop>1) Bath = wmixing*Bath + (1.d0-wmixing)*Bath_prev
       Bath_prev = Bath
-      !
-      !> check convergence
       converged = check_convergence(Weiss(:,1,1,1,1,:),dmft_error,nsuccess,nloop)
@@
    !
-   !> Compute Kinetic Energy
+   !> Compute Kinetic Energy: using ${\color{comment-color}\mathrm{DMFTtools}}$
    call dmft_kinetic_energy(Hk,Smats)

### 2025-05-30 05_examples.tex
Version 15h15 EST. Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 In this section we illustrate and benchmark the functionalities and of the \NAME
-library and its interfaces as solver for DMFT through a variety of examples. We also discuss in detailed the relevant code snippets from different programming languages. 
-Some tasks --particularly those associated to the implementation of the DMFT self-consistency--  are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
+library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code snippets from different programming languages. 
+Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
 In the implementation using Fortran, Python or other \NAME API we adopt a reverse communication strategy, which requires the user to independently implement these parts or, equivalently, to exploit existing utilities.
@@
 Where appropriate, we include comments that reference these external procedures.
-On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself—see the \texttt{DMFT.py} script~\cite{Wallerberger2019CPC}—which handles all these tasks seamlessly.
+On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which handles all these tasks seamlessly.
 Similarly, the TRIQS library offers an extensive toolbox for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
@@
 H = -t \sum_{\langle ij\rangle,\s} c^\dagger_{i\s} c_{j\s} + 
-    U \sum_i n_{i\up}n_{i\dw}
-    $$
-
+    U \sum_i n_{i\up}n_{i\dw},
+$$
 where $c^\dagger_{i\s}$ ($c_{i\s}$) are the creation (annihilation) 
@@
 The system is defined on a Bethe lattice with density of states
-$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$,
+$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$ This density of states does not normalize to 1,
 where $D=2t$ is the half-bandwidth.
-In DMFT this lattice model is mapped onto a quantum impurity problem with 
+In DMFT, this lattice model is mapped onto a quantum impurity problem with
 an effective electronic bath that must be determined
@@
 allocation, Bethe lattice creation, and solver initialization.
+'Bethe lattice creation' sounds a bit weird here.
+DMFT does not directly work with a lattice as a collection of sites, it only deals with the spectral functions.
 
@@
 using namespace std;
-!...
+//...
 //Main variables
@@
 int total_size_n5 = total_size * Lmats;    
-// Solver-specific arrays
+//Solver-specific arrays
 vector<complex<double>> Hloc(total_size);
@@
 vector<complex<double>> Delta(total_size_n5);
-...
-// Initialize Bethe arrays
+//...
+//Initialize Bethe arrays
 vector<double> Ebands, Dbands;
@@
 
-The bath is described by the (unknown) function $\GG^{-1}_0$, known as 
+The bath is described by the (unknown) function $\GG^{-1}_0$, called
 the Weiss field ({\tt Weiss}). In the ED approach implemented in \NAME, 
@@
   relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
-    \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
-    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$.
+    \Sigma(i\omega)$ $G_\mathrm{loc}$ inverted?. For the Bethe lattice, this simplifies to
+    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$ Missing square in the coefficient?.
 
@@
       0,0,wm.data(),Lmats,0);
-  //Build a local Green's function:
+  //Build a local Green's function
   for (int i=0;i<Lmats;++i) {
@@
     \caption{\label{figEx1}%
-      \textbf{The Metal-Insulator Mott transition.}
+      \textbf{The Metal-insulator Mott transition.}
       (a) Evolution of the spectral function $-\Im{G}(\omega)/\pi$ as
@@
       real-axis one $\Re\Sigma(\omega)$ across the Mott
-      transition. For a particle-hole symmetric case both allow to
+      transition. For a particle-hole symmetric case, both allow to
       estimate the renormalization constant $Z$ (see main text), using
@@
       values of $Z$ are reported in the legend.
-      The Mott insulating solution is associated to a singularity at
+      The Mott insulating solution is associated with a singularity at
       $\omega=0$ of $\Im\Sigma$.
@@
 Z=\left(1-\frac{\partial\Re\Sigma}{\partial\omega}\Biggr|_{\omega\rightarrow
-    0}\right)^{-1}.
+    0}\right)^{-1},
 $$
@@
 \subsubsection{Finite temperature solution (w2dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTw2d}
+Capitalization in 'w2dynamics' is different compared to Sec. 4.
 To demonstrate the usage of the w2dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
-In order to showcase the capabilities of \NAME to address low-temperature problems we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in w2dynamics against the \NAME solver at finite temperature.
+In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in w2dynamics against the \NAME solver at finite temperature.
 
@@
 CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
-    % \fixme{Are we sure we want to use these
-    % fancy markers?
-As I saw the earlier version, I know what they are doing and I understand that all data coincide perfectly and how this can make for a fancy plot.
-But I suspect that looking at it without any prior knowledge, at a glance, I would just desume that the w2d and edipack calculations are not matching.
-I would probably just go with the usual "x", "." and "+" markers, that all together make for a fancy multicolor "*".
-The dot in front of everything, with the most fluo color (e.g.
-bright green).
-The "x" and "+" in complementary colors, like blue and red, not in fluo version, so that they do not "hide" the dot.
-Something like that.}
-    % NOW I LOVE IT :)
         }
@@
 eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
-\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and there were two references to the same paper
+\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and 
 later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 

### 2025-05-30 edipack2_examples/edipack2triqs/hubbard_kanamori.py
Minor fixes in hubbard_kanamori.py

@@ -28,7 +28,7 @@ fops_bath_dn = [('B_dn', i) for i in range(3 * 2)]
 # Non-interacting part of the impurity Hamiltonian
 h_loc = np.diag([-0.7, -0.5, -0.7])
 H = sum(h_loc[o1, o2] * c_dag(spin, o1) * c(spin, o2)
-for spin, o1, o2 in product(spins, orbs, orbs))
+        for spin, o1, o2 in product(spins, orbs, orbs))
 
 # Interaction part
 U = 3.0     # Local intra-orbital interactions U
@@ -85,8 +85,8 @@ solver.solve(beta=beta,
 # On master MPI node, output some calculation results
 if MPI.COMM_WORLD.Get_rank() == 0:
     # Print values of the static observables
-    print("Potential energy", solver.e_pot)
-    print("Kinetic energy", solver.e_kin)
+    print("Potential energy:", solver.e_pot)
+    print("Kinetic energy:", solver.e_kin)
     print("Densities (per orbital):", solver.densities)
     print("Double occupancy (per orbital):", solver.double_occ)
 
@@ -96,7 +96,8 @@ if MPI.COMM_WORLD.Get_rank() == 0:
     # Plot the Matsubara Green's functions (imaginary part)
     plt.figure(figsize=(4, 4))
     for orb in orbs:
-        oplot(solver.g_iw['up'][orb, orb], mode='I', label=f"${\\rm Im} G_%i(i\\omega_n)$" % orb)
+        oplot(solver.g_iw['up'][orb, orb], mode='I',
+              label=r"${\rm Im} G_" + str(orb) + r"(i\omega_n)$")
     plt.xlim((-3, 3))
     plt.ylabel(r"${\rm Im} G(i\omega_n)$")
     plt.legend()

### 2025-05-30 01_intro.tex
Updates from Overleaf

@@
 \begin{document}
+
+\fixme{AA: this needs a further edit + all bibliography. I also need to add a paragraph to comments relation with other ED codes and cite them all.}
 
@@
 The library builds on the foundations of
-its predecessor~\cite{Amaricci2022}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
+its predecessor~\cite{amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
 The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.
@@
 In this paper, we present the mathematical framework, implementation
-details, and key features of \NAME \textcolor{red}{2.0 i get that we want to say this is the updated edipack, but now it is version 5.0.5...
-i believe this could create confusion}, along with several illustrative
+details, and key features of \NAME, along with several illustrative
 applications. We aim to demonstrate how this flexible,

### 2025-05-30 02_install.tex
Updates from Overleaf

@@
 \begin{document}
+\fixme{AA: reviewed. Misses possible References}
 
@@
 The software builds into two distinct libraries.
-The main one is a static Fortran library called {\tt libedipack.a} which, alongside the compiled
-modules, wraps the \NAME software in both its single- and multi-impurity variants.
+The main one is a static Fortran library named {\tt libedipack.a} which, alongside the compiled
+modules, wraps the \NAME software.
 A second dynamic library, {\tt libedipack\_cbindings.so}, together with the associated header
@@
 \subsection{Structure}\label{sSecInstallStructure}
-\NAME is a modular library organized into three main components. At its 
+\NAME is a modular library organized into two main components. At its 
 core, constituting the primary computational engine, 
-is the exact diagonalization solver for the quantum single-impurity Hamiltonian.
+is the  Exact Diagonalization solver for the quantum single-impurity Hamiltonian.
 Building on this, the library includes 
-{\tt EDIpack2ineq}, an extension for handling multiple inequivalent 
-impurity problems. Finally, the Fortran-C/C++ interface is provided for 
-seamless integration with external software and the development of 
-additional APIs.
+\NAME{2ineq}, an extension for handling multiple inequivalent impurity problems at once. Finally, a Fortran-C/C++ interface is provided for 
+seamless integration with external software and the development of additional APIs.
 
@@
   provided in \secu{SecEDIpack}.
-
-\item{\bf EDIpack2ineq.}
+  \begin{itemize}
+    \item[$\hookrightarrow$]
+    {\it EDIpack2ineq.}
   This extension, developed using suitable Fortran interfaces,
@@
 problems, as discussed in \secu{sSecIneq}.
+\end{itemize}
 
@@
 \NAME directly depends on two external libraries.
-\begin{itemize}
+\begin{enumerate}
 \item {\bf SciFortran}: an open-source Fortran library that provides support
-for mathematical and scientific software development.
-\item {\bf MPI} (optional): a distributed memory parallel communication layer with support for modern Fortran compiler.
-\end{itemize}
+for mathematical and scientific software development, available at \href{https://github.com/SciFortran/SciFortran}{github.com/SciFortran}.
+\item {\bf MPI}: a distributed memory parallel communication layer with support for modern Fortran compiler.
+\end{enumerate}
 
-SciFortran provides a solid development platform enabling access to
+{\bf SciFortran} provides a solid development platform enabling access to
 many algorithms and functions, including standard linear algebra
@@
 greatly reduces code clutter and development time.
-The use of distributed memory parallel environment, although optional,
+The use of distributed memory parallel environment 
 is required to access scalable parallel diagonalization algorithms,
-which speed up calculations for large systems.
+which speed up calculations for large systems. Nonetheless, through careful design \NAME operates serially even without initialization of the MPI framework.
 
@@
 \subsubsection{Compilation from source}
-The software can be installed from source as follows. The source code can
+The software can be installed from source as follows. The code package can
 be retrieved directly from its GitHub repository, for instance using
@@
 \end{lstlisting}
-Then, assuming being in the software source directory, a conventional
-out-of-source building can be performed using two alternative compilation backends.
+Then, assuming being in the software root directory ({\tt \$cd EDIpack}), a conventional out-of-source building can be performed using two alternative compilation backends.
 
@@
 \end{center}
-
+%
 The default target builds and installs both the main library and the C-bindings.
-Separate build targets for either are available. A recap message is printed at the end of the
-CMake configuration step.
+Separate build targets for either components are available.
+A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.
 
@@
 environment containing Python ($\geq3.10$).
-
+%
 The Conda package installation procedure for a virtual environment called {\tt myenv} reads
@@
 \end{lstlisting}
-\noindent
-which installs a bundle of SciFortran and \NAME libraries together with
+and installs a bundle of SciFortran and \NAME libraries together with
 specific {\tt pkg-config} configuration files, which can be used to

### 2025-05-30 03_edipack2.tex
Updates from Overleaf

@@
 \end{equation}
-and represents the quadratic part, with $d_{\a\sigma}$ ($d^\dagger_{\a\sigma}$) being the annihilation (creation)
+and represents the non-interacting part, with $d_{\a\sigma}$ ($d^\dagger_{\a\sigma}$) being the annihilation (creation)
 operators for impurity electrons in 
-orbital $\alpha=1,\dots,N_\a$, with the number of orbitals $N_\a$,
+orbital $\alpha=1,\dots,N_\a$, where $N_\a$ is the number of orbitals,
 and spin $\sigma=\up,\dw$.
-The internal structure of the non-interacting part is captured by the 
+The internal structure of this quadratic part is captured by the 
 matrix $h^{0}_{\a\b\sigma\sigma'}$, which can include 
 orbital-dependent on-site energies or amplitudes, spin-orbit coupling or other single-particle terms.
+In \NAME the matrix $\hat{h}_0$ is set by the user passing an complex array through the function {\tt ed\_set\_Hloc}.
 
@@
 However, we typically 
-adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013AROCMP}:
+adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ARCMP}:
 \begin{equation}
@@
 interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Georges2013AROCMP}.  
+$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PR,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
 The last two terms are, respectively, the spin-exchange ($J_X$) and
@@
 U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013AROCMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013AROCMP}.
+$J_X=J_P=J$~\cite{Georges2013ARCMP}. Different choices, preserving part
+of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ARCMP}.
 
@@
 $V^p_{\a\b\s\sigma'}$ describes the coupling with the impurity.   
+The bath parametrization is handled in \NAME using reverse communication strategy as will be discussed later in \secu{sSecBath}.
 
@@
 %Indeed, if the expectation value of the bosonic displacement operator $\langle b_q^\dagger + b_q\rangle$ is non-zero, a change of variables from the bosons $b^{(\dagger)}_q$ leads to new effective bosons $\tilde{b}^{(\dagger)}_q = b^{(\dagger)}_q- A_q$ for which the displacement operator has a smaller expectation value (ideally zero if we can impose $A_m = \langle \hat{O}_m\rangle$).
-For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_d = g_1 \sum_{\sigma} d^{\dagger}_{\sigma}d_{\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
-For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_1 - n_2)$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ h.c.)$.
+%
+For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
+For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.
+
 For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}.
@@
 \end{align*}
-where $\#_{a\sigma}=\sum_{b\sigma'<a\sigma} n_{b\sigma'}$ accounts for the fermionic sign imposed by the Pauli principle.
+where $\#_{a\sigma}=\sum_{i\sigma'<a\sigma} n_{i\sigma'}$ accounts for the fermionic sign imposed by the Pauli principle.
 The bosonic operators $b$ and $b^\dagger$ act on the phonon part $\ket{p}$ of the Fock state as
@@
   b\ket{p} &= \sqrt{p-1}\ket{p}, \\
-  b^\dagger\ket{p} &= \sqrt{p}\ket{p}. \\
+  b^\dagger\ket{p} &= \sqrt{p}\ket{p}.
 \end{align*}
@@
 of the fermionic creation and annihilation operators as functions 
-{\tt CDG} and {\tt C}, used throughout the code. Additionally, 
+{\tt CDG} and {\tt C}, used throughout the code. 
+Additionally, 
 we provide the function {\tt bdecomp} for reconstructing the Fock  state bit sequence from the integer representation.
 
-\begin{lstlisting}[style=fstyle,numbers=none]
-  subroutine C(pos,in,out,fsgn) !$c_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle$
-    integer,intent(in)    :: pos  !Position to be set to 1
-    integer,intent(in)    :: in   !Input index
-    integer,intent(inout) :: out  !Output index
-    real(8),intent(inout) :: fsgn !Fermionic sign   
-    integer               :: l
-    if(.not.btest(in,pos-1))stop "C error: C_i|...0_i...>"
-    fsgn=1d0
-    do l=1,pos-1
-       if(btest(in,l-1))fsgn=-fsgn
-    enddo
-    out = ibclr(in,pos-1)         !Set bit at pos to 0
-  end subroutine C
-\end{lstlisting}
-
-\begin{lstlisting}[style=fstyle,numbers=none]
-  subroutine CDG(pos,in,out,fsgn) !$c^\dagger_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle$
-    integer,intent(in)    :: pos  !Position to be set to 1
-    integer,intent(in)    :: in   !Input index
-    integer,intent(inout) :: out  !Output index
-    real(8),intent(inout) :: fsgn !Fermionic sign   
-    integer               :: l
-    if(btest(in,pos-1))stop "C^+ error: C^+_i|...1_i...>"
-    fsgn=1d0
-    do l=1,pos-1
-       if(btest(in,l-1))fsgn=-fsgn
-    enddo
-    out = ibset(in,pos-1)         !Set bit at pos to 1
-  end subroutine CDG
-\end{lstlisting}
-
-\begin{lstlisting}[style=fstyle,numbers=none]
- !Binary decomposition of the ${\color{comment-color} i\in\NNN}$ with Ntot bits
- function Bdecomp(i,Ntot) result(ivec)
-    integer :: Ntot,ivec(Ntot),l,i
-    logical :: busy
-    do l=0,Ntot-1
-       busy=btest(i,l)
-       ivec(l+1)=0
-       if(busy)ivec(l+1)=1
-    enddo
-  end function Bdecomp
-\end{lstlisting}
+% \begin{lstlisting}[style=fstyle,numbers=none]
+%   subroutine C(pos,in,out,fsgn)   !${\color{comment-color}c_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle}$
+%     integer,intent(in)    :: pos  !Position to be set to 1
+%     integer,intent(in)    :: in   !Input index
+%     integer,intent(inout) :: out  !Output index
+%     real(8),intent(inout) :: fsgn !Fermionic sign   
+%     integer               :: l
+%     if(.not.btest(in,pos-1))stop "C error: C_i|...0_i...>"
+%     fsgn=1d0
+%     do l=1,pos-1
+%        if(btest(in,l-1))fsgn=-fsgn
+%     enddo
+%     out = ibclr(in,pos-1)         !Set bit at pos to 0
+%   end subroutine C
+% \end{lstlisting}
+
+% \begin{lstlisting}[style=fstyle,numbers=none]
+%   subroutine CDG(pos,in,out,fsgn) !${\color{comment-color}c^\dagger_\mathrm{pos}|\mathrm{in}\rangle=|\mathrm{out}\rangle}$
+%     integer,intent(in)    :: pos  !Position to be set to 1
+%     integer,intent(in)    :: in   !Input index
+%     integer,intent(inout) :: out  !Output index
+%     real(8),intent(inout) :: fsgn !Fermionic sign   
+%     integer               :: l
+%     if(btest(in,pos-1))stop "C^+ error: C^+_i|...1_i...>"
+%     fsgn=1d0
+%     do l=1,pos-1
+%        if(btest(in,l-1))fsgn=-fsgn
+%     enddo
+%     out = ibset(in,pos-1)         !Set bit at pos to 1
+%   end subroutine CDG
+% \end{lstlisting}
+% %
+
+% \begin{lstlisting}[style=fstyle,numbers=none]
+%  !Binary decomposition of the ${\color{comment-color} i\in\NNN}$ with Ntot bits
+%  function Bdecomp(i,Ntot) result(ivec)
+%     integer :: Ntot,ivec(Ntot),l,i
+%     logical :: busy
+%     do l=0,Ntot-1
+%        busy=btest(i,l)
+%        ivec(l+1)=0
+%        if(busy)ivec(l+1)=1
+%     enddo
+%   end function Bdecomp
+% \end{lstlisting}
 
@@
 specific case is discussed extensively
-Ref.~\cite{Amaricci2022}, so we will cover it no further here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
+Ref.~\cite{Amaricci2022CPC}, so we will cover it no further here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
 
@@
 $\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the electronic states $\ket{i}$
-within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I_e}$ in the Fock space.
+within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I_e}$ in the electronic Fock space. 
 This map is typically implemented as a rank-1
 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
-The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p 2^{2 N_s}$.
+The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.
 
@@
 $[I_\up,I_\dw]$ as $I_e=I_\up +   I_\dw 2^{N_\mathrm{s}}$.
-For a more detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022}.
+For a more detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022CPC}.
 
@@
 symmetric due to the factorized nature of the sectors as discussed
-above, see also Ref.~\cite{Amaricci2022}.
+above, see also Ref.~\cite{Amaricci2022CPC}.
 The analysis of the spectrum is then reduced to inspecting the
@@
 
-% Although the sectors have dimensions much smaller than the full Fock
-% space, for large systems storing the Hamiltonian matrix in the memory
-% can still be highly inefficient. In such cases, any Krylov  subspace  
 % method~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996}
-% can be implemented using a storage-free algorithm, performing the
-% necessary linear operations on-the-fly.
-% This solution has generally a negative impact on the execution
-% time, however this can be well compensated by scaling in a distributed 
-% parallel framework.
 
@@
 The following code snippets summarize the various available implementations.
-The core idea is to loop over the necessary Fock states through the integers $I_\sigma=1,\dots,2^{N_s}$ and to enforce the quantum number constraint:
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.27\linewidth}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+The core idea is to loop over the Fock states and  enforce the quantum number constraint:
+\begin{center}
+\begin{minipage}[t]{0.32\linewidth}
+\textbf{Normal}
+\begin{lstlisting}[style=fstyle,frame=leftline,numbers=none,basicstyle={\ttfamily\scriptsize}]
 i=0
@@
   i = i+1
-  H(iud+Ns)%map(i) = Idw
+  H(iud+Ns)%map(i)=Idw
 enddo
@@
 \end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.27\linewidth}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+%
+\begin{minipage}[t]{0.32\linewidth}
+\textbf{Superc}
+\begin{lstlisting}[style=fstyle,frame=leftline,numbers=none,basicstyle={\ttfamily\scriptsize}]
 i=0
@@
     sz_  = nup_ - ndw_
-    if(sz_ /= self%Sz)cycle
+    if(sz_ /=self%Sz)cycle
     i=i+1
-    self%H(1)%map(i) = &
+    self%H(1)%map(i)= &
         Iup+Idw*2**N
@@
 enddo
+$\phantom{.}$
+$\phantom{.}$
 \end{lstlisting}
 \end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.3\linewidth}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+%
+\begin{minipage}[t]{0.32\linewidth}
+\textbf{Nonsu2}
+\begin{lstlisting}[style=fstyle,frame=leftline,numbers=none,basicstyle={\ttfamily\scriptsize}]
 i=0
@@
     i=i+1
-    self%H(1)%map(i) = &
+    self%H(1)%map(i)= &
         Iup+Idw*2**Ns
@@
 enddo
+$\phantom{.}$
+$\phantom{.}$
 \end{lstlisting}
 \end{minipage}
-}
-\savestack{\listingC}{\box0}
-
-\vspace{2mm}
-\begin{tabular}{c|c|c}\label{list1}
-    {\bf normal} & {\bf superc} & {\bf nonsu2}\\
-    \hline
-\stackinset{l}{}{t}{}{}{\listingA} &
-\stackinset{l}{}{t}{}{}{\listingB} &
-\stackinset{l}{}{t}{}{}{\listingC} \\
-\end{tabular}
-\vspace{2mm}
+\end{center}
 
@@
 \end{lstlisting}
-where {\tt NORB} is the number of orbitals $N_\a$.\\
+where {\tt NORB} is the number of orbitals $N_\a$.
 Each line defines a two-body second-quantized operator of the form 
@@
 are mutually exclusive, it is allowed to set both to {\tt F}. 
-In any case, the user can specify additional interaction terms in the calling program or script by means of the procedure {\tt add\_twobody\_operator}, before the impurity problem is solved.
+In this case, the user can specify additional interaction terms in the calling program or script by means of the procedure {\tt add\_twobody\_operator}, before the impurity problem is solved.
 The input of this function has the same form of each line of the {\tt UMATRIX} file.
-The list of user-provided interaction terms will be added to those read from file or from the Hubbard-Kanamori coefficients in case the relative flags are {\tt T}.
-To clear the list, the procedure {\tt reset\_umatrix} has to be called.\\
+A list of user-provided interaction terms will be added to those read from file or from the Hubbard-Kanamori coefficients in case the relative flags are {\tt T}.
+To clear the list, the procedure {\tt reset\_umatrix} has to be called.
+
 For reference and future use, when the impurity problem is solved, a list of the interaction operators used in each call to the solver is saved in the output file 
@@
 hash tables. Each key corresponds to a row index, while the associated 
-value contains a pair of dynamic arrays: one for the non-zero (NNZ) matrix 
+value contains a pair of dynamic arrays: one for the non-zero matrix 
 elements and one for their respective column indices. 
-
-\begin{lstlisting}[style=fstyle,numbers=none]
-! sparse row: contains the NNZ elements on any row of the sparse matrix.
-type sparse_row_csr
-   integer                                   :: size  !size of the row = NNZ
-   real(8),dimension(:),allocatable          :: dvals !rank-1 array for double precision
-   complex(8),dimension(:),allocatable       :: cvals !rank-1 array for double complex
-   integer,dimension(:),allocatable          :: cols  !rank-1 array for column indices
-end type sparse_row_csr
-! Sparse Matrix: allocatable array of sparse rows
-type sparse_matrix_csr
-   type(sparse_row_csr),dimension(:),pointer :: row  !array of {\tt sparse\_row\_csr} 
-   integer                                   :: Nrow !total number of rows
-   integer                                   :: Ncol !total number of columns
-   logical                                   :: status=.false. !Allocation status
-#ifdef _MPI
-   type(sparse_row_csr),dimension(:),pointer :: loc      !array for the diagonal blocks
-   integer                                   :: istart=0 !start index MPI range
-   integer                                   :: iend=0   !end index MPI range
-   integer                                   :: ishift=0 !shift index MPI range
-   logical                                   :: mpi=.false.
-#endif
-end type sparse_matrix_csr
-\end{lstlisting}
-
-Each instance of {\tt sparse\_matrix\_csr} can be stored in either 
-a serial manner (one copy per process) or distributed across multiple 
-processes, with rows dynamically assigned to each process. 
+In an MPI framework, elements local in the memory are store in a separate set of row, i.e. {\tt loc} while keeping track of the indices of the global share, {\tt istart, ishift, iend}. 
+Each instance of {\tt sparse\_matrix\_csr} can be stored serially (one copy per process) or distributed across multiple 
+processes with rows dynamically assigned to each process.
+
+% \begin{lstlisting}[style=fstyle,numbers=none]
+% ! sparse row: contains the NNZ elements on any row of the sparse matrix.
+% type sparse_row_csr
+%    integer                                   :: size  !size of the row = NNZ
+%    real(8),dimension(:),allocatable          :: dvals !rank-1 array for double precision
+%    complex(8),dimension(:),allocatable       :: cvals !rank-1 array for double complex
+%    integer,dimension(:),allocatable          :: cols  !rank-1 array for column indices
+% end type sparse_row_csr
+% ! Sparse Matrix: allocatable array of sparse rows
+% type sparse_matrix_csr
+%    type(sparse_row_csr),dimension(:),pointer :: row  !array of {\tt sparse\_row\_csr} 
+%    integer                                   :: Nrow !total number of rows
+%    integer                                   :: Ncol !total number of columns
+%    logical                                   :: status=.false. !Allocation status
+% #ifdef _MPI
+%    type(sparse_row_csr),dimension(:),pointer :: loc      !array for the diagonal blocks
+%    integer                                   :: istart=0 !start index MPI range
+%    integer                                   :: iend=0   !end index MPI range
+%    integer                                   :: ishift=0 !shift index MPI range
+%    logical                                   :: mpi=.false.
+% #endif
+% end type sparse_matrix_csr
+% \end{lstlisting}
+
 Matrix elements are inserted using the 
@@
 implicit reallocation, i.e.~{\tt vec=[vec,new\_element]}. 
-
+%
 This approach offers several key advantages, including efficient 
@@
 \subsubsection{Sparse map}\label{CodeSparseMap}
-% \fixme{General question: Could it be more instructive to use the left bit shift notation in some expression, e.g. $A \ll N$ instead of $A \cdot 2^N$?}
 As discussed in \secu{sSecRDM}, the construction of a symmetry 
@@
 and bath components and where we highlight the overall ordering in
-spin-up and spin-down parts (see \equ{eq:FockState_|nupndw>}).
+spin-$\up$ and spin-$\dw$ parts (see \equ{eq:FockState_|nupndw>}).
 
@@
 Specifically, for each impurity configuration 
-$\vec{i}_\s$ (key), it maintains a list of compatible bath 
-configurations $\vec{b}_\s$ (values) consistent with the conserved 
+$\vec{i}_\s$ ({\it key}), it maintains a list of compatible bath 
+configurations $\vec{b}_\s$ ({\it values}) consistent with the conserved 
 quantum numbers of the given sector (see \secu{sSecQNs}).
 The {\tt sparse\_map} objects ${\cal P}$ are constructed upon call of the {\tt
-  build\_sector} ({\tt sector} constructor) using different algorithms 
+  build\_sector} (i.e. the {\tt sector} constructor) using different algorithms 
 for each value of {\tt ed\_mode}.
@@
    integer                               :: bath_state_max!largest bath state
-   integer,dimension(:),allocatable      :: bath_state    !rank-1 bath states
+   integer,dimension(:),allocatable      :: bath_state    !Values:rank-1 bath states
    integer,dimension(:),allocatable      :: sector_indx   !bath state sector indices
@@
 
-In the {\bf normal} mode, the sector object contains two separate {\tt
+In the {\bf normal} mode, the {\tt sector} object contains two separate {\tt
   sparse\_maps} objects ${\cal P}_{\s=\up,\dw}$, reflecting the
@@
 The sparse maps are built as follows. 
-For any spin Fock state appearing in the sector $\ket{J_\s}=\ket{{\vec{I}_{\s}\vec{B}_{\s}}}$,
-the \emph{key} is determined by the integer $I_\s$ corresponding to the
-impurity bitset $\vec{I}_\s$. The \emph{values} are given by any
-integer $B_\s$ corresponding to any bath bitset
+For any spin Fock state appearing in the sector $\ket{j}\xrightarrow{\MM}\ket{J_\s}=\ket{{\vec{I}_{\s}\vec{B}_{\s}}}$,
+the {\it key} is determined by the integer $I_\s$ corresponding to the
+impurity bitset $\vec{I}_\s$. The {\it values} are given by all 
+integers $B_\s$ corresponding to any bath bit set
 $\vec{B_\s}$ associated with $\vec{I}_\s$ by the sector symmetry constraint: $\#\vec{I}_\s + \#\vec{B}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
-Thus, any given \emph{key-value} combination 
+Thus, any given {\it key-value} combination 
 reconstructs an integer $J_\s$ representing a Fock state in the
@@
 
-An overview of the implementation, complementing the symmetry sector construction, is reported in the following listing:
-\setbox0=\hbox{%
-  \begin{minipage}{0.42\linewidth}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+An overview of the implementation leveraging the Fortran intrinsic {\tt ibits(I,pos,len)} is reported in the following listing:
+\begin{center}
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{Normal}
+\begin{lstlisting}[style=fstyle,frame=leftline,numbers=none,basicstyle={\ttfamily\scriptsize}]
 i=0
@@
 enddo
+!
 i=0
@@
 \end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.45\linewidth}
-\begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
+%
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{Superc/Nonsu2}
+\begin{lstlisting}[style=fstyle,frame=leftline,numbers=none,basicstyle={\ttfamily\scriptsize}]
 i=0
@@
     iImp   = iImpUp  + iImpDw*(2**Norb)
-    iBath  = iBathUp + iBathDw*(2**(Norb*Nbath))
+    iBath  = iBathUp + iBathDw*(2**Ns)
     call sp_insert_state(self%H(1)%sp,&
@@
 \end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list2}
-{\bf normal} & {\bf superc/nonsu2}\\
-\hline
-  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-\vspace{1mm}
-
-It leverages the Fortran intrinsic function {\tt ibits(I,pos,len)} which returns the integer representation of the bit subset of length {\tt len} starting from {\tt pos} of the  integer {\tt I}.
+\end{center}
 
@@
 is minimized by automatically distributing it among all processors in suitable shares
-according to the nature of the quantum numbers $\vec{Q}$.
+according to the value of {\tt ed\_mode}. 
 While for zero-temperature calculations only the ground state (with its
-degeneracy) is stored, for finite temperatures the list also includes all the necessary excited states.
-
-\begin{lstlisting}[style=fstyle,numbers=none]    
-!Single element of the list: contains a single eigenpair.
-!Twin states are just pointers, no memory.
-!double or cmplx vectors are automatically MPI distributed.
-type sparse_estate
-   integer                             :: sector        !Symmetry sector index
-   real(8)                             :: e             !eigenvalue: ordering key
-   real(8),dimension(:),allocatable    :: dvec          !double  eigenvector
-   complex(8),dimension(:),allocatable :: cvec          !complex eigenvector
-   logical                             :: itwin=.false. !twin sector logical label
-   type(sparse_estate),pointer         :: twin=>null()  !link to twin state in the list
-   type(sparse_estate),pointer         :: next=>null()  !List next pointer
-end type sparse_estate
-!Ordered list storing the lower part of the Hamiltonian spectrum: 
-type sparse_espace
-   integer                     :: size               !Current list
-   real(8)                     :: emax               !Max energy fixed by ${\color{comment-color}e^{-\beta {\tt emax}}\!<\!{\tt cutoff}}$
-   real(8)                     :: emin               !Min energy: the ground state energy
-   logical                     :: status=.false.     !Allocation status
-   type(sparse_estate),pointer :: root=>null()       !Root of the linked list
-end type sparse_espace
-
-\end{lstlisting}
+degeneracy) is stored, for finite temperature the list includes all the necessary excited states.
+If the input variable {\tt ED\_TWIN=T}, the {\it twin sectors}, i.e.
+sectors with symmetric values of the quantum numbers ($S_z\to -S_z$ and $N\to N_s-N$), are excluded from the list and their contribution is reconstructed by symmetry where needed.
+% \begin{lstlisting}[style=fstyle,numbers=none]    
+% !Single element of the list: contains a single eigenpair.
+% !Twin states are just pointers, no memory.
+% !double or cmplx vectors are automatically MPI distributed.
+% type sparse_estate
+%    integer                             :: sector        !Symmetry sector index
+%    real(8)                             :: e             !eigenvalue: ordering key
+%    real(8),dimension(:),allocatable    :: dvec          !double  eigenvector
+%    complex(8),dimension(:),allocatable :: cvec          !complex eigenvector
+%    logical                             :: itwin=.false. !twin sector logical label
+%    type(sparse_estate),pointer         :: twin=>null()  !link to twin state in the list
+%    type(sparse_estate),pointer         :: next=>null()  !List next pointer
+% end type sparse_estate
+% !Ordered list storing the lower part of the Hamiltonian spectrum: 
+% type sparse_espace
+%    integer                     :: size               !Current list
+%    real(8)                     :: emax               !Max energy fixed by ${\color{comment-color}e^{-\beta {\tt emax}}\!<\!{\tt cutoff}}$
+%    real(8)                     :: emin               !Min energy: the ground state energy
+%    logical                     :: status=.false.     !Allocation status
+%    type(sparse_estate),pointer :: root=>null()       !Root of the linked list
+% end type sparse_espace
+% \end{lstlisting}
 A truncation mechanism is put in place to avoid the unbounded growth of this list. On the first call, a fixed number of
@@
 
-The list dynamically adjusts to optimize the distribution of states 
+By successive call to the \NAME solver, the list dynamically adjusts to optimize the distribution of states 
 across sectors, balancing memory use and computation time. The
@@
 The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, 
-which provides an efficient, multi-layer data structure for storing 
+which provides an efficient, multi-layer, data structure for storing 
 all weights and poles required for the evaluation of DCFs. This 
 class is designed to handle multiple operators and sectors, allowing 
-for rapid, on-the-fly evaluation of the DCF for any complex frequency 
+on-the-fly evaluation of the DCF for any complex frequency 
 $z\in\CCC$.
@@
 The use of this data structure significantly reduces the computational 
-cost of evaluating DCFs by minimizing redundant calculations and 
-avoiding repeated diagonalizations, making it a critical component 
+cost of evaluating DCFs making it a critical component 
 for the high-performance execution of \NAME.
 
-\begin{lstlisting}[style=fstyle,numbers=none]   
-!The contributions to the GF Kallen-Lehmann sum are stored as
-!GF_{ab,sr}%state%channel%{w,e}.
-!A couple of weight,poles {w,e} is stored: 
-!for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
-!
-!Sub-class: contains the actual weight and poles:
-type GFspectrum
-   complex(8),dimension(:),allocatable       :: weight
-   real(8),dimension(:),allocatable          :: poles
-end type GFspectrum
-!
-!N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
-!Subclass: contains a given set of weights and poles.
-!Each instance of this subclass corresponds to a given input state 
-!and a given operator in the Kallen-Lehmann representation.  
-type GFchannel
-   type(GFspectrum),dimension(:),allocatable :: channel 
-end type GFchannel
-!
-!Main class: stores  weights and poles of a given DCF 
-!obtained through the dynamical Lanczos algorithm.
-!state_list%size = Number of states in the spectrum 
-type GFmatrix
-   type(GFchannel),dimension(:),allocatable  :: state
-   logical                                   :: status=.false. !Allocation status
-end type GFmatrix
-\end{lstlisting}
+% \begin{lstlisting}[style=fstyle,numbers=none]   
+% !The contributions to the GF Kallen-Lehmann sum are stored as
+% !GF_{ab,sr}%state%channel%{w,e}.
+% !A couple of weight,poles {w,e} is stored: 
+% !for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
+% !
+% !Sub-class: contains the actual weight and poles:
+% type GFspectrum
+%    complex(8),dimension(:),allocatable       :: weight
+%    real(8),dimension(:),allocatable          :: poles
+% end type GFspectrum
+% !
+% !N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
+% !Subclass: contains a given set of weights and poles.
+% !Each instance of this subclass corresponds to a given input state 
+% !and a given operator in the Kallen-Lehmann representation.  
+% type GFchannel
+%    type(GFspectrum),dimension(:),allocatable :: channel 
+% end type GFchannel
+% !
+% !Main class: stores  weights and poles of a given DCF 
+% !obtained through the dynamical Lanczos algorithm.
+% !state_list%size = Number of states in the spectrum 
+% type GFmatrix
+%    type(GFchannel),dimension(:),allocatable  :: state
+%    logical                                   :: status=.false. !Allocation status
+% end type GFmatrix
+% \end{lstlisting}
 
@@
 \equ{Hbath}, the bath is parametrized by two components: the
-Hamiltonian matrices, $h^p$, and the hybridization amplitudes,
-$V^p$, for $p = 1, \dots, N_\mathrm{bath}$.
+Hamiltonian matrices, $h_{\a\b\s\s'}^p$, and the hybridization amplitudes,
+$V_{\a\b\s\s'}^p$, for $p = 1, \dots, N_\mathrm{bath}$.
 Internally, the bath is represented by a dedicated object, {\tt
@@
 the user's perspective, all parameters are consolidated into a rank-1
-array of doubles, managed using a reverse communication strategy. This
-approach ensures that a local array remains accessible to the
-user while preventing direct access to the internal copy, thereby
-preserving data integrity and reducing memory overhead.
+array of doubles, managed using a reverse communication strategy. 
+% to ensure 
+% that a local array remains accessible to the
+% user while preventing direct access to the internal copy, thereby
+% preserving data integrity and reducing memory overhead.
 
@@
 electronic levels assigned to the bath, is specified
-through the input variable {\tt bath\_type}. In \NAME this variable can take one of four possible values: {\bf normal}, {\bf hybrid}, {\bf replica}, and {\bf general}.
+through the input variable {\tt bath\_type}. 
+In \NAME this variable can take one of four possible values: 
+{\bf normal}, {\bf hybrid}, {\bf replica}, and {\bf general}.
 
@@
 considered. In this case, the bath Hamiltonian gains 
-an additional set of parameters $\Delta^p_{\a}\delta_{\a\b}\delta_{\s \bar{\s}}$, diagonal in orbital space but
-off-diagonal in the spin, where $\Delta^p_\a$ represents the pairing amplitudes. 
-This choice corresponds to a Nambu representation for each  component, with the Hamiltonian matrices taking the Nambu form:
-
-$$
-\hat{h}^p = \e^p\tau_z + \Delta^p\tau_x .
-$$
-
-% \fixme{ (Samuele) Here and before h with or without hat? I would say without since it is how we wrote it in 3.1.1}
-% \fixme{The superc h should have tau\_z instead of tau\_0 in nambu repr}
-where $\tau_{i=0,x,y,z}$ are Pauli matrices.
+an additional set of parameters $\Delta^p_{\a}\delta_{\a\b}\delta_{\s \bar{\s}}$, where $\Delta^p_\a$ represents the orbital diagonal pairing amplitudes. 
+This choice corresponds to a Nambu representation for each component, with the Hamiltonian matrices taking the form:
+
+$$
+h_{\a\b\s\s'}^p = \e_\a^p\delta_{\a\b}\tau^z_{\s\s'} + \Delta^p_\a\delta_{\a\b}\tau^x_{\s\s'} .
+$$
+
+where $\tau^{i=0,x,y,z}$ are Pauli matrices.
 %
@@
 %
-Thus, the total number of parameters used to determine the bath is $N_\mathrm{param}=2N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal} or $N_\mathrm{param}=3N_\a N_\mathrm{bath}$ for the other two values of {\tt ed\_mode}.
+
+The resulting total number of parameters used to determine the bath is $N_\mathrm{param}=2N_\a N_\mathrm{bath}$ for {\tt ed\_mode}={\bf normal} or $N_\mathrm{param}=3N_\a N_\mathrm{bath}$ for the other two values of {\tt ed\_mode}.
 
 \paragraph{{\tt bath\_type}={\bf hybrid}.}
-This hybrid topology is the simplest generalization of the bath pa\-ra\-me\-tri\-za\-tion which captures the effects of locally
+The hybrid topology is the simplest generalization of the bath pa\-ra\-me\-tri\-za\-tion which captures the effects of locally
 coupled impurity orbitals. However, this setup typically requires a more challenging optimization process, especially
@@
 $$
-%
+For {\tt ed\_mode}={\bf superc} additional anomalous components 
+$\Delta_\a^p\delta_{\a\b}\delta_{\s\bar{\s}}$ diagonal in the orbital basis are included.
+%
+
 The key difference compared to the previous case is that the hybridization matrix elements are generally off-diagonal in the orbital indices:
@@
 $$
-Moreover, the {\tt ed\_mode}={\bf superc} introduces additional anomalous components 
-$\Delta^p\delta_{\a\b}\delta_{\s\bar{\s}}$ diagonal in the orbital basis.
 %
@@
 %
+
 The resulting total numbers of available bath parameters are 
@@
 The choice of the matrix basis can be inspired by symmetry group considerations \cite{Koch2008PRB,Senechal2010PRB}, by the internal structure
-of the quantum impurity, i.e. $\hat{h}^0$, or determined
-case-by-case, depending on the desired properties of the solution.
+of the quantum impurity or determined
+case-by-case depending on the desired properties of the solution.
 In this scheme, the total number of bath levels is  $N_\mathrm{b}
@@
 \vspace{2mm}
-All the procedures concerning the bath, either on the user side or concerning the internal {\tt effective\_bath}, are grouped into a set of modules wrapped by {\tt ED\_BATH}.
+All the procedures concerning the bath
+% , either on the user side or concerning the internal {\tt effective\_bath}, 
+are grouped into a set of modules wrapped by {\tt ED\_BATH}. 
 We divided the set of modules into three categories, according to their scope.
@@
 This group of modules provides user-oriented utilities, including 
-standard symmetry operations on the bath array, such as orbital 
+standard symmetry operations on the bath array, e.g. orbital 
 symmetry and particle-hole symmetry, available in 
-{\tt ED\_BATH\_USER}. The critical functionality here is the 
+{\tt ED\_BATH\_USER}.
+
+The critical functionality here is the 
 determination of the total bath array dimension, implemented in 
@@
 arrays, ensuring they contain exactly the necessary number of 
-parameters. Any following call
-to functions hosting the bath as an input verify the array's 
-dimensionality using {\tt check\_bath\_dimension} to prevent 
-allocation errors.
+parameters. 
+% Any following call
+% to functions hosting the bath as an input verify the array's 
+% dimensionality using {\tt check\_bath\_dimension} to prevent 
+% allocation errors.
 
@@
 The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica}/{\tt Hge\-ne\-ral} for the {\bf replica}/{\bf general} bath parametrizations.
-In  addition to standard object construction, destruction, reading, and saving, this module provides matrix basis
-$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ setup as well as  the variational parameters $\vec{\lambda}$ initialization through {\tt set\_Hreplica}/{\tt set\_Hge\-ne\-ral}. 
+In  addition to standard object construction, destruction, reading and saving, this module provides the setup for either the matrix basis
+$\{ \Gamma^\nu \}_{\nu=1,\dots,N_\mathrm{sym}}$ and the initial variational parameters $\vec{\lambda}$ through the function  {\tt set\_Hreplica}/{\tt set\_Hge\-ne\-ral}. 
 %
@@
 {\tt build\_Hreplica}/{\tt build\_Hge\-ne\-ral} via the relation
-$$
-h^p = \vec{\lambda}^p \cdot \vec{\Gamma}.
-$$
+$
+h^p = \vec{\lambda}^p \cdot \vec{\Gamma}
+$.
 
@@
 Lanczos-based eigensolver with distributed memory support
-\cite{Lehoucq1998}. This method incorporates re-orthogonalization within
-a block-Lanczos routine, ensuring the accurate convergence of the desired eigenpairs. However, it is also possible to select a simpler,
+\cite{Lehoucq1998} ensuring the accurate convergence of the desired eigenpairs. 
+However, it is also possible to select a simpler,
 though less efficient, parallel Lanczos algorithm using the input variable {\tt lanc\_method}.
@@
 high-performance diagonalization algorithms.
-In \onlinecite{Amaricci2022} we discussed in greater details the distributed-memory massively parallel strategies currently employed in \NAME to optimize this step and presented various benchmarks of the parallel scaling.
+In Ref.~\onlinecite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling.
 Here, we provide a brief outline of the main ideas following the notation introduced
-in \onlinecite{Amaricci2022}, and focusing on the impact of the choice of {\tt ed\_mode}.
+in Ref.~\onlinecite{Amaricci2022CPC}, and focusing on the impact of the choice of {\tt ed\_mode}. 
 For sake of clarity, here we focus on the purely electronic case, i.e.
@@
 The MVP is carried out using the {\tt MPI\_AllGatherV} algorithm which, as noted  
-\onlinecite{Amaricci2022}, requires reconstruction of distributed
+Ref.~\onlinecite{Amaricci2022CPC}, requires reconstruction of distributed
 arrays and incurs significant communication overhead.
@@
 the MPI environment, and configures the appropriate MVP procedure
-based on the symmetries of the problem. This logic is implemented in
+based on the symmetries of the problem. This is implemented in
 a set of independent modules, {\tt ED\_HAMILTONIAN\_<ed\_mode>}. Any module includes two functions: {\tt build\_Hv\_sector\_<ed\_mode>} and  {\tt vecDim\-\_\-Hv\-\_\-sector\-\_\-<ed\_mode>}.
@@
     %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}[\AA]}{z - dE^\nu_{mn}[\AA]} 
-    = \frac{1}{Z}\sum_n
-    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
+    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
+    \equiv \frac{1}{Z}\sum_n
+    \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
   \end{split}
@@
 where the terms are grouped as a sum over spectral weights and
-poles. We introduced the notation $g(\nu, w(\AA)^{\nu}_{mn},  dE(\AA)^\nu_{mn})$ does $g$ also depend on $z$?
+poles. We introduced the notation $g(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn})$
 for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
@@
 Krylov subspace algorithm and for channel $\nu$.
-This approach significantly reduces the computational burden, as it
-requires a much smaller set of basis states.
-
-However, this method is typically limited to diagonal DCF like
+% This approach significantly reduces the computational burden, as it
+% requires a much smaller set of basis states.
+
+This method is  limited to diagonal DCF like
 \equ{eqGaa}. In practice, many applications also require building off-diagonal
@@
 $$
-C_{\AA\BB}(z) = \ibra T_{\pm}[\AA(t) \BB^\dagger]\iket\, .
+C_{\AA\BB}(t) = \ibra T_{\pm}[\AA(t) \BB^\dagger]\iket\, .
 $$
@@
 $$
-G_{\a\b\s\s'}=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^\dagger ]\iket
+G_{\a\b\s\s'}(t)=\ibra \TT_\pm[ c_{\a\s}(t) c_{\b\s'}^\dagger ]\iket
 $$
@@
 c^\dagger_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
-spin-singlet exciton\cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton.
+spin-singlet exciton \cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton \cite{Amaricci2023_excitons}.
 
@@
 sufficient to compute only the top row elements along with 
-a few auxiliary functions\cite{Capone2001PRL,Capone2002Science,Capone2004sc,Toschi2005NJP,Toschi2005PRB,Capone2009RMP}.
+a few auxiliary functions \cite{Capone2001PRL,Capone2002Science,Capone2004PRLsc,Toschi2005NJP,Toschi2005PRB,Capone2009RMP}.
 %
@@
 $F_{\a\b\up\dw}$ requires distinct combinations of 
-creation and annihilation operators\cite{Capone2001PRL,Capone2002Science,Capone2004sc,Toschi2005NJP,Toschi2005PRB}. First, the component 
+creation and annihilation operators \cite{Capone2001PRL,Capone2002Science,Capone2004PRLsc,Toschi2005NJP,Toschi2005PRB}. First, the component 
 $\bar{G}_{\a\a\dw\dw}$ is evaluated as an auxiliary term 
@@
 where $E_n$ and $\ket{\psi_n}$ are the $N_{\tt state\_list}$ low-lying eigenstates 
-of the system stored in the {\tt state\_list}. This approach 
-greatly reduces computational overhead by focusing on the 
-relevant, low-energy sector.
+of the system stored in the {\tt state\_list}. 
+% This approach 
+% greatly reduces computational overhead by focusing on the 
+% relevant, low-energy sector.
 
@@
 extending the algorithm initially proposed in 
-Ref.~\onlinecite{BellomiaPhD}, to support the analysis of entanglement 
+Ref.~\onlinecite{BellomiaPhD,Bellomia2024PR}, to support the analysis of entanglement 
 properties of quantum impurities for any value of {\tt ed\_mode}.
@@
 ensemble average $\ibra \rho^\mathrm{imp} \iket$, as defined in 
-\equ{eq:thermal_average}.What is the meaning of $\langle\rangle$ here?
-\equ{eq:thermal_average} contains a weighted sum over the states of the full system, while $\rho^\mathrm{imp}$ is already reduced over the bath degrees of freedom.
+\equ{eq:thermal_average}.
 
@@
 where the corresponding pure density matrix $\rho$ is given by:
-\begin{equation}
+\begin{equation}\label{DefRho}
 \rho = \ket{\psi}\bra{\psi} = \sum_{IJ=1}^{4^{N_\mathrm{s}}} 
@@
 block structure of the Fock space defined by the symmetry sectors and
-the subsequent map sparsity, to perform the trace \emph{on-the-fly}. 
+the subsequent map sparsity, to perform the trace {\it on-the-fly}. 
 This approach significantly reduces the computational cost by limiting 
@@
 This structure stores, for each impurity configuration 
-(the \emph{key}), the 
+(the {\it key}), the 
 corresponding bath configurations 
-(the \emph{values}) that 
+(the {\it values}) that 
 satisfy the symmetry constraints over the sector quantum numbers
@@
 subspace $\ket{\vec{n}_{\bar{\s}}}$ without introducing any 
-fermionic sign.
-
-In the {\bf normal} mode, the iRDM is restricted to 
+fermionic sign. In this basis \equ{DefRho} takes the form:
+\begin{equation}\label{RhoNormal}
+\rho = 
+    \sum_{i_\up=1}^{D_{i_\up}}\!
+    \sum_{p_\up=1}^{D_{p_\up}}\!
+    \sum_{i_\dw=1}^{D_{i_\dw}}\!
+    \sum_{p_\dw=1}^{D_{p_\dw}}\!
+    \sum_{j_\up=1}^{D_{j_\up}}\!
+    \sum_{q_\up=1}^{D_{q_\up}}\!
+    \sum_{j_\dw=1}^{D_{j_\dw}}\!
+    \sum_{q_\dw=1}^{D_{q_\dw}}\!
+    a_{i_\up p_\up i_\dw p_\dw}a^*_{j_\up q_\up j_\dw q_\dw}
+    % \left[
+    \ket{\vec{i}_\up}\ket{\vec{p}_\up}\!\otimes\!\ket{\vec{i}_\dw}\ket{\vec{p}_\dw}
+    %\right]
+    % \left[
+    \bra{\vec{q}_\dw}\bra{\vec{j}_\dw}\!\otimes\!\bra{\vec{q}_\up}\bra{\vec{j}_\up}
+    %\right].   
+\end{equation}
+where the coefficients $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the
+expansion coefficients of the state on the Fock basis
+$\ket{\psi} = \sum_I a_I \ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}$.
+
+Before proceeding further we show that in the {\bf normal} mode the iRDM is restricted to 
 {spin-diagonal} blocks. This follows from the observation 
 that the conserved quantum numbers are 
-\emph{additive} quantities, i.e. 
+{\it additive} quantities, i.e. 
 $N_\s = N_\s^\mathrm{imp} + N_\s^\mathrm{bath}$,
@@
 the impurity quantum numbers $N_\s^\mathrm{imp}$.
-The resulting iRDM takes the form:
+
+Using \equ{RhoNormal} the iRDM takes the form:
 \begin{equation}
@@
   \begin{aligned}
-  \rho^\mathrm{imp} &= {\color{Plum}\Tr_{b_\up b_\dw}}{\rho} = 
-  {\color{Plum}
-  \sum_{b_\up=1}^{D_{b_\up}}
-  \sum_{b_\dw=1}^{D_{b_\dw}}
-  }
+  \rho^\mathrm{imp} &= \Tr_{{\color{red}b_\up b_\dw}}{\rho} = 
+  \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
+  \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
   \bra{b_\up}\otimes\bra{b_\dw}
@@
     &=
-    {\color{Plum}
-    \sum_{b_\up=1}^{D_{b_\up}}
-    }
+    \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
     \sum_{i_\up=1}^{D_{i_\up}}
@@
     \Bigg(    
-    {\color{Plum}
-    \sum_{b_\dw=1}^{D_{b_\dw}}
-    }
+    \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
     \sum_{i_\dw=1}^{D_{i_\dw}}
@@
     \underbrace{\left(
-    {\color{Plum}
-    \sum_{b_\up=1}^{D_{b_\up}}
-    \sum_{b_\dw=1}^{D_{b_\dw}}
-    }
+    \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
+    \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
     a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
@@
 \end{equation}
-where the coefficients $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the
-expansion coefficients of the state on the Fock basis
-$\ket{\psi} = \sum_I a_I \ket{i_\uparrow\,  b_\uparrow\,} \otimes \ket{i_\downarrow
-  \, b_\downarrow}$.
+
 Notably, the factors $C_{i,b}$, which account for the potential 
@@
 indices.
-% \fixme{(igor and lorenzo) to be honest we took a while to understand this equation.
-There are a lot of indices...
-could it be rewritten more compactly e.g.
-by not explicitly writing |p><q|?
-Or perhaps by only showing one spin species, since the Fock space factorizes?
-Or alternatively, maybe color-code the parts?
-I get that
-% sum\_p sum\_q <b|p><q|b> is a trace... but it's not immediate}
-% {\color{teal}(Gabriele) Mmm, if I recall it correctly, surely writing it for just
-% one spin species (after saying that the final rho factorizes), would look 
-% cleaner, but the fermionic signs will need to be computed explicitly. Cause
-% they cancel to 1 only after actually doing the product between the up and the
-% dw part. Color coding the parts could be very pretty and easy to follow,
-% \sout{I can think about that, thanks for the feedback!} I tried, by highlighting
-% the summations involved in the trace. All the remaining indices come from the
-% full impurity-bath and up-dw decomposition of the state, that is clearlly written
-% in equation (\ref{eq:decomposition_for_rdm_normal})}
 
@@
 Consider a generic Fock basis state in the form 
-$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, and define the 
-ground state as $\ket{\psi} = \sum_I a_I \ket{I}$. 
-The pure density 
-matrix is then given by
-$\rho = \sum_{IJ} a_I a^*_J \ket{I}\bra{J}$ ,
-while the iRDM is obtained by tracing over the bath degrees of 
-freedom:
+$\ket{I} =\ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}$, and express the 
+ground state as 
+$$
+\ket{\psi} = \sum_I a_I \ket{I} = 
+    \sum_{i_\up=1}^{D_{i_\up}}
+    \sum_{b_\up=1}^{D_{b_\up}}
+    \sum_{i_\dw=1}^{D_{i_\dw}}
+    \sum_{b_\dw=1}^{D_{b_\dw}}
+    a_{i_\up b_\up i_\dw b_\dw}
+    \ket{{i}_\up\,{b}_\up\,{i}_\dw\,{b}_\dw}.
+$$ 
+By tracing over the bath degrees of freedom of the corresponding pure density matrix $\rho$ we obtain:
 \begin{equation}
@@
 \end{equation}
-where $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the expansion
-coefficient in the Fock basis.
 
@@
           iBath = Bath(ib)
-          !Decompose iBath into B_Up, B_dw to reconstruct B bitset. 
-          !B --> {B_up,B_dw}
-          iBathUp = mod(iBath,2**Nbath)
-          iBathDw = (iBath)/2**Nbath
           !Reconstruct the Fock state Ii map back to sector state i
-          ii= iImpUp + iImpDw*2**Ns + 2**Norb*(IBathUp + IBathDw*2**Ns)
+          ii= iImpUp + iImpDw*2**Ns + iBath*2**Norb
           i = binary_search(sectorI%H(1)%map,ii)
           !Reconstruct the Fock state Jj map back to sector state j
-          jj= jImpUp + jImpDw*2**Ns + 2**Norb*(IBathUp + IBathDw*2**Ns)
+          jj= jImpUp + jImpDw*2**Ns + iBath*2**Norb
           j = binary_search(sectorI%H(1)%map,jj)
@@
 \begin{equation}
-\Delta_{\a\b\s\s'}(z) = \sum_p V^p_{\a\s} 
-\left( z\11 - \hat{h}^p \right)_{\a\b\s\s'}^{-1} V^p_{\b\s'},
+\Delta_{\a\b\s\s'}(z) = \sum_p \left[\hat{V}^p
+\left( z\11 - \hat{h}^p \right)^{-1} \hat{V}^p\right]_{\a\b\s\s'},
 \end{equation}
@@
 \end{equation}
-where $V^p_{\a\s}$ and $h^p_{\a\b\s\s'}$ are the bath coupling 
+where $V^p_{\a\b\s\s'}$ and $h^p_{\a\b\s\s'}$ are the bath coupling 
 and bath Hamiltonian matrices, respectively, and $\mu$ is the chemical 
@@
 
-In the superconducting case, where {\tt ed\_mode}={\bf superc}, 
+In the superconducting case, {\tt ed\_mode}={\bf superc}, 
 special care is needed to properly handle the anomalous (off-diagonal) 
 components within the Nambu basis. In this case, the bath functions 
-must include both the normal and anomalous components, 
-which can significantly alter the form of the self-energy. Similar issues arise in the {\bf nonsu2} case, where spin off-diagonal components usually drive the physics of the problem.
+include both the normal and anomalous components.
 
@@
 While different optimization methods have been developed for 
-truncated algorithms like sCI~\cite{Mejuto_Bath_ASCI-DMFT} or DMRG~\cite{dmrg}, 
+truncated algorithms, e.g. sCI~\cite{Mejuto_Bath_ASCI-DMFT} or DMRG~\cite{Bauernfeind2017PRX}, 
 which handle systems with a 
@@
 logical OR between these criteria, with the parameter value selecting 
-which condition to apply. Is the actual stop condition the logical or between $C_1$ and $C_2$? What is meant here?
+which condition to apply.
 \end{itemize}

### 2025-05-30 04_cbinding.tex
Updates from Overleaf

@@
 The recent growing availability of state-of-the-art software dedicated
-to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}Unfinished list of references
+to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}
 poses a serious challenge to test accuracy and reliability of the
@@
 provides a general interface, which encompasses all dimension of the
-input array there including inequivalent impurities support. Not sure what is meant here
+input array there including inequivalent impurities support.
 For example, the function {\tt get\_sigma} returns the self-energy

### 2025-05-30 05_examples.tex
Updates from Overleaf

@@
 The system is defined on a Bethe lattice with density of states
-$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$ This density of states does not normalize to 1,
+$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$,
 where $D=2t$ is the half-bandwidth.
@@
 allocation, Bethe lattice creation, and solver initialization.
-'Bethe lattice creation' sounds a bit weird here.
-DMFT does not directly work with a lattice as a collection of sites, it only deals with the spectral functions.
 
@@
   relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
-    \Sigma(i\omega)$ $G_\mathrm{loc}$ inverted?. For the Bethe lattice, this simplifies to
-    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$ Missing square in the coefficient?.
+    \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
+    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$.
 
@@
 \subsubsection{Finite temperature solution (w2dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTw2d}
-Capitalization in 'w2dynamics' is different compared to Sec. 4.
 To demonstrate the usage of the w2dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
@@
     \textbf{Finite temperature DMFT solution.}
-    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and Self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT.
+    Comparison of the imaginary parts of the Green's function $\Im{G}(i\omega_n)$ and self-energy $\Im{\Sigma}(i\omega_n)$ from different solutions of the Hubbard model on the Bethe lattice using DMFT.
 Data are for $T/D=0.01$ and $U/D=2.0$.
@@
 
-\item Update the Weiss fields components, respectively 
+\item Update the Weiss field's components, respectively 
   $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
@@
 \item Optimize the bath parameters $\vec{x}$ to best describe the updated
-    Weiss fields, potentially using \NAME provided conjugate gradient  fit
+    Weiss fields, potentially using the \NAME provided conjugate gradient  fit
     procedures.
@@
 converged=False;iloop=0
-while (not converged and iloop<ed.Nloop ):
+while (not converged and iloop<ed.Nloop):
     iloop=iloop+1
@@
     H_\mathrm{int} = \sum_i \Big[\omega_0 b^\dagger_i b_i + g(b^\dagger_i +
-    b_i)\sum_{\sigma}(c^\dagger_{i\sigma}c_{i\sigma}
-    -\frac{1}{2})\Big]. 
+    b_i)\sum_{\sigma}\left(c^\dagger_{i\sigma}c_{i\sigma}
+    -\frac{1}{2}\right)\Big]. 
 \end{equation}
@@
 \begin{equation}\label{HlikeAttraction}
-    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}) \Big]^2
+    H_\mathrm{int} \overset{ \omega_0 \rightarrow \infty}{ \longrightarrow } -\frac{\lambda}{2} \sum_i \Big[\sum_\sigma\left(c^\dagger_{i\sigma}c_{i\sigma} -\frac{1}{2}\right) \Big]^2,
 \end{equation}
@@
 In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
-enters in a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
+enters a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
 choice of the coupling.
 
-We characterize the model solution by showin the evolution of the
+We characterize the model solution by showing the evolution of the
 double occupation $\langle n_{\up}n_{\dw}\rangle$ as a function of the
-phonon frequency $\omega_0$, see panel (A). In this panel we compare
+phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
 the behavior for the normal solution ({\tt ed\_mode=normal}) against the superconductive
@@
 To better characterize the nature of the superconducting
-phase in the Holstein model we report the evolution of the anomalous order
-parameter $\phi$ in the adiabatic to anti-adiabatic crossover.
+phase in the Holstein model, we report the evolution of the anomalous order
+parameter $\phi$ in the adiabatic to anti-adiabatic crossover (panel (B) of \figu{figEx5}).
 The DMFT results obtained with \NAME show a rapid increase in the
@@
     \caption{\label{figEx3}%
-        Imaginary part of the Matsubara Green's function (left) and the
-        corresponding orbital-resolved spectral function (right) computed for a
+        Imaginary part of the Matsubara Green's function $G_\alpha(i\omega_n)$ (left) and the
+        corresponding orbital-resolved spectral function $A_\alpha(\omega) = -\Im{G_\alpha(\omega)} / \pi$ (right) computed for a
         three-orbital impurity model with an interaction of the Hubbard-Kanamori
-        type (\ref{Hint}). This illustration is produced by the edipack2triqs
+        type (\ref{Hint}). This illustration is produced by the EDIpack2TRIQS
         example script presented in \secu{SecExamplesTRIQS}.
@@
 
-We proceed to demonstrate how to use the edipack2triqs compatibility
+We proceed to demonstrate how to use the EDIpack2TRIQS compatibility
 layer (\secu{sSecInteropTRIQS}) to solve a quantum system comprised by a
@@
 
-A Python script implementing a calculation that makes use of edipack2triqs
+A Python script implementing a calculation that makes use of EDIpack2TRIQS
 generally begins with a few module imports.
@@
                  basicstyle={\scriptsize\ttfamily},
-                 firstline=85, lastline=112]
+                 firstline=85, lastline=113]
 {edipack2_examples/edipack2triqs/hubbard_kanamori.py}
@@
 interactions this model admits an excitonic phase in which opposite
-orbitals electrons and holes across the band gap bound into a coherent phase.
+orbital electrons and holes across the band gap bind into a coherent phase.
 
@@
 $$
-H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int}
+H = \sum_{k}\psi_{k}^\dagger H(k)\psi_{k} + H_{\rm int},
 $$
@@
 c_{1\downarrow k}, c_{2\downarrow k} ]$ is the spinor collecting
-annihilation operator $c_{a\sigma k}$ destructing an electrons at
+annihilation operator $c_{a\sigma k}$ destroying an electron at
 orbital $a=1,2$ with spin  $\sigma=\up,\dw$ and lattice momentum
@@
 H(k) = \left[M-2t(\cos{k_x}+\cos{k_y}) \right]\Gamma_{03} +
-   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02}
+   \lambda\sin{k_x}\Gamma_{31} -   \lambda\sin{k_y}\Gamma_{02},
 $$
@@
    H_{\rm int} = (U-J)\frac{\hat{N}(\hat{N}-1)}{2} - J\left( \frac{1}{4}\hat{N}^2 +
-   \hat{S_z}^2 - 2 \hat{T_z}^2\right)
+   \hat{S_z}^2 - 2 \hat{T_z}^2\right),
  $$
@@
 
-The code implementation follows the same guidelines discusses above
-for the other examples. There are two specific modifications requied
-to the  user. The first is to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone in
+The code implementation follows the same guidelines discussed above
+for the other examples. There are two specific modifications required
+from the user. The first is to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone in
 order to obtain the local interacting Green's function, used in the
 implementation of the self-consistency conditions:
-$\GG^{-1}=G_\mathrm{loc}^{-1}+\Sigma$, with: 
+$\GG^{-1}=G_\mathrm{loc}^{-1}+\Sigma$, with 
 $$
@@
 parameter
-$\vec{E}=[E_0,E_x,E_y,E_z]$ where $E_a=\langle\psi^\dagger
+$\vec{E}=[E_0,E_x,E_y,E_z]$, where $E_a=\langle\psi^\dagger
 \Gamma_{a1}\psi \rangle$.
 The first component $E_0$ describes the singlet excitonic state,
-whereas the remaing ones correspond to the triplet states with
+whereas the remaining ones correspond to the triplet states with
 different spin orientation.   
@@
 and/or $E_y$ different from zero.
-Interestingly, this state breakes several symmetries including
-time-reversal and spin SU(2) which protect the topological state.
+Interestingly, this state breaks several symmetries including
+time-reversal and spin SU(2), which protect the topological state.
 
@@
 \end{lstlisting}
-where we use the local non-interacting Hamiltonian 
+Here we use the local non-interacting Hamiltonian 
 $H_\mathrm{loc}=\tfrac{1}{N_k}\sum_k H(k)$ to set 
@@
 possibility of forming an excitonic ordered phase, the replica bath
-is constructed out of matrix basis with 4 distinct elements
+is constructed out of the matrix basis with 4 distinct elements
 $\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which
@@
 $E_0$, the exciton triplet along easy-axis $E_z$ and in-plane
-$E_x$ (we assume $E_y=0$ levaraging on residual $U(1)$ in-plane
-symmetry. 
+$E_x$ (we assume $E_y=0$ leveraging on residual $U(1)$ in-plane
+symmetry). 
 %
-In the following we consider the case of $M=1$ which corresponds to a
+In the following we consider the case of $M=1$, which corresponds to a
 QSHI in the non-interacting limit and $J/U=0.25$.
-The implemention is nearly identical to the cases discussed above and
+The implementation is nearly identical to the cases discussed above and
 we report it here for completeness:
@@
 %
-The main effect of the interaction to the topological properties can be captured by the renormalized mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
-real-part of the self-energy being proportional to $\Gamma_{03}$
+The main effect of the interaction on the topological properties can be captured by the renormalized mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
+real part of the self-energy being proportional to $\Gamma_{03}$
 corrects the mass term with respect to its bare value. To leading
-order this correction is given proportional to $\tfrac{U-5J}{4}\langle
+order this correction is proportional to $\tfrac{U-5J}{4}\langle
 \hat{T}_z\rangle$. So, for our choice of parameters, the effect of
@@
 reducing the topological band gap. In the strong-coupling limit the
-two orbitals get populated with one electron per site, reaching the
+two orbitals get populated by one electron per site, reaching the
 conditions for the formation of a Mott insulating state.
 As reported in panel (A) of \figu{figEx4}, at intermediate coupling,
-the DMFT solutions features the formation of a
+the DMFT solution features the formation of a
 region of exciton condensation with $\langle E_x\rangle>0$, $\langle
@@
 To further illustrate the nature of the three distinct phases of this
-system, we leverage on the direct access to real-axis spectral
+system, we rely on the direct access to the real-axis spectral
 function provided by \NAME solver. In panels (B)-(D) of \figu{figEx4}
@@
 larger high-energy weight.
-Finally, in the MI the two orbital spectral function describes the two 
+Finally, in the MI the two-orbital spectral function describes the two 
 characteristic Hubbard bands separated by a large Mott gap.
@@
 
-To complete the overview of \NAME capabilities, we consider another
-model for interacting quantum spin-Hall insulators, defined on the honeycomb lattice, with two inequivalent sites in the unit-cell.
-Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit-cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
+To complete the overview of \NAME's capabilities, we consider another
+model for interacting quantum spin-Hall insulators defined on the honeycomb lattice, with two inequivalent sites in the unit cell.
+Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
 \begin{align*}
@@
 with a spin-dependent $\pm\tfrac{\pi}{2}$ chiral phase arising from spin-orbit coupling, which is well-known to open a topological gap at the Fermi level \cite{Kane2005PRLa,Kane2005PRL}.
-The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$, are 
+The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$ are 
 defined in terms of $\sigma_a$ and $\tau_\ell$ Pauli matrices, respectively 
@@
 To investigate the effects of electron-electron repulsion on the
-Kane-Mele model we include a local interaction, 
+Kane-Mele model, we include a local interaction
 leading to the Kane-Mele-Hubbard Hamiltonian \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}
@@
 
-The essential features of the groundstate phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
-For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above above a critical $U/t$ ratio\footnote{In contrast with the expectations for a generic half-filled bipartite lattice, for which the groundstate is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
-at the Fermi level renders ineffective the logarithmic instability, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
+The essential features of the ground state phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
+For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio\footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
+at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
 With a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.
@@
 either the \texttt{replica} and \texttt{general} choices for 
-the \texttt{bath\_type} option. The most stable strategy to 
-verify that the groundstate of the model is magnetized in the
+the \texttt{bath\_type} option. The most robust strategy to
+verify that the ground state of the model is magnetized in the
 plane also in DMFT is to allow either an $S_z$ or an $S_x$ (equivalently $S_y$) magnetization in the bath, and then
@@
       !  - normal mode: normal/AFMz and we fit spin-components independently
-      !  - nonsu2 mode: broken Sz-conservation and we fit both spin components altogether
+      !  - nonsu2 mode: broken Sz-conservation and we fit
+      !                 both spin components together
       select case(ed_mode)
@@
       !
-      !> linear mixing and check convergence: using ${\color{comment-color}\mathrm{DMFTtools}}$
+      !> linear mixing and convergence check: using ${\color{comment-color}\mathrm{DMFTtools}}$
       if(iloop>1) Bath = wmixing*Bath + (1.d0-wmixing)*Bath_prev
@@
 and AFM$_\parallel$ calculations and compare them to establish which 
-is favored as the groundstate of the system. In \figu{fig:KMenergy}(a)
+is favored as the ground state of the system. In \figu{fig:KMenergy}(a)
 we show results for the energy difference $E_\parallel-E_\perp$ across
@@
 DMFT with NRG solver and lattice AFQMC data, as taken from 
-Ref.\,\cite{Racz2020}.
+Ref.~\cite{Racz2020}.
 
@@
     off-plane AFM solutions found with \NAME at $T=0$. Negative values
-    signal a groundstate with in-plane magnetization. The plateau at zero
+    signal a ground state with in-plane magnetization. The plateau at zero
     energy difference marks the topological phase of the model (a 
-    paramagnetic quantum spin-Hall insulator), at all points except on the $\lambda_\mathrm{so}=0$ line, where the groundstate is an interacting
+    paramagnetic quantum spin-Hall insulator), at all points except on the $\lambda_\mathrm{so}=0$ line, where the ground state is an interacting
     Dirac liquid, at weak coupling, or an isotropic antiferromagnet at strong coupling. In panel (b) we compare the total energies, across the 
@@
 The capabilities of the EDIpack2ineq layer go well beyond the
-simple case of a two-site unit-cell. We can readily adapt the
+simple case of a two-site unit cell. We can readily adapt the
 code to deal with nanoscopic systems such as hexagonal flakes
@@
 Panel (a) shows the interaction dependence of the local magnetization,
-computed from the impurity groundstate as  
+computed from the impurity ground state as  
 $ \ibra S_x \iket = \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket$,
-so that we can define the $S_x$ spin-occupation numbers as
+so that we can define the $S_x$ spin occupation numbers as
 \begin{equation*}

### 2025-05-30 06_conclusions_acknowledgement_appendix.tex
Updates from Overleaf

@@
 generic quantum impurity problems. Leveraging on the massively
-parallel algorithms introduced with its predecessor, this version of
+parallel algorithms introduced by its predecessor, this version of
 the library features new capabilities and symmetries within a unified
 framework, providing reliable evaluations of the dynamical correlation
-functions on arbitrary complex argument.
+functions of an arbitrary complex frequency.
 This makes it particularly well-suited for capturing the sharp
@@
 most important algorithms and classes. We presented in
-details the third-party interfaces which extend exact diagonalization
+detail the third-party interfaces which extend exact diagonalization
 capabilities beyond the realm of the library itself.   
 Finally, we showcased the use of the \NAME software in different
-contexts via elaborated example which can serve as reference for the
-potential users.
+contexts via elaborated examples, which can serve as a reference for potential users.
 
@@
 \section*{Acknowledgements}
-We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou,  M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, A.~Camjayi, M.~Rozenberg.
+We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.
 
@@
 L.C. devised and developed the C-binding layer, the Python, Julia and Monicelli interface together with Python specific deployment and installation tools. 
-I.K. developed the Triqs interface and contributed to the testing part. 
+I.K. developed the TRIQS interface and contributed to the testing part. 
 A.K., M.W. and G.S. developed the integration with W2Dynamics.  
@@
 A.A. and L.C. wrote the backbone of the manuscript.
-All authors participated in the writing and revision process.
+All authors participated in writing this manuscript.
 
@@
 It is written in C++ and offers wrappers for the basic
-types and operations thereof. The syntax replicates a cultural italian
+types and operations thereof. The syntax replicates a cultural Italian
 phenomenon known as ``supercazzola", a rambling nonsensical discourse
@@
 the EDIpack functions.
-The first part of the DMFT code load all the required functions from
+The first part of the DMFT code loads all the required functions from
 {\tt bagaglio.cpp}, in particular it loads the interface to the \NAME
@@
 by retrieving the self-energy function which is used to obtain the
-local Green's function. These enters the self-consistency equation
-which update the Weiss field. Finally bath optimization is performed
+local Green's function. These enter the self-consistency equation
+which updates the Weiss field. Finally bath optimization is performed
 and if error condition is met the loop exit.
@@
 contains a number of functions implementing complex algebra, array
-costruction and interfacing the \NAME procedures. The directory also
+construction and interfacing the \NAME procedures. The directory also
 contains an example of input file and a converged bath parametrization
@@
 \end{lstlisting}
-A simple run using provided input file {\tt inputED.conf} will
-re-converge the solution within few loops.
+A simple run using the provided input file {\tt inputED.conf} will
+re-converge the solution within a few loops.
 

### 2025-05-31 edipack2_examples/AHM_EDIpack2EDIpy/data/script_figAHM2.py
Updated figure figAHM.pdf

@@ -1,0 +1,154 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+from mpl_toolkits.axes_grid1.inset_locator import inset_axes
+
+
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 30})
+plt.rcParams['figure.figsize'] = [35, 15]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    """
+)
+
+
+axs["A"].text(0.02, 0.98, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.02, 0.98, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.02, 0.98, r"(C)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U0.6/Gloc_i1_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U1.0/Gloc_i1_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U1.5/Gloc_i1_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
+rho4 = np.genfromtxt('U2.0/Gloc_i1_realw.dat',skip_header=0);x4=rho4[:,0];y4=-rho4[:,1]/np.pi
+rho5 = np.genfromtxt('U3.0/Gloc_i1_realw.dat',skip_header=0);x5=rho5[:,0];y5=-rho5[:,1]/np.pi
[…]

### 2025-05-31 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_2d.f90

@@ -1,5 +1,5 @@
 program ed_ahm_2d
-  USE EDIPACK2
+  USE EDIPACK
   USE SCIFOR
   USE DMFT_TOOLS
   implicit none

### 2025-05-31 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_square.f90

@@ -1,5 +1,5 @@
 program ed_ahm_square
-  USE EDIPACK2
+  USE EDIPACK
   USE SCIFOR
   USE DMFT_TOOLS
   USE MPI

### 2025-05-31 01_intro.tex
Updates from Overleaf

@@
 Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem \cite{Georges1996RMP}.
+\fixme{(Samuele)I would also cite gutzwiller approx and DMET, we should not restrict the number of users of the code :). Something like:
+
+Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012_DMET} and Gutzwiller approximation (GA)~\cite{Lanata2015_GA}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
+The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.
+}
 By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.

### 2025-05-31 03_edipack2.tex
Updates from Overleaf

@@
 high-performance diagonalization algorithms.
-In Ref.~\onlinecite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling.
+In Ref.~\cite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling.
 Here, we provide a brief outline of the main ideas following the notation introduced

### 2025-05-31 04_cbinding.tex
Updates from Overleaf

@@
 The recent growing availability of state-of-the-art software dedicated
-to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Mejuto_Bath_ASCI-DMFT,...}
-poses a serious challenge to test accuracy and reliability of the
+to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Wallerberger2019CPC,Mejuto_Bath_ASCI-DMFT}
+poses a challenge to test accuracy and reliability of the
 results.
-As such, complex software packages are expected to develop a higher level of interoperability, i.e. the capability to operate with other software, possibly written in different programming languages.
+As such, software packages are expected to develop a higher level of interoperability, i.e. the capability to operate with other software, possibly written in different programming languages.
 Modern Fortran, which is the language of choice for \NAME, since many
@@
 variables that are interoperable with C.
+Here we describe the implementation of an interoperability layer aiming at developing APIs for other languages as well as 
+integrating \NAME in complex scientific frameworks, e.g. TRIQS~\cite{Parcollet2015CPC} or W2Dynamics~\cite{Wallerberger2019CPC}.
 
@@
 {\tt ISO\_C\_BINDING} module, which is part of the Fortran
-standard since 2003. The module contains definitions of named
+standard since 2003\cite{Reid2003CISE,Reid2007SFF}. The module contains definitions of named
 constants, types and procedures for C interoperability.
@@
 Function overloading is also not supported, hence all interfaced Fortran functions, for example supporting multiple input variable combinations with different types and ranks, are here represented by multiple alternative functions.
-As an example, the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters, is callable in C++ in the following variants:
+
+As an example, we consider the {\tt ed\_chi2\_fitgf} Fortran function, which handles the fitting of bath parameters. This is callable in C++ in the following variants:
 \begin{itemize}
-    \item  {\tt chi2\_fitgf\_single\_normal\_n3}: for {\tt ed\_mode=normal/nonsu2}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_normal\_n5}: for {\tt ed\_mode=normal/nonsu2}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_superc\_n3}: for {\tt ed\_mode=superc}, single-site DMFT and rank-3 Weiss field/hybridization function arrays
-    \item  {\tt chi2\_fitgf\_single\_superc\_n5}: for {\tt ed\_mode=superc}, single-site DMFT and rank-5 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_normal\_n3}: for {\tt ed\_mode=normal/nonsu2} rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_normal\_n5}: for {\tt ed\_mode=normal/nonsu2} rank-5 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n3}: for {\tt ed\_mode=superc} rank-3 Weiss field/hybridization function arrays
+    \item  {\tt chi2\_fitgf\_single\_superc\_n5}: for {\tt ed\_mode=superc} rank-5 Weiss field/hybridization function arrays
 \end{itemize}
-and analogous functions for the inequivalent impurities case, i.e. EDIpack2Ineq. All functions are listed and thorougly documented in the online manual.
+Analogous functions for the inequivalent impurities case, i.e. \NAME{2Ineq}, are available. All functions are listed and thoroughly documented in the online manual associated to this release. 
 When using \NAME functions in a C/C++ program, care must be taken in the way arrays are passed.
@@
 \paragraph{{\bf Main}.} This group contains interface to the exact
-digonalization solver, interfacing the solver itself {\tt
+diagonalization method, interfacing the solver  {\tt
   solve\_site/ineq} as well as its initialization
@@
 set the non-interacting part of the impurity Hamiltonian
-$h^0_{\a\b\s\s'}$ through the functions {\tt set\_Hloc}, as well as the
+$h^0_{\a\b\s\s'}$ through the functions {\tt set\_Hloc}, or the
 interaction Hamiltonian through {\tt add\_twobody\_operator}.
@@
 EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
-The source code can be obtained from the git repository \href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py} and installed via
-
+The code can be obtained and and installed from source as:
 \begin{lstlisting}[style=mybash]
@@
 \paragraph{Anaconda.}
-Similarly to \NAME, the Python API in EDIpack2py is available as an
+Similarly to \NAME, the Python API EDIpack2py is available as an
 Anaconda package for GNU/Linux and macOS systems. Packages are available for
-Python version 3.10 and newer. The \NAME package contains the {\tt
+Python$\geq 3.10$. The \NAME package contains the {\tt
   EDIpack2py} Python module as well as \NAME and SciFortran
@@
 \subsection{EDIpack2TRIQS: the TRIQS interface}\label{sSecInteropTRIQS}
-A thin compatibility layer between \NAME and the Toolbox for Research on
-Interacting Quantum Systems (TRIQS)\cite{Parcollet2015CPC} called EDIpack2TRIQS
-is available as a stand-alone project. This is a pure Python package
-built upon \NAME's Python API EDIpack2py (see \secu{sSecInteropEDIpy}) that provides a
+A thin compatibility layer between \NAME and TRIQS~\cite{Parcollet2015CPC}, i.e. Toolbox for Research on
+Interacting Quantum Systems,  called EDIpack2TRIQS is available as a stand-alone project. This is a pure Python package
+built upon EDIpack2py (see \secu{sSecInteropEDIpy}) that provides a
 limited object-oriented interface to the most important features of \NAME.
+
 EDIpack2TRIQS strives to offer seamless interoperability with program tools
@@
 common to other TRIQS-based impurity solvers, such as
-TRIQS/CTHYB\cite{Seth2016CPC}. It also enables execution of \NAME calculations
+TRIQS/CTHYB~\cite{Seth2016CPC}. It also enables execution of \NAME calculations
 in the MPI parallel mode with no extra effort from the user.
@@
 found online at \href{https://krivenko.github.io/edipack2triqs/}
-{krivenko.github.io/edipack2triqs/}.
+{krivenko.github.io/edipack2triqs}.
 
 \subsubsection{Installation}\label{sSecInteropTRIQSInstallation}
-The package depends on \NAME (which ultimately depends on SciFortran), EDIpack2py
+The package depends on \NAME, and its dependencies therein, EDIpack2py
 and TRIQS version 3.1 or newer. Assuming the three prerequisites are correctly 
-installed in the OS, the current development version of EDIpack2TRIQS can be 
+installed in the system, the current development version of EDIpack2TRIQS can be 
 installed with {\tt pip} from its 
@@
 \paragraph{{\bf Constructor}.}
-Constructor of {\tt EDIpackSolver} accepts the Hamiltonian to be diagonalized
+The constructor of {\tt EDIpackSolver} accepts the Hamiltonian to be diagonalized
 in the form of a second-quantized fermionic operator, the TRIQS {\tt Operator}
@@
 \NAME is supported as alternative impurity solver in the W2Dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
-The only prerequisite to use this option is the presence of a functioning EDIpack2py installation, which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameters.
-
+The only prerequisite to use this option is the presence of a functioning EDIpack2py installation (see \secu{sSecInteropEDIpy}), which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameters.
 The  behavior of W2Dynamics is controlled by means of an input file, by default called
 {\tt Parameters.in}.
-First, in order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
 
-Then, in order to configure the ED solver, the content of a specific section in the parameters file, called {\tt [EDIPACK]}, has to be specified.
+In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
+In line to the current design of W2Dynamics, the \NAME solver is configured and controlled by setting the content of a specific section in the parameters file, called {\tt [EDIPACK]}.
 
@@
 This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath elements {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
-
+%
 A second set of input variables, including physical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the W2Dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
@@
 
-Solver specificities are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard CT-HYB code.
-For example, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format.
-Moreover, W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{}.
+Specific \NAME solver features are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard CT-HYB code.
+For instance, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format.
+Moreover, W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{2Ineq}.
 As a consequence, functionalities that would require specific support from W2Dynamics and are currently not available can not be used through the interface, including e.g.\ the solution of impurity problems in the superconductive phase, i.e.
@@
 The C-binding approach is extremely handy, in that it opens the way for interoperability  with a large number of languages and frameworks. 
-As a further significant example, an experimental Julia API 
-is provided for \NAME. Although this is at the present a proof of concept, it is capable of replicating the results of Fortran, C++ and
-Python implementations for the Bethe lattice example driver.
+As a further significant example, an {\bf experimental} Julia API 
+is provided for \NAME. Although this is at the present a proof of concept, it is capable of replicating the results obtained with Fortran, C++ and
+Python implementations for the Bethe lattice example driver (see \secu{SecExamples}).
 Its structure and operation mimic that of the EDIpack2py layer, with minimal language-specific differences.
@@
 The \NAME{} Julia API consists of a module called {\tt EDIpack2jl}, which provides access to the global variables and functions contained in {\tt  libedipack\_cbindings.so (.dylib)}. 
-
 The library is searched upon loading the module, with the following order of priority:
@@
 \end{lstlisting}
-
+%
 and the location of the source files needs to be included in the user program via
@@
 \end{lstlisting}
-
+%
 The correct way to access global variables and functions is as in the following example:
@@
 The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.
-
-Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multithreading.
+Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
 At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
@@
 
-We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt  examples} folder of the EDIpack2jl repository.
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the \secu{SecExamples} folder of the EDIpack2jl repository.
 This script is intended to be run serially.

### 2025-05-31 05_examples.tex
Updates from Overleaf

@@
 In this section we illustrate and benchmark the functionalities and of the \NAME
-library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code snippets from different programming languages. 
+library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages.
+
 Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
-In the implementation using Fortran, Python or other \NAME API we adopt a reverse communication strategy, which requires the user to independently implement these parts or, equivalently, to exploit existing utilities.
+Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to exploit existing utilities.
+
 In our examples based on the Fortran APIs we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors) to perform specific tasks, including the evaluation of the local Green's function, the implementation of the self-consistency, the construction of the tight-binding model or the calculation of the kinetic energy.
@@
 On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which handles all these tasks seamlessly.
-Similarly, the TRIQS library offers an extensive toolbox for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
+Similarly, the TRIQS library offers an extensive framework for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
 
@@
 in a Bethe lattice, i.e., a Cayley tree with coordination number 
-$z\to\infty$~\cite{Georges1996RMP}.
+$z\to\infty$~\cite{Zhang1993PRLb,Caffarel1994PRL,Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
 Here, we present a guided implementation of the DMFT 
@@
 $\langle ij \rangle$.
-
-The system is defined on a Bethe lattice with density of states
-$\rho(\e)=\frac{1}{2D}\sqrt{D^2-\e^2}$,
+We consider the system defined on a Bethe lattice with density of states
+$\rho(\e)=\frac{2}{\pi D^2}\sqrt{D^2-\e^2}$,
 where $D=2t$ is the half-bandwidth.
-In DMFT, this lattice model is mapped onto a quantum impurity problem with
-an effective electronic bath that must be determined
-self-consistently.
+Within DMFT framework~\cite{Georges1996RMP}, this lattice model is mapped onto a quantum impurity problem with an effective electronic bath that must be determined self-consistently.
 
@@
 samples share a similar initial structure, including memory 
-allocation, Bethe lattice creation, and solver initialization.
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.465\linewidth}
+allocation, creation of the Bethe DOS and solver initialization.
+
+\begin{center}
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{Fortran}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 \end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.505\linewidth}
+%
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{C++}
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 ed_set_Hloc_single_N4(Hloc.data(), d);
+$\phantom{.}$
+$\phantom{.}$
 \end{lstlisting}
 \end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list3}
-{\bf Fortran} & {\bf C++}\\
-  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-
-The bath is described by the (unknown) function $\GG^{-1}_0$, called
-the Weiss field ({\tt Weiss}). In the ED approach implemented in \NAME, 
+\end{center}
+
+The bath is described by the (unknown) function $\GG^{-1}_0$, i.e. 
+the Weiss field ({\tt Weiss}). In the ED method implemented in \NAME, 
 the bath is approximated using a finite number of discrete energy levels. 
-The function $\GG^{-1}_0$ is then used to determine the bath parameters 
-$\vec{x} = \{V, h\}$ through the optimization method outlined in 
-\secu{sSecFit}.
+The Weiss field $\GG^{-1}_0$ is then used to determine the bath parameters $\vec{x} = \{\hat{V}, \hat{h}\}$ through the optimization method outlined in \secu{sSecFit}.
 
@@
 
-\setbox0=\hbox{%
-  \begin{minipage}{0.465\linewidth}
-    \center
+\begin{center} 
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{Fortran}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
    call ed_init_solver(bath)
+$\phantom{.}$   
+$\phantom{.}$   
 \end{lstlisting}
 \end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.505\linewidth}
-    \center
+%
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{C++}
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 \end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list4}
-  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
-
-The iterative algorithm to solve the DMFT problem is based on
-a reverse communication strategy and proceeds as follows:
+\end{center}
+
+The iterative algorithm to solve the DMFT problem proceeds as follows:
 \begin{itemize}  
-
-\item[{\tiny {\bf EDIpack}}] Call the exact diagonalization {\bf impurity solver}
+\item[{\tiny {\bf EDIpack}}] Call the \NAME {\bf impurity solver}
   whose only input is the set of parameters $\vec{x}$ contained in a
@@
 \item[{\tiny {\bf EDIpack}}] Retrieve the self-energy functions $\Sigma_{\a\b\s\s'}(i\omega)$ on the
-  Matsubara axis using dedicated function provided by \NAME API.
+  Matsubara axis using dedicated function {\tt ed\_get\_sigma} available in the \NAME API.
 
@@
 with  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
+Note that this step can be performed analytically for the Bethe lattice~\cite{Georges1996RMP} or completely substituted by retrieving the impurity Green's function $G_\mathrm{imp}$ via the {\tt ed\_get\_gimp} function.
 
@@
     \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
-    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$.
+    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$ or, equivalently, $\Delta = \tfrac{D}{4}G_\mathrm{imp}$.
 
   \item[{\tiny {\it User} \textgreater\ {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ against the updated
-    Weiss field,  potentially using the conjugate gradient procedures 
-supplied by \NAME. Then, restart at step 1.
+    Weiss field using the conjugate gradient procedures supplied by \NAME. Then, restart at step 1.
 \end{itemize}
@@
 results. Alternative optimization methods can also be employed as 
-needed. 
+needed~\cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
 An example of implementation is provided in the following listings.
 
-\setbox0=\hbox{%
-  \begin{minipage}{0.46\linewidth}
-    \center
+\begin{center} 
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{Fortran}
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
     call ed_solve(bath)     
-    !Retrieve $\Sigma(i\omega_n)$
+    !Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
     call ed_get_sigma(Smats,'m')
@@
     enddo
+
     !Self-consistency
-    Delta = D/4d0*Gmats
+    Delta = 0.25d0*D*Gmats
+
     !Fitting -> new bath
     call ed_chi2_fitgf(Weiss,bath,ispin=1)
-    !Check convergence: from $\mathrm{DMFTtools}$
+
+    !Check convergence: from ${\color{comment-color}\mathrm{DMFTtools}}$
     converged=check_convergence(Delta,&
           dmft_error,Nsuccess,Nloop)
+
 enddo
+$\phantom{.}$   
 \end{lstlisting}
 \end{minipage}
-}
-\savestack{\listingA}{\box0}
-
-\setbox0=\hbox{%
-  \begin{minipage}{0.51\linewidth}
-    \center
+%
+\begin{minipage}[t]{0.49\linewidth}
+\textbf{C++}
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
   solve_site(Bath.data(),bath_dim,1,1);      
-  //Retrieve $\Sigma(i\omega_n)$
+  //Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
   get_sigma_site_n5(Smats.data(),//
@@
 \end{minipage}
-}
-\savestack{\listingB}{\box0}
-
-\begin{tabular}{c|c}\label{list5}
-  \stackinset{l}{}{t}{}{}{\listingA} & \stackinset{l}{}{t}{}{}{\listingB} 
-\end{tabular}
+\end{center}
 
 \paragraph{Results.}
-In the following, we present results for the interaction-driven Mott 
-transition in the Bethe lattice, which captures the gradual 
-transformation of a partially-filled metallic state into a correlated 
-insulator.
-To illustrate this, we report in panel (A) the evolution of the spectral 
-function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of the 
-interaction strength $U$. Despite the inherently {\it spiky} nature 
-of the spectrum, resulting from the finite number of poles in the 
+In the following, we present \NAME results for the interaction-driven MIT obtained with previous implementations.
+The MIT captures the gradual transformation of a partially-filled metallic state into a correlated insulator.
+
+To illustrate this, we report in panel (A) the evolution of the spectral function $-{\rm Im}G_\mathrm{loc}(\omega)/\pi$ as a function of the  interaction strength $U$. 
+Despite the inherently {\it spiky} nature of the spectrum, resulting from the finite number of poles in the 
 discretized effective bath, the characteristic features of the Mott 
@@
     \caption{\label{figEx1}%
-      \textbf{The Metal-insulator Mott transition.}
+      \textbf{The metal-insulator Mott transition.}
       (a) Evolution of the spectral function $-\Im{G}(\omega)/\pi$ as
@@
 reflects the complete localization of the electrons, effectively 
-suppressing coherent quasi-particle excitations. Specifically, 
-causality dictates that the real part of the self-energy must also 
+suppressing coherent quasi-particle excitations. Causality dictates that the real part of the self-energy must also 
 grow significantly near the singularity, making it impossible to 
@@
 level.
-
-Panels (B) and (C) illustrate this phenomenon by showing the evolution 
-of the self-energy $\Sigma$. In panel (B), we present the Matsubara 
-self-energy ${\rm Im}\Sigma(i\omega)$ in the low-energy regime. As the 
-interaction strength $U$ increases, this function progressively 
-grows, eventually diverging as the critical interaction threshold 
-$U > U_\mathrm{c}$ is crossed.
+Panels (B) and (C) illustrate this phenomenon by showing the evolution of the self-energy $\Sigma$.
+In panel (B), we present the Matsubara self-energy ${\rm Im}\Sigma(i\omega)$ in the low-energy regime.
+As the  interaction strength $U$ increases, this function progressively grows, eventually diverging as the critical interaction threshold $U > U_\mathrm{c}$ is crossed.
 This divergence along the Matsubara axis is directly linked to the
@@
   Im}\Sigma$ singularity at $\omega = 0$.
-
 Panel (C) complements this picture by displaying the real part 
-$\Re{\Sigma}(\omega)$ in the same low-energy regime. Here, increasing 
-$U$ leads to a rapid rise of this component, culminating in a 
-discontinuous behavior as the critical point is approached. This 
+$\Re{\Sigma}(\omega)$ on the real-axis near the Fermi level.
+Here, increasing $U$ leads to a rapid rise of this component, culminating in a discontinuous behavior as the critical point is approached.
+This
 discontinuity directly reflects the divergence in the imaginary part
@@
 A quantitative measure of this transition is provided by the 
-quasi-particle renormalization factor $Z$, which can be used to capture the degree 
-of electron delocalization. This parameter ranges from 1 for a 
-non-interacting metal to 0 for a fully localized Mott insulator. It is 
+quasi-particle renormalization factor $Z$, which can be used to capture the degree of electron delocalization.
+This parameter ranges from 1 for a non-interacting metal to 0 for a fully localized Mott insulator.
+It is
 defined through the low-energy expansion of the self-energy as
@@
 diverges, reflecting the onset of complete electron localization as 
-$Z \to 0$, consistent with the divergence 
-${\rm Im}\Sigma(\omega) \rightarrow -\infty$.
-
-\subsubsection{Finite temperature solution (w2dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTw2d}
-To demonstrate the usage of the w2dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
-In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in w2dynamics against the \NAME solver at finite temperature.
-
-In contrast to the \NAME API that only enables access to the impurity solver and bath optimization procedures, but requires the user to implement (using different methods) the DMFT algorithm themselves, the standard way to use w2dynamics is fundamentally different: a single Python script {\tt DMFT.py} is provided that takes care of the whole DMFT calculation via dedicated classes to implement generic self-consistency.
-The w2dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
-Further information about the functioning of w2dynamics can be found in Ref.~\onlinecite{Wallerberger2019CPC}
-
-Another important difference concerns the initial point of the iterative DMFT solution algorithm: while \NAME starts from a given discrete bath, w2dynamics is initialized with a zero self-energy function or alternatively reads this quantity from a converged solution file.
-When using the \NAME ED interface, the initial Weiss field is determined using self-consistency and finally an initial discrete bath is obtained through the \NAME bath optimization procedure.
-
-The w2dynamics configuration file for the solution of the Bethe lattice problem at finite temperature reads: 
+$Z \to 0$, consistent with the singular behavior  
+$-{\rm Im}\Sigma(\omega\to0) \to\infty$.
+
+\subsubsection{Finite temperature solution (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
+To demonstrate the usage of the W2Dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
+In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in W2Dynamics against the \NAME solver at finite temperature.
+
+Unlike \NAME, which provides only the impurity solver and bath optimization procedures and requires the user to implement the DMFT algorithm themselves (potentially using various methods), W2Dynamics adopts a fundamentally different approach: a single Python script, {\tt DMFT.py}, handles the entire DMFT calculation, leveraging dedicated classes that implement the generic self-consistency.
+The W2Dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
+Further information about the functioning of W2Dynamics can be found in Ref.~\cite{Wallerberger2019CPC}
+
+Another important difference concerns the initial point of the iterative DMFT solution algorithm: while \NAME starts from a given discrete bath, W2Dynamics is initialized with a zero self-energy function or alternatively reads this quantity from a converged solution file.
+Thus, when using the \NAME interface in W2Dynamics, the initial Weiss field is determined using self-consistency and  an initial discrete bath is obtained through the \NAME bath optimization procedure.
+
+The W2Dynamics configuration file for the solution of the Bethe lattice problem at finite temperature reads: 
 \begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 {\tt bethe\_dmft.in}, the DMFT simulation can then by run on {\tt NC} cores via:
-\begin{lstlisting}[style=mybash,numbers=none]
+\begin{lstlisting}[style=mybash,numbers=none,morekeywords={mpiexec},deletekeywords={in}]
 mpiexec -n NC /path/to/w2dynamics/DMFT.py bethe_dmft.in
@@
 
-The results are collected into an HDF5 archive in the usual w2dynamics format, including output quantities inherited from \NAME.
-Results can be viewed using the script {\tt hgrep} provided with w2dynamics or with other HDF5 tools.
+The results are collected into an HDF5~\cite{The_HDF_Group_Hierarchical_Data_Format} archive in the usual W2Dynamics format, including output quantities inherited from \NAME.
+Results can be viewed using the script {\tt hgrep} provided with W2Dynamics or with other HDF5 tools.
 In this example we extract the Matsubara self-energy function $\Sigma(i\omega_n)$ for the last DMFT iteration:
@@
 Data are for $T/D=0.01$ and $U/D=2.0$.
-CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
+CTQMC results from the solver included with W2Dynamics are compared against \NAME ED results, used both through the W2Dynamics interface and with a standalone Fortran program.
         }
@@
 
-In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC solver in w2dynamics and using the \NAME ED method both as a solver in w2dynamics and with a program using the Fortran API directly as shown in the previous subsection.
+In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC and the \NAME ED method as solvers in W2Dynamics.
+In addition we compare with results obtained using the Fortran API directly as shown in the previous subsection.
 Using DMFT, we solve the Hubbard model on a Bethe lattice for $T/D=0.01$ and $U/D=2.00$, corresponding to a correlated metallic state.
-In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ (note that w2dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver).
+
+In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ which is the direct output for both methods (note that W2Dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver).
 In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$.
-The results obtained from the three calculations are in this case nearly identical already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics.
+The results obtained from the three calculations are in excellent agreement one with another already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics ({\tt Nmeas=200000}).
 
@@
 The second example we present concerns the DMFT description of the 
-attractive Hubbard model on a two-dimensional square lattice. This 
+attractive Hubbard model~\cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. This 
 example has a twofold aim: (i) to demonstrate the support of \NAME 
 for ($s$-wave) superconductivity, and (ii) to illustrate the use of 
-the library's Python API through a concrete working example. The 
+the library's Python API through a concrete working example.
+
+The 
 model Hamiltonian is given by:
@@
 $$
-where $U > 0$, $c^\dagger_{\ka\s} = \tfrac{1}{\sqrt{N}} 
-\sum_i e^{-i\ka \cdot R_i} c^\dagger_{i\s}$, and $c^\dagger_{i\s}$ 
-is the creation operator for an electron at site $i$ with spin $\s$. 
+where $U > 0$, $c^\dagger_{i\s}$ 
+is the creation operator for an electron at site $i$ with spin $\s$ and $c^\dagger_{\ka\s} = \tfrac{1}{\sqrt{N}} 
+\sum_i e^{-i\ka \cdot R_i} c^\dagger_{i\s}$. 
 The occupation operator is $n_{i\s} = c^\dagger_{i\s} c_{i\s}$, and 
@@
 The DMFT workflow for this case is largely similar to the previous 
-example, but it now operates in the Nambu basis defined by the spinor
-$$
-\psi_i=\begin{bmatrix} c_{i\up} \\ c^\dagger_{i\dw} \end{bmatrix}. 
-$$
+example, but it now operates in the Nambu basis defined by the spinor $\psi_i=[\hat{c}_{i\up}\quad  \hat{c}^\dagger_{i\dw}]^T$ where the symbol $\hat{o}$ indicates the potential multi-orbital nature of the system, which reduces to a scalar in the present single-orbital case.
 In this basis, the Green's function takes the matrix form:
@@
 \end{equation}
-where the symbol $\hat{A}$ indicates the potential multi-orbital 
-nature of the system, which reduces to a scalar in the present 
-single-orbital case. The components in the second row, denoted 
-by $\hat{\bar{A}}$, are connected to the first row by particle-hole 
-and time-reversal symmetries. The specific relations depend on the 
+The components in the second row, denoted 
+by $\hat{\bar{A}}$, are connected to the first row by particle-hole and time-reversal symmetries. The specific relations depend on the 
 symmetry of the order parameter (here, $s$-wave) and whether the 
@@
 independent components from the first row, significantly reducing 
-the computational effort. The initial part of the code handles the 
+the computational effort. 
+Note that part of the operations required to implement the DMFT cycle are implemented in the Python module {\tt aux\_funx.py}, adapting from {\tt DMFTtools} functions.  
+The initial part of the code handles the 
 lattice structure and solver initialization, as described below.
@@
 import numpy as np
+#Import EDIpack2py:
 from edipack2py import global_env as ed
+#Import MPI support 
 import mpi4py
 from mpi4py import MPI
+#Import functions to build ${\color{comment-color}G_\mathrm{loc}}$ and perform DMFT self-consistency in Nambu space
+from aux_funx import * 
 import os,sys
-from aux_funx import * #include function to build $G_\mathrm{loc}$ 
+
+#Start MPI framework:
 comm = MPI.COMM_WORLD
@@
 master = (rank==0)
-#Functions
+
+#Functions: build 2D grid and dispersion ${\color{comment-color}\e(k)}$
 def generate_kgrid(Nk):
@@
     return np.dot(gridout,[b1,b2])
+
 def h_square2d(k,t):
@@
 
-#Generate Hk and set Hloc
+#Generate Hk=${\color{comment-color}\e(k)}$ and set Hloc
 kgrid   = generate_kgrid(Nk)
 Hk      = h_square2d(kgrid,t_hop)
-HkNambu   = np.array([h_square2d(kgrid,t_hop),-np.conj(h_square2d(-kgrid,t_hop))])
 Hloc    = np.sum(Hk,axis=0)/Nk**2
 ed.set_hloc(Hloc.astype(complex))
+
+#Build dispersion in Nambu space ${\color{comment-color}\e(k)\tau^z}$
+HkNambu = np.array([h_square2d(kgrid,t_hop),-np.conj(h_square2d(-kgrid,t_hop))])
 
@@
 \begin{itemize}
-\item Call the exact diagonalization {\bf impurity solver} {\tt
+\item[{\tiny {\bf EDIpack}}] Call the exact diagonalization {\bf impurity solver} {\tt
     ed.solve} providing the set of bath parameters $\vec{x}=\{V,h\}$  as input.
@@
 
-\item
+\item[{\tiny {\bf EDIpack}}]
   Evaluate the interacting local Green's functions $\hat{G}_\mathrm{loc}$ and
@@
 
-\item Update the Weiss field's components, respectively 
+\item[{\tiny {\it User}}] Update the Weiss field's components, respectively 
   $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
@@
 
-\item Optimize the bath parameters $\vec{x}$ to best describe the updated
+\item[{\tiny {\it User}}\textgreater\ {\tiny {\bf EDIpack}}] Optimize the bath parameters $\vec{x}$ to best describe the updated
     Weiss fields, potentially using the \NAME provided conjugate gradient  fit
@@
     iloop=iloop+1
-    #Solve impurity problem
+    #Solve quantum impurity problem for the current bath
     ed.solve(bath)
-    #Self-consistency with aux_funx procedures:
+
+    #Retrieve the Matsubara self-energy components ${\color{comment-color}\Sigma(i\omega_n) }$ and ${\color{comment-color}S(i\omega_n) }$
     Smats = np.array([ed.get_sigma(axis="m",typ="n"),ed.get_sigma(axis="m",typ="a")])
+
+    #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
     Gmats = get_gloc(wm*1j       ,ed.xmu,HkNambu,Smats,axis="m")
     Weiss = dmft_weiss_field(Gmats,Smats)
-    #Fit
+
+    #Fit Weiss field and update the bath
     bath = ed.chi2_fitgf(Weiss[0],Weiss[1],bath)
+
     #Error check
@@
 Here we showcase some results for the DMFT solution of the 
-attractive Hubbard model across the BCS to BEC crossover regime, 
+attractive Hubbard model across the BCS-to-BEC crossover regime~\cite{Toschi2005PRB,Toschi2005NJP,Amaricci2014PRA} 
 illustrating the capability of \NAME to handle $s$-wave 
@@
 $-\tfrac{1}{\pi}\Im G_\mathrm{loc}(\omega)$, as a function of the 
-attraction $U$. For any finite $U$, the Van Hove peak at 
-$\omega = 0$ characteristic of the 2D square lattice (visible at 
-$U = 0$) is split by the formation of a superconducting gap, whose 
-width increases with $U$. This gap reflects the emergence of a finite 
-order parameter $\phi = \langle c_\up c_\dw \rangle$, signaling the 
-onset of superconducting coherence.
-
-The evolution of this order parameter is presented in panel (B), 
-highlighting the crossover from the weak-coupling BCS regime to the 
-strong-coupling BEC regime. In the BCS limit, $\phi$ shows the 
-characteristic exponential growth with $U$, reflecting the formation 
-of weakly bound Cooper pairs. This regime is known to be 
+attraction $U$. For any finite $U$, the Van Hove peak near the Fermi level characteristic of the 2D square lattice (visible at 
+$U = 0$) is split by the formation of a superconducting gap. The latter reflects the emergence of a finite 
+order parameter $\phi = \langle c_\up c_\dw \rangle$ and onset of superconducting coherence.
+
+The evolution of the order parameter with attraction $U$ is presented in panel (B). The figure  
+highlights the crossover from the weak-coupling BCS regime to the 
+strong-coupling BEC regime. In the BCS limit, $\phi$ displays the 
+characteristic exponential growth with $U$, known to be 
 computationally challenging. In the opposite, strong-coupling, limit 
-$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$, 
-indicating tightly bound local pairs. Comparison with the mean-field result 
-(gray line) reveals the effect of local dynamical fluctuations, which 
-slightly suppress the order parameter, particularly in the intermediate 
-regime.
+$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the mean-field result 
+(gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime.
 
 To quantify these dynamical effects, we plot in panel (C) the 
-\emph{correlation strength}
-$\Theta=\frac{|S(i\omega\to 0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$
-where $S(i\omega)$ is the anomalous self-energy.
-This ratio encapsulates, in a single positive number, % sorry, but "statically captures" sounded quite mysterious to me (I guess it refers to having just a single number, but it requires hard mental processing, imho)
-the amplitude of the dynamical dependence of $S(i\omega)$ by comparing its 
-BCS-like limit at high energy with the low-energy behavior at the Fermi level. 
+{\it correlation strength}~\cite{Amaricci2015PRL,Amaricci2016PRB}
+$\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
 Large values of $\Theta$ indicate an anomalous self-energy with 
 significant dynamical effects, hence a more correlated superconducting state.
-Our results show that both the weak 
-and strong coupling limits are relatively close to the BCS results, 
-while the intermediate regime is marked by strong 
-correlations, significantly departing from the mean-field picture.
-
-To further illustrate the impact of dynamical fluctuations, we 
-present in panel (D) the evolution of the double occupancy 
-$d = \langle n_\up n_\dw \rangle$ as a function of $U$. At half-filling, 
-the mean-field expression for this quantity is $d = 1/4 + \phi^2$, 
-reflecting the sole contribution of the order parameter. Our DMFT 
-results show a slight increase in $d$ over the mean-field prediction 
-in the weak coupling regime, corresponding to a steep growth of
-the correlation strength $\Theta$. 
-However, as $U$ increases, the double occupancy drops below 
-the BCS result, reflecting the onset of strong pairing and 
-pair localization in the BEC limit. Correspondingly, $\Theta$ 
-progressively decreases at large $U$ attraction strength.
-
-Finally, we demonstrate the ability of \NAME to capture finite 
+Our results show that the DMFT solution significantly departs from the MF picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
+A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D).
+We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$.
+The DMFT
+results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
+the MF result.
+
+Finally, we demonstrate the capability of \NAME to describe finite 
 temperature effects. Panel (E) shows the temperature dependence of 
@@
 $\phi \sim (T_\mathrm{c} - T)^\beta$ with $\beta = 1/2$, consistent 
-with classical Ginzburg-Landau theory.
+with  Ginzburg-Landau theory.
 
@@
 handling both ground state and finite temperature superconducting 
-phases, capturing the complex physics of the BCS-BEC crossover with 
-high accuracy.
+phases, for instance capturing the complex physics of the BCS-BEC crossover with high accuracy.
 

### 2025-05-31 06_conclusions_acknowledgement_appendix.tex
Updates from Overleaf

@@
 
-\noindent
-V: {\it Lei ha clacsonato?}\\
-P: {\it Tu ha clacsonato?}\\
-M: {\it Tarapia tapioco, prematurata l'interfaccia, o scherziamo?}\\
-V: {\it Prego}?\\
-M: {\it Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico
-basato su C++ e utilizzante la toolchain di LLVM anche per Linux e
-Unix soltanto in due, oppure in quattro anche scribai con il file
+\begin{dialogue}
+\speak{\MakeUppercase{V}} {\it Lei ha clacsonato!}
+
+\speak{\MakeUppercase{P}} {\it Tu ha clacsonato?}
+\par\lips\par
+
+\speak{\MakeUppercase{M}} {\it Tarapia tapioco, prematurata l'interfaccia, o scherziamo?}
+
+\speak{\MakeUppercase{V}} {\it Prego}?
+
+\speak{\MakeUppercase{M}} {\it Scusi noi siamo in Monicelli, come fosse un linguaggio esoterico basato su C++ e utilizzante la toolchain di LLVM anche per Linux e Unix soltanto in due, oppure in quattro anche scribai con il file
 sorgente {\tt hm\_bethe.mc}? \\ Come {\tt
-  github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}\\
-V: {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano
-programmando loro, non si intrometta!}\\
-M: {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le
-funzioni? Lo vede che interfacciano gli array, non supportati da
-Monicelli, e prematurano anche! 
+  github.com/lcrippa/prematurata\_la\_dmft}, per esempio?}
+
+\speak{\MakeUppercase{V}} {\it Ma che DMFT, mi faccia il piacere! Questi signori stavano programmando loro, non si intrometta!}
+
+\speak{\MakeUppercase{M}} {\it Ma no, dico, mi porga il file {\tt bagaglio.cpp}. Le vede le funzioni? Lo vede che interfacciano gli array, non supportati da {\tt Monicelli}, e prematurano anche! 
 Ora io le direi, anche con il rispetto per l'autorità, anche solo le
@@
 \href{https://github.com/esseks/monicelli.git}{github.com/esseks/monicelli.git}
-%\url{https://github.com/esseks/monicelli.git}
-e compila il file {\tt hm\_bethe.mc}, per esempio.}\\
-V: {\it Basta così! Mi seguano nel programma di test!}\\
-P: {\it No, no, no, attenzione! Il loop dmft completo \`e supportato
-secondo la Ref.~\onlinecite{Georges1996RMP}, abbia pazienza,
+e compila il file {\tt hm\_bethe.mc}, per esempio.}
+
+\speak{\MakeUppercase{V}} {\it Basta così! Mi seguano nel programma di test!}
+
+\speak{\MakeUppercase{P}} {\it No, no, no, attenzione! Il loop DMFT completo \`e supportato secondo la Ref.~\cite{Georges1996RMP}, abbia pazienza,
 senn\`o.... Plotta i dati, anche un pochino di Green's function e
-Self-energy in prefettura.}\\
-M: {\it Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.}\\
-V: {\it Ho bello che capito. Si farà finta di passar da bischeri!}\\
+Self-energy in prefettura.}
+
+\speak{\MakeUppercase{M}} {\it Senza contare che {\tt prematurata\_la\_dmft} ha perso i contatti con il tarapia tapioco, dopo.}
+
+\par\lips\par
+
+\speak{\MakeUppercase{V}} {\it Ho bello che capito. Si farà finta di passar da bischeri!}
+\end{dialogue}
 

### 2025-05-31 01_intro.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load.
+\fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility.
+Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017_EDLib} and the more recent XDiag~\cite{wietek2025_xdiag}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015_pomerol}; and for fermions coupled with spins, such as H$\Phi$~\cite{KAWAMURA2017_Hphi,Ido2024_Hphiupdate}.
+
+N.B. if added we may want to delete "(ED)" from the next sentence since it is defined here.}
 

### 2025-05-31 05_examples.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
    !...  
-   !Read variables
+   !EDIpack: Read variables
    call ed_read_input('inputED.conf')
-   !Solver-specific arays
+
+   !Solver-specific arrays. Using Rank-5  
    allocate(Smats(Nspin,Nspin,Norb,Norb,Lmats))
@@
    !...
-   !Initialize Bethe arrays
+   !Construct Bethe DOS using SciFortran functions
    allocate(Ebands(Le),Dbands(Le))
-   !From SciFortran:
    Ebands = linspace(-D,D,Le,mesh=de)
    Dbands = dens_bethe(Ebands,Wband)*de
-   !Set local H
+   !
+   !EDIpack: Set impurity Hamiltonian
    call ed_set_hloc(Hloc)
@@
 double D = 1.0;
-//Read  variables    
+
+//EDIpack: Read  variables    
 char input[] = "inputED.conf"; 
@@
 int total_size_n5 = total_size * Lmats;    
-//Solver-specific arrays
+//Solver-specific arrays rank5
 vector<complex<double>> Hloc(total_size);
@@
 //...
-//Initialize Bethe arrays
+//Construct Bethe DOS
 vector<double> Ebands, Dbands;
+
 //Locally defined functions:
@@
 Dbands = dens_bethe(Ebands,Wband,de);
-//set local H
+
+//EDIpack: Set impurity Hamiltonian
 ed_set_Hloc_single_N4(Hloc.data(), d);
-$\phantom{.}$
-$\phantom{.}$
 \end{lstlisting}
@@
 \begin{lstlisting}[style=fstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-   !Initialize solver
+   !EDIpack: Initialize solver
    Nb=ed_get_bath_dimension()
@@
 \begin{lstlisting}[style=cstyle,frame=none,numbers=none,basicstyle={\scriptsize\ttfamily}]
-// Initialize solver
+//EDIpack: Initialize solver
 int Nb;
@@
 \item[{\tiny {\it User}}] Update the Weiss field via the {\bf self-consistency}
-  relation: $\GG^{-1}_0(i\omega) = G_\mathrm{loc}(i\omega) +
+  relation: $\GG^{-1}_0(i\omega) = G^{-1}_\mathrm{loc}(i\omega) +
     \Sigma(i\omega)$. For the Bethe lattice, this simplifies to
-    $\Delta = \tfrac{D}{4}G_\mathrm{loc}$ or, equivalently, $\Delta = \tfrac{D}{4}G_\mathrm{imp}$.
+    $\Delta = \tfrac{D^2}{4}G_\mathrm{loc}$ or, equivalently, $\Delta = \tfrac{D^2}{4}G_\mathrm{imp}$.
 
@@
     iloop=iloop+1
-    !Call ED Solver
+
+    !EDIpack: Call ED solver
     call ed_solve(bath)     
-    !Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
+    !EDIpack: Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
     call ed_get_sigma(Smats,'m')
+
     !Build local Green's function
@@
           dmft_error,Nsuccess,Nloop)          
-
 enddo
-$\phantom{.}$   
 \end{lstlisting}
@@
 while (iloop < Nloop && !converged) {
-  //Call ED Solver
+  //EDIpack: Call ED solver
   solve_site(Bath.data(),bath_dim,1,1);      
-  //Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
+  //EDIpack: Retrieve ${\color{comment-color} \Sigma(i\omega_n)}$
   get_sigma_site_n5(Smats.data(),//
       0,0,wm.data(),Lmats,0);
-  //Build a local Green's function
+  //Build local Green's function
   for (int i=0;i<Lmats;++i) {
@@
   $\GG_0^{-1}$ and $\FF_0^{-1}$, through the {\bf self-con\-sis\-ten\-cy}
-  relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}_\mathrm{loc}(i\omega) +
+  relation: $\mathbfcal{G}^{-1}_0(i\omega) = {\mathbf G}^{-1}_\mathrm{loc}(i\omega) +
   {\mathbf \Sigma}(i\omega)$ in Nambu space.
@@
       function of the attraction $U$. Data for BCS (gray) is compared
-      to DMFT results (blue line and symbols). 
-      (c) The correlation strength
-      $\Theta=\frac{|S(i\omega\to0)-S(i\omega\to\infty)|}{S(i\omega\to\infty)}$ as a function of the
+      to DMFT results (blue line and symbols). Inset: the correlation strength
+      $\Theta$ (see main text) as a function of the
       attraction $U$ across the BCS-BEC crossover. 
-      (d) Comparison of the double occupation $D=\langle n_\up
-      n_\dw\rangle$ as a function of attraction $U$ between BCS (gray
-      solid line) and DMFT (blue solid line and symbols). 
       (e) Superconducting order
@@
 (gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime. 
-
-To quantify these dynamical effects, we plot in panel (C) the 
+To further quantify these dynamical effects, we plot in the inset of the same panel the 
 {\it correlation strength}~\cite{Amaricci2015PRL,Amaricci2016PRB}
@@
 Our results show that the DMFT solution significantly departs from the MF picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
-A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D).
+% A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D).
 We show the evolution of the double occupancy $d = \langle n_\up n_\dw \rangle$ as a function of $U$ compared to the MF expression $d = 1/4 + \phi^2$.
 The DMFT
-results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
-the MF result.
+% results obtained with \NAME show a slight increase in $d$ over the MF prediction in the BCS regime. As $U$ increases and local correlation becomes sizable, the double occupancy drops below 
+% the MF result.
 
@@
 One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
-i.e. \textbf{ed\_mode=superc}. 
-In this example, we discuss  the normal and
-superconductive solution of the pure Holstein model on the Bethe
-lattice within DMFT.
-We stress that, using Fortran API, the code
+i.e. {\tt ed\_mode=superc}. In order to illustrate this property using a simple application, in this example we discuss the normal and
+superconductive solution of the pure Holstein model on the Bethe lattice within DMFT.
+We stress that  the code
 implementation for this specific case is essentially identical to the listing reported in the sections
 \ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
-\ref{SecExamplesAHM} ({\tt ed\_mode=superc}).
-
-So we consider the model introduced in \secu{SecExamplesBetheDMFT}
+\ref{SecExamplesAHM} ({\tt ed\_mode=superc}), provided electron-electron interaction is set to zero and phonon parameters are properly configured.
+
+We consider the model introduced in \secu{SecExamplesBetheDMFT}
 with $U=0$ and the additional phononic and electron-phonon terms:
@@
 \end{equation}
-We consider the half-filling regime of the particle-hole symmetric Bethe lattice density of states.
-We set the half-bandwidth as our energy unit $D=1$ and introduced the electron-phonon coupling $\lambda = \tfrac{2g^2}{\omega_0D}$.
-The iterative DMFT solution algorithm follows the same principles
-illustrated in the previous sections.
-
-\paragraph{Results}
+We focus on the half-filling regime of the particle-hole symmetric Bethe lattice DOS.
+We set the half-bandwidth as our energy unit $D=1$ and introduced the electron-phonon coupling $\lambda = \tfrac{2g^2}{\omega_0}$.
+The iterative DMFT solution algorithm follows the same principles illustrated in the previous sections.
+
+\paragraph{Results.}
 In the following we discuss the adiabatic ($\omega_0\to0$) to
@@
 the uniform solution of the Holstein model at constant coupling $\lambda=1.0$.
-
+%
 In the anti-adiabatic limit, the Holstein interaction takes a
@@
 In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
-enters a Bipolaronic Insulating phase~\cite{Capone2006PRB} for our
-choice of the coupling.
+enters a Bipolaronic Insulating phase for our
+choice of the coupling~\cite{Capone2006PRB}.
 
@@
 phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
-the behavior for the normal solution ({\tt ed\_mode=normal}) against the superconductive
+the behavior for the normal  ({\tt ed\_mode=normal}) against the superconductive
 solution ({\tt ed\_mode=superc}). Our results capture the whole
@@
 phase in the Holstein model, we report the evolution of the anomalous order
-parameter $\phi$ in the adiabatic to anti-adiabatic crossover (panel (B) of \figu{figEx5}).
+parameter $\phi$ in the adiabatic to anti-adiabatic crossover, see panel (B) of \figu{figEx5}.
 The DMFT results obtained with \NAME show a rapid increase in the
@@
 The interaction term of the impurity Hamiltonian is in the Hubbard-Kanamori
-form (\equ{Hint}).
+form of \equ{Hint}.
 
@@
 consider an impurity atom with three correlated orbitals and two bath states
-per each impurity orbital. This information must be encoded in the fundamental
+per each impurity orbital, which corresponds to {\tt bath\_type=normal} in \NAME. This information must be encoded in the fundamental
 set objects that are later used to construct the solver.
@@
 Bernevig-Hughes-Zhang (BHZ).
-As shown in Ref.~\onlinecite{AmaricciPRB2022}, at moderate
+As shown in Ref.~\cite{Amaricci2023PR}, at moderate
 interactions this model admits an excitonic phase in which opposite
-orbital electrons and holes across the band gap bind into a coherent phase.
+orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason,Amaricci2023PR,Giuli2023PRB}
 
@@
 lattice interacting through a Hubbard-Kanamori term and describing
-a quantum spin Hall insulator.
+a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Konig2007S,Hasan2010RMPa,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PR,Paoletti2024PR}.
 We consider a suitable matrix basis in terms of the Dirac
@@
 where $\psi_{k}=[c_{1\uparrow k}, c_{2\uparrow k},
-c_{1\downarrow k}, c_{2\downarrow k} ]$ is the spinor collecting
+c_{1\downarrow k}, c_{2\downarrow k} ]^T$ is the spinor collecting
 annihilation operator $c_{a\sigma k}$ destroying an electron at
@@
 Kanamori interaction. We neglect the pair-hopping and spin-flip purely
-for numerical reasons.
-
-In the non-interacting regime, i.e. $U=J=0$ this model describes a
+for numerical reasons \cite{Amaricci2022CPC}. 
+%
+In the non-interacting regime this model describes a
 quantum spin Hall insulator (QSHI) for $M<4t$ and a trivial Band
 Insulator (BI) for $M>4t$.
-The transition point at $M=4t$ describes the formation of a gapless
-Dirac state with linear band crossing at $k=[0,0]$.
-
-The code implementation follows the same guidelines discussed above
-for the other examples. There are two specific modifications required
-from the user. The first is to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone in
-order to obtain the local interacting Green's function, used in the
-implementation of the self-consistency conditions:
-$\GG^{-1}=G_\mathrm{loc}^{-1}+\Sigma$, with 
+The transition point at $M=4t$ describes the formation of a gapless Dirac state at  $k=[0,0]$.
+
+The code implementation follows the same guidelines discussed above for the other examples. The user is required to generate the Hamiltonian $H(k)$ on a discretized Brillouin zone. 
+This is employed to evaluate the local interacting Green's function:
 $$
@@
 $$
-where $\z\in\CCC$  and $\Sigma(z)$ is the self-energy function obtained from the DMFT
-solution of the proble.  $N_k$ is the number of $k$-points. 
-The second is to  construct the ``renormalized'' topological
-Hamiltonian
+entering in self-consistency conditions $\GG^{-1}=G_\mathrm{loc}^{-1}+\Sigma$. 
+Here  $\z\in\CCC$, $N_k$ is the number of $k$-points   and $\Sigma(z)$ is the self-energy matrix  obtained from the DMFT solution of the problem.  
+Moreover, the $H(k)$ is used to  construct the {\it renormalized} topological Hamiltonian \cite{Wang2010PRL,Wang2012PRX,Blason2023PRB}
 $$
@@
 $$
-where $Z$ is the renormalization constant. $H_\mathrm{top}$ describes the
-low-energy properties of many-body problem and can be used to obtain a 
-topological characterization of the interacting system.
+where $Z$ is the renormalization constant matrix. The matrix $H_\mathrm{top}$ describes the
+low-energy properties of the many-body solution andcan be used to determine the characterize the topological nature of the interacting system  \cite{Gurarie2011PRB,Wang2012PRX,Wagner2023NC,Blason2023PRB,Bau2024PRB}.
 
@@
 $\vec{E}=[E_0,E_x,E_y,E_z]$, where $E_a=\langle\psi^\dagger
-\Gamma_{a1}\psi \rangle$.
+\Gamma_{a1}\psi \rangle$ \cite{Budich2014,Kunes2014PRB,Kaneko2015JOPCS,Kunes2015JOPCM,Knolle2017PRL,Guerci2019PRM,Geffroy2019PRL,Mazza2020PRL,De-Palo2023PRB}.
+
 The first component $E_0$ describes the singlet excitonic state,
 whereas the remaining ones correspond to the triplet states with
-different spin orientation.   
+different spin orientation \cite{Blason,Amaricci2023PR}.   
 The analysis of the strong-coupling regime as well as impurity
@@
 instability to an in-plane spin-triplet exciton phase, i.e. with $E_x$
-and/or $E_y$ different from zero.
+and/or $E_y$ different from zero, see \cite{Amaricci2023PR}.
 Interestingly, this state breaks several symmetries including
@@
 
-Thus, here we illustrate the DMFT solution of the excitonic phase as a way to
-illustrate the ability of \NAME to capture matter phases with lowered
-spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
+Here we showcase the DMFT description of the excitonic phase in the interacting BHZ model as a way to
+illustrate the \NAME ability to capture matter phases with lowered spin-symmetry ({\tt ed\_mode=nonsu2}) and the use of {\tt
   bath\_type=replica}.
+
+The initial part of the code implementation is a simple generalization of the previously discussed cases. 
+The next non-trivial steps are: i) construct the lattice Hamiltonian $H(k)$ and the corresponding local part $H_\mathrm{loc}$, which determines the impurity properties, and ii) construct a matrix basis representation for the replica bath.
+These two steps can be implemented as follows:
+
+%${\color{comment-color}  }
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
-   !> Set $H_\mathrm{loc}$
+   !> Set $\smash{{\color{comment-color}H_\mathrm{loc}}}$ 
    allocate(Hloc(Nso,Nso))
@@
    where(abs(dreal(Hloc))<1d-6)Hloc=zero
+
+   !EDIpack: set the impurity Hamiltonian: $\smash{{\color{comment-color}H_\mathrm{loc}\to h^0}}$
    call ed_set_hloc(Hloc)
-   !> Setup the replica bath basis:
+
+   !EDIpack: set the replica bath matrix basis $\smash{{\color{comment-color}  \vec{\Gamma}}}$ and $\smash{{\color{comment-color}  \vec{\lambda}}}$
+   !Here Nsym=4.
+   !Build the basis and init the variational parameters:
    allocate(lambdasym_vector(Nbath,4))
@@
    Hsym_basis(:,:,4)=Gamma11 ;lambdasym_vector(:,4)=-sb_field
-   !> Set the replica bath
+
+   !EDIpack: set the basis and initial values of $\smash{{\color{comment-color}  \vec{\lambda}}}$
    call ed_set_Hreplica(Hsym_basis,lambdasym_vector)
-   !> Get bath dimension and allocate user bath to this size
-   Nb=ed_get_bath_dimension(4)   !There are 4 symmetries
+
+   !EDIpack: get bath dimension and allocate user bath to this size
+   Nb=ed_get_bath_dimension(4)
    allocate(Bath(Nb))
-   !
-   !> Initialize the ED solver (bath is guessed or read from file) 
+
+   !EDIpack: Initialize the ED solver
    call ed_init_solver(bath)
@@
 possibility of forming an excitonic ordered phase, the replica bath
-is constructed out of the matrix basis with 4 distinct elements
-$\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which
-are proportional, respectively, to the mass term, the exciton singlet
+is constructed out of a matrix basis with 4 distinct elements
+$\Gamma_{03}$, $\Gamma_{01}$, $\Gamma_{31}$, $\Gamma_{11}$ which are proportional, respectively, to the mass term, the exciton singlet
 $E_0$, the exciton triplet along easy-axis $E_z$ and in-plane
-$E_x$ (we assume $E_y=0$ leveraging on residual $U(1)$ in-plane
-symmetry). 
-%
-In the following we consider the case of $M=1$, which corresponds to a
-QSHI in the non-interacting limit and $J/U=0.25$.
+$E_x$ (we assume $E_y=0$ leveraging on residual $U(1)$ in-plane symmetry). 
+In the following we consider the case of $M=1$, which corresponds to a QSHI in the non-interacting limit and $J/U=0.25$.
 The implementation is nearly identical to the cases discussed above and
@@
      iloop=iloop+1
-     !> Solve the impurity problem, retrieve $\Sigma(i\omega)$
+
+     !EDIpack: Solve the impurity problem
      call ed_solve(bath)
+
+     !EDIpack: Retrieve  ${\color{comment-color} \Sigma(i\omega)}$
      call ed_get_sigma(Smats,axis='mats')
-     !> Get $G_\mathrm{loc}$ using $\color{comment-color}\mathrm{DMFTtools}$
+
+     !Get $\color{comment-color}G_\mathrm{loc}}$ using $\color{comment-color}\mathrm{DMFTtools}$
      call get_gloc(Hk,Gmats,Smats,axis='m')
-     !> Update the Weiss field ${\color{comment-color}\GG^{-1}=G^{-1}_\mathrm{loc}+\Sigma}$ +  Linear mixing: using $\color{comment-color}\mathrm{DMFTtools}$
+
+     !Update the Weiss field (self-consistency) using $\color{comment-color}\mathrm{DMFTtools}$
      call dmft_self_consistency(Gmats,Smats,Weiss)
+
+     !Linear mixing the Weiss fields
      if(iloop>1)Weiss = wmixing*Weiss + (1.d0-wmixing)*Weiss_;Weiss_=Weiss
-     !> Fit to updated the bath
+
+     !EDIpack: Fit to update the bath
      call ed_chi2_fitgf(Weiss,bath,ispin=1)
+
      !Check convergence: using $\color{comment-color}\mathrm{DMFTtools}$
@@
 %
-The main effect of the interaction on the topological properties can be captured by the renormalized mass term $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. The
-real part of the self-energy being proportional to $\Gamma_{03}$
-corrects the mass term with respect to its bare value. To leading
-order this correction is proportional to $\tfrac{U-5J}{4}\langle
+The main effect of the interaction on the topological properties is contained in the mass term renormalization.  
+The real part of the self-energy being proportional to $\Gamma_{03}$
+corrects the mass term with respect to its bare value: $M_\mathrm{eff}=M+\tfrac{1}{4}\Tr{\Re\Sigma(i\omega\to0)}$. 
+To leading order (mean-field) this correction is proportional to $\tfrac{U-5J}{4}\langle
 \hat{T}_z\rangle$. So, for our choice of parameters, the effect of
-interaction would be to reduce the (effective) mass term and thus
-reducing the topological band gap. In the strong-coupling limit the
-two orbitals get populated by one electron per site, reaching the
+interaction would be to effectively reduce the mass term. Thus, in the strong-coupling limit the two orbitals get populated by one electron per site, reaching the
 conditions for the formation of a Mott insulating state.
-As reported in panel (A) of \figu{figEx4}, at intermediate coupling,
+This effect is highlighted in panel (A) of \figu{figEx4}, where we report the progressive reduction of the
+orbital polarization  $\langle T_z\rangle$ and, thus, of the effective mass.
+
+In the same panel (A), we show that at intermediate coupling 
 the DMFT solution features the formation of a
@@
 E_0\rangle=\langle E_z\rangle=0$.
-Unlike the static mean-field description~\cite{Blason}, the
+
+Unlike the static mean-field description \cite{Blason}, the
 transition from the QSHI topological state to the Excitonic Insulator 
-(EI) becomes of first-order in the presence of the dynamical fluctuations~\cite{Continentino,Paoletti,BellomiaKMH} contained in DMFT. On the
-other hand, the EI continuously evolves into a Mott Insulator (MI)
+(EI) becomes of first-order upon including the local dynamical fluctuations \cite{Paoletti2024PR,BellomiaKMH} contained in DMFT. 
+The EI continuously evolves into a Mott Insulator (MI)
 for larger interaction (neglecting for simplicity any 
@@
 regime).
-In the same panel, we report the evolution of
-$\langle T_z\rangle$ to illustrate the progressive reduction of the
-orbital polarization and, thus, of the effective mass.
+The \NAME solution of this model nicely captures the two transitions which involve breaking of the spin symmetry group SU(2).
 
@@
 $U$ placing the solution, respectively, in the QSHI, the EI and the MI.
+
 The correlated QSHI is characterized by the presence of an 
@@
 
-To complete the overview of \NAME's capabilities, we consider another
-model for interacting quantum spin-Hall insulators defined on the honeycomb lattice, with two inequivalent sites in the unit cell.
+To complete the overview of \NAME features, we consider another
+model of interacting quantum spin-Hall insulator defined on the honeycomb lattice, with two inequivalent sites in the unit cell.
 Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as
@@
 \end{align}
-where ${u} = (3/2, \sqrt{3}/2)$, and ${v} = (3/2, -\sqrt{3}/2)$
+where ${u} = (3a/2, \sqrt{3}a/2)$, and ${v} = (3a/2, -\sqrt{3}a/2)$ 
 are suitable basis vectors for the honeycomb lattice, $t$ is the
@@
 The spinorial $4\times4$ matrices $\Gamma_{a\ell} = \sigma_a\otimes\tau_\ell$ are 
-defined in terms of $\sigma_a$ and $\tau_\ell$ Pauli matrices, respectively 
-referred to spin and sublattice degrees of freedom, with the convention that 
-$\sigma_0$ and $\tau_0$ are $2\times2$ identity matrices.
-
-To investigate the effects of electron-electron repulsion on the
-Kane-Mele model, we include a local interaction
-leading to the Kane-Mele-Hubbard Hamiltonian \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}
+defined in terms of Pauli matrices $\sigma_a$, $\tau_\ell$ referred, respectively 
+to spin and sublattice degrees of freedom.
+% , with the convention that 
+% $\sigma_0$ and $\tau_0$ are $2\times2$ identity matrices.
+To investigate the effects of electron-electron repulsion we consider a local Hubbard term \cite{Hohenadler2013ROPIP,Rachel2018ROPIP}:
 \begin{equation}
-    H_\mathrm{KMH} = H_\mathrm{KM} 
+    H = H_\mathrm{KM} 
     + U\sum_{i}\Biggl[
@@
 The essential features of the ground state phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
-For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to relatively high Hubbard repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio\footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
+For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to large repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio\footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
 at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
-With a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.
+For a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.
 Furthermore, the long-range ordering
@@
       !
-      !> Update local Weiss fields ${\color{comment-color}\GG^{-1}_0 = G_{loc} + \Sigma}$ :using ${\color{comment-color}\mathrm{DMFTtools}}$
+      !> Update local Weiss fields $\smash{{\color{comment-color}\GG^{-1}_0 = G^{-1}_{loc} + \Sigma}}$: using ${\color{comment-color}\mathrm{DMFTtools}}$
       call dmft_self_consistency(Gmats,Smats,Weiss)
@@
 
-We observe that, after convergence is reached, we can perform some 
-post-processing to get quantities of interest, e.g. computing the 
-lattice kinetic energy (as implemented in the \texttt{dmft\_tools} 
+After convergence is reached, we evaluate some quantities of interest, e.g. computing the 
+lattice kinetic energy (as implemented in the \texttt{DMFTtools} 
 library). The potential energy, as well as the AFM order parameters
-and most impurity observables are automatically computed by \NAME, 
-and saved with an appropriate inequivalent-impurity filename suffix 
-by the EDIpack2ineq layer.
-
-Hence, we can readily evaluate the total energy of both the AFM$_\perp$
-and AFM$_\parallel$ calculations and compare them to establish which 
-is favored as the ground state of the system. In \figu{fig:KMenergy}(a)
-we show results for the energy difference $E_\parallel-E_\perp$ across
-a wide range of $U/t$ and $\lambda_\mathrm{so}$ values. To assess the
+and impurity observables are automatically computed by \NAME, 
+and saved to files with the appropriate inequivalent-impurity label.
+
+We evaluate the total energy of both the AFM$_\perp$
+and AFM$_\parallel$ calculations and compare them to establish which  is favored as the ground state of the system. In \figu{fig:KMenergy}(A)
+we show results for the energy difference $E_\parallel-E_\perp$ across a wide range of $U/t$ and $\lambda_\mathrm{so}$ values. To assess the
 degree of accuracy of our total energy calculation, we report in
-\figu{fig:KMenergy}(b) a $\lambda_\mathrm{so}=0$ benchmark against
+\figu{fig:KMenergy}(B) a $\lambda_\mathrm{so}=0$ benchmark against
 Hartree-Fock (simple static mean-field, but inherently variational), 
@@
 \begin{figure}
-\hspace{1cm} (a) \hspace{7.25cm} (b)\\
+\hspace{1cm} (A) \hspace{7.25cm} (B)\\
     \includegraphics[width=0.47\linewidth,trim={0 0 0 5mm},clip]{figures/KMH_energy.pdf}\hfill
     \includegraphics[width=0.45\linewidth]{figures/benchEnergy_honey.pdf}\\
-    \caption{In panel (a) we report the total energy difference between 
+    \caption{In panel (A) we report the total energy difference between 
     the in-plane and the
@@
 The capabilities of the EDIpack2ineq layer go well beyond the
-simple case of a two-site unit cell. We can readily adapt the
-code to deal with nanoscopic systems such as hexagonal flakes
-\cite{Valli2016PRB,Valli2018NL}, by building a
+simple case of a two-site unit cell.
+Bulding on the previous example, we can readily adapt the calculation to deal with a nanoscopic~\cite{Amaricci2014PRA} system with $N_\mathrm{ineq}$ inequivalent atoms, such as hexagonal flakes
+\cite{Valli2016PRB,Valli2018NL}.
+For we consider a 
 $N_\mathrm{ineq}\times N_\mathrm{ineq}$ local Hamiltonian 
@@
 the self-consistent equations with a trivial single momentum 
-$k=0$. With respect to the infinite lattice, it is expected that
-the system develops an inhomogeneous magnetization, so the number
-of impurity models to solve cannot be halved by imposing the usual
-Néel symmetry. Some lowered point symmetry can be found, but a 
-safer approach of solving all the $N_\mathrm{ineq}$ impurity models
-leads to good results, with fair control of spatial numerical noise.
+$k=0$. In this configuration the system develops an inhomogeneous magnetization, so that in general no particular lattice symmetry group, e.g. N\'eel, can be exploited. 
+% Some lowered point symmetry can be found, but a 
+% safer approach of solving all the $N_\mathrm{ineq}$ impurity models
+% leads to good results, with fair control of spatial numerical noise.
 
@@
 \end{equation}
-in the basis of the \emph{natural} spin-orbitals, whose occupation numbers
+in the basis of the {\it natural} spin-orbitals, whose occupation numbers
 are given by $n_{i,\rightarrow}$ and $n_{i,\leftarrow}$.
 
-As extensively discussed in \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr},
+As  discussed in \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr},
 by defining the spin traces of $\rho^\mathrm{imp}$, as

### 2025-05-31 06_conclusions_acknowledgement_appendix.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
   Monicelli} compiler {\tt mcc}, which statically links LLVM.
+
 We believe the discourse flow of this language is best captured by 
-illustrating its features and \NAME interface via a paraphrase of the original supercazzola, an epic dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
+illustrating its features and \NAME interface via a paraphrase of the original supercazzola, an epic non-sensical dialogue between a traffic policeman (V), count Mascetti (M) and G. Perozzi (P) (see
 \href{https://it.wikipedia.org/wiki/Supercazzola#Origine}{it.wikipedia.org/wiki/Supercazzola}

### 2025-05-31 01_intro.tex
AA: fixed bib issues. Going local to update intro + conclusions.

@@
 The library builds on the foundations of
-its predecessor~\cite{amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
+its predecessor~\cite{Amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
 The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.

### 2025-06-01 01_intro.tex
GB wide pass on the full text

@@
 
-Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012_DMET} and Gutzwiller approximation (GA)~\cite{Lanata2015_GA}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
+Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012_DMET} and the Gutzwiller approximation (GA)~\cite{Lanata2015_GA}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
 The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.

### 2025-06-01 03_edipack2.tex
AA: Version 2.0 Iterated full text but intro and conclusions. Added a lot of references. Fixed (almost) all comments. Updated figAHM.
taking a pause before attacking intro  + conclusions. 

Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>
GB wide pass on the full text

@@
 adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ARCMP}:
-\begin{equation}
+\begin{equation}\label{Hint}
   \begin{split}
@@
 \end{split}
-\label{Hint}
 \end{equation}
@@
 \begin{lstlisting}[style=fstyle,numbers=none]
-!sparse row: contains bath state values for each impurity key 
+!Sparse row: contains bath state values for each impurity key 
 type sparse_row
@@
 end type sparse_row
-!Sparse Map: array of sparse rows 
+!Sparse map: array of sparse rows 
 type sparse_map
-   type(sparse_row),dimension(:),pointer :: imp_state     !Key: impurity states
-   integer                               :: Nimp_state    !Key upper limit 
+   type(sparse_row),dimension(:),pointer :: imp_state     !key: impurity states
+   integer                               :: Nimp_state    !key upper limit 
    logical                               :: status=.false.!allocation status
@@
 The number of independent bath parameters to optimize is either 
-$N_\mathrm{params} = (N_\mathrm{sym}+1)N_\mathrm{bath}$ for {\tt bath\_type}={\bf replica} or 
-$N_\mathrm{params} = (N_\mathrm{sym}+N_\a N_\s)N_\mathrm{bath}$ for {\tt bath\_type}={\bf general}.
+$N_\mathrm{param} = (N_\mathrm{sym}+1)N_\mathrm{bath}$ for {\tt bath\_type}={\bf replica} or 
+$N_\mathrm{param} = (N_\mathrm{sym}+N_\a N_\s)N_\mathrm{bath}$ for {\tt bath\_type}={\bf general}.
 
@@
 {\tt ED\_BATH\_DIM}. The function {\tt ed\_get\_bath\_dimension} 
-calculates the required dimension $N_\mathrm{params}$ for user-allocated bath 
+calculates the required dimension $N_\mathrm{param}$ for user-allocated bath 
 arrays, ensuring they contain exactly the necessary number of 
@@
 
-The following table summarizes the total number of parameters $N_\mathrm{params}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:
+The following table summarizes the total number of parameters $N_\mathrm{param}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:
 
@@
  \hline     
- $N_\mathrm{params}$ & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
+ $N_\mathrm{param}$ & {\bf normal} & {\bf hybrid} & {\bf replica} & {\bf general}\\
  \hline 
@@
  $(N_\mathrm{sym}+1)N_\mathrm{bath}$ & 
- $(N_\mathrm{sym}+N_\a)N_\mathrm{bath}$\\
+ $(N_\mathrm{sym}+N_\a N_\sigma)N_\mathrm{bath}$\\
  \hline

### 2025-06-01 05_examples.tex
AA: fixed bib issues. Going local to update intro + conclusions.
GB wide pass on the full text

@@
    !...
-   !Construct Bethe DOS using SciFortran functions
+   !Construct Bethe DOS using SciFortran
    allocate(Ebands(Le),Dbands(Le))
@@
 
-\subsubsection{Finite temperature solution (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
+\subsubsection{Finite temperature (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
 To demonstrate the usage of the W2Dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
@@
       \textbf{The BCS to BEC crossover.}
-      (a) Evolution of the spectral functions
+      (A) Evolution of the spectral functions
       $-\Im{G_\mathrm{loc}(\omega)}/\pi$ as a function of increasing
       attraction $U$. 
-      (b) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
+      (B) The order parameter $\phi=\langle c_\up c_\dw\rangle$ as a
       function of the attraction $U$. Data for BCS (gray) is compared
@@
       attraction $U$ across the BCS-BEC crossover. 
-      (e) Superconducting order
+      (C) Superconducting order
       parameter $\phi$ as a function of temperature across the
@@
 computationally challenging. In the opposite, strong-coupling, limit 
-$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the mean-field result 
+$\phi$ saturates at its theoretical maximum of $\phi \rightarrow 1/2$. The comparison with the BCS mean-field result 
 (gray line) reveals the effect of local dynamical fluctuations, which  slightly suppress the order parameter, particularly in the intermediate regime. 
@@
 significant dynamical effects, hence a more correlated superconducting state.
-Our results show that the DMFT solution significantly departs from the MF picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
+Our results show that the DMFT solution significantly departs from the BCS picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
 % A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D).
@@
 We stress that  the code
-implementation for this specific case is essentially identical to the listing reported in the sections
+implementation for this specific case is essentially identical to the listings reported in the sections
 \ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
@@
       square) and $6.00$ (red diamond) capturing, respectively, the
-      QSHI (B), the Excitonic Insulator (C) and the Mott Insulator
-      (D). 
+      QSHI \textbf{\textit{(B)}}, the Excitonic Insulator \textbf{\textit{(C)}} and the Mott Insulator
+      \textbf{\textit{(D)}}. 
     }
@@
 
-     !Get $\color{comment-color}G_\mathrm{loc}}$ using $\color{comment-color}\mathrm{DMFTtools}$
+     !Get $\color{comment-color}G_\mathrm{loc}$ using $\color{comment-color}\mathrm{DMFTtools}$
      call get_gloc(Hk,Gmats,Smats,axis='m')
@@
 $\lambda_{1,p} \equiv \epsilon_p$ as the degenerate
-bath levels that are Zeeman split by $\lambda_{2,p} \equiv m_p$, respectively in the $S_z$ and $S_x$ bases.
+bath levels that are Zeeman split by $\lambda_{2,p} \equiv m_p$, respectively in the $S_z$ and $S_x$ bases 
+(see \secu{sSecBath}).
 
@@
 After convergence is reached, we evaluate some quantities of interest, e.g. computing the 
-lattice kinetic energy (as implemented in the \texttt{DMFTtools} 
+lattice kinetic energy (as implemented in the {DMFTtools} 
 library). The potential energy, as well as the AFM order parameters
@@
 We evaluate the total energy of both the AFM$_\perp$
-and AFM$_\parallel$ calculations and compare them to establish which  is favored as the ground state of the system. In \figu{fig:KMenergy}(A)
+and AFM$_\parallel$ calculations and compare them to establish which  is favored as the ground state of the system. In \figu{fig:KMenergy}(a)
 we show results for the energy difference $E_\parallel-E_\perp$ across a wide range of $U/t$ and $\lambda_\mathrm{so}$ values. To assess the
 degree of accuracy of our total energy calculation, we report in
-\figu{fig:KMenergy}(B) a $\lambda_\mathrm{so}=0$ benchmark against
+\figu{fig:KMenergy}(b) a $\lambda_\mathrm{so}=0$ benchmark against
 Hartree-Fock (simple static mean-field, but inherently variational), 
@@
 \begin{figure}
-\hspace{1cm} (A) \hspace{7.25cm} (B)\\
+\hspace{1cm} (a) \hspace{6.5cm} (b)\\
     \includegraphics[width=0.47\linewidth,trim={0 0 0 5mm},clip]{figures/KMH_energy.pdf}\hfill
     \includegraphics[width=0.45\linewidth]{figures/benchEnergy_honey.pdf}\\
-    \caption{In panel (A) we report the total energy difference between 
+    \caption{In panel (a) we report the total energy difference between 
     the in-plane and the
@@
     In (a) the local in-plane
-    magnetization $n_{i,\rightarrow}-n_{i,\leftarrow}$. In
+    magnetization $\ibra S_x \iket = \ibra n_{i,\rightarrow}-n_{i,\leftarrow}\iket$. In
     (b) the local correlation as measured by the mutual 
     information between local in-plane spin eigenstates
-    $I(\rightarrow:\leftarrow)$ \cite{BellomiaPhD}. Both the
-    (a)-(b) panels mark the edge and "bulk" sites in lighter 
-    and darker colors, respectively.
+    $I(\rightarrow:\leftarrow)$ \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr}. 
+    Both the (a) and (b) panels mark the edge and "bulk" 
+    sites in lighter and darker colors, respectively.
     In (c) and (d) a visual representation of the given 
@@
     circles is proportional to $I(\rightarrow:\leftarrow)$, 
-    the length of the arrows to the local magnetization.
+    the length of the arrows to $\ibra S_x \iket$.
     All data are taken at $\lambda_\mathrm{so}=0.3t$ and $T=0$.}
@@
 
-\subsubsection{Kane-Mele Nanoflakes}
+\subsubsection{Kane-Mele-Hubbard model at the nanoscale}
 The capabilities of the EDIpack2ineq layer go well beyond the
@@
 \cite{Valli2016PRB,Valli2018NL}.
-For we consider a 
+We consider a 
 $N_\mathrm{ineq}\times N_\mathrm{ineq}$ local Hamiltonian 
@@
 computed from the impurity ground state as  
-$ \ibra S_x \iket = \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket$,
+$ \ibra S_x \iket = \ibra c^\dagger_{i,\up} c_{i,\dw} + c^\dagger_{i,\dw} c_{i,\up} \iket \equiv \ibra n_{i,\rightarrow} \iket - \ibra n_{i,\leftarrow} \iket$,
 so that we can define the $S_x$ spin occupation numbers as
@@
 (see \ref{sSecRDM}), once diagonalized, takes the familiar form
-\cite{XiDai2013,WalshLetter2019,BellomiaPhD,BellomiaKMH,Bellomia_intracorr} 
+\cite{Zanardi2002,XiDai2013,WalshLetter2019} 
 \begin{equation}
@@
 \end{equation}
-in the basis of the {\it natural} spin-orbitals, whose occupation numbers
+in the basis of the {\it natural} spin-orbitals
+\cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr}, 
+whose occupation numbers
 are given by $n_{i,\rightarrow}$ and $n_{i,\leftarrow}$.
-
 As  discussed in \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr},
@@
 more correlated than internal ("bulk") sites, based on the reduced
-lattice coordination, the inter-spin mutual information beautifully
-highlights in a quantitative fashion the phenomenon: the edge correlations,
+lattice coordination, the inter-spin mutual information quantifies directly the phenomenon: the edge correlations,
 marked in lighter green, are decidedly higher as long as the system 

### 2025-06-01 06_conclusions_acknowledgement_appendix.tex
GB wide pass on the full text

@@
 \section*{Acknowledgements}
-We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto~Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.
+We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto-Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, S.~Adler, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.
 
@@
 A.A. and M.C. conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library. M.C. devised the inclusion of the electron-phonon coupling. 
-A.A., M.C., L.d.M. and G.S designed additional algorithms extending functionalities of the core software.   
+A.A., M.C., L.d.M. and G.S designed additional algorithms for extended functionalities of the core software.   
 A.A., L.C., I.K., A.K., S.G. and G.B. performed the calculations, analyzed the results and prepared the data presentation in the examples.

### 2025-06-01 03_edipack2.tex
Full coloring of the iRDM/normal formulae

@@
 However, the memory footprint of $\rho$, as well as the CPU footprint 
-of the summations involved in this trace scales exponentially 
-with the system size, i.e.~$4^{N_\mathrm{s}}$, quickly becoming prohibitive.
-
+of the summations involved in the trace, scale exponentially 
+with the system size, i.e.~as $4^{N_\mathrm{s}}$, quickly becoming prohibitive.
 To overcome the issue, we implement a fast algorithm that exploits the 
@@
 This approach significantly reduces the computational cost by limiting 
-the summation to the sector size $D_\SS$ of the symmetry sector 
+the summation to the size $D_\SS$ of the symmetry sector 
 $\SS$, to which the ground state (or any eigenstate) belongs, and avoiding
 the storage of the large matrix associated with $\rho$.
-
-To efficiently manage this decomposition, we employ a 
+We employ a 
 {\tt sparse\_map} ${\cal P}$, as detailed in \secu{CodeSparseMap}. 
@@
 We denote the number of (spin-dependent) keys and values respectively
-as ${\cal D}_{i\s}$ and ${\cal D}_{b\s}$.
+as ${D}_{i\s}$ and ${D}_{b\s}$.
 The fast summation algorithm for evaluating the iRDM differs 
@@
 \ket{\vec{n}} =
-\ket{\vec{n}_\up}\otimes \ket{\vec{n}_\dw} =
-\ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}.
+\ket{{\color{xkcdRed}\vec{n}_\up}}\otimes \ket{{\color{xkcdBlue}\vec{n}_\dw}} =
+\ket{{\color{xkcdRaspberry}\vec{i}_\up}}\ket{{\color{xkcdPumpkin}\vec{b}_\up}}\otimes \ket{{\color{xkcdPurple}\vec{i}_\dw}}\ket{{\color{xkcdTeal}\vec{b}_\dw}}.
 \label{eq:decomposition_for_rdm_normal}
@@
 \rho = 
-    \sum_{i_\up=1}^{D_{i_\up}}\!
-    \sum_{p_\up=1}^{D_{p_\up}}\!
-    \sum_{i_\dw=1}^{D_{i_\dw}}\!
-    \sum_{p_\dw=1}^{D_{p_\dw}}\!
-    \sum_{j_\up=1}^{D_{j_\up}}\!
-    \sum_{q_\up=1}^{D_{q_\up}}\!
-    \sum_{j_\dw=1}^{D_{j_\dw}}\!
-    \sum_{q_\dw=1}^{D_{q_\dw}}\!
-    a_{i_\up p_\up i_\dw p_\dw}a^*_{j_\up q_\up j_\dw q_\dw}
+    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}\!
+    \sum_{{\color{xkcdPumpkin}p_\up}=1}^{D_{p_\up}}\!
+    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}\!
+    \sum_{{\color{xkcdTeal}p_\dw}=1}^{D_{p_\dw}}\!
+    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}\!
+    \sum_{{\color{xkcdPumpkin}q_\up}=1}^{D_{q_\up}}\!
+    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}\!
+    \sum_{{\color{xkcdTeal}q_\dw}=1}^{D_{q_\dw}}\!
+    a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdPumpkin}p_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdTeal}p_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdPumpkin}q_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdTeal}q_\dw}}
     % \left[
-    \ket{\vec{i}_\up}\ket{\vec{p}_\up}\!\otimes\!\ket{\vec{i}_\dw}\ket{\vec{p}_\dw}
+    \ket{{\color{xkcdRaspberry}\vec{i}_\up}}\ket{{\color{xkcdPumpkin}\vec{p}_\up}}\!\otimes\!\ket{{\color{xkcdPurple}\vec{i}_\dw}}\ket{{\color{xkcdTeal}\vec{p}_\dw}}
     %\right]
     % \left[
-    \bra{\vec{q}_\dw}\bra{\vec{j}_\dw}\!\otimes\!\bra{\vec{q}_\up}\bra{\vec{j}_\up}
+    \bra{{\color{xkcdTeal}\vec{q}_\dw}}\bra{{\color{xkcdPurple}\vec{j}_\dw}}\!\otimes\!\bra{{\color{xkcdPumpkin}\vec{q}_\up}}\bra{{\color{xkcdRaspberry}\vec{j}_\up}}
     %\right].   
 \end{equation}
-where the coefficients $a_I = a_{i_\up b_\up i_\dw b_\dw}$ are the
+where the coefficients $a_I = a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdPumpkin}b_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdTeal}b_\dw}}$ are the
 expansion coefficients of the state on the Fock basis
-$\ket{\psi} = \sum_I a_I \ket{\vec{i}_\up}\ket{\vec{b}_\up}\otimes \ket{\vec{i}_\dw}\ket{\vec{b}_\dw}$.
-
-Before proceeding further we show that in the {\bf normal} mode the iRDM is restricted to 
+$\ket{\psi} = \sum_I a_I \ket{{\color{xkcdRaspberry}{i}_\up}}\ket{{\color{xkcdPumpkin}{b}_\up}}\otimes \ket{{\color{xkcdPurple}{i}_\dw}}\ket{{\color{xkcdTeal}{b}_\dw}}$.
+Before proceeding further, we show that in the {\bf normal} mode the iRDM is restricted to 
 {spin-diagonal} blocks. This follows from the observation 
@@
   \begin{aligned}
-  \rho^\mathrm{imp} &= \Tr_{{\color{red}b_\up b_\dw}}{\rho} = 
-  \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
-  \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
-  \bra{b_\up}\otimes\bra{b_\dw}
+  \rho^\mathrm{imp} &= \Tr_{{\color{xkcdCoral}b_\up} {\color{xkcdAzure}b_\dw}}{\rho} = 
+  \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
+  \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
+  \bra{{\color{xkcdCoral}b_\up}}\otimes\bra{{\color{xkcdAzure}b_\dw}}
     \rho
-    \ket{b_\dw}\otimes\ket{b_\up}    \cr
+    \ket{{\color{xkcdAzure}b_\dw}}\otimes\ket{\color{xkcdCoral}{b_\up}}    \cr
     %
     &=
-    \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
-    \sum_{i_\up=1}^{D_{i_\up}}
-    \sum_{p_\up=1}^{D_{p_\up}}
-    \sum_{j_\up=1}^{D_{j_\up}} 
-    \sum_{q_\up=1}^{D_{q_\up}}
+    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
+    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}\!
+    \sum_{{\color{xkcdPumpkin}p_\up}=1}^{D_{p_\up}}\!
+    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}\!
+    \sum_{{\color{xkcdPumpkin}q_\up}=1}^{D_{q_\up}}\!
     \Bigg(    
-    \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
-    \sum_{i_\dw=1}^{D_{i_\dw}}
-    \sum_{p_\dw=1}^{D_{p_\dw}}
-    \sum_{j_\dw=1}^{D_{j_\dw}} 
-    \sum_{q_\dw=1}^{D_{q_\dw}}
-    C_{i,p}\,C_{j,q}\,a_{i_\up p_\up i_\dw p_\dw} a^*_{j_\up q_\up j_\dw q_\dw} \cr
+    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
+    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}\!
+    \sum_{{\color{xkcdTeal}p_\dw}=1}^{D_{p_\dw}}\!
+    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}\!
+    \sum_{{\color{xkcdTeal}q_\dw}=1}^{D_{q_\dw}}\!
+    C_{i,p}\,C_{j,q}\,a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdPumpkin}p_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdTeal}p_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdPumpkin}q_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdTeal}q_\dw}} \cr
     %
     &\qquad    
-    \langle b_\up| p_\up\rangle| i_\up\rangle\langle j_\up |\langle q_\up| b_\up\rangle   \otimes \langle b_\dw| p_\dw \rangle|i_\dw\rangle \langle j_\dw  |\langle q_\dw| b_\dw\rangle \Bigg)
+    \langle {\color{xkcdCoral}b_\up}| {\color{xkcdPumpkin}p_\up}\rangle| {\color{xkcdRaspberry}i_\up}\rangle\langle {\color{xkcdRaspberry}j_\up} |\langle {\color{xkcdPumpkin}q_\up}| {\color{xkcdCoral}b_\up}\rangle   \otimes \langle {\color{xkcdAzure}b_\dw}| {\color{xkcdTeal}p_\dw} \rangle|{\color{xkcdPurple}i_\dw}\rangle \langle {\color{xkcdPurple}j_\dw}  |\langle {\color{xkcdTeal}q_\dw}| {\color{xkcdAzure}b_\dw}\rangle \Bigg)
     \cr
@@
     \underbrace{\left(
-    \sum_{{\color{Red} b_\up=1}}^{{\color{red} D_{b_\up}}}
-    \sum_{{\color{Red} b_\dw=1}}^{{\color{red} D_{b_\dw}}}
-    a_{i_\up b_\up i_\dw b_\dw} a^*_{j_\up b_\up j_\dw b_\dw}
-    \right)}_{\rho^\mathrm{imp}_{i_\up j_\up} \otimes\, \rho^\mathrm{imp}_{i_\dw j_\dw} }
-    \ket{i_\up}\bra{j_\up}\otimes \ket{i_\dw}\bra{j_\dw},
+    \sum_{{\color{xkcdCoral} b_\up}=1}^{D_{b_\up}}
+    \sum_{{\color{xkcdAzure} b_\dw}=1}^{D_{b_\dw}}
+    a_{{\color{xkcdRaspberry}i_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}i_\dw} {\color{xkcdAzure}b_\dw}}a^*_{{\color{xkcdRaspberry}j_\up} {\color{xkcdCoral}b_\up} {\color{xkcdPurple}j_\dw} {\color{xkcdAzure}b_\dw}}
+    \right)}_{\rho^\mathrm{imp}_{{\color{xkcdRaspberry}i_\up j_\up}} \otimes\, \rho^\mathrm{imp}_{{\color{xkcdPurple}i_\dw j_\dw}} }
+    \ket{{\color{xkcdRaspberry}i_\up}}\bra{{\color{xkcdRaspberry}j_\up}}\otimes \ket{{\color{xkcdPurple}i_\dw}}\bra{{\color{xkcdPurple}j_\dw}},
   \end{aligned}
@@
 
-Notably, the factors $C_{i,b}$, which account for the potential 
-fermionic sign from reordering bath and impurity components, are 
+Notably, the factors $C_{i,b}$, which account for the 
+fermionic sign associated to swapping bath and impurity components, are 
 trivially 1 due to the absence of cross-spin interference in this 

### 2025-06-01 05_examples.tex
Full coloring of the iRDM/normal formulae

@@
 where $Z$ is the renormalization constant matrix. The matrix $H_\mathrm{top}$ describes the
-low-energy properties of the many-body solution andcan be used to determine the characterize the topological nature of the interacting system  \cite{Gurarie2011PRB,Wang2012PRX,Wagner2023NC,Blason2023PRB,Bau2024PRB}.
+low-energy properties of the many-body solution and can be used to characterize the topological nature of the interacting system  \cite{Gurarie2011PRB,Wang2012PRX,Wagner2023NC,Blason2023PRB,Bau2024PRB}.
 
@@
 \begin{equation}
-    H = H_\mathrm{KM} 
+    H_\mathrm{KMH}  = H_\mathrm{KM} 
     + U\sum_{i}\Biggl[
@@
     $I(\rightarrow:\leftarrow)$ \cite{BellomiaPhD,BellomiaKMH,Bellomia_intracorr}. 
-    Both the (a) and (b) panels mark the edge and "bulk" 
+    Both the (a) and (b) panels mark the edge and ``bulk'' 
     sites in lighter and darker colors, respectively.
@@
 simple case of a two-site unit cell.
-Bulding on the previous example, we can readily adapt the calculation to deal with a nanoscopic~\cite{Amaricci2014PRA} system with $N_\mathrm{ineq}$ inequivalent atoms, such as hexagonal flakes
+Building on the previous example, we can readily adapt the calculation to deal with a nanoscopic~\cite{Amaricci2014PRA} system with $N_\mathrm{ineq}$ inequivalent atoms, such as hexagonal flakes
 \cite{Valli2016PRB,Valli2018NL}.
@@
 finite system. While it is usually assumed that edge sites must be
-more correlated than internal ("bulk") sites, based on the reduced
+more correlated than internal (``bulk'') sites, based on the reduced
 lattice coordination, the inter-spin mutual information quantifies directly the phenomenon: the edge correlations,

### 2025-06-01 02_install.tex
Listing overhaul Fine tune colors New keywords (python)

@@
  \hline
-  {\bf Option}               & {\bf Scope} & {\bf Value} \\
+  {\bf Option}               & {\bf Scope} & {\bf Value (default in {\color{xkcdEmerald}green})}\\
   \hline
-  -D{\bf PREFIX}          & Install directory  & {\color{red} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{red}False}\\
-  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{red}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{red}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{red}RELEASE}/TESTING/DEBUG \\
+  -D{\bf PREFIX}          & Install directory  & {\color{xkcdEmerald} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
+  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{xkcdEmerald}False}\\
+  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{xkcdEmerald}True}/{False}\\
+  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}/{False}\\ 
+  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}/TESTING/DEBUG \\
  \hline

### 2025-06-01 05_examples.tex
Listing overhaul Fine tune colors New keywords (python)

@@
     #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
-    Gmats = get_gloc(wm*1j       ,ed.xmu,HkNambu,Smats,axis="m")
+    Gmats = get_gloc(wm*1j,ed.xmu,HkNambu,Smats,axis="m")
     Weiss = dmft_weiss_field(Gmats,Smats)

### 2025-06-01 01_intro.tex
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

--- 2025-05-31 01_intro.tex
@@
 
-Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012_DMET} and Gutzwiller approximation (GA)~\cite{Lanata2015_GA}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
+Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012PRL} and the Gutzwiller approximation (GA)~\cite{Lanata2015PRX}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
 The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.
@@
 \fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility.
-Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017_EDLib} and the more recent XDiag~\cite{wietek2025_xdiag}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015_pomerol}; and for fermions coupled with spins, such as H$\Phi$~\cite{KAWAMURA2017_Hphi,Ido2024_Hphiupdate}.
+Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017} and the more recent XDiag~\cite{Wietek2025}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015}; and for fermions coupled with spins, such as H$\Phi$~\cite{Kawamura2017CPC,Ido2024CPC}.
 

### 2025-06-01 03_edipack2.tex
Amend ad4d7cc630a5fc8fa6d78971c7b7e0a3bb68d447 I forgot 4 indices...
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

@@
 interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PR,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
+$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PRB,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
 The last two terms are, respectively, the spin-exchange ($J_X$) and
@@
 %
-For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model\cite{Holstein1959APNY}.
-For two-orbital models we included also the two Jahn-Teller modes\cite{Capone2010ACMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.
-
-For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRB,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRB_ph,Paci2006PRB}.
+For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model~\cite{Holstein1959APNY}.
+For two-orbital models we included also the two Jahn-Teller modes~\cite{Capone2010AICMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$~\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.
+
+For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling~\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction~\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}.
 The larger the number of excited phonons in the ground state, the larger the cutoff.
-For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime\cite{Capone2003PRL}.
+For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime~\cite{Capone2003PRL}.
 Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
@@
 $\vec{L}\cdot\vec{S}$, in-plane spin ordering~\cite{BellomiaKMH} or
-in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
+in-plane spin-triplet exciton condensation~\cite{Amaricci2023PRB,Blason2020PRB}.  
 \end{itemize}
@@
 c^\dagger_{\a\s}\tau^i_{\s\s'}c_{\b\s'}$, where $i=0$ represents the
-spin-singlet exciton \cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton \cite{Amaricci2023_excitons}.
+spin-singlet exciton \cite{Giuli2023PRB}, and $i=x,y,z$  correspond to the spin-triplet exciton \cite{Amaricci2023PRB}.
 
@@
 extending the algorithm initially proposed in 
-Ref.~\onlinecite{BellomiaPhD,Bellomia2024PR}, to support the analysis of entanglement 
+Ref.~\cite{BellomiaPhD,Bellomia2024PRB}, to support the analysis of entanglement 
 properties of quantum impurities for any value of {\tt ed\_mode}.
@@
 &=
-    \sum_{i_\up=1}^{D_{i_\up}}
-    \sum_{j_\up=1}^{D_{j_\up}}
-    \sum_{i_\dw=1}^{D_{i_\dw}}
-    \sum_{j_\dw=1}^{D_{j_\dw}}
+    \sum_{{\color{xkcdRaspberry}i_\up}=1}^{D_{i_\up}}
+    \sum_{{\color{xkcdRaspberry}j_\up}=1}^{D_{j_\up}}
+    \sum_{{\color{xkcdPurple}i_\dw}=1}^{D_{i_\dw}}
+    \sum_{{\color{xkcdPurple}j_\dw}=1}^{D_{j_\dw}}
     \underbrace{\left(
@@
 Several algorithms have been proposed for this optimization 
-step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto_Bath_ASCI-DMFT}, each with strengths suited 
+step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto-Zaera2020PRB}, each with strengths suited 
 to different physical contexts. To maintain flexibility in \NAME, 
@@
 While different optimization methods have been developed for 
-truncated algorithms, e.g. sCI~\cite{Mejuto_Bath_ASCI-DMFT} or DMRG~\cite{Bauernfeind2017PRX}, 
+truncated algorithms, e.g. sCI~\cite{Mejuto-Zaera2020PRB} or DMRG~\cite{Bauernfeind2017PRX}, 
 which handle systems with a 

### 2025-06-01 04_cbinding.tex
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

@@
 The recent growing availability of state-of-the-art software dedicated
-to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Wallerberger2019CPC,Mejuto_Bath_ASCI-DMFT}
+to the solution of quantum impurity problems using different methods \cite{Bulla2008RMP,Parcollet2015CPC,Seth2016CPC,Bauernfeind2017PRX,Ganahl2015PRB,Wallerberger2019CPC,Mejuto-Zaera2020PRB}
 poses a challenge to test accuracy and reliability of the

### 2025-06-01 05_examples.tex
Updated Bibliobraphy with correct naming conventions <Author><Year><JournalAcronym>[a-z]

@@
 Bernevig-Hughes-Zhang (BHZ).
-As shown in Ref.~\cite{Amaricci2023PR}, at moderate
+As shown in Ref.~\cite{Amaricci2023PRB}, at moderate
 interactions this model admits an excitonic phase in which opposite
-orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason,Amaricci2023PR,Giuli2023PRB}
+orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
 
@@
 lattice interacting through a Hubbard-Kanamori term and describing
-a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Konig2007S,Hasan2010RMPa,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PR,Paoletti2024PR}.
+a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Konig2007S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
 We consider a suitable matrix basis in terms of the Dirac
@@
 $\vec{E}=[E_0,E_x,E_y,E_z]$, where $E_a=\langle\psi^\dagger
-\Gamma_{a1}\psi \rangle$ \cite{Budich2014,Kunes2014PRB,Kaneko2015JOPCS,Kunes2015JOPCM,Knolle2017PRL,Guerci2019PRM,Geffroy2019PRL,Mazza2020PRL,De-Palo2023PRB}.
+\Gamma_{a1}\psi \rangle$ \cite{Budich2014PRL,Kunes2014PRB,Kaneko2015JOPCS,Kunes2015JOPCM,Knolle2017PRL,Guerci2019PRM,Geffroy2019PRL,Mazza2020PRL,De-Palo2023PRB}.
 
@@
 whereas the remaining ones correspond to the triplet states with
-different spin orientation \cite{Blason,Amaricci2023PR}.   
+different spin orientation \cite{Blason2020PRB,Amaricci2023PRB}.   
 The analysis of the strong-coupling regime as well as impurity
@@
 instability to an in-plane spin-triplet exciton phase, i.e. with $E_x$
-and/or $E_y$ different from zero, see \cite{Amaricci2023PR}.
+and/or $E_y$ different from zero, see \cite{Amaricci2023PRB}.
 Interestingly, this state breaks several symmetries including
@@
 
-Unlike the static mean-field description \cite{Blason}, the
+Unlike the static mean-field description \cite{Blason2020PRB}, the
 transition from the QSHI topological state to the Excitonic Insulator 
-(EI) becomes of first-order upon including the local dynamical fluctuations \cite{Paoletti2024PR,BellomiaKMH} contained in DMFT. 
+(EI) becomes of first-order upon including the local dynamical fluctuations \cite{Paoletti2024PRB,BellomiaKMH} contained in DMFT. 
 The EI continuously evolves into a Mott Insulator (MI)
@@
 For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to large repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio\footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
-at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{SorellaTosatti92,Graphene_RMP}.}.
+at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{Sorella1992ELE,Castro-Neto2009RMP}.}.
 For a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.
@@
 eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
-\cite{3dXY_KMH}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and
+\cite{Griset2012PRB}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and
 later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
@@
 DMFT with NRG solver and lattice AFQMC data, as taken from 
-Ref.~\cite{Racz2020}.
+Ref.~\cite{Raczkowski2020PRB}.
 
@@
     $\lambda_\mathrm{so}=0$ line, to published data for Hartree-Fock,
-    DMFT-NRG and AFQMC solutions \cite{Racz2020}.}
+    DMFT-NRG and AFQMC solutions~\cite{Raczkowski2020PRB}.}
     \label{fig:KMenergy}
@@
 (see \ref{sSecRDM}), once diagonalized, takes the familiar form
-\cite{Zanardi2002,XiDai2013,WalshLetter2019} 
+\cite{Zanardi2002PRA,Su2013MPLB,Walsh2019PRL} 
 \begin{equation}

### 2025-06-01 01_intro.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.

@@
 
-\fixme{AA: this needs a further edit + all bibliography. I also need to add a paragraph to comments relation with other ED codes and cite them all.}
+\section{Introduction and Motivation}\label{SecIntro}
+Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with an extended non-interacting environment \cite{Nozieres1980JP,Hewson1993}.
+Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} progressively becoming powerful tools for exploring a wide range of quantum many-body phenomena \cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
+More recently, their importance has extended beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
 
-\section{Introduction and Motivation}\label{SecIntro}
-Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with an extended non-interacting environment.
-Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem, and beyond that they have progressively become powerful tools for exploring a wide range of quantum many-body phenomena.
-More recently, their importance has extended beyond the realm of condensed matter, influencing understanding of other areas such as quantum information or ultra-cold atomic systems.
-%Asymptotic freedom
+At the heart of quantum impurity models is the interaction between a localized ``impurity''  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons \cite{Hewson1993}.
+In this context, the definition of the impurity can be taken as rather general, in order to contain orbital and spin local degrees of freedom as well as a finite number of lattice sites.
+This setup captures many essential aspects of strong correlation including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
+Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like density-matrix embedding theory (DMET) \cite{Knizia2012PRL}, Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
+Variational Cluster Approximations \cite{Potthoff2003TEPJBCMACS,Senechal2008,Potthoff2011ACP,Nuss2011,Dionne2023SPC,Dionne2023SPCa}
+or Dynamical Mean-Field Theory (DMFT) \cite{Georges1996RMP, Kotliar2004PT,Kotliar2006RMP}.
+Within these approaches the complex physics of the lattice systems get reduced to an effective self-consistent quantum impurity problem.
+By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds or unconventional superconductors.
 
-At the heart of quantum impurity models is the interaction between a localized ``impurity''  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons.
-In this context, the definition of the impurity can be taken as rather general, in order to contain orbital and spin local degrees of freedom as well as a finite number of lattice sites.
-%MC eliminated inequivalent to avoid confusion with the last point
-This setup captures many essential aspects of strong correlation including screening, decoherence and entanglement in a computationally tractable way. 
-Most notably, quantum impurity problems lie at the core of dynamical mean-field theory (DMFT) where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem \cite{Georges1996RMP}.
-\fixme{(Samuele)I would also cite gutzwiller approx and DMET, we should not restrict the number of users of the code :). Something like:
-
-Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like dynamical mean-field theory (DMFT)~\cite{Georges1996RMP}, density-matrix embedding theory (DMET)~\cite{Knizia2012PRL} and the Gutzwiller approximation (GA)~\cite{Lanata2015PRX}, where the complex behavior of the lattice systems is reduced to an effective self-consistent quantum impurity problem.
-The present code has been developed with a particular focus for DMFT but its usage extends also to the aforementioned methods.
-}
-By accounting for local quantum fluctuations, DMFT can successfully describe the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds, and high-temperature superconductors.
-
-Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains a
+Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains though a
 critical challenge, particularly for multi-orbital systems, systems
 at low temperatures or endowed with lower symmetry.
-During many years of development, different advanced numerical techniques have been developed together with cutting edge approaches aimed to reduce computational load.
-\fixme{(Samuele) Numerous exact diagonalization (ED) open-source software packages have been developed by the scientific community addressing the quantum many-body problem, with a strong emphasis on both efficiency and flexibility.
-Notably, these include codes designed for general systems of interacting fermions, such as EDLib~\cite{Iskakov2017} and the more recent XDiag~\cite{Wietek2025}; for systems involving both fermions and bosons, such as Pomerol~\cite{Antipov2015}; and for fermions coupled with spins, such as H$\Phi$~\cite{Kawamura2017CPC,Ido2024CPC}.
+%
+To this end, over many years many advanced numerical techniques have been developed which incorporate cutting-edge strategies to reduce computational loads and leverage state-of-the-art algorithms \cite{Bauer2011JOSMTAE,Parcollet2015CPC}.
+These range from continuous-time quantum Monte Carlo 
+methods \cite{Gull2011RMP,Rubtsov2005PRB,Haule2007PRB,Seth2016CPC,Wallerberger2019CPC},
+to numerical renormalization group approaches \cite{Zitko2009PRB,Bulla2001PRB,Bulla2008RMP,Debertolis2021PRB} 
+and density-matrix renormalization group \cite{Zitko2009PRB,Bulla2001PRB,Bulla2008RMP,Nunez-Fernandez2025A} or Configuration Interaction \cite{Zgid2012PRB,Lu2014PRB,Go2017PRB,Bi2019CPC,Mejuto-Zaera2019PRB} solvers.
+In this context, the Exact Diagonalization (ED) approach plays a significant 
+and distinctive role \cite{Caffarel1994PRL,Dolfen2006,Perroni2007PRB,Capone2007PRB,Weber2012PRB,Lu2017TEPJST,Amaricci2022CPC}.
 
-N.B. if added we may want to delete "(ED)" from the next sentence since it is defined here.}
+More in general, several open-source ED software packages have recently been made available  within the condensed matter community to address quantum many-body problems with an emphasis on efficiency and flexibility.
+Examples include \texttt{EDLib} \cite{Iskakov2017} and the newer
+\texttt{XDiag} \cite{Wietek2025}, which focus on generic fermionic systems; 
+\texttt{Pomerol} \cite{Antipov2015} designed for fermion-boson models and interfaced with TRIQS \cite{Parcollet2015CPC}; \texttt{H$\Phi$} \cite{Kawamura2017CPC,Ido2024CPC} 
+for fermions coupled to spins; and general-purpose spin-model solvers such as 
+\texttt{QuSpin} \cite{Weinberg2017SP,Weinberg2019SP}, all contributing to the 
+rich landscape of ED-based techniques.
 
@@
 The library builds on the foundations of
-its predecessor~\cite{Amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms while including several significant extensions and improvements.
-The library now supports, within a unified framework, both zero and finite temperature calculations for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.
+its predecessor \cite{Amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms \cite{Lanczos1950JRNBSB,Lehoucq1998,Maschhoff1996} while including several significant extensions and improvements.
+The library now supports, within a unified framework, both zero and finite temperature calculations \cite{Amaricci2022CPC,Capone2007PRB} for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.
 It also provides direct
-access to numerically exact
-dynamical correlation functions across the
+access to numerically exact dynamical correlation functions across the
 entire frequency complex plane, thus enabling calculations of spectral functions, local susceptibilities, and other response properties.
@@
 Additionally, \NAME offers access to the Fock space of
-the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix
-(iRDM).
-This capability enables quantum information-inspired analyses, providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems.
-These
-features are increasingly recognized as essential for understanding the emergent behavior in correlated matter, including quantum criticality and superconductivity.
+the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix (iRDM).
+This capability enables quantum information-inspired analyses providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems \cite{Walsh2021PNAS,Bellomia2024PRB}.
+In the quantum embedding context, these features are increasingly recognized as essential to understand the emergent behavior of correlated matter, including quantum criticality and superconductivity.
+% MC this last point is intrinsically DMFT (or embedding) and it has no connection with impurity physics. Right: I added an opening which should clarify the sentence.
 
-%MC this last point is intrinsically DMFT (or embedding) and it has no connection with impurity physics
-This new version also includes support for systems with non-equivalent impurities.
+This new \NAME version also includes support for systems with non-equivalent impurities.
 This is a critical feature in DMFT or, more generally, in quantum embedding methods, to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
-This capability makes it
-possible to explore a wide range of inhomogeneous systems, including
-oxide interfaces or disordered systems, where
-translational symmetry is broken.
-%Repetition
+% This capability makes it 
+% possible to explore a wide range of inhomogeneous systems, including
+% oxide interfaces or disordered systems, where
+% translational symmetry is broken.
+%MC? Repetition.. removed
 
 %\paragraph{Interoperability}\\
-With the growing importance of  quantum impurity models in the study of correlated materials,
-standardization and interoperability between solution software suites has
+With the growing importance of  quantum impurity models in the study of correlated materials, standardization and interoperability between solution software suites has
 become a critical necessity.
@@
 A key development feature in \NAME, unlocked by the introduction of the Python API, 
-is the possibility to directly interface to the TRIQS (Toolbox for Research on Interacting Quantum Systems) and
-W2Dynamics software suites, which are two of the most important and widely used computational tools in
-the field. \NAME slots in as an alternative solver to the native Quantum Monte Carlo 
-implementations, extending the parameter (and especially temperature) range reachable by 
+is the possibility to directly interface to both TRIQS \cite{Parcollet2015CPC} (Toolbox for Research on Interacting Quantum Systems) and
+W2Dynamics \cite{Wallerberger2019CPC} software suites, which are two of the most important and widely used computational framework in the field.
+\NAME slots in as an alternative solver to the native Quantum Monte Carlo 
+implementations \cite{Gull2011RMP,Seth2016CPC}, extending the parameter (and especially temperature) range reachable by 
 the simulation while minimizing the coding requirements for the end user.
@@
 Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
-enhancing reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat, see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}.
+enhancing reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat (see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}).
 
@@
 high-performance solver can be used to tackle a wide range of
-challenging impurity problems. 
-The rest of this work has the following structure. In \secu{SecInstall} we 
+challenging problems. 
+The rest of this work is organized as follow. In \secu{SecInstall} we 
 briefly illustrate the overall structure of \NAME together with its dependencies, configuration
-and installation procedures. In the following  \secu{SecEDIpack} we present the quantum impurity
-problem and review the software implementation in full detail. In \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
+and installation procedures. In \secu{SecEDIpack} we present the quantum impurity
+problem and review the software implementation in detail. In \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
 interoperability capabilities of \NAME. In this section we also discuss 4 interface layers: i) 
-the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) a basic Julia API.
-Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and 
-all the discussed extensions with a series of illustrative examples.
+the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) an experimental, yet operative, Julia API.
+Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and  all the discussed extensions with a series of illustrative examples.
 
@@
 }{}
+
 \end{document}

### 2025-06-01 03_edipack2.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.

@@
 However, we typically 
-adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction~\cite{Georges2013ARCMP}:
+adopt a generic formulation of the local multi-orbital Hubbard-Kanamori interaction \cite{Georges2013ARCMP}:
 \begin{equation}\label{Hint}
@@
 interaction, where $U$ is the local intra-orbital Coulomb repulsion,
-$U'$ the inter-orbital one and $J$ the Hund's coupling~\cite{Werner2008PRL,Werner2009PRB,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
+$U'$ the inter-orbital one and $J$ the Hund's coupling \cite{Werner2008PRL,Werner2009PRB,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
 The last two terms are, respectively, the spin-exchange ($J_X$) and
@@
 U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$~\cite{Georges2013ARCMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other numbers of orbitals~\cite{Georges2013ARCMP}.
-
-\subsubsection{Bath and Hybrization}
+$J_X=J_P=J$ \cite{Georges2013ARCMP}. Different choices, preserving part
+of the combined symmetry group, can be made for other numbers of orbitals \cite{Georges2013ARCMP}.
+
+\subsubsection{Bath and Hybridization}
 The coupling between the impurity and the bath is described by
@@
 %
-For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model~\cite{Holstein1959APNY}.
-For two-orbital models we included also the two Jahn-Teller modes~\cite{Capone2010AICMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$~\cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.
-
-For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling~\cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction~\cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}.
+For single-orbital impurities, the relevant case is $\hat{O}_1 = g_1 n_{1d} = g_1 \sum_{\sigma} d^{\dagger}_{1\sigma}d_{1\sigma}$, which defines the Holstein model \cite{Holstein1959APNY}.
+For two-orbital models we included also the two Jahn-Teller modes \cite{Capone2010AICMP}, for which $\hat{O}_2 = g_2(n_{1d} - n_{2d})$ \cite{Scazzola2023PRB} and $\hat{O}_3 = g_3 \sum_{\sigma} (d^{\dagger}_{1\sigma}d_{2\sigma}+ H.c.)$.
+
+For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling \cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction \cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}.
 The larger the number of excited phonons in the ground state, the larger the cutoff.
-For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime~\cite{Capone2003PRL}.
+For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime \cite{Capone2003PRL}.
 Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
@@
 specific case is discussed extensively
-Ref.~\cite{Amaricci2022CPC}, so we will cover it no further here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
+Ref. \cite{Amaricci2022CPC}, so we will cover it no further here recalling that any consideration concerning the {\tt normal} case extends directly to this case as well.
 
@@
 This scenario captures effects such as local spin-orbit coupling
-$\vec{L}\cdot\vec{S}$, in-plane spin ordering~\cite{BellomiaKMH} or
-in-plane spin-triplet exciton condensation~\cite{Amaricci2023PRB,Blason2020PRB}.  
+$\vec{L}\cdot\vec{S}$, in-plane spin ordering \cite{BellomiaKMH} or
+in-plane spin-triplet exciton condensation \cite{Amaricci2023PRB,Blason2020PRB}.  
 \end{itemize}
@@
 $[I_\up,I_\dw]$ as $I_e=I_\up +   I_\dw 2^{N_\mathrm{s}}$.
-For a more detailed discussion on the structure of the Fock basis in this case, see Ref.~\cite{Amaricci2022CPC}.
+For a more detailed discussion on the structure of the Fock basis in this case, see Ref. \cite{Amaricci2022CPC}.
 
@@
 symmetric due to the factorized nature of the sectors as discussed
-above, see also Ref.~\cite{Amaricci2022CPC}.
+above, see also Ref. \cite{Amaricci2022CPC}.
 The analysis of the spectrum is then reduced to inspecting the
@@
 
-% method~\cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996}
+% method \cite{Lanczos1950JRNBSB,Lin1993CIP,Lehoucq1998,Maschhoff1996}
 
@@
 $dE_{mn}=E_m-E_n$ is the corresponding excitation energy.
-% \fixme{How does the operator $A$ enter this expression?}
 
@@
 \paragraph{Bath replica/general.}
-The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica}/{\tt Hge\-ne\-ral} for the {\bf replica}/{\bf general} bath parametrizations.
+The module {\tt ED\_BATH\_REPLICA} defines the class {\tt Hreplica}/{\tt Hge\-ne\-ral} for the {\bf replica}/{\bf general} bath parametrization.
 In  addition to standard object construction, destruction, reading and saving, this module provides the setup for either the matrix basis
@@
 high-performance diagonalization algorithms.
-In Ref.~\cite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling.
+In Ref.
+\cite{Amaricci2022CPC} we discussed in greater details the massively parallel strategies  employed in \NAME to optimize the MVP operations and presented various benchmarks of the parallel scaling.
 Here, we provide a brief outline of the main ideas following the notation introduced
@@
 \paragraph{{\bf superc}.}
-In the supercondutive case, the orbital-dependent Nambu $s$-wave
+In the superconductive case, the orbital-dependent Nambu $s$-wave
 Green's function has the form:
@@
 extending the algorithm initially proposed in 
-Ref.~\cite{BellomiaPhD,Bellomia2024PRB}, to support the analysis of entanglement 
+Ref. \cite{BellomiaPhD,Bellomia2024PRB}, to support the analysis of entanglement 
 properties of quantum impurities for any value of {\tt ed\_mode}.
@@
 local non-interacting Hamiltonian. The Weiss field is obtained from the DMFT 
-self-consistency equation~\cite{Georges1996RMP}, while the bath 
+self-consistency equation \cite{Georges1996RMP}, while the bath 
 discretization requires a careful fitting of this continuous function 
@@
 Several algorithms have been proposed for this optimization 
-step~\cite{Garcia2004PRL,Taranto2012PRB,Mejuto-Zaera2020PRB}, each with strengths suited 
+step \cite{Garcia2004PRL,Taranto2012PRB,Mejuto-Zaera2020PRB}, each with strengths suited 
 to different physical contexts. To maintain flexibility in \NAME, 
@@
 While different optimization methods have been developed for 
-truncated algorithms, e.g. sCI~\cite{Mejuto-Zaera2020PRB} or DMRG~\cite{Bauernfeind2017PRX}, 
+truncated algorithms, e.g. sCI \cite{Mejuto-Zaera2020PRB} or DMRG \cite{Bauernfeind2017PRX}, 
 which handle systems with a 
@@
 \texttt{0} for a Fletcher-Reeves-Polak-Ribiere variant adapted from 
-Numerical Recipes~\cite{NumRec77}, and \texttt{1} for the original 
+Numerical Recipes \cite{NumRec77}, and \texttt{1} for the original 
 algorithm described in Ref. \cite{Georges1996RMP}, commonly used 
@@
 translational symmetry is broken, as in heterostructures, disordered 
-systems, or multiorbital setups.
+systems, or multi-orbital setups.
 

### 2025-06-01 04_cbinding.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.

@@
 Here we describe the implementation of an interoperability layer aiming at developing APIs for other languages as well as 
-integrating \NAME in complex scientific frameworks, e.g. TRIQS~\cite{Parcollet2015CPC} or W2Dynamics~\cite{Wallerberger2019CPC}.
+integrating \NAME in complex scientific frameworks, e.g. TRIQS \cite{Parcollet2015CPC} or W2Dynamics \cite{Wallerberger2019CPC}.
 
@@
   type of system we are considering (normal, superconductive,
-  non-SU(2) symmteric) a different set of inputs has to be passed. The specifics
+  non-SU(2) symmetric) a different set of inputs has to be passed. The specifics
   of the numerical fitting routines are controlled in the input file.
@@
 function array (evaluated on-the-fly) for a specified supported shape,
-normal or anomlous type and on a specific axis or frequency domain.
+normal or anomalous type and on a specific axis or frequency domain.
 
@@
 \subsection{EDIpack2TRIQS: the TRIQS interface}\label{sSecInteropTRIQS}
-A thin compatibility layer between \NAME and TRIQS~\cite{Parcollet2015CPC}, i.e. Toolbox for Research on
+A thin compatibility layer between \NAME and TRIQS \cite{Parcollet2015CPC}, i.e. Toolbox for Research on
 Interacting Quantum Systems,  called EDIpack2TRIQS is available as a stand-alone project. This is a pure Python package
@@
 common to other TRIQS-based impurity solvers, such as
-TRIQS/CTHYB~\cite{Seth2016CPC}. It also enables execution of \NAME calculations
+TRIQS/CTHYB \cite{Seth2016CPC}. It also enables execution of \NAME calculations
 in the MPI parallel mode with no extra effort from the user.
@@
 \subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-\NAME is supported as alternative impurity solver in the W2Dynamics DMFT package~\cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
+\NAME is supported as alternative impurity solver in the W2Dynamics DMFT package \cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
 The only prerequisite to use this option is the presence of a functioning EDIpack2py installation (see \secu{sSecInteropEDIpy}), which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameters.
@@
 The full set of configuration options can be found in the {\tt configspec} file, contained in the subfolder {\tt w2dyn/auxiliaries} of the W2Dynamics repository.
-See also~\cite{Wallerberger2019CPC}
+See also \cite{Wallerberger2019CPC}
 for further details.

### 2025-06-01 05_examples.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.

@@
 On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which handles all these tasks seamlessly.
-Similarly, the TRIQS library offers an extensive framework for the manipulation of Green’s functions and related quantities~\cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
+Similarly, the TRIQS library offers an extensive framework for the manipulation of Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
 
@@
 in a Bethe lattice, i.e., a Cayley tree with coordination number 
-$z\to\infty$~\cite{Zhang1993PRLb,Caffarel1994PRL,Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
+$z\to\infty$ \cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
 Here, we present a guided implementation of the DMFT 
@@
 where $D=2t$ is the half-bandwidth.
-Within DMFT framework~\cite{Georges1996RMP}, this lattice model is mapped onto a quantum impurity problem with an effective electronic bath that must be determined self-consistently.
+Within DMFT framework \cite{Georges1996RMP}, this lattice model is mapped onto a quantum impurity problem with an effective electronic bath that must be determined self-consistently.
 
@@
 with  $\zeta=i\omega+\mu-h^0-\Sigma(i\omega)$.
-Note that this step can be performed analytically for the Bethe lattice~\cite{Georges1996RMP} or completely substituted by retrieving the impurity Green's function $G_\mathrm{imp}$ via the {\tt ed\_get\_gimp} function.
+Note that this step can be performed analytically for the Bethe lattice \cite{Georges1996RMP} or completely substituted by retrieving the impurity Green's function $G_\mathrm{imp}$ via the {\tt ed\_get\_gimp} function.
 
@@
 results. Alternative optimization methods can also be employed as 
-needed~\cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
+needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 
 An example of implementation is provided in the following listings.
@@
 The W2Dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
-Further information about the functioning of W2Dynamics can be found in Ref.~\cite{Wallerberger2019CPC}
+Further information about the functioning of W2Dynamics can be found in Ref.
+\cite{Wallerberger2019CPC}
 
@@
 
-The results are collected into an HDF5~\cite{The_HDF_Group_Hierarchical_Data_Format} archive in the usual W2Dynamics format, including output quantities inherited from \NAME.
+The results are collected into an HDF5 \cite{The_HDF_Group_Hierarchical_Data_Format} archive in the usual W2Dynamics format, including output quantities inherited from \NAME.
 Results can be viewed using the script {\tt hgrep} provided with W2Dynamics or with other HDF5 tools.
@@
 The second example we present concerns the DMFT description of the 
-attractive Hubbard model~\cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. This 
+attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. This 
 example has a twofold aim: (i) to demonstrate the support of \NAME 
@@
 Here we showcase some results for the DMFT solution of the 
-attractive Hubbard model across the BCS-to-BEC crossover regime~\cite{Toschi2005PRB,Toschi2005NJP,Amaricci2014PRA} 
+attractive Hubbard model across the BCS-to-BEC crossover regime \cite{Toschi2005PRB,Toschi2005NJP,Amaricci2014PRA} 
 illustrating the capability of \NAME to handle $s$-wave 
@@
 To further quantify these dynamical effects, we plot in the inset of the same panel the 
-{\it correlation strength}~\cite{Amaricci2015PRL,Amaricci2016PRB}
+{\it correlation strength} \cite{Amaricci2015PRL,Amaricci2016PRB}
 $\Theta=|S(i\omega\to 0)-S(i\omega\to\infty)|/S(i\omega\to\infty)$. 
@@
 enters a Bipolaronic Insulating phase for our
-choice of the coupling~\cite{Capone2006PRB}.
+choice of the coupling \cite{Capone2006PRB}.
 
@@
 Bernevig-Hughes-Zhang (BHZ).
-As shown in Ref.~\cite{Amaricci2023PRB}, at moderate
+As shown in Ref. \cite{Amaricci2023PRB}, at moderate
 interactions this model admits an excitonic phase in which opposite
@@
 lattice interacting through a Hubbard-Kanamori term and describing
-a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Konig2007S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
+a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
 We consider a suitable matrix basis in terms of the Dirac
@@
 
-%${\color{comment-color}  }
 \begin{lstlisting}[style=fstyle,numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
      !EDIpack: Retrieve ${\color{comment-color} \Sigma(i\omega)}$
-     call ed_get_sigma(Smats,axis='mats')
+     call ed_get_sigma(Smats,axis="mats")
 
      !Get $\color{comment-color}G_\mathrm{loc}$ using $\color{comment-color}\mathrm{DMFTtools}$
-     call get_gloc(Hk,Gmats,Smats,axis='m')
+     call get_gloc(Hk,Gmats,Smats,axis="m")
 
@@
 Furthermore, the long-range ordering
-eventually stabilized at large $U/t$, is characterized by a lowered spin symmetry, due to the inherent coupling of spin and lattice degrees of freedom that favors in-plane easy-axis magnetization
-\cite{Griset2012PRB}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and
+eventually stabilized at large $U/t$, is characterized by a lowered
+spin symmetry, due to the inherent coupling of spin and lattice
+degrees of freedom that favors in-plane easy-axis magnetization \cite{Griset2012PRB}, as predicted by Hartree-Fock and $t$-$J$ perturbative expansions \cite{Rachel2010PRB} and
 later confirmed by Auxiliary-Field Quantum Monte Carlo (AFQMC) 
@@
 DMFT with NRG solver and lattice AFQMC data, as taken from 
-Ref.~\cite{Raczkowski2020PRB}.
+Ref. \cite{Raczkowski2020PRB}.
 
@@
     $\lambda_\mathrm{so}=0$ line, to published data for Hartree-Fock,
-    DMFT-NRG and AFQMC solutions~\cite{Raczkowski2020PRB}.}
+    DMFT-NRG and AFQMC solutions \cite{Raczkowski2020PRB}.}
     \label{fig:KMenergy}
@@
 simple case of a two-site unit cell.
-Building on the previous example, we can readily adapt the calculation to deal with a nanoscopic~\cite{Amaricci2014PRA} system with $N_\mathrm{ineq}$ inequivalent atoms, such as hexagonal flakes
+Building on the previous example, we can readily adapt the calculation to deal with a nanoscopic \cite{Amaricci2014PRA} system with $N_\mathrm{ineq}$ inequivalent atoms, such as hexagonal flakes
 \cite{Valli2016PRB,Valli2018NL}.

### 2025-06-01 06_conclusions_acknowledgement_appendix.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.

@@
 \section{Conclusions}
-{\color{red} Tentative conclusions}
 We have presented \NAME{}, a versatile, high-performance solver for
 generic quantum impurity problems. Leveraging on the massively
-parallel algorithms introduced by its predecessor, this version of
+parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
 the library features new capabilities and symmetries within a unified
-framework, providing reliable evaluations of the dynamical correlation
+framework, providing for instance reliable evaluations of the dynamical correlation
 functions of an arbitrary complex frequency.
-This makes it particularly well-suited for capturing the sharp
+This makes it particularly well-suited for capturing the
 low-energy excitations and complex spectral features of strongly
-correlated systems. We have shown that this new version enables the evaluation of impurity
-reduced density matrices directly from Fock space quantities and thus unlock 
-quantum information analyses of correlated systems.
+correlated systems.
+We have shown that this new version enables the evaluation of impurity
+reduced density matrices directly from Fock space quantities and thus unlocks 
+quantum information analyses of correlated systems, an increasingly
+essential tool to address emergent phases of quantum materials.
 
@@
 These interfaces enable seamless integration with broader
-computational frameworks like TRIQS and W2Dynamics, expanding the
+computational frameworks, like TRIQS \cite{Parcollet2015CPC} and
+W2Dynamics \cite{Wallerberger2019CPC}, expanding the
 functionality of these platforms and providing a robust foundation for
@@
 most important algorithms and classes. We presented in
-detail the third-party interfaces which extend exact diagonalization
+detail the third-party interfaces which extend ED
 capabilities beyond the realm of the library itself.   
@@
 The modular and extensible design of \NAME provides a
-natural foundation for future extensions, for instance to cluster-DMFT where the
+natural foundation for future extensions.
+For instance to
+cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} where the
 impurity problem is generalized to include clusters of interacting
@@
 order, and complex spin textures in strongly correlated systems.
+A different outlook is the development of an integration layer with other
+quantum embedding methods, such ghost Gutzwiller \cite{Lanata2015PRX},
+which heavily rely on solving effective impurity problems.    
 We anticipate that \NAME will become a valuable tool for the
@@
 
-\speak{\MakeUppercase{P}} {\it No, no, no, attenzione! Il loop DMFT completo \`e supportato secondo la Ref.~\cite{Georges1996RMP}, abbia pazienza,
+\speak{\MakeUppercase{P}} {\it No, no, no, attenzione! Il loop DMFT completo \`e supportato secondo la Ref. \cite{Georges1996RMP}, abbia pazienza,
 senn\`o.... Plotta i dati, anche un pochino di Green's function e

### 2025-06-01 01_intro.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \section{Introduction and Motivation}\label{SecIntro}
-Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom with an extended non-interacting environment \cite{Nozieres1980JP,Hewson1993}.
-Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} progressively becoming powerful tools for exploring a wide range of quantum many-body phenomena \cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
-More recently, their importance has extended beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
+Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom to an extended non-interacting environment \cite{Nozieres1980JP,Hewson1993}.
+Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} have progressively become powerful tools for exploring a wide range of quantum many-body phenomena \cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
+More recently, their importance has expanded beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
 
 At the heart of quantum impurity models is the interaction between a localized ``impurity''  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons \cite{Hewson1993}.
-In this context, the definition of the impurity can be taken as rather general, in order to contain orbital and spin local degrees of freedom as well as a finite number of lattice sites.
-This setup captures many essential aspects of strong correlation including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
+In this context, the  impurity  can be defined more generally, so as to include orbital and spin local degrees of freedom as well as a finite number of lattice sites.
+This setup captures many essential aspects of strong correlation, including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
 Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like density-matrix embedding theory (DMET) \cite{Knizia2012PRL}, Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
@@
 or Dynamical Mean-Field Theory (DMFT) \cite{Georges1996RMP, Kotliar2004PT,Kotliar2006RMP}.
-Within these approaches the complex physics of the lattice systems get reduced to an effective self-consistent quantum impurity problem.
-By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds or unconventional superconductors.
+Within these approaches the complex physics of the lattice systems gets reduced to an effective self-consistent quantum impurity problem.
+By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds and unconventional superconductors.
 
-Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, remains though a
-critical challenge, particularly for multi-orbital systems, systems
+Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, nonetheless remains a critical challenge, particularly for multi-orbital systems, systems
 at low temperatures or endowed with lower symmetry.
 %
-To this end, over many years many advanced numerical techniques have been developed which incorporate cutting-edge strategies to reduce computational loads and leverage state-of-the-art algorithms \cite{Bauer2011JOSMTAE,Parcollet2015CPC}.
+To this end, over the years 
+many advanced numerical techniques have been developed, incorporating cutting-edge strategies to reduce computational loads and leverage state-of-the-art algorithms \cite{Bauer2011JOSMTAE,Parcollet2015CPC}.
 These range from continuous-time quantum Monte Carlo 
@@
 
-More in general, several open-source ED software packages have recently been made available  within the condensed matter community to address quantum many-body problems with an emphasis on efficiency and flexibility.
+More generally, several open-source ED software packages have recently been made available  within the condensed matter community to address quantum many-body problems with an emphasis on efficiency and flexibility.
 Examples include \texttt{EDLib} \cite{Iskakov2017} and the newer
@@
 %EDIPACK
-In this work we present the renewed and improved \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+In this work we present the improved and renewed \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
 The library builds on the foundations of
 its predecessor \cite{Amaricci2022CPC}, featuring massively parallel Lanczos-based algorithms \cite{Lanczos1950JRNBSB,Lehoucq1998,Maschhoff1996} while including several significant extensions and improvements.
-The library now supports, within a unified framework, both zero and finite temperature calculations \cite{Amaricci2022CPC,Capone2007PRB} for a wide set of impurity models, making it capable of addressing a large set of problems, from spin-orbit coupling effects in quantum materials to multi-orbital superconductivity.
+The library now supports, within a unified framework, both zero and finite temperature calculations \cite{Amaricci2022CPC,Capone2007PRB} for a wide set of impurity models, making it suitable for addressing a broad class of problems, from spin-orbit coupling in quantum materials to multi-orbital superconductivity.
 It also provides direct
@@
 Additionally, \NAME offers access to the Fock space of
-the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix (iRDM).
-This capability enables quantum information-inspired analyses providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems \cite{Walsh2021PNAS,Bellomia2024PRB}.
+the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix (iRDM), enabling quantum information-inspired analyses providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems \cite{Walsh2021PNAS,Bellomia2024PRB}.
 In the quantum embedding context, these features are increasingly recognized as essential to understand the emergent behavior of correlated matter, including quantum criticality and superconductivity.
@@
 
-This new \NAME version also includes support for systems with non-equivalent impurities.
+This new \NAME version also includes support for systems with inequivalent impurities.
 This is a critical feature in DMFT or, more generally, in quantum embedding methods, to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
@@
 %\paragraph{Interoperability}\\
-With the growing importance of  quantum impurity models in the study of correlated materials, standardization and interoperability between solution software suites has
+With the growing importance of quantum impurity models in the study of correlated materials, standardization and interoperability across software suites has
 become a critical necessity.
@@
 Especially notable in this sense is the Python API, EDIpack2py, which beyond providing a 
-high-level interface for defining and solving impurity problems, also allows integration with established scientific libraries, such as NumPy and SciPy, facilitating data analysis and
+high-level interface for defining and solving impurity problems, it also allows integration with established scientific libraries, such as NumPy and SciPy, facilitating data analysis and
 rapid prototyping.
@@
 is the possibility to directly interface to both TRIQS \cite{Parcollet2015CPC} (Toolbox for Research on Interacting Quantum Systems) and
-W2Dynamics \cite{Wallerberger2019CPC} software suites, which are two of the most important and widely used computational framework in the field.
+W2Dynamics \cite{Wallerberger2019CPC} software suites, which are two of the most important and widely used computational frameworks in the field.
 \NAME slots in as an alternative solver to the native Quantum Monte Carlo 
@@
 extensive data handling and analysis tools in the TRIQS ecosystem. 
-Overall, interoperability extends the cumulative reach and trustworthiness of all these platforms,
-enhancing reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat (see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}).
+Overall, interoperability enhances the collective reach and reliability of these platforms, 
+improving reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat (see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}).
 
@@
 challenging problems. 
-The rest of this work is organized as follow. In \secu{SecInstall} we 
+The rest of this work is organized as follows. In \secu{SecInstall} we 
 briefly illustrate the overall structure of \NAME together with its dependencies, configuration

### 2025-06-01 02_install.tex
v1 complete Full revision. Syntax check (but more checks to do). References fully added. Color codes set. Freezing this.
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \begin{document}
-\fixme{AA: reviewed. Misses possible References}
 
@@
 The configuration and installation of \NAME is handled by CMake, which ensures
-multi-platform compatibility and dependencies resolution.  
+cross-platform compatibility and dependency resolution.  
 The software builds into two distinct libraries.
-The main one is a static Fortran library named {\tt libedipack.a} which, alongside the compiled
+The main one is a static Fortran library named {\tt libedipack.a}, which alongside the compiled
 modules, wraps the \NAME software.
@@
 \subsection{Structure}\label{sSecInstallStructure}
-\NAME is a modular library organized into two main components. At its 
-core, constituting the primary computational engine, 
-is the  Exact Diagonalization solver for the quantum single-impurity Hamiltonian.
-Building on this, the library includes 
-\NAME{2ineq}, an extension for handling multiple inequivalent impurity problems at once. Finally, a Fortran-C/C++ interface is provided for 
-seamless integration with external software and the development of additional APIs.
+\NAME is a modular library organized into two main components. 
+At its core lies the ED solver for the quantum
+single-impurity Hamiltonian, constituting the primary computational engine.
+Building on this, the library includes \NAME{2ineq}, an extension for handling multiple inequivalent impurity problems at once.
+Finally, a Fortran-C/C++ interface is provided for seamless integration with external software and the development of additional APIs.
 
@@
 \item{\bf EDIpack.}
-  This module forms the foundation of the library, implementing the 
+  This module forms the foundation of the library, implementing a 
   Lanczos-based solver for general quantum impurity problems. It 
-  supports systems with a wide range of symmetries leveraging different quantum numbers conservation, multi-orbital models, and even coupling to local 
+  supports systems with a wide range of symmetries leveraging conservation of different quantum numbers, multi-orbital models, and even coupling to local 
   phonons. The \NAME solver is structured hierarchically and modularly, 
@@
   execution, and finalization, while abstracting the underlying data 
-  structures. A detailed overview of this part of the library is 
-  provided in \secu{SecEDIpack}.
+  structures. A detailed overview of this part of the library is   provided in \secu{SecEDIpack}.
   \begin{itemize}
@@
 for mathematical and scientific software development, available at \href{https://github.com/SciFortran/SciFortran}{github.com/SciFortran}.
-\item {\bf MPI}: a distributed memory parallel communication layer with support for modern Fortran compiler.
+\item {\bf MPI}: a distributed memory parallel communication layer with support for modern Fortran compilers.
 \end{enumerate}
@@
 is required to access scalable parallel diagonalization algorithms,
-which speed up calculations for large systems. Nonetheless, through careful design \NAME operates serially even without initialization of the MPI framework.
+which speed up calculations for large systems. Nonetheless, thanks to careful design, \NAME can operate serially even without initializing the MPI framework.
 
@@
 \end{lstlisting}
-Then, assuming being in the software root directory ({\tt \$cd EDIpack}), a conventional out-of-source building can be performed using two alternative compilation backends.
+Then, assuming to be in the software root directory ({\tt \$cd EDIpack}), a conventional out-of-source building can be performed using two alternative compilation backends.
 
@@
 The default target builds and installs both the main library and the C-bindings.
-Separate build targets for either components are available.
+Separate build targets for each component are available.
 A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.
@@
 \subsubsection{Anaconda}
-As an alternative, we provide for both Linux and macOS systems
-installation through Anaconda packages into a virtual
-environment containing Python ($\geq3.10$).
+Installation is also available through Anaconda packages for Linux and macOS systems, within a virtual environment containing Python
+($\geq$ 3.10).
 %
@@
 \begin{enumerate}
-\item  A CMake-generated configuration file for an environment module
-  which allows to load and unload the library at any time. This is
+\item  A CMake-generated configuration file for an environment module which allows users to load and unload the library at any time. This is
   preferred solution for HPC systems. 
@@
 \end{enumerate}
-An automatically generated recap message with all instructions is
-generated at the end of the installation procedure.
+A recap message with all instructions is automatically generated at the end of the installation procedure.
 

### 2025-06-01 03_edipack2.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 orbital-dependent on-site energies or amplitudes, spin-orbit coupling or other single-particle terms.
-In \NAME the matrix $\hat{h}_0$ is set by the user passing an complex array through the function {\tt ed\_set\_Hloc}.
+In \NAME the matrix $\hat{h}_0$ is set by the user passing a complex array through the function {\tt ed\_set\_Hloc}.
 
 The interaction part of the impurity Hamiltonian, 
- $\hat{H}^{\mathrm{int}}$ can in principle contain any 
+ $\hat{H}^{\mathrm{int}}$ can, in principle, contain any 
 set of two-body operators: 
@@
 $U'$ the inter-orbital one and $J$ the Hund's coupling \cite{Werner2008PRL,Werner2009PRB,Mravlje2011PRL,Medici2011PRL,Medici2011PRB,Georges2013ARCMP}.  
-The last two terms are, respectively, the spin-exchange ($J_X$) and
-the pair-hopping ($J_P$).
+The last two terms are, respectively, the spin-exchange ($J_X$) and the pair-hopping ($J_P$).
 In the three-orbital case $N_\a=3$ a fully symmetric $SU(3)_\mathrm{orbital}\otimes SU(2)_\mathrm{spin}\otimes
 U(1)_\mathrm{charge}$ form of the interaction is obtained by setting $U'=U-2J$ and
-$J_X=J_P=J$ \cite{Georges2013ARCMP}. Different choices, preserving part
-of the combined symmetry group, can be made for other numbers of orbitals \cite{Georges2013ARCMP}.
+$J_X=J_P=J$ \cite{Georges2013ARCMP}. Alternative choices that preserve part
+of the combined symmetry group can be made for other numbers of orbitals \cite{Georges2013ARCMP}.
 
@@
 The parametrization of the bath Hamiltonian is 
-diagonal in both orbital and spin space, i.e.
+diagonal in both orbital and spin spaces, i.e.
 $$

### 2025-06-01 05_examples.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 \section{Examples}\label{SecExamples}
-In this section we illustrate and benchmark the functionalities and of the \NAME
+In this section we illustrate and benchmark the functionalities and of  \NAME
 library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages.
@@
 Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
-Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to exploit existing utilities.
-
-In our examples based on the Fortran APIs we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors) to perform specific tasks, including the evaluation of the local Green's function, the implementation of the self-consistency, the construction of the tight-binding model or the calculation of the kinetic energy.
+Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes, we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to take advantage of existing utilities.
+
+In our examples based on the Fortran APIs, we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors), to perform specific tasks, including evaluating the local Green’s function, implementing the self-consistency, constructing the tight-binding model, or calculating the kinetic energy.
 Where appropriate, we include comments that reference these external procedures.
-On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which handles all these tasks seamlessly.
-Similarly, the TRIQS library offers an extensive framework for the manipulation of Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
+
+On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which seamlessly handles all these tasks.
+Similarly, the TRIQS library offers an comprehensive framework fo manipulating Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
 
 \subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
-The test bed for any DMFT implementation is conventionally considered 
-the description of the Mott or metal-to-insulator transition (MIT) 
-in a Bethe lattice, i.e., a Cayley tree with coordination number 
-$z\to\infty$ \cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
+The description of the Mott transition using the Hubbard model on the Bethe lattice is conventionally regarded as the standard test bed for any DMFT implementation.
+\cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
+
 Here, we present a guided implementation of the DMFT 
@@
 \subsubsection{Finite temperature (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
-To demonstrate the usage of the W2Dynamics interface to \NAME,  here we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
+To demonstrate how the W2Dynamics interface integrates with  \NAME, we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
 In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in W2Dynamics against the \NAME solver at finite temperature.
@@
 
-The W2Dynamics configuration file for the solution of the Bethe lattice problem at finite temperature reads: 
+The following is the W2Dynamics configuration file used to solve the Bethe lattice problem at finite temperature: 
 \begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$.
-The results obtained from the three calculations are in excellent agreement one with another already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics ({\tt Nmeas=200000}).
+The results obtained from the three calculations are in excellent agreement with each other already for a small number of bath levels ({\tt NBATH=7}) and relatively low QMC statistics ({\tt Nmeas=200000} with {\tt NC=10} parallel processes).
 
@@
 The second example we present concerns the DMFT description of the 
-attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. This 
-example has a twofold aim: (i) to demonstrate the support of \NAME 
-for ($s$-wave) superconductivity, and (ii) to illustrate the use of 
-the library's Python API through a concrete working example.
+attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. 
+This  example two main goals: (i) to demonstrate \NAME's support for $s$-wave superconductivity, and (ii) to showcase the Python API through a concrete example.
 
@@
 \cos{(k_y a)}]$, where we set the lattice spacing 
-$a=1$  and the choose the energy unit such as $4t=D=1$ for convenience.
+$a=1$  and the choose the energy unit such that $4t=D=1$ for convenience.
 
@@
 example, with some notable adjustments related to the Nambu basis. 
-Specifically, the above symmetries allow one to compute only the 
-independent components from the first row, significantly reducing 
+These symmetries allow computing only the 
+independent components in the first row, reducing 
 the computational effort. 
@@
 
-    #Perform self-consistency levaragin {\tt aux\_funx.py} procedures:
+    #Perform self-consistency levaraging {\tt aux\_funx.py} procedures:
     Gmats = get_gloc(wm*1j,ed.xmu,HkNambu,Smats,axis="m")
@@
 significant dynamical effects, hence a more correlated superconducting state.
-Our results show that the DMFT solution significantly departs from the BCS picture in the strongly correlated intermediate-coupling regime, which is known to host the largest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
+Our results show that the DMFT solution significantly departs from the BCS picture in the strongly correlated intermediate-coupling, a regime known to host the highest critical temperature \cite{Toschi2005NJP,Toschi2005PRB}.
 % A different angle further illustrating the impact of dynamical fluctuations, is reported in panel (D).
@@
 
-One of the features introduced in \NAME is the possibility of treating local phonons in conjunction with the superconductive phase,
+One of the new features introduced in \NAME is the support for local phonons in combination with superconductivity,
 i.e. {\tt ed\_mode=superc}. In order to illustrate this property using a simple application, in this example we discuss the normal and
 superconductive solution of the pure Holstein model on the Bethe lattice within DMFT.
-We stress that  the code
-implementation for this specific case is essentially identical to the listings reported in the sections
+Note that the code
+implementation for this case is essentially identical to the listings in the previous sections
 \ref{SecExamplesBetheDMFT} ({\tt ed\_mode=normal}) and
@@
 (mediated by local phonons).
-In the opposite, adiabatic, limit, $\omega_0 \rightarrow 0$ the system
+In the  adiabatic limit, $\omega_0 \rightarrow 0$ the system
 enters a Bipolaronic Insulating phase for our
@@
 phonon frequency $\omega_0$, see panel (A) of \figu{figEx5}. In this panel we compare
-the behavior for the normal  ({\tt ed\_mode=normal}) against the superconductive
-solution ({\tt ed\_mode=superc}). Our results capture the whole
+the behavior for the normal phase ({\tt ed\_mode=normal}) and the superconductive
+phase ({\tt ed\_mode=superc}). Our results capture the whole
 crossover from adiabatic to anti-adiabatic regime. In the former
@@
 \subsection{Interacting Bernevig-Hughes-Zhang model (Fortran API, {\tt ed\_mode=nonsu2})}
-In this section we focus on the DMFT solution of the interacting
-Bernevig-Hughes-Zhang (BHZ).
-As shown in Ref. \cite{Amaricci2023PRB}, at moderate
-interactions this model admits an excitonic phase in which opposite
-orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
+In this section, we focus on the DMFT solution of the interacting
+Bernevig-Hughes-Zhang (BHZ) model.
+As shown in Ref. \cite{Amaricci2023PRB}, this model exhibits an excitonic phase at moderate
+interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
 
 We consider a system of two-orbital electrons on a square
-lattice interacting through a Hubbard-Kanamori term and describing
-a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
+lattice, interacting via a Hubbard-Kanamori term.
+This system realizes a quantum spin Hall insulator \cite{Kane2005PRL,Bernevig2006S,Hasan2010RMP,Hohenadler2011PRL,Amaricci2015PRL,Tang2017NP,Amaricci2023PRB,Paoletti2024PRB}.
 We consider a suitable matrix basis in terms of the Dirac
@@
 
-To complete the overview of \NAME features, we consider another
-model of interacting quantum spin-Hall insulator defined on the honeycomb lattice, with two inequivalent sites in the unit cell.
+To complete the overview of \NAME's features, we consider an additional interacting quantum spin-Hall insulator model, defined on the honeycomb lattice, with two inequivalent sites in the unit cell.
 Neglecting the Rashba spin-orbit interaction and discarding any ionic character of the unit cell, the noninteracting Kane-Mele Hamiltonian \cite{Kane2005PRLa,Kane2005PRL} can be written in momentum space as

### 2025-06-01 06_conclusions_acknowledgement_appendix.tex
v1 + few corrections Co-authored-by: Adriano Amaricci <adriano.amaricci@gmail.com>

@@
 We have presented \NAME{}, a versatile, high-performance solver for
-generic quantum impurity problems. Leveraging on the massively
+generic quantum impurity problems. Building on the massively
 parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
 the library features new capabilities and symmetries within a unified
-framework, providing for instance reliable evaluations of the dynamical correlation
+framework providing, for example, reliable evaluations of the dynamical correlation
 functions of an arbitrary complex frequency.
@@
 We have shown that this new version enables the evaluation of impurity
-reduced density matrices directly from Fock space quantities and thus unlocks 
-quantum information analyses of correlated systems, an increasingly
-essential tool to address emergent phases of quantum materials.
+reduced density matrices directly from Fock space quantities and thus enables  
+quantum information analysis of correlated systems, which is becoming an essential tool to address emergent phases of quantum materials.
 
@@
 natural foundation for future extensions.
-For instance to
-cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} where the
+For instance it provides a suitable basis to develop cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} methods, where the
 impurity problem is generalized to include clusters of interacting

### 2025-06-01 01_intro.tex
Different colors for different languages

@@
 Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} have progressively become powerful tools for exploring a wide range of quantum many-body phenomena \cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
-More recently, their importance has expanded beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
+More recently, their importance has expanded beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Stocker2022,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
 
@@
 This setup captures many essential aspects of strong correlation, including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
-Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like density-matrix embedding theory (DMET) \cite{Knizia2012PRL}, Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
+Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like density-matrix embedding theory (DMET) \cite{Knizia2012PRL}, the Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
 Variational Cluster Approximations \cite{Potthoff2003TEPJBCMACS,Senechal2008,Potthoff2011ACP,Nuss2011,Dionne2023SPC,Dionne2023SPCa}

### 2025-06-01 05_examples.tex
Different colors for different languages

@@
 
-\subsection{Hubbard model on the Bethe lattice (Fortran API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
+\subsection{Hubbard model on the Bethe lattice (Fortran/C++ API, {\tt ed\_mode=normal})}\label{SecExamplesBetheDMFT}
 The description of the Mott transition using the Hubbard model on the Bethe lattice is conventionally regarded as the standard test bed for any DMFT implementation.
@@
    real(8),allocatable   :: Bath(:)
-   complex(8),allocatable :: Hloc(:,:,:,:)
+   complex(8),allocatable:: Hloc(:,:,:,:)
    real(8),allocatable   :: Ebands(:),Dbands(:)
-   complex(8),allocatable :: Smats(:,:,:,:,:)
-   complex(8),allocatable :: Delta(:,:,:,:,:)
+   complex(8),allocatable:: Smats(:,:,:,:,:)
+   complex(8),allocatable:: Delta(:,:,:,:,:)
    !...  
@@
 
-#Generate Hk=${\color{comment-color}\e(k)}$ and set Hloc
+#Generate ${\color{comment-color}H_k=\e(k)}$ and set Hloc
 kgrid   = generate_kgrid(Nk)

### 2025-06-02 01_intro.tex
v1.1 arXiv ready AA, MC and GB

--- 2025-06-01 01_intro.tex
@@
 \section{Introduction and Motivation}\label{SecIntro}
-Quantum impurity models play a central role in the study of strongly correlated electron systems, capturing the coupling of a small number of localized degrees of freedom to an extended non-interacting environment \cite{Nozieres1980JP,Hewson1993}.
-Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have led to the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} have progressively become powerful tools for exploring a wide range of quantum many-body phenomena \cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
-More recently, their importance has expanded beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
+Quantum impurity models play a central role in the study of strongly correlated electron systems.
+They describe the coupling of a small number of localized degrees of freedom to an extended non-interacting environment \cite{Nozieres1980JP,Hewson1993}.
+Originally introduced to describe diluted magnetic impurities in metallic hosts, single-impurity models have played a central role in the field of quantum many-body systems through the decades, starting from the full understanding of the Kondo problem \cite{Anderson1961PR,Kondo1964POTP,Schrieffer1966PR} and subsequently proving crucial to the understanding of a wide range of quantum many-body phenomena\cite{Wilson1975RMP,Georges1996RMP,Kotliar2004PT,Kotliar2006RMP}.
+More recently, their scope has expanded beyond the realm of condensed matter, influencing the understanding of other areas such as quantum information \cite{Su2013MPLB,Walsh2019PRL,Walsh2020PQ,Walsh2021PNAS,Stocker2022,Bellomia2024PRB} or ultra-cold atomic systems \cite{Dao2007PRL,Amaricci2014PRA,Del-Re2018PRA,Walsh2019PRB,Tusi2022NP}.
 
 At the heart of quantum impurity models is the interaction between a localized ``impurity''  and a surrounding bath of itinerant particles, usually represented as a conduction band of electrons \cite{Hewson1993}.
-In this context, the  impurity  can be defined more generally, so as to include orbital and spin local degrees of freedom as well as a finite number of lattice sites.
-This setup captures many essential aspects of strong correlation, including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
-Most notably, quantum impurity problems lie at the core of many quantum embedding methods, like density-matrix embedding theory (DMET) \cite{Knizia2012PRL}, Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
-Variational Cluster Approximations \cite{Potthoff2003TEPJBCMACS,Senechal2008,Potthoff2011ACP,Nuss2011,Dionne2023SPC,Dionne2023SPCa}
-or Dynamical Mean-Field Theory (DMFT) \cite{Georges1996RMP, Kotliar2004PT,Kotliar2006RMP}.
-Within these approaches the complex physics of the lattice systems gets reduced to an effective self-consistent quantum impurity problem.
+In this context, the impurity  can be defined more generally, so as to include orbital and spin local degrees of freedom as well as a finite number of lattice sites, i.e.
+quantum clusters, immersed in a suitable environment.
+This setup lies at the core of several quantum embedding methods, including Density-Matrix Embedding Theory (DMET) \cite{Knizia2012PRL,Sun2020PRB} and further extensions \cite{Scott2021PRB,Nusspickel2022PRX}, the Gutzwiller Approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
+Quantum Cluster methods \cite{Potthoff2003TEPJBCMACS,Potthoff2011ACP,Dionne2023SPC,Dionne2023SPCa}
+or Dynamical Mean-Field Theory (DMFT) \cite{Georges1996RMP, Kotliar2004PT,Kotliar2006RMP}, capturing many essential aspects of strong correlation, including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}.
+
+%MC non in tutti questi metodi si introduce un modello di impurezza: 
+%AA "sistemato" facendo una piccola generalizzazione del concetto di impurity problem, includendo quantum clusters (VCA, CPA, etc.) or embedded fragments (DMET). Accettabile? 
+% This setup captures many essential aspects of strong correlation, including screening \cite{Roekeghem2014PRL,Roekeghem2014EL,Werner2016JOPCM,Tomczak2017TEPJST}, decoherence and entanglement in a computationally tractable way \cite{Walsh2021PNAS,Bellomia2024PRB}, lying at the core of several quantum embedding methods, such as Density-Matrix Embedding Theory (DMET) \cite{Knizia2012PRL,Sun2020PRB} and extensions\cite{Scott2021PRB,Nusspickel2022PRX}, the Gutzwiller approximation (GA) \cite{Lanata2015PRX,Mejuto-Zaera2023PRB},
+% Quantum Cluster methods \cite{Potthoff2003TEPJBCMACS,Potthoff2011ACP,Dionne2023SPC,Dionne2023SPCa}
+% or Dynamical Mean-Field Theory (DMFT) \cite{Georges1996RMP, Kotliar2004PT,Kotliar2006RMP}.
+
+In several of these embedding schemes, most notably DMFT, the complex physics of the lattice systems gets reduced to an effective self-consistent quantum impurity problem.
 By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds and unconventional superconductors.
-
-Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, nonetheless remains a critical challenge, particularly for multi-orbital systems, systems
+%
+Accurately and efficiently solving a quantum impurity problem and computing the Green's functions, which are central in the DMFT framework, nonetheless remains a critical challenge, particularly for multi-orbital systems, those
 at low temperatures or endowed with lower symmetry.
 %
-To this end, over the years 
-many advanced numerical techniques have been developed, incorporating cutting-edge strategies to reduce computational loads and leverage state-of-the-art algorithms \cite{Bauer2011JOSMTAE,Parcollet2015CPC}.
+To this end, 
+many advanced numerical techniques have been developed over the years, incorporating cutting-edge strategies to reduce computational loads and leverage state-of-the-art algorithms \cite{Bauer2011JOSMTAE,Parcollet2015CPC}.
 These range from continuous-time quantum Monte Carlo 
@@
 
-More generally, several open-source ED software packages have recently been made available  within the condensed matter community to address quantum many-body problems with an emphasis on efficiency and flexibility.
+Several open-source ED software packages have recently been made available within the condensed matter community to address quantum many-body problems with an emphasis on efficiency and flexibility.
 Examples include \texttt{EDLib} \cite{Iskakov2017} and the newer
@@
 %EDIPACK
-In this work we present the improved and renewed \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an exact diagonalization (ED) solver for generic Quantum Impurity Problems.
+In this work we present the improved and renewed \NAME{}: a flexible, high-performance numerical library designed to address these challenges, providing an ED solver for generic quantum impurity problems.
 The library builds on the foundations of
@@
 Additionally, \NAME offers access to the Fock space of
-the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix (iRDM), enabling quantum information-inspired analyses providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems \cite{Walsh2021PNAS,Bellomia2024PRB}.
+the impurity system and thus, for instance, the possibility to evaluate the impurity reduced density matrix, enabling quantum information-inspired analyses providing insights into the entanglement properties, subsystem purity, and quantum correlations of interacting electron systems \cite{Walsh2021PNAS,Bellomia2024PRB}.
 In the quantum embedding context, these features are increasingly recognized as essential to understand the emergent behavior of correlated matter, including quantum criticality and superconductivity.
-% MC this last point is intrinsically DMFT (or embedding) and it has no connection with impurity physics. Right: I added an opening which should clarify the sentence.
 
@@
 This is a critical feature in DMFT or, more generally, in quantum embedding methods, to study hetero-structures, super-lattices, and disordered systems, where the local environment varies significantly across different sites.
-% This capability makes it 
-% possible to explore a wide range of inhomogeneous systems, including
-% oxide interfaces or disordered systems, where
-% translational symmetry is broken.
-%MC? Repetition.. removed
 
 %\paragraph{Interoperability}\\
-With the growing importance of quantum impurity models in the study of correlated materials, standardization and interoperability across software suites has
-become a critical necessity.
+With the growing importance of quantum impurity models in the study of correlated materials, standardization and interoperability across software suites have become critical necessities.
 \NAME has been expressly designed following this guiding principle. 
@@
 Overall, interoperability enhances the collective reach and reliability of these platforms, 
-improving reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat (see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}).
+improving the reproducibility and cross-validation of numerical results, with the ultimate goal of achieving standardization for quantum impurity solvers along the guiding principles of initiatives such as FAIRmat (see \href{https://www.fairmat-nfdi.eu/fairmat/}{fairmat-nfdi.eu/fairmat}).
 
 %\paragraph{closure}
-In this paper, we present the mathematical framework, implementation
-details, and key features of \NAME, along with several illustrative
-applications. We aim to demonstrate how this flexible,
+In this paper, we present the mathematical framework, details of the implementation, and key features of \NAME, along with several illustrative applications. We aim to demonstrate how this flexible,
 high-performance solver can be used to tackle a wide range of
@@
 The rest of this work is organized as follows. In \secu{SecInstall} we 
-briefly illustrate the overall structure of \NAME together with its dependencies, configuration
-and installation procedures. In \secu{SecEDIpack} we present the quantum impurity
-problem and review the software implementation in detail. In \secu{SecInterop} we thoroughly discuss the C-binding interface which is at the heart of the 
+briefly illustrate the overall structure of \NAME together with its dependencies, configuration, and installation procedures. In \secu{SecEDIpack} we present the quantum impurity
+problem and review the software implementation in detail. In \secu{SecInterop} we thoroughly discuss the C-binding interface that is at the heart of the 
 interoperability capabilities of \NAME. In this section we also discuss 4 interface layers: i) 

### 2025-06-02 05_examples.tex
v1.1 arXiv ready AA, MC and GB

@@
 
-In our examples based on the Fortran APIs, we rely on external open-source libraries, such as DMFTtools\footnote{\url{https://github.com/aamaricci/DMFTtools}} (also developed by some of the authors), to perform specific tasks, including evaluating the local Green’s function, implementing the self-consistency, constructing the tight-binding model, or calculating the kinetic energy.
+In our examples based on the Fortran APIs, we rely on external open-source libraries, such as DMFTtools (see \href{https://github.com/aamaricci/DMFTtools}{github.com/aamaricci/DMFTtools}), to perform specific tasks, including evaluating the local Green’s function, implementing the self-consistency, constructing the tight-binding model, or calculating the kinetic energy.
 Where appropriate, we include comments that reference these external procedures.
@@
 \cite{Georges1996RMP,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Kotliar2002PRL}.
-
+%
 Here, we present a guided implementation of the DMFT 
@@
 
-Below, we present the key components of a basic DMFT implementation 
+Below, we discuss the key components of a basic DMFT implementation 
 using \NAME for the Bethe lattice, employing either the Fortran or 
-C++ APIs. Fully operational versions of the two codes can be found 
+C++ APIs and which can be found 
 in the {\tt examples} directory of the \NAME source code. Both 
 samples share a similar initial structure, including memory 
-allocation, creation of the Bethe DOS and solver initialization.
-
+allocation, creation of the Bethe DOS and solver initialization:
  \begin{center}

### 2025-06-02 06_conclusions_acknowledgement_appendix.tex
v1.1 arXiv ready AA, MC and GB

--- 2025-06-01 06_conclusions_acknowledgement_appendix.tex
@@
 \section{Conclusions}
-We have presented \NAME{}, a versatile, high-performance solver for
-generic quantum impurity problems. Leveraging on the massively
+We have presented \NAME{}, a versatile and high-performance ED solver for generic quantum impurity problems. Building on the massively
 parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
-the library features new capabilities and symmetries within a unified
-framework, providing for instance reliable evaluations of the dynamical correlation
-functions of an arbitrary complex frequency.
-This makes it particularly well-suited for capturing the
-low-energy excitations and complex spectral features of strongly
-correlated systems.
-We have shown that this new version enables the evaluation of impurity
-reduced density matrices directly from Fock space quantities and thus unlocks 
-quantum information analyses of correlated systems, an increasingly
-essential tool to address emergent phases of quantum materials.
+the library features new capabilities allowing for different broken-symmetry solutions within a unified
+framework that provides, for instance, reliable evaluations of a variety of local dynamical correlation
+functions of an arbitrary complex frequency ranging from the Green's functions to superconducting, excitonic and magnetic response functions.
+
+This new version allows for an efficient evaluation of 
+reduced density matrices of the impurity directly from Fock space quantities and thus enables  
+quantum information analysis of correlated systems, which is becoming an essential tool to address emergent phases of quantum materials.
 
@@
 
-We thoroughly discussed the implementation of the \NAME library, the
+We thoroughly discussed the implementation of the \NAME library and its
 most important algorithms and classes. We presented in
 detail the third-party interfaces which extend ED
-capabilities beyond the realm of the library itself.   
+capabilities beyond the domain of the library itself. 
 Finally, we showcased the use of the \NAME software in different
-contexts via elaborated examples, which can serve as a reference for potential users.
+contexts through elaborated examples, which can serve as a reference for potential users.
 
@@
 natural foundation for future extensions.
-For instance to
-cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} where the
+For instance it provides a suitable basis to implement cluster-DMFT \cite{Capone2004PRB,Kotliar2006RMP,Park2008PRL} methods, where the
 impurity problem is generalized to include clusters of interacting
-sites. This approach would enable the treatment of spatial
-correlations beyond the single-site approximation, capturing effects
-such as d-wave pairing in high-temperature superconductors, charge
-order, and complex spin textures in strongly correlated systems.
-A different outlook is the development of an integration layer with other
-quantum embedding methods, such ghost Gutzwiller \cite{Lanata2015PRX},
+sites. This approach includes spatial correlations beyond the single-site approximation, capturing effects
+such as $d$-wave pairing, charge ordering, and complex spin textures in strongly correlated systems.
+A different outlook is the development of an integration layer with other quantum embedding methods, such as the ghost Gutzwiller scheme \cite{Lanata2015PRX},
 which heavily rely on solving effective impurity problems.    
-We anticipate that \NAME will become a valuable tool for the
-computational condensed matter community, supporting a wide range of
+We anticipate that \NAME will become a valuable tool for the computational condensed matter community, supporting a wide range of
 studies on strongly correlated materials and providing a reliable
@@
 \paragraph{Author contributions}
-A.A. designed the project, developed the main structure of the software and conceived the computational algorithms in the core library. 
+A.A.
+designed the project, developed the main structure of the software and conceived the computational algorithms in the core library.
+A.A.
+and M.C.
+conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library.
+M.C.
+devised the inclusion of the electron-phonon coupling and of the superconducting state.
 L.C., G.M., F.P.
@@
 A.K., M.W. and G.S. developed the integration with W2Dynamics.  
-A.A. and M.C. conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library. M.C. devised the inclusion of the electron-phonon coupling. 
 A.A., M.C., L.d.M. and G.S designed additional algorithms for extended functionalities of the core software.   

### 2025-06-02 05_examples.tex
v1.1.2 updated 05_examples.tex added figures and script into figures. compiles independently as for arXiv.

@@
     \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/G_iw.pdf}
+        {figures/G_iw.pdf}
     \includegraphics[width=0.5\linewidth]
-        {edipack2_examples/edipack2triqs/A_w.pdf}
+        {figures/A_w.pdf}
     \caption{\label{figEx3}%
@@
                  firstline=1, lastline=13]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+{figures/hubbard_kanamori.py}
 
@@
                  firstline=15, lastline=26]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+{figures/hubbard_kanamori.py}
 The next step is to define a TRIQS many-body operator expression that represents
@@
                  firstline=28, lastline=67]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+{figures/hubbard_kanamori.py}
 Finally, one creates a solver object and performs the actual calculation by
@@
                  firstline=69, lastline=83]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+{figures/hubbard_kanamori.py}
 The computation results are readily available as attributes of the solver
@@
                  firstline=85, lastline=113]
-{edipack2_examples/edipack2triqs/hubbard_kanamori.py}
+{figures/hubbard_kanamori.py}
 

### 2025-06-10 01_intro.tex
Updated version. Submitting to Scipost. Added arXiv version.

@@
 is the possibility to directly interface to both TRIQS \cite{Parcollet2015CPC} (Toolbox for Research on Interacting Quantum Systems) and
-W2Dynamics \cite{Wallerberger2019CPC} software suites, which are two of the most important and widely used computational frameworks in the field.
+w2dynamics \cite{Wallerberger2019CPC} software suites, which are two of the most important and widely used computational frameworks in the field.
 \NAME slots in as an alternative solver to the native Quantum Monte Carlo 
@@
 interoperability capabilities of \NAME. In this section we also discuss 4 interface layers: i) 
-the Python API, ii) the TRIQS interface, iii) the W2Dynamics interface and iv) an experimental, yet operative, Julia API.
+the Python API, ii) the TRIQS interface, iii) the w2dynamics interface and iv) an experimental, yet operative, Julia API.
 Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and  all the discussed extensions with a series of illustrative examples.

### 2025-06-10 02_install.tex
Updated version. Submitting to Scipost. Added arXiv version.

@@
 \end{lstlisting}
-Then, assuming to be in the software root directory ({\tt \$cd EDIpack}), a conventional out-of-source building can be performed using two alternative compilation backends.
+Then, assuming to be in the software root directory ({\tt \$cd EDIpack}), a conventional out-of-source building can be performed as follows:
+%using two alternative compilation backends.
 
-\begin{itemize}
-  \item {\bf GNU Make}\\
-This is the default CMake workflow:
+%\begin{itemize}
+%  \item {\bf GNU Make}\\
+%This is the default CMake workflow:
 \begin{lstlisting}[style=mybash,numbers=none]
@@
 
-\item{\bf Ninja}
+%\item{\bf Ninja}
 
-An alternative workflow employs the Ninja building backend with
-Fortran support. Ninja is generally faster and automatically supports
-parallel compilation:
-\begin{lstlisting}[style=mybash,numbers=none]
-mkdir build
-cd build
-cmake -GNinja ..
-ninja
-ninja install
-\end{lstlisting}
-\end{itemize}
+%An alternative workflow employs the Ninja building backend with
+%Fortran support. Ninja is generally faster and automatically supports
+%parallel compilation:
+%\begin{lstlisting}[style=mybash,numbers=none]
+%mkdir build
+%cd build
+%cmake -GNinja ..
+%ninja
+%ninja install
+%\end{lstlisting}
+%\end{itemize}
 

### 2025-06-10 04_cbinding.tex
Updated version. Submitting to Scipost. Added arXiv version.

@@
 Here we describe the implementation of an interoperability layer aiming at developing APIs for other languages as well as 
-integrating \NAME in complex scientific frameworks, e.g. TRIQS \cite{Parcollet2015CPC} or W2Dynamics \cite{Wallerberger2019CPC}.
+integrating \NAME in complex scientific frameworks, e.g. TRIQS \cite{Parcollet2015CPC} or w2dynamics \cite{Wallerberger2019CPC}.
 
@@
 
-\subsection{W2Dynamics interface}\label{sSecInteropW2DYN}
-\NAME is supported as alternative impurity solver in the W2Dynamics DMFT package \cite{Wallerberger2019CPC} available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
-The only prerequisite to use this option is the presence of a functioning EDIpack2py installation (see \secu{sSecInteropEDIpy}), which W2Dynamics will attempt to import at runtime only if the user sets the appropriate configuration parameters.
-The  behavior of W2Dynamics is controlled by means of an input file, by default called
-{\tt Parameters.in}.
+\subsection{w2dynamics interface}\label{sSecInteropw2dyN}
+\NAME is supported as an alternative impurity solver in the w2dynamics DMFT package \cite{Wallerberger2019CPC}, available on \href{https://github.com/w2dynamics/w2dynamics}{github.com/w2dynamics/w2dynamics}.
+This integration enables users to 
+seamlessly switch from the default hybridization expansion continuous-time QMC  (CT-HYB), included natively
+in w2dynamics, to the \NAME ED solver. This requires no changes to the input file and at most minor  adjustments to configuration parameters.
 
-In order to use the \NAME impurity solver for a calculation instead of the built-in implementation of the CT-HYB algorithm, the user needs to set the {\tt solver} parameter in section {\tt General} to {\tt EDIpack}.
-In line to the current design of W2Dynamics, the \NAME solver is configured and controlled by setting the content of a specific section in the parameters file, called {\tt [EDIPACK]}.
+\subsubsection{Installation}\label{sSecInteropw2dyNPrereq}
+Use of the interface requires a current version of w2dynamics ($\geq 1.1.6$) and a working installation of EDIpack2py (see 
+\secu{sSecInteropEDIpy}). 
+Users may build and optionally install w2dynamics using conventional CMake based source installation: 
+\begin{lstlisting}[style=mybash]
+git clone https://github.com/w2dynamics/w2dynamics.git
+cd w2dynamics
+mkdir build
+cd build
+cmake ..
+make install
+\end{lstlisting}
+This enables the default CT-HYB solver. For DMFT calculations 
+using the \NAME interface, it is sufficient that the 
+\texttt{EDIpack2py} module is available for import at runtime, and no compilation is required on the w2dynamics side.
 
-For most of the \NAME input variables, W2Dynamics accepts a parameter of the same name (in all uppercase letters) that allows the corresponding variable to be set, and is declared in the {\tt [EDIPACK]} section of the parameters file.
-This set of variables includes most of the control parameters to be tuned for a specific DMFT-ED calculation, such as the number of bath elements {\tt NBATH} and options for the bath fitting and diagonalization algorithms.
+\subsubsection{Implementation}\label{sSecInteropw2dyNPrereq}
+The \NAME interface is implemented as the class \texttt{EDIpackSolver} 
+in the Python module \texttt{w2dyn.dmft.edipack\_solver}. It is a subclass of 
+\texttt{ImpuritySolver} and can be used as a drop-in replacement for 
+\texttt{CtHybSolver}. The w2dynamics DMFT solver provides the hybridization 
+function and local Hamiltonian for the auxiliary impurity problem via 
+an \texttt{ImpurityProblem} instance passed to \texttt{set\_problem}. It then 
+it invokes the \texttt{solve} method to obtain the results, including, 
+e.g., the Green's function, as an \texttt{ImpurityResult}.
 %
-A second set of input variables, including physical quantities such as {\tt NORB}, {\tt ULOC}, {\tt BETA}, and {\tt   NLOOP}, directly map to parameters available in other sections of the W2Dynamics input file, such as {\tt [General]} or {\tt [Atoms]}.
-An example of a properly formatted input file is provided in \secu{SecExamples}.
-The full set of configuration options can be found in the {\tt configspec} file, contained in the subfolder {\tt w2dyn/auxiliaries} of the W2Dynamics repository.
-See also \cite{Wallerberger2019CPC}
-for further details.
+The \texttt{solve} method sets up the calculation using \NAME by calling 
+\texttt{EDIpack2py}, writing input files to a subdirectory, running 
+\NAME, and processing both the return values of \texttt{EDIpack2py} 
+methods and the output files. It then formats the results following the w2dynamics conventions.
 
-%All of the these variables correspond to or follow from configuration parameters that a user also needs to set for a CT-HYB calculation, and in order to present a consistent and rather ``solver-agnostic'' user interface, no redundant parameters are added to the {\tt EDIPACK} section and the usual parameters such as {\tt   beta} in section {\tt General} must be used instead.
-Note however in particular that if the \NAME solver is used, {\tt beta} is by default only used as cut-off and does not imply a finite temperature calculation unless the user explicitly sets the parameter {\tt   ED\_FINITE\_TEMP} in section {\tt EDIPACK} to {\tt True}.
+This implementation allows w2dynamics to abstract over the specific 
+choice of impurity solver as much as possible. \NAME is only called 
+to solve individual impurity problems, while the standard w2dynamics 
+code handles higher-level tasks such as the DMFT loop, support for 
+multiple inequivalent impurities, and the user-facing interface via 
+standard w2dynamics input files and output in its usual HDF5 format.
 
-Specific \NAME solver features are abstracted away to the greatest reasonable extent by having the input, output, and DMFT loop handled by W2Dynamics in a way closely resembling the standard CT-HYB code.
-For instance, results such as the Green's functions are stored into the W2Dynamics HDF5 output file in the typical format.
-Moreover, W2Dynamics uses only its own logic for calculations with multiple inequivalent impurities without relying on any related implementation provided by \NAME{2Ineq}.
-As a consequence, functionalities that would require specific support from W2Dynamics and are currently not available can not be used through the interface, including e.g.\ the solution of impurity problems in the superconductive phase, i.e.
-{\tt ed\_mode=superc}.
+As a result, features that require explicit support from w2dynamics 
+but are not yet implemented cannot be used through the \NAME interface. 
+In particular, solving impurity problems in the superconducting phase 
+(\texttt{ed\_mode=superc}) is not yet  supported.
+
+\subsubsection{Configuration and Usage}\label{sSecInteropw2dyNConfig}
+w2dynamics reads its configuration parameters from a file named \texttt{Parameters.in} by default.
+To use \NAME methods, the {\tt solver} parameter in the section {\tt General} needs to be set as follows:
+\begin{lstlisting}[style=mybash]
+[General]
+solver = EDIPACK
+\end{lstlisting}
+Additional parameters specific to \NAME are defined in the accessory section \texttt{[EDIPACK]}.
+These set many of the \NAME's corresponding input variables (in  uppercase letters).
+For example,  the number of bath sites {\tt NBATH} can be configured as:
+\begin{lstlisting}[style=mybash]
+[EDIPACK]
+NBATH = 7
+\end{lstlisting}
+
+This section includes also the options to control the bath optimization and  diagonalization algorithms.
+Other input variables that define the model (e.g., {\tt NORB}, {\tt ULOC}, and {\tt BETA}) or relate to functionalities handled by
+w2dynamics itself (e.g., \texttt{NLOOP}) must be provided through 
+standard parameters in other sections, such as \texttt{[General]} or 
+\texttt{[Atoms]}. An example of a complete properly formatted input file is provided in \secu{SecExamplesBetheDMFTW2D}.
+The full set of configuration parameters can be found in the {\tt configspec} file, located in the {\tt w2dyn/auxiliaries} of the w2dynamics repository, see  \cite{Wallerberger2019CPC} for further details.
+
+A calculation can be launched by running the w2dynamics DMFT program 
+\texttt{DMFT.py}, which supports parallel execution via MPI to take 
+advantage of \NAME's parallelization.
+
+\subsubsection{Output and Results}\label{sSecInteropw2dyNOutput}
+Calculation results are stored in an HDF5 file, grouped by DMFT iteration (with group names formatted as {\tt dmft-001}) and inequivalent impurity (for impurity-specific data, using group names like 
+\texttt{ineq-001}). 
+The content of this file can be accessed using the 
+\texttt{hgrep} script provided with w2dynamics or other HDF5 tools. 
+Stored quantities include, for example, the impurity self-energy (in 
+datasets \texttt{siw-full}) and Green's function (in 
+\texttt{giw-full}) on the Matsubara frequency axis, as well as single 
+and double occupations (in \texttt{occ}). Additionally, the interface 
+provides access to results not available when using the CT-HYB solver, 
+such as the impurity self-energy (\texttt{somega}) and Green's function 
+(\texttt{gomega}) on the real frequency axis.
+Standard \NAME output files for each individual ED impurity solution are also available in subdirectories named like the the main HDF5 output file with iteration and impurity numbers appended.
 

### 2025-06-10 05_examples.tex
Updated version. Submitting to Scipost. Added arXiv version.

@@
 
-On the other hand, the results obtained with W2Dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which seamlessly handles all these tasks.
+On the other hand, the results obtained with w2dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which seamlessly handles all these tasks.
 Similarly, the TRIQS library offers an comprehensive framework fo manipulating Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
@@
 
-\subsubsection{Finite temperature (W2Dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
-To demonstrate how the W2Dynamics interface integrates with  \NAME, we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using W2Dynamics. 
-In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in W2Dynamics against the \NAME solver at finite temperature.
-
-Unlike \NAME, which provides only the impurity solver and bath optimization procedures and requires the user to implement the DMFT algorithm themselves (potentially using various methods), W2Dynamics adopts a fundamentally different approach: a single Python script, {\tt DMFT.py}, handles the entire DMFT calculation, leveraging dedicated classes that implement the generic self-consistency.
-The W2Dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
-Further information about the functioning of W2Dynamics can be found in Ref.
+\subsubsection{Finite temperature (w2dynamics interface, CT-HYB benchmark)}\label{SecExamplesBetheDMFTW2D}
+To demonstrate how the w2dynamics interface integrates with  \NAME, we briefly discuss how to solve the same problem, i.e. the Hubbard model on the Bethe lattice within DMFT using w2dynamics. 
+In order to showcase the capabilities of \NAME to address low-temperature problems, we compare the continuous-time Quantum Monte Carlo (CTQMC) solver using the hybridization expansion method (CT-HYB) included in w2dynamics against the \NAME solver at finite temperature.
+
+Unlike \NAME, which provides only the impurity solver and bath optimization procedures and requires the user to implement the DMFT algorithm themselves (potentially using various methods), w2dynamics adopts a fundamentally different approach: a single Python script, {\tt DMFT.py}, handles the entire DMFT calculation, leveraging dedicated classes that implement the generic self-consistency.
+The w2dynamics calculation is then entirely controlled by a model-dependent parameters file {\tt Parameters.in}, which contains a number of variable specifications including options to control the ED solver inherited from \NAME.
+Further information about the functioning of w2dynamics can be found in Ref.
 \cite{Wallerberger2019CPC}
 
-Another important difference concerns the initial point of the iterative DMFT solution algorithm: while \NAME starts from a given discrete bath, W2Dynamics is initialized with a zero self-energy function or alternatively reads this quantity from a converged solution file.
-Thus, when using the \NAME interface in W2Dynamics, the initial Weiss field is determined using self-consistency and  an initial discrete bath is obtained through the \NAME bath optimization procedure.
-
-The following is the W2Dynamics configuration file used to solve the Bethe lattice problem at finite temperature: 
+Another important difference concerns the initial point of the iterative DMFT solution algorithm: while \NAME starts from a given discrete bath, w2dynamics is initialized with a zero self-energy function or alternatively reads this quantity from a converged solution file.
+Thus, when using the \NAME interface in w2dynamics, the initial Weiss field is determined using self-consistency and  an initial discrete bath is obtained through the \NAME bath optimization procedure.
+
+The following is the w2dynamics configuration file used to solve the Bethe lattice problem at finite temperature: 
 \begin{lstlisting}[style=mybash,language={},numbers=none,basicstyle={\scriptsize\ttfamily}]
@@
 
-The results are collected into an HDF5 \cite{The_HDF_Group_Hierarchical_Data_Format} archive in the usual W2Dynamics format, including output quantities inherited from \NAME.
-Results can be viewed using the script {\tt hgrep} provided with W2Dynamics or with other HDF5 tools.
+The results are collected into an HDF5 \cite{The_HDF_Group_Hierarchical_Data_Format} archive in the usual w2dynamics format, including output quantities inherited from \NAME.
+Results can be viewed using the script {\tt hgrep} provided with w2dynamics or with other HDF5 tools.
 In this example we extract the Matsubara self-energy function $\Sigma(i\omega_n)$ for the last DMFT iteration:
@@
 Data are for $T/D=0.01$ and $U/D=2.0$.
-CTQMC results from the solver included with W2Dynamics are compared against \NAME ED results, used both through the W2Dynamics interface and with a standalone Fortran program.
+CTQMC results from the solver included with w2dynamics are compared against \NAME ED results, used both through the w2dynamics interface and with a standalone Fortran program.
         }
@@
 
-In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC and the \NAME ED method as solvers in W2Dynamics.
+In \figu{figEx1W} we report a comparison of the results obtained using the hybridization expansion CTQMC and the \NAME ED method as solvers in w2dynamics.
 In addition we compare with results obtained using the Fortran API directly as shown in the previous subsection.
@@
 
-In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ which is the direct output for both methods (note that W2Dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver).
+In panel (A) we show the behavior of the imaginary part of the impurity Green's function $\Im{G}(i\omega_n)$ which is the direct output for both methods (note that w2dynamics does not directly have access to the real-axis Green's function when using the CTQMC solver).
 In panel (B) we show the same comparison for impurity self-energy $\Im{\Sigma}(i\omega_n)$.

### 2025-06-10 06_conclusions_acknowledgement_appendix.tex
v1.2 arXiv
Updated version. Submitting to Scipost. Added arXiv version.

@@
 computational frameworks, like TRIQS \cite{Parcollet2015CPC} and
-W2Dynamics \cite{Wallerberger2019CPC}, expanding the
+w2dynamics \cite{Wallerberger2019CPC}, expanding the
 functionality of these platforms and providing a robust foundation for
@@
 I.K. developed the TRIQS interface and contributed to the testing part. 
-A.K., M.W. and G.S. developed the integration with W2Dynamics.  
+A.K., M.W. and G.S. developed the integration with w2dynamics.  
 A.A., M.C., L.d.M. and G.S designed additional algorithms for extended functionalities of the core software.   
@@
 F.P. acknowledges support from the Swiss National Science Foundation via NCCR Marvel and SNSF Grant No. 200021-196966.
-%M.W.
+M.W. acknowledges support from the Austrian Science Fund (FWF) through grant DOI 10.55776/P36332.
 %G.M.

### 2025-07-12 01_intro.tex
Initial Overleaf Import

@@
 In several of these embedding schemes, most notably DMFT, the complex physics of the lattice systems gets reduced to an effective self-consistent quantum impurity problem.
-By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials, including Mott insulators, heavy fermion compounds and unconventional superconductors.
+By accounting for local quantum fluctuations, DMFT successfully describes the most important physical features of correlated materials~\cite{Georges1996RMP,Kotliar2006RMP}, including Mott insulators~\cite{Georges1992PRL,Zhang1993PRLb,Rozenberg1994PRB,Kotliar1996PRB,Rozenberg1999PRL,Kotliar1999EPJB,Kotliar2000PRL,Bulla2001PRB,Capone2001PRL,Kotliar2002PRL,Limelette2003S8}, heavy fermion compounds~\cite{Shim2007N,De-Leo2008PRL,Haule2009NP,Crippa2024NC,Gleis2024PRX,Crispino2025PRL,Gleis2025PRL} and unconventional superconductors~\cite{Emery1987PRL,Caffarel1994PRL,Capone2001PRL,Capone2002Science,Toschi2005NJP,Toschi2005PRB,Haule2007PRB,Medici2014PRL,Giannetti2016AIP,Mazza2021PRB,Walsh2021PNAS}.
+
 %
@@
 Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and  all the discussed extensions with a series of illustrative examples. 
+In \secu{SecConclusions} we present some concluding remarks and considerations.
 

### 2025-07-12 03_edipack2.tex
Initial Overleaf Import

@@
 orbital-dependent on-site energies or amplitudes, spin-orbit coupling or other single-particle terms.
-In \NAME the matrix $\hat{h}_0$ is set by the user passing a complex array through the function {\tt ed\_set\_Hloc}.
+In \NAME the matrix $\hat{h}_0$ must be set by the user before the solver is initialized using the function {\tt ed\_set\_Hloc}.
+The latter  accepts complex arrays of rank-2 or 4 as only argument.
+In a quantum embedding framework, e.g.
+DMFT, the matrix $\hat{h}_0$ corresponds to the local part of the non-interacting Hamiltonian.
+Some examples of use can be found in  \secu{SecExamples}.
 
@@
 \end{equation}
+where the symbols $\{ijkl\}$ collect both orbital and spin indices, e.g.  $i=\alpha\sigma$.   
 However, we typically 
@@
 
-For each phonon mode, one has to introduce a cut-off in the phonon number, which has to be chosen according to the value of the electron-phonon coupling \cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction \cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}.
+For each phonon mode, one has to introduce a cut-off in the phonon number to avoid unbounded growth of the phonons Fock space.
+The cutoff has to be chosen in a problem dependent way, also considering the value of the electron-phonon coupling \cite{Capone2003PRL,Capone2006PRB} and its interplay with the electron-electron interaction \cite{Capone2004PRL,Capone2004PRLsc,Sangiovanni2005PRL,Paci2005PRL,Sangiovanni2006PRL,Sangiovanni2006PRBa,Paci2006PRB}.
 The larger the number of excited phonons in the ground state, the larger the cutoff. 
-For practical calculations around 20 phonons are sufficient to achieve converged results except for the deep polaronic regime \cite{Capone2003PRL}.
-Choosing properly the shift $A_m$, one can reduce the number of excited phonons in the ground state and consequently the required cutoff. 
+For practical calculations a cutoff of about 20 phonons is usually sufficient to achieve converged results, except for the deep polaronic regime \cite{Capone2003PRL}.
+
+In many cases one can reduce the number of excited phonons in the ground state, and consequently the required cutoff, by choosing properly the shift $A_m$.  
 Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.
@@
 \begin{align*}
-  b\ket{p} &= \sqrt{p-1}\ket{p}, \\
-  b^\dagger\ket{p} &= \sqrt{p}\ket{p}.
+  b\ket{p} &= \sqrt{p-1}\ket{p-1}, \\
+  b^\dagger\ket{p} &= \sqrt{p}\ket{p+1}.
 \end{align*}
@@
 sector amounts to defining an injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the electronic states $\ket{i}$
-within a given symmetry sector $\SS_{\vec{Q}}$ to the states $\ket{I_e}$ in the electronic Fock space. 
-This map is typically implemented as a rank-1
-integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
+$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutives indexing of the electronic states  $\ket{i}$
+within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
+This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
 The global Fock state $\ket{I}=\ket{I_e}\ket{p}$, including the phonon part, is univocally determined by the relation: $I\to I_e + p\,2^{2 N_s}$.
@@
 These functions use different algorithms depending on the nature 
-of the quantum numbers $\vec{Q}$, i.e.
-the value of {\tt ed\_mode}.
-The following code snippets summarize the various available implementations.
-The core idea is to loop over the Fock states and  enforce the quantum number constraint:
+of the quantum numbers $\vec{Q}$, i.e. the value of {\tt ed\_mode}. The key idea is to loop over the Fock states and enforce the quantum number constraint.
+The following code snippets summarize the various available implementations and serve as a basis to understand other parts of the software, see \secu{CodeSparseMap}.  
 \begin{center}
@@
 $$
-\OO\ket{v} = \sum_i a_i C_{\a_i,\s_i}+ b_i C^{\dagger}_{\b_i,\r_i}\ket{v}
+\OO\ket{v} = \sum_i \left( a_i C_{\a_i,\s_i}+ b_i C^{\dagger}_{\b_i,\r_i}\right)\ket{v}
 $$ 
@@
 supported and controlled by the input parameters {\tt ULOC}$=U$, {\tt
-  UST}$=U'$, {\tt JH}$=J$, {\tt JX}$=J_{x}$ and {\tt JP}$=J_{p}$.
+  UST}$=U'$, {\tt JH}$=J$, {\tt JX}$=J_{X}$ and {\tt JP}$=J_{P}$.
 These quantities can be specified either in the input file or directly
@@
 $$
+where the indices $\{ijkl\}$ condense orbital and spin degrees of freedom, e.g. $i=\alpha\sigma$. 
 Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement.
@@
 elements and one for their respective column indices. 
-In an MPI framework, elements local in the memory are store in a separate set of row, i.e. {\tt loc} while keeping track of the indices of the global share, {\tt istart, ishift, iend}. 
+In an MPI framework, each matrix instance on any given thread stores only a given set $Q=D_\SS/N_{cpu}$ of matrix rows.
+In addition, the elements local in the memory are stored in a separate set of rows, i.e.
+{\tt loc}, and used to speed up the execution of matrix-vector product.
+We keep track, for each thread, of the relative position of the matrix rows $q=1,\dots,Q$ with respect to the global indexing $i=1,\dots,D_\SS$, through the definition of additional indices {\tt istart, iend, ishift}.
+These correspond, respectively, to the initial global index $i_1$ for $q=1$, the final global index $i_Q$ for $q=Q$ and the integer shift mapping the index $q$ into $i$.
 Each instance of {\tt sparse\_matrix\_csr} can be stored serially (one copy per process) or distributed across multiple 
@@
 
-% \begin{lstlisting}[style=fstyle,numbers=none]
-% ! sparse row: contains the NNZ elements on any row of the sparse matrix.
-% type sparse_row_csr
-%    integer                                   :: size  !size of the row = NNZ
-%    real(8),dimension(:),allocatable          :: dvals !rank-1 array for double precision
-%    complex(8),dimension(:),allocatable       :: cvals !rank-1 array for double complex
-%    integer,dimension(:),allocatable          :: cols  !rank-1 array for column indices
-% end type sparse_row_csr
-% ! Sparse Matrix: allocatable array of sparse rows
-% type sparse_matrix_csr
-%    type(sparse_row_csr),dimension(:),pointer :: row  !array of {\tt sparse\_row\_csr} 
-%    integer                                   :: Nrow !total number of rows
-%    integer                                   :: Ncol !total number of columns
-%    logical                                   :: status=.false. !Allocation status
-% #ifdef _MPI
-%    type(sparse_row_csr),dimension(:),pointer :: loc      !array for the diagonal blocks
-%    integer                                   :: istart=0 !start index MPI range
-%    integer                                   :: iend=0   !end index MPI range
-%    integer                                   :: ishift=0 !shift index MPI range
-%    logical                                   :: mpi=.false.
-% #endif
-% end type sparse_matrix_csr
-% \end{lstlisting}
+\begin{lstlisting}[style=fstyle,numbers=none]
+! sparse row: contains the NNZ elements on any row of the sparse matrix.
+type sparse_row_csr
+   integer                                   :: size  !size of the row = NNZ
+   real(8),dimension(:),allocatable          :: dvals !rank-1 array for double precision
+   complex(8),dimension(:),allocatable       :: cvals !rank-1 array for double complex
+   integer,dimension(:),allocatable          :: cols  !rank-1 array for column indices
+end type sparse_row_csr
+! Sparse Matrix: allocatable array of sparse rows
+type sparse_matrix_csr
+   type(sparse_row_csr),dimension(:),pointer :: row  !array of {\tt sparse\_row\_csr} 
+   integer                                   :: Nrow !total number of rows
+   integer                                   :: Ncol !total number of columns
+   logical                                   :: status=.false. !Allocation status
+#ifdef _MPI
+   type(sparse_row_csr),dimension(:),pointer :: loc      !array for the diagonal blocks
+   integer                                   :: istart=0 !start index MPI range
+   integer                                   :: iend=0   !end index MPI range
+   integer                                   :: ishift=0 !shift index MPI range
+   logical                                   :: mpi=.false.
+#endif
+end type sparse_matrix_csr
+\end{lstlisting}
 
@@
 \subsubsection{Sparse map}\label{CodeSparseMap}
-As discussed in \secu{sSecRDM}, the construction of a symmetry 
+As will be discussed in \secu{sSecRDM}, the construction of a symmetry 
 sector often requires associating each sector state $\ket{i}$ with 
@@
 integers $B_\s$ corresponding to any bath bit set
-$\vec{B_\s}$ associated with $\vec{I}_\s$ by the sector symmetry constraint: $\#\vec{I}_\s + \#\vec{B}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
+$\vec{B}_\s$ associated with $\vec{I}_\s$ by the sector symmetry constraint: $\#\vec{I}_\s + \#\vec{B}_\s = \mathtt{popcnt}(I_\s) + \mathtt{popcnt}(B_\s)= N_\s$.
 Thus, any given {\it key-value} combination 
@@
 ground state energy, $\beta=1/T$ is the inverse temperature ($k_B=1$) and \texttt{cutoff} is an input parameter fixing an {\it a priori} energy threshold.
-
+In the following we indicate with $N_{\tt state\_list}$ the number of eigen-solutions stored in the list. 
 By successive call to the \NAME solver, the list dynamically adjusts to optimize the distribution of states 
@@
 $$
-C(z) = \tfrac{1}{Z}\sum_n e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}(\AA)|^2}{ z
+C(z) = \tfrac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n} \sum_{m=1}^{N} \tfrac{|w_{mn}(\AA)|^2}{ z
   - dE_{mn}}
@@
 where $w_{mn}(\AA)$ is the weight determined by the amplitude of operator $\AA$ between the
-$m^{\rm th}$ eigenstate and the $n^{\rm th}$ Krylov basis vector and
+$m^{\rm th}$ eigenstate and the $n^{\rm th}$ Krylov basis vector, 
 $dE_{mn}=E_m-E_n$ is the corresponding excitation energy.
@@
 
-% \begin{lstlisting}[style=fstyle,numbers=none]   
-% !The contributions to the GF Kallen-Lehmann sum are stored as
-% !GF_{ab,sr}%state%channel%{w,e}.
-% !A couple of weight,poles {w,e} is stored: 
-% !for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
-% !
-% !Sub-class: contains the actual weight and poles:
-% type GFspectrum
-%    complex(8),dimension(:),allocatable       :: weight
-%    real(8),dimension(:),allocatable          :: poles
-% end type GFspectrum
-% !
-% !N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
-% !Subclass: contains a given set of weights and poles.
-% !Each instance of this subclass corresponds to a given input state 
-% !and a given operator in the Kallen-Lehmann representation.  
-% type GFchannel
-%    type(GFspectrum),dimension(:),allocatable :: channel 
-% end type GFchannel
-% !
-% !Main class: stores  weights and poles of a given DCF 
-% !obtained through the dynamical Lanczos algorithm.
-% !state_list%size = Number of states in the spectrum 
-% type GFmatrix
-%    type(GFchannel),dimension(:),allocatable  :: state
-%    logical                                   :: status=.false. !Allocation status
-% end type GFmatrix
-% \end{lstlisting}
+\begin{lstlisting}[style=fstyle,numbers=none]   
+!The contributions to the GF Kallen-Lehmann sum are stored as
+!GF_{ab,sr}%state%channel%{w,e}.
+!A couple of weight,poles {w,e} is stored: 
+!for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
+!
+!Sub-class: contains the actual weight and poles:
+type GFspectrum
+   complex(8),dimension(:),allocatable       :: weight
+   real(8),dimension(:),allocatable          :: poles
+end type GFspectrum
+!
+!N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
+!Subclass: contains a given set of weights and poles.
+!Each instance of this subclass corresponds to a given input state 
+!and a given operator in the Kallen-Lehmann representation.  
+type GFchannel
+   type(GFspectrum),dimension(:),allocatable :: channel 
+end type GFchannel
+!
+!Main class: stores  weights and poles of a given DCF 
+!obtained through the dynamical Lanczos algorithm.
+!state_list%size = Number of states in the spectrum 
+type GFmatrix
+   type(GFchannel),dimension(:),allocatable  :: state
+   logical                                   :: status=.false. !Allocation status
+end type GFmatrix
+\end{lstlisting}
 
@@
 $$
-
 where $\tau^{i=0,x,y,z}$ are Pauli matrices.
@@
     %
-    & =\frac{1}{Z}\sum_n e^{-\beta E_n}\sum_m
+    & =\frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}\sum_m
   \frac{ |\bra{\psi_m}\AA^\dagger \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
@@
   \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_n e^{-\beta E_n}
+    C_\AA(z)  &\simeq \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
     \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^\dagger\ket{\psi_n} |a^n_m|^2}{
@@
     %
-    &= \frac{1}{Z}\sum_n\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
+    &= \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}}\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
     \equiv \frac{1}{Z}\sum_n
@@
 poles. We introduced the notation $g(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn})$
-for the {\tt gfmatrix} object containing the weights $w(\AA)^{\nu}_{mn}$ and
-poles $dE(\AA)^{\nu}_{mn}$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
+for the {\tt gfmatrix} object containing the weights $w^{\nu}_{mn}(\AA)$ and
+poles $dE^{\nu}_{mn}(\AA)$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
 contributing to the low energy spectrum, for every order $m$ of the
@@
 \begin{equation}
-\ibra \OO\iket = \frac{1}{Z}\sum_n e^{-\beta E_n}
-\bra{\psi_n} \OO \ket{\psi_n}\simeq \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
+\ibra \OO\iket = \frac{1}{Z}\sum_{n=1}^{\infty} e^{-\beta E_n}
+\bra{\psi_n} \OO \ket{\psi_n}\simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
 \bra{\psi_n} \OO \ket{\psi_n},
@@
 where $E_n$ and $\ket{\psi_n}$ are the $N_{\tt state\_list}$ low-lying eigenstates 
-of the system stored in the {\tt state\_list}. 
+of the system stored in the {\tt state\_list} and $\tilde{Z}=\sum_{n=1}^{N_{\tt state\_list}}e^{-\beta E_n}$. 
 % This approach 
@@
 %For $q\neq2$ we are implementing something that is not a matrix norm (better to not comment on it explicitly)
-We prospect to expand the choices for \texttt{cg\_norm} in future updates of \NAME, as the \textbf{nonsu2} and \textbf{superc}
+ \fixme{We prospect to expand the choices for \texttt{cg\_norm} in future updates of \NAME, as the \textbf{nonsu2} and \textbf{superc}
 diagonalization modes entail nontrivial subtleties in optimizing 
-the off-diagonal components of $X$.
+the off-diagonal components of $X$.}
 \item \texttt{cg\_Ftol} - Controls the fit tolerance, setting the 

### 2025-07-12 05_examples.tex
Initial Overleaf Import

@@
 library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages. 
+The codes,the data and the script to generate the figures presented here can be found in the repository \href{https://github.com/EDIpack/EDIpack2examples}{github.com/EDIpack/EDIpack2examples}.
 
@@
 On the other hand, the results obtained with w2dynamics rely on the internal framework provided by the software itself -- see the script \texttt{DMFT.py} \cite{Wallerberger2019CPC}, which seamlessly handles all these tasks.
-Similarly, the TRIQS library offers an comprehensive framework fo manipulating Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
+Similarly, the TRIQS library offers a comprehensive framework for manipulating Green’s functions and related quantities \cite{Parcollet2015CPC}, making these tasks easily accessible while maintaining very high standards of optimization and accuracy.
 
@@
 discretized effective bath, the characteristic features of the Mott 
-transition are clearly visible. At low energies, a renormalized 
+transition are clearly visible. The results in panel (A) have been obtained using a broadening {\tt eps=0.01}. 
+At low energies, a renormalized 
 quasi-particle peak develops at the Fermi level ($\omega = 0$). 
@@
 attractive Hubbard model \cite{Caffarel1994PRL,Toschi2005NJP,Toschi2005PRB} on a two-dimensional square lattice. 
-This  example two main goals: (i) to demonstrate \NAME's support for $s$-wave superconductivity, and (ii) to showcase the Python API through a concrete example.
+This  example has two main goals: (i) to demonstrate \NAME's support for $s$-wave superconductivity, and (ii) to showcase the Python API through a concrete example.
 
@@
 The essential features of the ground state phase diagram have been established by intensive multi-method analyses \cite{Rachel2018ROPIP}.
-For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to large repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio\footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states
-at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{Sorella1992ELE,Castro-Neto2009RMP}.}.
+For $\lambda_\mathrm{so}=0$ the model describes a Dirac semimetal, up to large repulsion, and magnetizes to an isotropic Néel state above a critical $U/t$ ratio \cite{Sorella1992ELE,Castro-Neto2009RMP}.
+% \footnote{In contrast to the expectations for a generic half-filled bipartite lattice, for which the ground state is antiferromagnetic for any nonzero interaction, this property descends from the peculiar properties of Dirac cones: the vanishing density of states at the Fermi level renders the logarithmic instability ineffective, even in the presence of perfect nesting \cite{Sorella1992ELE,Castro-Neto2009RMP}.}.
 For a finite spin-orbit coupling $\lambda_\mathrm{so}\neq0$, the quantum spin-Hall state results increasingly stable against magnetic ordering, due to its symmetry-protected nontrivial topology.

### 2025-07-12 Reply_EDIPACK2.tex
Initial Overleaf Import

\documentclass[a4paper,12pt]{letter}
\usepackage [english]{babel}
\usepackage [autostyle, english = american]{csquotes}
\MakeOuterQuote{"}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage[nodayofweek]{datetime}
\usepackage{geometry}
\geometry{a4paper, inner=25mm, top=20mm, outer=25mm , bottom=20mm}
\usepackage{setspace}
\usepackage[svgnames]{xcolor}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=red]{hyperref}
\usepackage[normalem]{ulem}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{physics}
\usepackage{todonotes}

%-------------------------------------------

\newcommand{\refereesays}[1]
{{\it \color{NavyBlue}{#1}}\vspace{1cm}}

%SIMBOLI VARI
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\def\a{\alpha}
\def\b{\beta}
\def\g{\gamma}
\def\d{\delta}
\def\e{\varepsilon}
\def\z{\zeta}
\def\h{\eta}
\def\th{\theta}
\def\k{\kappa}
\def\l{\lambda}
 \def\m{\mu}
\def\n{\nu}
\def\x{\xi}
\def\p{\pi}
\def\r{\rho}
 \def\s{\sigma}
\def\t{\tau}
\def\f{\varphi}
\def\ph{\varphi}
\def\c{\chi}
\def\ps{\pi}
\def\y{\upsilon}
\def\o{\omega}
\def\si{\varsigma}
\def\G{\Gamma}
\def\D{\Delta}
\def\Th{\Theta}
\def\L{\Lambda}
\def\X{\Xi}
\def\P{\Pi}
\def\Si{\Sigma}
\def\F{\Phi}
\def\Ps{\Psi}
\def\O{\Omega}
\def\Y{\Upsilon}
\def\PP{{\cal P}}
\def\EE{{\cal E}}
\def\MM{{\cal M}}
\def\VV{{\cal V}}
\def\CC{{\cal C}}
\def\FF{{\cal F}}
\def\HH{{\cal H}}
\def\WW{{\cal W}}
\def\TT{{\cal T}}
\def\NN{{\cal N}}
\def\BB{{\cal B}}
\def\II{{\cal I}}
\def\RR{{\cal R}}
\def\LL{{\cal L}}
\def\JJ{{\cal J}}
\def\OO{{\cal O}}
\def\DD{{\cal D}}
\def\GG{{\cal G}}
\def\RRR{\mathbb{R}}
\def\CCC{\mathbb{C}}
\def\up{\uparrow}
\def\down{\downarrow}
\def\bra{\langle}
\def\ket{\rangle}

%Author's comments
\def \fixme#1{\color{Red}{fixme: #1}}
\date{\today}

\begin{document}

{\textbf{Reply to  Referee A}}

We thank the refereee for their time and work in reviewing our
manuscript. Here below we address point by point all the issues raised
in their reports.

\refereesays{Exact diagonalization (ED) plays a vital role in the study of quantum impurity problems. In this work, the authors present an ED library and describe its usage in considerable detail. While it builds upon the previous EDIpack library, the manuscript introduces sufficient new developments to warrant a separate publication. Notably, several significant extensions and improvements are included, such as a unified framework for zero- and finite-temperature calculations for a wide range of impurity models; access to the full complex frequency plane; access to the Fock space and the ability to evaluate quantities like reduced density matrices; support for inequivalent impurities; integration with other programming languages and scientific libraries; and compatibility with widely used software suites such as TRIQS and w2dynamics.}

\refereesays{Overall, the paper is well written and highly detailed, allowing new users to install and utilize the library with ease. Furthermore, the comprehensive DMFT tests, demonstrated through a variety of examples and accompanied by corresponding scripts, provide excellent starting points for newcomers. I believe this work makes a valuable contribution to the community and am therefore pleased to recommend its publication in SciPost.}

\begin{enumerate}

\item \refereesays{On page 3, a large portion of paragraph 3, which introduces DMFT, lacks citations. For example, the authors mention the success of DMFT in capturing key features of various materials, including Mott insulators, heavy fermion compounds, and unconventional superconductors. It would be helpful to include relevant references here to guide interested readers toward further reading.}

\item \refereesays{Perhaps a sentence like “Section 6 provides the conclusions” was intended at the end of Section 1 but was inadvertently omitted?}

\item \refereesays{Were the spin indices omitted in Eq. (3)? Or do the indices i,j,k,l represent “flavors” that is, combined spin and orbital indices—rather than orbitals alone? The same question applies to the display equation of $H^{int}$ on page 13. This could be confusing to readers, especially since the spin index is also not explicitly shown in the format of the <UMATRIX\_FILE>.restart file described on the same page.}

\item \refereesays{The last display equation on page 10 seems incorrect, since the creation and annihilation operators do not appear to result in any particle being created or annihilated.}

\item \refereesays{In Sec. 3.3, it appears that users must manually select one of the three provided symmetry configurations to perform block-diagonalization. Is there a plan to extend the code to automatically detect all relevant symmetries—especially in cases where orbitals or sites possess additional symmetries that would allow further block-diagonalization of the matrix?}

\item \refereesays{On page 43, it is mentioned that the spectrum obtained from ED is “inherently spiky”. What is the value of the broadening parameter used in these simulations? Including this information in the main text may improve the clarity and reproducibility of the paper.}

\item \refereesays{"$J_x \rightarrow J_X$" and "$J_p \rightarrow J_P$" in the second paragraph of page 13}

\item \refereesays{“store” $\rightarrow$  “stored” in the last line of page 13}

\item \refereesays{"As discussed" $\rightarrow$ "As will be discussed" at the beginning of Sec. 3.5.2}

\item \refereesays{"$\vec{B_\sigma}$" $\rightarrow$ "$\vec{B}_\sigma$" in the sentence "The values are given by all integers $B_\sigma$ corresponding to..." of page 14}

\item \refereesays{for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq.~(14)}

\item \refereesays{should be no indentation for the sentence right after the first display equation on page 17}

\item \refereesays{"$w(\mathcal{A})_{mn}^\nu$" $\rightarrow$ "$w_{mn}^\nu(\mathcal{A})$" in the second line after Eq.~(14)}

\item \refereesays{"This example two main goals" $\rightarrow$ "This example has two main goals" on page 46.}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\textbf{Reply to Referee B}}

We thank the refereee for their time and work in reviewing our
manuscript. Here below we address point by point all the issues raised
in their reports.

\refereesays{This paper presents the current status in an exact diagonalisation impurity solver EDIpack. It provides a detailed exposition of the multiple interfaces as well as a number of tutorial-style examples that provide details that will be appreciated to new users of the package. I believe that providing robust and well-tested computer codes, as well as high quality documentation, are a big service to the community. I wholeheartedly recommend this work for publication.}

\begin{enumerate}

\item \refereesays{On p. 8, function {\tt ed\_set\_Hloc} is introduced, but without much further information. Maybe the reader could be referred to some later section where its use is illustrated.}

\item \refereesays{On p. 9, the discussion about the phonon cutoff sounds potentially a bit misleading. The cutoff is surely problem dependent, and there are (generalized) cases where the shift A\_m cannot be considered as a free parameter.}

\item \refereesays{I find the discussion at the end of page 11 somewhat unclear, especially the terminology. Is this a discussion of consecutive indexing vs. occupation number representation?}

\item \refereesays{The motivation of including the code on p. 12 is unclear. What is the intention here?}

\item \refereesays{Parenthesis missing in the equation at the bottom of p. 12.}

\item \refereesays{Bottom of p. 13: "are store" -> "are stored"}

\item \refereesays{Top of p. 14: What is global share, what are istart, ishift, iend? I suppose this is Fortran-specific.}

\item \refereesays{p. 16: GFmatrix is said to be a critical component for high-speed execution. Maybe it could be describe in more detail? In what way is it efficient? What does it mean it is multi-layed? In passing, it would be nice if the capitalization would be uniform, e.g. GFmatrix vs. gfmatrix (I understand that Fortran compiler does not care, but the human reader perhaps does).}

\item \refereesays{A trick for computing off-diagonal functions is presented on p. 21. Doesn't this require switching to complex-valued floating points even in cases where the Hamiltonian is purely real?}

\item \refereesays{In Eq. (18), is Z the same on both sides of approximation sign?}

\item \refereesays{Are the code listings on p. 25 and p. 26 of sufficient interest to readers?}

\item \refereesays{p. 28: "as the nonsu2 and superc diagonalizations entail nontrivial subtleties in optimizing the off-diagonal components of X". What are these subtleties?}

\item \refereesays{As a general coding comment: would it be possible to remove use of global variables?}

\item \refereesays{p. 40: I find the discussion of parallelism in Julia wrapper unnecessary. Such information does not necessarily age well. This belongs to a readme file.}

\item \refereesays{p. 41: "an comprehensive" -> "a", "fo manipulating" -> for}

\item \refereesays{p. 41: The code listing mentions Wband and de, but I don't see where this is coming from.}

\item \refereesays{p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?}

\item \refereesays{p. 46: This example two main goals: missing "has"?}

\item \refereesays{p. 47: generate_kgrid is confusingly complex. There must be a simpler way to accomplish this.}

\item \refereesays{p. 57: Is the footnote necessary? Will it be of interest to the expected readers of this paper?}

\end{enumerate}

\end{document}

### 2025-07-12 edipack2_examples/AHM_EDIpack2EDIpy/data/script_figAHM.py

@@ -1,0 +1,166 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+
+
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 30})
+plt.rcParams['figure.figsize'] = [35, 15]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    AADE
+    """
+)
+
+
+axs["A"].text(0.02, 0.98, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.02, 0.98, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.02, 0.98, r"(C)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+axs["D"].text(0.02, 0.98, r"(D)",transform=axs["D"].transAxes,fontsize=24, va='top', color='black')
+axs["E"].text(0.94, 0.98, r"(E)",transform=axs["E"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U0.6/Gloc_i1_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U1.0/Gloc_i1_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U1.5/Gloc_i1_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
+rho4 = np.genfromtxt('U2.0/Gloc_i1_realw.dat',skip_header=0);x4=rho4[:,0];y4=-rho4[:,1]/np.pi
+rho5 = np.genfromtxt('U3.0/Gloc_i1_realw.dat',skip_header=0);x5=rho5[:,0];y5=-rho5[:,1]/np.pi
[…]

### 2025-07-12 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_2d.f90

@@ -1,0 +1,159 @@
+program ed_ahm_2d
+  USE EDIPACK
+  USE SCIFOR
+  USE DMFT_TOOLS
+  implicit none
+  integer,parameter                         :: Le=1000
+  real(8),parameter                         :: D=1
+  integer                                   :: iloop,i
+  integer                                   :: Nb,Nso
+  logical                                   :: converged,get_sigma,get_dos
+  !Bath:
+  real(8),allocatable,dimension(:)          :: Bath,Bath_Prev
+  !The local functions:
+  complex(8),allocatable,dimension(:,:,:,:) :: Gmats
+  complex(8),allocatable,dimension(:,:,:,:) :: Greal
+  complex(8),allocatable,dimension(:,:,:,:) :: Smats
+  complex(8),allocatable,dimension(:,:,:,:) :: Sreal
+  complex(8),allocatable,dimension(:,:,:,:) :: Weiss
+  !
+  character(len=16)                         :: finput
+  real(8)                                   :: wmixing
+  real(8)                                   :: de
+  real(8),dimension(:,:),allocatable        :: Ddos
+  real(8),dimension(:,:,:),allocatable      :: Edos
+  real(8),dimension(:,:),allocatable        :: H0
+  !
+  call parse_cmd_variable(finput,"FINPUT",default='inputAHM.conf')
+  call parse_input_variable(wmixing,"wmixing",finput,default=0.5d0,comment="Mixing bath parameter")
+  call parse_input_variable(get_sigma,"get_sigma",finput,default=.false.)
+  call parse_input_variable(get_dos,"get_dos",finput,default=.false.)
+  !
+  call ed_read_input(trim(finput))
+
+
+  !Add DMFT CTRL Variables used in DMFT_TOOLS:
+  call add_ctrl_var(Norb,"norb")
+  call add_ctrl_var(Nspin,"nspin")
+  call add_ctrl_var(beta,"beta")
+  call add_ctrl_var(xmu,"xmu")
+  call add_ctrl_var(wini,'wini')
+  call add_ctrl_var(wfin,'wfin')
+  call add_ctrl_var(eps,"eps")
+
+
+
[…]

### 2025-07-12 edipack2_examples/AHM_EDIpack2EDIpy/ed_ahm_square.f90

@@ -1,0 +1,220 @@
+program ed_ahm_square
+  USE EDIPACK
+  USE SCIFOR
+  USE DMFT_TOOLS
+  USE MPI
+  implicit none
+  integer                                       :: iloop,Lk,Nso,Nambu,Nno
+  logical                                       :: converged
+  !Bath:
+  integer                                       :: Nb,Nsym
+  real(8),allocatable                           :: Bath(:),Prev(:)
+  real(8),dimension(:,:),allocatable            :: LambdaVec
+  complex(8),dimension(:,:,:),allocatable       :: Hsym_basis
+  !variables for the model:
+  integer                                       :: Nx,Nkpath
+  real(8)                                       :: delta,lambda,wmixing,ts,alpha,D
+  character(len=16)                             :: finput
+  logical                                       :: phsym,normal_bath
+  !The local hybridization function:
+  complex(8),allocatable                        :: Hloc(:,:)
+  complex(8),allocatable,dimension(:,:,:,:,:,:) :: Gmats,Greal,Smats,Sreal,Weiss
+  complex(8),allocatable                        :: Hk(:,:,:,:)
+  !MPI
+  integer                                       :: comm,rank
+  logical                                       :: master
+
+
+  call init_MPI()
+  comm = MPI_COMM_WORLD
+  call StartMsg_MPI(comm)
+  rank = get_Rank_MPI(comm)
+  master = get_Master_MPI(comm)
+
+
+
+  call parse_cmd_variable(finput,"FINPUT",default='inputED.conf')
+  call parse_input_variable(Nsym,"NSYM",finput,default=2,comment="2: diagonal SC; 3: diag+off-diag SC")
+  call parse_input_variable(ts,"TS",finput,default=0.5d0,comment="hopping parameter")
+  call parse_input_variable(alpha,"ALPHA",finput,default=1d0,comment="bandwidth ratio t_2 = alpha*t_1")
[…]

### 2025-07-12 edipack2_examples/BHZ/ed_exct_bhz_2d.f90

@@ -1,0 +1,243 @@
+program ed_bhz
+  USE EDIPACK
+  USE SCIFOR
+  USE DMFT_TOOLS
+  USE MPI
+  implicit none
+
+  integer                                 :: iloop,Lk,Nso
+  logical                                 :: converged
+  !Bath:
+  integer                                 :: Nb
+  real(8),allocatable                     :: Bath(:)
+  !The local hybridization function:
+  !The local hybridization function:
+  complex(8),dimension(:,:,:),allocatable :: Weiss, Weiss_
+  complex(8),dimension(:,:,:),allocatable :: Smats,Sreal
+  complex(8),dimension(:,:,:),allocatable :: Gmats,Greal
+  !hamiltonian input:
+  complex(8),dimension(:,:,:),allocatable :: Hk
+  complex(8),dimension(:,:),allocatable   :: Hloc
+  complex(8),dimension(:,:),allocatable   :: sigmaBHZ
+  real(8),dimension(:,:),allocatable      :: Zbhz
+  !variables for the model:
+  integer                                 :: Nx,Nkpath
+  real(8)                                 :: mh,lambda,wmixing,z2
+  character(len=16)                       :: finput
+  !>Gamma matrices:
+  complex(8),dimension(4,4)               :: Gamma1,Gamma2,Gamma5,GammaN
+  complex(8),dimension(4,4)               :: GammaE0,GammaEx,GammaEy,GammaEz
+  !>Replica bath
+  real(8),dimension(:,:),allocatable      :: lambdasym_vector
+  complex(8),dimension(:,:,:),allocatable :: Hsym_basis
+  !MPI Vars:
+  integer                                 :: comm,rank
+  logical                                 :: master,fhtop
+
+  call init_MPI()
+  comm = MPI_COMM_WORLD
+  call StartMsg_MPI(comm)
+  rank = get_Rank_MPI(comm)
+  master = get_Master_MPI(comm)
+
+
+  !Parse additional variables && read Input && read H(k)^4x4
+  call parse_cmd_variable(finput,"FINPUT",default='inputED_BHZ.conf')  
[…]

### 2025-07-12 edipack2_examples/Bethe_EDIpack/data/script_figBethe.py

@@ -1,0 +1,197 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+
+def zimS(x,z):
+  y = (1.0-1.0/z)*x#-1/z*x
+  return y
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 24})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AABC
+    """
+)
+
+
+axs["A"].text(0.94, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.94, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+axs["C"].text(0.94, 0.04, r"(C)",transform=axs["C"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Data DOS")
+rho1 = np.genfromtxt('U1.00/Gloc_realw.dat',skip_header=0);x1=rho1[:,0];y1=-rho1[:,1]/np.pi
+rho2 = np.genfromtxt('U2.00/Gloc_realw.dat',skip_header=0);x2=rho2[:,0];y2=-rho2[:,1]/np.pi
+rho3 = np.genfromtxt('U2.50/Gloc_realw.dat',skip_header=0);x3=rho3[:,0];y3=-rho3[:,1]/np.pi
[…]

### 2025-07-12 edipack2_examples/Bethe_Holstein/script_figBethe.py

@@ -1,0 +1,97 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+W0_list = ["0.2","0.5","1.0","2.0","4.0","32.0","50.0","200.0","infty"]
+W0_plot = np.float64(W0_list[:-1])
+#W0_list = ["0.2","0.5","1.0","2.0","32.0","50.0","200.0","infty"]
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 40})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AB
+    """
+)
+
+
+axs["A"].text(0.96, 0.04, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.96, 0.04, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+
+
+ms=20
+
+
+##################################################################
+#Plot docc
+ax=axs["A"]
+n_docc_list=np.zeros(len(W0_list))
+s_docc_list=np.zeros(len(W0_list))
+print("Read Data docc...")
+for iW,W0 in enumerate(W0_list):
+  print("w0:",W0)
+  n_docc_list[iW] = np.loadtxt(f'normal/W{W0}/observables_last.ed',unpack=True)[1]
+  s_docc_list[iW] = np.loadtxt(f'superc/W{W0}/observables_last.ed',unpack=True)[1]
+
+ax.set_xscale("log")
+ax.set_xlabel(r'$\omega_0$/D')
+ax.set_ylabel(r'$ \langle n_\uparrow n_\downarrow \rangle$')
+ax.set_ylim(0.4,0.5)
+
+ax.plot(W0_plot,n_docc_list[:-1],label="normal",c="orange",marker="o",lw=6,markersize=ms,zorder=1)
[…]

### 2025-07-12 edipack2_examples/W2Dynamics2EDIpack/script_figBetheW2D.py

@@ -1,0 +1,114 @@
+import numpy as np
+import matplotlib.image as image
+import matplotlib.pyplot as plt
+from scipy.interpolate import griddata
+import pandas as pd
+import sys
+from matplotlib.colors import LinearSegmentedColormap
+from scipy import optimize
+
+def dens_bethe(x,d):
+  root=(1-(x/d)**2)+0.j
+  root=np.sqrt(root)
+  dens_bethe=(2/(np.pi*d))*root
+  return dens_bethe.real
+
+
+
+def zimS(x,z):
+  y = (1.0-1.0/z)*x#-1/z*x
+  return y
+
+
+plt.rcParams["font.family"] = "Times"
+plt.rcParams['text.usetex'] = True
+plt.rc('text.latex', preamble=r'\usepackage{amsmath,xcolor,amssymb,latexsym}')
+plt.rcParams.update({'font.size': 28})
+plt.rcParams['figure.figsize'] = [35, 10]
+
+
+fig = plt.figure()
+axs = plt.figure(layout="constrained").subplot_mosaic(
+    """
+    AB
+    """
+)
+
+
+axs["A"].text(0.01, 0.98, r"(A)",transform=axs["A"].transAxes,fontsize=24, va='top', color='black')
+axs["B"].text(0.01, 0.98, r"(B)",transform=axs["B"].transAxes,fontsize=24, va='top', color='black')
+
+
+
+
+
+##################################################################
+ax=axs["A"]
+
+print("Read Gimp")
+gf = np.genfromtxt('w2d_cthyb/giw.dat',skip_header=0);x1=gf[:,0];y1=gf[:,2]
+gf = np.genfromtxt('w2d_ed/giw.dat',skip_header=0)   ;x2=gf[:,0];y2=gf[:,2]
+gf = np.genfromtxt('ed_for/impG_l11_s1_iw.ed',skip_header=0);x3=gf[:,0];y3=gf[:,1]
+
+ax.set_xlim([0, 2])
+ax.set_ylim([-2,0])
+ax.set_xlabel(r'$\omega_n$')
+ax.set_ylabel(r'${\rm Im}G(i\omega_n)$')
+
+ax.tick_params(length=6, width=2,direction='out')
+#ax.yaxis.grid(True, which='both', alpha=0.5)
+#ax.yaxis.set_major_locator(mticker.LogLocator(base=10, numticks=10))
+
+lw=5
+
+
[…]

### 2025-07-12 edipack2_examples/edipack2triqs/hubbard_kanamori.py

@@ -1,0 +1,113 @@
+# Import common Python modules
+from itertools import product
+import numpy as np
+
+# Initialize the MPI library before creating the solver object
+from mpi4py import MPI
+
+# Import TRIQS many-body operator objects: annihilation, creation and
+# occupation number operators
+from triqs.operators import c, c_dag, n
+
+# Import the solver object
+from edipack2triqs.solver import EDIpackSolver
+
+spins = ['up', 'dn']    # Names of spin projections
+orbs = [0, 1, 2]        # List of impurity orbitals
+bath_sites = [0, 1]     # List of bath sites, each carrying 3 orbitals
+
+# Fundamental sets for impurity spin up/down degrees of freedom
+fops_imp_up = [('up', orb) for orb in orbs]
+fops_imp_dn = [('dn', orb) for orb in orbs]
+
+# Fundamental sets for bath spin up/down degrees of freedom
+# There are a total of 6 bath states for each spin projection
+fops_bath_up = [('B_up', i) for i in range(3 * 2)]
+fops_bath_dn = [('B_dn', i) for i in range(3 * 2)]
+
+# Non-interacting part of the impurity Hamiltonian
+h_loc = np.diag([-0.7, -0.5, -0.7])
+H = sum(h_loc[o1, o2] * c_dag(spin, o1) * c(spin, o2)
+        for spin, o1, o2 in product(spins, orbs, orbs))
+
+# Interaction part
+U = 3.0     # Local intra-orbital interactions U
+Ust = 1.2   # Local inter-orbital interaction U'
+Jh = 0.2    # Hund's coupling
+Jx = 0.15   # Spin-exchange coupling constant
+Jp = 0.1    # Pair-hopping coupling constant
+
+H += U * sum(n('up', o) * n('dn', o) for o in orbs)
+H += Ust * sum(int(o1 != o2) * n('up', o1) * n('dn', o2)
+               for o1, o2 in product(orbs, orbs))
+
+H += (Ust - Jh) * sum(int(o1 < o2) * n(s, o1) * n(s, o2)
+                      for s, o1, o2 in product(spins, orbs, orbs))
+H -= Jx * sum(int(o1 != o2) * c_dag('up', o1) * c('dn', o1) * c_dag('dn', o2) * c('up', o2)
+              for o1, o2 in product(orbs, orbs))
+H += Jp * sum(int(o1 != o2) * c_dag('up', o1) * c_dag('dn', o1) * c('dn', o2) * c('up', o2)
[…]

### 2025-07-13 03_edipack2.tex

@@
 sector amounts to defining an injective map
-$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutives indexing of the electronic states  $\ket{i}$
+$\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
 within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
@@
 $G_{\a\b\up\up}=\tfrac{1}{2}[C_\OO + C_\PP -
-(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})$.
+(1-i)(G_{\a\a\up\up}+G_{\b\b\up\up})]$.
 

### 2025-07-13 Reply_RefereeA.md
Updates from Overleaf

<!--We make use of MarkDown in this reply to ease integration with Scipost scheme.

This comment can be used to learn some of the MD syntax:

long line <double space before new line like \\ in Latex> 
new line

# chapter ,## section, ### subsection,...

italic:
*text*

bold:
**text**

blockquote:
> text

highlighted:
==text==

inline math:
$latex math$

display math as for latex doc:
$$
latex math
$$

OR

\begin{latex environment, i.e. equation}
latex math
\end{latex environment, i.e. equation}

list:
*
*

enumareted list:
1.
2.

comments:
see this comment itself

-->

We thank the referee for their time and work in reviewing our
manuscript. Here below we address point by point all the issues raised
in their reports.

<!-- *Exact diagonalization (ED) plays a vital role in the study of quantum impurity problems. In this work, the authors present an ED library and describe its usage in considerable detail. While it builds upon the previous EDIpack library, the manuscript introduces sufficient new developments to warrant a separate publication. Notably, several significant extensions and improvements are included, such as a unified framework for zero- and finite-temperature calculations for a wide range of impurity models; access to the full complex frequency plane; access to the Fock space and the ability to evaluate quantities like reduced density matrices; support for inequivalent impurities; integration with other programming languages and scientific libraries; and compatibility with widely used software suites such as TRIQS and w2dynamics.* -->

> *Overall, the paper is well written and highly detailed, allowing new users to install and utilize the library with ease. Furthermore, the comprehensive DMFT tests, demonstrated through a variety of examples and accompanied by corresponding scripts, provide excellent starting points for newcomers. I believe this work makes a valuable contribution to the community and am therefore pleased to recommend its publication in SciPost.*

We thank the referee for their constructive assessement of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.

> *On page 3, a large portion of paragraph 3, which introduces DMFT, lacks citations. For example, the authors mention the success of DMFT in capturing key features of various materials, including Mott insulators, heavy fermion compounds, and unconventional superconductors. It would be helpful to include relevant references here to guide interested readers toward further reading.
*

We totally agree with the referee comment. In the revised version we amended to this issue, including several references to DMFT in each of the mentioned subjects. Although it is nearly impossible to

> *Perhaps a sentence like “Section 6 provides the conclusions” was intended at the end of Section 1 but was inadvertently omitted?*

Reply:

> *Were the spin indices omitted in Eq. (3)? Or do the indices i,j,k,l represent “flavors” that is, combined spin and orbital indices—rather than orbitals alone? The same question applies to the display equation of $H^{int}$ on page 13. This could be confusing to readers, especially since the spin index is also not explicitly shown in the format of the <UMATRIX\_FILE>.restart file described on the same page.*

Reply:

> *The last display equation on page 10 seems incorrect, since the creation and annihilation operators do not appear to result in any particle being created or annihilated.*

Reply:

> *In Sec. 3.3, it appears that users must manually select one of the three provided symmetry configurations to perform block-diagonalization. Is there a plan to extend the code to automatically detect all relevant symmetries—especially in cases where orbitals or sites possess additional symmetries that would allow further block-diagonalization of the matrix?*

Reply:

> *On page 43, it is mentioned that the spectrum obtained from ED is “inherently spiky”. What is the value of the broadening parameter used in these simulations? Including this information in the main text may improve the clarity and reproducibility of the paper.*

Reply:

> *"$J_x \rightarrow J_X$" and "$J_p \rightarrow J_P$" in the second paragraph of page 13*

Reply:

> *“store” $\rightarrow$  “stored” in the last line of page 13*

Reply:

> *"As discussed" $\rightarrow$ "As will be discussed" at the beginning of Sec. 3.5.2*

Reply:

> *"$\vec{B_\sigma}$" $\rightarrow$ "$\vec{B}_\sigma$" in the sentence "The values are given by all integers $B_\sigma$ corresponding to..." of page 14*

Reply:

> *for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq.~(14)*

Reply:

> *should be no indentation for the sentence right after the first display equation on page 17*

Reply:

> *"$w(\mathcal{A})_{mn}^\nu$" $\rightarrow$ "$w_{mn}^\nu(\mathcal{A})$" in the second line after Eq.~(14)*

Reply:

> *"This example two main goals" $\rightarrow$ "This example has two main goals" on page 46.*

Reply:

### 2025-07-13 Reply_RefereeB.md
Updates from Overleaf

<!--We make use of MarkDown in this reply to ease integration with Scipost scheme.

This comment can be used to learn some of the MD syntax:

long line <double space before new line like \\ in Latex> 
new line

# chapter ,## section, ### subsection,...

italic:
*text*

bold:
**text**

blockquote:
> text

highlighted:
==text==

inline math:
$latex math$

display math as for latex doc:
$$
latex math
$$

OR

\begin{latex environment, i.e. equation}
latex math
\end{latex environment, i.e. equation}

list:
*
*

enumareted list:
1.
2.

comments:
see this comment itself

-->

We thank the referee for their time and work in reviewing our
manuscript. Here below we address point by point all the issues raised
in their reports.

> *This paper presents the current status in an exact diagonalisation impurity solver EDIpack. It provides a detailed exposition of the multiple interfaces as well as a number of tutorial-style examples that provide details that will be appreciated to new users of the package. I believe that providing robust and well-tested computer codes, as well as high quality documentation, are a big service to the community. I wholeheartedly recommend this work for publication.*

Reply:

> *On p. 8, function {\tt ed\_set\_Hloc} is introduced, but without much further information. Maybe the reader could be referred to some later section where its use is illustrated.*

Reply:

> *On p. 9, the discussion about the phonon cutoff sounds potentially a bit misleading. The cutoff is surely problem dependent, and there are (generalized) cases where the shift A\_m cannot be considered as a free parameter.*

Reply:

> *I find the discussion at the end of page 11 somewhat unclear, especially the terminology. Is this a discussion of consecutive indexing vs. occupation number representation?*

Reply:

> *The motivation of including the code on p. 12 is unclear. What is the intention here?*

Reply:

> *Parenthesis missing in the equation at the bottom of p. 12.*

Reply:

> *Bottom of p. 13: "are store" -> "are stored"*

Reply:

> *Top of p. 14: What is global share, what are istart, ishift, iend? I suppose this is Fortran-specific.*

Reply:

> *p. 16: GFmatrix is said to be a critical component for high-speed execution. Maybe it could be describe in more detail? In what way is it efficient? What does it mean it is multi-layed? In passing, it would be nice if the capitalization would be uniform, e.g. GFmatrix vs. gfmatrix (I understand that Fortran compiler does not care, but the human reader perhaps does).*

Reply:

> *A trick for computing off-diagonal functions is presented on p. 21. Doesn't this require switching to complex-valued floating points even in cases where the Hamiltonian is purely real?*

Reply:

> *In Eq. (18), is Z the same on both sides of approximation sign?*

Reply:

> *Are the code listings on p. 25 and p. 26 of sufficient interest to readers?*

Reply:

> *p. 28: "as the nonsu2 and superc diagonalizations entail nontrivial subtleties in optimizing the off-diagonal components of X". What are these subtleties?*

Reply:

> *As a general coding comment: would it be possible to remove use of global variables?*

Reply:

> *p. 40: I find the discussion of parallelism in Julia wrapper unnecessary. Such information does not necessarily age well. This belongs to a readme file.*

Reply:

> *p. 41: "an comprehensive" -> "a", "fo manipulating" -> for*

Reply:

> *p. 41: The code listing mentions Wband and de, but I don't see where this is coming from.*

Reply:

> *p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?*

Reply:

> *p. 46: This example two main goals: missing "has"?*

Reply:

> *p. 47: generate_kgrid is confusingly complex. There must be a simpler way to accomplish this.*

Reply:

> *p. 57: Is the footnote necessary? Will it be of interest to the expected readers of this paper?*

Reply:

### 2025-07-13 Reply_RefereeA.md
AA Moved replies to .md files to comply with Scipost rules. Drafted reply to Referee A.
TODO: 
* Finish draft to Referee B
* Update and check corrections to the manuscript according to the replies.

@@
 
-We totally agree with the referee comment. In the revised version we amended to this issue, including several references to DMFT in each of the mentioned subjects. Although it is nearly impossible to
+We agree with this comment of the referee.
+Although it is impossible to give justice to the wide literature accumulated over the years, we have made concerted efforts to incorporate key references that reflect the breadth and depth of research in this field.
+In the revised version, we have included several citations pertinent to DMFT across the discussed subjects, ensuring that foundational and more recent contributions are acknowledged.
+This approach aims to provide a balanced overview while addressing the referee's insightful comment.
 
@@
 
-Reply:
+We sincerely appreciate the referee's prompt attention to this matter.
+We must admit that we "inadvertently" overlooked a reference to Section 6, i.e.
+the conclusions, at the end of the introduction when discussing the manuscript's structure.
+We amended to this issue in the revised text by including the sentence:
+*"In Sec. 6 we present some concluding remarks and considerations."*
 
@@
 
-Reply:
+Thanks for this insightful comment.
+Indeed, both in Eq.(3) and in the display equation of $H^{int}$ on page 13, the indices $i, j, k, l$  represent "flavors",  corresponding to the combined spin and orbital indices rather than orbitals alone.
+We acknowledge that this could be potentially confusing, especially given the absence of explicit spin indices in the format of the <UMATRIX_FILE>.restart file described on the same page.
+
+To clarify this, we will revise the manuscript to explicitly state that the indices denote combined spin and orbital components.
+Additionally, we will add a note to the relevant sections to highlight this point, ensuring that readers can interpret the equations and file formats correctly.
+
+We appreciate your attention to this detail and believe that your suggestion will enhance the clarity of our presentation.
 
@@
 
-Reply:
+We express our gratitude to the referee for bringing to our attention the discrepancy in the equations for the bosonic operators.
+In the revised manuscript, we have rectified this error by modifying the expressions on the right-hand side of the equations to account for the change in the bosonic number.
 
@@
 
-Reply:
+We acknowledge the referee’s observation.
+While the code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries.
+Regrettably, we do not have any plans to incorporate automatic detection of all pertinent symmetries within the code.
+In the current setup, this would be feasible through an accurate analysis of the effective bath decomposition, as discussed in section 3.6, excluding simpler cases described by `bath_type=normal, hybrid`.
+
+Nevertheless, we are actively exploring development avenues that aim to integrate more sophisticated conservation laws, which would further reduce the matrix dimensions.
+We are confident that these enhancements would enhance the code’s flexibility and efficiency in managing systems characterized by intricate symmetry patterns.
 
@@
 
-Reply:
+We appreciate the referee's  observation.
+As briefly elaborated upon in the manuscript, the inherently "spiky" nature of the spectral function arises due to the finite size of the system under consideration.
+This finiteness results in a discrete set of poles contributing to the Källén-Lehmann spectral representation.
+To mitigate the singularities associated with these delta-like poles, a common practice involves applying a broadening technique using a Lorentzian function.
+
+The extent of this broadening is controlled by the input parameter `eps`, which determines the width of the Lorentzian function.
+It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each case.
+In the particular examples discussed on page 43 of our manuscript, we have employed a broadening parameter of `eps = 0.01`, expressed in units of the half-bandwidth `D`.
+
+In response to the referee's valuable suggestion, we have updated the manuscript to explicitly specify the value of this broadening parameter in all relevant examples that illustrate the behavior of the spectral function.
+We believe this addition enhances the clarity and reproducibility of our results, and we thank the referee for their constructive feedback.
+
+> *for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq.~(14)*
+
+We appreciate the referee's careful observation regarding the summation indices in the display equation of $C(z)$ on page 16 and Eq.~(14).
+To maintain consistency and clarity, we have revised the manuscript to ensure that both indices $m$ and $n$ have clearly defined lower and upper bounds, as they represent dummy variables for the same summation.
+
+In particular, we now explicitly indicate the summation upper bound for $n$ by using the number $N_{\rm state\_list}$ of eigenstates contained in the `state_list` class and describing the lower end of the energy spectrum.
+Following the referee's observation, we propagated this correction to all the expression involving a trace over Hamiltonian spectrum. We appreciate the referee's attention to this detail.
 
@@
 
-Reply:
-
 > *“store” $\rightarrow$  “stored” in the last line of page 13*
-
-Reply:
 
@@
 
-Reply:
-
 > *"$\vec{B_\sigma}$" $\rightarrow$ "$\vec{B}_\sigma$" in the sentence "The values are given by all integers $B_\sigma$ corresponding to..." of page 14*
-
-Reply:
-
-> *for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq.~(14)*
-
-Reply:
-
-> *should be no indentation for the sentence right after the first display equation on page 17*
-
-Reply:
 
@@
 
-Reply:
-
 > *"This example two main goals" $\rightarrow$ "This example has two main goals" on page 46.*
 
-Reply:
+> *should be no indentation for the sentence right after the first display equation on page 17*
+>
+
+We sincerely appreciate the referee's careful review and constructive feedback.
+In the revised manuscript, we have addressed all the indicated typos and corrections as suggested.
+We are grateful for the referee’s meticulous attention to detail, which has significantly contributed to improving the clarity and accuracy of our manuscript.

### 2025-07-15 Reply_RefereeA.md
CMake options have changed. Updated table

@@
 We thank the referee for their time and work in reviewing our
-manuscript. Here below we address point by point all the issues raised
+manuscript. In the following, we address point by point all the issues raised
 in their reports.
@@
 
-We thank the referee for their constructive assessement of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.
+We thank the referee for their constructive assessment of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.
 
@@
 We agree with this comment of the referee.
-Although it is impossible to give justice to the wide literature accumulated over the years, we have made concerted efforts to incorporate key references that reflect the breadth and depth of research in this field.
+Although it is impossible to do justice to the wide literature accumulated over the years, we have made concerted efforts to incorporate key references that reflect the breadth and depth of research in this field.
 In the revised version, we have included several citations pertinent to DMFT across the discussed subjects, ensuring that foundational and more recent contributions are acknowledged.
@@
 the conclusions, at the end of the introduction when discussing the manuscript's structure.
-We amended to this issue in the revised text by including the sentence:
+We resolved this issue in the revised text by including the sentence:
 *"In Sec. 6 we present some concluding remarks and considerations."*
@@
 Indeed, both in Eq.(3) and in the display equation of $H^{int}$ on page 13, the indices $i, j, k, l$  represent "flavors",  corresponding to the combined spin and orbital indices rather than orbitals alone.
-We acknowledge that this could be potentially confusing, especially given the absence of explicit spin indices in the format of the <UMATRIX_FILE>.restart file described on the same page.
+We acknowledge that this could potentially be confusing, especially given the absence of explicit spin indices in the format of the <UMATRIX\_FILE>.restart file described on the same page.
 
-To clarify this, we will revise the manuscript to explicitly state that the indices denote combined spin and orbital components.
-Additionally, we will add a note to the relevant sections to highlight this point, ensuring that readers can interpret the equations and file formats correctly.
+To clarify this, we have revised the manuscript to explicitly state that the indices denote combined spin and orbital components.
+Additionally, we will add a note to the relevant sections to highlight this point, ensuring that the readers can interpret the equations and file formats correctly.
 
@@
 We acknowledge the referee’s observation.
-While the code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries.
+Although the code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries.
 Regrettably, we do not have any plans to incorporate automatic detection of all pertinent symmetries within the code.
@@
 Nevertheless, we are actively exploring development avenues that aim to integrate more sophisticated conservation laws, which would further reduce the matrix dimensions.
-We are confident that these enhancements would enhance the code’s flexibility and efficiency in managing systems characterized by intricate symmetry patterns.
+We are confident that these enhancements would improve code’s flexibility and efficiency in managing systems characterized by intricate symmetries.
 
@@
 
-> *for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq.~(14)*
+> *for the display equation of $C(z)$ on page 16, summation index $m$ has lower and upper bounds, while index $n$ does not, although they are dummy variables for the same thing. Same for Eq. (14)*
 
-We appreciate the referee's careful observation regarding the summation indices in the display equation of $C(z)$ on page 16 and Eq.~(14).
+We appreciate the referee's careful observation regarding the summation indices in the display equation of $C(z)$ on page 16 and Eq.
+(14).
 To maintain consistency and clarity, we have revised the manuscript to ensure that both indices $m$ and $n$ have clearly defined lower and upper bounds, as they represent dummy variables for the same summation.

### 2025-07-15 Reply_RefereeB.md
CMake options have changed. Updated table

@@
-<!--We make use of MarkDown in this reply to ease integration with Scipost scheme.
-
-This comment can be used to learn some of the MD syntax:
-
-long line <double space before new line like \\ in Latex> 
-new line
-
-# chapter ,## section, ### subsection,...
-
-italic:
-*text*
-
-bold:
-**text**
-
-blockquote:
-> text
-
-highlighted:
-==text==
-
-inline math:
-$latex math$
-
-display math as for latex doc:
-$$
-latex math
-$$
-
-OR
-
-\begin{latex environment, i.e. equation}
-latex math
-\end{latex environment, i.e. equation}
-
-list:
-*
-*
-
-enumareted list:
-1.
-2.
-
-comments:
-see this comment itself
-
--->
-
-We thank the referee for their time and work in reviewing our
+We thank the refereee for their time and work in reviewing our
 manuscript. Here below we address point by point all the issues raised
@@
 
-Reply:
+We sincerely thank the referee for their positive and encouraging comments.
+We are very pleased to hear that the exposition, interfaces, and tutorial examples were found to be helpful and of value to new users.
+We are grateful for your recommendation for publication and your support for open and well-maintained scientific software.
 
@@
 
-Reply:
+We acknowledge the referee’s suggestion.
+The function ${\tt ed\_set\_Hloc}$, introduced in Section 3.1.1, is employed to define the impurity Hamiltonian.
+At this stage of the manuscript, its purpose is solely described: setting the local non-interacting component of the impurity Hamiltonian, without further elaboration.
+
+To enhance clarity and facilitate reader comprehension of its practical application, we have revised the text at this location.
+Specifically, we have included a forward reference to Section 5, where ${\tt ed\_set\_Hloc}$ is explicitly utilized in various application examples.
+These examples encompass the Hubbard model on the Bethe lattice (Section 5.1), the interacting Bernevig-Hughes-Zhang model (Section 5.5), and the Kane-Mele-Hubbard model (Section 5.6).
+These instances aim to elucidate both the structure of the input arguments and the context in which this function is commonly employed.
 
@@
 
-Reply:
+We thank the referee for this observation.
+Indeed, the cutoff on the number of phonon excitations is inherently problem dependent and should be carefully adjusted in light of the specific electron-phonon coupling regime, the phonon frequency, and the interplay with electronic correlations.
+Furthermore, we agree that the shift $A_m$, while often treated as a tunable parameter in simplified models, is not always free to choose.
+In more general contexts, such as in first-principles-derived Hamiltonians or systems constrained by symmetry or external potentials, $A_m$ may be fixed by physical considerations or derived from the underlying microscopic model.
+
+To reflect this more nuanced detail, we have revised the paragraph on page 9 to acknowledge that the shift $A_m$ is not universally a free parameter. The new text reads:
+
+*“In many cases, one can reduce the number of excited phonons in the ground state, and consequently the required cutoff, by appropriately choosing the shift $A_m$.
+However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter.
+In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence.”*
+
+This modification ensures that our discussion does not overgeneralise while aligning with the range of physical contexts in which EDIpack may be applied.
+We thank the referee for helping us clarify this important point.
 
@@
 
-Reply:
+We thank the referee for pointing out this issue.
+Indeed, the original text aimed to explain how electronic Fock states within a given symmetry sector are indexed and related to their underlying occupation number (bitstring) representation.
+However, we acknowledge that the terminology and phrasing in the original submission may have been ambiguous.
+
+To clarify this point, we have revised the final paragraph of page 11 in the current version of the manuscript. The updated text now reads:
+
+*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in their number representation.
+This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D^{\mathcal{S}}$.”*
+
+This new formulation replaces the previous wording and makes explicit the distinction between the consecutive indexing of the sector states $|i\rangle$ and the Fock states in the integer-based occupation number representation $|I_e\rangle$.
+In doing so, we clarify that the mapping $\mathcal{M}$ is what connects the two encodings of the same physical state.
+We believe the revised text should eliminate the ambiguity the referee noted.
 
@@
 
-Reply:
+We thank the referee for raising this point.
+The code snippet on page 12 was originally included to illustrate the concrete implementation of the mapping from Fock states to symmetry sectors for different values of ${\tt ed\_mode}$.
+Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization.
+Moreover, this code snippet is useful to understand the structure of the ${\tt sparse_map}$ used to implement fast-algorithm for the evaluation of the reduced impurity density matrix in section 3.5.2.
 
-> *Parenthesis missing in the equation at the bottom of p. 12.*
+In response to the referee’s comment, we have slightly revised the manuscript to clarify this intent. Specifically, we have added the following introductory sentence to the relevant section:
 
-Reply:
-
-> *Bottom of p. 13: "are store" -> "are stored"*
-
-Reply:
+*“The following code excerpts illustrate how the sector construction algorithms differ depending on the value of ed_mode, and serve as a concrete reference for understanding how quantum number constraints are enforced in practice.”*
 
@@
 
-Reply:
+We thank the referee for their close reading and for raising this question concerning the variables ${\tt istart}$, ${\tt iend}$, and ${\tt ishift}$.
+
+We recognise that the earlier reference to the global share was misleading and ultimately unnecessary concept that we have chosen to eliminate for clarity.
+
+The issue at hand concerns the parallel construction of a matrix that is distributed across multiple threads or MPI processes.
+In such a setting, each thread is responsible for computing and storing only a subset—or "chunk" ${\tt Q}$—of the full matrix, typically defined as a range of contiguous rows.
+To maintain consistency with the global indexing of the matrix, while allowing each thread to work independently and with locally indexed arrays, a mapping must be established between global and local indices.
+
+The variables ${\tt istart}$ and ${\tt iend}$ define the global index range of matrix rows assigned to a given thread or process.
+That is, a given thread will handle only the rows from ${\tt istart}$ to ${\tt iend}$ (inclusive), corresponding to its local share of the full matrix.
+The variable ${\tt ishift}$ is then used to translate global row indices into local ones, effectively setting ${\tt ishift = mpiRank*Q}$.
+This allows local arrays to be aligned correctly with the globally defined matrix structure.
+
+While the code is written in Fortran, this construction is not specific to the language itself.
+Rather, it is a general approach for handling parallel matrix distribution in any programming environment where the global matrix is divided into row blocks across multiple processing units.
+To avoid potential confusion and to make the implementation choices more transparent to the reader in the revised we now write:
+
+"*In a parallel setting, each thread is assigned a contiguous block of matrix rows $Q=D_{\mathcal S}/N_{cpu}$.
+We denote the locally stored rows on a given thread by $q = 1, \ldots, Q$, and relate them to their corresponding global indices $i = 1, \ldots, D_{\mathcal S}$ via the variables \texttt{istart}, \texttt{iend}, and \texttt{ishift}.
+Here, \texttt{istart} and \texttt{iend} define the global index range $[q_1, q_Q]$ assigned to the thread, corresponding to $q_1 = \texttt{istart}$ and $q_Q = \texttt{iend}$.
+The variable \texttt{ishift} $= \texttt{istart} - 1$ allows for mapping between the local index $q$ and the global index $i$ through the simple relation $i = q + \texttt{ishift}$.
+This mapping ensures consistent global indexing while enabling efficient local computation.*"
 
@@
 
-Reply:
+We thank the referee for pointing out the need for a clearer and more detailed description of the ${\tt gfmatrix}$ type, which indeed plays a central role in the performance of the code.
+In response, we have revised the corresponding section of the manuscript (page 16) to provide a more precise explanation of its structure and efficiency features.
+
+The term multi-layered refers to the hierarchical organization of the ${\tt gfmatrix}$ object, which is essential for storing and accessing the analytic structure of correlation functions, i.e.
+the weights and the poles, in a flexible and scalable way.
+Specifically, the data are organized across three conceptual layers: (1) the many-body eigenstates of the Hamiltonian spectrum, (2) the amplitude channels associated to each such state, and (3) the set of poles and weights corresponding to physical excitations from this state.
+This structure is necessary to correctly represent the Lehmann decomposition of Green's functions and related objects, while still allowing dynamic access and manipulation during calculations.
+
+The efficiency of ${\tt gfmatrix}$ stems from two main features.
+First, correlation functions do not need to be precomputed and stored on fixed frequency or time grids; instead, their values are computed on-the-fly at arbitrary complex arguments, allowing precise and flexible evaluation as required by different solvers or output formats.
+Second, memory usage is optimized by avoiding redundant storage.
+The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis.
+We also recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph at page 16 in a more precise way as:
+
+"*The module ${\tt ED\_GFMATRIX}$ implements the class ${\tt gfmatrix}$, which provides an efficient and flexible representation of DCFs.
+It is structured as a hierarchical, or {\it multi-layered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.
+This structure allows the ${\tt gfmatrix}$ class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$.
+By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
+As a result, ${\tt gfmatrix}$ is a core component of EDIpack, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"
+
+We also thank the referee for pointing out inconsistencies in capitalization. We have now ensured that the identifier is uniformly written as **gfmatrix** throughout the manuscript.
 
@@
 
-Reply:
+We thank the referee for this  observation.
+It is indeed correct that the general strategy presented for computing off-diagonal DCFs, as described on page 21, involves constructing linear combinations of operators, which in the most general case would require working with complex-valued floating point arithmetic—even if the Hamiltonian itself is real.
+
+However, in the special case where the Hamiltonian is real and symmetric, the resulting Green's functions are symmetric under exchange of orbital indices, i.e., $G_{\alpha\beta}(z) = G_{\beta\alpha}(z)$.
+This property can be exploited to compute off-diagonal elements using only real-valued linear combinations of operators.
+In such cases, all required DCFs can be obtained exploiting memory advantages of real-valued computations.
+
+In the revised manuscript we clarify this point by writing in the **normal** paragraph of the section 3.8:
+
+"*The sector Hamiltonian matrix in this mode is assumed 
+to be real symmetric, which simplifies the evaluation 
+of the off-diagonal terms by exploiting the following symmetry 
+under orbital exchange $G_{\alpha\beta\sigma\sigma}(z)=G_{\beta\alpha\sigma\sigma}(z)$. 
+In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
+${\mathcal O}=c_{\alpha\sigma}+c_{\beta\sigma}$, along wit the identity 
+$G_{\alpha\beta\sigma\sigma}=\tfrac{1}{2}(C_{\mathcal O} - G_{\alpha\alpha\sigma\sigma} - G_{\beta\beta\sigma\sigma})$,
+where $C_{\mathcal O}$ denotes the DCF associated to ${\mathcal O}$. This approach, avoiding the need for complex arithmetic, preserves the efficiency of real-valued computation.*"
 
@@
 
-Reply:
+We are indebted with the referee for pointing out this important subtlety, which in fact extends to both sections 3.8 and 3.9.
+In the original version of the manuscript, the partition function $Z$ appearing in different expressions (including the Eq.(18) indicated the referee), may have misleadingly suggested that it was being evaluated exactly, even though the trace had been truncated.
+
+In the revised manuscript we have corrected this issue.
+We now use the symbol $Z$ to indicate the exact partition function and reserve the symbol $\tilde{Z}$ to  explicitly indicated the partition function approximated using only the finite set of low-energy eigenstates retained in the trace, i.e., those contributing significantly due to their large Boltzmann weights.
+This makes the approximation consistent on both sides of the involved equations, namely Eqs.
+(13), (14) and (18), properly reflecting the finite-state summation used in practice.
 
@@
 
-Reply:
+We acknowledge the referee observation.
+We believe that the code listings on pages 25 and 26, i.e.
+the implementation of the fast-algorithm for the evaluation of the impurity RDM,    provide valuable insight into the practical aspects of the implementation discussed in the text, particularly with respect to the subtle issues related to state decomposition and the treatment of fermionic sign conventions where required.
+
+These listings are intended to complement the discussion by offering concrete examples that clarify how the formal logic is realized in code.
+Given the potential for confusion when dealing with basis state reconstruction and operator ordering in fermionic systems, we believe that these examples will be of interest and practical benefit to users aiming to extend or interface with the library.
 
@@
 
-Reply:
+We acknowledge that our brief comment reads a bit obscure while this point requires a more detailed, yet brief, discussion.
+
+The bath optimization is a crucial step in the DMFT framework.
+As we discuss in the manuscript, to preserve the general application of EDIpack we introduced several control parameters for the conjugate-gradient fit.
+A key one is the definition of the norm, or distance, between matrix functions appearing in Eq.
+30.
+
+While for function matrices with a particularly symmetric structure the choice of the metric is inessential, it might dramatically affect the quality of the optimization in more general cases. 
+The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric.
+In either case, the coexistence of components having a very different physical interpretation, e.g., anomalous terms, and/or spanning very different energy scales represents a serious challenge to the optimization of the bath.
+This requires careful tuning of the control parameters to ensure that the optimization does not disproportionately favor certain matrix elements over others, thereby maintaining the overall fidelity of the bath representation.
+In this sense, introducing other norms which ensure a better balance among the components is a development line to improve EDIpack usage.
+
+In the revised manuscript we amended to this unclear statement writing:   
+*"We plan to expand the available options for the cg_norm parameter in future EDIpack updates, since the nonsu2 and superc diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X, due to the coexistence of matrix elements with different physical meanings and energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation."*
 
@@
 
-Reply:
+We thank the referee for this general but important observation.
+In principle, it is indeed possible to eliminate the use of global variables by explicitly passing all data structures through subroutine arguments.
+However, in the context of Fortran, and similarly in other compiled languages, global variables (typically implemented via module-level variables) do not incur any performance or memory management penalties.
+
+Their use in EDIpack is deliberate and serves to maintain clarity and modularity in the code, particularly for widely shared objects such as configuration parameters, system-wide operators, or state indexing data.
+Removing these global definitions would require passing a large number of arguments through deep call chains, which we believe would significantly increase code complexity, reduce readability, and introduce greater potential errors, without offering any computational or architectural advantages.
+
+However, we recognise the importance of careful design in managing global memory, and we have ensured that such variables are encapsulated within dedicated modules with well defined scopes.
+Should it prove beneficial for future code maintainability or extension by third-party contributors, we are ready to reviewing and refining this aspect of the implementation.
 
@@
 
-Reply:
+We thank the referee for this suggestion.
+We agree that the detailed discussion of parallelism integration within the Julia wrapper is better suited for specialized documentation such as a README file or the on-line user manual rather than the main manuscript.
+Accordingly, we have removed the entire paragraph from the revised version to keep the presentation focused and ensure the manuscript’s longevity and clarity.
+Relevant implementation details regarding MPI usage in Julia will be provided in the package documentation to better serve users requiring this information.
+
+> *p. 41: The code listing mentions Wband and de, but I don't see where this is coming from.*
+
+We thank the referee for carefully reviewing this sectoin and pointing this out.
+Indeed, the variable ${\tt Wband}$ should not appear in the code listing, as it corresponds to ${\tt D}$, which is correctly defined earlier in the script.
+Additionally, the variable ${\tt de}$ represents the energy grid spacing, computed as ${\tt de = 2D / Le}$, where Le is the number of energy points discretizing the Bethe lattice density of states.
+We have corrected the code listing accordingly to eliminate Wband and clarify the definition of de.
+
+> *p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?*
+
+We thank the referee for pointing out the ambiguity in this sentence.
+Our intention was to clarify that, although the bath optimization problem is conceptually distinct from the core impurity diagonalization task for which EDIpack was originally developed, nonetheless the package provides access to a well-tested implementation of the conjugate-gradient fitting procedure for the bath optimization.
+We have revised the sentence accordingly in the manuscript to make this connection and the role of these functions more explicit writing:
+
+*"Given the critical importance of this optimization, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*
+
+> *p. 47: generate_kgrid is confusingly complex. There must be a simpler way to accomplish this.*
+
+We agree with the referee that the implementation of ${\tt generate_kgrid}$ could be simplified for clarity.
+The purpose of this function is merely to construct a uniform 2D grid in the Brillouin zone using the reciprocal lattice vectors, which can indeed be achieved with more concise or intuitive code.
+
+More generally, we note that this step is not essential to the core functionalities provided by EDIpack, as it pertains only to the sampling of the Brillouin zone.
+For more involved tight-binding constructions, users may wish to rely on specialized libraries such as PythTB, which are designed for this purpose.
+Our goal here was only to provide a minimal working example for illustration.
+
+> *p. 57: Is the footnote necessary? Will it be of interest to the expected readers of this paper?*
+
+We appreciate the referee’s suggestion. Upon reconsideration, we agree that the footnote was not essential for the intended readership and have removed it from the revised version of the manuscript.
+
+> *Parenthesis missing in the equation at the bottom of p. 12.*
+
+> *Bottom of p. 13: "are store" -> "are stored"*
 
@@
 
-Reply:
-
-> *p. 41: The code listing mentions Wband and de, but I don't see where this is coming from.*
-
-Reply:
-
-> *p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?*
-
-Reply:
-
 > *p. 46: This example two main goals: missing "has"?*
 
-Reply:
-
-> *p. 47: generate_kgrid is confusingly complex. There must be a simpler way to accomplish this.*
-
-Reply:
-
-> *p. 57: Is the footnote necessary? Will it be of interest to the expected readers of this paper?*
-
-Reply:
+We thank the referee for carefully pointing out these typographical errors. All the mentioned issues have been corrected in the revised version of the manuscript.

### 2025-07-15 02_install.tex
CMake options have changed. Updated table

@@
 \begin{center}
+\small
 \begin{tabular}{ l|l|l } 
@@
   \hline
-  -D{\bf PREFIX}          & Install directory  & {\color{xkcdEmerald} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{xkcdEmerald}False}\\
-  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{xkcdEmerald}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}/TESTING/DEBUG \\
+  -D{\bf CMAKE\_INSTALL\_PREFIX}          & Install prefix override  & {\color{xkcdEmerald} None}\textbf{/}User-defined path \\
+
+  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/}\\
+  &install prefix unset)&{\color{xkcdEmerald}TAG/} (\textit{e.g. 5.3.3})\\
+  &&{\color{xkcdEmerald}PLAT/} (\textit{gnu/intel/...})\\
+  &&{\color{xkcdEmerald}BRANCH} (\textit{main/debug/...})\textbf{/}\\
+  &&$\sim$/opt/edipack/custom \\
+  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
+  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
+  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
+  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
  \hline

### 2025-07-15 03_edipack2.tex
CMake options have changed. Updated table

@@
 
-In many cases one can reduce the number of excited phonons in the ground state, and consequently the required cutoff, by choosing properly the shift $A_m$.  
+In many cases, one can reduce the number of excited phonons in the ground state, and
+consequently the required cutoff, by appropriately choosing the shift $A_m$.
+In practice one can use $A_m = \langle \hat{O}_m \rangle $ and redefine a shifted bosonic fields $\tilde{b}_m^{(\dagger)} = b_m^{(\dagger)} + \frac{\langle \hat{O}_m \rangle }{\omega_0}$.
+This choice would ensure that $\langle \tilde{b}_m^\dagger + \tilde{b}_m \rangle =0$ effectively reducing the number of phonons required for the calculation.
+Observables on the physical bosons are linked to the new one via the previous transformation.
+{ \color{red} However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter.
+In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence.
+SG: i would remove this part}
 Although feasible, dealing with more than one phonon mode quickly becomes computationally very demanding, thus we will consider only one mode and we drop the $m$ index in the rest of this work.
@@
 \begin{align*}
-  b\ket{p} &= \sqrt{p-1}\ket{p-1}, \\
-  b^\dagger\ket{p} &= \sqrt{p}\ket{p+1}.
+  b\ket{p} &= \sqrt{p} \ket{p-1}, \\
+  b^\dagger\ket{p} &= \sqrt{p+1}\ket{p+1}.
 \end{align*}
@@
 
-\subsubsection{GFmatrix}
+\subsubsection{gfmatrix}
 One of the main goals of the \NAME is to evaluate dynamical correlations
@@
 
-The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, 
-which provides an efficient, multi-layer, data structure for storing 
-all weights and poles required for the evaluation of DCFs. This 
-class is designed to handle multiple operators and sectors, allowing 
-on-the-fly evaluation of the DCF for any complex frequency 
-$z\in\CCC$.
-
-The use of this data structure significantly reduces the computational 
-cost of evaluating DCFs making it a critical component 
-for the high-performance execution of \NAME.
-
-\begin{lstlisting}[style=fstyle,numbers=none]   
-!The contributions to the GF Kallen-Lehmann sum are stored as
-!GF_{ab,sr}%state%channel%{w,e}.
-!A couple of weight,poles {w,e} is stored: 
-!for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
-!
-!Sub-class: contains the actual weight and poles:
-type GFspectrum
-   complex(8),dimension(:),allocatable       :: weight
-   real(8),dimension(:),allocatable          :: poles
-end type GFspectrum
-!
-!N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
-!Subclass: contains a given set of weights and poles.
-!Each instance of this subclass corresponds to a given input state 
-!and a given operator in the Kallen-Lehmann representation.  
-type GFchannel
-   type(GFspectrum),dimension(:),allocatable :: channel 
-end type GFchannel
-!
-!Main class: stores  weights and poles of a given DCF 
-!obtained through the dynamical Lanczos algorithm.
-!state_list%size = Number of states in the spectrum 
-type GFmatrix
-   type(GFchannel),dimension(:),allocatable  :: state
-   logical                                   :: status=.false. !Allocation status
-end type GFmatrix
-\end{lstlisting}
+The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix}, which provides an efficient and flexible representation of DCFs.
+It is structured as a hierarchical, or {\it multi-layered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $\ket{n}$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $\ket{n}$, each characterized by a pole and its corresponding weight.
+This structure allows the {\tt gfmatrix} class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$.
+By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
+As a result, {\tt gfmatrix} is a core component of \NAME, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.
+
+% The module {\tt ED\_GFMATRIX} implements the class {\tt gfmatrix} for the efficient storage of these quantities.
+It is designed as a hierarchical, or  {\it multi-layered}, data structure that organize spectral weights and poles using three distinct levels: i) the initial eigenstate $\ket{n}$ of the Hamiltonian spectrum, ii) the amplitude channel associated to this state, i.e.
+the operator applied and, finally, iii) the weights and poles corresponding to each physical excitation from such initial state.
+% This class is designed to handle multiple operators and states, allowing 
+% on-the-fly evaluation of the DCF for any complex frequency $z\in\CCC$. 
+% The use of this data structure significantly reduces the computational cost of evaluating DCFs, making it a critical component in \NAME both from the point of view of memory management, data conservation and post-processing analysis.
+
+% \begin{lstlisting}[style=fstyle,numbers=none]   
+% !The contributions to the GF Kallen-Lehmann sum are stored as
+% !GF_{ab,sr}%state%channel%{w,e}.
+% !A couple of weight,poles {w,e} is stored: 
+% !for each *channel, i.e. !applied operator, for any starting state ${\color{comment-color}\ket{n}}$.
+% !
+% !Sub-class: contains the actual weight and poles:
+% type GFspectrum
+%    complex(8),dimension(:),allocatable       :: weight
+%    real(8),dimension(:),allocatable          :: poles
+% end type GFspectrum
+% !
+% !N_channel = ${\color{comment-color} C,\, C^\dagger,\, C \pm C^\dagger,\, C \pm iC^\dagger}$, etc.
+% !Subclass: contains a given set of weights and poles.
+% !Each instance of this subclass corresponds to a given input state 
+% !and a given operator in the Kallen-Lehmann representation.  
+% type GFchannel
+%    type(GFspectrum),dimension(:),allocatable :: channel 
+% end type GFchannel
+% !
+% !Main class: stores  weights and poles of a given DCF 
+% !obtained through the dynamical Lanczos algorithm.
+% !state_list%size = Number of states in the spectrum 
+% type gfmatrix
+%    type(GFchannel),dimension(:),allocatable  :: state
+%    logical                                   :: status=.false. !Allocation status
+% end type gfmatrix
+% \end{lstlisting}
 
@@
 bosons ($-$), and $\ibra \cdot \iket=\frac{1}{Z}\Tr{ \left[ e^{-\beta
-      H}\cdot \right]}$, with $Z=\sum_ne^{-\beta E_n}$, the thermodynamic
+      H}\cdot \right]}$, with $Z=\sum_n e^{-\beta E_n}$, the thermodynamic
 average.
@@
     %
-    & =\frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}\sum_m
+    & \simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}\sum_m
   \frac{ |\bra{\psi_m}\AA^\dagger \ket{\psi_n}|^2 }  {z-(E_m-E_n)}
@@
 \end{equation}
-where $z\in\CCC$, and $\{\ket{\psi_n}, E_n\}$ are the eigenpairs of the
+where $z\in\CCC$, $\tilde{Z}=\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}$ and $\{\ket{\psi_n}, E_n\}$ are the eigenpairs of the
 Hamiltonian $H$. 
@@
   \begin{split}
-    C_\AA(z)  &\simeq \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
+    C_\AA(z)  &\simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
     \sum_{m=1}^{N} \frac{\bra{\psi_n}\AA \AA^\dagger\ket{\psi_n} |a^n_m|^2}{
@@
     %
-    &= \frac{1}{Z}\sum_{n=1}^{N_{\tt state\_list}}\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
-    \equiv \frac{1}{Z}\sum_n
+    &= \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}}\sum_{m=1}^{N} \sum_{\nu=\pm}\frac{w^{\nu}_{mn}(\AA)}{z - dE^\nu_{mn}(\AA)} 
+    \equiv \frac{1}{\tilde{Z}}\sum_n
     \sum_{m=1}^{N} \sum_{\nu=\pm} g_\AA(z;\nu, w^{\nu}_{mn},  dE^\nu_{mn}), \cr
@@
 The sector Hamiltonian matrix in this mode is assumed 
-to be real symmetric, which significantly simplifies the evaluation of the off-diagonal terms. In this case, the following symmetry relation 
-$G_{\a\b\s\s}=G_{\b\a\s\s}$ holds, allowing the computation of 
-off-diagonal components using an auxiliary operator 
-$\OO=c_{\a\s}+c_{\b\s}$ and the identity:
-$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$.
+to be real symmetric, which simplifies the evaluation 
+of the off-diagonal terms by exploiting the following symmetry 
+under orbital exchange $G_{\a\b\s\s}(z)=G_{\b\a\s\s}(z)$. 
+In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
+$\OO=c_{\a\s}+c_{\b\s}$, along wit the identity 
+$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$,
+where $C_\OO$ denotes the DCF associated to $\OO$      . This approach, avoiding the need for complex arithmetic, preserves the efficiency of real-valued computation.
 
@@
 \begin{equation}
-\ibra \OO\iket = \frac{1}{Z}\sum_{n=1}^{\infty} e^{-\beta E_n}
+\ibra \OO\iket 
+= \frac{1}{Z}\sum_{n=1}^{\infty} e^{-\beta E_n}
 \bra{\psi_n} \OO \ket{\psi_n}\simeq \frac{1}{\tilde{Z}}\sum_{n=1}^{N_{\tt state\_list}} e^{-\beta E_n}
@@
 where $E_n$ and $\ket{\psi_n}$ are the $N_{\tt state\_list}$ low-lying eigenstates 
-of the system stored in the {\tt state\_list} and $\tilde{Z}=\sum_{n=1}^{N_{\tt state\_list}}e^{-\beta E_n}$. 
-% This approach 
-% greatly reduces computational overhead by focusing on the 
-% relevant, low-energy sector.
+of the system stored in the {\tt state\_list},  $Z=\sum_n e^{-\beta E_n}$ and  $\tilde{Z}=\sum_{n=1}^{N_{\tt state\_list}}e^{-\beta E_n}$.
 
@@
 %For $q\neq2$ we are implementing something that is not a matrix norm (better to not comment on it explicitly)
- \fixme{We prospect to expand the choices for \texttt{cg\_norm} in future updates of \NAME, as the \textbf{nonsu2} and \textbf{superc}
-diagonalization modes entail nontrivial subtleties in optimizing 
-the off-diagonal components of $X$.}
+%  \fixme{We prospect to expand the choices for \texttt{cg\_norm} in future updates of \NAME, as the \textbf{nonsu2} and \textbf{superc}
+% diagonalization modes entail nontrivial subtleties in optimizing 
+% the off-diagonal components of $X$.}
+We plan to expand the available options for the {tt cg\_norm} parameter in future \NAME updates, since the {\tt nonsu2} and {\tt superc} diagonalization modes involve subtle challenges in optimizing the off-diagonal components of $X$, due to the coexistence of matrix elements with different physical meanings and/or spanning different energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation.
 \item \texttt{cg\_Ftol} - Controls the fit tolerance, setting the 

### 2025-07-15 04_cbinding.tex
CMake options have changed. Updated table

@@
 The names and inputs of the Julia-wrapped functions are entirely analogous to those of the Python API.
-Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
+% Particular care has to be taken with respect to parallelism: Julia offers an in-house platform for parallel computing with memory sharing through multi-threading.
 At present, there is no integration between this architecture and the MPI-based parallelism of \NAME{}, and their concurrent use in a single program is entirely untested and not encouraged.
-If the \NAME{} library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
+% If the \NAME{} library is compiled with enabled parallelism, MPI support will need to be enabled in the user-created Julia program, by making use of modules such as {\tt  MPI.jl}.
 The {\tt MPI\_COMM\_WORLD} communicator will need to be correctly initialized by the user as well, and the program will need to be run with {\tt  mpiexec/mpirun}.

### 2025-07-15 05_examples.tex
CMake options have changed. Updated table

@@
    !Construct Bethe DOS using SciFortran
+   !de = 2*D/Le
    allocate(Ebands(Le),Dbands(Le))
    Ebands = linspace(-D,D,Le,mesh=de)
-   Dbands = dens_bethe(Ebands,Wband)*de
+   Dbands = dens_bethe(Ebands,D)*de
    !
@@
 
-//Locally defined functions:
+//Locally defined functions: de = 2*D/Le
 Ebands = linspace(-D,D,Le);
-Dbands = dens_bethe(Ebands,Wband,de);
+Dbands = dens_bethe(Ebands,D,de);
 
@@
 close the self-consistency loop and optimize the bath.
-Given the 
-critical importance of this optimization, \NAME provides access to 
-well-tested functions, ensuring stability and reproducibility of 
-results. Alternative optimization methods can also be employed as 
+Given the critical importance of this optimization, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
+Alternative optimization methods can also be employed as 
 needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 

### 2025-07-15 Reply_RefereeA.md
Minimal changes

@@
 
-In particular, we now explicitly indicate the summation upper bound for $n$ by using the number $N_{\rm state\_list}$ of eigenstates contained in the `state_list` class and describing the lower end of the energy spectrum.
-Following the referee's observation, we propagated this correction to all the expression involving a trace over Hamiltonian spectrum. We appreciate the referee's attention to this detail.
+In particular, we now explicitly indicate the upper summation bound for $n$ by using the number $N_{\rm state\_list}$ of eigenstates contained in the `state_list` class and describing the lower end of the energy spectrum.
+Following the referee's observation, we propagated this correction to all the expressions involving a trace over the Hamiltonian spectrum. We appreciate the referee's attention to this detail.
 

### 2025-07-15 Reply_RefereeB.md
Minimal changes

@@
-We thank the refereee for their time and work in reviewing our
-manuscript. Here below we address point by point all the issues raised
+We thank the referee for their time and work in reviewing our
+manuscript. In the following, we address point by point all the issues raised
 in their reports.
@@
 We are very pleased to hear that the exposition, interfaces, and tutorial examples were found to be helpful and of value to new users.
-We are grateful for your recommendation for publication and your support for open and well-maintained scientific software.
+We are grateful for their recommendation for publication and their support for open and well-maintained scientific software.
 
@@
 The function ${\tt ed\_set\_Hloc}$, introduced in Section 3.1.1, is employed to define the impurity Hamiltonian.
-At this stage of the manuscript, its purpose is solely described: setting the local non-interacting component of the impurity Hamiltonian, without further elaboration.
+At this stage of the manuscript, its purpose is solely as described: setting the local non-interacting component of the impurity Hamiltonian, without further elaboration.
 

### 2025-07-15 01_intro.tex
Minimal changes

@@
 the Python API, ii) the TRIQS interface, iii) the w2dynamics interface and iv) an experimental, yet operative, Julia API.
-Finally, in \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and  all the discussed extensions with a series of illustrative examples. 
-In \secu{SecConclusions} we present some concluding remarks and considerations.
+In \secu{SecExamples} we discuss the functionalities and the capabilities of \NAME and  all the discussed extensions with a series of illustrative examples. 
+Finally, in \secu{SecConclusions} we present some concluding remarks and considerations.
 

### 2025-07-15 02_install.tex
Minimal changes

--- 2025-06-10 02_install.tex
@@
   \hline
-  -D{\bf PREFIX}          & Install directory  & {\color{xkcdEmerald} $\sim$/opt/EDIpack/TAG/PLAT/BRANCH} \\
-  -D{\bf USE\_MPI}       & MPI support  &  True/{\color{xkcdEmerald}False}\\
-  -D{\bf WITH\_INEQ}   & multi-impurities support & {\color{xkcdEmerald}True}/{False}\\
-  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}/{False}\\ 
-  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}/TESTING/DEBUG \\
+  -D{\bf CMAKE\_INSTALL\_PREFIX}          & Install prefix override  & {\color{xkcdEmerald} None}\textbf{/}User-defined path \\
+
+  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
+  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
+  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
+  &&{\color{xkcdEmerald}BRANCH} (\textit{main/debug/...})\textbf{/}\\
+  &&$\sim$/opt/edipack/custom \\
+  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
+  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
+  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
+  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
  \hline

### 2025-07-15 Reply_RefereeB.md
Further tweaks in the installation section: cmake flags have changed

@@
 Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization.
-Moreover, this code snippet is useful to understand the structure of the ${\tt sparse_map}$ used to implement fast-algorithm for the evaluation of the reduced impurity density matrix in section 3.5.2.
+Moreover, this code snippet is useful to understand the structure of the ${\tt sparse_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.
 
@@
 Rather, it is a general approach for handling parallel matrix distribution in any programming environment where the global matrix is divided into row blocks across multiple processing units.
-To avoid potential confusion and to make the implementation choices more transparent to the reader in the revised we now write:
+To avoid potential confusion and to make the implementation choices more transparent to the reader in the revised, we now write:
 
@@
 Here, \texttt{istart} and \texttt{iend} define the global index range $[q_1, q_Q]$ assigned to the thread, corresponding to $q_1 = \texttt{istart}$ and $q_Q = \texttt{iend}$.
-The variable \texttt{ishift} $= \texttt{istart} - 1$ allows for mapping between the local index $q$ and the global index $i$ through the simple relation $i = q + \texttt{ishift}$.
+The variable \texttt{ishift} $= \texttt{istart} - 1$ allows mapping between the local index $q$ and the global index $i$ through the simple relation $i = q + \texttt{ishift}$.
 This mapping ensures consistent global indexing while enabling efficient local computation.*"
@@
 The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis.
-We also recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph at page 16 in a more precise way as:
+We also recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as
 
 "*The module ${\tt ED\_GFMATRIX}$ implements the class ${\tt gfmatrix}$, which provides an efficient and flexible representation of DCFs.
-It is structured as a hierarchical, or {\it multi-layered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.
+It is structured as a hierarchical, or {\it multilayered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.
 This structure allows the ${\tt gfmatrix}$ class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$.
@@
 In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
-${\mathcal O}=c_{\alpha\sigma}+c_{\beta\sigma}$, along wit the identity 
+${\mathcal O}=c_{\alpha\sigma}+c_{\beta\sigma}$, along with the identity 
 $G_{\alpha\beta\sigma\sigma}=\tfrac{1}{2}(C_{\mathcal O} - G_{\alpha\alpha\sigma\sigma} - G_{\beta\beta\sigma\sigma})$,
@@
 We are indebted with the referee for pointing out this important subtlety, which in fact extends to both sections 3.8 and 3.9.
-In the original version of the manuscript, the partition function $Z$ appearing in different expressions (including the Eq.(18) indicated the referee), may have misleadingly suggested that it was being evaluated exactly, even though the trace had been truncated.
+In the original version of the manuscript, the partition function $Z$ appearing in different expressions (including the Eq.(18) indicated by the referee), may have misleadingly suggested that it was being evaluated exactly, even though the trace had been truncated.
 
 In the revised manuscript we have corrected this issue.
-We now use the symbol $Z$ to indicate the exact partition function and reserve the symbol $\tilde{Z}$ to  explicitly indicated the partition function approximated using only the finite set of low-energy eigenstates retained in the trace, i.e., those contributing significantly due to their large Boltzmann weights.
+We now use the symbol $Z$ to indicate the exact partition function and reserve the symbol $\tilde{Z}$ to explicitly indicate the partition function approximated using only the finite set of low-energy eigenstates retained in the trace, i.e., those contributing significantly due to their large Boltzmann weights.
 This makes the approximation consistent on both sides of the involved equations, namely Eqs.
@@
 
-While for function matrices with a particularly symmetric structure the choice of the metric is inessential, it might dramatically affect the quality of the optimization in more general cases. 
+While for matrix functions with a particularly symmetric structure the choice of the metric is inessential, it might dramatically affect the quality of the optimization in more general cases. 
 The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric.
@@
 This requires careful tuning of the control parameters to ensure that the optimization does not disproportionately favor certain matrix elements over others, thereby maintaining the overall fidelity of the bath representation.
-In this sense, introducing other norms which ensure a better balance among the components is a development line to improve EDIpack usage.
+In this sense, introducing other norms, which ensure a better balance among the components, is a development line to improve EDIpack usage.
 
-In the revised manuscript we amended to this unclear statement writing:   
+In the revised manuscript we amended this unclear statement writing:
 *"We plan to expand the available options for the cg_norm parameter in future EDIpack updates, since the nonsu2 and superc diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X, due to the coexistence of matrix elements with different physical meanings and energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation."*
@@
 However, we recognise the importance of careful design in managing global memory, and we have ensured that such variables are encapsulated within dedicated modules with well defined scopes.
-Should it prove beneficial for future code maintainability or extension by third-party contributors, we are ready to reviewing and refining this aspect of the implementation.
+Should it prove beneficial for future code maintainability or extension by third-party contributors, we are ready to review and refine this aspect of the implementation.
 
@@
 
-We thank the referee for carefully reviewing this sectoin and pointing this out.
+We thank the referee for carefully reviewing this section and pointing this out.
 Indeed, the variable ${\tt Wband}$ should not appear in the code listing, as it corresponds to ${\tt D}$, which is correctly defined earlier in the script.
@@
 We thank the referee for pointing out the ambiguity in this sentence.
-Our intention was to clarify that, although the bath optimization problem is conceptually distinct from the core impurity diagonalization task for which EDIpack was originally developed, nonetheless the package provides access to a well-tested implementation of the conjugate-gradient fitting procedure for the bath optimization.
-We have revised the sentence accordingly in the manuscript to make this connection and the role of these functions more explicit writing:
+Our intention was to clarify that, although the bath optimization problem is conceptually distinct from the core impurity diagonalization task, for which EDIpack was originally developed, nonetheless the package provides access to a well-tested implementation of the conjugate-gradient fitting procedure for the bath optimization.
+We have revised the sentence accordingly in the manuscript to make this connection and the role of these functions more explicit by writing:
 

### 2025-07-15 02_install.tex
Further tweaks in the installation section: cmake flags have changed

@@
   &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
-  &&{\color{xkcdEmerald}BRANCH} (\textit{main/debug/...})\textbf{/}\\
+  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\textbf{/}\\
   &&$\sim$/opt/edipack/custom \\
@@
 retrieve compilation and linking flags. In order to compile Fortran/C++ 
-drivers, the {\tt compilers} conda package will need to be installed.
+programs, the {\tt compilers} conda package will need to be installed.
 
@@
 privileges, the results of the building step are installed by default in user's {\tt HOME}
-directory, specified by the CMake variable {\tt PREFIX}.
+directory.
 As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
@@
   default environment.
-\item A CMake generated {\tt pkg-config} file to be added in
+\item A CMake-generated {\tt pkg-config} file to be added in
   the {\tt PKG\_CONFIG\_PATH} itself.  

### 2025-07-15 03_edipack2.tex
Further tweaks in the installation section: cmake flags have changed

@@
 $$
-where the indices $\{ijkl\}$ condense orbital and spin degrees of freedom, e.g. $i=\alpha\sigma$. 
+where the indices $\{ijkl\}$ refer to the combined spin and internal (orbital, valley...) degrees of freedom, e.g. $i=\alpha\sigma$. 
 Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement.
@@
 In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
-$\OO=c_{\a\s}+c_{\b\s}$, along wit the identity 
+$\OO=c_{\a\s}+c_{\b\s}$, along with the identity 
 $G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$,

### 2025-07-15 04_cbinding.tex
Further tweaks in the installation section: cmake flags have changed

@@
 
-We provide an example script for the simple case of the Bethe lattice in the normal phase in the \secu{SecExamples} folder of the EDIpack2jl repository.
+We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt examples} folder of the EDIpack2jl repository.
 This script is intended to be run serially.

### 2025-07-15 06_conclusions_acknowledgement_appendix.tex
Initial Overleaf Import
Further tweaks in the installation section: cmake flags have changed

@@
 
-\section{Conclusions}
+\section{Conclusions}\label{SecConclusions}
 We have presented \NAME{}, a versatile and high-performance ED solver for generic quantum impurity problems. Building on the massively
@@
 \section*{Acknowledgements}
-We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto-Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, S.~Adler, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.
+We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto-Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, S.~Adler, F.~Paoletti, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.
 
@@
 designed the project, developed the main structure of the software and conceived the computational algorithms in the core library.
-A.A.
+A.A., L.C.
 and M.C.
 conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library.
-M.C.
+A.A., G.M., A.S., S.G.
+and M.C.
 devised the inclusion of the electron-phonon coupling and of the superconducting state.
@@
 M.W. acknowledges support from the Austrian Science Fund (FWF) through grant DOI 10.55776/P36332.
-%G.M.
 G.M. acknowledges support from the MUR - Italian Ministry of University and Research - through the Rita-Levi Montalcini program.

### 2025-07-15 Reply_RefereeA.md
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

@@
 
-We thank the referee for their constructive assessment of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.
+We thank the referee for their positive assessment of our work and for recognizing its value in a more general context. We deeply appreciate their recommendation.
 
@@
 We sincerely appreciate the referee's prompt attention to this matter.
-We must admit that we "inadvertently" overlooked a reference to Section 6, i.e.
+We indeed  "inadvertently" overlooked a reference to Section 6, i.e.
 the conclusions, at the end of the introduction when discussing the manuscript's structure.
@@
 We acknowledge the referee’s observation.
-Although the code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries.
-Regrettably, we do not have any plans to incorporate automatic detection of all pertinent symmetries within the code.
-In the current setup, this would be feasible through an accurate analysis of the effective bath decomposition, as discussed in section 3.6, excluding simpler cases described by `bath_type=normal, hybrid`.
+While the main code currently necessitates manual selection of one of the provided symmetry configurations, we recognize the value of automating the detection of all relevant symmetries.
+In fact, the Triqs interface ${\tt edipack2triqs}$ features an efficient algorithm to automatically recognize the symmetries of the problem and select the appropriate value for ${\tt ed\_mode}$.
+In the actual implementation of the Fortran API this can not be achieved, but we have plans to incorporate it in future release.
+In the current setup, this requires to accurately analyse the model Hamiltonian and the effective bath decomposition, as discussed in section 3.6, at initialization time.
 
-Nevertheless, we are actively exploring development avenues that aim to integrate more sophisticated conservation laws, which would further reduce the matrix dimensions.
+At the same time, we are actively exploring development avenues that aim to integrate more sophisticated conservation laws, which would further reduce the matrix dimensions.
 We are confident that these enhancements would improve code’s flexibility and efficiency in managing systems characterized by intricate symmetries.
@@
 We appreciate the referee's  observation.
-As briefly elaborated upon in the manuscript, the inherently "spiky" nature of the spectral function arises due to the finite size of the system under consideration.
-This finiteness results in a discrete set of poles contributing to the Källén-Lehmann spectral representation.
-To mitigate the singularities associated with these delta-like poles, a common practice involves applying a broadening technique using a Lorentzian function.
-
-The extent of this broadening is controlled by the input parameter `eps`, which determines the width of the Lorentzian function.
+The extent of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`.
 It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each case.
 In the particular examples discussed on page 43 of our manuscript, we have employed a broadening parameter of `eps = 0.01`, expressed in units of the half-bandwidth `D`.
-
-In response to the referee's valuable suggestion, we have updated the manuscript to explicitly specify the value of this broadening parameter in all relevant examples that illustrate the behavior of the spectral function.
-We believe this addition enhances the clarity and reproducibility of our results, and we thank the referee for their constructive feedback.
+In response to the referee's valuable suggestion, we have updated the manuscript  explicitly specifying the value of this broadening parameter.
 

### 2025-07-15 Reply_RefereeB.md
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

@@
 
-To reflect this more nuanced detail, we have revised the paragraph on page 9 to acknowledge that the shift $A_m$ is not universally a free parameter. The new text reads:
-
-*“In many cases, one can reduce the number of excited phonons in the ground state, and consequently the required cutoff, by appropriately choosing the shift $A_m$.
-However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter.
-In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence.”*
-
-This modification ensures that our discussion does not overgeneralise while aligning with the range of physical contexts in which EDIpack may be applied.
-We thank the referee for helping us clarify this important point.
+To reflect this more nuanced detail, we have revised the paragraph on page 9 to acknowledge that the shift $A_m$ is not universally a free parameter.
+This ensures that our discussion does not overgeneralise while aligning with the range of physical contexts in which EDIpack may be applied.
 
@@
 Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization.
-Moreover, this code snippet is useful to understand the structure of the ${\tt sparse_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.
+Moreover, this code snippet is useful to understand the structure of the ${\tt sparse\_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.
 
@@
 The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis.
-We also recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as
+We recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as
 
@@
 By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
-As a result, ${\tt gfmatrix}$ is a core component of EDIpack, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"
+Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"
 
@@
 The bath optimization is a crucial step in the DMFT framework.
-As we discuss in the manuscript, to preserve the general application of EDIpack we introduced several control parameters for the conjugate-gradient fit.
+Hence, to ensure EDIpack has a large degree of versatility while preserving robustness, we introduced several control parameters for the conjugate-gradient fit.
 A key one is the definition of the norm, or distance, between matrix functions appearing in Eq.
@@
 
-While for matrix functions with a particularly symmetric structure the choice of the metric is inessential, it might dramatically affect the quality of the optimization in more general cases. 
+While the choice of metric plays a limited role for matrix-valued functions with particularly symmetric structures, it can significantly impact the quality of the optimization in more general cases. 
 The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric.
@@
 However, we recognise the importance of careful design in managing global memory, and we have ensured that such variables are encapsulated within dedicated modules with well defined scopes.
-Should it prove beneficial for future code maintainability or extension by third-party contributors, we are ready to review and refine this aspect of the implementation.
+Should it prove beneficial for future code maintainability or extension by third-party contributors, we are open to review and refine this aspect of the implementation.
 
@@
 
-*"Given the critical importance of this optimization, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*
+*"Given the critical importance of this step, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*
 

### 2025-07-15 02_install.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

@@
   &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
-  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\textbf{/}\\
+  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\\
   &&$\sim$/opt/edipack/custom \\

### 2025-07-15 03_edipack2.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

@@
 Observables on the physical bosons are linked to the new one via the previous transformation.
-{ \color{red} However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter.
+% { \color{red} However, we stress that this is not always possible: in some generalized models or realistic systems derived from microscopic considerations, $A_m$ may be fixed and not a freely tunable parameter.
 In such cases, the phonon cutoff must be increased accordingly to ensure numerical convergence.
@@
 $\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
-within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation. 
+within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation~\cite{Wallerberger2022PRR}. 
 This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
@@
 By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
-As a result, {\tt gfmatrix} is a core component of \NAME, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.
+Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.
 

### 2025-07-15 05_examples.tex
Iterated Revision: AA, LC, IK, SG and GB. Ready to share to all authors.

--- 2025-07-12 05_examples.tex
@@
    !Construct Bethe DOS using SciFortran
+   !de = 2*D/(Le-1)
    allocate(Ebands(Le),Dbands(Le))
    Ebands = linspace(-D,D,Le,mesh=de)
-   Dbands = dens_bethe(Ebands,Wband)*de
+   Dbands = dens_bethe(Ebands,D)*de
    !
@@
 
-//Locally defined functions:
+//Locally defined functions: de = 2*D/(Le-1)
 Ebands = linspace(-D,D,Le);
-Dbands = dens_bethe(Ebands,Wband,de);
+Dbands = dens_bethe(Ebands,D,de);
 
@@
 close the self-consistency loop and optimize the bath.
-Given the 
-critical importance of this optimization, \NAME provides access to 
-well-tested functions, ensuring stability and reproducibility of 
-results. Alternative optimization methods can also be employed as 
+Given the critical importance of this step, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
+Alternative optimization methods can also be employed as 
 needed \cite{Mejuto-Zaera2020PRB,Huang2023PRB,Nakatsukasa2018SJOSC}. 

### 2025-07-17 Reply_RefereeA.md
Minimal modifications (LC)

@@
 
-We agree with this comment of the referee.
+We agree with this comment by the referee.
 Although it is impossible to do justice to the wide literature accumulated over the years, we have made concerted efforts to incorporate key references that reflect the breadth and depth of research in this field.
@@
 We sincerely appreciate the referee's prompt attention to this matter.
-We indeed  "inadvertently" overlooked a reference to Section 6, i.e.
-the conclusions, at the end of the introduction when discussing the manuscript's structure.
+We indeed inadvertently overlooked a reference to Section 6 at the end of the introduction when discussing the manuscript's structure.
 We resolved this issue in the revised text by including the sentence:
@@
 
-We appreciate your attention to this detail and believe that your suggestion will enhance the clarity of our presentation.
+We appreciate their attention to this detail and believe that their suggestion will enhance the clarity of our presentation.
 
@@
 In fact, the Triqs interface ${\tt edipack2triqs}$ features an efficient algorithm to automatically recognize the symmetries of the problem and select the appropriate value for ${\tt ed\_mode}$.
-In the actual implementation of the Fortran API this can not be achieved, but we have plans to incorporate it in future release.
+In the actual version of the Fortran API this is not implemented yet, but we have plans to incorporate it in future release.
 In the current setup, this requires to accurately analyse the model Hamiltonian and the effective bath decomposition, as discussed in section 3.6, at initialization time.
@@
 We appreciate the referee's  observation.
-The extent of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`.
-It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each case.
+The size of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`.
+It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each simulation.
 In the particular examples discussed on page 43 of our manuscript, we have employed a broadening parameter of `eps = 0.01`, expressed in units of the half-bandwidth `D`.
-In response to the referee's valuable suggestion, we have updated the manuscript  explicitly specifying the value of this broadening parameter.
+In response to the referee's suggestion, we have updated the manuscript  explicitly specifying the value of this broadening parameter.
 

### 2025-07-17 Reply_RefereeB.md
Minimal modifications (LC)

@@
 
-We sincerely thank the referee for their positive and encouraging comments.
+We sincerely thank the referee for their positive comments.
 We are very pleased to hear that the exposition, interfaces, and tutorial examples were found to be helpful and of value to new users.
@@
 
-*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in their number representation.
+*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in occupation number representation.
 This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D^{\mathcal{S}}$.”*
 
-This new formulation replaces the previous wording and makes explicit the distinction between the consecutive indexing of the sector states $|i\rangle$ and the Fock states in the integer-based occupation number representation $|I_e\rangle$.
+This new formulation replaces the previous wording and makes explicit the distinction between the consecutive indexing of the sector states $|i\rangle$ and the Fock states in the occupation number representation $|I_e\rangle$.
 In doing so, we clarify that the mapping $\mathcal{M}$ is what connects the two encodings of the same physical state.
@@
 We thank the referee for raising this point.
-The code snippet on page 12 was originally included to illustrate the concrete implementation of the mapping from Fock states to symmetry sectors for different values of ${\tt ed\_mode}$.
+The purpose of the code snippet in question is to illustrate the concrete implementation of the mapping from Fock states to symmetry sectors for different values of ${\tt ed\_mode}$.
 Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization.
-Moreover, this code snippet is useful to understand the structure of the ${\tt sparse\_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.
+We suggest this code snippet is useful to understand the structure of the ${\tt sparse\_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.
 
@@
 Second, memory usage is optimized by avoiding redundant storage.
-The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis.
+The internal design separates spectral data and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis.
 We recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as
@@
 By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
-Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"
+Through the use of ${\tt gfmatrix}$ EDIpack achieves efficient memory management, consistent storage of spectral data and high-performance post-processing.*"
 
@@
 These listings are intended to complement the discussion by offering concrete examples that clarify how the formal logic is realized in code.
-Given the potential for confusion when dealing with basis state reconstruction and operator ordering in fermionic systems, we believe that these examples will be of interest and practical benefit to users aiming to extend or interface with the library.
+Given the potential for confusion when dealing with basis state reconstruction and operator ordering in fermionic systems, we believe that these examples can be of interest and practical benefit to users aiming to extend or interface with the library.
 
@@
 
-The bath optimization is a crucial step in the DMFT framework.
+The bath optimization is a crucial step in the DMFT-ED algorithm.
 Hence, to ensure EDIpack has a large degree of versatility while preserving robustness, we introduced several control parameters for the conjugate-gradient fit.
@@
 
-*"Given the critical importance of this step, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*
+*"Given the critical importance of this step, EDIpack provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results.
+This task is conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package."*
 
@@
 We agree with the referee that the implementation of ${\tt generate_kgrid}$ could be simplified for clarity.
-The purpose of this function is merely to construct a uniform 2D grid in the Brillouin zone using the reciprocal lattice vectors, which can indeed be achieved with more concise or intuitive code.
+The purpose of this function is merely to construct a uniform 2D grid in the Brillouin zone using the reciprocal lattice vectors.
+In the case of the square lattice discussed in this example, this implementation is indeed rather overcomplicated, given the orthodonality of the reciprocal lattice vectors.
+Being completely generic, however, this function can also be used for less simple 2d lattices (e.g.
+triangular).
+We further note that in the way it is written, relying entirely on numpy functions, it avoids making use of explicit python ${\tt for}$ loops, which cause performance degradation when the requested number of k-points is large.
 
@@
 For more involved tight-binding constructions, users may wish to rely on specialized libraries such as PythTB, which are designed for this purpose.
-Our goal here was only to provide a minimal working example for illustration.
 

### 2025-07-17 03_edipack2.tex
Minimal modifications (LC)

@@
 $\MM:\SS_{\vec{Q}}\rightarrow \FF_e$ that relates the consecutive indexing of the electronic states  $\ket{i}$
-within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in their number representation~\cite{Wallerberger2022PRR}. 
+within a given symmetry sector $\SS_{\vec{Q}}$ to the Fock states $\ket{I_e}$ in the electronic Fock space in occupation number representation~\cite{Wallerberger2022PRR}. 
 This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D_{\SS_{\vec{Q}}}$. 
@@
 \end{lstlisting}
-where {\tt NORB} is the number of orbitals $N_\a$.
+where {\tt NORB} is the number of orbitals $N_\a$ and $\{ijkl\}$ refer to the combined spin ({\tt u/d}) and internal (e.g.
+orbital index) degrees of freedom.
+For example, if {\tt i1} refers to orbital 1, spin up, it is written explicitly as {\tt 1 u}.
 Each line defines a two-body second-quantized operator of the form 
@@
 $$
-where the indices $\{ijkl\}$ refer to the combined spin and internal (orbital, valley...) degrees of freedom, e.g. $i=\alpha\sigma$. 
+
 Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement.
@@
 By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead.
-Through the use of ${\tt gfmatrix}$ EDIpack achieve and efficient memory management, consistent storage of spectral data, and high-performance post-processing.
+Through the use of ${\tt gfmatrix}$ EDIpack achieves efficient memory management, consistent storage of spectral data and high-performance post-processing.
 

### 2025-07-17 05_examples.tex
Minimal modifications (LC)

@@
 close the self-consistency loop and optimize the bath.
-Given the critical importance of this step, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results, even though this task remains conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
+Given the critical importance of this step, \NAME provides access to a well-tested implementation of the conjugate gradient method for performing the bath optimization, ensuring stability and reproducibility of the results.
+This task is conceptually distinct from the  diagonalization of the impurity problem, which remains the core focus of the package.
 Alternative optimization methods can also be employed as 

### 2025-07-18 Reply_RefereeA.md
GB pass on manuscript and replies

@@
 
-We appreciate their attention to this detail and believe that their suggestion will enhance the clarity of our presentation.
+We appreciate the referee's attention to this detail and believe that their suggestion will enhance the clarity of our presentation.
 
@@
 In fact, the Triqs interface ${\tt edipack2triqs}$ features an efficient algorithm to automatically recognize the symmetries of the problem and select the appropriate value for ${\tt ed\_mode}$.
-In the actual version of the Fortran API this is not implemented yet, but we have plans to incorporate it in future release.
+In the actual version of the Fortran API this is not implemented yet, but we have plans to incorporate it in a future release.
 In the current setup, this requires to accurately analyse the model Hamiltonian and the effective bath decomposition, as discussed in section 3.6, at initialization time.
@@
 We appreciate the referee's  observation.
-The size of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`.
+The width of the Lorentzian broadening of the spectral poles is controlled by the input parameter `eps`.
 It is important to note that the value of `eps` is not fixed universally but rather is chosen based on the specific requirements of each simulation.

### 2025-07-18 Reply_RefereeB.md
GB pass on manuscript and replies

@@
 
-*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in occupation number representation.
+*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states $|i\rangle$ within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in occupation number representation.
 This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D^{\mathcal{S}}$.”*
@@
 "*The module ${\tt ED\_GFMATRIX}$ implements the class ${\tt gfmatrix}$, which provides an efficient and flexible representation of DCFs.
-It is structured as a hierarchical, or {\it multilayered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.
+It is structured as a hierarchical, or *multilayered*, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.
 This structure allows the ${\tt gfmatrix}$ class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$.
@@
 The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric.
-In either case, the coexistence of components having a very different physical interpretation, e.g., anomalous terms, and/or spanning very different energy scales represents a serious challenge to the optimization of the bath.
+In either case, the coexistence of off-diagonal components having a very different physical origin, e.g.
+anomalous vs normal terms, and/or having different order of magnitude, represents a serious challenge to the optimization of the bath.
 This requires careful tuning of the control parameters to ensure that the optimization does not disproportionately favor certain matrix elements over others, thereby maintaining the overall fidelity of the bath representation.
-In this sense, introducing other norms, which ensure a better balance among the components, is a development line to improve EDIpack usage.
+In this sense, introducing other norms which allow a fine tuning of the balance among the components, is a development line to improve EDIpack usage.
 
 In the revised manuscript we amended this unclear statement writing:
-*"We plan to expand the available options for the cg_norm parameter in future EDIpack updates, since the nonsu2 and superc diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X, due to the coexistence of matrix elements with different physical meanings and energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation."*
+*"We plan to expand the available options for the cg_norm parameter in future EDIpack updates, since the nonsu2 and superc diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X.
+These difficulties are related to the coexistence of matrix elements with different physical origin, so that they can live on different orders of magnitude, hence requiring carefully balanced optimization metrics to ensure an accurate bath representation."*
 
@@
 In principle, it is indeed possible to eliminate the use of global variables by explicitly passing all data structures through subroutine arguments.
-However, in the context of Fortran, and similarly in other compiled languages, global variables (typically implemented via module-level variables) do not incur any performance or memory management penalties.
+However, in the context of Fortran, and similarly in other static languages, global variables (typically implemented via module-level variables) do not incur any performance or memory management penalties.
 
 Their use in EDIpack is deliberate and serves to maintain clarity and modularity in the code, particularly for widely shared objects such as configuration parameters, system-wide operators, or state indexing data.
-Removing these global definitions would require passing a large number of arguments through deep call chains, which we believe would significantly increase code complexity, reduce readability, and introduce greater potential errors, without offering any computational or architectural advantages.
+Removing these global definitions would require passing a large number of arguments through deep call chains, which we believe would significantly increase code complexity, reduce readability, and introduce greater potential errors.
+All of this without offering any computational or architectural advantage that fits our current development plan.
 
@@
 
-We agree with the referee that the implementation of ${\tt generate_kgrid}$ could be simplified for clarity.
+We agree with the referee that the implementation of ${\tt generate\_kgrid}$ could be simplified for clarity.
 The purpose of this function is merely to construct a uniform 2D grid in the Brillouin zone using the reciprocal lattice vectors.
-In the case of the square lattice discussed in this example, this implementation is indeed rather overcomplicated, given the orthodonality of the reciprocal lattice vectors.
+In the case of the square lattice discussed in this example, this implementation is indeed rather overcomplicated, given the orthogonality of the reciprocal lattice vectors.
 Being completely generic, however, this function can also be used for less simple 2d lattices (e.g.

### 2025-07-18 03_edipack2.tex
GB pass on manuscript and replies

@@
 % the off-diagonal components of $X$.}
-We plan to expand the available options for the {tt cg\_norm} parameter in future \NAME updates, since the {\tt nonsu2} and {\tt superc} diagonalization modes involve subtle challenges in optimizing the off-diagonal components of $X$, due to the coexistence of matrix elements with different physical meanings and/or spanning different energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation.
+We plan to expand the available options for the {tt cg\_norm} parameter in future \NAME updates, since the {\tt nonsu2} and {\tt superc} diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X.
+These difficulties are related to the coexistence of matrix elements with different physical origin, so that they can live on different orders of magnitude, hence requiring carefully balanced optimization metrics to ensure an accurate bath representation.
 \item \texttt{cg\_Ftol} - Controls the fit tolerance, setting the 

### 2025-07-18 05_examples.tex
GB pass on manuscript and replies

@@
 library and its interfaces as a solver for DMFT through a variety of examples. We also discuss in detail the relevant code parts from different programming languages. 
-The codes,the data and the script to generate the figures presented here can be found in the repository \href{https://github.com/EDIpack/EDIpack2examples}{github.com/EDIpack/EDIpack2examples}.
-
-Some tasks -- particularly those associated with the implementation of the DMFT self-consistency -- are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
+The codes, the data and the scripts to rework some of the examples presented here, as well as additional upcoming tutorials, can be found in the repository \href{https://github.com/EDIpack/EDIpack2examples}{github.com/EDIpack/EDIpack2examples}.
+
+Some tasks---particularly those associated with the implementation of the DMFT self-consistency---are inherently independent of \NAME itself, and the impurity solver is agnostic about them. 
 Thus, in the implementations using Fortran, Python or other \NAME interfaces to scientific toolboxes, we adopt a reverse communication strategy, which requires the user to independently carry out these parts or, equivalently, to take advantage of existing utilities.

### 2025-08-07 05_examples.tex
Updated text and bib to SciPost proofs.

@@
 As shown in Ref. \cite{Amaricci2023PRB}, this model exhibits an excitonic phase at moderate
-interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2020,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
+interactions in which opposite orbital electrons and holes across the band gap bind and form a coherent phase \cite{Knolle2017PRL,Jia2022NP,Varsano2020NN,Blason2020PRB,Amaricci2023PRB,Giuli2023PRB}
 

### 2025-08-29 02_install.tex
Proofs update. Minor typos and tables fixed

@@
 \noindent
-The CMake configuration can be further tuned using the following variables:
-\begin{center}
+The CMake configuration can be further tuned using the following
+variables:
+\begin{table}
+\centering
 \small
@@
   &&$\sim$/opt/edipack/custom \\
-  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
+  -D{\bf USE\_MPI}       & MPI support  &  \textbf{/}{\color{xkcdEmerald}True}\textbf{/}{False}\\
   -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
@@
 \end{tabular}
-\end{center}
+\caption{{\bf CMake optional flags}. The table lists the CMake
+  optional flags available for the configuration step of the \NAME
+  installation. Default variables are indicated in green.}
+\label{Table1}
+\end{table}
 %
@@
 In order to avoid possible conflicts or the requirement for administrative
-privileges, the results of the building step are installed by default in user's {\tt HOME}
+privileges, the results of the building step are installed by default
+in the user's {\tt HOME}
 directory.
@@
 \begin{enumerate}
-\item  A CMake-generated configuration file for an environment module which allows users to load and unload the library at any time. This is
-  preferred solution for HPC systems. 
+\item  A CMake-generated configuration file for an environment module
+  which allows users to load and unload the library at any time. This
+  is the preferred solution for HPC systems. 
 \item A CMake-generated bash script to be sourced (once or

### 2025-08-29 03_edipack2.tex
Proofs update. Minor typos and tables fixed

@@
 \subsubsection{System setup}
-We consider a quantum impurity system comprised by a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
+We consider a quantum impurity system comprised of a single multi-orbital impurity, a bath discretized into a number $N_\mathrm{bath}$ of {\it elements} possibly endowed with an internal structure, and a number of available phonons.
 The total size of the system is determined by three contributions: i) the number of impurity orbitals $N_\a$, ii) the total count of electronic bath levels $N_\mathrm{b}$, and iii) by the maximum  number of allowed phonons $N_\mathrm{ph}$, introducing a cutoff to the unbounded dimension of the local phonon Hilbert space.
@@
 {\bf superc}, {\bf nonsu2} are available. A summary of the sector properties is provided in
-Table~(\ref{TabSector}).
+Table~(\ref{Table2}).
 
@@
 
-\begin{table}%[ht]
-\begin{tabularx}{\linewidth}{ |X|X|X| }
+\begin{table}
+  \centering
+  \begin{tabular}{ |c|c|c| }
  \hline
@@
  \hline  
-\end{tabularx}
-\vspace{2mm}
-\caption{\label{TabSector}
+\end{tabular}
+\caption{
  {\bf Quantum Numbers}.
@@
 given value of the quantum numbers $\vec{Q}$.}
+\label{Table2}
 \end{table}
@@
 
-We summarize the total number $N_s$ of electronic levels of the quantum impurity system according to the value of $N_\a$, $N_\mathrm{bath}$ and the bath topology in the following table:
-\begin{center}
+We summarize the total number $N_s$ of electronic levels of the
+quantum impurity system according to the value of $N_\a$,
+$N_\mathrm{bath}$ and the bath topology in Table~\ref{Table3}:
+
+\begin{table}
+\centering
 \begin{tabular}{ |c||c|c|c|c| } 
@@
 \end{tabular}
-\end{center}
-
-\vspace{2mm}
+\caption{
+  {\bf Total number of electronic levels}.
+  The table summarizes the possible number of the electronic levels $N_s$ (second row) according to the value of the {\tt bath\_type}
+(first row), the number of impurity orbitals $N_\alpha$ and the number
+of the bath sites $N_{\rm bath}$.}
+\label{Table3}
+\end{table}
+
+% \vspace{2mm}
 All the procedures concerning the bath
@@
 
-The following table summarizes the total number of parameters $N_\mathrm{param}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:
-
-\begin{center}
+Table~\ref{Table4} summarizes the total number of parameters $N_\mathrm{param}$, as returned by the function {\tt ed\_get\_bath\_dimension} and required to describe the bath according to the values of {\tt ed\_mode} and {\tt bath\_type}:
+
+\begin{table}
+\centering
 \begin{tabular}{ |c||c|c|c|c| } 
@@
 \end{tabular}
-\end{center}
+\caption{
+  {\bf Total number of bath parameters}. The table lists the number of
+  bath parameters $N_{\rm param}$ according to the conserved
+  symmetry {\tt ed\_mode} (first column), and the
+  bath topology {\tt bath\_type} (first
+  row). The number of parameters is obtained as a function of the
+  impurity orbitals $N_\alpha$, the number of spin channels
+  $N_\sigma$, the number of bath sites $N_{\rm bath}$ and, where
+  applicable, the size of the matrix basis used to describe the {\tt
+    replica/general} bath structure $N_{\rm sym}$.}
+\label{Table4}
+\end{table}
 
@@
 in Ref.~\onlinecite{Amaricci2022CPC}, and focusing on the impact of the choice of {\tt ed\_mode}. 
-For sake of clarity, here we focus on the purely electronic case, i.e.
+For the sake of clarity, here we focus on the purely electronic case, i.e.
 neglecting the electron-phonon part.
@@
 \subsection{Dynamical correlation functions}\label{sSecGF}
-The determination of the low energy part of the Hamiltonian's spectrum
+The determination of the low-energy part of the Hamiltonian's spectrum
 enables evaluation of the Dynamical Correlation Functions (DCFs) using Krylov subspace algorithm.
@@
 poles $dE^{\nu}_{mn}(\AA)$ for the operator $\AA$, for every initial state $\ket{\psi_n}$
-contributing to the low energy spectrum, for every order $m$ of the
+contributing to the low-energy spectrum, for every order $m$ of the
 Krylov subspace algorithm and for channel $\nu$.
@@
 
-For sake of simplicity, this section focuses on the zero-temperature limit, 
+For the sake of simplicity, this section focuses on the zero-temperature limit, 
 assuming a non-degenerate ground state $\ket{\psi}$ present in the 

### 2025-08-29 04_cbinding.tex
Proofs update. Minor typos and tables fixed

@@
 The interface layer is contained in the Fortran module {\tt
-  EDIPACK\_C}. It contains a common part and two set of functions,
+  EDIPACK\_C}. It contains a common part and two sets of functions,
 one to interface the procedures from \NAME and a second
@@
 EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
-The code can be obtained and and installed from source as:
+The code can be obtained and installed from source as:
 \begin{lstlisting}[style=mybash]
@@
   libedipack\-\_cbindings.so (.dylib)} containing the Fortran-C bindings
-for \NAME. By default the library search proceeds as follow: 
+for \NAME. By default the library search proceeds as follows: 
 \begin{enumerate}

### 2025-08-29 05_examples.tex
Proofs update. Minor typos and tables fixed

@@
 
-\item Use the dedicated
+\item[{\tiny {\bf EDIpack}}]  Use the dedicated
   input/output \NAME procedures to retrieve the self-energy functions  
